### 2022-03-16 Manuscript analyses.Rmd
Start Rmd with summary tables

---
title: "Manuscript analyses"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type= "text/css">

.## Figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

## Table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

```{r library}
library(tidyverse)
library(ggplot2)
library(gtsummary)
library(labelled)
# library(survival)
# library(survminer)
```

```{r load}
path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias")

Characteristics <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Characteristics", skip = 1, n_max = 54) %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Counts <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Counts") %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Infections <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Infections") %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Support <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Support") %>% 
  mutate(MRN = as.character(MRN),
         MRN = coalesce(MRN, PT))
Pneumo_titers <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Pneumo Titers") %>% 
  mutate(MRN = as.character(MRN))
Other_titers <-
  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
                    sheet = "Other Titers") %>% 
  mutate(MRN = as.character(MRN))
```

```{r join}
cart <- full_join(Characteristics, Counts, by = c("PT", "MRN")) %>% 
  full_join(., Infections, by = c("PT", "MRN")) %>% 
  full_join(., Support, by = c("PT", "MRN", "Date of CAR T infusion")) %>% 
  full_join(., Pneumo_titers, by = c("PT", "MRN")) %>% 
  select(-`Date of leukapheresis.y`, `Date of leukapheresis` = `Date of leukapheresis.x`) %>% 
  full_join(., Other_titers, by = c("PT", "MRN"))
```

```{r data cleaning}
cart1 <- cart %>% 
  # defining BMI categories
  mutate(bmicat = case_when(
    `BMI at apheresis` < 25             ~ "< 25 kg/m2",
    `BMI at apheresis` >= 25 & 
      cart$`BMI at apheresis` < 30      ~ "25 to < 30 kg/m2",
    `BMI at apheresis` >= 30            ~ "≥ 30 kg/m2"
  ),
  bmicat = factor(bmicat, levels = c("< 25 kg/m2", "25 to < 30 kg/m2", "≥ 30 kg/m2"))
  ) %>% 
  mutate(bmicat2 = case_when(
    `BMI at apheresis` < 25             ~ "< 25 kg/m2",
    `BMI at apheresis` >= 25            ~ "≥ 25 kg/m2"
  ),
  bmicat2 = factor(bmicat2, levels = c("< 25 kg/m2", "≥ 25 kg/m2"))
  ) %>% 
  # age categories
  mutate(agecat = case_when(
    Age < 65                            ~ "< 65 years",
    Age >= 65                           ~ "≥ 65 years"
  ),
  agecat = factor(agecat, levels = c("< 65 years", "≥ 65 years"))
  ) %>% 
  mutate_at(c("Extramedullary Disease? (yes=1, no=0)",
              "ECOG > or = 2? (Yes=1, No=0)",
              "Deletion 17p prior to CAR-T infusion (yes=1, no=0)",
              "t(4:14) prior to CAR-T infusion (yes=1, no=0)",
              "t(14:16) prior to CAR-T infusion (yes=1, no=0)",
              "Bridging Therapy (Yes=1, No=0)",
              "Prior auto SCT (yes=1, no=0)",
              "Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)"), 
            ~ case_when(
              . == 1                                              ~ "YES",
              . == 0                                              ~ "NO",
              TRUE                                                ~ NA_character_
            )) %>% 
  # tumor burden
  mutate(tumor_burden = case_when(
    `High Marrow Burden? (yes=1, no=0)` == "NO" ~ "Low",
    `High Marrow Burden? (yes=1, no=0)` == "YES" ~ "High"),
    tumor_burden = factor(tumor_burden, levels = c("Low", "High"))
  ) %>% 
  # ECOG
  mutate(`ECOG at LD (at baseline visit)` = case_when(
    `ECOG at LD (at baseline visit)` == 0 | 
      `ECOG at LD (at baseline visit)` ==1 ~ "0-1"
  )) %>% 
  # cytogenetics
  mutate(cyto = case_when(
    `ECOG > or = 2? (Yes=1, No=0)` == "YES" | 
      `t(4:14) prior to CAR-T infusion (yes=1, no=0)` == "YES" | 
      `t(14:16) prior to CAR-T infusion (yes=1, no=0)` == "YES"      ~ "YES",
    `ECOG > or = 2? (Yes=1, No=0)` == "NO" &
      `t(4:14) prior to CAR-T infusion (yes=1, no=0)` == "NO" &
      `t(14:16) prior to CAR-T infusion (yes=1, no=0)` == "NO"       ~ "NO"
  )) %>% 
  # refractory status
  mutate_at(c("Lenalidomide (exposed=0 vs. refractory=1)",
              "Bortezomib (exposed=0 vs. refractory=1)",
              "Carfilzomib (exposed=0 vs. refractory=1)",
              "Pomalidomide (exposed=0 vs. refractory=1)",
              "Daratumumab (exposed=0 vs. refractory=1)"), 
            ~ case_when(
              . == 1                                              ~ "Refractory",
              . == 0                                              ~ "Exposed",
              TRUE                                                ~ NA_character_
            )) %>% 
  mutate(immuno = case_when(
    `Lenalidomide (exposed=0 vs. refractory=1)` == "Exposed" &
      `Pomalidomide (exposed=0 vs. refractory=1)` == "Exposed"        ~ "NO",
    `Lenalidomide (exposed=0 vs. refractory=1)` == "Refractory" |
      `Pomalidomide (exposed=0 vs. refractory=1)` == "Refractory"     ~ "YES"
  )) %>% 
  mutate(proteasome = case_when(
    `Bortezomib (exposed=0 vs. refractory=1)` == "Exposed" &
      `Bortezomib (exposed=0 vs. refractory=1)` == "Exposed"      ~ "NO",
    `Bortezomib (exposed=0 vs. refractory=1)` == "Refractory" |
      `Bortezomib (exposed=0 vs. refractory=1)` == "Refractory"   ~ "YES"
  )) %>% 
  mutate(dara = case_when(
    `Daratumumab (exposed=0 vs. refractory=1)` == "Refractory"      ~ "YES",
    `Daratumumab (exposed=0 vs. refractory=1)` == "Exposed"             ~ "NO"
  )) %>% 
  mutate(doubleref = case_when(
    proteasome == "NO" | 
      immuno == "NO"                                              ~ "NO",
    proteasome == "YES" &
      immuno == "YES"                                         ~ "YES"
  )) %>% 
  mutate(tripleref = case_when(
    proteasome == "NO" | 
      immuno == "NO" |
      `Daratumumab (exposed=0 vs. refractory=1)` == "Exposed"      ~ "NO",
    proteasome == "YES" &
      immuno == "YES" &
      `Daratumumab (exposed=0 vs. refractory=1)` == "Refractory"        ~ "YES"
  )) %>% 
  mutate(pentaref = case_when(
    `Bortezomib (exposed=0 vs. refractory=1)` == "Exposed" | 
      `Carfilzomib (exposed=0 vs. refractory=1)` == "Exposed" |
      `Lenalidomide (exposed=0 vs. refractory=1)` == "Exposed" | 
      `Pomalidomide (exposed=0 vs. refractory=1)` == "Exposed" | 
      `Daratumumab (exposed=0 vs. refractory=1)` == "Exposed"     ~ "NO",
    `Bortezomib (exposed=0 vs. refractory=1)` == "Refractory" & 
      `Carfilzomib (exposed=0 vs. refractory=1)` == "Refractory" &
      `Lenalidomide (exposed=0 vs. refractory=1)` == "Refractory" & 
      `Pomalidomide (exposed=0 vs. refractory=1)` == "Refractory" & 
      `Daratumumab (exposed=0 vs. refractory=1)` == "Refractory"  ~ "YES"
  )) %>% 
# CRS 
  mutate(CRS_any = ifelse(`Max CRS grade (0-5)` == 0, "NO", "YES"),
         CRS_any2 = ifelse(CRS_any== "NO", 0, 1),
         CRS_gradecat = case_when(
           `Max CRS grade (0-5)` == 0                             ~ "No CRS",
           `Max CRS grade (0-5)` == 1                             ~ "Grade 1 or 2",
           `Max CRS grade (0-5)` == 2                             ~ "Grade 1 or 2",
           `Max CRS grade (0-5)` >= 3                             ~ "Grade ≥3"),
         CRS_gradecat = factor(CRS_gradecat, levels = c("No CRS", "Grade 1 or 2", "Grade ≥3"))
  ) %>% 
  # mutate( = case_when(
  #    == 30                ~ NA,
  #   TRUE                          ~ CRS_fup
  # )) %>% 
  # ICANS 
  mutate(ICANS_any = ifelse(`Max ICANS (relative to infusion)` == 0, "NO", "YES"),
         ICANS_any2 <- ifelse(ICANS_any == "NO", 0, 1),
         ICANS_gradecat = case_when(
           `Max ICANS (relative to infusion)` == 0 ~              "No ICANS",
           `Max ICANS (relative to infusion)` == 1 ~              "Grade 1 or 2",
           `Max ICANS (relative to infusion)` == 2 ~              "Grade 1 or 2",
           `Max ICANS (relative to infusion)` >= 3 ~              "Grade ≥3"),
         ICANS_gradecat = factor(ICANS_gradecat, levels = c("No ICANS", "Grade 1 or 2", "Grade ≥3"))
  )

# # CrCl
# table(cart$`Baseline CrCl`)
# cart$crcl[cart$`Baseline CrCl` == ">70" | cart$`Baseline CrCl` == "60.8" | cart$`Baseline CrCl` == "62" | cart$`Baseline CrCl` == "67"] <- ">60"
# cart$crcl[cart$`Baseline CrCl` == "25" | cart$`Baseline CrCl` == "27" | cart$`Baseline CrCl` == "34" | cart$`Baseline CrCl` == "41" | cart$`Baseline CrCl` == "43" | cart$`Baseline CrCl` == "50" | cart$`Baseline CrCl` == "54" | cart$`Baseline CrCl` == "55"] <- "≤60"
# table(cart$crcl)
# # CRS
# table(cart$`Max CRS grade (0-5)`)
# as.factor(cart$`Max CRS grade (0-5)`)
# table(cart$`Duration of CRS (days)`)
# table(cart$`Duration of ICANS (days)`)
# # steroid use
# table(cart$`Steroid use(Yes, No)`)
# 
# 
# 
# # dose reduction
# cart$`Fludarabine Dose Reduction`[cart$`Fludarabine Dose Reduction` == "YES (HD)"] <- "YES"
# table(cart$`Fludarabine Dose Reduction`)
# 
# # RSS
# table(cart$`R-ISS at CAR-T Infusion`)
# cart$`R-ISS at CAR-T Infusion`[cart$`R-ISS at CAR-T Infusion` == "R-ISS  II"] <- "R-ISS II"

# day 30 + MRD for figure
#table(tct$day30_response_revised, tct$MRD_status, useNA= "ifany")
#table(tct$day30_response_revised, tct$day30_response, useNA= "ifany")
#tct$ORR_MRD <- case_when(#tct$day30_response_revised== "SD" ~ "SD",
                         #tct$day30_response_revised== "PD" ~ "PD",
                         #tct$day30_response_revised== "MR" ~ "MR",
#                         tct$day30_response_revised== "PR" ~ "PR",
                         #tct$day30_response_revised== "PR" & tct$MRD_status== "Positive" ~ "PR and MRD-positive",
                         #tct$day30_response_revised== "PR" & is.na(tct$MRD_status) ~ "PR and MRD unknown",
#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Negative" ~ "sCR and MRD-negative",
#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Positive" ~ "sCR and MRD-positive")
#table(tct$ORR_MRD)
## Labeling
var_label(cart1) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
                         tumor_burden = "Tumor burden", proteasome = "Refractory to Proteasome Inhibitors", 
                         immuno = "Refractory to Immunomodulators", doubleref = "Double refractory", 
                         tripleref= "Triple refractory", pentaref= "Penta refractory",
                         bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese", CRS_any = "Any CRS", CRS_gradecat = "CRS Grade", 
                         ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", cyto= "High risk cytogenetics", 
                         `ECOG > or = 2? (Yes=1, No=0)` = "Deletion 17p at Infusion", 
                         `t(4:14) prior to CAR-T infusion (yes=1, no=0)` = "t(4:14) at Infusion", `t(14:16) prior to CAR-T infusion (yes=1, no=0)` = "t(4:16) at Infusion", 
                         `Prior auto SCT (yes=1, no=0)` = "Prior auto SCT", `Extramedullary Disease? (yes=1, no=0)` = "Extramedullary disease", dara= "Refractory to Daratumumab")

```

<br>

### Tables

## Table 1. Patient baseline characteristics
```{r}
selected <- cart1 %>% 
  select(Age, agecat, Sex, `BMI at apheresis`, bmicat, bmicat2, `Extramedullary Disease? (yes=1, no=0)`, tumor_burden, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, `ECOG > or = 2? (Yes=1, No=0)`, `t(4:14) prior to CAR-T infusion (yes=1, no=0)`, `t(14:16) prior to CAR-T infusion (yes=1, no=0)`, cyto, `Bridging Therapy (Yes=1, No=0)`, `Number of prior lines of therapy`, `Prior auto SCT (yes=1, no=0)`, immuno, proteasome, dara, doubleref, tripleref, pentaref, CRS_any, CRS_gradecat, `Duration of CRS (days)`, ICANS_any, ICANS_gradecat, `Duration of ICANS (days)`, `Infection (yes, no)`, `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`, 
                             # `Baseline CRP`, `Max CRP`, `Baseline Ferritin`, `Max Ferritin`, `Cell Dose (million cells)`, 
                             # `LDH at Baseline`, 
                             `LDH day +30`, `LDH day +90`#, 
                             # `B2 Microglobulin at Baseline`, `Day 30 B2 Microglobulin`, `Day 90 B2 Microglobulin`, `Cyclophosphamide Dose (mg)`, `Cyclophosphamide Actual Dose (mg/m2)`, `Fludarabine Total Dose (mg)`, `Fludarabine Actual Dose (mg/m2)`, `Fludarabine Dose Reduction`
                             )
# write.csv(selected,"/Volumes/Peres_Research/Myeloma/CART/selected_data.csv", row.names = TRUE)
selected %>% 
  tbl_summary(
            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
            digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_stat_label() %>% 
             #modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  # use `modify_footnote(everything() ~ NA, abbreviation = TRUE)` to delete abbrev. footnotes
  modify_footnote(update = everything() ~ NA)
```

<!-- Age (years)	 -->
<!--      Median (range)	 -->
<!--      60 – n (%)	 -->
<!-- Male sex – n (%)	 -->
<!-- Extramedullary disease – n (%)	 -->
<!-- High marrow burden (≥50%) – n (%)	 -->
<!-- ECOG performance status at lymphodepletion – n (%)	 -->
<!--      0	 -->
<!--      1	 -->
<!--      2	 -->
<!--      3	 -->
<!-- R-ISS stage – n (%)	 -->
<!--      I	 -->
<!--      II	 -->
<!--      III	 -->
<!--      Unknown	 -->
<!-- High-risk cytogenetics – n (%)	 -->
<!--      del(17p)	 -->
<!--      t(4;14)	 -->
<!--      t(14;16)	 -->
<!--      Unknown	 -->
<!-- Bridging therapy – n (%)	 -->
<!-- Prior anti-myeloma regimens – median (range)	 -->
<!--      Prior autoSCT – n (%)	 -->
<!--      Prior alloSCT – n (%)	 -->
<!--      Prior BCMA-directed therapy – n (%)	 -->
<!-- Refractory status – n (%)	 -->
<!--      Immunomodulatory agent	 -->
<!--      Proteasome inhibitor	 -->
<!--      Daratumumab	 -->
<!--      Double-refractory disease	 -->
<!--      Triple-refractory disease	 -->
<!--      Penta-refractory disease	 -->
<!-- Eligible for KarMMa 1 trial at apheresis – n (%)	 -->

## Table 2. Clinical outcomes

<!-- CRS maximum grade – n (%)	 -->
<!--      0	 -->
<!--      1	 -->
<!--      2	 -->
<!--      3	 -->
<!--      4	 -->
<!--      5	 -->
<!-- Time to CRS onset (days) – median (range)	 -->
<!-- Time to maximum severity CRS (days) – median (range)	 -->
<!-- Duration of CRS (days) – median (range)	 -->
<!-- ICANS maximum grade – n (%)	 -->
<!--      0	 -->
<!--      1	 -->
<!--      2	 -->
<!--      3	 -->
<!--      4	 -->
<!--      5	 -->
<!-- Time to ICANS onset (days) – median (range)	 -->
<!-- Time to maximum severity ICANS (days) – median (range)	 -->
<!-- Duration of ICANS (days) – median (range)	 -->
<!-- Treatment for toxicity – n (%)	 -->
<!--      Steroid use	 -->
<!--      Tocilizumab use	 -->
<!--      Anakinra use	 -->
<!-- Day 30 response – n (%)	 -->
<!--      ORR	 -->
<!--      CR or sCR	 -->
<!--           MRD negative	 -->
<!--      VGPR	 -->
<!--      PR	 -->
<!-- Day 90 response – n (%)	 -->
<!--      ORR	 -->
<!--      CR or sCR	 -->
<!--           MRD negative	 -->
<!--      VGPR	 -->
<!--      PR	 -->
<!-- Best response in first 90 days – n (%)	 -->
<!--      CR or sCR	 -->
<!--           MRD negative	 -->
<!--      VGPR	 -->
<!--      PR	 -->

For responses make denominator evaluable patients
Patient who died or was lost to follow-up or had non-secretory disease would not be evaluable

## Table 3. Bone marrow biopsy findings

<!-- 	Baseline (n=52)	Day 30 (n=44)	Day 90 (n=32) -->
<!-- Marrow cellularity – n (%)			 -->
<!--      Hypocellular			 -->
<!--      Normocellular			 -->
<!--      Hypercellular			 -->
<!--      Variable			 -->
<!-- Marrow cellularity (%) – median (range)			 -->
<!-- % CD138 positive by IHC – median (range)			 -->
<!-- Fibrosis grade – median (range)			 -->
<!-- Dysplasia present – n (%)			 -->

## Table 4. Supportive therapies and engraftment

<!-- Granulocyte colony stimulating factor (G-CSF)	 -->
<!--      G-CSF administered – n (%)	 -->
<!--      First day of G-CSF – median (range)	 -->
<!--      Last day of G-CSF – median (range)	 -->
<!-- CD34 stem cell boost	 -->
<!--      Stem cell boost administered – n (%)	 -->
<!--      Day of stem cell boost – median (range)	 -->
<!--      Dose of stem cell boost (million cells) – median (range)	 -->
<!-- Engraftment day – median (range)	 -->
<!-- Transfusions post-CART – n (%)	 -->
<!--      RBC transfusion within 7 days	 -->
<!--      Plt transfusion within 7 days	 -->
<!--      RBC transfusion >7 days	 -->
<!--      Plt transfusion >7 days	 -->
<!-- Intravenous immunoglobulin (IVIG)	 -->
<!--      IVIG administered – n (%)	 -->
<!--      First day of IVIG – median (range)	 -->
<!--      Last day of IVIG – median (range)	 -->

## Table S1. Apheresis and product characteristics

<!-- Collection goal (TBV) – median (range)	 -->
<!-- Whole blood processed (mL) – median (range)	 -->
<!-- Total blood volume processed (mL) – median (range)	 -->
<!-- Access type – n (%)	 -->
<!--      Non-tunneled central venous catheter	 -->
<!--      Peripheral line	 -->
<!--      Other	 -->
<!-- Final collection volume (mL) – median (range)	 -->
<!-- Run time (minutes) – median (range)	 -->
<!-- Time from apheresis to product infusion (days) – median (range)	 -->
<!-- Total bags infused – median (range)	 -->
<!-- Total dose volume (mL) – median (range)	 -->
<!-- Total cell dose (million cells) – median (range)	 -->

## Table S2. Cytopenias following ide-cel

<!-- 	Apheresis	Day -5	Day 0	Day 7	Day 14	Day 21	Day 30	Day 90 -->
<!-- Leukopenia – n (%)								 -->
<!--      Any grade								 -->
<!--      Grade 3+								 -->
<!-- Neutropenia – n (%)								 -->
<!--      Any grade								 -->
<!--      Grade 3+								 -->
<!-- Anemia – n (%)								 -->
<!--      Any grade								 -->
<!--      Grade 3+								 -->
<!-- Thrombocytopenia – n (%)								 -->
<!--      Any grade								 -->
<!--      Grade 3+								 -->

## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30

## Table S3. Patient characteristics by grade 3+ cytopenia at Day 90

(Similar to above)

## Table S4. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30

## Table S4. Details of infections after ide-cel

## Table S5. Patients with infections in the first 30 days by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy

## Table S6. Patients with infections in the first 100 days by cell counts and immunoglobulin levels

### Figures

## Figure 1. Consort diagram

## Figure 2. Inflammatory markers after ide-cel

## Figure 3. Cellular and humoral immune reconstitution after ide-cel

## Figure 4. Cytopenias over time

As discussed at meeting, rather than showing count recovery over time plan to show Grade 3+ cytopenias (Hb, Plt, ANC, WBC) over time (Day –5, Day +30, Day +60, Day +90)

## Figure 5. Cumulative incidence of infection and infection density

## Figure S1. Viral titers after ide-cel

A)	HSV 1/2 IgG

Example from prior cytopenia paper below. We can show this data however you think best
Interpretation: ≤0.89=negative (not immune)
                        0.90-1.09=indeterminate (can consider negative for purposes of analysis)
                        ≥1.10=positive (immune)

B)	VZV IgG (positive=immune vs negative or equivocal=not immune)

C)	CMV IgG (positive=immune vs negative=not immune)

## Figure S2. Pneumococcal titers after ide-cel

Antibody concentration >1.0 is considered long-term protection (immune)
If antibody concentration ≤1.0 consider negative (not immune)

### 2022-03-17 Manuscript analyses.Rmd
Add tables

@@
 ```{r load}
-path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias")
+# path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias")
 
 Characteristics <-
-  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
+  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
                     sheet = "Characteristics", skip = 1, n_max = 54) %>% 
@@
 Counts <-
-  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
+  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
                     sheet = "Counts") %>% 
@@
 Infections <-
-  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
+  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
                     sheet = "Infections") %>% 
@@
 Support <-
-  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
-                    sheet = "Support") %>% 
+  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
+                    sheet = "Support",
+                    range = "A1:U53") %>% 
   mutate(MRN = as.character(MRN),
@@
 Pneumo_titers <-
-  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
+  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
                     sheet = "Pneumo Titers") %>% 
@@
 Other_titers <-
-  readxl::read_xlsx(paste0(path,"/CytopeniaManuscriptData_3.16.22.xlsx"),
+  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
                     sheet = "Other Titers") %>% 
@@
   ) %>% 
+  mutate(male_sex = case_when(
+    Sex == "M"                                                    ~ 1,
+    TRUE                                                          ~ 0
+  )) %>% 
   mutate_at(c("Extramedullary Disease? (yes=1, no=0)",
@@
               "Prior auto SCT (yes=1, no=0)",
+              "Prior Allo SCT (Yes=1, No=0)",
+              "Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)",
               "Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)"), 
@@
   # ECOG
-  mutate(`ECOG at LD (at baseline visit)` = case_when(
-    `ECOG at LD (at baseline visit)` == 0 | 
-      `ECOG at LD (at baseline visit)` ==1 ~ "0-1"
-  )) %>% 
+  # mutate(`ECOG at LD (at baseline visit)` = case_when(
+  #   `ECOG at LD (at baseline visit)` == 0 | 
+  #     `ECOG at LD (at baseline visit)` == 1                       ~ "0-1",
+  #   TRUE                                                          ~ `ECOG at LD (at baseline visit)`
+  # )) %>% 
   # cytogenetics
@@
          ICANS_gradecat = factor(ICANS_gradecat, levels = c("No ICANS", "Grade 1 or 2", "Grade ≥3"))
-  )
+  ) %>% 
+  # mutate(best_response = ) %>% 
+  mutate(Leukopenia_apheresis = case_when(
+    `WBC apheresis` < 4                                           ~ "YES"
+  )) %>% 
+  mutate(`Leukopenia_-5d` = case_when(
+    `WBC day -5 (k/ul)` < 4                                        ~ "YES"
+  )) %>% 
+  mutate(`Leukopenia_0d` = case_when(
+    `WBC day 0 (k/uL)` < 4                                        ~ "YES"
+  )) %>% 
+  mutate(`Leukopenia_7d` = case_when(
+    `WBC day +7` < 4                                              ~ "YES"
+  )) %>% 
+  mutate(`Leukopenia_14d` = case_when(
+    `WBC day +14` < 4                                             ~ "YES"
+  )) %>% 
+  mutate(`Leukopenia_21d` = case_when(
+    `WBC day +21` < 4                                             ~ "YES"
+  )) %>% 
+  mutate(`Leukopenia_30d` = case_when(
+    `WBC day +30` < 4                                             ~ "YES"
+  )) %>% 
+  mutate(`Leukopenia_90d` = case_when(
+    `WBC day +90` < 4                                             ~ "YES"
+  )) %>% 
+  mutate(gr3_Leukopenia_apheresis = case_when(
+    `WBC apheresis` < 2                                           ~ "YES"
+  )) %>% 
+  mutate(`gr3_Leukopenia_-5d` = case_when(
+    `WBC day -5 (k/ul)` < 2                                       ~ "YES"
+  )) %>% 
+  mutate(`gr3_Leukopenia_0d` = case_when(
+    `WBC day 0 (k/uL)` < 2                                        ~ "YES"
+  )) %>% 
+  mutate(`gr3_Leukopenia_7d` = case_when(
+    `WBC day +7` < 2                                              ~ "YES"
+  )) %>% 
+  mutate(`gr3_Leukopenia_14d` = case_when(
+    `WBC day +14` < 2                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Leukopenia_21d` = case_when(
+    `WBC day +21` < 2                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Leukopenia_30d` = case_when(
+    `WBC day +30` < 2                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Leukopenia_90d` = case_when(
+    `WBC day +90` < 2                                             ~ "YES"
+  )) %>%
+
+  mutate(Neutropenia_apheresis = case_when(
+    `ANC apheresis` < 1.8                                           ~ "YES"
+  )) %>% 
+  mutate(`Neutropenia_-5d` = case_when(
+    `ANC day -5 (k/ul)` < 1.8                                        ~ "YES"
+  )) %>% 
+  mutate(`Neutropenia_0d` = case_when(
+    `ANC day 0 (k/uL)` < 1.8                                        ~ "YES"
+  )) %>% 
+  mutate(`Neutropenia_7d` = case_when(
+    `ANC day +7` < 1.8                                              ~ "YES"
+  )) %>% 
+  mutate(`Neutropenia_14d` = case_when(
+    `ANC day +14` < 1.8                                             ~ "YES"
+  )) %>% 
+  mutate(`Neutropenia_21d` = case_when(
+    `ANC day +21` < 1.8                                             ~ "YES"
+  )) %>% 
+  mutate(`Neutropenia_30d` = case_when(
+    `ANC day +30` < 1.8                                             ~ "YES"
+  )) %>% 
+  mutate(`Neutropenia_90d` = case_when(
+    `ANC day +90` < 1.8                                             ~ "YES"
+  )) %>% 
+  mutate(gr3_Neutropenia_apheresis = case_when(
+    `ANC apheresis` < 1                                           ~ "YES"
+  )) %>% 
+  mutate(`gr3_Neutropenia_-5d` = case_when(
+    `ANC day -5 (k/ul)` < 1                                        ~ "YES"
+  )) %>% 
+  mutate(`gr3_Neutropenia_0d` = case_when(
+    `ANC day 0 (k/uL)` < 1                                        ~ "YES"
+  )) %>% 
+  mutate(`gr3_Neutropenia_7d` = case_when(
+    `ANC day +7` < 1                                              ~ "YES"
+  )) %>% 
+  mutate(`gr3_Neutropenia_14d` = case_when(
+    `ANC day +14` < 1                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Neutropenia_21d` = case_when(
+    `ANC day +21` < 1                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Neutropenia_30d` = case_when(
+    `ANC day +30` < 1                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Neutropenia_90d` = case_when(
+    `ANC day +90` < 1                                             ~ "YES"
+  )) %>%
+
+  mutate(Anemia_apheresis = case_when(
+    `Hb apheresis` < 11.4                                           ~ "YES"
+  )) %>% 
+  mutate(`Anemia_-5d` = case_when(
+    `Hb day -5 (k/ul)` < 11.4                                        ~ "YES"
+  )) %>% 
+  mutate(`Anemia_0d` = case_when(
+    `Hb day 0 (k/uL)` < 11.4                                        ~ "YES"
+  )) %>% 
+  mutate(`Anemia_7d` = case_when(
+    `Hb day +7` < 11.4                                              ~ "YES"
+  )) %>% 
+  mutate(`Anemia_14d` = case_when(
+    `Hb day +14` < 11.4                                             ~ "YES"
+  )) %>% 
+  mutate(`Anemia_21d` = case_when(
+    `Hb day +21` < 11.4                                             ~ "YES"
+  )) %>% 
+  mutate(`Anemia_30d` = case_when(
+    `Hb day +30` < 11.4                                             ~ "YES"
+  )) %>% 
+  mutate(`Anemia_90d` = case_when(
+    `Hb day +90` < 11.4                                             ~ "YES"
+  )) %>% 
+  mutate(gr3_Anemia_apheresis = case_when(
+    `Hb apheresis` < 8                                           ~ "YES"
+  )) %>% 
+  mutate(`gr3_Anemia_-5d` = case_when(
+    `Hb day -5 (k/ul)` < 8                                        ~ "YES"
+  )) %>% 
+  mutate(`gr3_Anemia_0d` = case_when(
+    `Hb day 0 (k/uL)` < 8                                        ~ "YES"
+  )) %>% 
+  mutate(`gr3_Anemia_7d` = case_when(
+    `Hb day +7` < 8                                              ~ "YES"
+  )) %>% 
+  mutate(`gr3_Anemia_14d` = case_when(
+    `Hb day +14` < 8                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Anemia_21d` = case_when(
+    `Hb day +21` < 8                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Anemia_30d` = case_when(
+    `Hb day +30` < 8                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Anemia_90d` = case_when(
+    `Hb day +90` < 8                                             ~ "YES"
+  )) %>%
+
+  mutate(Thrombocytopenia_apheresis = case_when(
+    `Plt apheresis` < 143                                           ~ "YES"
+  )) %>% 
+  mutate(`Thrombocytopenia_-5d` = case_when(
+    `Plt day -5 (k/ul)` < 143                                        ~ "YES"
+  )) %>% 
+  mutate(`Thrombocytopenia_0d` = case_when(
+    `Plt day 0 (k/uL)` < 143                                        ~ "YES"
+  )) %>% 
+  mutate(`Thrombocytopenia_7d` = case_when(
+    `Plt day +7` < 143                                              ~ "YES"
+  )) %>% 
+  mutate(`Thrombocytopenia_14d` = case_when(
+    `Plt day +14` < 143                                             ~ "YES"
+  )) %>% 
+  mutate(`Thrombocytopenia_21d` = case_when(
+    `Plt day +21` < 143                                             ~ "YES"
+  )) %>% 
+  mutate(`Thrombocytopenia_30d` = case_when(
+    `Plt day +30` < 143                                             ~ "YES"
+  )) %>% 
+  mutate(`Thrombocytopenia_90d` = case_when(
+    `Plt day +90` < 143                                             ~ "YES"
+  )) %>% 
+  mutate(gr3_Thrombocytopenia_apheresis = case_when(
+    `Plt apheresis` < 50                                           ~ "YES"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_-5d` = case_when(
+    `Plt day -5 (k/ul)` < 50                                        ~ "YES"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_0d` = case_when(
+    `Plt day 0 (k/uL)` < 50                                        ~ "YES"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_7d` = case_when(
+    `Plt day +7` < 50                                              ~ "YES"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_14d` = case_when(
+    `Plt day +14` < 50                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_21d` = case_when(
+    `Plt day +21` < 50                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_30d` = case_when(
+    `Plt day +30` < 50                                             ~ "YES"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_90d` = case_when(
+    `Plt day +90` < 50                                             ~ "YES"
+  )) %>%
+
+  mutate(`cytopenia_30d` = case_when(
+    `WBC day +30` < 4 | 
+      `ANC day +30` < 1.8 | 
+      `Hb day +30` < 11.4 | 
+      `Plt day +30` < 143                                             ~ "YES",
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(`gr3_cytopenia_90d` = case_when(
+    `WBC day +90` < 2 | 
+      `ANC day +90` < 1 | 
+      `Hb day +90` < 8 | 
+      `Plt day +90` < 50                                             ~ "YES",
+    TRUE                                                              ~ "NO"
+  ))
 
@@
 #table(tct$ORR_MRD)
+```
+
+```{r}
 ## Labeling
-var_label(cart1) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
+var_label(cart1) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", 
+                         # bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
                          tumor_burden = "Tumor burden", proteasome = "Refractory to Proteasome Inhibitors", 
@@
                          tripleref= "Triple refractory", pentaref= "Penta refractory",
-                         bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese", CRS_any = "Any CRS", CRS_gradecat = "CRS Grade", 
+                         # bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese", 
+                         CRS_any = "Any CRS", CRS_gradecat = "CRS Grade", 
                          ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", cyto= "High risk cytogenetics", 
-                         `ECOG > or = 2? (Yes=1, No=0)` = "Deletion 17p at Infusion", 
+                         # `ECOG > or = 2? (Yes=1, No=0)` = "Deletion 17p at Infusion", 
                          `t(4:14) prior to CAR-T infusion (yes=1, no=0)` = "t(4:14) at Infusion", `t(14:16) prior to CAR-T infusion (yes=1, no=0)` = "t(4:16) at Infusion", 
-                         `Prior auto SCT (yes=1, no=0)` = "Prior auto SCT", `Extramedullary Disease? (yes=1, no=0)` = "Extramedullary disease", dara= "Refractory to Daratumumab")
+                         `Prior auto SCT (yes=1, no=0)` = "Prior autoSCT", 
+                         `Prior Allo SCT (Yes=1, No=0)` = "Prior alloSCT",
+         # `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)` = "Prior BCMA-directed therapy ",
+         `Extramedullary Disease? (yes=1, no=0)` = "Extramedullary disease", dara= "Refractory to Daratumumab"#,
+         # best_response = "Best response in first 90 days"
+         )
 
@@
 ## Table 1. Patient baseline characteristics
+**Change Male Sex**
 ```{r}
-selected <- cart1 %>% 
-  select(Age, agecat, Sex, `BMI at apheresis`, bmicat, bmicat2, `Extramedullary Disease?
-(yes=1, no=0)`, tumor_burden, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, `ECOG > or = 2?
-(Yes=1, No=0)`, `t(4:14) prior to CAR-T infusion (yes=1, no=0)`, `t(14:16) prior to CAR-T infusion (yes=1, no=0)`, cyto, `Bridging Therapy (Yes=1, No=0)`, `Number of prior lines of therapy`, `Prior auto SCT (yes=1, no=0)`, immuno, proteasome, dara, doubleref, tripleref, pentaref, CRS_any, CRS_gradecat, `Duration of CRS (days)`, ICANS_any, ICANS_gradecat, `Duration of ICANS (days)`, `Infection (yes, no)`, `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (yes=1, no=0)`, 
+         tumor_burden, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, cyto, 
+         `Bridging Therapy (Yes=1, No=0)`,
+         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`) %>% 
+  tbl_summary(
+    type = list(
+    `Extramedullary Disease? (yes=1, no=0)` ~ "categorical",
+    cyto ~ "categorical",
+    `Bridging Therapy (Yes=1, No=0)` ~ "categorical",
+    `Prior auto SCT (yes=1, no=0)` ~ "categorical",
+    immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
+    doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
+    `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)` ~"categorical"),
+
+    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1
+    ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
+
+## Table 2. Clinical outcomes
+**organize response**
+**best response**
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(#`BMI at apheresis`, 
+         # `t(4:14) prior to CAR-T infusion (yes=1, no=0)`, `t(14:16) prior to CAR-T infusion (yes=1, no=0)`, 
+    `Max CRS grade (0-5)`,
+         # CRS_any, CRS_gradecat, 
+    `Day of onset of CRS relative to infusion`,
+         `Day of Max CRS (relative to infusion)`, `Duration of CRS (days)`,
+
+    `Max ICANS (relative to infusion)`,
+         # ICANS_any, ICANS_gradecat, 
+    `Day of onset of ICANS relative to infusion`,
+    `Day of Max ICANS (relative to infusion)`,
+         `Duration of ICANS (days)`,
+
+    `Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`,
+
+         # `Infection (yes, no)`,
+    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`,
+    `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`
+
                              # `Baseline CRP`, `Max CRP`, `Baseline Ferritin`, `Max Ferritin`, `Cell Dose (million cells)`, 
                              # `LDH at Baseline`, 
-                             `LDH day +30`, `LDH day +90`#, 
+                             # `LDH day +30`, `LDH day +90`#, 
                              # `B2 Microglobulin at Baseline`, `Day 30 B2 Microglobulin`, `Day 90 B2 Microglobulin`, `Cyclophosphamide Dose (mg)`, `Cyclophosphamide Actual Dose (mg/m2)`, `Fludarabine Total Dose (mg)`, `Fludarabine Actual Dose (mg/m2)`, `Fludarabine Dose Reduction`
-                             )
-# write.csv(selected,"/Volumes/Peres_Research/Myeloma/CART/selected_data.csv", row.names = TRUE)
-selected %>% 
-  tbl_summary(
+                             ) %>% 
+  tbl_summary(type = list(
+    c(`Day of onset of CRS relative to infusion`, `Day of onset of ICANS relative to infusion`,
+      `Day of Max ICANS (relative to infusion)`, `Duration of ICANS (days)`) ~ "continuous",
+    c(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`) ~ "categorical"
+  ),
             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
@@
   bold_labels() %>% add_stat_label() %>% 
-             #modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  # use `modify_footnote(everything() ~ NA, abbreviation = TRUE)` to delete abbrev. footnotes
   modify_footnote(update = everything() ~ NA)
 ```
-
-<!-- Age (years)	 -->
-<!--      Median (range)	 -->
-<!--      60 – n (%)	 -->
-<!-- Male sex – n (%)	 -->
-<!-- Extramedullary disease – n (%)	 -->
-<!-- High marrow burden (≥50%) – n (%)	 -->
-<!-- ECOG performance status at lymphodepletion – n (%)	 -->
-<!--      0	 -->
-<!--      1	 -->
-<!--      2	 -->
-<!--      3	 -->
-<!-- R-ISS stage – n (%)	 -->
-<!--      I	 -->
-<!--      II	 -->
-<!--      III	 -->
-<!--      Unknown	 -->
-<!-- High-risk cytogenetics – n (%)	 -->
-<!--      del(17p)	 -->
-<!--      t(4;14)	 -->
-<!--      t(14;16)	 -->
-<!--      Unknown	 -->
-<!-- Bridging therapy – n (%)	 -->
-<!-- Prior anti-myeloma regimens – median (range)	 -->
-<!--      Prior autoSCT – n (%)	 -->
-<!--      Prior alloSCT – n (%)	 -->
-<!--      Prior BCMA-directed therapy – n (%)	 -->
-<!-- Refractory status – n (%)	 -->
-<!--      Immunomodulatory agent	 -->
-<!--      Proteasome inhibitor	 -->
-<!--      Daratumumab	 -->
-<!--      Double-refractory disease	 -->
-<!--      Triple-refractory disease	 -->
-<!--      Penta-refractory disease	 -->
-<!-- Eligible for KarMMa 1 trial at apheresis – n (%)	 -->
-
-## Table 2. Clinical outcomes
-
-<!-- CRS maximum grade – n (%)	 -->
-<!--      0	 -->
-<!--      1	 -->
-<!--      2	 -->
-<!--      3	 -->
-<!--      4	 -->
-<!--      5	 -->
-<!-- Time to CRS onset (days) – median (range)	 -->
-<!-- Time to maximum severity CRS (days) – median (range)	 -->
-<!-- Duration of CRS (days) – median (range)	 -->
-<!-- ICANS maximum grade – n (%)	 -->
-<!--      0	 -->
-<!--      1	 -->
-<!--      2	 -->
-<!--      3	 -->
-<!--      4	 -->
-<!--      5	 -->
-<!-- Time to ICANS onset (days) – median (range)	 -->
-<!-- Time to maximum severity ICANS (days) – median (range)	 -->
-<!-- Duration of ICANS (days) – median (range)	 -->
-<!-- Treatment for toxicity – n (%)	 -->
-<!--      Steroid use	 -->
-<!--      Tocilizumab use	 -->
-<!--      Anakinra use	 -->
-<!-- Day 30 response – n (%)	 -->
-<!--      ORR	 -->
-<!--      CR or sCR	 -->
-<!--           MRD negative	 -->
-<!--      VGPR	 -->
-<!--      PR	 -->
-<!-- Day 90 response – n (%)	 -->
-<!--      ORR	 -->
-<!--      CR or sCR	 -->
-<!--           MRD negative	 -->
-<!--      VGPR	 -->
-<!--      PR	 -->
-<!-- Best response in first 90 days – n (%)	 -->
-<!--      CR or sCR	 -->
-<!--           MRD negative	 -->
-<!--      VGPR	 -->
-<!--      PR	 -->
-
 For responses make denominator evaluable patients
@@
 ## Table 3. Bone marrow biopsy findings
+**make sure of the variables used then combine them**
+```{r}
+tbl1 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`marrow cellularity baseline`, `marrow cellularity baseline (%)`,
+         `marrow CD138 baseline (%)`, `marrow fibrosis baseline`, `marrow dysplasia baseline`
+  ) %>% 
+  tbl_summary(type = list(
+    c(#`marrow cellularity baseline (%)`, `marrow CD138 baseline (%)`, 
+      `marrow fibrosis baseline`) ~ "continuous"
+  ),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
 
-<!-- 	Baseline (n=52)	Day 30 (n=44)	Day 90 (n=32) -->
-<!-- Marrow cellularity – n (%)			 -->
-<!--      Hypocellular			 -->
-<!--      Normocellular			 -->
-<!--      Hypercellular			 -->
-<!--      Variable			 -->
-<!-- Marrow cellularity (%) – median (range)			 -->
-<!-- % CD138 positive by IHC – median (range)			 -->
-<!-- Fibrosis grade – median (range)			 -->
-<!-- Dysplasia present – n (%)			 -->
+tbl2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`marrow cellularity day +30`, `marrow % cellularity day +30`,
+         `marrow %CD138 day +30`, `marrow fibrosis day +30`, `marrow dysplasia day +30`
+  ) %>% 
+  tbl_summary(#type = list(
+  #   c(`marrow % cellularity day +30`, `marrow %CD138 day +30`, `marrow fibrosis day +30`) ~ "continuous"
+  # ),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl3 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`marrow cellularity day +90`, `marrow % cellularity day +90`,
+         `marrow %CD138 day +90`, `marrow fibrosis day +90`, `marrow dysplasia day +90`
+  ) %>% 
+  tbl_summary(#type = list(
+  #   c(`marrow % cellularity day +90`, `marrow %CD138 day +90`, `marrow fibrosis day +90`) ~ "continuous"
+  # ),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl_merge(list(tbl1, tbl2, tbl3), tab_spanner = c("Baseline", "Day 30", "Day 90"))
+```
 
 ## Table 4. Supportive therapies and engraftment
-
-<!-- Granulocyte colony stimulating factor (G-CSF)	 -->
-<!--      G-CSF administered – n (%)	 -->
-<!--      First day of G-CSF – median (range)	 -->
-<!--      Last day of G-CSF – median (range)	 -->
-<!-- CD34 stem cell boost	 -->
-<!--      Stem cell boost administered – n (%)	 -->
-<!--      Day of stem cell boost – median (range)	 -->
-<!--      Dose of stem cell boost (million cells) – median (range)	 -->
-<!-- Engraftment day – median (range)	 -->
-<!-- Transfusions post-CART – n (%)	 -->
-<!--      RBC transfusion within 7 days	 -->
-<!--      Plt transfusion within 7 days	 -->
-<!--      RBC transfusion >7 days	 -->
-<!--      Plt transfusion >7 days	 -->
-<!-- Intravenous immunoglobulin (IVIG)	 -->
-<!--      IVIG administered – n (%)	 -->
-<!--      First day of IVIG – median (range)	 -->
-<!--      Last day of IVIG – median (range)	 -->
+**Fix the + and <**
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Need for G-CSF post infus (Yes, No)`, `First Day of GCSF`, `Last Day of GCSF`,
+         `CD34 stem cell boost`, `Day of stem cell boost`, `Boost cell dose (million cells)`,
+         `Engraftment Day`,
+         `RBC transfusion within 7d post CART`, `Plt transfusion within 7d post CART`, 
+         `RBC transfusion >7d post CART`, `Plt transfusion >7d post CART`,
+         `Need for IVIG (Yes, No)`, `First day of IVIG`, `Last day of IVIG`
+  ) %>% 
+  tbl_summary(type = list(
+    c(#`Last Day of GCSF`,
+    `Day of stem cell boost`, `Boost cell dose (million cells)`) ~ "continuous"
+  ),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
 
 ## Table S1. Apheresis and product characteristics
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Final collection volume (mL)`, `Whole blood processed (mL)`,
+         `TBV processed`, `Access type`, `Final collection volume (mL)`,
+         `Run time (min)`,
+         `Time from apheresis to CAR-T infusion (days)`, `Total bags`,
+         `Total dose volume (mL)`, `Total cell dose (million cells)`
 
-<!-- Collection goal (TBV) – median (range)	 -->
-<!-- Whole blood processed (mL) – median (range)	 -->
-<!-- Total blood volume processed (mL) – median (range)	 -->
-<!-- Access type – n (%)	 -->
-<!--      Non-tunneled central venous catheter	 -->
-<!--      Peripheral line	 -->
-<!--      Other	 -->
-<!-- Final collection volume (mL) – median (range)	 -->
-<!-- Run time (minutes) – median (range)	 -->
-<!-- Time from apheresis to product infusion (days) – median (range)	 -->
-<!-- Total bags infused – median (range)	 -->
-<!-- Total dose volume (mL) – median (range)	 -->
-<!-- Total cell dose (million cells) – median (range)	 -->
+  ) %>% 
+  tbl_summary(type = list(c(`Total bags`) ~ "continuous"),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
 
 ## Table S2. Cytopenias following ide-cel
+**Change %**
+```{r}
+tbl1 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Leukopenia_apheresis`, `gr3_Leukopenia_apheresis`, 
+         `Neutropenia_apheresis`, `gr3_Neutropenia_apheresis`, 
+         `Anemia_apheresis`, `gr3_Anemia_apheresis`, 
+         `Thrombocytopenia_apheresis`, `gr3_Thrombocytopenia_apheresis`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
 
-<!-- 	Apheresis	Day -5	Day 0	Day 7	Day 14	Day 21	Day 30	Day 90 -->
-<!-- Leukopenia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
-<!-- Neutropenia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
-<!-- Anemia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
-<!-- Thrombocytopenia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
+tbl2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Leukopenia_-5d`, `gr3_Leukopenia_-5d`, 
+         `Neutropenia_-5d`, `gr3_Neutropenia_-5d`,
+         `Anemia_-5d`, `gr3_Anemia_-5d`, 
+         `Thrombocytopenia_-5d`, `gr3_Thrombocytopenia_-5d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl3 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Leukopenia_0d`, `gr3_Leukopenia_0d`, 
+         `Neutropenia_0d`, `gr3_Neutropenia_0d`, 
+         `Anemia_0d`, `gr3_Anemia_0d`,
+         `Thrombocytopenia_0d`, `gr3_Thrombocytopenia_0d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl4 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Leukopenia_7d`, `gr3_Leukopenia_7d`, 
+         `Neutropenia_7d`, `gr3_Neutropenia_7d`, 
+         `Anemia_7d`, `gr3_Anemia_7d`, 
+         `Thrombocytopenia_7d`, `gr3_Thrombocytopenia_7d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl5 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Leukopenia_14d`, `gr3_Leukopenia_14d`, 
+         `Neutropenia_14d`, `gr3_Neutropenia_14d`,
+         `Anemia_14d`, `gr3_Anemia_14d`,
+         `Thrombocytopenia_14d`, `gr3_Thrombocytopenia_14d` 
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl6 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Leukopenia_21d`,
+         `gr3_Leukopenia_21d`, 
+         `Neutropenia_21d`, `gr3_Neutropenia_21d`, 
+         `Anemia_21d`, `gr3_Anemia_21d`,
+         `Thrombocytopenia_21d`, `gr3_Thrombocytopenia_21d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl7 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Leukopenia_30d`, `gr3_Leukopenia_30d`,
+         `Neutropenia_30d`, `gr3_Neutropenia_30d`,
+         `Anemia_30d`, `gr3_Anemia_30d`, 
+         `Thrombocytopenia_30d`, `gr3_Thrombocytopenia_30d` 
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl8 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Leukopenia_90d`, `gr3_Leukopenia_90d`,
+         `Neutropenia_90d`, `gr3_Neutropenia_90d`,
+         `Anemia_90d`,`gr3_Anemia_90d`,
+         `Thrombocytopenia_90d`, `gr3_Thrombocytopenia_90d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), 
+          tab_spanner = c("Apheresis", "Day -5",	"Day 0",	"Day 7",	"Day 14",	"Day 21",	"Day 30",	"Day 90"))
+```
 
 ## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30
+**add tab_spanning**
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (yes=1, no=0)`, 
+         tumor_burden, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, cyto, 
+         `Bridging Therapy (Yes=1, No=0)`,
+         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
+         `cytopenia_30d`) %>% 
+  tbl_summary(by = `cytopenia_30d`,
+    type = list(
+    `Extramedullary Disease? (yes=1, no=0)` ~ "categorical",
+    cyto ~ "categorical",
+    `Bridging Therapy (Yes=1, No=0)` ~ "categorical",
+    `Prior auto SCT (yes=1, no=0)` ~ "categorical",
+    immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
+    doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
+    `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)` ~"categorical"),
+
+    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1
+    ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
 
 ## Table S3. Patient characteristics by grade 3+ cytopenia at Day 90
+**add tab_spanning**
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (yes=1, no=0)`, 
+         tumor_burden, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, cyto, 
+         `Bridging Therapy (Yes=1, No=0)`,
+         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
+         `gr3_cytopenia_90d`) %>% 
+  tbl_summary(by = `gr3_cytopenia_90d`,
+    type = list(
+    `Extramedullary Disease? (yes=1, no=0)` ~ "categorical",
+    cyto ~ "categorical",
+    `Bridging Therapy (Yes=1, No=0)` ~ "categorical",
+    `Prior auto SCT (yes=1, no=0)` ~ "categorical",
+    immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
+    doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
+    `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)` ~"categorical"),
 
-(Similar to above)
+    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1
+    ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
 

### 2022-03-18 Manuscript analyses.Rmd
Add plots, fix Unk, type, etc

--- 2022-03-16 Manuscript analyses.Rmd
@@
 library(labelled)
+library(DescTools)
+library(patchwork)
 # library(survival)
@@
 cart1 <- cart %>% 
+  mutate(across(where(is.character), ~ str_replace(., "NE", NA_character_))) %>%
+  # censored days > 100 to 100
+  mutate(across(contains("day") & where(is.numeric), ~ case_when(
+    . > 100                                                       ~ 100,
+    TRUE                                                          ~ as.numeric(.)
+  ))) %>% 
   # defining BMI categories
@@
   ) %>% 
+  mutate(male_sex = case_when(
+    Sex == "M"                                                    ~ 1,
+    TRUE                                                          ~ 0
+  )) %>% 
   mutate_at(c("Extramedullary Disease? (yes=1, no=0)",
+              "High Marrow Burden? (yes=1, no=0)",
               "ECOG > or = 2? (Yes=1, No=0)",
@@
               "t(14:16) prior to CAR-T infusion (yes=1, no=0)",
+              "Steroid use (Yes=1, No=0)", "Tocilizumab (Yes=1, No=0)", "Anakinra (Yes=1, No=0)",
               "Bridging Therapy (Yes=1, No=0)",
               "Prior auto SCT (yes=1, no=0)",
+              "Prior Allo SCT (Yes=1, No=0)",
+              "Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)",
+              "Need for G-CSF post infus (Yes, No)",
+              "Need for IVIG (Yes, No)",
+              "CD34 stem cell boost",
+              "RBC transfusion within 7d post CART", "Plt transfusion within 7d post CART", 
+              "RBC transfusion >7d post CART", "Plt transfusion >7d post CART",
               "Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)"), 
@@
             )) %>% 
-  # tumor burden
-  mutate(tumor_burden = case_when(
-    `High Marrow Burden? (yes=1, no=0)` == "NO" ~ "Low",
-    `High Marrow Burden? (yes=1, no=0)` == "YES" ~ "High"),
-    tumor_burden = factor(tumor_burden, levels = c("Low", "High"))
-  ) %>% 
   # ECOG
-  mutate(`ECOG at LD (at baseline visit)` = case_when(
-    `ECOG at LD (at baseline visit)` == 0 | 
-      `ECOG at LD (at baseline visit)` ==1 ~ "0-1"
-  )) %>% 
+  # mutate(`ECOG at LD (at baseline visit)` = case_when(
+  #   `ECOG at LD (at baseline visit)` == 0 | 
+  #     `ECOG at LD (at baseline visit)` == 1                       ~ "0-1",
+  #   TRUE                                                          ~ `ECOG at LD (at baseline visit)`
+  # )) %>% 
   # cytogenetics
   mutate(cyto = case_when(
-    `ECOG > or = 2? (Yes=1, No=0)` == "YES" | 
+    `Deletion 17p prior to CAR-T infusion (yes=1, no=0)` == "YES" | 
       `t(4:14) prior to CAR-T infusion (yes=1, no=0)` == "YES" | 
       `t(14:16) prior to CAR-T infusion (yes=1, no=0)` == "YES"   ~ "YES",
-    `ECOG > or = 2? (Yes=1, No=0)` == "NO" &
+    `Deletion 17p prior to CAR-T infusion (yes=1, no=0)` == "NO" &
       `t(4:14) prior to CAR-T infusion (yes=1, no=0)` == "NO" &
@@
     `Bortezomib (exposed=0 vs. refractory=1)` == "Exposed" &
-      `Bortezomib (exposed=0 vs. refractory=1)` == "Exposed"      ~ "NO",
+      `Carfilzomib (exposed=0 vs. refractory=1)` == "Exposed"      ~ "NO",
     `Bortezomib (exposed=0 vs. refractory=1)` == "Refractory" |
-      `Bortezomib (exposed=0 vs. refractory=1)` == "Refractory"   ~ "YES"
+      `Carfilzomib (exposed=0 vs. refractory=1)` == "Refractory"   ~ "YES"
   )) %>% 
@@
          ICANS_gradecat = factor(ICANS_gradecat, levels = c("No ICANS", "Grade 1 or 2", "Grade ≥3"))
-  )
+  ) %>% 
+  mutate(`marrow cellularity baseline` = case_when(
+    `marrow cellularity baseline` == "\"patchy\""                 ~ "hyper",
+    TRUE                                                          ~ `marrow cellularity baseline`
+  )) %>% 
+  mutate(`marrow cellularity day +30` = case_when(
+    `marrow cellularity day +30` == "aplastic"                    ~ "hypo",
+    TRUE                                                          ~ `marrow cellularity day +30`
+  )) %>% 
+  mutate(`Access type` = case_when(
+    `Access type` == "Femoral"                                    ~ "Non-tunneled",
+    `Access type` == "AVF"                                        ~ "Peripheral",
+    TRUE                                                          ~ `Access type`
+  )) %>% 
+  # mutate(best_response = ) %>% 
+  mutate(Leukopenia_apheresis = case_when(
+    `WBC apheresis` < 4                                           ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_-5d` = case_when(
+    `WBC day -5 (k/ul)` < 4                                       ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_0d` = case_when(
+    `WBC day 0 (k/uL)` < 4                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_7d` = case_when(
+    `WBC day +7` < 4                                              ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_14d` = case_when(
+    `WBC day +14` < 4                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_21d` = case_when(
+    `WBC day +21` < 4                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_30d` = case_when(
+    `WBC day +30` < 4                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_90d` = case_when(
+    `WBC day +90` < 4                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(gr3_Leukopenia_apheresis = case_when(
+    `WBC apheresis` < 2                                           ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_-5d` = case_when(
+    `WBC day -5 (k/ul)` < 2                                       ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_0d` = case_when(
+    `WBC day 0 (k/uL)` < 2                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_7d` = case_when(
+    `WBC day +7` < 2                                              ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_14d` = case_when(
+    `WBC day +14` < 2                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_21d` = case_when(
+    `WBC day +21` < 2                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_30d` = case_when(
+    `WBC day +30` < 2                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_90d` = case_when(
+    `WBC day +90` < 2                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>%
+
+  mutate(Neutropenia_apheresis = case_when(
+    `ANC apheresis` < 1.8                                           ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_-5d` = case_when(
+    `ANC day -5 (k/ul)` < 1.8                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_0d` = case_when(
+    `ANC day 0 (k/uL)` < 1.8                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_7d` = case_when(
+    `ANC day +7` < 1.8                                              ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_14d` = case_when(
+    `ANC day +14` < 1.8                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_21d` = case_when(
+    `ANC day +21` < 1.8                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_30d` = case_when(
+    `ANC day +30` < 1.8                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_90d` = case_when(
+    `ANC day +90` < 1.8                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(gr3_Neutropenia_apheresis = case_when(
+    `ANC apheresis` < 1                                           ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_-5d` = case_when(
+    `ANC day -5 (k/ul)` < 1                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_0d` = case_when(
+    `ANC day 0 (k/uL)` < 1                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_7d` = case_when(
+    `ANC day +7` < 1                                              ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_14d` = case_when(
+    `ANC day +14` < 1                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_21d` = case_when(
+    `ANC day +21` < 1                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_30d` = case_when(
+    `ANC day +30` < 1                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_90d` = case_when(
+    `ANC day +90` < 1                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>%
+
+  mutate(Anemia_apheresis = case_when(
+    `Hb apheresis` < 11.4                                           ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_-5d` = case_when(
+    `Hb day -5 (k/ul)` < 11.4                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_0d` = case_when(
+    `Hb day 0 (k/uL)` < 11.4                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_7d` = case_when(
+    `Hb day +7` < 11.4                                              ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_14d` = case_when(
+    `Hb day +14` < 11.4                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_21d` = case_when(
+    `Hb day +21` < 11.4                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_30d` = case_when(
+    `Hb day +30` < 11.4                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_90d` = case_when(
+    `Hb day +90` < 11.4                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(gr3_Anemia_apheresis = case_when(
+    `Hb apheresis` < 8                                           ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_-5d` = case_when(
+    `Hb day -5 (k/ul)` < 8                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_0d` = case_when(
+    `Hb day 0 (k/uL)` < 8                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_7d` = case_when(
+    `Hb day +7` < 8                                              ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_14d` = case_when(
+    `Hb day +14` < 8                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_21d` = case_when(
+    `Hb day +21` < 8                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_30d` = case_when(
+    `Hb day +30` < 8                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_90d` = case_when(
+    `Hb day +90` < 8                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>%
+
+  mutate(Thrombocytopenia_apheresis = case_when(
+    `Plt apheresis` < 143                                           ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_-5d` = case_when(
+    `Plt day -5 (k/ul)` < 143                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_0d` = case_when(
+    `Plt day 0 (k/uL)` < 143                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_7d` = case_when(
+    `Plt day +7` < 143                                              ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_14d` = case_when(
+    `Plt day +14` < 143                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_21d` = case_when(
+    `Plt day +21` < 143                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_30d` = case_when(
+    `Plt day +30` < 143                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_90d` = case_when(
+    `Plt day +90` < 143                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(gr3_Thrombocytopenia_apheresis = case_when(
+    `Plt apheresis` < 50                                           ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_-5d` = case_when(
+    `Plt day -5 (k/ul)` < 50                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_0d` = case_when(
+    `Plt day 0 (k/uL)` < 50                                        ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_7d` = case_when(
+    `Plt day +7` < 50                                              ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_14d` = case_when(
+    `Plt day +14` < 50                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_21d` = case_when(
+    `Plt day +21` < 50                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_30d` = case_when(
+    `Plt day +30` < 50                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_90d` = case_when(
+    `Plt day +90` < 50                                             ~ "YES",
+    TRUE                                                          ~ "NO"
+  )) %>%
+
+  mutate(`cytopenia_30d` = case_when(
+    `WBC day +30` < 4 | 
+      `ANC day +30` < 1.8 | 
+      `Hb day +30` < 11.4 | 
+      `Plt day +30` < 143                                             ~ "YES",
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(`gr3_cytopenia_30d` = case_when(
+    `WBC day +30` < 2 | 
+      `ANC day +30` < 1 | 
+      `Hb day +30` < 8 | 
+      `Plt day +30` < 50                                              ~ "YES",
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(`gr3_cytopenia_90d` = case_when(
+    `WBC day +90` < 2 | 
+      `ANC day +90` < 1 | 
+      `Hb day +90` < 8 | 
+      `Plt day +90` < 50                                             ~ "YES",
+    TRUE                                                              ~ "NO"
+  ))
 
@@
 #table(tct$ORR_MRD)
+```
+
+```{r}
 ## Labeling
-var_label(cart1) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
-                         tumor_burden = "Tumor burden", proteasome = "Refractory to Proteasome Inhibitors", 
+var_label(cart1) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", 
+                         `Extramedullary Disease? (yes=1, no=0)` = "Extramedullary disease", 
+                         `High Marrow Burden? (yes=1, no=0)` = "High marrow burden (≥50%)",
+                         # bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
+                         proteasome = "Refractory to Proteasome Inhibitors", 
                          immuno = "Refractory to Immunomodulators", doubleref = "Double refractory", 
                          tripleref= "Triple refractory", pentaref= "Penta refractory",
-                         bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese", CRS_any = "Any CRS", CRS_gradecat = "CRS Grade", 
+                         # bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese", 
+                         CRS_any = "Any CRS", CRS_gradecat = "CRS Grade", 
                          ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", cyto= "High risk cytogenetics", 
-                         `ECOG > or = 2? (Yes=1, No=0)` = "Deletion 17p at Infusion", 
+                         # `ECOG > or = 2? (Yes=1, No=0)` ,
+                         `Deletion 17p prior to CAR-T infusion (yes=1, no=0)` = "Deletion 17p at Infusion", 
                          `t(4:14) prior to CAR-T infusion (yes=1, no=0)` = "t(4:14) at Infusion", `t(14:16) prior to CAR-T infusion (yes=1, no=0)` = "t(4:16) at Infusion", 
-                         `Prior auto SCT (yes=1, no=0)` = "Prior auto SCT", `Extramedullary Disease? (yes=1, no=0)` = "Extramedullary disease", dara= "Refractory to Daratumumab")
+                         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)` = "Prior BCMA-directed therapy",
+                         `Prior auto SCT (yes=1, no=0)` = "Prior autoSCT", 
+                         `Prior Allo SCT (Yes=1, No=0)` = "Prior alloSCT",
+                         # `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)` = "Prior BCMA-directed therapy ",
+                         dara= "Refractory to Daratumumab"#,
+                         # best_response = "Best response in first 90 days"
+)
 
@@
 ## Table 1. Patient baseline characteristics
+**Change Male Sex**
 ```{r}
-selected <- cart1 %>% 
-  select(Age, agecat, Sex, `BMI at apheresis`, bmicat, bmicat2, `Extramedullary Disease?
-(yes=1, no=0)`, tumor_burden, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, `ECOG > or = 2?
-(Yes=1, No=0)`, `t(4:14) prior to CAR-T infusion (yes=1, no=0)`, `t(14:16) prior to CAR-T infusion (yes=1, no=0)`, cyto, `Bridging Therapy (Yes=1, No=0)`, `Number of prior lines of therapy`, `Prior auto SCT (yes=1, no=0)`, immuno, proteasome, dara, doubleref, tripleref, pentaref, CRS_any, CRS_gradecat, `Duration of CRS (days)`, ICANS_any, ICANS_gradecat, `Duration of ICANS (days)`, `Infection (yes, no)`, `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
-                             # `Baseline CRP`, `Max CRP`, `Baseline Ferritin`, `Max Ferritin`, `Cell Dose (million cells)`, 
-                             # `LDH at Baseline`, 
-                             `LDH day +30`, `LDH day +90`#, 
-                             # `B2 Microglobulin at Baseline`, `Day 30 B2 Microglobulin`, `Day 90 B2 Microglobulin`, `Cyclophosphamide Dose (mg)`, `Cyclophosphamide Actual Dose (mg/m2)`, `Fludarabine Total Dose (mg)`, `Fludarabine Actual Dose (mg/m2)`, `Fludarabine Dose Reduction`
-                             )
-# write.csv(selected,"/Volumes/Peres_Research/Myeloma/CART/selected_data.csv", row.names = TRUE)
-selected %>% 
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (yes=1, no=0)`, 
+         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, 
+         `R-ISS at CAR-T Infusion`, 
+         cyto, `Deletion 17p prior to CAR-T infusion (yes=1, no=0)`,
+         `t(4:14) prior to CAR-T infusion (yes=1, no=0)`,
+         `t(14:16) prior to CAR-T infusion (yes=1, no=0)`,
+         `Bridging Therapy (Yes=1, No=0)`,
+         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`) %>% 
   tbl_summary(
+    type = list(
+      c(`Extramedullary Disease? (yes=1, no=0)`, `High Marrow Burden? (yes=1, no=0)`,
+        cyto, `Deletion 17p prior to CAR-T infusion (yes=1, no=0)`,
+        `t(4:14) prior to CAR-T infusion (yes=1, no=0)`,
+        `t(14:16) prior to CAR-T infusion (yes=1, no=0)`,
+        `Bridging Therapy (Yes=1, No=0)`, `Prior auto SCT (yes=1, no=0)`,
+        immuno, proteasome, dara, doubleref, tripleref, pentaref,
+        `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`)
+      ~"categorical"),
+
+    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
+
+## Table 2. Clinical outcomes
+**organize response**
+**best response**
+```{r}
+tbl1 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Max CRS grade (0-5)`,
+         `Day of onset of CRS relative to infusion`,
+         `Day of Max CRS (relative to infusion)`, `Duration of CRS (days)`,
+
+         `Max ICANS (relative to infusion)`,
+         `Day of onset of ICANS relative to infusion`,
+         `Day of Max ICANS (relative to infusion)`,
+         `Duration of ICANS (days)`
+  ) %>% 
+  tbl_summary(type = list(
+    c(`Day of onset of CRS relative to infusion`, `Day of onset of ICANS relative to infusion`,
+      `Day of Max ICANS (relative to infusion)`, `Duration of ICANS (days)`) ~ "continuous"
+  ),
+  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+  digits = all_continuous() ~ 1,
+  missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, 
+         `Anakinra (Yes=1, No=0)`,
+         `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`,
+         `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`
+  ) %>% 
+  tbl_summary(type = list(
+    c(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`) ~ "categorical"
+  ),
   statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
@@
   bold_labels() %>% add_stat_label() %>% 
-             #modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  # use `modify_footnote(everything() ~ NA, abbreviation = TRUE)` to delete abbrev. footnotes
   modify_footnote(update = everything() ~ NA)
+
+tbl_stack(list(tbl1, tbl2))
 ```
-
-<!-- Age (years)	 -->
-<!--      Median (range)	 -->
-<!--      60 – n (%)	 -->
-<!-- Male sex – n (%)	 -->
-<!-- Extramedullary disease – n (%)	 -->
-<!-- High marrow burden (≥50%) – n (%)	 -->
-<!-- ECOG performance status at lymphodepletion – n (%)	 -->
-<!--      0	 -->
-<!--      1	 -->
-<!--      2	 -->
-<!--      3	 -->
-<!-- R-ISS stage – n (%)	 -->
-<!--      I	 -->
-<!--      II	 -->
-<!--      III	 -->
-<!--      Unknown	 -->
-<!-- High-risk cytogenetics – n (%)	 -->
-<!--      del(17p)	 -->
-<!--      t(4;14)	 -->
-<!--      t(14;16)	 -->
-<!--      Unknown	 -->
-<!-- Bridging therapy – n (%)	 -->
-<!-- Prior anti-myeloma regimens – median (range)	 -->
-<!--      Prior autoSCT – n (%)	 -->
-<!--      Prior alloSCT – n (%)	 -->
-<!--      Prior BCMA-directed therapy – n (%)	 -->
-<!-- Refractory status – n (%)	 -->
-<!--      Immunomodulatory agent	 -->
-<!--      Proteasome inhibitor	 -->
-<!--      Daratumumab	 -->
-<!--      Double-refractory disease	 -->
-<!--      Triple-refractory disease	 -->
-<!--      Penta-refractory disease	 -->
-<!-- Eligible for KarMMa 1 trial at apheresis – n (%)	 -->
-
-## Table 2. Clinical outcomes
-
-<!-- CRS maximum grade – n (%)	 -->
-<!--      0	 -->
-<!--      1	 -->
-<!--      2	 -->
-<!--      3	 -->
-<!--      4	 -->
-<!--      5	 -->
-<!-- Time to CRS onset (days) – median (range)	 -->
-<!-- Time to maximum severity CRS (days) – median (range)	 -->
-<!-- Duration of CRS (days) – median (range)	 -->
-<!-- ICANS maximum grade – n (%)	 -->
-<!--      0	 -->
-<!--      1	 -->
-<!--      2	 -->
-<!--      3	 -->
-<!--      4	 -->
-<!--      5	 -->
-<!-- Time to ICANS onset (days) – median (range)	 -->
-<!-- Time to maximum severity ICANS (days) – median (range)	 -->
-<!-- Duration of ICANS (days) – median (range)	 -->
-<!-- Treatment for toxicity – n (%)	 -->
-<!--      Steroid use	 -->
-<!--      Tocilizumab use	 -->
-<!--      Anakinra use	 -->
-<!-- Day 30 response – n (%)	 -->
-<!--      ORR	 -->
-<!--      CR or sCR	 -->
-<!--           MRD negative	 -->
-<!--      VGPR	 -->
-<!--      PR	 -->
-<!-- Day 90 response – n (%)	 -->
-<!--      ORR	 -->
-<!--      CR or sCR	 -->
-<!--           MRD negative	 -->
-<!--      VGPR	 -->
-<!--      PR	 -->
-<!-- Best response in first 90 days – n (%)	 -->
-<!--      CR or sCR	 -->
-<!--           MRD negative	 -->
-<!--      VGPR	 -->
-<!--      PR	 -->
 
@@
 ## Table 3. Bone marrow biopsy findings
+**make sure of the variables used then combine them**
+```{r}
+tbl1 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("marrow cellularity" = `marrow cellularity baseline`, 
+         "marrow cellularity (%)" = `marrow cellularity baseline (%)`,
+         "% CD138 positive by IHC" = `marrow CD138 baseline (%)`, 
+         "Fibrosis grade" = `marrow fibrosis baseline`, 
+         "Dysplasia present" = `marrow dysplasia baseline`
+  ) %>% 
+  tbl_summary(type = list(
+    c(#`marrow cellularity baseline (%)`, `marrow CD138 baseline (%)`, 
+      `Fibrosis grade`) ~ "continuous"
+  ),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
 
-<!-- 	Baseline (n=52)	Day 30 (n=44)	Day 90 (n=32) -->
-<!-- Marrow cellularity – n (%)			 -->
-<!--      Hypocellular			 -->
-<!--      Normocellular			 -->
-<!--      Hypercellular			 -->
-<!--      Variable			 -->
-<!-- Marrow cellularity (%) – median (range)			 -->
-<!-- % CD138 positive by IHC – median (range)			 -->
-<!-- Fibrosis grade – median (range)			 -->
-<!-- Dysplasia present – n (%)			 -->
+tbl2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("marrow cellularity" = `marrow cellularity day +30`, 
+         "marrow cellularity (%)" = `marrow % cellularity day +30`,
+         "% CD138 positive by IHC" = `marrow %CD138 day +30`, 
+         "Fibrosis grade" = `marrow fibrosis day +30`, 
+         "Dysplasia present" = `marrow dysplasia day +30`
+  ) %>% 
+  mutate(`marrow cellularity (%)` = as.numeric(`marrow cellularity (%)`)) %>% 
+  mutate(`% CD138 positive by IHC` = as.numeric(`% CD138 positive by IHC`)) %>% 
+  mutate(`Fibrosis grade` = as.numeric(`Fibrosis grade`)) %>% 
+  mutate(`Dysplasia present` = as.numeric(`Dysplasia present`)) %>% 
+  tbl_summary(type = list(
+    c(`marrow cellularity (%)`, `% CD138 positive by IHC`, 
+      `Fibrosis grade`, `Dysplasia present`) ~ "continuous"
+  ),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl3 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("marrow cellularity" = `marrow cellularity day +90`, 
+         "marrow cellularity (%)" = `marrow % cellularity day +90`,
+         "% CD138 positive by IHC" = `marrow %CD138 day +90`, 
+         "Fibrosis grade" = `marrow fibrosis day +90`, 
+         "Dysplasia present" = `marrow dysplasia day +90`
+  ) %>% 
+  mutate(`marrow cellularity (%)` = as.numeric(`marrow cellularity (%)`)) %>% 
+  mutate(`% CD138 positive by IHC` = as.numeric(`% CD138 positive by IHC`)) %>% 
+  mutate(`Fibrosis grade` = as.numeric(`Fibrosis grade`)) %>% 
+  mutate(`Dysplasia present` = as.numeric(`Dysplasia present`)) %>% 
+  tbl_summary(type = list(
+    c(`marrow cellularity (%)`, `% CD138 positive by IHC`, 
+      `Fibrosis grade`, `Dysplasia present`) ~ "continuous"
+  ),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl_merge(list(tbl1, tbl2, tbl3), tab_spanner = c("Baseline", "Day 30", "Day 90"))
+```
 
 ## Table 4. Supportive therapies and engraftment
+Jenn
 
-<!-- Granulocyte colony stimulating factor (G-CSF)	 -->
-<!--      G-CSF administered – n (%)	 -->
-<!--      First day of G-CSF – median (range)	 -->
-<!--      Last day of G-CSF – median (range)	 -->
-<!-- CD34 stem cell boost	 -->
-<!--      Stem cell boost administered – n (%)	 -->
-<!--      Day of stem cell boost – median (range)	 -->
-<!--      Dose of stem cell boost (million cells) – median (range)	 -->
-<!-- Engraftment day – median (range)	 -->
-<!-- Transfusions post-CART – n (%)	 -->
-<!--      RBC transfusion within 7 days	 -->
-<!--      Plt transfusion within 7 days	 -->
-<!--      RBC transfusion >7 days	 -->
-<!--      Plt transfusion >7 days	 -->
-<!-- Intravenous immunoglobulin (IVIG)	 -->
-<!--      IVIG administered – n (%)	 -->
-<!--      First day of IVIG – median (range)	 -->
-<!--      Last day of IVIG – median (range)	 -->
+```{r}
+# cart1 %>% 
+#   distinct(MRN, .keep_all = TRUE) %>% 
+#   select(`Need for G-CSF post infus (Yes, No)`, `First Day of GCSF`, `Last Day of GCSF`,
+#          `CD34 stem cell boost`, `Day of stem cell boost`, `Boost cell dose (million cells)`,
+#          `Engraftment Day`,
+#          `RBC transfusion within 7d post CART`, `Plt transfusion within 7d post CART`, 
+#          `RBC transfusion >7d post CART`, `Plt transfusion >7d post CART`,
+#          `Need for IVIG (Yes, No)`, `First day of IVIG`, `Last day of IVIG`
+#   ) %>% 
+#   tbl_summary(type = list(
+#     c(`Day of stem cell boost`, `Boost cell dose (million cells)`,
+#     `Last day of IVIG`) ~ "continuous",
+#     c(`Need for G-CSF post infus (Yes, No)`,
+#       `CD34 stem cell boost`,
+#       `RBC transfusion within 7d post CART`, `Plt transfusion within 7d post CART`, 
+#          `RBC transfusion >7d post CART`, `Plt transfusion >7d post CART`,
+#       `Need for IVIG (Yes, No)`) ~ "categorical"
+#   ),
+#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+#             digits = all_continuous() ~ 1) %>% 
+#   bold_labels() %>% add_stat_label() %>% 
+#   modify_footnote(update = everything() ~ NA)
+```
 
 ## Table S1. Apheresis and product characteristics
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Final collection volume (mL)`, `Whole blood processed (mL)`,
+         `TBV processed`, `Access type`, `Final collection volume (mL)`,
+         `Run time (min)`,
+         `Time from apheresis to CAR-T infusion (days)`, `Total bags`,
+         `Total dose volume (mL)`, `Total cell dose (million cells)`
 
-<!-- Collection goal (TBV) – median (range)	 -->
-<!-- Whole blood processed (mL) – median (range)	 -->
-<!-- Total blood volume processed (mL) – median (range)	 -->
-<!-- Access type – n (%)	 -->
-<!--      Non-tunneled central venous catheter	 -->
-<!--      Peripheral line	 -->
-<!--      Other	 -->
-<!-- Final collection volume (mL) – median (range)	 -->
-<!-- Run time (minutes) – median (range)	 -->
-<!-- Time from apheresis to product infusion (days) – median (range)	 -->
-<!-- Total bags infused – median (range)	 -->
-<!-- Total dose volume (mL) – median (range)	 -->
-<!-- Total cell dose (million cells) – median (range)	 -->
+  ) %>% 
+  tbl_summary(type = list(c(`Total bags`) ~ "continuous"),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
 
 ## Table S2. Cytopenias following ide-cel
+**Change %**
+```{r}
+tbl1 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_apheresis`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_apheresis`, 
+         "Neutropenia" = `Neutropenia_apheresis`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_apheresis`, 
+         "Anemia" = `Anemia_apheresis`, 
+         "Grade3+ Anemia" = `gr3_Anemia_apheresis`, 
+         "Thrombocytopenia" = `Thrombocytopenia_apheresis`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_apheresis`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
 
-<!-- 	Apheresis	Day -5	Day 0	Day 7	Day 14	Day 21	Day 30	Day 90 -->
-<!-- Leukopenia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
-<!-- Neutropenia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
-<!-- Anemia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
-<!-- Thrombocytopenia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
+tbl2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_-5d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_-5d`, 
+         "Neutropenia" = `Neutropenia_-5d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_-5d`,
+         "Anemia" = `Anemia_-5d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_-5d`, 
+         "Thrombocytopenia" = `Thrombocytopenia_-5d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_-5d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl3 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_0d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_0d`, 
+         "Neutropenia" = `Neutropenia_0d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_0d`, 
+         "Anemia" = `Anemia_0d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_0d`,
+         "Thrombocytopenia" = `Thrombocytopenia_0d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_0d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl4 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_7d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_7d`, 
+         "Neutropenia" = `Neutropenia_7d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_7d`, 
+         "Anemia" = `Anemia_7d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_7d`, 
+         "Thrombocytopenia" = `Thrombocytopenia_7d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_7d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl5 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_14d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_14d`, 
+         "Neutropenia" = `Neutropenia_14d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_14d`,
+         "Anemia" = `Anemia_14d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_14d`,
+         "Thrombocytopenia" = `Thrombocytopenia_14d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_14d` 
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl6 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_21d`,
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_21d`, 
+         "Neutropenia" = `Neutropenia_21d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_21d`, 
+         "Anemia" = `Anemia_21d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_21d`,
+         "Thrombocytopenia" = `Thrombocytopenia_21d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_21d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl7 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_30d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_30d`,
+         "Neutropenia" = `Neutropenia_30d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_30d`,
+         "Anemia" = `Anemia_30d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_30d`, 
+         "Thrombocytopenia" = `Thrombocytopenia_30d`,
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_30d` 
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl8 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_90d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_90d`,
+         "Neutropenia" = `Neutropenia_90d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_90d`,
+         "Anemia" = `Anemia_90d`,
+         "Grade3+ Anemia" = `gr3_Anemia_90d`,
+         "Thrombocytopenia" = `Thrombocytopenia_90d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_90d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1,
+            missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), 
+          tab_spanner = c("Apheresis", "Day -5",	"Day 0",	"Day 7",	"Day 14",	"Day 21",	"Day 30",	"Day 90"))
+```
 
 ## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30
+**add tab_spanning**
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (yes=1, no=0)`, 
+         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, cyto, 
+         `Bridging Therapy (Yes=1, No=0)`,
+         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
+         `gr3_cytopenia_30d`) %>% 
+  tbl_summary(by = `gr3_cytopenia_30d`,
+    type = list(
+    `Extramedullary Disease? (yes=1, no=0)` ~ "categorical",
+    cyto ~ "categorical",
+    `Bridging Therapy (Yes=1, No=0)` ~ "categorical",
+    `Prior auto SCT (yes=1, no=0)` ~ "categorical",
+    immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
+    doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
+    `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)` ~"categorical"),
+
+    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1
+    ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
+```
 
 ## Table S3. Patient characteristics by grade 3+ cytopenia at Day 90
+**add tab_spanning**
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (yes=1, no=0)`, 
+         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, cyto, 
+         `Bridging Therapy (Yes=1, No=0)`,
+         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
+         `gr3_cytopenia_90d`) %>% 
+  tbl_summary(by = `gr3_cytopenia_90d`,
+    type = list(
+    `Extramedullary Disease? (yes=1, no=0)` ~ "categorical",
+    cyto ~ "categorical",
+    `Bridging Therapy (Yes=1, No=0)` ~ "categorical",
+    `Prior auto SCT (yes=1, no=0)` ~ "categorical",
+    immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
+    doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
+    `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)` ~"categorical"),
 
-(Similar to above)
+    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1
+    ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 90?**")
+```
 
 ## Table S4. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
+```{r}
+tbl1 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Max CRS grade (0-5)`,
+         `Day of onset of CRS relative to infusion`,
+         `Day of Max CRS (relative to infusion)`, `Duration of CRS (days)`,
+
+         `Max ICANS (relative to infusion)`,
+         `Day of onset of ICANS relative to infusion`,
+         `Day of Max ICANS (relative to infusion)`,
+         `Duration of ICANS (days)`,
+         gr3_cytopenia_30d
+  ) %>% 
+  tbl_summary(by =`gr3_cytopenia_30d`,
+              type = list(
+                c(`Day of onset of CRS relative to infusion`, `Day of onset of ICANS relative to infusion`,
+                  `Day of Max ICANS (relative to infusion)`, `Duration of ICANS (days)`) ~ "continuous"
+              ),
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
+
+tbl2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, 
+         `Anakinra (Yes=1, No=0)`,
+         `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`,
+         `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`,
+         gr3_cytopenia_30d
+  ) %>% 
+  tbl_summary(by =`gr3_cytopenia_30d`,
+              type = list(
+                c(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`) ~ "categorical"
+              ),
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl_stack(list(tbl1, tbl2))
+```
 
 ## Table S4. Details of infections after ide-cel
+Jenn
 
@@
 ## Figure 2. Inflammatory markers after ide-cel
+```{r}
+# LDH <- cyto %>% select(`LDH at Pre-Leukapheresis.y`, `LDH day 0`, `LDH day +7`, `LDH day +14`, `LDH day +21`, `LDH day +30`)
+# LDH_long <- gather(LDH, day, LDH_value, `LDH at Pre-Leukapheresis.y`:`LDH day +30`)
+# LDH_long$day[LDH_long$day=="LDH at Pre-Leukapheresis.y"] <- "Pre"
+# LDH_long$day[LDH_long$day=="LDH day 0"] <- "Day 0"
+# LDH_long$day[LDH_long$day=="LDH day +7"] <- "Day 7"
+# LDH_long$day[LDH_long$day=="LDH day +14"] <- "Day 14"
+# LDH_long$day[LDH_long$day=="LDH day +21"] <- "Day 21"
+# LDH_long$day[LDH_long$day=="LDH day +30"] <- "Day 30"
+# LDH_long$day <- factor(LDH_long$day, levels = c("Pre", "Day 0", "Day 7", "Day 14", "Day 21", "Day 30"))
+# ggplot(LDH_long, aes(x=day, y=LDH_value)) + geom_boxplot() + xlab("Days") + ylab("LDH") + theme_classic() + ggtitle("LDH") + expand_limits(x= c(0.5, 6.5), y = c(0, 7000)) + scale_y_break(c(1250, 3500), ticklabels=c(4000, 7000), scales=0.10)
+# 
+# cyto$`Ferritin day +7`[cyto$`Ferritin day +7`==">33511"] <- 33511
+# cyto$`Ferritin day +7` <- as.numeric(cyto$`Ferritin day +7`)
+# Ferritin <- cyto %>% select(MRN, `Ferritin at Pre-Leukapheresis`, `Ferritin day 0`, `Ferritin day +7`, `Ferritin day +14`, `Ferritin day +21`, `Ferritin day +30`)
+# Ferritin_long <- gather(Ferritin, day, Ferritin_value, `Ferritin at Pre-Leukapheresis`:`Ferritin day +30`)
+# Ferritin_long$day[Ferritin_long$day=="Ferritin at Pre-Leukapheresis"] <- "Pre"
+# Ferritin_long$day[Ferritin_long$day=="Ferritin day 0"] <- "Day 0"
+# Ferritin_long$day[Ferritin_long$day=="Ferritin day +7"] <- "Day 7"
+# Ferritin_long$day[Ferritin_long$day=="Ferritin day +14"] <- "Day 14"
+# Ferritin_long$day[Ferritin_long$day=="Ferritin day +21"] <- "Day 21"
+# Ferritin_long$day[Ferritin_long$day=="Ferritin day +30"] <- "Day 30"
+# Ferritin_long$day <- factor(Ferritin_long$day, levels = c("Pre", "Day 0", "Day 7", "Day 14", "Day 21", "Day 30"))
+# ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + geom_boxplot() + xlab("Days") + ylab("Ferritin") + theme_classic() + ggtitle("Ferritin") + expand_limits(x= c(0.5, 6.5), y = c(0, 34000)) + scale_y_break(c(11000, 32900), ticklabels=c(33000, 34000), scales=0.05)
+# 
+# cyto$`CRP Pre-Leukapheresis`[cyto$`CRP Pre-Leukapheresis`=="<0.03"] <- 0.07
+# cyto$`CRP Pre-Leukapheresis` <- as.numeric(cyto$`CRP Pre-Leukapheresis`)
+# cyto$`CRP day +14`[cyto$`CRP day +14`=="<0.03"] <- 0.07
+# cyto$`CRP day +14` <- as.numeric(cyto$`CRP day +14`)
+# cyto$`CRP day +21`[cyto$`CRP day +21`=="<0.03"] <- 0.07
+# cyto$`CRP day +21` <- as.numeric(cyto$`CRP day +21`)
+# cyto$`CRP day +30`[cyto$`CRP day +30`=="<0.03"] <- 0.07
+# cyto$`CRP day +30` <- as.numeric(cyto$`CRP day +30`)
+# CRP <- cyto %>% select(`CRP Pre-Leukapheresis`, `CRP day 0`, `CRP day +7`, `CRP day +14`, `CRP day +21`, `CRP day +30`)
+# CRP_long <- gather(CRP, day, CRP_value, `CRP Pre-Leukapheresis`:`CRP day +30`)
+# CRP_long$day[CRP_long$day=="CRP Pre-Leukapheresis"] <- "Pre"
+# CRP_long$day[CRP_long$day=="CRP day 0"] <- "Day 0"
+# CRP_long$day[CRP_long$day=="CRP day +7"] <- "Day 7"
+# CRP_long$day[CRP_long$day=="CRP day +14"] <- "Day 14"
+# CRP_long$day[CRP_long$day=="CRP day +21"] <- "Day 21"
+# CRP_long$day[CRP_long$day=="CRP day +30"] <- "Day 30"
+# CRP_long$day <- factor(CRP_long$day, levels = c("Pre", "Day 0", "Day 7", "Day 14", "Day 21", "Day 30"))
+# ggplot(CRP_long, aes(x=day, y=CRP_value)) + geom_boxplot() + xlab("Days") + ylab("CRP") + theme_classic() + ggtitle("CRP") + expand_limits(x= c(0.5, 6.5), y = c(0, 20)) + scale_y_break(c(5, 6), ticklabels=c(7, 10, 15, 20), scales=0.20)
+```
 
 ## Figure 3. Cellular and humoral immune reconstitution after ide-cel
+```{r, fig.width=12, fig.height=12}
+cart2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE)
+# WBC
+timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 60, 90)
+WBC_fig <-
+  data.frame(timepoints,
+             t(round(
+               sapply(cart2[, c(
+                 "WBC apheresis",
+                 "WBC day -5 (k/ul)",
+                 "WBC day 0 (k/uL)",
+                 "WBC day +7",
+                 "WBC day +14",
+                 "WBC day +21",
+                 "WBC day +30",
+                 "WBC day +60",
+                 "WBC day +90"
+               )],
+               MedianCI,
+               conf.level = 0.95,
+               na.rm = TRUE), 9
+             )))
+WBC_fig <- WBC_fig %>%
+  ggplot(aes(x = timepoints, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days") + 
+  ylab("Median WBC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","D-5", "D0", "D7", "D14", "D21", "D30", "D60", "D90")
+  ) + ylim(0, 8)
+
+# ANC
+ANC_fig <-
+  data.frame(timepoints, t(round(
+    sapply(cart2[, c(
+      "ANC apheresis",
+      "ANC day -5 (k/ul)",
+      "ANC day 0 (k/uL)",
+      "ANC day +7",
+      "ANC day +14",
+      "ANC day +21",
+      "ANC day +30",
+      "ANC day +60",
+      "ANC day +90"
+    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+  )))
+ANC_fig <- ANC_fig %>% 
+  ggplot(aes(x = timepoints, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days") + 
+  ylab("Median ANC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","D-5", "D0", "D7", "D14", "D21", "D30", "D60", "D90")
+  ) + 
+  ylim(0, 5)
+
+Hb_fig <-
+  data.frame(timepoints, t(round(
+    sapply(cart2[, c(
+      "Hb apheresis",
+      "Hb day -5 (k/ul)",
+      "Hb day 0 (k/uL)",
+      "Hb day +7",
+      "Hb day +14",
+      "Hb day +21",
+      "Hb day +30",
+      "Hb day +60",
+      "Hb day +90"
+    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+  )))
+Hb_fig <- Hb_fig %>% 
+  ggplot(aes(x = timepoints, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days") + 
+  ylab("Median Hb") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","D-5", "D0", "D7", "D14", "D21", "D30", "D60", "D90")
+  ) + 
+  ylim(5, 15)
+
+# ALC
+ALC_fig <-
+  data.frame(timepoints, t(round(
+    sapply(cart2[, c(
+      "ALC apheresis",
+      "ALC day -5 (k/ul)",
+      "ALC day 0 (k/uL)",
+      "ALC day +7",
+      "ALC day +14",
+      "ALC day +21",
+      "ALC day +30",
+      "ALC day +60",
+      "ALC day +90"
+    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+  )))
+ALC_fig <- ALC_fig %>% 
+  ggplot(aes(x = timepoints, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days") + 
+  ylab("Median ALC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","D-5", "D0", "D7", "D14", "D21", "D30", "D60", "D90")
+  ) + 
+  ylim(0, 1.50)
+
+# Plt
+Plt_fig <-
+  data.frame(timepoints, t(round(
+    sapply(cart2[, c(
+      "Plt apheresis",
+      "Plt day -5 (k/ul)",
+      "Plt day 0 (k/uL)",
+      "Plt day +7",
+      "Plt day +14",
+      "Plt day +21",
+      "Plt day +30",
+      "Plt day +60",
+      "Plt day +90"
+    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+  )))
+Plt_fig <- Plt_fig %>% 
+  ggplot(aes(x = timepoints, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days") + 
+  ylab("Median Plt") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","D-5", "D0", "D7", "D14", "D21", "D30", "D60", "D90")
+  ) +
+  ylim(0, 200)
+
+# IgG
+#table(cart2$`IgG day +90`)
+#table(cart2$`IgG day +180`)
+cart2$`IgG day +90`[cart2$`IgG day +90` == "<109"] <- 77
+cart2$`IgG day +30`[cart2$`IgG day +30` == "<109"] <- 77
+cart2$`IgG day -5`[cart2$`IgG day -5` == "<109"] <- 77
+cart2$`IgG apheresis`[cart2$`IgG apheresis` == "<109"] <- 77
+
+cart2$`IgG day +90` <- as.numeric(cart2$`IgG day +90`)
+cart2$`IgG day +30` <- as.numeric(cart2$`IgG day +30`)
+cart2$`IgG day -5` <- as.numeric(cart2$`IgG day -5`)
+cart2$`IgG apheresis` <- as.numeric(cart2$`IgG apheresis`)
+timepoints2 <- c(-28, -5, 30, 90)
+IgG_fig <-
+  data.frame(timepoints2, t(round(
+    sapply(cart2[, c(
+      "IgG apheresis", 
+      "IgG day -5",
+      # "IgG day 0 (k/uL)", 
+      "IgG day +30", 
+      "IgG day +90")], MedianCI, conf.level =
+             0.95, na.rm = TRUE), 9
+  )))
+IgG_fig <- IgG_fig %>% 
+  ggplot(aes(x = timepoints2, y = median)) + 
+  geom_line(col = "blue") + xlab("Days") + 
+  ylab("Median IgG") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 30, 90),
+    labels = c("Apheresis", "D-5", "D0", "D30", "D90")) + 
+  ylim(0, 2000)
+
+(WBC_fig | ANC_fig) /
+  (Hb_fig | ALC_fig) /
+  (Plt_fig | IgG_fig) +
+  plot_annotation(tag_levels = "A")
+```
+
+<span style="color:blue">**IgG I need to fix the other 109**</span>
+
+Values less than the limit of detection (<109) were considered to be 77 which is the lower limit of detection divided by the square root of 2.
+One patient had an IgG day 0 value of <320.
+As this is above the limit of detection, I used the midway point between 320 and the lower limit of detection -- 214 -- as the value instead of <320.
+
+<br>
 

### 2022-03-25 Manuscript analyses.Rmd
Fix and add variables, add plots

--- 2022-03-16 Manuscript analyses.Rmd
@@
 library(labelled)
+library(DescTools)
+library(patchwork)
+library(ggbreak)
 # library(survival)
-# library(survminer)
+library(survminer)
 ```
@@
 cart1 <- cart %>% 
+  mutate(across(where(is.character), ~ str_replace(., "NE", NA_character_))) %>%
+  # censored days > 100 to 100
+  mutate(across(c(`Day of onset of CRS relative to infusion`,
+                  `Day of Max CRS (relative to infusion)`,
+                  `Day of onset of ICANS relative to infusion`,
+                  `Day of Max ICANS (relative to infusion)`), ~ case_when(
+    . > 100                                                       ~ 100,
+    TRUE                                                          ~ as.numeric(.)
+  ))) %>% 
   # defining BMI categories
@@
   mutate(ICANS_any = ifelse(`Max ICANS (relative to infusion)` == 0, "NO", "YES"),
-         ICANS_any2 <- ifelse(ICANS_any == "NO", 0, 1),
+         ICANS_any2 = ifelse(ICANS_any == "NO", 0, 1),
          ICANS_gradecat = case_when(
@@
          ICANS_gradecat = factor(ICANS_gradecat, levels = c("No ICANS", "Grade 1 or 2", "Grade ≥3"))
-  )
+  ) %>% 
+  mutate(`marrow cellularity baseline` = case_when(
+    `marrow cellularity baseline` == "\"patchy\""                 ~ "hyper",
+    TRUE                                                          ~ `marrow cellularity baseline`
+  )) %>% 
+  mutate(`marrow cellularity day +30` = case_when(
+    `marrow cellularity day +30` == "aplastic"                    ~ "hypo",
+    TRUE                                                          ~ `marrow cellularity day +30`
+  )) %>% 
+  mutate(`Access type` = case_when(
+    `Access type` == "Femoral"                                    ~ "Non-tunneled",
+    `Access type` == "AVF"                                        ~ "Peripheral",
+    TRUE                                                          ~ `Access type`
+  )) %>% 
+  # mutate(best_response = ) %>% 
+  mutate(Leukopenia_apheresis = case_when(
+    `WBC apheresis` < 4                                           ~ "YES",
+    is.na(`WBC apheresis`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_-5d` = case_when(
+    `WBC day -5 (k/ul)` < 4                                       ~ "YES",
+    is.na(`WBC day -5 (k/ul)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_0d` = case_when(
+    `WBC day 0 (k/uL)` < 4                                        ~ "YES",
+    is.na(`WBC day 0 (k/uL)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_7d` = case_when(
+    `WBC day +7` < 4                                              ~ "YES",
+    is.na(`WBC day +7`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_14d` = case_when(
+    `WBC day +14` < 4                                             ~ "YES",
+    is.na(`WBC day +14`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_21d` = case_when(
+    `WBC day +21` < 4                                             ~ "YES",
+    is.na(`WBC day +21`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_30d` = case_when(
+    `WBC day +30` < 4                                             ~ "YES",
+    is.na(`WBC day +30`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_60d` = case_when(
+    `WBC day +60` < 4                                             ~ "YES",
+    is.na(`WBC day +60`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Leukopenia_90d` = case_when(
+    `WBC day +90` < 4                                             ~ "YES",
+    is.na(`WBC day +90`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(gr3_Leukopenia_apheresis = case_when(
+    `WBC apheresis` < 2                                           ~ "YES",
+    is.na(`WBC apheresis`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_-5d` = case_when(
+    `WBC day -5 (k/ul)` < 2                                       ~ "YES",
+    is.na(`WBC day -5 (k/ul)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_0d` = case_when(
+    `WBC day 0 (k/uL)` < 2                                        ~ "YES",
+    is.na(`WBC day 0 (k/uL)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_7d` = case_when(
+    `WBC day +7` < 2                                              ~ "YES",
+    is.na(`WBC day +7`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_14d` = case_when(
+    `WBC day +14` < 2                                             ~ "YES",
+    is.na(`WBC day +14`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_21d` = case_when(
+    `WBC day +21` < 2                                             ~ "YES",
+    is.na(`WBC day +21`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_30d` = case_when(
+    `WBC day +30` < 2                                             ~ "YES",
+    is.na(`WBC day +30`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_60d` = case_when(
+    `WBC day +60` < 2                                             ~ "YES",
+    is.na(`WBC day +60`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Leukopenia_90d` = case_when(
+    `WBC day +90` < 2                                             ~ "YES",
+    is.na(`WBC day +90`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
+
+  mutate(Neutropenia_apheresis = case_when(
+    `ANC apheresis` < 1.8                                           ~ "YES",
+    is.na(`ANC apheresis`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_-5d` = case_when(
+    `ANC day -5 (k/ul)` < 1.8                                        ~ "YES",
+    is.na(`ANC day -5 (k/ul)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_0d` = case_when(
+    `ANC day 0 (k/uL)` < 1.8                                        ~ "YES",
+    is.na(`ANC day 0 (k/uL)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_7d` = case_when(
+    `ANC day +7` < 1.8                                              ~ "YES",
+    is.na(`ANC day +7`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_14d` = case_when(
+    `ANC day +14` < 1.8                                             ~ "YES",
+    is.na(`ANC day +14`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_21d` = case_when(
+    `ANC day +21` < 1.8                                             ~ "YES",
+    is.na(`ANC day +21`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_30d` = case_when(
+    `ANC day +30` < 1.8                                             ~ "YES",
+    is.na(`ANC day +30`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_60d` = case_when(
+    `ANC day +60` < 1.8                                             ~ "YES",
+    is.na(`ANC day +60`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Neutropenia_90d` = case_when(
+    `ANC day +90` < 1.8                                             ~ "YES",
+    is.na(`ANC day +90`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(gr3_Neutropenia_apheresis = case_when(
+    `ANC apheresis` < 1                                           ~ "YES",
+    is.na(`ANC apheresis`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_-5d` = case_when(
+    `ANC day -5 (k/ul)` < 1                                        ~ "YES",
+    is.na(`ANC day -5 (k/ul)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_0d` = case_when(
+    `ANC day 0 (k/uL)` < 1                                        ~ "YES",
+    is.na(`ANC day 0 (k/uL)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_7d` = case_when(
+    `ANC day +7` < 1                                              ~ "YES",
+    is.na(`ANC day +7`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_14d` = case_when(
+    `ANC day +14` < 1                                             ~ "YES",
+    is.na(`ANC day +14`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_21d` = case_when(
+    `ANC day +21` < 1                                             ~ "YES",
+    is.na(`ANC day +21`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_30d` = case_when(
+    `ANC day +30` < 1                                             ~ "YES",
+    is.na(`ANC day +30`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_60d` = case_when(
+    `ANC day +60` < 1                                             ~ "YES",
+    is.na(`ANC day +60`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Neutropenia_90d` = case_when(
+    `ANC day +90` < 1                                             ~ "YES",
+    is.na(`ANC day +90`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
+
+  mutate(Anemia_apheresis = case_when(
+    `Hb apheresis` < 11.4                                           ~ "YES",
+    is.na(`Hb apheresis`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_-5d` = case_when(
+    `Hb day -5 (k/ul)` < 11.4                                        ~ "YES",
+    is.na(`Hb day -5 (k/ul)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_0d` = case_when(
+    `Hb day 0 (k/uL)` < 11.4                                        ~ "YES",
+    is.na(`Hb day 0 (k/uL)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_7d` = case_when(
+    `Hb day +7` < 11.4                                              ~ "YES",
+    is.na(`Hb day +7`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_14d` = case_when(
+    `Hb day +14` < 11.4                                             ~ "YES",
+    is.na(`Hb day +14`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_21d` = case_when(
+    `Hb day +21` < 11.4                                             ~ "YES",
+    is.na(`Hb day +21`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_30d` = case_when(
+    `Hb day +30` < 11.4                                             ~ "YES",
+    is.na(`Hb day +30`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_60d` = case_when(
+    `Hb day +60` < 11.4                                             ~ "YES",
+    is.na(`Hb day +60`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Anemia_90d` = case_when(
+    `Hb day +90` < 11.4                                             ~ "YES",
+    is.na(`Hb day +90`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(gr3_Anemia_apheresis = case_when(
+    `Hb apheresis` < 8                                           ~ "YES",
+    is.na(`Hb apheresis`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_-5d` = case_when(
+    `Hb day -5 (k/ul)` < 8                                        ~ "YES",
+    is.na(`Hb day -5 (k/ul)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_0d` = case_when(
+    `Hb day 0 (k/uL)` < 8                                        ~ "YES",
+    is.na(`Hb day 0 (k/uL)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_7d` = case_when(
+    `Hb day +7` < 8                                              ~ "YES",
+    is.na(`Hb day +7`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_14d` = case_when(
+    `Hb day +14` < 8                                             ~ "YES",
+    is.na(`Hb day +14`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_21d` = case_when(
+    `Hb day +21` < 8                                             ~ "YES",
+    is.na(`Hb day +21`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_30d` = case_when(
+    `Hb day +30` < 8                                             ~ "YES",
+    is.na(`Hb day +30`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_60d` = case_when(
+    `Hb day +60` < 8                                             ~ "YES",
+    is.na(`Hb day +60`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Anemia_90d` = case_when(
+    `Hb day +90` < 8                                             ~ "YES",
+    is.na(`Hb day +90`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
+
+  mutate(Thrombocytopenia_apheresis = case_when(
+    `Plt apheresis` < 143                                           ~ "YES",
+    is.na(`Plt apheresis`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_-5d` = case_when(
+    `Plt day -5 (k/ul)` < 143                                        ~ "YES",
+    is.na(`Plt day -5 (k/ul)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_0d` = case_when(
+    `Plt day 0 (k/uL)` < 143                                        ~ "YES",
+    is.na(`Plt day 0 (k/uL)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_7d` = case_when(
+    `Plt day +7` < 143                                              ~ "YES",
+    is.na(`Plt day +7`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_14d` = case_when(
+    `Plt day +14` < 143                                             ~ "YES",
+    is.na(`Plt day +14`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_21d` = case_when(
+    `Plt day +21` < 143                                             ~ "YES",
+    is.na(`Plt day +21`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_30d` = case_when(
+    `Plt day +30` < 143                                             ~ "YES",
+    is.na(`Plt day +30`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_60d` = case_when(
+    `Plt day +60` < 143                                             ~ "YES",
+    is.na(`Plt day +60`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`Thrombocytopenia_90d` = case_when(
+    `Plt day +90` < 143                                             ~ "YES",
+    is.na(`Plt day +90`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(gr3_Thrombocytopenia_apheresis = case_when(
+    `Plt apheresis` < 50                                           ~ "YES",
+    is.na(`Plt apheresis`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_-5d` = case_when(
+    `Plt day -5 (k/ul)` < 50                                        ~ "YES",
+    is.na(`Plt day -5 (k/ul)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_0d` = case_when(
+    `Plt day 0 (k/uL)` < 50                                        ~ "YES",
+    is.na(`Plt day 0 (k/uL)`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_7d` = case_when(
+    `Plt day +7` < 50                                              ~ "YES",
+    is.na(`Plt day +7`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_14d` = case_when(
+    `Plt day +14` < 50                                             ~ "YES",
+    is.na(`Plt day +14`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_21d` = case_when(
+    `Plt day +21` < 50                                             ~ "YES",
+    is.na(`Plt day +21`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_30d` = case_when(
+    `Plt day +30` < 50                                             ~ "YES",
+    is.na(`Plt day +30`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_60d` = case_when(
+    `Plt day +60` < 50                                             ~ "YES",
+    is.na(`Plt day +60`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>% 
+  mutate(`gr3_Thrombocytopenia_90d` = case_when(
+    `Plt day +90` < 50                                             ~ "YES",
+    is.na(`Plt day +90`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
+
+  mutate(`cytopenia_30d` = case_when(
+    `WBC day +30` < 4 | 
+      `ANC day +30` < 1.8 | 
+      `Hb day +30` < 11.4 | 
+      `Plt day +30` < 143                                             ~ "YES",
+    is.na(`WBC day +30`) |
+      is.na(`ANC day +30`) |
+      is.na(`Hb day +30`) |
+      is.na(`Plt day +30`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(`gr3_cytopenia_30d` = case_when(
+    `WBC day +30` < 2 | 
+      `ANC day +30` < 1 | 
+      `Hb day +30` < 8 | 
+      `Plt day +30` < 50                                              ~ "YES",
+    is.na(`WBC day +30`) |
+      is.na(`ANC day +30`) |
+      is.na(`Hb day +30`) |
+      is.na(`Plt day +30`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(`gr3_cytopenia_90d` = case_when(
+    `WBC day +90` < 2 | 
+      `ANC day +90` < 1 | 
+      `Hb day +90` < 8 | 
+      `Plt day +90` < 50                                             ~ "YES",
+    is.na(`WBC day +90`) |
+      is.na(`ANC day +90`) |
+      is.na(`Hb day +90`) |
+      is.na(`Plt day +90`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(any_infection = case_when(
+    `Infection (yes, no)` == 1                                    ~ "Yes",
+    `Infection (yes, no)` == 0                                    ~ "No"
+  )) %>% 
+  mutate(any_sevinfection = case_when(
+    `Severe Infection (yes, no)` == 1                              ~ "Yes",
+    `Severe Infection (yes, no)` == 0                              ~ "No"
+  )) %>%
+
+  mutate(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` = case_when(
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "VGPR")        ~ "VGPR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "PR")          ~ "PR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "evaluable")   ~ NA_character_,
+    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` == "CR"	                   ~ "CR, MRD unknown",
+    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` == "CR, MRD+"	             ~ "CR, MRD+",
+
+    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` == "sCR, MRD+"           	 ~ "sCR, MRD+",
+    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` %in% c(
+      "sCR MRD-", "sCR, MRD-")                                                         ~ "sCR, MRD-",
+
+    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` %in% c(
+      "sCR", "sCR (flow neg, no clonoSEQ ID)", "sCR MRD - by flow/no clonoSEQ)",
+      "sCR, MRD- by flow/no clonoSEQ)")                                                ~ "sCR, MRD unknown",
+
+    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`
+  )) %>% 
+  mutate(ORR_30days = case_when(
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "CR")   ~ "ORR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "PR")   ~ "ORR",
+    is.na(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`)              ~ NA_character_,
+    TRUE                                                                        ~ "PD/SD/MR"
+  )) %>% 
+  mutate(MRDneg_30days = case_when(
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "MRD-")        ~ "Yes",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "MRD")         ~ "No",
+    TRUE                             ~ NA_character_
+  )) %>% 
+  mutate(day30_response = case_when(
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "VGPR")        ~ "VGPR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "PR")          ~ "PR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "sCR")	       ~ "sCR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "CR")	         ~ "CR",
+    is.na(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`)                     ~ NA_character_,
+    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`
+  )) %>% 
+  mutate(day30_response_group = case_when(
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "VGPR")        ~ "VGPR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "PR")          ~ "PR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "CR")	         ~ "CR or sCR",
+    is.na(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`)                     ~ NA_character_,
+    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`
+  )) %>% 
+  mutate(day30_response_sCRvsOthers = case_when(
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "CR")	         ~ "CR or sCR",
+    is.na(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`)                     ~ NA_character_,
+    TRUE           ~ "Others"
+  )) %>%
+
+  mutate(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` = case_when(
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "VGPR")        ~ "VGPR",
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "PR")          ~ "PR",
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "evaluable")   ~ NA_character_,
+
+    `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
+      "CR", "CR (no clonoSEQ/MRD as no marrow)")                                      ~ "CR, MRD unknown",
+
+    `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
+      "sCR (clonoSEQ pending, flow neg)", 
+      "sCR (no clonoSEQ for MRD, flow suspicious for MRD)",
+      "sCR (no clonoSEQ, flow neg)")                                                  ~ "sCR, MRD unknown",
+
+    `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
+      "sCR, MRD - (by flow+)", "sCR, MRD-	12 (24%)")                                  ~ "sCR, MRD-",
+
+    `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` == "sCR, MRD+"	            ~	"sCR, MRD+",
+
+    TRUE           ~ `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`
+  )) %>% 
+  mutate(ORR_90days = case_when(
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "CR")    ~ "ORR",
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "PR")    ~ "ORR",
+    is.na(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`)               ~ NA_character_,
+    TRUE                                                                        ~ "PD/SD/MR"
+  )) %>% 
+  mutate(MRDneg_90days = case_when(
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD-")        ~ "Yes",
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD")         ~ "No",
+    TRUE                             ~ NA_character_
+  )) %>% 
+  mutate(day90_response_group = case_when(
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "VGPR")        ~ "VGPR",
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "PR")          ~ "PR",
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "CR")	        ~ "CR or sCR",
+    is.na(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`)                     ~ NA_character_,
+    TRUE           ~ `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`
+  )) %>% 
+  mutate(day90_response = case_when(
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "VGPR")        ~ "VGPR",
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "PR")          ~ "PR",
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "sCR")	        ~ "sCR",
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "CR")	        ~ "CR",
+    is.na(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`)                     ~ NA_character_,
+    TRUE           ~ `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`
+  )) %>% 
+  mutate(day90_response_sCRvsOthers = case_when(
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "CR")	         ~ "CR or sCR",
+    is.na(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`)                      ~ NA_character_,
+    TRUE           ~ "Others"
+  )) %>% 
+  mutate(best_response = case_when(
+    day30_response_group == "CR or sCR" |
+      day90_response_group == "CR or sCR"                                             ~ "CR or sCR",
+    day30_response_group == "VGPR" |
+      day90_response_group == "VGPR"                                                  ~ "VGPR",
+    day30_response_group == "PR" |
+      day90_response_group == "PR"                                                    ~ "PR",
+    TRUE                                                                        ~ NA_character_
+  )) %>% 
+  mutate(MRDneg_in_best_response = case_when(
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD-") |
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "MRD-")        ~ "Yes",
+    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD") |
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "MRD")         ~ "No",
+    TRUE                             ~ NA_character_
+  ))
 
@@
 ```{r}
-selected <- cart1 %>% 
-  select(Age, agecat, Sex, `BMI at apheresis`, bmicat, bmicat2, `Extramedullary Disease?
-(yes=1, no=0)`, tumor_burden, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, `ECOG > or = 2?
-(Yes=1, No=0)`, `t(4:14) prior to CAR-T infusion (yes=1, no=0)`, `t(14:16) prior to CAR-T infusion (yes=1, no=0)`, cyto, `Bridging Therapy (Yes=1, No=0)`, `Number of prior lines of therapy`, `Prior auto SCT (yes=1, no=0)`, immuno, proteasome, dara, doubleref, tripleref, pentaref, CRS_any, CRS_gradecat, `Duration of CRS (days)`, ICANS_any, ICANS_gradecat, `Duration of ICANS (days)`, `Infection (yes, no)`, `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
-                             # `Baseline CRP`, `Max CRP`, `Baseline Ferritin`, `Max Ferritin`, `Cell Dose (million cells)`, 
-                             # `LDH at Baseline`, 
-                             `LDH day +30`, `LDH day +90`#, 
-                             # `B2 Microglobulin at Baseline`, `Day 30 B2 Microglobulin`, `Day 90 B2 Microglobulin`, `Cyclophosphamide Dose (mg)`, `Cyclophosphamide Actual Dose (mg/m2)`, `Fludarabine Total Dose (mg)`, `Fludarabine Actual Dose (mg/m2)`, `Fludarabine Dose Reduction`
-                             )
-# write.csv(selected,"/Volumes/Peres_Research/Myeloma/CART/selected_data.csv", row.names = TRUE)
-selected %>% 
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (yes=1, no=0)`, 
+         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, 
+         `R-ISS at CAR-T Infusion`, 
+         cyto, `Deletion 17p prior to CAR-T infusion (yes=1, no=0)`,
+         `t(4:14) prior to CAR-T infusion (yes=1, no=0)`,
+         `t(14:16) prior to CAR-T infusion (yes=1, no=0)`,
+         `Bridging Therapy (Yes=1, No=0)`,
+         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`) %>% 
   tbl_summary(
+    type = list(
+      c(`Extramedullary Disease? (yes=1, no=0)`, `High Marrow Burden? (yes=1, no=0)`,
+        cyto, `Deletion 17p prior to CAR-T infusion (yes=1, no=0)`,
+        `t(4:14) prior to CAR-T infusion (yes=1, no=0)`,
+        `t(14:16) prior to CAR-T infusion (yes=1, no=0)`,
+        `Bridging Therapy (Yes=1, No=0)`, `Prior auto SCT (yes=1, no=0)`,
+        immuno, proteasome, dara, doubleref, tripleref, pentaref,
+        `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`)
+      ~"categorical"),
+
+    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
+
+## Table 2. Clinical outcomes
+**best response**
+```{r}
+tbl1 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Max CRS grade (0-5)`,
+         `Day of onset of CRS relative to infusion`,
+         `Day of Max CRS (relative to infusion)`, `Duration of CRS (days)`,
+
+         `Max ICANS (relative to infusion)`,
+         `Day of onset of ICANS relative to infusion`,
+         `Day of Max ICANS (relative to infusion)`,
+         `Duration of ICANS (days)`) %>% 
+  tbl_summary(type = list(
+    c(`Day of onset of CRS relative to infusion`, `Day of onset of ICANS relative to infusion`,
+      `Day of Max ICANS (relative to infusion)`, `Duration of ICANS (days)`) ~ "continuous"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, 
+         `Anakinra (Yes=1, No=0)`) %>% 
+  tbl_summary(type = list(
+    c(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, 
+      `Anakinra (Yes=1, No=0)`) ~ "categorical"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl3 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(MRDneg_30days,
+         ORR_30days,
+         day30_response,
+         day30_response_group) %>% 
+  tbl_summary(type = list(
+    c(MRDneg_30days) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl4 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(day30_response_group == "CR or sCR") %>% 
+  select(MRDneg_30days) %>% 
+  tbl_summary(type = list(c(MRDneg_30days) ~ "categorical"),
+              label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
+              digits = all_continuous() ~ 1,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl5 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(MRDneg_90days,
+         ORR_90days,
+         day90_response,
+         day90_response_group) %>% 
+  tbl_summary(type = list(
+    c(MRDneg_90days) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl6 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(day90_response_group == "CR or sCR") %>% 
+  select(MRDneg_90days) %>% 
+  tbl_summary(type = list(c(MRDneg_90days) ~ "categorical"),
+              label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
+              digits = all_continuous() ~ 1,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl7 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(best_response) %>% 
+  tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"),
+              label = list(best_response ~ "best response in the first 90 days"),
+              digits = all_continuous() ~ 1,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl8 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(best_response == "CR or sCR") %>% 
+  select(MRDneg_in_best_response) %>% 
+  tbl_summary(type = list(c(MRDneg_in_best_response) ~ "categorical"),
+              label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() %>%
+  gt::tab_source_note(gt::md("**At 30days: <br>
+                             1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
+                             1 patients was not evaluated. <br>
+                             At 90days: <br>
+                             1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
+                             1 patient is not Heme not evaluable; <br>
+                             2 patients were not evaluated; <br>
+                             1 patients is not evaluable by death**"))
+
+```
+
+For responses make denominator evaluable patients
+Patient who died or was lost to follow-up or had non-secretory disease would not be evaluable
+
+## Table 3. Bone marrow biopsy findings
+```{r}
+tbl1 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("marrow cellularity" = `marrow cellularity baseline`, 
+         "marrow cellularity (%)" = `marrow cellularity baseline (%)`,
+         "% CD138 positive by IHC" = `marrow CD138 baseline (%)`, 
+         "Fibrosis grade" = `marrow fibrosis baseline`, 
+         "Dysplasia present" = `marrow dysplasia baseline`
+  ) %>% 
+  tbl_summary(type = list(
+    c(#`marrow cellularity baseline (%)`, `marrow CD138 baseline (%)`, 
+      `Fibrosis grade`) ~ "continuous"
+  ),
             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
@@
   bold_labels() %>% add_stat_label() %>% 
-             #modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  # use `modify_footnote(everything() ~ NA, abbreviation = TRUE)` to delete abbrev. footnotes
   modify_footnote(update = everything() ~ NA)
-```
-
-<!-- Age (years)	 -->
-<!--      Median (range)	 -->
-<!--      60 – n (%)	 -->
-<!-- Male sex – n (%)	 -->
-<!-- Extramedullary disease – n (%)	 -->
-<!-- High marrow burden (≥50%) – n (%)	 -->
-<!-- ECOG performance status at lymphodepletion – n (%)	 -->
-<!--      0	 -->
-<!--      1	 -->
-<!--      2	 -->
-<!--      3	 -->
-<!-- R-ISS stage – n (%)	 -->
-<!--      I	 -->
-<!--      II	 -->
-<!--      III	 -->
-<!--      Unknown	 -->
-<!-- High-risk cytogenetics – n (%)	 -->
-<!--      del(17p)	 -->
-<!--      t(4;14)	 -->
-<!--      t(14;16)	 -->
-<!--      Unknown	 -->
-<!-- Bridging therapy – n (%)	 -->
-<!-- Prior anti-myeloma regimens – median (range)	 -->
-<!--      Prior autoSCT – n (%)	 -->
-<!--      Prior alloSCT – n (%)	 -->
-<!--      Prior BCMA-directed therapy – n (%)	 -->
-<!-- Refractory status – n (%)	 -->
-<!--      Immunomodulatory agent	 -->
-<!--      Proteasome inhibitor	 -->
-<!--      Daratumumab	 -->
-<!--      Double-refractory disease	 -->
-<!--      Triple-refractory disease	 -->
-<!--      Penta-refractory disease	 -->
-<!-- Eligible for KarMMa 1 trial at apheresis – n (%)	 -->
-
-## Table 2. Clinical outcomes
-
-<!-- CRS maximum grade – n (%)	 -->
-<!--      0	 -->
-<!--      1	 -->
-<!--      2	 -->
-<!--      3	 -->
-<!--      4	 -->
-<!--      5	 -->
-<!-- Time to CRS onset (days) – median (range)	 -->
-<!-- Time to maximum severity CRS (days) – median (range)	 -->
-<!-- Duration of CRS (days) – median (range)	 -->
-<!-- ICANS maximum grade – n (%)	 -->
-<!--      0	 -->
-<!--      1	 -->
-<!--      2	 -->
-<!--      3	 -->
-<!--      4	 -->
-<!--      5	 -->
-<!-- Time to ICANS onset (days) – median (range)	 -->
-<!-- Time to maximum severity ICANS (days) – median (range)	 -->
-<!-- Duration of ICANS (days) – median (range)	 -->
-<!-- Treatment for toxicity – n (%)	 -->
-<!--      Steroid use	 -->
-<!--      Tocilizumab use	 -->
-<!--      Anakinra use	 -->
-<!-- Day 30 response – n (%)	 -->
-<!--      ORR	 -->
-<!--      CR or sCR	 -->
-<!--           MRD negative	 -->
-<!--      VGPR	 -->
-<!--      PR	 -->
-<!-- Day 90 response – n (%)	 -->
-<!--      ORR	 -->
-<!--      CR or sCR	 -->
-<!--           MRD negative	 -->
-<!--      VGPR	 -->
-<!--      PR	 -->
-<!-- Best response in first 90 days – n (%)	 -->
-<!--      CR or sCR	 -->
-<!--           MRD negative	 -->
-<!--      VGPR	 -->
-<!--      PR	 -->
-
-For responses make denominator evaluable patients
-Patient who died or was lost to follow-up or had non-secretory disease would not be evaluable
-
-## Table 3. Bone marrow biopsy findings
-
-<!-- 	Baseline (n=52)	Day 30 (n=44)	Day 90 (n=32) -->
-<!-- Marrow cellularity – n (%)			 -->
-<!--      Hypocellular			 -->
-<!--      Normocellular			 -->
-<!--      Hypercellular			 -->
-<!--      Variable			 -->
-<!-- Marrow cellularity (%) – median (range)			 -->
-<!-- % CD138 positive by IHC – median (range)			 -->
-<!-- Fibrosis grade – median (range)			 -->
-<!-- Dysplasia present – n (%)			 -->
+
+tbl2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("marrow cellularity" = `marrow cellularity day +30`, 
+         "marrow cellularity (%)" = `marrow % cellularity day +30`,
+         "% CD138 positive by IHC" = `marrow %CD138 day +30`, 
+         "Fibrosis grade" = `marrow fibrosis day +30`, 
+         "Dysplasia present" = `marrow dysplasia day +30`
+  ) %>% 
+  mutate(`marrow cellularity (%)` = as.numeric(`marrow cellularity (%)`)) %>% 
+  mutate(`% CD138 positive by IHC` = as.numeric(`% CD138 positive by IHC`)) %>% 
+  mutate(`Fibrosis grade` = as.numeric(`Fibrosis grade`)) %>% 
+  mutate(`Dysplasia present` = as.numeric(`Dysplasia present`)) %>% 
+  tbl_summary(type = list(
+    c(`marrow cellularity (%)`, `% CD138 positive by IHC`, 
+      `Fibrosis grade`) ~ "continuous"
+  ),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl3 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("marrow cellularity" = `marrow cellularity day +90`, 
+         "marrow cellularity (%)" = `marrow % cellularity day +90`,
+         "% CD138 positive by IHC" = `marrow %CD138 day +90`, 
+         "Fibrosis grade" = `marrow fibrosis day +90`, 
+         "Dysplasia present" = `marrow dysplasia day +90`
+  ) %>% 
+  mutate(`marrow cellularity (%)` = as.numeric(`marrow cellularity (%)`)) %>% 
+  mutate(`% CD138 positive by IHC` = as.numeric(`% CD138 positive by IHC`)) %>% 
+  mutate(`Fibrosis grade` = as.numeric(`Fibrosis grade`)) %>% 
+  mutate(`Dysplasia present` = as.numeric(`Dysplasia present`)) %>% 
+  tbl_summary(type = list(
+    c(`marrow cellularity (%)`, `% CD138 positive by IHC`, 
+      `Fibrosis grade`) ~ "continuous"
+  ),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl_merge(list(tbl1, tbl2, tbl3), tab_spanner = c("Baseline", "Day 30", "Day 90"))
+```
 
 ## Table 4. Supportive therapies and engraftment
-
-<!-- Granulocyte colony stimulating factor (G-CSF)	 -->
-<!--      G-CSF administered – n (%)	 -->
-<!--      First day of G-CSF – median (range)	 -->
-<!--      Last day of G-CSF – median (range)	 -->
-<!-- CD34 stem cell boost	 -->
-<!--      Stem cell boost administered – n (%)	 -->
-<!--      Day of stem cell boost – median (range)	 -->
-<!--      Dose of stem cell boost (million cells) – median (range)	 -->
-<!-- Engraftment day – median (range)	 -->
-<!-- Transfusions post-CART – n (%)	 -->
-<!--      RBC transfusion within 7 days	 -->
-<!--      Plt transfusion within 7 days	 -->
-<!--      RBC transfusion >7 days	 -->
-<!--      Plt transfusion >7 days	 -->
-<!-- Intravenous immunoglobulin (IVIG)	 -->
-<!--      IVIG administered – n (%)	 -->
-<!--      First day of IVIG – median (range)	 -->
-<!--      Last day of IVIG – median (range)	 -->
+Jenn
+
+```{r}
+# cart1 %>% 
+#   distinct(MRN, .keep_all = TRUE) %>% 
+#   select(`Need for G-CSF post infus (Yes, No)`, `First Day of GCSF`, `Last Day of GCSF`,
+#          `CD34 stem cell boost`, `Day of stem cell boost`, `Boost cell dose (million cells)`,
+#          `Engraftment Day`,
+#          `RBC transfusion within 7d post CART`, `Plt transfusion within 7d post CART`, 
+#          `RBC transfusion >7d post CART`, `Plt transfusion >7d post CART`,
+#          `Need for IVIG (Yes, No)`, `First day of IVIG`, `Last day of IVIG`
+#   ) %>% 
+#   tbl_summary(type = list(
+#     c(`Day of stem cell boost`, `Boost cell dose (million cells)`,
+#     `Last day of IVIG`) ~ "continuous",
+#     c(`Need for G-CSF post infus (Yes, No)`,
+#       `CD34 stem cell boost`,
+#       `RBC transfusion within 7d post CART`, `Plt transfusion within 7d post CART`, 
+#          `RBC transfusion >7d post CART`, `Plt transfusion >7d post CART`,
+#       `Need for IVIG (Yes, No)`) ~ "categorical"
+#   ),
+#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+#             digits = all_continuous() ~ 1) %>% 
+#   bold_labels() %>% add_stat_label() %>% 
+#   modify_footnote(update = everything() ~ NA)
+```
 
 ## Table S1. Apheresis and product characteristics
-
-<!-- Collection goal (TBV) – median (range)	 -->
-<!-- Whole blood processed (mL) – median (range)	 -->
-<!-- Total blood volume processed (mL) – median (range)	 -->
-<!-- Access type – n (%)	 -->
-<!--      Non-tunneled central venous catheter	 -->
-<!--      Peripheral line	 -->
-<!--      Other	 -->
-<!-- Final collection volume (mL) – median (range)	 -->
-<!-- Run time (minutes) – median (range)	 -->
-<!-- Time from apheresis to product infusion (days) – median (range)	 -->
-<!-- Total bags infused – median (range)	 -->
-<!-- Total dose volume (mL) – median (range)	 -->
-<!-- Total cell dose (million cells) – median (range)	 -->
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(TBV, `Whole blood processed (mL)`,
+         `Final collection volume (mL)`, 
+         `TBV processed`, 
+         `Access type`, `Final collection volume (mL)`,
+         `Run time (min)`,
+         `Time from apheresis to CAR-T infusion (days)`, `Total bags`,
+         `Total dose volume (mL)`, `Total cell dose (million cells)`
+
+  ) %>% 
+  tbl_summary(type = list(c(TBV, `Total bags`) ~ "continuous"),
+            statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+            digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
 
 ## Table S2. Cytopenias following ide-cel
-
-<!-- 	Apheresis	Day -5	Day 0	Day 7	Day 14	Day 21	Day 30	Day 90 -->
-<!-- Leukopenia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
-<!-- Neutropenia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
-<!-- Anemia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
-<!-- Thrombocytopenia – n (%)								 -->
-<!--      Any grade								 -->
-<!--      Grade 3+								 -->
+**NAs are the patients who died (black) and test was not done (grey), they are remove from the denom (%) but not from the the N**
+
+```{r}
+tbl1 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_apheresis`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_apheresis`, 
+         "Neutropenia" = `Neutropenia_apheresis`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_apheresis`, 
+         "Anemia" = `Anemia_apheresis`, 
+         "Grade3+ Anemia" = `gr3_Anemia_apheresis`, 
+         "Thrombocytopenia" = `Thrombocytopenia_apheresis`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_apheresis`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1#,
+            # missing = "no"
+            ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_-5d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_-5d`, 
+         "Neutropenia" = `Neutropenia_-5d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_-5d`,
+         "Anemia" = `Anemia_-5d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_-5d`, 
+         "Thrombocytopenia" = `Thrombocytopenia_-5d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_-5d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1#,
+            # missing = "no"
+            ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl3 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_0d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_0d`, 
+         "Neutropenia" = `Neutropenia_0d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_0d`, 
+         "Anemia" = `Anemia_0d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_0d`,
+         "Thrombocytopenia" = `Thrombocytopenia_0d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_0d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1#,
+            # missing = "no"
+            ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl4 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_7d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_7d`, 
+         "Neutropenia" = `Neutropenia_7d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_7d`, 
+         "Anemia" = `Anemia_7d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_7d`, 
+         "Thrombocytopenia" = `Thrombocytopenia_7d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_7d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1#,
+            # missing = "no"
+            ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl5 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(is.na(Not_evaluable_at_14days)) %>% 
+  select("Leukopenia" = `Leukopenia_14d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_14d`, 
+         "Neutropenia" = `Neutropenia_14d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_14d`,
+         "Anemia" = `Anemia_14d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_14d`,
+         "Thrombocytopenia" = `Thrombocytopenia_14d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_14d` 
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1#,
+            # missing = "no"
+            ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl6 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(is.na(Not_evaluable_at_21days)) %>% 
+  select("Leukopenia" = `Leukopenia_21d`,
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_21d`, 
+         "Neutropenia" = `Neutropenia_21d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_21d`, 
+         "Anemia" = `Anemia_21d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_21d`,
+         "Thrombocytopenia" = `Thrombocytopenia_21d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_21d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1#,
+            # missing = "no"
+            ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl7 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(is.na(Not_evaluable_at_30days)) %>% 
+  select("Leukopenia" = `Leukopenia_30d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_30d`,
+         "Neutropenia" = `Neutropenia_30d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_30d`,
+         "Anemia" = `Anemia_30d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_30d`, 
+         "Thrombocytopenia" = `Thrombocytopenia_30d`,
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_30d` 
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1#,
+            # missing = "no"
+            ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl8 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(is.na(Not_evaluable_at_90days)) %>% 
+  select("Leukopenia" = `Leukopenia_90d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_90d`,
+         "Neutropenia" = `Neutropenia_90d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_90d`,
+         "Anemia" = `Anemia_90d`,
+         "Grade3+ Anemia" = `gr3_Anemia_90d`,
+         "Thrombocytopenia" = `Thrombocytopenia_90d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_90d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+            digits = all_continuous() ~ 1#,
+            # missing = "no"
+            ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), 
+          tab_spanner = c("Apheresis", "Day -5",	"Day 0",	"Day 7",	"Day 14",	"Day 21",	"Day 30",	"Day 90")) %>% as_gt() %>%
+  gt::tab_source_note(gt::md("**Not evaluable patients are removed from the denominator <br>
+                             1 patient has missing 90 days values**"))
+```
 
 ## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30
+**Make sure that if one of wbc, anc, hb or plt is NA then cytopenia should be NA**
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(is.na(Not_evaluable_at_30days)) %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (yes=1, no=0)`, 
+         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, cyto, 
+         `Bridging Therapy (Yes=1, No=0)`,
+         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
+         `gr3_cytopenia_30d`) %>% 
+  tbl_summary(by = `gr3_cytopenia_30d`,
+    type = list(
+    `Extramedullary Disease? (yes=1, no=0)` ~ "categorical",
+    cyto ~ "categorical",
+    `Bridging Therapy (Yes=1, No=0)` ~ "categorical",
+    `Prior auto SCT (yes=1, no=0)` ~ "categorical",
+    immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
+    doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
+    `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)` ~"categorical"),
+
+    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1
+    ) %>% 
+  bold_labels() %>% add_stat_label() %>% add_p() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
+```
 
 ## Table S3. Patient characteristics by grade 3+ cytopenia at Day 90
-
-(Similar to above)
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(is.na(Not_evaluable_at_90days)) %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (yes=1, no=0)`, 
+         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, cyto, 
+         `Bridging Therapy (Yes=1, No=0)`,
+         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
+         `gr3_cytopenia_90d`) %>% 
+  tbl_summary(by = `gr3_cytopenia_90d`,
+    type = list(
+    `Extramedullary Disease? (yes=1, no=0)` ~ "categorical",
+    cyto ~ "categorical",
+    `Bridging Therapy (Yes=1, No=0)` ~ "categorical",
+    `Prior auto SCT (yes=1, no=0)` ~ "categorical",
+    immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
+    doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
+    `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)` ~"categorical"),
+
+    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1
+    ) %>% 
+  bold_labels() %>% add_stat_label() %>%  add_p() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 90?**")
+```
 
 ## Table S4. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
+```{r}
+tbl1 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(is.na(Not_evaluable_at_30days)) %>% 
+  select(CRS_gradecat,
+         `Day of onset of CRS relative to infusion`,
+         `Day of Max CRS (relative to infusion)`, `Duration of CRS (days)`,
+
+         ICANS_gradecat,
+         `Day of onset of ICANS relative to infusion`,
+         `Day of Max ICANS (relative to infusion)`,
+         `Duration of ICANS (days)`, gr3_cytopenia_30d) %>% 
+  tbl_summary(by =`gr3_cytopenia_30d`,
+              type = list(
+    c(`Day of onset of CRS relative to infusion`, 
+      `Day of Max CRS (relative to infusion)`,
+      `Day of onset of ICANS relative to infusion`,
+      `Day of Max ICANS (relative to infusion)`, `Duration of ICANS (days)`) ~ "continuous"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
+
+tbl2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(is.na(Not_evaluable_at_30days)) %>% 
+  select(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, 
+         `Anakinra (Yes=1, No=0)`, gr3_cytopenia_30d) %>% 
+  tbl_summary(by =`gr3_cytopenia_30d`,
+              type = list(
+    c(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, 
+      `Anakinra (Yes=1, No=0)`) ~ "categorical"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl3 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(is.na(Not_evaluable_at_30days)) %>% 
+  select(#MRDneg_30days,
+         ORR_30days, day30_response_sCRvsOthers,
+         day30_response_group, gr3_cytopenia_30d) %>% 
+  tbl_summary(by =`gr3_cytopenia_30d`,
+    #           type = list(
+    # c(MRDneg_30days) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
+
+# tbl4 <- cart1 %>% 
+#   distinct(MRN, .keep_all = TRUE) %>% 
+#   filter(is.na(Not_evaluable_at_30days)) %>% 
+#   filter(day30_response_group == "CR or sCR") %>% 
+#   select(MRDneg_30days, gr3_cytopenia_30d) %>% 
+#   tbl_summary(by =`gr3_cytopenia_30d`,
+#               type = list(c(MRDneg_30days) ~ "categorical"),
+#               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>% 
+#   bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl5 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(is.na(Not_evaluable_at_30days)) %>% 
+  select(#MRDneg_90days,
+         ORR_90days, day90_response_sCRvsOthers,
+         day90_response_group, gr3_cytopenia_30d) %>% 
+  tbl_summary(by =`gr3_cytopenia_30d`,
+    #           type = list(
+    # c(MRDneg_90days) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
+
+# tbl6 <- cart1 %>% 
+#   distinct(MRN, .keep_all = TRUE) %>% 
+#   filter(is.na(Not_evaluable_at_30days)) %>% 
+#   filter(day90_response_group == "CR or sCR") %>% 
+#   select(MRDneg_90days, gr3_cytopenia_30d) %>% 
+#   tbl_summary(by =`gr3_cytopenia_30d`,
+#               type = list(c(MRDneg_90days) ~ "categorical"),
+#               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>% 
+#   bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl7 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(is.na(Not_evaluable_at_30days)) %>% 
+  select(best_response, gr3_cytopenia_30d) %>% 
+  tbl_summary(by =`gr3_cytopenia_30d`,
+              #type = list(c(MRDneg_90days) ~ "categorical"),
+              label = list(best_response ~ "best response in the first 90 days"),
+              digits = all_continuous() ~ 1,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
+
+# tbl8 <- cart1 %>% 
+#   distinct(MRN, .keep_all = TRUE) %>% 
+#   filter(is.na(Not_evaluable_at_30days)) %>% 
+#   filter(best_response == "CR or sCR") %>% 
+#   select(MRDneg_in_best_response, gr3_cytopenia_30d) %>% 
+#   tbl_summary(by =`gr3_cytopenia_30d`,
+#               type = list(c(MRDneg_in_best_response) ~ "categorical"),
+#               label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
+#               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>% 
+#   bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl_stack(list(tbl1, tbl2, tbl3, tbl5, tbl7))
+```
 
 ## Table S4. Details of infections after ide-cel
+Jenn
 
 ## Table S5. Patients with infections in the first 30 days by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(CRS_gradecat, ICANS_gradecat,
+         `Steroid use (Yes=1, No=0)`, 
+         `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`,
+         `Bridging Therapy (Yes=1, No=0)`, any_infection) %>% 
+  tbl_summary(by=any_infection, 
+              type = list(all_dichotomous() ~ "categorical")) %>%
+  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any infection**")
+
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(CRS_gradecat, ICANS_gradecat,
+         `Steroid use (Yes=1, No=0)`, 
+         `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`,
+         `Bridging Therapy (Yes=1, No=0)`, any_sevinfection) %>% 
+  tbl_summary(by=any_sevinfection, 
+              type = list(all_dichotomous() ~ "categorical")) %>%
+  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
+```
 
 ## Table S6. Patients with infections in the first 100 days by cell counts and immunoglobulin levels
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`IgG day -5`, `IgA day -5`, `IgM day -5`,
+         `WBC day -5 (k/ul)`, `ANC day -5 (k/ul)`,
+         `Eos day -5 (k/ul)`, `Monos day -5 (k/ul)`,
+         `CD3 apheresis`, `CD4 apheresis`, `CD8 apheresis`,
+         `CD56 apheresis`, `CD19 apheresis`, 
+         `CD3 day +90`, `CD4 day +90`, `CD8 day +90`,
+         `CD56 day +90`, `CD19 day +90`,
+         any_infection) %>%
+
+  tbl_summary(by = any_infection,
+
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1) %>% 
+  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any infection**")
+
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`IgG day -5`, `IgA day -5`, `IgM day -5`,
+         `WBC apheresis`, `ANC apheresis`,
+         `Eos apheresis`, `Monos apheresis`,
+         `CD3 apheresis`, `CD4 apheresis`, `CD8 apheresis`,
+         `CD56 apheresis`, `CD19 apheresis`, 
+         `CD3 day +90`, `CD4 day +90`, `CD8 day +90`,
+         `CD56 day +90`, `CD19 day +90`,
+         any_sevinfection) %>%
+
+  tbl_summary(by = any_sevinfection,
+
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1) %>% 
+  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
+```
 
@@
 ## Figure 2. Inflammatory markers after ide-cel
+```{r}
+LDH <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`LDH at Pre-Leukapheresis`, `LDH day -5`, `LDH day 0`, 
+         `LDH day +7`, `LDH day +14`, `LDH day +21`, `LDH day +30`)
+LDH_long <- gather(LDH, day, LDH_value, `LDH at Pre-Leukapheresis`:`LDH day +30`)
+LDH_long$day[LDH_long$day=="LDH at Pre-Leukapheresis"] <- "Pre"
+LDH_long$day[LDH_long$day=="LDH day -5"] <- "Day -5"
+LDH_long$day[LDH_long$day=="LDH day 0"] <- "Day 0"
+LDH_long$day[LDH_long$day=="LDH day +7"] <- "Day 7"
+LDH_long$day[LDH_long$day=="LDH day +14"] <- "Day 14"
+LDH_long$day[LDH_long$day=="LDH day +21"] <- "Day 21"
+LDH_long$day[LDH_long$day=="LDH day +30"] <- "Day 30"
+LDH_long$day <- factor(LDH_long$day, levels = c("Pre", "Day -5", "Day 0", 
+                                                "Day 7", "Day 14", "Day 21", "Day 30"))
+ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
+  geom_boxplot() + xlab("Days") + ylab("LDH") + 
+  theme_classic() + ggtitle("LDH") + 
+  expand_limits(y = c(0, 7000)) + 
+  scale_y_break(c(1188, 4000), 
+                ticklabels=c(4000, 7000), scales=0.10)
+
+# cart1$`Ferritin day +7`[cart1$`Ferritin day +7`==">33511"] <- 33511
+# cart1$`Ferritin day +7` <- as.numeric(cart1$`Ferritin day +7`)
+Ferritin <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(MRN, `Ferritin at Pre-Leukapheresis`, `Ferritin day -5`,
+         `Ferritin day 0`, `Ferritin day +7`, `Ferritin day +14`, 
+         `Ferritin day +21`, `Ferritin day +30`)
+Ferritin_long <- gather(Ferritin, day, Ferritin_value, `Ferritin at Pre-Leukapheresis`:`Ferritin day +30`)
+Ferritin_long$day[Ferritin_long$day=="Ferritin at Pre-Leukapheresis"] <- "Pre"
+Ferritin_long$day[Ferritin_long$day=="Ferritin day -5"] <- "Day -5"
+Ferritin_long$day[Ferritin_long$day=="Ferritin day 0"] <- "Day 0"
+Ferritin_long$day[Ferritin_long$day=="Ferritin day +7"] <- "Day 7"
+Ferritin_long$day[Ferritin_long$day=="Ferritin day +14"] <- "Day 14"
+Ferritin_long$day[Ferritin_long$day=="Ferritin day +21"] <- "Day 21"
+Ferritin_long$day[Ferritin_long$day=="Ferritin day +30"] <- "Day 30"
+Ferritin_long$day <- factor(Ferritin_long$day, levels = c("Pre", "Day -5", "Day 0",
+                                                          "Day 7", "Day 14", "Day 21", "Day 30"))
+ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
+  geom_boxplot() + 
+  xlab("Days") + ylab("Ferritin") + 
+  theme_classic() + ggtitle("Ferritin") + 
+  expand_limits(y = c(0, 34000)) +
+  scale_y_break(c(13600, 33000), ticklabels=c(33000, 34000), scales=0.10)
+
+# cart1$`CRP Pre-Leukapheresis`[cart1$`CRP Pre-Leukapheresis`=="<0.03"] <- 0.07
+# cart1$`CRP Pre-Leukapheresis` <- as.numeric(cart1$`CRP Pre-Leukapheresis`)
+# cart1$`CRP day +14`[cart1$`CRP day +14`=="<0.03"] <- 0.07
+# cart1$`CRP day +14` <- as.numeric(cart1$`CRP day +14`)
+# cart1$`CRP day +21`[cart1$`CRP day +21`=="<0.03"] <- 0.07
+# cart1$`CRP day +21` <- as.numeric(cart1$`CRP day +21`)
+# cart1$`CRP day +30`[cart1$`CRP day +30`=="<0.03"] <- 0.07
+# cart1$`CRP day +30` <- as.numeric(cart1$`CRP day +30`)
+CRP <- cart1 %>%
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(`CRP Pre-Leukapheresis`, `CRP day -5`, `CRP day 0`,
+         `CRP day +7`, `CRP day +14`, `CRP day +21`, `CRP day +30`)
+CRP_long <- gather(CRP, day, CRP_value, `CRP Pre-Leukapheresis`:`CRP day +30`)
+CRP_long$day[CRP_long$day=="CRP Pre-Leukapheresis"] <- "Pre"
+CRP_long$day[CRP_long$day=="CRP day -5"] <- "Day -5"
+CRP_long$day[CRP_long$day=="CRP day 0"] <- "Day 0"
+CRP_long$day[CRP_long$day=="CRP day +7"] <- "Day 7"
+CRP_long$day[CRP_long$day=="CRP day +14"] <- "Day 14"
+CRP_long$day[CRP_long$day=="CRP day +21"] <- "Day 21"
+CRP_long$day[CRP_long$day=="CRP day +30"] <- "Day 30"
+CRP_long$day <- factor(CRP_long$day, levels = c("Pre", "Day -5", "Day 0", "Day 7", "Day 14", "Day 21", "Day 30"))
+ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+  geom_boxplot() + 
+  xlab("Days") + ylab("CRP") + 
+  theme_classic() + ggtitle("CRP") + 
+  expand_limits(y = c(0, 20)) +
+  scale_y_break(c(4.55, 7.5, 9.5, 18.0), ticklabels=c(8,9,18, 20), 
+                scales=c(0.10)
+                )
+
+# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+#   geom_violin() + 
+#   xlab("Days") + ylab("CRP") + 
+#   theme_classic() + ggtitle("CRP")+
+#   expand_limits(y = c(0, 20)) +
+#   scale_y_break(c(5.9, 18.0), ticklabels=c(18, 20), 
+#                 scales=c(0.25)
+#                 )
+# 
+# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+#   geom_violin() + 
+#   xlab("Days") + ylab("CRP") + 
+#   theme_classic() + ggtitle("log10 CRP") + 
+#   expand_limits(y = c(0, 100)) +
+#   scale_y_log10()
+# 
+# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+#   geom_violin() + 
+#   xlab("Days") + ylab("log2 CRP") + 
+#   theme_classic() + ggtitle("CRP") + 
+#   # expand_limits(y = c(0, 100)) +
+#   scale_y_continuous(trans = "log2")
+
+ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
+  geom_boxplot() + 
+  xlab("Days") + ylab("LDH represented with a log2 scale") + 
+  theme_classic() + ggtitle("LDH") + 
+  scale_y_continuous(trans = "log2") +
+  stat_compare_means(label.x = 5 
+                     # aes(label = paste0("p = ", ..p.format..))
+  #                  aes(
+  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
+  )
+
+ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
+  geom_boxplot() + 
+  xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
+  theme_classic() + ggtitle("Ferritin") + 
+  scale_y_continuous(trans = "log2") +
+  stat_compare_means(label.x = 5)
+
+ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+  geom_boxplot() + 
+  xlab("Days") + ylab("CRP represented with a log2 scale") + 
+  theme_classic() + ggtitle("CRP") + 
+  scale_y_continuous(trans = "log2") +
+  stat_compare_means(label.x = 5)
+
+```
 
 ## Figure 3. Cellular and humoral immune reconstitution after ide-cel
+**I can probably remove the x axis title on the 4 top plots**
+```{r, fig.width=12, fig.height=12}
+cart2 <- cart1 %>% 
+  distinct(MRN, .keep_all = TRUE)
+# WBC
+timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 60, 90)
+WBC_fig <-
+  data.frame(timepoints,
+             t(round(
+               sapply(cart2[, c(
+                 "WBC apheresis",
+                 "WBC day -5 (k/ul)",
+                 "WBC day 0 (k/uL)",
+                 "WBC day +7",
+                 "WBC day +14",
+                 "WBC day +21",
+                 "WBC day +30",
+                 "WBC day +60",
+                 "WBC day +90"
+               )],
+               MedianCI,
+               conf.level = 0.95,
+               na.rm = TRUE), 9
+             )))
+WBC_fig <- WBC_fig %>%
+  ggplot(aes(x = timepoints, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median WBC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  ) + ylim(0, 6)
+
+# ANC
+ANC_fig <-
+  data.frame(timepoints, t(round(
+    sapply(cart2[, c(
+      "ANC apheresis",
+      "ANC day -5 (k/ul)",
+      "ANC day 0 (k/uL)",
+      "ANC day +7",
+      "ANC day +14",
+      "ANC day +21",
+      "ANC day +30",
+      "ANC day +60",
+      "ANC day +90"
+    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+  )))
+ANC_fig <- ANC_fig %>% 
+  ggplot(aes(x = timepoints, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median ANC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  ) + 
+  ylim(0, 4)
+
+Hb_fig <-
+  data.frame(timepoints, t(round(
+    sapply(cart2[, c(
+      "Hb apheresis",
+      "Hb day -5 (k/ul)",
+      "Hb day 0 (k/uL)",
+      "Hb day +7",
+      "Hb day +14",
+      "Hb day +21",
+      "Hb day +30",
+      "Hb day +60",
+      "Hb day +90"
+    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+  )))
+Hb_fig <- Hb_fig %>% 
+  ggplot(aes(x = timepoints, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median Hb") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  ) + 
+  ylim(7.5, 12)
+
+# ALC
+ALC_fig <-
+  data.frame(timepoints, t(round(
+    sapply(cart2[, c(
+      "ALC apheresis",
+      "ALC day -5 (k/ul)",
+      "ALC day 0 (k/uL)",
+      "ALC day +7",
+      "ALC day +14",
+      "ALC day +21",
+      "ALC day +30",
+      "ALC day +60",
+      "ALC day +90"
+    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+  )))
+ALC_fig <- ALC_fig %>% 
+  ggplot(aes(x = timepoints, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median ALC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  ) + 
+  ylim(0, 1.1)
+
+# Plt
+Plt_fig <-
+  data.frame(timepoints, t(round(
+    sapply(cart2[, c(
+      "Plt apheresis",
+      "Plt day -5 (k/ul)",
+      "Plt day 0 (k/uL)",
+      "Plt day +7",
+      "Plt day +14",
+      "Plt day +21",
+      "Plt day +30",
+      "Plt day +60",
+      "Plt day +90"
+    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+  )))
+Plt_fig <- Plt_fig %>% 
+  ggplot(aes(x = timepoints, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median Plt") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  ) +
+  ylim(20, 170)
+
+# IgG
+#table(cart2$`IgG day +90`)
+#table(cart2$`IgG day +180`)
+# cart2$`IgG day +90`[cart2$`IgG day +90` == "<109"] <- 77
+# cart2$`IgG day +30`[cart2$`IgG day +30` == "<109"] <- 77
+# cart2$`IgG day -5`[cart2$`IgG day -5` == "<109"] <- 77
+# cart2$`IgG apheresis`[cart2$`IgG apheresis` == "<109"] <- 77
+# 
+# cart2$`IgG day +90` <- as.numeric(cart2$`IgG day +90`)
+# cart2$`IgG day +30` <- as.numeric(cart2$`IgG day +30`)
+# cart2$`IgG day -5` <- as.numeric(cart2$`IgG day -5`)
+# cart2$`IgG apheresis` <- as.numeric(cart2$`IgG apheresis`)
+timepoints2 <- c(-28, -5, 30, 90)
+IgG_fig <-
+  data.frame(timepoints2, t(round(
+    sapply(cart2[, c(
+      "IgG apheresis", 
+      "IgG day -5",
+      # "IgG day 0 (k/uL)", 
+      "IgG day +30", 
+      "IgG day +90")], MedianCI, conf.level =
+             0.95, na.rm = TRUE), 9
+  )))
+IgG_fig <- IgG_fig %>% 
+  ggplot(aes(x = timepoints2, y = median)) + 
+  geom_line(col = "blue") +
+  xlab("Days relative to infusion") + 
+  ylab("Median IgG") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 30, 90),
+    labels = c("Apheresis", "-5", "0", "30", "90"))# + 
+  # ylim(0, 2000)
+
+(WBC_fig | ANC_fig) /
+  (Hb_fig | ALC_fig) /
+  (Plt_fig | IgG_fig) +
+  plot_annotation(tag_levels = "A")
+```
+
+<!-- <span style="color:blue">**IgG I need to fix the other 109**</span>  -->
+
+<!-- Values less than the limit of detection (<109) were considered to be 77 which is the lower limit of detection divided by the square root of 2.
+One patient had an IgG day 0 value of <320.
+As this is above the limit of detection, I used the midway point between 320 and the lower limit of detection -- 214 -- as the value instead of <320.
+-->
+
+<br>
 
@@
 As discussed at meeting, rather than showing count recovery over time plan to show Grade 3+ cytopenias (Hb, Plt, ANC, WBC) over time (Day –5, Day +30, Day +60, Day +90)
+**We want grade 3 only right?**
+```{r}
+cart2 %>% 
+  select(PT,
+         `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
+         `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
+         `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
+         `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
+  ) %>% 
+  pivot_longer(cols = `gr3_Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
+  group_by(name, value) %>% 
+  filter(!is.na(value)) %>% 
+  summarise(count=n()) %>% 
+  mutate(perc=(count/sum(count)*100)
+  ) %>% 
+  separate("name", into = c("gr3", "name", "day"), sep = "_") %>% 
+  filter(value == "YES") %>% 
+  # unite(time, c("day":"me"), sep = " ") %>% 
+  ggplot(aes(x= day, y= perc, fill= name))+
+  geom_bar(stat = "identity",
+           position=position_dodge(width=0.9))+
+  scale_fill_viridis_d() +
+  labs(fill = NULL, y = "%", title = "Grade 3+")+
+  theme_classic()
+
+cart2 %>% 
+  select(PT,
+         `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
+         `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
+         `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
+         `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
+
+         `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
+         `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
+         `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
+         `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
+  ) %>% 
+  pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
+  mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
+         grade = case_when(
+           grade == "gr3_"       ~ "Grade 3+",
+           TRUE                  ~ "Any grade"
+         )) %>% 
+  mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
+         name2 = coalesce(name1, name)) %>% 
+  group_by(name2, value, grade) %>% 
+  filter(!is.na(value)) %>% 
+  summarise(count=n()) %>% 
+  mutate(perc=(count/sum(count)*100)
+  ) %>% 
+  separate("name2", into = c("name", "day"), sep = "_") %>% 
+  filter(value == "YES") %>% 
+  # unite(time, c("day":"me"), sep = " ") %>% 
+  ggplot(aes(x= day, y= perc, fill= name, alpha= grade))+
+  geom_bar(stat = "identity",
+           position=position_dodge(width=0.9))+
+  scale_fill_viridis_d() + 
+  scale_alpha_ordinal(range = c(0.5, 1))+
+  labs(fill = NULL, y = "%")+
+  theme_classic()
+
+cart2 %>% 
+  select(PT,
+         `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
+         `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
+         `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
+         `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
+
+         `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
+         `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
+         `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
+         `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
+  ) %>% 
+  pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
+  mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
+         grade = case_when(
+           grade == "gr3_"       ~ "Grade 3+",
+           TRUE                  ~ "Any grade"
+         )) %>% 
+  mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
+         name2 = coalesce(name1, name)) %>% 
+  group_by(name2, value, grade) %>% 
+  filter(!is.na(value)) %>% 
+  summarise(count=n()) %>% 
+  mutate(perc=(count/sum(count)*100)
+  ) %>% 
+  separate("name2", into = c("name", "day"), sep = "_") %>% 
+  filter(value == "YES") %>% 
+  # unite(time, c("day":"me"), sep = " ") %>% 
+  ggplot(aes(x= name, y= perc, fill= name, alpha= grade))+
+  geom_bar(stat = "identity", position = "stack")+
+  facet_grid(day ~ .,)+
+  scale_fill_viridis_d() + 
+  scale_alpha_ordinal(range = c(0.4, 1))+
+  labs(fill = NULL, x= NULL, y = "%")+
+  theme_classic()+
+  coord_flip()
+```
 
 ## Figure 5. Cumulative incidence of infection and infection density
+Lauren
+```{r}
+# library(cmprsk)
+# 
+# table(cart$`Latest Day of CRS (relateive to infusion)`)
+# # cart$CRS_fup2 <- cart$CRS_fup
+# # cart$CRS_fup2[cart$CRS_fup2==30] <- NA
+# # table(cart$CRS_fup2)
+# # 
+# # cart1$CRS_fup[cart1$CRS_fup==30] <- 7
+# CRS <- 
+#  cuminc(
+#     ftime = cart1$`Latest Day of CRS (relateive to infusion)`, 
+#     fstatus = cart1$CRS_any2, 
+#     group = cart1$`Infection type`)
+# ggcompetingrisks(CRS, multiple_panels = FALSE) + 
+#   scale_linetype_manual(name="Infection type", values=1:2,#labels=c("High","Low")
+#   )+
+#   guides(col="none")
+
+```
 
@@
                         ≥1.10=positive (immune)
+```{r}
+cart2 %>% 
+  select(PT, 
+         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`
+
+  ) %>% 
+  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
+  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+  unite(time, c("na":"me"), sep = " ") %>% 
+  # mutate(value = as.numeric(value)) %>% 
+  mutate(day = case_when(
+    day == "D90"        ~ 90,
+    day == "apheresis"  ~ 0
+  )) %>% 
+  ggplot(aes(x= day, y= value, color= PT))+
+  geom_point()+
+  geom_line()+
+  scale_x_continuous(
+    breaks = c(0, 90),
+    labels = c("Apheresis", "D90"))+
+  scale_color_viridis_d() +
+  labs(fill = "Patients", x = NULL)+
+  theme_classic()
+
+cart2 %>% 
+  select(PT, 
+         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
+  mutate(`IgG HSV1/2 apheresis` = case_when(
+    `IgG HSV1/2 apheresis` < 0.9         ~ "negative",
+    `IgG HSV1/2 apheresis` >= 0.9 &
+      `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
+    `IgG HSV1/2 apheresis` >= 1.10       ~ "positive",
+  )) %>%
+  mutate(`IgG HSV1/2 D90` = case_when(
+    `IgG HSV1/2 D90` < 0.9         ~ "negative",
+    `IgG HSV1/2 D90` >= 0.9 &
+      `IgG HSV1/2 D90` < 1.10      ~ "indeterminate",
+    `IgG HSV1/2 D90` >= 1.10       ~ "positive",
+  )) %>% 
+  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
+  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+  unite(name, c("na":"me"), sep = " ") %>% 
+  ggplot(aes(x= day,  fill= value))+
+  geom_bar()
+
+cart2 %>% 
+  select(PT, 
+         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
+  mutate(`IgG HSV1/2 apheresis` = case_when(
+    `IgG HSV1/2 apheresis` < 0.9         ~ "negative",
+    `IgG HSV1/2 apheresis` >= 0.9 &
+      `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
+    `IgG HSV1/2 apheresis` >= 1.10       ~ "positive",
+  )) %>%
+  mutate(`IgG HSV1/2 D90` = case_when(
+    `IgG HSV1/2 D90` < 0.9         ~ "negative",
+    `IgG HSV1/2 D90` >= 0.9 &
+      `IgG HSV1/2 D90` < 1.10      ~ "indeterminate",
+    `IgG HSV1/2 D90` >= 1.10       ~ "positive",
+  )) %>% 
+  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
+  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+  unite(name, c("na":"me"), sep = " ") %>% 
+  filter(!is.na(value)) %>% 
+  group_by(name, day, value) %>% 
+  summarise(count=n()) %>% 
+  mutate(perc=(count/sum(count)*100)
+  ) %>% 
+  ggplot(aes(x= day, y= perc, fill= value))+
+  geom_bar(stat = "identity")
+
+cart2 %>% 
+  select(PT, 
+         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
+  mutate(`IgG HSV1/2 apheresis` = case_when(
+    `IgG HSV1/2 apheresis` < 0.9         ~ "negative",
+    `IgG HSV1/2 apheresis` >= 0.9 &
+      `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
+    `IgG HSV1/2 apheresis` >= 1.10       ~ "positive",
+  )) %>%
+  mutate(`IgG HSV1/2 D90` = case_when(
+    `IgG HSV1/2 D90` < 0.9         ~ "negative",
+    `IgG HSV1/2 D90` >= 0.9 &
+      `IgG HSV1/2 D90` < 1.10      ~ "indeterminate",
+    `IgG HSV1/2 D90` >= 1.10       ~ "positive",
+  )) %>% 
+  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
+  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+  unite(name, c("na":"me"), sep = " ") %>% 
+  filter(!is.na(value)) %>% 
+  group_by(name, day, value) %>% 
+  summarise(count=n()) %>%
+
+  ggplot(aes(x= day, y= count, fill= value))+
+  geom_bar(stat = "identity",
+           position=position_dodge(width=0.9))
+
+```
 
 B)	VZV IgG (positive=immune vs negative or equivocal=not immune)
+```{r, fig.width=5, fig.height=6}
+# cart2 %>% 
+#   mutate(`VZV IgG apheresis` = case_when(
+#     `VZV IgG apheresis` == "0"         ~ "negative",
+#     `VZV IgG apheresis` == "1"         ~ "immune",
+#     TRUE                          ~ `VZV IgG apheresis`
+#   )) %>% 
+#   mutate(`VZV IgG D90 (1=pos, 0=neg)` = case_when(
+#     `VZV IgG D90 (1=pos, 0=neg)` == "0"         ~ "negative",
+#     `VZV IgG D90 (1=pos, 0=neg)` == "1"         ~ "immune",
+#     TRUE                          ~ `VZV IgG D90 (1=pos, 0=neg)`
+#   )) %>% 
+#   select(PT, 
+#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
+#   ) %>% 
+#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(time, c("na":"me"), sep = " ") %>% 
+#   # mutate(value = as.numeric(value)) %>% 
+#   mutate(day = case_when(
+#     day == "D90"        ~ 90,
+#     day == "apheresis"  ~ 0
+#   )) %>% 
+#   ggplot(aes(x= day, y= value, color= PT))+
+#   geom_point(position=position_dodge(width=0.9))+
+#   scale_x_continuous(
+#     breaks = c(0, 90),
+#     labels = c("Apheresis", "D90"))+
+#   scale_color_viridis_d() +
+#   labs(fill = "Patients", x = NULL)+
+#   theme_classic()
+
+cart2 %>% 
+  mutate(`VZV IgG apheresis` = case_when(
+    `VZV IgG apheresis` == "0"         ~ "negative",
+    `VZV IgG apheresis` == "1"         ~ "immune",
+    TRUE                          ~ `VZV IgG apheresis`
+  )) %>% 
+  mutate(`VZV IgG D90 (1=pos, 0=neg)` = case_when(
+    `VZV IgG D90 (1=pos, 0=neg)` == "0"         ~ "negative",
+    `VZV IgG D90 (1=pos, 0=neg)` == "1"         ~ "immune",
+    TRUE                          ~ `VZV IgG D90 (1=pos, 0=neg)`
+  )) %>% 
+  select(PT, 
+         `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
+  ) %>% 
+  pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
+  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+  unite(time, c("na":"me"), sep = " ") %>% 
+  filter(!is.na(value)) %>% 
+  arrange(value) %>% 
+  ggplot(aes(x= day, y= fct_reorder2(PT, value, day), fill= value))+
+  geom_tile(color = "white")+
+  labs(fill = NULL, x = NULL, y= NULL)+
+  theme_classic()
+```
+
+```{r}
+cart2 %>% 
+  mutate(`VZV IgG apheresis` = case_when(
+    `VZV IgG apheresis` == "0"         ~ "negative",
+    `VZV IgG apheresis` == "1"         ~ "immune",
+    TRUE                          ~ `VZV IgG apheresis`
+  )) %>% 
+  mutate(`VZV IgG D90 (1=pos, 0=neg)` = case_when(
+    `VZV IgG D90 (1=pos, 0=neg)` == "0"         ~ "negative",
+    `VZV IgG D90 (1=pos, 0=neg)` == "1"         ~ "immune",
+    TRUE                          ~ `VZV IgG D90 (1=pos, 0=neg)`
+  )) %>% 
+  select(PT, 
+         `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
+  ) %>% 
+  pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
+  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+  unite(name, c("na":"me"), sep = " ") %>% 
+  filter(!is.na(value)) %>% 
+  group_by(name, day, value) %>% 
+  summarise(count=n()) %>%
+
+  ggplot(aes(x= day, y= count, fill= value))+
+  geom_bar(stat = "identity",
+           position=position_dodge(width=0.9))
+```
 
 C)	CMV IgG (positive=immune vs negative=not immune)
+```{r}
+cart2 %>% 
+  mutate(`CMV IgG apheresis` = case_when(
+    `CMV IgG apheresis` == "0"         ~ "negative",
+    `CMV IgG apheresis` == "1"         ~ "immune"
+  )) %>% 
+  mutate(`CMV IgG D90 (1=pos, 0=neg)` = case_when(
+    `CMV IgG D90 (1=pos, 0=neg)` == "0"         ~ "negative",
+    `CMV IgG D90 (1=pos, 0=neg)` == "1"         ~ "immune"
+  )) %>% 
+  select(PT, 
+         `CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`
+  ) %>% 
+  pivot_longer(cols = `CMV IgG apheresis` : `CMV IgG D90 (1=pos, 0=neg)`) %>% 
+  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+  unite(time, c("na":"me"), sep = " ") %>% 
+  # mutate(value = as.numeric(value)) %>% 
+  mutate(day = case_when(
+    day == "D90"        ~ 90,
+    day == "apheresis"  ~ 0
+  )) %>% 
+  ggplot(aes(x= day, y= value, color= PT))+
+  geom_point(position=position_dodge(width=0.9))+
+  scale_x_continuous(
+    breaks = c(0, 90),
+    labels = c("Apheresis", "D90"))+
+  scale_color_viridis_d() +
+  labs(fill = "Patients", x = NULL)+
+  theme_classic()
+```
 
@@
 If antibody concentration ≤1.0 consider negative (not immune)
+```{r, fig.width=12, fig.height=12}
+cart2 %>% 
+  select(PT, 
+         starts_with("Pneumo")
+
+  ) %>% 
+  pivot_longer(cols = -PT) %>% 
+  filter(!is.na(value)) %>% 
+  mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
+  mutate(name = str_remove(name, " apheresis| D90")) %>%
+
+  mutate(value = case_when(
+    value <= 1           ~ "negative",
+    value > 1            ~ "immune"
+  )) %>% 
+  group_by(name, day, value) %>% 
+  summarise(count=n()) %>% 
+  mutate(perc=(count/sum(count)*100)
+  ) %>%
+
+  ggplot(aes(x= day, y= perc, fill= value))+
+  geom_bar(stat = "identity",
+           position=position_dodge2(width=0.9, preserve = "single"))+
+  facet_wrap(.~ name)
+
+```

### 2022-03-31 Manuscript analyses.Rmd
modify and prepare plot panels

@@
     TRUE                             ~ NA_character_
+  )) %>%
+
+  mutate(`IgG HSV1/2 apheresis` = case_when(
+    `IgG HSV1/2 apheresis` < 0.9         ~ "Negative",
+    `IgG HSV1/2 apheresis` >= 0.9 &
+      `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
+    `IgG HSV1/2 apheresis` >= 1.10       ~ "Positive",
+  )) %>%
+  mutate(`IgG HSV1/2 D90` = case_when(
+    `IgG HSV1/2 D90` < 0.9         ~ "Negative",
+    `IgG HSV1/2 D90` >= 0.9 &
+      `IgG HSV1/2 D90` < 1.10      ~ "indeterminate",
+    `IgG HSV1/2 D90` >= 1.10       ~ "Positive",
+  )) %>% 
+  mutate_at(c("VZV IgG apheresis",
+              "VZV IgG D90 (1=pos, 0=neg)",
+              "CMV IgG apheresis",
+              "CMV IgG D90 (1=pos, 0=neg)"), 
+            ~ case_when(
+              . == 1                                              ~ "Positive",
+              . == 0                                              ~ "Negative",
+              . == "Equivocal"                                    ~ "Negative",
+              TRUE                                                ~ as.character(.)
+            )) %>% 
+  mutate_at(c("IgG HSV1/2 apheresis",
+              "IgG HSV1/2 D90",
+              "VZV IgG apheresis",
+              "VZV IgG D90 (1=pos, 0=neg)",
+              "CMV IgG apheresis",
+              "CMV IgG D90 (1=pos, 0=neg)"),
+            ~ factor(., levels = c("Positive", "Negative"))) %>% 
+  mutate(across(starts_with("Pneumo"), ~ case_when(
+    . <= 1                                                    ~ "Negative",
+    . > 1                                                     ~ "Positive"
+  ))) %>%
+
+  mutate(igg_hsv_change = case_when(
+    `IgG HSV1/2 apheresis` == "Positive" &
+      `IgG HSV1/2 D90` == "Negative"         ~ -1,
+    `IgG HSV1/2 apheresis` == "Negative" &
+      `IgG HSV1/2 D90` == "Positive"         ~ 1,
+    `IgG HSV1/2 apheresis` == "Negative" &
+      `IgG HSV1/2 D90` == "Negative"         ~ -0.25,
+    `IgG HSV1/2 apheresis` == "Positive" &
+      `IgG HSV1/2 D90` == "Positive"         ~ 0.25
+  )) %>% 
+  mutate(igg_vzv_change = case_when(
+    `VZV IgG apheresis` == "Positive" &
+      `VZV IgG D90 (1=pos, 0=neg)` == "Negative"               ~ -1,
+    `VZV IgG apheresis` == "Negative" &
+      `VZV IgG D90 (1=pos, 0=neg)` == "Positive"               ~ 1,
+    `VZV IgG apheresis` == "Negative" &
+      `VZV IgG D90 (1=pos, 0=neg)` == "Negative"               ~ -0.25,
+    `VZV IgG apheresis` == "Positive" &
+      `VZV IgG D90 (1=pos, 0=neg)` == "Positive"               ~ 0.25
+  )) %>% 
+  mutate(igg_cmv_change = case_when(
+    `CMV IgG apheresis` == "Positive" &
+      `CMV IgG D90 (1=pos, 0=neg)` == "Negative"               ~ -1,
+    `CMV IgG apheresis` == "Negative" &
+      `CMV IgG D90 (1=pos, 0=neg)` == "Positive"               ~ 1,
+    `CMV IgG apheresis` == "Negative" &
+      `CMV IgG D90 (1=pos, 0=neg)` == "Negative"               ~ -0.25,
+    `CMV IgG apheresis` == "Positive" &
+      `CMV IgG D90 (1=pos, 0=neg)` == "Positive"               ~ 0.25
   ))
+
+# Create Pneumo titers change value
+for (i in colnames(cart1 %>%
+                   select(c(starts_with("Pneumo"))))) {
+
+  pneumo_type <-
+    str_match(i, ".*(apheresis|D90)")[, 1] %>% 
+    # str_replace_all(., " ", "_") %>% 
+    str_remove(., " apheresis| D90")
+
+  pneumo_subset <- cart1 %>% select(PT, starts_with(pneumo_type))
+
+  pneumo_type <-
+    str_replace_all(pneumo_type, " ", "_")
+  # day <-
+  #   str_match(i, ".*(apheresis|D90)")[, 2]
+
+  name <- paste0(pneumo_type, "_", "change")
+
+  cart1[[paste0(pneumo_type, "_", "change")]] <-  case_when(
+    pneumo_subset[2] == "Positive" &
+      pneumo_subset[3] == "Negative"               ~ -1,
+    pneumo_subset[2] == "Negative" &
+      pneumo_subset[3] == "Positive"               ~ 1,
+    pneumo_subset[2] == "Negative" &
+      pneumo_subset[3] == "Negative"               ~ -0.25,
+    pneumo_subset[2] == "Positive" &
+      pneumo_subset[3] == "Positive"               ~ 0.25
+  )
+}
 
@@
 #                         tct$day30_response_revised== "PR" ~ "PR",
-                         #tct$day30_response_revised== "PR" & tct$MRD_status== "Positive" ~ "PR and MRD-positive",
+                         #tct$day30_response_revised== "PR" & tct$MRD_status== "Positive" ~ "PR and MRD-Positive",
                          #tct$day30_response_revised== "PR" & is.na(tct$MRD_status) ~ "PR and MRD unknown",
-#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Negative" ~ "sCR and MRD-negative",
-#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Positive" ~ "sCR and MRD-positive")
+#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Negative" ~ "sCR and MRD-Negative",
+#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Positive" ~ "sCR and MRD-Positive")
 #table(tct$ORR_MRD)
@@
 ## Figure 2. Inflammatory markers after ide-cel
-```{r}
+```{r, fig.height=12}
 LDH <- cart1 %>% 
@@
                                                 "Day 7", "Day 14", "Day 21", "Day 30"))
-ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
-  geom_boxplot() + xlab("Days") + ylab("LDH") + 
-  theme_classic() + ggtitle("LDH") + 
-  expand_limits(y = c(0, 7000)) + 
-  scale_y_break(c(1188, 4000), 
-                ticklabels=c(4000, 7000), scales=0.10)
+# ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
+#   geom_boxplot() + xlab("Days") + ylab("LDH") + 
+#   geom_jitter(color= "grey")+
+#   theme_classic() + ggtitle("LDH") + 
+#   expand_limits(y = c(0, 7000)) + 
+#   scale_y_break(c(1188, 4000), 
+#                 ticklabels=c(4000, 7000), scales=0.10)
 
@@
                                                           "Day 7", "Day 14", "Day 21", "Day 30"))
-ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
-  geom_boxplot() + 
-  xlab("Days") + ylab("Ferritin") + 
-  theme_classic() + ggtitle("Ferritin") + 
-  expand_limits(y = c(0, 34000)) +
-  scale_y_break(c(13600, 33000), ticklabels=c(33000, 34000), scales=0.10)
+# ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
+#   geom_boxplot() + 
+#   xlab("Days") + ylab("Ferritin") + 
+#   theme_classic() + ggtitle("Ferritin") + 
+#   expand_limits(y = c(0, 34000)) +
+#   scale_y_break(c(13600, 33000), ticklabels=c(33000, 34000), scales=0.10)
 
@@
 CRP_long$day <- factor(CRP_long$day, levels = c("Pre", "Day -5", "Day 0", "Day 7", "Day 14", "Day 21", "Day 30"))
-ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-  geom_boxplot() + 
-  xlab("Days") + ylab("CRP") + 
-  theme_classic() + ggtitle("CRP") + 
-  expand_limits(y = c(0, 20)) +
-  scale_y_break(c(4.55, 7.5, 9.5, 18.0), ticklabels=c(8,9,18, 20), 
-                scales=c(0.10)
-                )
+# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+#   geom_boxplot() + 
+#   xlab("Days") + ylab("CRP") + 
+#   theme_classic() + ggtitle("CRP") + 
+#   expand_limits(y = c(0, 20)) +
+#   scale_y_break(c(4.55, 7.5, 9.5, 18.0), ticklabels=c(8,9,18, 20), 
+#                 scales=c(0.10)
+#                 )
 
@@
 
-ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
+#   geom_jitter(color= "grey")+
+
+a <- ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
   geom_boxplot() + 
@@
 
-ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
+b <- ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
   geom_boxplot() + 
@@
 
-ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+c <- ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
   geom_boxplot() + 
@@
 
+(a) /
+(b) /
+(c)+
+plot_annotation(tag_levels = "A")
+
+a <- ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
+  geom_boxplot() + 
+  geom_jitter(color= "grey")+
+  xlab("Days") + ylab("LDH represented with a log2 scale") + 
+  theme_classic() + ggtitle("LDH") + 
+  scale_y_continuous(trans = "log2") +
+  stat_compare_means(label.x = 5 
+                     # aes(label = paste0("p = ", ..p.format..))
+  #                  aes(
+  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
+  )
+
+b <- ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
+  geom_boxplot() + 
+  geom_jitter(color= "grey")+
+  xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
+  theme_classic() + ggtitle("Ferritin") + 
+  scale_y_continuous(trans = "log2") +
+  stat_compare_means(label.x = 5)
+
+c <- ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+  geom_boxplot() + 
+  geom_jitter(color= "grey")+
+  xlab("Days") + ylab("CRP represented with a log2 scale") + 
+  theme_classic() + ggtitle("CRP") + 
+  scale_y_continuous(trans = "log2") +
+  stat_compare_means(label.x = 5)
+
+(a) /
+(b) /
+(c) +
+plot_annotation(tag_levels = "A")
 ```
@@
 ```{r}
-cart2 %>% 
-  select(PT,
-         `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
-         `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
-         `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
-         `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
-  ) %>% 
-  pivot_longer(cols = `gr3_Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
-  group_by(name, value) %>% 
-  filter(!is.na(value)) %>% 
-  summarise(count=n()) %>% 
-  mutate(perc=(count/sum(count)*100)
-  ) %>% 
-  separate("name", into = c("gr3", "name", "day"), sep = "_") %>% 
-  filter(value == "YES") %>% 
-  # unite(time, c("day":"me"), sep = " ") %>% 
-  ggplot(aes(x= day, y= perc, fill= name))+
-  geom_bar(stat = "identity",
-           position=position_dodge(width=0.9))+
-  scale_fill_viridis_d() +
-  labs(fill = NULL, y = "%", title = "Grade 3+")+
-  theme_classic()
-
-cart2 %>% 
+# cart2 %>% 
+#   select(PT,
+#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
+#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
+#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
+#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
+#   ) %>% 
+#   pivot_longer(cols = `gr3_Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
+#   group_by(name, value) %>% 
+#   filter(!is.na(value)) %>% 
+#   summarise(count=n()) %>% 
+#   mutate(perc=(count/sum(count)*100)
+#   ) %>% 
+#   separate("name", into = c("gr3", "name", "day"), sep = "_") %>% 
+#   filter(value == "YES") %>% 
+#   # unite(time, c("day":"me"), sep = " ") %>% 
+#   ggplot(aes(x= day, y= perc, fill= name))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))+
+#   scale_fill_viridis_d() +
+#   labs(fill = NULL, y = "%", title = "Grade 3+")+
+#   theme_classic()
+# 
+# cart2 %>% 
+#   select(PT,
+#          `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
+#          `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
+#          `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
+#          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
+#          
+#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
+#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
+#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
+#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
+#   ) %>% 
+#   pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
+#   mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
+#          grade = case_when(
+#            grade == "gr3_"       ~ "Grade 3+",
+#            TRUE                  ~ "Any grade"
+#          )) %>% 
+#   mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
+#          name2 = coalesce(name1, name)) %>% 
+#   group_by(name2, value, grade) %>% 
+#   filter(!is.na(value)) %>% 
+#   summarise(count=n()) %>%
+#   group_by(name2, grade) %>% 
+#   mutate(perc=(count/sum(count)*100)
+#   ) %>%
+#   separate("name2", into = c("name", "day"), sep = "_") %>% 
+#   filter(value == "YES") %>% 
+#   # unite(time, c("day":"me"), sep = " ") %>% 
+#   ggplot(aes(x= day, y= perc, fill= name, alpha= grade))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))+
+#   scale_fill_viridis_d() + 
+#   scale_alpha_ordinal(range = c(0.5, 1))+
+#   labs(fill = NULL, y = "%")+
+#   theme_classic()
+
+a <- cart2 %>% 
   select(PT,
@@
   summarise(count=n()) %>%
+  group_by(name2, grade) %>% 
   mutate(perc=(count/sum(count)*100)
@@
   separate("name2", into = c("name", "day"), sep = "_") %>% 
-  filter(value == "YES") %>% 
+  ungroup() %>% 
+  filter(value == "YES")
+b <- a %>% filter(grade == "Any grade")
+a %>% filter(grade == "Grade 3+") %>% 
   # unite(time, c("day":"me"), sep = " ") %>% 
-  ggplot(aes(x= day, y= perc, fill= name, alpha= grade))+
+  ggplot(aes(x= day, 
+             y= perc, 
+             fill= name, alpha= 1
+             ))+
   geom_bar(stat = "identity",
            position=position_dodge(width=0.9))+
+  geom_bar(stat = "identity",
+           position=position_dodge(width=0.9), data= b,
+           aes(x= day, y= perc, fill= name), alpha= 0.4)+
+  # facet_grid(name ~ .,)+
   scale_fill_viridis_d() + 
-  scale_alpha_ordinal(range = c(0.5, 1))+
-  labs(fill = NULL, y = "%")+
-  theme_classic()
-
-cart2 %>% 
-  select(PT,
-         `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
-         `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
-         `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
-         `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
-
-         `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
-         `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
-         `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
-         `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
-  ) %>% 
-  pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
-  mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
-         grade = case_when(
-           grade == "gr3_"       ~ "Grade 3+",
-           TRUE                  ~ "Any grade"
-         )) %>% 
-  mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
-         name2 = coalesce(name1, name)) %>% 
-  group_by(name2, value, grade) %>% 
-  filter(!is.na(value)) %>% 
-  summarise(count=n()) %>% 
-  mutate(perc=(count/sum(count)*100)
-  ) %>% 
-  separate("name2", into = c("name", "day"), sep = "_") %>% 
-  filter(value == "YES") %>% 
-  # unite(time, c("day":"me"), sep = " ") %>% 
-  ggplot(aes(x= name, y= perc, fill= name, alpha= grade))+
-  geom_bar(stat = "identity", position = "stack")+
-  facet_grid(day ~ .,)+
-  scale_fill_viridis_d() + 
-  scale_alpha_ordinal(range = c(0.4, 1))+
-  labs(fill = NULL, x= NULL, y = "%")+
+  labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
   theme_classic()+
-  coord_flip()
+  scale_alpha_continuous(limits = c(0.4,1), breaks = c(0.4,1),
+                         labels= c("Any Grade", "Grade 3+"))
 ```
@@
 
-A)	HSV 1/2 IgG
+### A)	HSV 1/2 IgG
 
@@
                         ≥1.10=positive (immune)
+
+```{r, echo=TRUE}
+# mutate(`IgG HSV1/2 apheresis` = case_when(
+#     `IgG HSV1/2 apheresis` < 0.9         ~ "Negative",
+#     `IgG HSV1/2 apheresis` >= 0.9 &
+#       `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
+#     `IgG HSV1/2 apheresis` >= 1.10       ~ "Positive",
+#   ))
+```
+
 ```{r}
-cart2 %>% 
-  select(PT, 
-         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`
-
-  ) %>% 
-  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
-  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-  unite(time, c("na":"me"), sep = " ") %>% 
-  # mutate(value = as.numeric(value)) %>% 
-  mutate(day = case_when(
-    day == "D90"        ~ 90,
-    day == "apheresis"  ~ 0
-  )) %>% 
-  ggplot(aes(x= day, y= value, color= PT))+
-  geom_point()+
-  geom_line()+
-  scale_x_continuous(
-    breaks = c(0, 90),
-    labels = c("Apheresis", "D90"))+
-  scale_color_viridis_d() +
-  labs(fill = "Patients", x = NULL)+
-  theme_classic()
-
+# cart2 %>% 
+#   select(PT, 
+#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>% 
+#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(time, c("na":"me"), sep = " ") %>% 
+#   # mutate(value = as.numeric(value)) %>% 
+#   mutate(day = case_when(
+#     day == "D90"        ~ 90,
+#     day == "apheresis"  ~ 0
+#   )) %>% 
+#   ggplot(aes(x= day, y= value, color= PT))+
+#   geom_point()+
+#   geom_line()+
+#   scale_x_continuous(
+#     breaks = c(0, 90),
+#     labels = c("Apheresis", "D90"))+
+#   scale_color_viridis_d() +
+#   labs(fill = "Patients", x = NULL)+
+#   theme_classic()
+
+# cart2 %>% 
+#   select(PT, 
+#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
+#   
+#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(name, c("na":"me"), sep = " ") %>% 
+#   ggplot(aes(x= day,  fill= value))+
+#   geom_bar()
+
+# Histogram
 cart2 %>% 
@@
          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
-  mutate(`IgG HSV1/2 apheresis` = case_when(
-    `IgG HSV1/2 apheresis` < 0.9         ~ "negative",
-    `IgG HSV1/2 apheresis` >= 0.9 &
-      `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
-    `IgG HSV1/2 apheresis` >= 1.10       ~ "positive",
-  )) %>%
-  mutate(`IgG HSV1/2 D90` = case_when(
-    `IgG HSV1/2 D90` < 0.9         ~ "negative",
-    `IgG HSV1/2 D90` >= 0.9 &
-      `IgG HSV1/2 D90` < 1.10      ~ "indeterminate",
-    `IgG HSV1/2 D90` >= 1.10       ~ "positive",
-  )) %>% 
-  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
-  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-  unite(name, c("na":"me"), sep = " ") %>% 
-  ggplot(aes(x= day,  fill= value))+
-  geom_bar()
-
-cart2 %>% 
-  select(PT, 
-         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
-  mutate(`IgG HSV1/2 apheresis` = case_when(
-    `IgG HSV1/2 apheresis` < 0.9         ~ "negative",
-    `IgG HSV1/2 apheresis` >= 0.9 &
-      `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
-    `IgG HSV1/2 apheresis` >= 1.10       ~ "positive",
-  )) %>%
-  mutate(`IgG HSV1/2 D90` = case_when(
-    `IgG HSV1/2 D90` < 0.9         ~ "negative",
-    `IgG HSV1/2 D90` >= 0.9 &
-      `IgG HSV1/2 D90` < 1.10      ~ "indeterminate",
-    `IgG HSV1/2 D90` >= 1.10       ~ "positive",
-  )) %>% 
   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
@@
   ggplot(aes(x= day, y= perc, fill= value))+
-  geom_bar(stat = "identity")
-
+  geom_bar(stat = "identity")+
+  labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
+       fill= "Immunity")+
+  scale_y_continuous(expand = c(0, 0))+
+  theme_classic()
+
+library(ggpattern)
 cart2 %>% 
@@
          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
-  mutate(`IgG HSV1/2 apheresis` = case_when(
-    `IgG HSV1/2 apheresis` < 0.9         ~ "negative",
-    `IgG HSV1/2 apheresis` >= 0.9 &
-      `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
-    `IgG HSV1/2 apheresis` >= 1.10       ~ "positive",
-  )) %>%
-  mutate(`IgG HSV1/2 D90` = case_when(
-    `IgG HSV1/2 D90` < 0.9         ~ "negative",
-    `IgG HSV1/2 D90` >= 0.9 &
-      `IgG HSV1/2 D90` < 1.10      ~ "indeterminate",
-    `IgG HSV1/2 D90` >= 1.10       ~ "positive",
-  )) %>% 
   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
@@
   summarise(count=n()) %>% 
-
-  ggplot(aes(x= day, y= count, fill= value))+
-  geom_bar(stat = "identity",
-           position=position_dodge(width=0.9))
-
-```
-
-B)	VZV IgG (positive=immune vs negative or equivocal=not immune)
+  mutate(perc=(count/sum(count)*100)
+  ) %>% 
+  ggplot(aes(x= day, y= perc))+
+  geom_bar_pattern(aes(pattern = value),
+                   stat = "identity",
+    fill            = 'white', 
+    colour          = 'black')+
+  # geom_bar(stat = "identity")+
+  labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
+       fill= "Immunity")+
+  scale_y_continuous(expand = c(0, 0))+
+  theme_classic()
+
+# cart2 %>% 
+#   select(PT, 
+#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
+#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(name, c("na":"me"), sep = " ") %>% 
+#   filter(!is.na(value)) %>% 
+#   group_by(name, day, value) %>% 
+#   summarise(count=n()) %>% 
+# 
+#   ggplot(aes(x= day, y= count, fill= value))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))
+```
+
 ```{r, fig.width=5, fig.height=6}
+# # Tile
+# cart2 %>% 
+#   select(PT, 
+#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
+#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(time, c("na":"me"), sep = " ") %>% 
+#   filter(!is.na(value)) %>% 
+#   arrange(value) %>% 
+#   ggplot(aes(x= day, y= fct_reorder2(PT, value, day), fill= value))+
+#   geom_tile(color = "white")+
+#   labs(fill = NULL, x = NULL, y= NULL)+
+#   theme_classic()
+```
+
+```{r}
+# Alluvial
+library(ggalluvial)
+
+alluvial_A <- cart2 %>% 
+  select(PT, igg_hsv_change,
+         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
+  # mutate(igg_hsv_change = case_when(
+  #   igg_hsv_change == 1        ~  "Acquired immunity",
+  #   igg_hsv_change == 0.25        ~  "Positive overtime",
+  #   igg_hsv_change == -0.25        ~  "Negative overtime",
+  #   igg_hsv_change == -1        ~  "Lost immunity"
+  # )) %>% 
+  drop_na() %>% 
+  group_by(`IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>% 
+  summarise(count=n()) %>%
+
+  ggplot(aes(axis1 = `IgG HSV1/2 apheresis`, axis2 = `IgG HSV1/2 D90`,
+             y = count)) +
+  geom_alluvium(aes(fill = `IgG HSV1/2 apheresis`)
+  )+
+  geom_stratum()+
+  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+  theme_classic()+
+  ggtitle("Evolution of virus titers")
+```
+
+### B)	VZV IgG (positive=immune vs negative or equivocal=not immune)
+```{r}
 # cart2 %>% 
 #   mutate(`VZV IgG apheresis` = case_when(
-#     `VZV IgG apheresis` == "0"         ~ "negative",
+#     `VZV IgG apheresis` == "0"         ~ "Negative",
 #     `VZV IgG apheresis` == "1"         ~ "immune",
@@
 #   mutate(`VZV IgG D90 (1=pos, 0=neg)` = case_when(
-#     `VZV IgG D90 (1=pos, 0=neg)` == "0"         ~ "negative",
+#     `VZV IgG D90 (1=pos, 0=neg)` == "0"         ~ "Negative",
 #     `VZV IgG D90 (1=pos, 0=neg)` == "1"         ~ "immune",
@@
 
-cart2 %>% 
-  mutate(`VZV IgG apheresis` = case_when(
-    `VZV IgG apheresis` == "0"         ~ "negative",
-    `VZV IgG apheresis` == "1"         ~ "immune",
-    TRUE                          ~ `VZV IgG apheresis`
-  )) %>% 
-  mutate(`VZV IgG D90 (1=pos, 0=neg)` = case_when(
-    `VZV IgG D90 (1=pos, 0=neg)` == "0"         ~ "negative",
-    `VZV IgG D90 (1=pos, 0=neg)` == "1"         ~ "immune",
-    TRUE                          ~ `VZV IgG D90 (1=pos, 0=neg)`
-  )) %>% 
-  select(PT, 
+# Histogram
+# cart2 %>% 
+#   select(PT, 
+#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
+#   ) %>% 
+#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(name, c("na":"me"), sep = " ") %>% 
+#   filter(!is.na(value)) %>% 
+#   group_by(name, day, value) %>% 
+#   summarise(count=n()) %>% 
+#   mutate(perc=(count/sum(count)*100)
+#   ) %>% 
+#   ggplot(aes(x= day, y= perc, fill= value))+
+#   geom_bar(stat = "identity")+
+#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
+#        fill= "Immunity")+
+#   scale_y_continuous(expand = c(0, 0))+
+#   theme_classic()
+
+# cart2 %>% 
+#   select(PT, 
+#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
+#   ) %>% 
+#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(name, c("na":"me"), sep = " ") %>% 
+#   filter(!is.na(value)) %>% 
+#   group_by(name, day, value) %>% 
+#   summarise(count=n()) %>% 
+# 
+#   ggplot(aes(x= day, y= count, fill= value))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))
+```
+
+```{r, fig.width=5, fig.height=6}
+# Tile
+# cart2 %>% 
+#   select(PT, 
+#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
+#   ) %>% 
+#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(time, c("na":"me"), sep = " ") %>% 
+#   filter(!is.na(value)) %>% 
+#   arrange(value) %>% 
+#   ggplot(aes(x= day, y= fct_reorder2(PT, value, day), fill= value))+
+#   geom_tile(color = "white")+
+#   labs(fill = NULL, x = NULL, y= NULL)+
+#   theme_classic()
+```
+
+```{r}
+# Alluvial
+alluvial_B <- cart2 %>% 
+  select(PT, igg_vzv_change,
          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
   ) %>% 
-  pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
-  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-  unite(time, c("na":"me"), sep = " ") %>% 
-  filter(!is.na(value)) %>% 
-  arrange(value) %>% 
-  ggplot(aes(x= day, y= fct_reorder2(PT, value, day), fill= value))+
-  geom_tile(color = "white")+
-  labs(fill = NULL, x = NULL, y= NULL)+
-  theme_classic()
-```
-
+  # mutate(igg_vzv_change = case_when(
+  #   igg_vzv_change == 1        ~  "Acquired immunity",
+  #   igg_vzv_change == 0.25        ~  "Positive overtime",
+  #   igg_vzv_change == -0.25        ~  "Negative overtime",
+  #   igg_vzv_change == -1        ~  "Lost immunity"
+  # )) %>% 
+  drop_na() %>% 
+  group_by(`VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`) %>% 
+  summarise(count=n()) %>%
+
+  ggplot(aes(axis1 = `VZV IgG apheresis`, axis2= `VZV IgG D90 (1=pos, 0=neg)`,
+             y = count)) +
+  geom_alluvium(aes(fill = `VZV IgG apheresis`)
+  )+
+  geom_stratum()+
+  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+  theme_classic()+
+  ggtitle("Evolution of virus titers")
+```
+
+### C)	CMV IgG (positive=immune vs negative=not immune)
 ```{r}
-cart2 %>% 
-  mutate(`VZV IgG apheresis` = case_when(
-    `VZV IgG apheresis` == "0"         ~ "negative",
-    `VZV IgG apheresis` == "1"         ~ "immune",
-    TRUE                          ~ `VZV IgG apheresis`
-  )) %>% 
-  mutate(`VZV IgG D90 (1=pos, 0=neg)` = case_when(
-    `VZV IgG D90 (1=pos, 0=neg)` == "0"         ~ "negative",
-    `VZV IgG D90 (1=pos, 0=neg)` == "1"         ~ "immune",
-    TRUE                          ~ `VZV IgG D90 (1=pos, 0=neg)`
-  )) %>% 
-  select(PT, 
-         `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
-  ) %>% 
-  pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
-  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-  unite(name, c("na":"me"), sep = " ") %>% 
-  filter(!is.na(value)) %>% 
-  group_by(name, day, value) %>% 
+# Histogram
+# cart2 %>% 
+#   
+#   select(PT, 
+#          `CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`
+#   ) %>% 
+#   pivot_longer(cols = `CMV IgG apheresis` : `CMV IgG D90 (1=pos, 0=neg)`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(name, c("na":"me"), sep = " ") %>% 
+#   filter(!is.na(value)) %>% 
+#   group_by(name, day, value) %>% 
+#   summarise(count=n()) %>% 
+#   mutate(perc=(count/sum(count)*100)
+#   ) %>% 
+#   ggplot(aes(x= day, y= perc, fill= value))+
+#   geom_bar(stat = "identity")+
+#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
+#        fill= "Immunity")+
+#   scale_y_continuous(expand = c(0, 0))+
+#   theme_classic()
+```
+
+```{r, fig.width=5, fig.height=6}
+# Tile
+# cart2 %>% 
+#   
+#   select(PT, 
+#          `CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`
+#   ) %>% 
+#   pivot_longer(cols = `CMV IgG apheresis` : `CMV IgG D90 (1=pos, 0=neg)`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(time, c("na":"me"), sep = " ") %>% 
+#   filter(!is.na(value)) %>% 
+#   arrange(value) %>% 
+#   ggplot(aes(x= day, y= fct_reorder2(PT, value, day), fill= value))+
+#   geom_tile(color = "white")+
+#   labs(fill = NULL, x = NULL, y= NULL)+
+#   theme_classic()
+```
+
+```{r}
+# Alluvial
+alluvial_C <- cart2 %>% 
+  select(PT, igg_cmv_change,
+         `CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`
+  ) %>% 
+  # mutate(igg_cmv_change = case_when(
+  #   igg_cmv_change == 1        ~  "Acquired immunity",
+  #   igg_cmv_change == 0.25        ~  "Positive overtime",
+  #   igg_cmv_change == -0.25        ~  "Negative overtime",
+  #   igg_cmv_change == -1        ~  "Lost immunity"
+  # )) %>% 
+  drop_na() %>% 
+  group_by(`CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`) %>% 
   summarise(count=n()) %>%
 
-  ggplot(aes(x= day, y= count, fill= value))+
-  geom_bar(stat = "identity",
-           position=position_dodge(width=0.9))
-```
-
-C)	CMV IgG (positive=immune vs negative=not immune)
-```{r}
-cart2 %>% 
-  mutate(`CMV IgG apheresis` = case_when(
-    `CMV IgG apheresis` == "0"         ~ "negative",
-    `CMV IgG apheresis` == "1"         ~ "immune"
-  )) %>% 
-  mutate(`CMV IgG D90 (1=pos, 0=neg)` = case_when(
-    `CMV IgG D90 (1=pos, 0=neg)` == "0"         ~ "negative",
-    `CMV IgG D90 (1=pos, 0=neg)` == "1"         ~ "immune"
-  )) %>% 
-  select(PT, 
-         `CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`
-  ) %>% 
-  pivot_longer(cols = `CMV IgG apheresis` : `CMV IgG D90 (1=pos, 0=neg)`) %>% 
-  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-  unite(time, c("na":"me"), sep = " ") %>% 
-  # mutate(value = as.numeric(value)) %>% 
-  mutate(day = case_when(
-    day == "D90"        ~ 90,
-    day == "apheresis"  ~ 0
-  )) %>% 
-  ggplot(aes(x= day, y= value, color= PT))+
-  geom_point(position=position_dodge(width=0.9))+
-  scale_x_continuous(
-    breaks = c(0, 90),
-    labels = c("Apheresis", "D90"))+
-  scale_color_viridis_d() +
-  labs(fill = "Patients", x = NULL)+
-  theme_classic()
+  ggplot(aes(axis1 = `CMV IgG apheresis`, axis2= `CMV IgG D90 (1=pos, 0=neg)`,
+             y = count)) +
+  geom_alluvium(aes(fill = `CMV IgG apheresis`)
+  )+
+  geom_stratum()+
+  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+  theme_classic()+
+  ggtitle("Evolution of virus titers")
+```
+
+```{r, fig.height=12}
+(alluvial_A) /
+  (alluvial_B) /
+  (alluvial_C) +
+  plot_annotation(tag_levels = "A")
 ```
@@
 ```{r, fig.width=12, fig.height=12}
-cart2 %>% 
-  select(PT, 
-         starts_with("Pneumo")
-
-  ) %>% 
-  pivot_longer(cols = -PT) %>% 
-  filter(!is.na(value)) %>% 
-  mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
-  mutate(name = str_remove(name, " apheresis| D90")) %>%
-
-  mutate(value = case_when(
-    value <= 1           ~ "negative",
-    value > 1            ~ "immune"
-  )) %>% 
-  group_by(name, day, value) %>% 
-  summarise(count=n()) %>% 
-  mutate(perc=(count/sum(count)*100)
-  ) %>%
-
-  ggplot(aes(x= day, y= perc, fill= value))+
-  geom_bar(stat = "identity",
-           position=position_dodge2(width=0.9, preserve = "single"))+
-  facet_wrap(.~ name)
-
-```
+# Histogram
+# cart2 %>% 
+#   select(PT, 
+#          starts_with("Pneumo"), -ends_with("change")) %>% 
+#   pivot_longer(cols = -PT) %>% 
+#   filter(!is.na(value)) %>% 
+#   mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
+#   mutate(name = str_remove(name, " apheresis| D90")) %>% 
+#   
+#   group_by(name, day, value) %>% 
+#   summarise(count=n()) %>% 
+#   mutate(perc=(count/sum(count)*100)
+#   ) %>% 
+# 
+#   ggplot(aes(x= day, y= perc, fill= value))+
+#   # geom_bar(stat = "identity",
+#   #          position=position_dodge2(width=0.9, preserve = "single"))+
+#   geom_bar(stat = "identity")+
+#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
+#        fill= "Immunity")+
+#   scale_y_continuous(expand = c(0, 0))+
+#   theme_classic()+
+#   facet_wrap(.~ name)
+```
+
+```{r, fig.width=12, fig.height=14}
+# Tile
+# cart2 %>% 
+#   select(PT, 
+#          starts_with("Pneumo"), -ends_with("change")) %>% 
+#   pivot_longer(cols = -PT) %>% 
+#   mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
+#   mutate(name = str_remove(name, " apheresis| D90")) %>% 
+#   
+#   
+#   filter(!is.na(value)) %>% 
+#   arrange(value) %>% 
+#   ggplot(aes(x= day, y= fct_reorder2(PT, value, day), fill= value))+
+#   geom_tile(color = "white")+
+#   labs(fill = NULL, x = NULL, y= NULL)+
+#   theme_classic()+
+#   facet_wrap(.~ name)
+```
+
+##########################
+
+```{r, fig.width=15, fig.height=12}
+library(ComplexHeatmap)
+mat <- cart2 %>% 
+  select(PT, intersect(starts_with("Pneumo"), ends_with("change"))) %>% 
+  drop_na() %>% 
+  # mutate(new_sort = rowSums(select(.,-PT), na.rm = TRUE)) %>%
+  mutate(new_sort = 
+           c(5,7,8,23,6,9,10,11,12,4,13,14,26,15,
+             24,3,16,25,17,2,18,21,19,20,1,22)) %>%
+
+  arrange(new_sort) %>% 
+    select(-new_sort)
+
+df5 <- t((as.matrix(mat)))
+
+df <- df5 %>% `colnames<-`(c(.[1,])) %>% 
+  .[-1,]
+
+df <- df %>% 
+sub(pattern = " 1.00", replacement = "Acquired immunity") %>% 
+sub(pattern = " 0.25", replacement = "Positive overtime") %>% 
+sub(pattern = "-0.25", replacement = "Negative overtime") %>% 
+sub(pattern = "-1.00", replacement = "Lost immunity")
+
+colors = structure(c("blue", "darkgrey", "lightgrey", "red"), 
+                   names = c("Lost immunity", "Negative overtime", "Positive overtime", "Acquired immunity"))
+
+ht_list <- Heatmap(df, name = "change", 
+        rect_gp = gpar(col = "white", lwd = 0.1),
+        column_title = "Change in titers",
+        show_column_names =FALSE,
+        row_names_side = "left",
+        row_names_gp = gpar(fontsize = 11),
+        col = colors)
+draw(ht_list, heatmap_legend_side = "bottom")
+# Heatmap(df, name = "change", 
+#         rect_gp = gpar(col = "white", lwd = 0.1),
+#         column_title = "Change in titers",
+#         column_names_rot = 45,
+#         column_names_gp = gpar(fontsize = 8),
+#         row_names_side = "left", 
+#         row_names_gp = gpar(fontsize = 10,
+#                             col = c("darkgreen", "pink", "orange", rep("blue", 28))),
+#         show_heatmap_legend = TRUE,
+#         col = colors)
+kjhkhkh
+```

### 2022-04-01 Manuscript analyses.Rmd
Color change

@@
 a %>% filter(grade == "Grade 3+") %>% 
-  # unite(time, c("day":"me"), sep = " ") %>% 
   ggplot(aes(x= day, 
@@
            aes(x= day, y= perc, fill= name), alpha= 0.4)+
-  # facet_grid(name ~ .,)+
-  scale_fill_viridis_d() + 
+  scale_fill_brewer(palette = "Spectral")+
   labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+

### 2022-04-04 Manuscript analyses.Rmd
quick add up

@@
   select(PT,
+         Leukopenia_apheresis,
          `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
+         Neutropenia_apheresis,
          `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
+         Anemia_apheresis,
          `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
+         Thrombocytopenia_apheresis,
          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
 
+         gr3_Leukopenia_apheresis,
          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
+         gr3_Neutropenia_apheresis,
          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
+         gr3_Anemia_apheresis,
          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
+         gr3_Thrombocytopenia_apheresis,
          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
   ) %>% 
-  pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
+  pivot_longer(cols = `Leukopenia_apheresis`: gr3_Thrombocytopenia_90d) %>% 
   mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
@@
   ungroup() %>% 
-  filter(value == "YES")
+  filter(value == "YES") %>% 
+  add_row("name"="Leukopenia",  "day"="apheresis", "value"= "YES", "grade"="Any grade", "count"=0, "perc"=0) %>% 
+  mutate(day = factor(day, levels = c("apheresis", "-5d", "30d", "60d", "90d")))
 b <- a %>% filter(grade == "Any grade")

### 2022-04-07 RWE Manuscript analyses.Rmd
Add RWE cart analyses Rmd

---
title: "Real World Manuscript Analyses"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_opatient_idions: 
  chunk_output_type: console
---

<style type= "text/css">

.## Figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

## Table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opatient_ids_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
opatient_idions(gtsummary.print_engine = "gt")
opatient_idions(gtsummary.as_gt.addl_cmds = "gt::tab_opatient_idions(table.font.size = 14, data_row.padding = gt::px(1))")
```

```{r library}
library(tidyverse)
library(ggplot2)
library(gtsummary)
library(labelled)
library(DescTools)
library(patchwork)
library(ggbreak)
library(survival)
library(survminer)
```

```{r load}
# path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias")

MM_cart <-
  readxl::read_xlsx("./Data ASCO 2022 Myeloma CAR-T SOC Outcomes 04072022.xlsx",
                    skip = 1, n_max = 200
                    ) %>% 
  rename(patient_id = `PT Identifier (DO NOT USE PHI)`)
```

```{r data cleaning}
cart <- MM_cart %>% 
  # Exclude patients who had manufacturing cart failure or died prior cart infusion
  filter(is.na(exclude_for_manufacturing_cart_failure_or_died_prior_cart_infusion)) %>% 
  # Keep seconf infusion date for patients who had failure
  # mutate(`Date of Apheresis (or # of days from apheresis to LD)` = as.character(`Date of Apheresis (or # of days from apheresis to LD)`))

  separate(`Date of Apheresis (or # of days from apheresis to LD)`, 
           into= c("first_date_of_apheresis", "date_of_apheresis"), sep = ", 2nd-|; 2nd - ", remove = FALSE) %>% 
  mutate(first_date_of_apheresis = str_remove(first_date_of_apheresis, "1st - |1st-"),
         first_date_of_apheresis = as.Date(as.numeric(first_date_of_apheresis), 
                                             origin = "1899-12-30"),
         date_of_apheresis = as.Date(date_of_apheresis, format = "%m/%d/%Y"),
         date_of_apheresis = coalesce(date_of_apheresis, first_date_of_apheresis)
         ) %>% 
  select(-first_date_of_apheresis)

```

### 2022-04-13 ide_cel/Manuscript analyses.Rmd
Update Rmd with new data

--- 2022-04-01 Manuscript analyses.Rmd
@@
 Characteristics <-
-  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
+  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
                     sheet = "Characteristics", skip = 1, n_max = 54) %>% 
@@
 Counts <-
-  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
+  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
                     sheet = "Counts") %>% 
@@
 Infections <-
-  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
+  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
                     sheet = "Infections") %>% 
@@
 Support <-
-  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
+  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
                     sheet = "Support",
@@
 Pneumo_titers <-
-  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
+  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
                     sheet = "Pneumo Titers") %>% 
@@
 Other_titers <-
-  readxl::read_xlsx("./CytopeniaManuscriptData_3.16.22.xlsx",
+  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
                     sheet = "Other Titers") %>% 
@@
               "Bridging Therapy (Yes=1, No=0)",
+              "Received alkylating therapy with bridging (Yes=1, No=0)",
               "Prior auto SCT (yes=1, no=0)",
@@
 
-  mutate(`cytopenia_30d` = case_when(
+  mutate(cytopenia_apheresis = case_when(
+    `WBC apheresis` < 4 | 
+      `ANC apheresis` < 1.8 | 
+      `Hb apheresis` < 11.4 | 
+      `Plt apheresis` < 143                                             ~ "YES",
+    is.na(`WBC apheresis`) |
+      is.na(`ANC apheresis`) |
+      is.na(`Hb apheresis`) |
+      is.na(`Plt apheresis`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(`cytopenia_-5d` = case_when(
+    `WBC day -5 (k/ul)` < 4 | 
+      `ANC day -5 (k/ul)` < 1.8 | 
+      `Hb day -5 (k/ul)` < 11.4 | 
+      `Plt day -5 (k/ul)` < 143                                             ~ "YES",
+    is.na(`WBC day -5 (k/ul)`) |
+      is.na(`ANC day -5 (k/ul)`) |
+      is.na(`Hb day -5 (k/ul)`) |
+      is.na(`Plt day -5 (k/ul)`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(cytopenia_0d = case_when(
+    `WBC day 0 (k/uL)` < 4 | 
+      `ANC day 0 (k/uL)` < 1.8 | 
+      `Hb day 0 (k/uL)` < 11.4 | 
+      `Plt day 0 (k/uL)` < 143                                             ~ "YES",
+    is.na(`WBC day 0 (k/uL)`) |
+      is.na(`ANC day 0 (k/uL)`) |
+      is.na(`Hb day 0 (k/uL)`) |
+      is.na(`Plt day 0 (k/uL)`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(cytopenia_7d = case_when(
+    `WBC day +7` < 4 | 
+      `ANC day +7` < 1.8 | 
+      `Hb day +7` < 11.4 | 
+      `Plt day +7` < 143                                             ~ "YES",
+    is.na(`WBC day +7`) |
+      is.na(`ANC day +7`) |
+      is.na(`Hb day +7`) |
+      is.na(`Plt day +7`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(cytopenia_14d = case_when(
+    `WBC day +14` < 4 | 
+      `ANC day +14` < 1.8 | 
+      `Hb day +14` < 11.4 | 
+      `Plt day +14` < 143                                             ~ "YES",
+    is.na(`WBC day +14`) |
+      is.na(`ANC day +14`) |
+      is.na(`Hb day +14`) |
+      is.na(`Plt day +14`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(cytopenia_21d = case_when(
+    `WBC day +21` < 4 | 
+      `ANC day +21` < 1.8 | 
+      `Hb day +21` < 11.4 | 
+      `Plt day +21` < 143                                             ~ "YES",
+    is.na(`WBC day +21`) |
+      is.na(`ANC day +21`) |
+      is.na(`Hb day +21`) |
+      is.na(`Plt day +21`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(cytopenia_30d = case_when(
     `WBC day +30` < 4 | 
@@
   )) %>% 
-  mutate(`gr3_cytopenia_30d` = case_when(
+  mutate(cytopenia_60d = case_when(
+    `WBC day +60` < 4 | 
+      `ANC day +60` < 1.8 | 
+      `Hb day +60` < 11.4 | 
+      `Plt day +60` < 143                                             ~ "YES",
+    is.na(`WBC day +60`) |
+      is.na(`ANC day +60`) |
+      is.na(`Hb day +60`) |
+      is.na(`Plt day +60`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(cytopenia_90d = case_when(
+    `WBC day +90` < 4 | 
+      `ANC day +90` < 1.8 | 
+      `Hb day +90` < 11.4 | 
+      `Plt day +90` < 143                                             ~ "YES",
+    is.na(`WBC day +90`) |
+      is.na(`ANC day +90`) |
+      is.na(`Hb day +90`) |
+      is.na(`Plt day +90`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>%
+
+   mutate(gr3_cytopenia_apheresis = case_when(
+    `WBC apheresis` < 2 | 
+      `ANC apheresis` < 1 | 
+      `Hb apheresis` < 8 | 
+      `Plt apheresis` < 50                                             ~ "YES",
+    is.na(`WBC apheresis`) |
+      is.na(`ANC apheresis`) |
+      is.na(`Hb apheresis`) |
+      is.na(`Plt apheresis`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(`gr3_cytopenia_-5d` = case_when(
+    `WBC day -5 (k/ul)` < 2 | 
+      `ANC day -5 (k/ul)` < 1 | 
+      `Hb day -5 (k/ul)` < 8 | 
+      `Plt day -5 (k/ul)` < 50                                             ~ "YES",
+    is.na(`WBC day -5 (k/ul)`) |
+      is.na(`ANC day -5 (k/ul)`) |
+      is.na(`Hb day -5 (k/ul)`) |
+      is.na(`Plt day -5 (k/ul)`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(gr3_cytopenia_0d = case_when(
+    `WBC day 0 (k/uL)` < 2 | 
+      `ANC day 0 (k/uL)` < 1 | 
+      `Hb day 0 (k/uL)` < 8 | 
+      `Plt day 0 (k/uL)` < 50                                              ~ "YES",
+    is.na(`WBC day 0 (k/uL)`) |
+      is.na(`ANC day 0 (k/uL)`) |
+      is.na(`Hb day 0 (k/uL)`) |
+      is.na(`Plt day 0 (k/uL)`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(gr3_cytopenia_7d = case_when(
+    `WBC day +7` < 2 | 
+      `ANC day +7` < 1 | 
+      `Hb day +7` < 8 | 
+      `Plt day +7` < 50                                              ~ "YES",
+    is.na(`WBC day +7`) |
+      is.na(`ANC day +7`) |
+      is.na(`Hb day +7`) |
+      is.na(`Plt day +7`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(gr3_cytopenia_14d = case_when(
+    `WBC day +14` < 2 | 
+      `ANC day +14` < 1 | 
+      `Hb day +14` < 8 | 
+      `Plt day +14` < 50                                              ~ "YES",
+    is.na(`WBC day +14`) |
+      is.na(`ANC day +14`) |
+      is.na(`Hb day +14`) |
+      is.na(`Plt day +14`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(gr3_cytopenia_21d = case_when(
+    `WBC day +21` < 2 | 
+      `ANC day +21` < 1 | 
+      `Hb day +21` < 8 | 
+      `Plt day +21` < 50                                              ~ "YES",
+    is.na(`WBC day +21`) |
+      is.na(`ANC day +21`) |
+      is.na(`Hb day +21`) |
+      is.na(`Plt day +21`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(gr3_cytopenia_30d = case_when(
     `WBC day +30` < 2 | 
@@
   )) %>% 
-  mutate(`gr3_cytopenia_90d` = case_when(
+  mutate(gr3_cytopenia_60d = case_when(
+    `WBC day +60` < 2 | 
+      `ANC day +60` < 1 | 
+      `Hb day +60` < 8 | 
+      `Plt day +60` < 50                                              ~ "YES",
+    is.na(`WBC day +60`) |
+      is.na(`ANC day +60`) |
+      is.na(`Hb day +60`) |
+      is.na(`Plt day +60`)                                            ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(gr3_cytopenia_90d = case_when(
     `WBC day +90` < 2 | 
@@
 
-  mutate(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` = case_when(
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "VGPR")        ~ "VGPR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "PR")          ~ "PR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "evaluable")   ~ NA_character_,
-    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` == "CR"	                   ~ "CR, MRD unknown",
-    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` == "CR, MRD+"	             ~ "CR, MRD+",
-
-    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` == "sCR, MRD+"           	 ~ "sCR, MRD+",
-    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` %in% c(
-      "sCR MRD-", "sCR, MRD-")                                                         ~ "sCR, MRD-",
-
-    `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )` %in% c(
-      "sCR", "sCR (flow neg, no clonoSEQ ID)", "sCR MRD - by flow/no clonoSEQ)",
-      "sCR, MRD- by flow/no clonoSEQ)")                                                ~ "sCR, MRD unknown",
-
-    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`
+  mutate(`Day 30 Response (sCR, CR, VGPR, PR)` = case_when(
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "evaluable")   ~ NA_character_,
+    # `Day 30 Response (sCR, CR, VGPR, PR)` == "CR"	                   ~ "CR, MRD unknown",
+    # `Day 30 Response (sCR, CR, VGPR, PR)` == "CR, MRD+"	             ~ "CR, MRD+",
+    # 
+    # `Day 30 Response (sCR, CR, VGPR, PR)` == "sCR, MRD+"           	 ~ "sCR, MRD+",
+    # `Day 30 Response (sCR, CR, VGPR, PR)` %in% c(
+    #   "sCR MRD-", "sCR, MRD-")                                                         ~ "sCR, MRD-",
+    # 
+    # `Day 30 Response (sCR, CR, VGPR, PR)` %in% c(
+    #   "sCR", "sCR (flow neg, no clonoSEQ ID)", "sCR MRD - by flow/no clonoSEQ)",
+    #   "sCR, MRD- by flow/no clonoSEQ)")                                                ~ "sCR, MRD unknown",
+
+    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR)`
   )) %>% 
   mutate(ORR_30days = case_when(
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "CR")   ~ "ORR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "PR")   ~ "ORR",
-    is.na(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`)              ~ NA_character_,
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR")   ~ "ORR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "PR")   ~ "ORR",
+    is.na(`Day 30 Response (sCR, CR, VGPR, PR)`)              ~ NA_character_,
     TRUE                                                                        ~ "PD/SD/MR"
   )) %>%
-  mutate(MRDneg_30days = case_when(
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "MRD-")        ~ "Yes",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "MRD")         ~ "No",
+
+  mutate_at(c("Day 30 MRD (Pos=1, Neg=0)",
+              "Day 90 MRD (Pos=1, Neg=0)"), 
+            ~ case_when(
+              . == 1                                              ~ "Positive",
+              . == 0                                              ~ "Negative",
               TRUE                                                ~ NA_character_
             )) %>%
+
+  # mutate(`Day 30 MRD (Pos=1, Neg=0)` = case_when(
+  #   str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD-")        ~ "Yes",
+  #   str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD")         ~ "No",
+  #   TRUE                             ~ NA_character_
+  # )) %>% 
   mutate(day30_response = case_when(
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "VGPR")        ~ "VGPR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "PR")          ~ "PR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "sCR")	       ~ "sCR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "CR")	         ~ "CR",
-    is.na(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`)                     ~ NA_character_,
-    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "sCR")	       ~ "sCR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR")	         ~ "CR",
+    is.na(`Day 30 Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
+    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR)`
   )) %>% 
   mutate(day30_response_group = case_when(
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "VGPR")        ~ "VGPR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "PR")          ~ "PR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "CR")	         ~ "CR or sCR",
-    is.na(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`)                     ~ NA_character_,
-    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR")	         ~ "CR or sCR",
+    is.na(`Day 30 Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
+    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR)`
   )) %>% 
   mutate(day30_response_sCRvsOthers = case_when(
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "CR")	         ~ "CR or sCR",
-    is.na(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`)                     ~ NA_character_,
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR")	         ~ "CR or sCR",
+    is.na(`Day 30 Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
     TRUE           ~ "Others"
@@
   mutate(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` = case_when(
-    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "VGPR")        ~ "VGPR",
-    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "PR")          ~ "PR",
+    # str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "VGPR")        ~ "VGPR",
+    # str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "PR")          ~ "PR",
     str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "evaluable")   ~ NA_character_,
 
-    `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
-      "CR", "CR (no clonoSEQ/MRD as no marrow)")                                      ~ "CR, MRD unknown",
-
-    `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
-      "sCR (clonoSEQ pending, flow neg)", 
-      "sCR (no clonoSEQ for MRD, flow suspicious for MRD)",
-      "sCR (no clonoSEQ, flow neg)")                                                  ~ "sCR, MRD unknown",
-
-    `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
-      "sCR, MRD - (by flow+)", "sCR, MRD-	12 (24%)")                                  ~ "sCR, MRD-",
-
-    `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` == "sCR, MRD+"	            ~	"sCR, MRD+",
+    # `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
+    #   "CR", "CR (no clonoSEQ/MRD as no marrow)")                                      ~ "CR, MRD unknown",
+    # 
+    # `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
+    #   "sCR (clonoSEQ pending, flow neg)", 
+    #   "sCR (no clonoSEQ for MRD, flow suspicious for MRD)",
+    #   "sCR (no clonoSEQ, flow neg)")                                                  ~ "sCR, MRD unknown",
+    # 
+    # `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
+    #   "sCR, MRD - (by flow+)", "sCR, MRD-	12 (24%)")                                  ~ "sCR, MRD-",
+    # 
+    # `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` == "sCR, MRD+"	            ~	"sCR, MRD+",
 
@@
   )) %>% 
-  mutate(MRDneg_90days = case_when(
-    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD-")        ~ "Yes",
-    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD")         ~ "No",
-    TRUE                             ~ NA_character_
-  )) %>% 
+  # mutate(`Day 90 MRD (Pos=1, Neg=0)` = case_when(
+  #   str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD-")        ~ "Yes",
+  #   str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD")         ~ "No",
+  #   TRUE                             ~ NA_character_
+  # )) %>% 
   mutate(day90_response_group = case_when(
@@
     str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD-") |
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "MRD-")        ~ "Yes",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD-")        ~ "Yes",
     str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD") |
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR and MRD+ vs MRD- )`, "MRD")         ~ "No",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD")         ~ "No",
     TRUE                             ~ NA_character_
@@
          `Bridging Therapy (Yes=1, No=0)`,
+         `Received alkylating therapy with bridging (Yes=1, No=0)`,
          `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
@@
         `Bridging Therapy (Yes=1, No=0)`, `Prior auto SCT (yes=1, no=0)`,
+        `Received alkylating therapy with bridging (Yes=1, No=0)`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref,
@@
   distinct(MRN, .keep_all = TRUE) %>% 
-  select(MRDneg_30days,
+  select(`Day 30 MRD (Pos=1, Neg=0)`,
          ORR_30days,
@@
   tbl_summary(type = list(
-    c(MRDneg_30days) ~ "categorical"),
+    c(`Day 30 MRD (Pos=1, Neg=0)`) ~ "categorical"),
     digits = all_continuous() ~ 1,
@@
   filter(day30_response_group == "CR or sCR") %>% 
-  select(MRDneg_30days) %>% 
-  tbl_summary(type = list(c(MRDneg_30days) ~ "categorical"),
-              label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
+  select(`Day 30 MRD (Pos=1, Neg=0)`) %>% 
+  tbl_summary(type = list(c(`Day 30 MRD (Pos=1, Neg=0)`) ~ "categorical"),
+              label = list(`Day 30 MRD (Pos=1, Neg=0)` ~ "`Day 30 MRD (Pos=1, Neg=0)` within CR/sCR"),
               digits = all_continuous() ~ 1,
@@
   distinct(MRN, .keep_all = TRUE) %>% 
-  select(MRDneg_90days,
+  select(`Day 90 MRD (Pos=1, Neg=0)`,
          ORR_90days,
@@
   tbl_summary(type = list(
-    c(MRDneg_90days) ~ "categorical"),
+    c(`Day 90 MRD (Pos=1, Neg=0)`) ~ "categorical"),
     digits = all_continuous() ~ 1,
@@
   filter(day90_response_group == "CR or sCR") %>% 
-  select(MRDneg_90days) %>% 
-  tbl_summary(type = list(c(MRDneg_90days) ~ "categorical"),
-              label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
+  select(`Day 90 MRD (Pos=1, Neg=0)`) %>% 
+  tbl_summary(type = list(c(`Day 90 MRD (Pos=1, Neg=0)`) ~ "categorical"),
+              label = list(`Day 90 MRD (Pos=1, Neg=0)` ~ "`Day 90 MRD (Pos=1, Neg=0)` within CR/sCR"),
               digits = all_continuous() ~ 1,
@@
   select(best_response) %>% 
-  tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"),
+  tbl_summary(#type = list(c(`Day 90 MRD (Pos=1, Neg=0)`) ~ "categorical"),
               label = list(best_response ~ "best response in the first 90 days"),
@@
          "Thrombocytopenia" = `Thrombocytopenia_apheresis`, 
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_apheresis`
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_apheresis`,
+         "Any Cytopenia" = cytopenia_apheresis,
+         "Grade3+ Cytopenia" = gr3_cytopenia_apheresis
   ) %>% 
@@
          "Thrombocytopenia" = `Thrombocytopenia_-5d`, 
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_-5d`
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_-5d`,
+         "Any Cytopenia" = `cytopenia_-5d`,
+         "Grade3+ Cytopenia" = `gr3_cytopenia_-5d`
   ) %>% 
@@
          "Thrombocytopenia" = `Thrombocytopenia_0d`, 
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_0d`
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_0d`,
+         "Any Cytopenia" = cytopenia_0d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_0d
   ) %>% 
@@
          "Thrombocytopenia" = `Thrombocytopenia_7d`, 
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_7d`
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_7d`,
+         "Any Cytopenia" = cytopenia_7d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_7d
   ) %>% 
@@
          "Thrombocytopenia" = `Thrombocytopenia_14d`, 
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_14d` 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_14d`,
+         "Any Cytopenia" = cytopenia_14d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_14d
   ) %>% 
@@
          "Thrombocytopenia" = `Thrombocytopenia_21d`, 
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_21d`
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_21d`,
+         "Any Cytopenia" = cytopenia_21d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_21d
   ) %>% 
@@
          "Thrombocytopenia" = `Thrombocytopenia_30d`,
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_30d` 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_30d`,
+         "Any Cytopenia" = cytopenia_30d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_30d
   ) %>% 
@@
          "Thrombocytopenia" = `Thrombocytopenia_90d`, 
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_90d`
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_90d`,
+         "Any Cytopenia" = cytopenia_90d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_90d
   ) %>% 
@@
   filter(is.na(Not_evaluable_at_30days)) %>% 
-  select(Age, agecat, male_sex, Sex,
+  select(
+    Age, agecat, male_sex, Sex,
          `Extramedullary Disease? (yes=1, no=0)`, 
@@
          `Bridging Therapy (Yes=1, No=0)`,
+    `Received alkylating therapy with bridging (Yes=1, No=0)`,
          `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
@@
          `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
+         cytopenia_apheresis, `cytopenia_-5d`, gr3_cytopenia_apheresis, `gr3_cytopenia_-5d`,
          `gr3_cytopenia_30d`) %>% 
@@
     `Bridging Therapy (Yes=1, No=0)` ~ "categorical",
+    `Received alkylating therapy with bridging (Yes=1, No=0)` ~ "categorical",
     `Prior auto SCT (yes=1, no=0)` ~ "categorical",
@@
   filter(is.na(Not_evaluable_at_30days)) %>% 
-  select(#MRDneg_30days,
+  select(#`Day 30 MRD (Pos=1, Neg=0)`,
          ORR_30days, day30_response_sCRvsOthers,
@@
     #           type = list(
-    # c(MRDneg_30days) ~ "categorical"),
+    # c(`Day 30 MRD (Pos=1, Neg=0)`) ~ "categorical"),
     digits = all_continuous() ~ 1,
@@
 #   filter(day30_response_group == "CR or sCR") %>% 
-#   select(MRDneg_30days, gr3_cytopenia_30d) %>% 
+#   select(`Day 30 MRD (Pos=1, Neg=0)`, gr3_cytopenia_30d) %>% 
 #   tbl_summary(by =`gr3_cytopenia_30d`,
-#               type = list(c(MRDneg_30days) ~ "categorical"),
-#               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
+#               type = list(c(`Day 30 MRD (Pos=1, Neg=0)`) ~ "categorical"),
+#               label = list(`Day 30 MRD (Pos=1, Neg=0)` ~ "`Day 30 MRD (Pos=1, Neg=0)` within CR/sCR"),
 #               digits = all_continuous() ~ 1,
@@
   filter(is.na(Not_evaluable_at_30days)) %>% 
-  select(#MRDneg_90days,
+  select(#`Day 90 MRD (Pos=1, Neg=0)`,
          ORR_90days, day90_response_sCRvsOthers,
@@
     #           type = list(
-    # c(MRDneg_90days) ~ "categorical"),
+    # c(`Day 90 MRD (Pos=1, Neg=0)`) ~ "categorical"),
     digits = all_continuous() ~ 1,
@@
 #   filter(day90_response_group == "CR or sCR") %>% 
-#   select(MRDneg_90days, gr3_cytopenia_30d) %>% 
+#   select(`Day 90 MRD (Pos=1, Neg=0)`, gr3_cytopenia_30d) %>% 
 #   tbl_summary(by =`gr3_cytopenia_30d`,
-#               type = list(c(MRDneg_90days) ~ "categorical"),
-#               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
+#               type = list(c(`Day 90 MRD (Pos=1, Neg=0)`) ~ "categorical"),
+#               label = list(`Day 90 MRD (Pos=1, Neg=0)` ~ "`Day 90 MRD (Pos=1, Neg=0)` within CR/sCR"),
 #               digits = all_continuous() ~ 1,
@@
   tbl_summary(by =`gr3_cytopenia_30d`,
-              #type = list(c(MRDneg_90days) ~ "categorical"),
+              #type = list(c(`Day 90 MRD (Pos=1, Neg=0)`) ~ "categorical"),
               label = list(best_response ~ "best response in the first 90 days"),
@@
   select(PT,
-         `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
+         # Leukopenia_apheresis,
+         # `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
+         Neutropenia_apheresis,
          `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
+         Anemia_apheresis,
          `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
+         Thrombocytopenia_apheresis,
          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
-
-         `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
+         cytopenia_apheresis, `cytopenia_-5d`, cytopenia_30d, cytopenia_60d, cytopenia_90d,
+
+         # gr3_Leukopenia_apheresis,
+         # `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
+         gr3_Neutropenia_apheresis,
          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
+         gr3_Anemia_apheresis,
          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
-         `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
-  ) %>% 
-  pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
+         gr3_Thrombocytopenia_apheresis,
+         `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d,
+         gr3_cytopenia_apheresis, `gr3_cytopenia_-5d`, gr3_cytopenia_30d, gr3_cytopenia_60d, gr3_cytopenia_90d
+  ) %>% 
+  pivot_longer(cols = Neutropenia_apheresis: gr3_cytopenia_90d) %>% 
   mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
@@
   ungroup() %>% 
-  filter(value == "YES")
+  filter(value == "YES") %>% 
+  # add_row("name"="Leukopenia",  "day"="apheresis", "value"= "YES", "grade"="Any grade", "count"=0, "perc"=0) %>% 
+  mutate(day = factor(day, levels = c("apheresis", "-5d", "30d", "60d", "90d"))) %>% 
+  mutate(name = str_replace(name, "^cytopenia", "Any Cytopenia")) %>% 
+  mutate(name = factor(name, levels = c("Anemia", "Neutropenia", "Thrombocytopenia", "Any Cytopenia")))
+
 b <- a %>% filter(grade == "Any grade")
@@
   scale_fill_brewer(palette = "Spectral")+
+  # scale_fill_manual(values = c("#D7191C", "#FDAE61", "violet", "#ABDDA4", "#2B83BA"))+
   labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
@@
   drop_na() %>% 
-  # mutate(new_sort = rowSums(select(.,-PT), na.rm = TRUE)) %>%
   mutate(new_sort = 
-           c(5,7,8,23,6,9,10,11,12,4,13,14,26,15,
-             24,3,16,25,17,2,18,21,19,20,1,22)) %>%
+           c(6,10,11,26,8,
+             12,24,13,31,
+             14,15, 5,9, 16,
+             17,30,18,27, 2,
+             7,4,19,29,20,
+             3, 21, 25, 22, 
+             23,1,28),
+         .before = 2) %>%
 
@@
 draw(ht_list, heatmap_legend_side = "bottom")
-# Heatmap(df, name = "change", 
-#         rect_gp = gpar(col = "white", lwd = 0.1),
-#         column_title = "Change in titers",
-#         column_names_rot = 45,
-#         column_names_gp = gpar(fontsize = 8),
-#         row_names_side = "left", 
-#         row_names_gp = gpar(fontsize = 10,
-#                             col = c("darkgreen", "pink", "orange", rep("blue", 28))),
-#         show_heatmap_legend = TRUE,
-#         col = colors)
-kjhkhkh
-```
+```
+
+```{r, fig.width=15, fig.height=12}
+ghgghjg
+```

### 2022-04-14 RWE/RWE Manuscript analyses.Rmd
Update RWE Rmd

---
title: "Real World Manuscript Analyses"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_opatient_idions: 
  chunk_output_type: console
editor_options: 
  chunk_output_type: console
---

<style type= "text/css">

.## Figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

## Table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

```{r library}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(gtsummary)
library(labelled)
library(DescTools)
library(patchwork)
library(ggbreak)
library(survival)
library(survminer)
```

```{r load}
# path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias")
path <- getwd()
MM_cart <-
  readxl::read_xlsx(paste0(path,
    "/RWE/FINAL 4.13.22 ASCO 2022 Myeloma CAR-T SOC Outcomes Spreadsheet.xlsx"),
                    skip = 1, n_max = 198
                    ) %>% 
  rename(patient_id = `PT Identifier (DO NOT USE PHI)`)
```

`r emo::ji("question_mark")` **Are we setting the days >100 to 100?**

```{r data cleaning}
cart0 <- MM_cart %>% 
  # Exclude patients who had manufacturing cart failure or died prior cart infusion
  filter(is.na(exclude_for_manufacturing_cart_failure_or_died_prior_cart_infusion)) %>% 
  # Keep second infusion date for patients who had failure
  separate(`Date of Apheresis (or # of days from apheresis to LD)`, 
           into= c("first_date_of_apheresis", "date_of_apheresis"), sep = ", 2nd-|; 2nd - ", remove = FALSE) %>% 
  mutate(first_date_of_apheresis = str_remove(first_date_of_apheresis, "1st - |1st-"),
         first_date_of_apheresis = as.Date(as.numeric(first_date_of_apheresis),
                                             origin = "1899-12-30"),
         date_of_apheresis = parse_date_time(date_of_apheresis, "mdy"),
         date_of_apheresis = coalesce(date_of_apheresis, first_date_of_apheresis)
         ) %>% 
  select(-c(`Date of Apheresis (or # of days from apheresis to LD)`, first_date_of_apheresis)) %>%

###########################################################################
###########################################################################
###########################################################################
###########################################################################
###########################################################################
###########################################################################

# censored days > 100 to 100
  mutate(across(c(#`Day of onset of CRS relative to infusion`,
                  `Day of Max CRS (relative to infusion)`,
                  #`Day of onset of ICANS relative to infusion`,
                  `Day of Max ICANS (relative to infusion)`), ~ case_when(
    . > 100                                                       ~ 100,
    TRUE                                                          ~ as.numeric(.)
  ))) %>% 
  # defining BMI categories
  # mutate(bmicat = case_when(
  #   `BMI at apheresis` < 25             ~ "< 25 kg/m2",
  #   `BMI at apheresis` >= 25 & 
  #     cart$`BMI at apheresis` < 30      ~ "25 to < 30 kg/m2",
  #   `BMI at apheresis` >= 30            ~ "≥ 30 kg/m2"
  # ),
  # bmicat = factor(bmicat, levels = c("< 25 kg/m2", "25 to < 30 kg/m2", "≥ 30 kg/m2"))
  # ) %>% 
  # mutate(bmicat2 = case_when(
  #   `BMI at apheresis` < 25             ~ "< 25 kg/m2",
  #   `BMI at apheresis` >= 25            ~ "≥ 25 kg/m2"
  # ),
  # bmicat2 = factor(bmicat2, levels = c("< 25 kg/m2", "≥ 25 kg/m2"))
  # ) %>% 
  # age categories
  mutate(agecat = case_when(
    Age < 65                            ~ "< 65 years",
    Age >= 65                           ~ "≥ 65 years"
  ),
  agecat = factor(agecat, levels = c("< 65 years", "≥ 65 years"))
  ) %>% 
  mutate(male_sex = case_when(
    Sex == "M"                                                    ~ 1,
    TRUE                                                          ~ 0
  )) %>% 
  mutate_at(c("ECOG at consult",
              "ECOG at LD"
              ), 
            ~ case_when(
              . == 1                                              ~ "YES",
              . == 0                                              ~ "NO",
              TRUE                                                ~ NA_character_
            )) %>% 
  # ECOG
  # mutate(`ECOG at LD` = case_when(
  #   `ECOG at LD` == 0 | 
  #     `ECOG at LD` == 1                       ~ "0-1",
  #   TRUE                                                          ~ `ECOG at LD`
  # )) %>% 
  # cytogenetics
  mutate(cyto = case_when(
    `Deletion 17p prior to CAR-T infusion (yes, no)` == "YES" | 
      `t(4:14) prior to CAR-T infusion (yes, no)` == "YES" | 
      `t(14:16) prior to CAR-T infusion (yes, no)` == "YES"   ~ "YES",
    `Deletion 17p prior to CAR-T infusion (yes, no)` == "NO" &
      `t(4:14) prior to CAR-T infusion (yes, no)` == "NO" &
      `t(14:16) prior to CAR-T infusion (yes, no)` == "NO"    ~ "NO"
  )) %>% 
  # refractory status
  # mutate_at(c("Lenalidomide (exposed vs. refractory)",
  #             "Bortezomib (exposed vs. refractory)",
  #             "Carfilzomib (exposed vs. refractory)",
  #             "Pomalidomide (exposed vs. refractory)",
  #             "Daratumumab (exposed vs. refractory)"), 
  #           ~ case_when(
  #             . == 1                                              ~ "Refractory",
  #             . == 0                                              ~ "Exposed",
  #             TRUE                                                ~ NA_character_
  #           )) %>% 
  mutate(immuno = case_when(
    `Lenalidomide (exposed vs. refractory)` == "Exposed" &
      `Pomalidomide (exposed vs. refractory)` == "Exposed"        ~ "NO",
    `Lenalidomide (exposed vs. refractory)` == "Refractory" |
      `Pomalidomide (exposed vs. refractory)` == "Refractory"     ~ "YES"
  )) %>% 
  mutate(proteasome = case_when(
    `Bortezomib (exposed vs. refractory)` == "Exposed" &
      `Carfilzomib (exposed vs. refractory)` == "Exposed"      ~ "NO",
    `Bortezomib (exposed vs. refractory)` == "Refractory" |
      `Carfilzomib (exposed vs. refractory)` == "Refractory"   ~ "YES"
  )) %>% 
  mutate(dara = case_when(
    `Daratumumab (exposed vs. refractory)` == "Refractory"      ~ "YES",
    `Daratumumab (exposed vs. refractory)` == "Exposed"             ~ "NO"
  )) %>% 
  mutate(doubleref = case_when(
    proteasome == "NO" | 
      immuno == "NO"                                              ~ "NO",
    proteasome == "YES" &
      immuno == "YES"                                         ~ "YES"
  )) %>% 
  mutate(tripleref = case_when(
    proteasome == "NO" | 
      immuno == "NO" |
      `Daratumumab (exposed vs. refractory)` == "Exposed"      ~ "NO",
    proteasome == "YES" &
      immuno == "YES" &
      `Daratumumab (exposed vs. refractory)` == "Refractory"        ~ "YES"
  )) %>% 
  mutate(pentaref = case_when(
    `Bortezomib (exposed vs. refractory)` == "Exposed" | 
      `Carfilzomib (exposed vs. refractory)` == "Exposed" |
      `Lenalidomide (exposed vs. refractory)` == "Exposed" | 
      `Pomalidomide (exposed vs. refractory)` == "Exposed" | 
      `Daratumumab (exposed vs. refractory)` == "Exposed"     ~ "NO",
    `Bortezomib (exposed vs. refractory)` == "Refractory" & 
      `Carfilzomib (exposed vs. refractory)` == "Refractory" &
      `Lenalidomide (exposed vs. refractory)` == "Refractory" & 
      `Pomalidomide (exposed vs. refractory)` == "Refractory" & 
      `Daratumumab (exposed vs. refractory)` == "Refractory"  ~ "YES"
  )) %>% 
# CRS 
  mutate(CRS_any = ifelse(`Max CRS grade (0-5)` == 0, "NO", "YES"),
         CRS_any2 = ifelse(CRS_any== "NO", 0, 1),
         CRS_gradecat = case_when(
           `Max CRS grade (0-5)` == 0                             ~ "No CRS",
           `Max CRS grade (0-5)` == 1                             ~ "Grade 1 or 2",
           `Max CRS grade (0-5)` == 2                             ~ "Grade 1 or 2",
           `Max CRS grade (0-5)` >= 3                             ~ "Grade ≥3"),
         CRS_gradecat = factor(CRS_gradecat, levels = c("No CRS", "Grade 1 or 2", "Grade ≥3"))
  ) %>% 
  # mutate( = case_when(
  #    == 30                ~ NA,
  #   TRUE                          ~ CRS_fup
  # )) %>% 
  # ICANS 
  mutate(ICANS_any = ifelse(`Max ICANS (relative to infusion)` == 0, "NO", "YES"),
         ICANS_any2 = ifelse(ICANS_any == "NO", 0, 1),
         ICANS_gradecat = case_when(
           `Max ICANS (relative to infusion)` == 0 ~              "No ICANS",
           `Max ICANS (relative to infusion)` == 1 ~              "Grade 1 or 2",
           `Max ICANS (relative to infusion)` == 2 ~              "Grade 1 or 2",
           `Max ICANS (relative to infusion)` >= 3 ~              "Grade ≥3"),
         ICANS_gradecat = factor(ICANS_gradecat, levels = c("No ICANS", "Grade 1 or 2", "Grade ≥3"))
  ) %>% 
  # mutate(`marrow cellularity baseline` = case_when(
  #   `marrow cellularity baseline` == "\"patchy\""                 ~ "hyper",
  #   TRUE                                                          ~ `marrow cellularity baseline`
  # )) %>% 
  # mutate(`marrow cellularity day +30` = case_when(
  #   `marrow cellularity day +30` == "aplastic"                    ~ "hypo",
  #   TRUE                                                          ~ `marrow cellularity day +30`
  # )) %>% 
  # mutate(`Access type` = case_when(
  #   `Access type` == "Femoral"                                    ~ "Non-tunneled",
  #   `Access type` == "AVF"                                        ~ "Peripheral",
  #   TRUE                                                          ~ `Access type`
  # )) %>% 
  # mutate(best_response = ) %>% 
  # mutate(Leukopenia_apheresis = case_when(
  #   `WBC apheresis` < 4                                           ~ "YES",
  #   is.na(`WBC apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Leukopenia_-5d` = case_when(
  #   `WBC day -5 (k/ul)` < 4                                       ~ "YES",
  #   is.na(`WBC day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Leukopenia_0d` = case_when(
  #   `WBC day 0 (k/uL)` < 4                                        ~ "YES",
  #   is.na(`WBC day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Leukopenia_7d` = case_when(
  #   `WBC day +7` < 4                                              ~ "YES",
  #   is.na(`WBC day +7`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Leukopenia_14d` = case_when(
  #   `WBC day +14` < 4                                             ~ "YES",
  #   is.na(`WBC day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Leukopenia_21d` = case_when(
  #   `WBC day +21` < 4                                             ~ "YES",
  #   is.na(`WBC day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Leukopenia_30d` = case_when(
  #   `WBC day +30` < 4                                             ~ "YES",
  #   is.na(`WBC day +30`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Leukopenia_60d` = case_when(
  #   `WBC day +60` < 4                                             ~ "YES",
  #   is.na(`WBC day +60`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Leukopenia_90d` = case_when(
  #   `WBC day +90` < 4                                             ~ "YES",
  #   is.na(`WBC day +90`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(gr3_Leukopenia_apheresis = case_when(
  #   `WBC apheresis` < 2                                           ~ "YES",
  #   is.na(`WBC apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Leukopenia_-5d` = case_when(
  #   `WBC day -5 (k/ul)` < 2                                       ~ "YES",
  #   is.na(`WBC day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Leukopenia_0d` = case_when(
  #   `WBC day 0 (k/uL)` < 2                                        ~ "YES",
  #   is.na(`WBC day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Leukopenia_7d` = case_when(
  #   `WBC day +7` < 2                                              ~ "YES",
  #   is.na(`WBC day +7`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Leukopenia_14d` = case_when(
  #   `WBC day +14` < 2                                             ~ "YES",
  #   is.na(`WBC day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Leukopenia_21d` = case_when(
  #   `WBC day +21` < 2                                             ~ "YES",
  #   is.na(`WBC day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Leukopenia_30d` = case_when(
  #   `WBC day +30` < 2                                             ~ "YES",
  #   is.na(`WBC day +30`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Leukopenia_60d` = case_when(
  #   `WBC day +60` < 2                                             ~ "YES",
  #   is.na(`WBC day +60`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Leukopenia_90d` = case_when(
  #   `WBC day +90` < 2                                             ~ "YES",
  #   is.na(`WBC day +90`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>%

  # mutate(Neutropenia_apheresis = case_when(
  #   `ANC apheresis` < 1.8                                           ~ "YES",
  #   is.na(`ANC apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Neutropenia_-5d` = case_when(
  #   `ANC day -5 (k/ul)` < 1.8                                        ~ "YES",
  #   is.na(`ANC day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Neutropenia_0d` = case_when(
  #   `ANC day 0 (k/uL)` < 1.8                                        ~ "YES",
  #   is.na(`ANC day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`Neutropenia_7d` = case_when(
    `ANC Day 7` < 1.8                                              ~ "YES",
    is.na(`ANC Day 7`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  # mutate(`Neutropenia_14d` = case_when(
  #   `ANC day +14` < 1.8                                             ~ "YES",
  #   is.na(`ANC day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Neutropenia_21d` = case_when(
  #   `ANC day +21` < 1.8                                             ~ "YES",
  #   is.na(`ANC day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`Neutropenia_30d` = case_when(
    `ANC Day 30` < 1.8                                             ~ "YES",
    is.na(`ANC Day 30`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  mutate(`Neutropenia_60d` = case_when(
    `ANC Day 60` < 1.8                                             ~ "YES",
    is.na(`ANC Day 60`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  mutate(`Neutropenia_90d` = case_when(
    `ANC Day 90` < 1.8                                             ~ "YES",
    is.na(`ANC Day 90`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  # mutate(gr3_Neutropenia_apheresis = case_when(
  #   `ANC apheresis` < 1                                           ~ "YES",
  #   is.na(`ANC apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Neutropenia_-5d` = case_when(
  #   `ANC day -5 (k/ul)` < 1                                        ~ "YES",
  #   is.na(`ANC day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Neutropenia_0d` = case_when(
  #   `ANC day 0 (k/uL)` < 1                                        ~ "YES",
  #   is.na(`ANC day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`gr3_Neutropenia_7d` = case_when(
    `ANC Day 7` < 1                                              ~ "YES",
    is.na(`ANC Day 7`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  # mutate(`gr3_Neutropenia_14d` = case_when(
  #   `ANC day +14` < 1                                             ~ "YES",
  #   is.na(`ANC day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Neutropenia_21d` = case_when(
  #   `ANC day +21` < 1                                             ~ "YES",
  #   is.na(`ANC day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`gr3_Neutropenia_30d` = case_when(
    `ANC Day 30` < 1                                             ~ "YES",
    is.na(`ANC Day 30`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  mutate(`gr3_Neutropenia_60d` = case_when(
    `ANC Day 60` < 1                                             ~ "YES",
    is.na(`ANC Day 60`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  mutate(`gr3_Neutropenia_90d` = case_when(
    `ANC Day 90` < 1                                             ~ "YES",
    is.na(`ANC Day 90`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%

  # mutate(Anemia_apheresis = case_when(
  #   `Hb apheresis` < 11.4                                           ~ "YES",
  #   is.na(`Hb apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Anemia_-5d` = case_when(
  #   `Hb day -5 (k/ul)` < 11.4                                        ~ "YES",
  #   is.na(`Hb day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Anemia_0d` = case_when(
  #   `Hb day 0 (k/uL)` < 11.4                                        ~ "YES",
  #   is.na(`Hb day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Anemia_7d` = case_when(
  #   `Hb day +7` < 11.4                                              ~ "YES",
  #   is.na(`Hb day +7`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Anemia_14d` = case_when(
  #   `Hb day +14` < 11.4                                             ~ "YES",
  #   is.na(`Hb day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Anemia_21d` = case_when(
  #   `Hb day +21` < 11.4                                             ~ "YES",
  #   is.na(`Hb day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Anemia_30d` = case_when(
  #   `Hb day +30` < 11.4                                             ~ "YES",
  #   is.na(`Hb day +30`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Anemia_60d` = case_when(
  #   `Hb day +60` < 11.4                                             ~ "YES",
  #   is.na(`Hb day +60`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Anemia_90d` = case_when(
  #   `Hb day +90` < 11.4                                             ~ "YES",
  #   is.na(`Hb day +90`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(gr3_Anemia_apheresis = case_when(
  #   `Hb apheresis` < 8                                           ~ "YES",
  #   is.na(`Hb apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Anemia_-5d` = case_when(
  #   `Hb day -5 (k/ul)` < 8                                        ~ "YES",
  #   is.na(`Hb day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Anemia_0d` = case_when(
  #   `Hb day 0 (k/uL)` < 8                                        ~ "YES",
  #   is.na(`Hb day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Anemia_7d` = case_when(
  #   `Hb day +7` < 8                                              ~ "YES",
  #   is.na(`Hb day +7`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Anemia_14d` = case_when(
  #   `Hb day +14` < 8                                             ~ "YES",
  #   is.na(`Hb day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Anemia_21d` = case_when(
  #   `Hb day +21` < 8                                             ~ "YES",
  #   is.na(`Hb day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Anemia_30d` = case_when(
  #   `Hb day +30` < 8                                             ~ "YES",
  #   is.na(`Hb day +30`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Anemia_60d` = case_when(
  #   `Hb day +60` < 8                                             ~ "YES",
  #   is.na(`Hb day +60`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Anemia_90d` = case_when(
  #   `Hb day +90` < 8                                             ~ "YES",
  #   is.na(`Hb day +90`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # 
  # mutate(Thrombocytopenia_apheresis = case_when(
  #   `Plt apheresis` < 143                                           ~ "YES",
  #   is.na(`Plt apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Thrombocytopenia_-5d` = case_when(
  #   `Plt day -5 (k/ul)` < 143                                        ~ "YES",
  #   is.na(`Plt day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Thrombocytopenia_0d` = case_when(
  #   `Plt day 0 (k/uL)` < 143                                        ~ "YES",
  #   is.na(`Plt day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`Thrombocytopenia_7d` = case_when(
    `Platelets Day 7` < 143                                              ~ "YES",
    is.na(`Platelets Day 7`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  # mutate(`Thrombocytopenia_14d` = case_when(
  #   `Plt day +14` < 143                                             ~ "YES",
  #   is.na(`Plt day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Thrombocytopenia_21d` = case_when(
  #   `Plt day +21` < 143                                             ~ "YES",
  #   is.na(`Plt day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`Thrombocytopenia_30d` = case_when(
    `Plateletes Day 30` < 143                                             ~ "YES",
    is.na(`Plateletes Day 30`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`Thrombocytopenia_60d` = case_when(
    `Platelets Day 60` < 143                                             ~ "YES",
    is.na(`Platelets Day 60`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`Thrombocytopenia_90d` = case_when(
    `Platelets Day 90` < 143                                             ~ "YES",
    is.na(`Platelets Day 90`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  # mutate(gr3_Thrombocytopenia_apheresis = case_when(
  #   `Plt apheresis` < 50                                           ~ "YES",
  #   is.na(`Plt apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Thrombocytopenia_-5d` = case_when(
  #   `Plt day -5 (k/ul)` < 50                                        ~ "YES",
  #   is.na(`Plt day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Thrombocytopenia_0d` = case_when(
  #   `Plt day 0 (k/uL)` < 50                                        ~ "YES",
  #   is.na(`Plt day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`gr3_Thrombocytopenia_7d` = case_when(
    `Platelets Day 7` < 50                                              ~ "YES",
    is.na(`Platelets Day 7`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  # mutate(`gr3_Thrombocytopenia_14d` = case_when(
  #   `Plt day +14` < 50                                             ~ "YES",
  #   is.na(`Plt day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Thrombocytopenia_21d` = case_when(
  #   `Plt day +21` < 50                                             ~ "YES",
  #   is.na(`Plt day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`gr3_Thrombocytopenia_30d` = case_when(
    `Plateletes Day 30` < 50                                             ~ "YES",
    is.na(`Plateletes Day 30`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`gr3_Thrombocytopenia_60d` = case_when(
    `Platelets Day 60` < 50                                             ~ "YES",
    is.na(`Platelets Day 60`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`gr3_Thrombocytopenia_90d` = case_when(
    `Platelets Day 90` < 50                                             ~ "YES",
    is.na(`Platelets Day 90`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  # 
  # mutate(`cytopenia_30d` = case_when(
  #   `WBC day +30` < 4 | 
  #     `ANC Day 30` < 1.8 | 
  #     `Hb day +30` < 11.4 | 
  #     `Plateletes Day 30` < 143                                             ~ "YES",
  #   is.na(`WBC day +30`) |
  #     is.na(`ANC Day 30`) |
  #     is.na(`Hb day +30`) |
  #     is.na(`Plateletes Day 30`)                                            ~ NA_character_,
  #   TRUE                                                              ~ "NO"
  # )) %>% 
  # mutate(`gr3_cytopenia_30d` = case_when(
  #   `WBC day +30` < 2 | 
  #     `ANC Day 30` < 1 | 
  #     `Hb day +30` < 8 | 
  #     `Plateletes Day 30` < 50                                              ~ "YES",
  #   is.na(`WBC day +30`) |
  #     is.na(`ANC Day 30`) |
  #     is.na(`Hb day +30`) |
  #     is.na(`Plateletes Day 30`)                                            ~ NA_character_,
  #   TRUE                                                              ~ "NO"
  # )) %>% 
  # mutate(`gr3_cytopenia_90d` = case_when(
  #   `WBC day +90` < 2 | 
  #     `ANC Day 90` < 1 | 
  #     `Hb day +90` < 8 | 
  #     `Platelets Day 90` < 50                                             ~ "YES",
  #   is.na(`WBC day +90`) |
  #     is.na(`ANC Day 90`) |
  #     is.na(`Hb day +90`) |
  #     is.na(`Platelets Day 90`)                                            ~ NA_character_,
  #   TRUE                                                              ~ "NO"
  # )) %>% 
  # mutate(any_infection = case_when(
  #   `Infection (yes, no)` == 1                                    ~ "Yes",
  #   `Infection (yes, no)` == 0                                    ~ "No"
  # )) %>% 
  # mutate(any_sevinfection = case_when(
  #   `Severe Infection (yes, no)` == 1                              ~ "Yes",
  #   `Severe Infection (yes, no)` == 0                              ~ "No"
  # )) %>%

  mutate(`Day 30 Response (sCR, CR, VGPR, PR)` = case_when(
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "evaluable")   ~ NA_character_,
    `Day 30 Response (sCR, CR, VGPR, PR)` == "CR"	                   ~ "CR, MRD unknown",
    `Day 30 Response (sCR, CR, VGPR, PR)` == "CR, MRD+"	             ~ "CR, MRD+",

    `Day 30 Response (sCR, CR, VGPR, PR)` == "sCR, MRD+"           	 ~ "sCR, MRD+",
    `Day 30 Response (sCR, CR, VGPR, PR)` %in% c(
      "sCR MRD-", "sCR, MRD-")                                                         ~ "sCR, MRD-",

    `Day 30 Response (sCR, CR, VGPR, PR)` %in% c(
      "sCR", "sCR (flow neg, no clonoSEQ ID)", "sCR MRD - by flow/no clonoSEQ)",
      "sCR, MRD- by flow/no clonoSEQ)")                                                ~ "sCR, MRD unknown",

    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR)`
  )) %>% 
  mutate(ORR_30days = case_when(
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR")   ~ "ORR",
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "PR")   ~ "ORR",
    is.na(`Day 30 Response (sCR, CR, VGPR, PR)`)              ~ NA_character_,
    TRUE                                                                        ~ "PD/SD/MR"
  )) %>% 
  # mutate(MRDneg_30days = case_when(
  #   str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD-")        ~ "Yes",
  #   str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD")         ~ "No",
  #   TRUE                             ~ NA_character_
  # )) %>% 
  mutate(day30_response = case_when(
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "sCR")	       ~ "sCR",
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR")	         ~ "CR",
    is.na(`Day 30 Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR)`
  )) %>% 
  mutate(day30_response_group = case_when(
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR")	         ~ "CR or sCR",
    is.na(`Day 30 Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR)`
  )) %>% 
  mutate(day30_response_sCRvsOthers = case_when(
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR")	         ~ "CR or sCR",
    is.na(`Day 30 Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
    TRUE           ~ "Others"
  )) %>%

  mutate(`3 Month Response (sCR, CR, VGPR, PR)` = case_when(
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "evaluable")   ~ NA_character_,

    `3 Month Response (sCR, CR, VGPR, PR)` %in% c(
      "CR", "CR (no clonoSEQ/MRD as no marrow)")                                      ~ "CR, MRD unknown",

    `3 Month Response (sCR, CR, VGPR, PR)` %in% c(
      "sCR (clonoSEQ pending, flow neg)", 
      "sCR (no clonoSEQ for MRD, flow suspicious for MRD)",
      "sCR (no clonoSEQ, flow neg)")                                                  ~ "sCR, MRD unknown",

    `3 Month Response (sCR, CR, VGPR, PR)` %in% c(
      "sCR, MRD - (by flow+)", "sCR, MRD-	12 (24%)")                                  ~ "sCR, MRD-",

    `3 Month Response (sCR, CR, VGPR, PR)` == "sCR, MRD+"	            ~	"sCR, MRD+",

    TRUE           ~ `3 Month Response (sCR, CR, VGPR, PR)`
  )) %>% 
  mutate(ORR_90days = case_when(
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "CR")    ~ "ORR",
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "PR")    ~ "ORR",
    is.na(`3 Month Response (sCR, CR, VGPR, PR)`)               ~ NA_character_,
    TRUE                                                                        ~ "PD/SD/MR"
  )) %>% 
  # mutate(MRDneg_90days = case_when(
  #   str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD-")        ~ "Yes",
  #   str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD")         ~ "No",
  #   TRUE                             ~ NA_character_
  # )) %>% 
  mutate(day90_response_group = case_when(
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "CR")	        ~ "CR or sCR",
    is.na(`3 Month Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
    TRUE           ~ `3 Month Response (sCR, CR, VGPR, PR)`
  )) %>% 
  mutate(day90_response = case_when(
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "sCR")	        ~ "sCR",
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "CR")	        ~ "CR",
    is.na(`3 Month Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
    TRUE           ~ `3 Month Response (sCR, CR, VGPR, PR)`
  )) %>% 
  mutate(day90_response_sCRvsOthers = case_when(
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "CR")	         ~ "CR or sCR",
    is.na(`3 Month Response (sCR, CR, VGPR, PR)`)                      ~ NA_character_,
    TRUE           ~ "Others"
  )) %>% 
  mutate(best_response = case_when(
    day30_response_group == "CR or sCR" |
      day90_response_group == "CR or sCR"                                             ~ "CR or sCR",
    day30_response_group == "VGPR" |
      day90_response_group == "VGPR"                                                  ~ "VGPR",
    day30_response_group == "PR" |
      day90_response_group == "PR"                                                    ~ "PR",
    TRUE                                                                        ~ NA_character_
  )) %>% 
  mutate(MRDneg_in_best_response = case_when(
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD-") |
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD-")        ~ "Yes",
    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD") |
    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD")         ~ "No",
    TRUE                             ~ NA_character_
  ))# %>%

  # mutate(`IgG HSV1/2 apheresis` = case_when(
  #   `IgG HSV1/2 apheresis` < 0.9         ~ "Negative",
  #   `IgG HSV1/2 apheresis` >= 0.9 &
  #     `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
  #   `IgG HSV1/2 apheresis` >= 1.10       ~ "Positive",
  # )) %>%
  # mutate(`IgG HSV1/2 D90` = case_when(
  #   `IgG HSV1/2 D90` < 0.9         ~ "Negative",
  #   `IgG HSV1/2 D90` >= 0.9 &
  #     `IgG HSV1/2 D90` < 1.10      ~ "indeterminate",
  #   `IgG HSV1/2 D90` >= 1.10       ~ "Positive",
  # )) %>% 
  # mutate_at(c("VZV IgG apheresis",
  #             "VZV IgG D90 (1=pos, 0=neg)",
  #             "CMV IgG apheresis",
  #             "CMV IgG D90 (1=pos, 0=neg)"), 
  #           ~ case_when(
  #             . == 1                                              ~ "Positive",
  #             . == 0                                              ~ "Negative",
  #             . == "Equivocal"                                    ~ "Negative",
  #             TRUE                                                ~ as.character(.)
  #           )) %>% 
  # mutate_at(c("IgG HSV1/2 apheresis",
  #             "IgG HSV1/2 D90",
  #             "VZV IgG apheresis",
  #             "VZV IgG D90 (1=pos, 0=neg)",
  #             "CMV IgG apheresis",
  #             "CMV IgG D90 (1=pos, 0=neg)"),
  #           ~ factor(., levels = c("Positive", "Negative"))) %>% 
  # mutate(across(starts_with("Pneumo"), ~ case_when(
  #   . <= 1                                                    ~ "Negative",
  #   . > 1                                                     ~ "Positive"
  # ))) %>% 
  # 
  # mutate(igg_hsv_change = case_when(
  #   `IgG HSV1/2 apheresis` == "Positive" &
  #     `IgG HSV1/2 D90` == "Negative"         ~ -1,
  #   `IgG HSV1/2 apheresis` == "Negative" &
  #     `IgG HSV1/2 D90` == "Positive"         ~ 1,
  #   `IgG HSV1/2 apheresis` == "Negative" &
  #     `IgG HSV1/2 D90` == "Negative"         ~ -0.25,
  #   `IgG HSV1/2 apheresis` == "Positive" &
  #     `IgG HSV1/2 D90` == "Positive"         ~ 0.25
  # )) %>% 
  # mutate(igg_vzv_change = case_when(
  #   `VZV IgG apheresis` == "Positive" &
  #     `VZV IgG D90 (1=pos, 0=neg)` == "Negative"               ~ -1,
  #   `VZV IgG apheresis` == "Negative" &
  #     `VZV IgG D90 (1=pos, 0=neg)` == "Positive"               ~ 1,
  #   `VZV IgG apheresis` == "Negative" &
  #     `VZV IgG D90 (1=pos, 0=neg)` == "Negative"               ~ -0.25,
  #   `VZV IgG apheresis` == "Positive" &
  #     `VZV IgG D90 (1=pos, 0=neg)` == "Positive"               ~ 0.25
  # )) %>% 
  # mutate(igg_cmv_change = case_when(
  #   `CMV IgG apheresis` == "Positive" &
  #     `CMV IgG D90 (1=pos, 0=neg)` == "Negative"               ~ -1,
  #   `CMV IgG apheresis` == "Negative" &
  #     `CMV IgG D90 (1=pos, 0=neg)` == "Positive"               ~ 1,
  #   `CMV IgG apheresis` == "Negative" &
  #     `CMV IgG D90 (1=pos, 0=neg)` == "Negative"               ~ -0.25,
  #   `CMV IgG apheresis` == "Positive" &
  #     `CMV IgG D90 (1=pos, 0=neg)` == "Positive"               ~ 0.25
  # ))

# Create Pneumo titers change value
# for (i in colnames(cart0 %>%
#                    select(c(starts_with("Pneumo"))))) {
# 
#   pneumo_type <-
#     str_match(i, ".*(apheresis|D90)")[, 1] %>% 
#     # str_replace_all(., " ", "_") %>% 
#     str_remove(., " apheresis| D90")
#   
#   pneumo_subset <- cart0 %>% select(patient_id, starts_with(pneumo_type))
#   
#   pneumo_type <-
#     str_replace_all(pneumo_type, " ", "_")
#   # day <-
#   #   str_match(i, ".*(apheresis|D90)")[, 2]
#  
#   name <- paste0(pneumo_type, "_", "change")
# 
#   cart0[[paste0(pneumo_type, "_", "change")]] <-  case_when(
#     pneumo_subset[2] == "Positive" &
#       pneumo_subset[3] == "Negative"               ~ -1,
#     pneumo_subset[2] == "Negative" &
#       pneumo_subset[3] == "Positive"               ~ 1,
#     pneumo_subset[2] == "Negative" &
#       pneumo_subset[3] == "Negative"               ~ -0.25,
#     pneumo_subset[2] == "Positive" &
#       pneumo_subset[3] == "Positive"               ~ 0.25
#   )
# }

# # CrCl
# table(cart$`Baseline CrCl`)
# cart$crcl[cart$`Baseline CrCl` == ">70" | cart$`Baseline CrCl` == "60.8" | cart$`Baseline CrCl` == "62" | cart$`Baseline CrCl` == "67"] <- ">60"
# cart$crcl[cart$`Baseline CrCl` == "25" | cart$`Baseline CrCl` == "27" | cart$`Baseline CrCl` == "34" | cart$`Baseline CrCl` == "41" | cart$`Baseline CrCl` == "43" | cart$`Baseline CrCl` == "50" | cart$`Baseline CrCl` == "54" | cart$`Baseline CrCl` == "55"] <- "≤60"
# table(cart$crcl)
# # CRS
# table(cart$`Max CRS grade (0-5)`)
# as.factor(cart$`Max CRS grade (0-5)`)
# table(cart$`Duration of CRS (days)`)
# table(cart$`Duration of ICANS (days)`)
# # steroid use
# table(cart$`Steroid use(Yes, No)`)
# 
# 
# 
# # dose reduction
# cart$`Fludarabine Dose Reduction`[cart$`Fludarabine Dose Reduction` == "YES (HD)"] <- "YES"
# table(cart$`Fludarabine Dose Reduction`)
# 
# # RSS
# table(cart$`R-ISS at CAR-T infusion`)
# cart$`R-ISS at CAR-T infusion`[cart$`R-ISS at CAR-T infusion` == "R-ISS  II"] <- "R-ISS II"

# day 30 + MRD for figure
#table(tct$day30_response_revised, tct$MRD_status, useNA= "ifany")
#table(tct$day30_response_revised, tct$day30_response, useNA= "ifany")
#tct$ORR_MRD <- case_when(#tct$day30_response_revised== "SD" ~ "SD",
                         #tct$day30_response_revised== "PD" ~ "PD",
                         #tct$day30_response_revised== "MR" ~ "MR",
#                         tct$day30_response_revised== "PR" ~ "PR",
                         #tct$day30_response_revised== "PR" & tct$MRD_status== "Positive" ~ "PR and MRD-Positive",
                         #tct$day30_response_revised== "PR" & is.na(tct$MRD_status) ~ "PR and MRD unknown",
#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Negative" ~ "sCR and MRD-Negative",
#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Positive" ~ "sCR and MRD-Positive")
#table(tct$ORR_MRD)
```

```{r}
## Labeling
# var_label(cart0) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", 
#                          `Extramedullary Disease? (Yes, No)` = "Extramedullary disease", 
#                          `High Marrow Burden (>= 50%)` = "High marrow burden (≥50%)",
#                          # bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
#                          proteasome = "Refractory to Proteasome Inhibitors", 
#                          immuno = "Refractory to Immunomodulators", doubleref = "Double refractory", 
#                          tripleref= "Triple refractory", pentaref= "Penta refractory",
#                          # bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese", 
#                          CRS_any = "Any CRS", CRS_gradecat = "CRS Grade", 
#                          ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", cyto= "High risk cytogenetics", 
#                          # `ECOG > or = 2? (Yes=1, No=0)` ,
#                          `Deletion 17p prior to CAR-T infusion (yes, no)` = "Deletion 17p at Infusion", 
#                          `t(4:14) prior to CAR-T infusion (yes, no)` = "t(4:14) at Infusion", `t(14:16) prior to CAR-T infusion (yes, no)` = "t(4:16) at Infusion", 
#                          `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` = "Prior BCMA-directed therapy",
#                          `Prior auto SCT (yes, no)` = "Prior autoSCT", 
#                          `Prior Allo SCT (Yes=1, No=0)` = "Prior alloSCT",
#                          # `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` = "Prior BCMA-directed therapy ",
#                          dara= "Refractory to Daratumumab"#,
#                          # best_response = "Best response in first 90 days"
# )

```

<br>

### Tables

## Table 1. Patient baseline characteristics
```{r}
cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         # cyto, 
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Prior auto SCT (yes, no)`, 
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         `Did patient met criteria for KarMMa1 pre-CAR-T?`) %>% 
  tbl_summary(
    type = list(
      c(`Extramedullary Disease? (Yes, No)`, `High Marrow Burden (>= 50%)`,
    #     cyto, 
    `Deletion 17p prior to CAR-T infusion (yes, no)`,
        `t(4:14) prior to CAR-T infusion (yes, no)`,
        `t(14:16) prior to CAR-T infusion (yes, no)`,
        `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
        immuno, proteasome, dara, doubleref, tripleref, pentaref,
        `Did patient met criteria for KarMMa1 pre-CAR-T?`)
      ~"categorical"),

    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## Table 2. Clinical outcomes
**best response**
```{r}
tbl1 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(`Max CRS grade (0-5)`,
         # `Day of onset of CRS relative to infusion`,
         `Day of Max CRS (relative to infusion)`,

         `Max ICANS (relative to infusion)`,
         # `Day of onset of ICANS relative to infusion`,
         `Day of Max ICANS (relative to infusion)`) %>% 
  tbl_summary(type = list(
    c(
      `Day of Max ICANS (relative to infusion)`) ~ "continuous"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1,
    missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)

tbl2 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
         `Anakinra (Yes, No)`) %>% 
  tbl_summary(type = list(
    c(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
      `Anakinra (Yes, No)`) ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_stat_label()

tbl3 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(#MRDneg_30days,
         ORR_30days,
         day30_response,
         day30_response_group) %>% 
  tbl_summary(#type = list(
    # c(MRDneg_30days) ~ "categorical"),
    digits = all_continuous() ~ 1,
    missing = "no") %>% 
  bold_labels() %>% add_stat_label()

# tbl4 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(day30_response_group == "CR or sCR") %>% 
#   select(MRDneg_30days) %>% 
#   tbl_summary(type = list(c(MRDneg_30days) ~ "categorical"),
#               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
#               digits = all_continuous() ~ 1,
#               missing = "no") %>% 
#   bold_labels() %>% add_stat_label()

tbl5 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(#MRDneg_90days,
         ORR_90days,
         day90_response,
         day90_response_group) %>% 
  tbl_summary(#type = list(
    # c(MRDneg_90days) ~ "categorical"),
    digits = all_continuous() ~ 1,
    missing = "no") %>% 
  bold_labels() %>% add_stat_label()

# tbl6 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(day90_response_group == "CR or sCR") %>% 
#   select(MRDneg_90days) %>% 
#   tbl_summary(type = list(c(MRDneg_90days) ~ "categorical"),
#               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
#               digits = all_continuous() ~ 1,
#               missing = "no") %>% 
#   bold_labels() %>% add_stat_label()

tbl7 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(best_response) %>% 
  tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"),
              label = list(best_response ~ "best response in the first 90 days"),
              digits = all_continuous() ~ 1,
              missing = "no") %>% 
  bold_labels() %>% add_stat_label()

tbl8 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  filter(best_response == "CR or sCR") %>% 
  select(MRDneg_in_best_response) %>% 
  tbl_summary(type = list(c(MRDneg_in_best_response) ~ "categorical"),
              label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              missing = "no") %>% 
  bold_labels() %>% add_stat_label()

tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() %>%
  gt::tab_source_note(gt::md("**
                             **"))

```

For responses make denominator evaluable patients
Patient who died or was lost to follow-up or had non-secretory disease would not be evaluable

## Table 3. Bone marrow biopsy findings
```{r}
# tbl1 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select("marrow cellularity" = `marrow cellularity baseline`, 
#          "marrow cellularity (%)" = `marrow cellularity baseline (%)`,
#          "% CD138 positive by IHC" = `marrow CD138 baseline (%)`, 
#          "Fibrosis grade" = `marrow fibrosis baseline`, 
#          "Dysplasia present" = `marrow dysplasia baseline`
#   ) %>% 
#   tbl_summary(type = list(
#     c(#`marrow cellularity baseline (%)`, `marrow CD138 baseline (%)`, 
#       `Fibrosis grade`) ~ "continuous"
#   ),
#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#             digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# tbl2 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select("marrow cellularity" = `marrow cellularity day +30`, 
#          "marrow cellularity (%)" = `marrow % cellularity day +30`,
#          "% CD138 positive by IHC" = `marrow %CD138 day +30`, 
#          "Fibrosis grade" = `marrow fibrosis day +30`, 
#          "Dysplasia present" = `marrow dysplasia day +30`
#   ) %>% 
#   mutate(`marrow cellularity (%)` = as.numeric(`marrow cellularity (%)`)) %>% 
#   mutate(`% CD138 positive by IHC` = as.numeric(`% CD138 positive by IHC`)) %>% 
#   mutate(`Fibrosis grade` = as.numeric(`Fibrosis grade`)) %>% 
#   mutate(`Dysplasia present` = as.numeric(`Dysplasia present`)) %>% 
#   tbl_summary(type = list(
#     c(`marrow cellularity (%)`, `% CD138 positive by IHC`, 
#       `Fibrosis grade`) ~ "continuous"
#   ),
#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#             digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# tbl3 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select("marrow cellularity" = `marrow cellularity day +90`, 
#          "marrow cellularity (%)" = `marrow % cellularity day +90`,
#          "% CD138 positive by IHC" = `marrow %CD138 day +90`, 
#          "Fibrosis grade" = `marrow fibrosis day +90`, 
#          "Dysplasia present" = `marrow dysplasia day +90`
#   ) %>% 
#   mutate(`marrow cellularity (%)` = as.numeric(`marrow cellularity (%)`)) %>% 
#   mutate(`% CD138 positive by IHC` = as.numeric(`% CD138 positive by IHC`)) %>% 
#   mutate(`Fibrosis grade` = as.numeric(`Fibrosis grade`)) %>% 
#   mutate(`Dysplasia present` = as.numeric(`Dysplasia present`)) %>% 
#   tbl_summary(type = list(
#     c(`marrow cellularity (%)`, `% CD138 positive by IHC`, 
#       `Fibrosis grade`) ~ "continuous"
#   ),
#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#             digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# tbl_merge(list(tbl1, tbl2, tbl3), tab_spanner = c("Baseline", "Day 30", "Day 90"))
```

## Table 4. Supportive therapies and engraftment
Jenn

```{r}
# cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select(`Need for G-CSF post infus (Yes, No)`, `First Day of GCSF`, `Last Day of GCSF`,
#          `CD34 stem cell boost`, `Day of stem cell boost`, `Boost cell dose (million cells)`,
#          `Engraftment Day`,
#          `RBC transfusion within 7d post CART`, `Plt transfusion within 7d post CART`, 
#          `RBC transfusion >7d post CART`, `Plt transfusion >7d post CART`,
#          `Need for IVIG (Yes, No)`, `First day of IVIG`, `Last day of IVIG`
#   ) %>% 
#   tbl_summary(type = list(
#     c(`Day of stem cell boost`, `Boost cell dose (million cells)`,
#     `Last day of IVIG`) ~ "continuous",
#     c(`Need for G-CSF post infus (Yes, No)`,
#       `CD34 stem cell boost`,
#       `RBC transfusion within 7d post CART`, `Plt transfusion within 7d post CART`, 
#          `RBC transfusion >7d post CART`, `Plt transfusion >7d post CART`,
#       `Need for IVIG (Yes, No)`) ~ "categorical"
#   ),
#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#             digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
```

## Table S1. Apheresis and product characteristics
```{r}
# cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select(TBV, `Whole blood processed (mL)`,
#          `Final collection volume (mL)`, 
#          `TBV processed`, 
#          `Access type`, `Final collection volume (mL)`,
#          `Run time (min)`,
#          `Time from apheresis to CAR-T infusion (days)`, `Total bags`,
#          `Total dose volume (mL)`, `Total cell dose (million cells)`
#          
#   ) %>% 
#   tbl_summary(type = list(c(TBV, `Total bags`) ~ "continuous"),
#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#             digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
```

## Table S2. Cytopenias following ide-cel
**NAs are the patients who died (black) and test was not done (grey), they are remove from the denom (%) but not from the the N**

```{r}
# tbl1 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select("Leukopenia" = `Leukopenia_apheresis`, 
#          "Grade3+ Leukopenia" = `gr3_Leukopenia_apheresis`, 
#          "Neutropenia" = `Neutropenia_apheresis`, 
#          "Grade3+ Neutropenia" = `gr3_Neutropenia_apheresis`, 
#          "Anemia" = `Anemia_apheresis`, 
#          "Grade3+ Anemia" = `gr3_Anemia_apheresis`, 
#          "Thrombocytopenia" = `Thrombocytopenia_apheresis`, 
#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_apheresis`
#   ) %>% 
#   tbl_summary(type = list(everything() ~ "dichotomous"),
#             digits = all_continuous() ~ 1#,
#             # missing = "no"
#             ) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# tbl2 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select("Leukopenia" = `Leukopenia_-5d`, 
#          "Grade3+ Leukopenia" = `gr3_Leukopenia_-5d`, 
#          "Neutropenia" = `Neutropenia_-5d`, 
#          "Grade3+ Neutropenia" = `gr3_Neutropenia_-5d`,
#          "Anemia" = `Anemia_-5d`, 
#          "Grade3+ Anemia" = `gr3_Anemia_-5d`, 
#          "Thrombocytopenia" = `Thrombocytopenia_-5d`, 
#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_-5d`
#   ) %>% 
#   tbl_summary(type = list(everything() ~ "dichotomous"),
#             digits = all_continuous() ~ 1#,
#             # missing = "no"
#             ) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# tbl3 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select("Leukopenia" = `Leukopenia_0d`, 
#          "Grade3+ Leukopenia" = `gr3_Leukopenia_0d`, 
#          "Neutropenia" = `Neutropenia_0d`, 
#          "Grade3+ Neutropenia" = `gr3_Neutropenia_0d`, 
#          "Anemia" = `Anemia_0d`, 
#          "Grade3+ Anemia" = `gr3_Anemia_0d`,
#          "Thrombocytopenia" = `Thrombocytopenia_0d`, 
#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_0d`
#   ) %>% 
#   tbl_summary(type = list(everything() ~ "dichotomous"),
#             digits = all_continuous() ~ 1#,
#             # missing = "no"
#             ) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)

tbl4 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(#"Leukopenia" = `Leukopenia_7d`, 
         # "Grade3+ Leukopenia" = `gr3_Leukopenia_7d`, 
         "Neutropenia" = `Neutropenia_7d`, 
         "Grade3+ Neutropenia" = `gr3_Neutropenia_7d`, 
         # "Anemia" = `Anemia_7d`, 
         # "Grade3+ Anemia" = `gr3_Anemia_7d`, 
         "Thrombocytopenia" = `Thrombocytopenia_7d`, 
         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_7d`
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
            digits = all_continuous() ~ 1#,
            # missing = "no"
            ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)

# tbl5 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(is.na(Not_evaluable_at_14days)) %>% 
#   select("Leukopenia" = `Leukopenia_14d`, 
#          "Grade3+ Leukopenia" = `gr3_Leukopenia_14d`, 
#          "Neutropenia" = `Neutropenia_14d`, 
#          "Grade3+ Neutropenia" = `gr3_Neutropenia_14d`,
#          "Anemia" = `Anemia_14d`, 
#          "Grade3+ Anemia" = `gr3_Anemia_14d`,
#          "Thrombocytopenia" = `Thrombocytopenia_14d`, 
#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_14d` 
#   ) %>% 
#   tbl_summary(type = list(everything() ~ "dichotomous"),
#             digits = all_continuous() ~ 1#,
#             # missing = "no"
#             ) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# tbl6 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(is.na(Not_evaluable_at_21days)) %>% 
#   select("Leukopenia" = `Leukopenia_21d`,
#          "Grade3+ Leukopenia" = `gr3_Leukopenia_21d`, 
#          "Neutropenia" = `Neutropenia_21d`, 
#          "Grade3+ Neutropenia" = `gr3_Neutropenia_21d`, 
#          "Anemia" = `Anemia_21d`, 
#          "Grade3+ Anemia" = `gr3_Anemia_21d`,
#          "Thrombocytopenia" = `Thrombocytopenia_21d`, 
#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_21d`
#   ) %>% 
#   tbl_summary(type = list(everything() ~ "dichotomous"),
#             digits = all_continuous() ~ 1#,
#             # missing = "no"
#             ) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)

tbl7 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  filter(is.na(Not_evaluable_at_30days)) %>% 
  select(#"Leukopenia" = `Leukopenia_30d`, 
         # "Grade3+ Leukopenia" = `gr3_Leukopenia_30d`,
         "Neutropenia" = `Neutropenia_30d`, 
         "Grade3+ Neutropenia" = `gr3_Neutropenia_30d`,
         # "Anemia" = `Anemia_30d`, 
         # "Grade3+ Anemia" = `gr3_Anemia_30d`, 
         "Thrombocytopenia" = `Thrombocytopenia_30d`,
         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_30d` 
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
            digits = all_continuous() ~ 1#,
            # missing = "no"
            ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)

tbl8 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  filter(is.na(Not_evaluable_at_90days)) %>% 
  select(#"Leukopenia" = `Leukopenia_90d`, 
         # "Grade3+ Leukopenia" = `gr3_Leukopenia_90d`,
         "Neutropenia" = `Neutropenia_90d`, 
         "Grade3+ Neutropenia" = `gr3_Neutropenia_90d`,
         # "Anemia" = `Anemia_90d`,
         # "Grade3+ Anemia" = `gr3_Anemia_90d`,
         "Thrombocytopenia" = `Thrombocytopenia_90d`, 
         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_90d`
  ) %>% 
  tbl_summary(type = list(everything() ~ "dichotomous"),
            digits = all_continuous() ~ 1#,
            # missing = "no"
            ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)

tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), 
          tab_spanner = c("Apheresis", "Day -5",	"Day 0",	"Day 7",	"Day 14",	"Day 21",	"Day 30",	"Day 90")) %>% as_gt() %>%
  gt::tab_source_note(gt::md("**Not evaluable patients are removed from the denominator <br>
                             1 patient has missing 90 days values**"))
```

## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30
**Make sure that if one of wbc, anc, hb or plt is NA then cytopenia should be NA**
```{r}
# cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(is.na(Not_evaluable_at_30days)) %>% 
#   select(Age, agecat, male_sex, Sex,
#          `Extramedullary Disease? (Yes, No)`, 
#          `High Marrow Burden (>= 50%)`, `ECOG at LD`, `R-ISS at CAR-T infusion`, #cyto, 
#          `Bridging Therapy? (Yes, No)`,
#          `Prior auto SCT (yes, no)`, 
#          `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
#          immuno, proteasome, dara, doubleref, tripleref, pentaref, 
#          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
#          `gr3_cytopenia_30d`) %>% 
#   tbl_summary(by = `gr3_cytopenia_30d`,
#     type = list(
#     `Extramedullary Disease? (Yes, No)` ~ "categorical",
#     # cyto ~ "categorical",
#     `Bridging Therapy? (Yes, No)` ~ "categorical",
#     `Prior auto SCT (yes, no)` ~ "categorical",
#     immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
#     doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
#     `Did patient met criteria for KarMMa1 pre-CAR-T?` ~"categorical"),
#     
#     statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
#     digits = all_continuous() ~ 1
#     ) %>% 
#   bold_labels() %>% add_stat_label() %>% add_p() %>% 
#   modify_footnote(update = everything() ~ NA) %>%
#   modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
```

## Table S3. Patient characteristics by grade 3+ cytopenia at Day 90
```{r}
# cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(is.na(Not_evaluable_at_90days)) %>% 
#   select(Age, agecat, male_sex, Sex,
#          `Extramedullary Disease? (Yes, No)`, 
#          `High Marrow Burden (>= 50%)`, `ECOG at LD`, `R-ISS at CAR-T infusion`, #cyto, 
#          `Bridging Therapy? (Yes, No)`,
#          `Prior auto SCT (yes, no)`,
#          `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
#          immuno, proteasome, dara, doubleref, tripleref, pentaref, 
#          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
#          `gr3_cytopenia_90d`) %>% 
#   tbl_summary(by = `gr3_cytopenia_90d`,
#     type = list(
#     `Extramedullary Disease? (Yes, No)` ~ "categorical",
#     cyto ~ "categorical",
#     `Bridging Therapy? (Yes, No)` ~ "categorical",
#     `Prior auto SCT (yes, no)` ~ "categorical",
#     immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
#     doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
#     `Did patient met criteria for KarMMa1 pre-CAR-T?` ~"categorical"),
#     
#     statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
#     digits = all_continuous() ~ 1
#     ) %>% 
#   bold_labels() %>% add_stat_label() %>%  add_p() %>% 
#   modify_footnote(update = everything() ~ NA) %>%
#   modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 90?**")
```

## Table S4. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
```{r}
# tbl1 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(is.na(Not_evaluable_at_30days)) %>% 
#   select(CRS_gradecat,
#          `Day of onset of CRS relative to infusion`,
#          `Day of Max CRS (relative to infusion)`, `Duration of CRS (days)`, 
#          
#          ICANS_gradecat,
#          `Day of onset of ICANS relative to infusion`,
#          `Day of Max ICANS (relative to infusion)`,
#          `Duration of ICANS (days)`, gr3_cytopenia_30d) %>% 
#   tbl_summary(by =`gr3_cytopenia_30d`,
#               type = list(
#     c(`Day of onset of CRS relative to infusion`, 
#       `Day of Max CRS (relative to infusion)`,
#       `Day of onset of ICANS relative to infusion`,
#       `Day of Max ICANS (relative to infusion)`, `Duration of ICANS (days)`) ~ "continuous"),
#     statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#     digits = all_continuous() ~ 1,
#     missing = "no") %>% 
#   bold_labels() %>% add_stat_label() %>% add_p() %>% 
#   modify_footnote(update = everything() ~ NA) %>%
#   modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
# 
# tbl2 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(is.na(Not_evaluable_at_30days)) %>% 
#   select(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, 
#          `Anakinra (Yes=1, No=0)`, gr3_cytopenia_30d) %>% 
#   tbl_summary(by =`gr3_cytopenia_30d`,
#               type = list(
#     c(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, 
#       `Anakinra (Yes=1, No=0)`) ~ "categorical"),
#     statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#     digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label() %>% add_p()
# 
# tbl3 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(is.na(Not_evaluable_at_30days)) %>% 
#   select(#MRDneg_30days,
#          ORR_30days, day30_response_sCRvsOthers,
#          day30_response_group, gr3_cytopenia_30d) %>% 
#   tbl_summary(by =`gr3_cytopenia_30d`,
#     #           type = list(
#     # c(MRDneg_30days) ~ "categorical"),
#     digits = all_continuous() ~ 1,
#     missing = "no") %>% 
#   bold_labels() %>% add_stat_label() %>% add_p()
# 
# # tbl4 <- cart0 %>% 
# #   distinct(patient_id, .keep_all = TRUE) %>% 
# #   filter(is.na(Not_evaluable_at_30days)) %>% 
# #   filter(day30_response_group == "CR or sCR") %>% 
# #   select(MRDneg_30days, gr3_cytopenia_30d) %>% 
# #   tbl_summary(by =`gr3_cytopenia_30d`,
# #               type = list(c(MRDneg_30days) ~ "categorical"),
# #               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
# #               digits = all_continuous() ~ 1,
# #               missing = "no") %>% 
# #   bold_labels() %>% add_stat_label() %>% add_p()
# 
# tbl5 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(is.na(Not_evaluable_at_30days)) %>% 
#   select(#MRDneg_90days,
#          ORR_90days, day90_response_sCRvsOthers,
#          day90_response_group, gr3_cytopenia_30d) %>% 
#   tbl_summary(by =`gr3_cytopenia_30d`,
#     #           type = list(
#     # c(MRDneg_90days) ~ "categorical"),
#     digits = all_continuous() ~ 1,
#     missing = "no") %>% 
#   bold_labels() %>% add_stat_label() %>% add_p()
# 
# # tbl6 <- cart0 %>% 
# #   distinct(patient_id, .keep_all = TRUE) %>% 
# #   filter(is.na(Not_evaluable_at_30days)) %>% 
# #   filter(day90_response_group == "CR or sCR") %>% 
# #   select(MRDneg_90days, gr3_cytopenia_30d) %>% 
# #   tbl_summary(by =`gr3_cytopenia_30d`,
# #               type = list(c(MRDneg_90days) ~ "categorical"),
# #               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
# #               digits = all_continuous() ~ 1,
# #               missing = "no") %>% 
# #   bold_labels() %>% add_stat_label() %>% add_p()
# 
# tbl7 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(is.na(Not_evaluable_at_30days)) %>% 
#   select(best_response, gr3_cytopenia_30d) %>% 
#   tbl_summary(by =`gr3_cytopenia_30d`,
#               #type = list(c(MRDneg_90days) ~ "categorical"),
#               label = list(best_response ~ "best response in the first 90 days"),
#               digits = all_continuous() ~ 1,
#               missing = "no") %>% 
#   bold_labels() %>% add_stat_label() %>% add_p()
# 
# # tbl8 <- cart0 %>% 
# #   distinct(patient_id, .keep_all = TRUE) %>% 
# #   filter(is.na(Not_evaluable_at_30days)) %>% 
# #   filter(best_response == "CR or sCR") %>% 
# #   select(MRDneg_in_best_response, gr3_cytopenia_30d) %>% 
# #   tbl_summary(by =`gr3_cytopenia_30d`,
# #               type = list(c(MRDneg_in_best_response) ~ "categorical"),
# #               label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
# #               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
# #               digits = all_continuous() ~ 1,
# #               missing = "no") %>% 
# #   bold_labels() %>% add_stat_label() %>% add_p()
# 
# tbl_stack(list(tbl1, tbl2, tbl3, tbl5, tbl7))
```

## Table S4. Details of infections after ide-cel
Jenn

## Table S5. Patients with infections in the first 30 days by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
```{r}
cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(CRS_gradecat, ICANS_gradecat,
         `Steroid use (Yes=1, No=0)`, 
         `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`,
         `Bridging Therapy? (Yes, No)`, any_infection) %>% 
  tbl_summary(by=any_infection, 
              type = list(all_dichotomous() ~ "categorical")) %>%
  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Any infection**")

cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(CRS_gradecat, ICANS_gradecat,
         `Steroid use (Yes=1, No=0)`, 
         `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`,
         `Bridging Therapy? (Yes, No)`, any_sevinfection) %>% 
  tbl_summary(by=any_sevinfection, 
              type = list(all_dichotomous() ~ "categorical")) %>%
  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
```

## Table S6. Patients with infections in the first 100 days by cell counts and immunoglobulin levels
```{r}
cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(`IgG day -5`, `IgA day -5`, `IgM day -5`,
         `WBC day -5 (k/ul)`, `ANC day -5 (k/ul)`,
         `Eos day -5 (k/ul)`, `Monos day -5 (k/ul)`,
         `CD3 apheresis`, `CD4 apheresis`, `CD8 apheresis`,
         `CD56 apheresis`, `CD19 apheresis`, 
         `CD3 day +90`, `CD4 day +90`, `CD8 day +90`,
         `CD56 day +90`, `CD19 day +90`,
         any_infection) %>%

  tbl_summary(by = any_infection,

              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1) %>% 
  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Any infection**")

cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(`IgG day -5`, `IgA day -5`, `IgM day -5`,
         `WBC apheresis`, `ANC apheresis`,
         `Eos apheresis`, `Monos apheresis`,
         `CD3 apheresis`, `CD4 apheresis`, `CD8 apheresis`,
         `CD56 apheresis`, `CD19 apheresis`, 
         `CD3 day +90`, `CD4 day +90`, `CD8 day +90`,
         `CD56 day +90`, `CD19 day +90`,
         any_sevinfection) %>%

  tbl_summary(by = any_sevinfection,

              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1) %>% 
  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
```

### Figures

## Figure 1. Consort diagram

## Figure 2. Inflammatory markers after ide-cel
```{r, fig.height=12}
LDH <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(`LDH at Pre-Leukapheresis`, `LDH day -5`, `LDH day 0`, 
         `LDH day +7`, `LDH day +14`, `LDH day +21`, `LDH day +30`)
LDH_long <- gather(LDH, day, LDH_value, `LDH at Pre-Leukapheresis`:`LDH day +30`)
LDH_long$day[LDH_long$day=="LDH at Pre-Leukapheresis"] <- "Pre"
LDH_long$day[LDH_long$day=="LDH day -5"] <- "Day -5"
LDH_long$day[LDH_long$day=="LDH day 0"] <- "Day 0"
LDH_long$day[LDH_long$day=="LDH day +7"] <- "Day 7"
LDH_long$day[LDH_long$day=="LDH day +14"] <- "Day 14"
LDH_long$day[LDH_long$day=="LDH day +21"] <- "Day 21"
LDH_long$day[LDH_long$day=="LDH day +30"] <- "Day 30"
LDH_long$day <- factor(LDH_long$day, levels = c("Pre", "Day -5", "Day 0", 
                                                "Day 7", "Day 14", "Day 21", "Day 30"))
# ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
#   geom_boxplot() + xlab("Days") + ylab("LDH") + 
#   geom_jitter(color= "grey")+
#   theme_classic() + ggtitle("LDH") + 
#   expand_limits(y = c(0, 7000)) + 
#   scale_y_break(c(1188, 4000), 
#                 ticklabels=c(4000, 7000), scales=0.10)

# cart0$`Ferritin day +7`[cart0$`Ferritin day +7`==">33511"] <- 33511
# cart0$`Ferritin day +7` <- as.numeric(cart0$`Ferritin day +7`)
Ferritin <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(patient_id, `Ferritin at Pre-Leukapheresis`, `Ferritin day -5`,
         `Ferritin day 0`, `Ferritin day +7`, `Ferritin day +14`, 
         `Ferritin day +21`, `Ferritin day +30`)
Ferritin_long <- gather(Ferritin, day, Ferritin_value, `Ferritin at Pre-Leukapheresis`:`Ferritin day +30`)
Ferritin_long$day[Ferritin_long$day=="Ferritin at Pre-Leukapheresis"] <- "Pre"
Ferritin_long$day[Ferritin_long$day=="Ferritin day -5"] <- "Day -5"
Ferritin_long$day[Ferritin_long$day=="Ferritin day 0"] <- "Day 0"
Ferritin_long$day[Ferritin_long$day=="Ferritin day +7"] <- "Day 7"
Ferritin_long$day[Ferritin_long$day=="Ferritin day +14"] <- "Day 14"
Ferritin_long$day[Ferritin_long$day=="Ferritin day +21"] <- "Day 21"
Ferritin_long$day[Ferritin_long$day=="Ferritin day +30"] <- "Day 30"
Ferritin_long$day <- factor(Ferritin_long$day, levels = c("Pre", "Day -5", "Day 0",
                                                          "Day 7", "Day 14", "Day 21", "Day 30"))
# ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
#   geom_boxplot() + 
#   xlab("Days") + ylab("Ferritin") + 
#   theme_classic() + ggtitle("Ferritin") + 
#   expand_limits(y = c(0, 34000)) +
#   scale_y_break(c(13600, 33000), ticklabels=c(33000, 34000), scales=0.10)

# cart0$`CRP Pre-Leukapheresis`[cart0$`CRP Pre-Leukapheresis`=="<0.03"] <- 0.07
# cart0$`CRP Pre-Leukapheresis` <- as.numeric(cart0$`CRP Pre-Leukapheresis`)
# cart0$`CRP day +14`[cart0$`CRP day +14`=="<0.03"] <- 0.07
# cart0$`CRP day +14` <- as.numeric(cart0$`CRP day +14`)
# cart0$`CRP day +21`[cart0$`CRP day +21`=="<0.03"] <- 0.07
# cart0$`CRP day +21` <- as.numeric(cart0$`CRP day +21`)
# cart0$`CRP day +30`[cart0$`CRP day +30`=="<0.03"] <- 0.07
# cart0$`CRP day +30` <- as.numeric(cart0$`CRP day +30`)
CRP <- cart0 %>%
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(`CRP Pre-Leukapheresis`, `CRP day -5`, `CRP day 0`,
         `CRP day +7`, `CRP day +14`, `CRP day +21`, `CRP day +30`)
CRP_long <- gather(CRP, day, CRP_value, `CRP Pre-Leukapheresis`:`CRP day +30`)
CRP_long$day[CRP_long$day=="CRP Pre-Leukapheresis"] <- "Pre"
CRP_long$day[CRP_long$day=="CRP day -5"] <- "Day -5"
CRP_long$day[CRP_long$day=="CRP day 0"] <- "Day 0"
CRP_long$day[CRP_long$day=="CRP day +7"] <- "Day 7"
CRP_long$day[CRP_long$day=="CRP day +14"] <- "Day 14"
CRP_long$day[CRP_long$day=="CRP day +21"] <- "Day 21"
CRP_long$day[CRP_long$day=="CRP day +30"] <- "Day 30"
CRP_long$day <- factor(CRP_long$day, levels = c("Pre", "Day -5", "Day 0", "Day 7", "Day 14", "Day 21", "Day 30"))
# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
#   geom_boxplot() + 
#   xlab("Days") + ylab("CRP") + 
#   theme_classic() + ggtitle("CRP") + 
#   expand_limits(y = c(0, 20)) +
#   scale_y_break(c(4.55, 7.5, 9.5, 18.0), ticklabels=c(8,9,18, 20), 
#                 scales=c(0.10)
#                 )

# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
#   geom_violin() + 
#   xlab("Days") + ylab("CRP") + 
#   theme_classic() + ggtitle("CRP")+
#   expand_limits(y = c(0, 20)) +
#   scale_y_break(c(5.9, 18.0), ticklabels=c(18, 20), 
#                 scales=c(0.25)
#                 )
# 
# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
#   geom_violin() + 
#   xlab("Days") + ylab("CRP") + 
#   theme_classic() + ggtitle("log10 CRP") + 
#   expand_limits(y = c(0, 100)) +
#   scale_y_log10()
# 
# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
#   geom_violin() + 
#   xlab("Days") + ylab("log2 CRP") + 
#   theme_classic() + ggtitle("CRP") + 
#   # expand_limits(y = c(0, 100)) +
#   scale_y_continuous(trans = "log2")

#   geom_jitter(color= "grey")+

a <- ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
  geom_boxplot() + 
  xlab("Days") + ylab("LDH represented with a log2 scale") + 
  theme_classic() + ggtitle("LDH") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 5 
                     # aes(label = paste0("p = ", ..p.format..))
  #                  aes(
  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
  )

b <- ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
  geom_boxplot() + 
  xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
  theme_classic() + ggtitle("Ferritin") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 5)

c <- ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
  geom_boxplot() + 
  xlab("Days") + ylab("CRP represented with a log2 scale") + 
  theme_classic() + ggtitle("CRP") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 5)

(a) /
(b) /
(c)+
plot_annotation(tag_levels = "A")

a <- ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
  geom_boxplot() + 
  geom_jitter(color= "grey")+
  xlab("Days") + ylab("LDH represented with a log2 scale") + 
  theme_classic() + ggtitle("LDH") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 5 
                     # aes(label = paste0("p = ", ..p.format..))
  #                  aes(
  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
  )

b <- ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
  geom_boxplot() + 
  geom_jitter(color= "grey")+
  xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
  theme_classic() + ggtitle("Ferritin") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 5)

c <- ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
  geom_boxplot() + 
  geom_jitter(color= "grey")+
  xlab("Days") + ylab("CRP represented with a log2 scale") + 
  theme_classic() + ggtitle("CRP") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 5)

(a) /
(b) /
(c) +
plot_annotation(tag_levels = "A")
```

## Figure 3. Cellular and humoral immune reconstitution after ide-cel
**I can probably remove the x axis title on the 4 top plots**
```{r, fig.width=12, fig.height=12}
cart2 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE)
# WBC
timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 60, 90)
WBC_fig <-
  data.frame(timepoints,
             t(round(
               sapply(cart2[, c(
                 "WBC apheresis",
                 "WBC day -5 (k/ul)",
                 "WBC day 0 (k/uL)",
                 "WBC day +7",
                 "WBC day +14",
                 "WBC day +21",
                 "WBC day +30",
                 "WBC day +60",
                 "WBC day +90"
               )],
               MedianCI,
               conf.level = 0.95,
               na.rm = TRUE), 9
             )))
WBC_fig <- WBC_fig %>%
  ggplot(aes(x = timepoints, y = median)) + 
  geom_line(col = "blue") + 
  xlab("Days relative to infusion") + 
  ylab("Median WBC") + 
  theme_classic() + 
  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
  scale_x_continuous(
    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
  ) + ylim(0, 6)

# ANC
ANC_fig <-
  data.frame(timepoints, t(round(
    sapply(cart2[, c(
      "ANC apheresis",
      "ANC day -5 (k/ul)",
      "ANC day 0 (k/uL)",
      "ANC Day 7",
      "ANC day +14",
      "ANC day +21",
      "ANC Day 30",
      "ANC Day 60",
      "ANC Day 90"
    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
  )))
ANC_fig <- ANC_fig %>% 
  ggplot(aes(x = timepoints, y = median)) + 
  geom_line(col = "blue") + 
  xlab("Days relative to infusion") + 
  ylab("Median ANC") + 
  theme_classic() + 
  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
  scale_x_continuous(
    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
  ) + 
  ylim(0, 4)

Hb_fig <-
  data.frame(timepoints, t(round(
    sapply(cart2[, c(
      "Hb apheresis",
      "Hb day -5 (k/ul)",
      "Hb day 0 (k/uL)",
      "Hb day +7",
      "Hb day +14",
      "Hb day +21",
      "Hb day +30",
      "Hb day +60",
      "Hb day +90"
    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
  )))
Hb_fig <- Hb_fig %>% 
  ggplot(aes(x = timepoints, y = median)) + 
  geom_line(col = "blue") + 
  xlab("Days relative to infusion") + 
  ylab("Median Hb") + 
  theme_classic() + 
  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
  scale_x_continuous(
    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
  ) + 
  ylim(7.5, 12)

# ALC
ALC_fig <-
  data.frame(timepoints, t(round(
    sapply(cart2[, c(
      "ALC apheresis",
      "ALC day -5 (k/ul)",
      "ALC day 0 (k/uL)",
      "ALC day +7",
      "ALC day +14",
      "ALC day +21",
      "ALC day +30",
      "ALC day +60",
      "ALC day +90"
    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
  )))
ALC_fig <- ALC_fig %>% 
  ggplot(aes(x = timepoints, y = median)) + 
  geom_line(col = "blue") + 
  xlab("Days relative to infusion") + 
  ylab("Median ALC") + 
  theme_classic() + 
  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
  scale_x_continuous(
    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
  ) + 
  ylim(0, 1.1)

# Plt
Plt_fig <-
  data.frame(timepoints, t(round(
    sapply(cart2[, c(
      "Plt apheresis",
      "Plt day -5 (k/ul)",
      "Plt day 0 (k/uL)",
      "Platelets Day 7",
      "Plt day +14",
      "Plt day +21",
      "Plateletes Day 30",
      "Platelets Day 60",
      "Platelets Day 90"
    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
  )))
Plt_fig <- Plt_fig %>% 
  ggplot(aes(x = timepoints, y = median)) + 
  geom_line(col = "blue") + 
  xlab("Days relative to infusion") + 
  ylab("Median Plt") + 
  theme_classic() + 
  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
  scale_x_continuous(
    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
  ) +
  ylim(20, 170)

# IgG
#table(cart2$`IgG day +90`)
#table(cart2$`IgG day +180`)
# cart2$`IgG day +90`[cart2$`IgG day +90` == "<109"] <- 77
# cart2$`IgG day +30`[cart2$`IgG day +30` == "<109"] <- 77
# cart2$`IgG day -5`[cart2$`IgG day -5` == "<109"] <- 77
# cart2$`IgG apheresis`[cart2$`IgG apheresis` == "<109"] <- 77
# 
# cart2$`IgG day +90` <- as.numeric(cart2$`IgG day +90`)
# cart2$`IgG day +30` <- as.numeric(cart2$`IgG day +30`)
# cart2$`IgG day -5` <- as.numeric(cart2$`IgG day -5`)
# cart2$`IgG apheresis` <- as.numeric(cart2$`IgG apheresis`)
timepoints2 <- c(-28, -5, 30, 90)
IgG_fig <-
  data.frame(timepoints2, t(round(
    sapply(cart2[, c(
      "IgG apheresis", 
      "IgG day -5",
      # "IgG day 0 (k/uL)", 
      "IgG day +30", 
      "IgG day +90")], MedianCI, conf.level =
             0.95, na.rm = TRUE), 9
  )))
IgG_fig <- IgG_fig %>% 
  ggplot(aes(x = timepoints2, y = median)) + 
  geom_line(col = "blue") +
  xlab("Days relative to infusion") + 
  ylab("Median IgG") + 
  theme_classic() + 
  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
  scale_x_continuous(
    breaks = c(-28, -5, 0, 30, 90),
    labels = c("Apheresis", "-5", "0", "30", "90"))# + 
  # ylim(0, 2000)

(WBC_fig | ANC_fig) /
  (Hb_fig | ALC_fig) /
  (Plt_fig | IgG_fig) +
  plot_annotation(tag_levels = "A")
```

<!-- <span style="color:blue">**IgG I need to fix the other 109**</span>  -->

<!-- Values less than the limit of detection (<109) were considered to be 77 which is the lower limit of detection divided by the square root of 2. One patient had an IgG day 0 value of <320. As this is above the limit of detection, I used the midway point between 320 and the lower limit of detection -- 214 -- as the value instead of <320.  -->

<br>

## Figure 4. Cytopenias over time

As discussed at meeting, rather than showing count recovery over time plan to show Grade 3+ cytopenias (Hb, Plt, ANC, WBC) over time (Day –5, Day +30, Day +60, Day +90)
**We want grade 3 only right?**
```{r}
# cart2 %>% 
#   select(patient_id,
#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
#   ) %>% 
#   pivot_longer(cols = `gr3_Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
#   group_by(name, value) %>% 
#   filter(!is.na(value)) %>% 
#   summarise(count=n()) %>% 
#   mutate(perc=(count/sum(count)*100)
#   ) %>% 
#   separate("name", into = c("gr3", "name", "day"), sep = "_") %>% 
#   filter(value == "YES") %>% 
#   # unite(time, c("day":"me"), sep = " ") %>% 
#   ggplot(aes(x= day, y= perc, fill= name))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))+
#   scale_fill_viridis_d() +
#   labs(fill = NULL, y = "%", title = "Grade 3+")+
#   theme_classic()
# 
# cart2 %>% 
#   select(patient_id,
#          `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
#          `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
#          `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
#          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
#          
#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
#   ) %>% 
#   pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
#   mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
#          grade = case_when(
#            grade == "gr3_"       ~ "Grade 3+",
#            TRUE                  ~ "Any grade"
#          )) %>% 
#   mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
#          name2 = coalesce(name1, name)) %>% 
#   group_by(name2, value, grade) %>% 
#   filter(!is.na(value)) %>% 
#   summarise(count=n()) %>%
#   group_by(name2, grade) %>% 
#   mutate(perc=(count/sum(count)*100)
#   ) %>%
#   separate("name2", into = c("name", "day"), sep = "_") %>% 
#   filter(value == "YES") %>% 
#   # unite(time, c("day":"me"), sep = " ") %>% 
#   ggplot(aes(x= day, y= perc, fill= name, alpha= grade))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))+
#   scale_fill_viridis_d() + 
#   scale_alpha_ordinal(range = c(0.5, 1))+
#   labs(fill = NULL, y = "%")+
#   theme_classic()

a <- cart2 %>% 
  select(patient_id,
         Leukopenia_apheresis,
         `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
         Neutropenia_apheresis,
         `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
         Anemia_apheresis,
         `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
         Thrombocytopenia_apheresis,
         `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,

         gr3_Leukopenia_apheresis,
         `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
         gr3_Neutropenia_apheresis,
         `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
         gr3_Anemia_apheresis,
         `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
         gr3_Thrombocytopenia_apheresis,
         `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
  ) %>% 
  pivot_longer(cols = `Leukopenia_apheresis`: gr3_Thrombocytopenia_90d) %>% 
  mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
         grade = case_when(
           grade == "gr3_"       ~ "Grade 3+",
           TRUE                  ~ "Any grade"
         )) %>% 
  mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
         name2 = coalesce(name1, name)) %>% 
  group_by(name2, value, grade) %>% 
  filter(!is.na(value)) %>%
  summarise(count=n()) %>%
  group_by(name2, grade) %>% 
  mutate(perc=(count/sum(count)*100)
  ) %>%
  separate("name2", into = c("name", "day"), sep = "_") %>% 
  ungroup() %>% 
  filter(value == "YES") %>% 
  add_row("name"="Leukopenia",  "day"="apheresis", "value"= "YES", "grade"="Any grade", "count"=0, "perc"=0) %>% 
  mutate(day = factor(day, levels = c("apheresis", "-5d", "30d", "60d", "90d")))
b <- a %>% filter(grade == "Any grade")
a %>% filter(grade == "Grade 3+") %>% 
  ggplot(aes(x= day, 
             y= perc, 
             fill= name, alpha= 1
             ))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9), data= b,
           aes(x= day, y= perc, fill= name), alpha= 0.4)+
  scale_fill_brewer(palette = "Spectral")+
  labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
  theme_classic()+
  scale_alpha_continuous(limits = c(0.4,1), breaks = c(0.4,1),
                         labels= c("Any Grade", "Grade 3+"))
```

## Figure 5. Cumulative incidence of infection and infection density
Lauren
```{r}
# library(cmprsk)
# 
# table(cart$`Latest Day of CRS (relateive to infusion)`)
# # cart$CRS_fup2 <- cart$CRS_fup
# # cart$CRS_fup2[cart$CRS_fup2==30] <- NA
# # table(cart$CRS_fup2)
# # 
# # cart0$CRS_fup[cart0$CRS_fup==30] <- 7
# CRS <- 
#  cuminc(
#     ftime = cart0$`Latest Day of CRS (relateive to infusion)`, 
#     fstatus = cart0$CRS_any2, 
#     group = cart0$`Infection type`)
# ggcompetingrisks(CRS, multiple_panels = FALSE) + 
#   scale_linetype_manual(name="Infection type", values=1:2,#labels=c("High","Low")
#   )+
#   guides(col="none")

```

## Figure S1. Viral titers after ide-cel

### A)	HSV 1/2 IgG

Example from prior cytopenia paper below. We can show this data however you think best
Interpretation: ≤0.89=negative (not immune)
                        0.90-1.09=indeterminate (can consider negative for purposes of analysis)
                        ≥1.10=positive (immune)

```{r, echo=TRUE}
# mutate(`IgG HSV1/2 apheresis` = case_when(
#     `IgG HSV1/2 apheresis` < 0.9         ~ "Negative",
#     `IgG HSV1/2 apheresis` >= 0.9 &
#       `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
#     `IgG HSV1/2 apheresis` >= 1.10       ~ "Positive",
#   ))
```

```{r}
# cart2 %>% 
#   select(patient_id, 
#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>% 
#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
#   unite(time, c("na":"me"), sep = " ") %>% 
#   # mutate(value = as.numeric(value)) %>% 
#   mutate(day = case_when(
#     day == "D90"        ~ 90,
#     day == "apheresis"  ~ 0
#   )) %>% 
#   ggplot(aes(x= day, y= value, color= patient_id))+
#   geom_point()+
#   geom_line()+
#   scale_x_continuous(
#     breaks = c(0, 90),
#     labels = c("Apheresis", "D90"))+
#   scale_color_viridis_d() +
#   labs(fill = "Patients", x = NULL)+
#   theme_classic()

# cart2 %>% 
#   select(patient_id, 
#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
#   
#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
#   unite(name, c("na":"me"), sep = " ") %>% 
#   ggplot(aes(x= day,  fill= value))+
#   geom_bar()

# Histogram
cart2 %>% 
  select(patient_id, 
         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
  unite(name, c("na":"me"), sep = " ") %>% 
  filter(!is.na(value)) %>% 
  group_by(name, day, value) %>% 
  summarise(count=n()) %>% 
  mutate(perc=(count/sum(count)*100)
  ) %>% 
  ggplot(aes(x= day, y= perc, fill= value))+
  geom_bar(stat = "identity")+
  labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
       fill= "Immunity")+
  scale_y_continuous(expand = c(0, 0))+
  theme_classic()

library(ggpattern)
cart2 %>% 
  select(patient_id, 
         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
  unite(name, c("na":"me"), sep = " ") %>% 
  filter(!is.na(value)) %>% 
  group_by(name, day, value) %>% 
  summarise(count=n()) %>% 
  mutate(perc=(count/sum(count)*100)
  ) %>% 
  ggplot(aes(x= day, y= perc))+
  geom_bar_pattern(aes(pattern = value),
                   stat = "identity",
    fill            = 'white', 
    colour          = 'black')+
  # geom_bar(stat = "identity")+
  labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
       fill= "Immunity")+
  scale_y_continuous(expand = c(0, 0))+
  theme_classic()

# cart2 %>% 
#   select(patient_id, 
#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
#   unite(name, c("na":"me"), sep = " ") %>% 
#   filter(!is.na(value)) %>% 
#   group_by(name, day, value) %>% 
#   summarise(count=n()) %>% 
# 
#   ggplot(aes(x= day, y= count, fill= value))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))
```

```{r, fig.width=5, fig.height=6}
# # Tile
# cart2 %>% 
#   select(patient_id, 
#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
#   unite(time, c("na":"me"), sep = " ") %>% 
#   filter(!is.na(value)) %>% 
#   arrange(value) %>% 
#   ggplot(aes(x= day, y= fct_reorder2(patient_id, value, day), fill= value))+
#   geom_tile(color = "white")+
#   labs(fill = NULL, x = NULL, y= NULL)+
#   theme_classic()
```

```{r}
# Alluvial
library(ggalluvial)

alluvial_A <- cart2 %>% 
  select(patient_id, igg_hsv_change,
         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
  # mutate(igg_hsv_change = case_when(
  #   igg_hsv_change == 1        ~  "Acquired immunity",
  #   igg_hsv_change == 0.25        ~  "Positive overtime",
  #   igg_hsv_change == -0.25        ~  "Negative overtime",
  #   igg_hsv_change == -1        ~  "Lost immunity"
  # )) %>% 
  drop_na() %>% 
  group_by(`IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>% 
  summarise(count=n()) %>%

  ggplot(aes(axis1 = `IgG HSV1/2 apheresis`, axis2 = `IgG HSV1/2 D90`,
             y = count)) +
  geom_alluvium(aes(fill = `IgG HSV1/2 apheresis`)
  )+
  geom_stratum()+
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  theme_classic()+
  ggtitle("Evolution of virus titers")
```

### B)	VZV IgG (positive=immune vs negative or equivocal=not immune)
```{r}
# cart2 %>% 
#   mutate(`VZV IgG apheresis` = case_when(
#     `VZV IgG apheresis` == "0"         ~ "Negative",
#     `VZV IgG apheresis` == "1"         ~ "immune",
#     TRUE                          ~ `VZV IgG apheresis`
#   )) %>% 
#   mutate(`VZV IgG D90 (1=pos, 0=neg)` = case_when(
#     `VZV IgG D90 (1=pos, 0=neg)` == "0"         ~ "Negative",
#     `VZV IgG D90 (1=pos, 0=neg)` == "1"         ~ "immune",
#     TRUE                          ~ `VZV IgG D90 (1=pos, 0=neg)`
#   )) %>% 
#   select(patient_id, 
#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
#   ) %>% 
#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
#   unite(time, c("na":"me"), sep = " ") %>% 
#   # mutate(value = as.numeric(value)) %>% 
#   mutate(day = case_when(
#     day == "D90"        ~ 90,
#     day == "apheresis"  ~ 0
#   )) %>% 
#   ggplot(aes(x= day, y= value, color= patient_id))+
#   geom_point(position=position_dodge(width=0.9))+
#   scale_x_continuous(
#     breaks = c(0, 90),
#     labels = c("Apheresis", "D90"))+
#   scale_color_viridis_d() +
#   labs(fill = "Patients", x = NULL)+
#   theme_classic()

# Histogram
# cart2 %>% 
#   select(patient_id, 
#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
#   ) %>% 
#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
#   unite(name, c("na":"me"), sep = " ") %>% 
#   filter(!is.na(value)) %>% 
#   group_by(name, day, value) %>% 
#   summarise(count=n()) %>% 
#   mutate(perc=(count/sum(count)*100)
#   ) %>% 
#   ggplot(aes(x= day, y= perc, fill= value))+
#   geom_bar(stat = "identity")+
#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
#        fill= "Immunity")+
#   scale_y_continuous(expand = c(0, 0))+
#   theme_classic()

# cart2 %>% 
#   select(patient_id, 
#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
#   ) %>% 
#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
#   unite(name, c("na":"me"), sep = " ") %>% 
#   filter(!is.na(value)) %>% 
#   group_by(name, day, value) %>% 
#   summarise(count=n()) %>% 
# 
#   ggplot(aes(x= day, y= count, fill= value))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))
```

```{r, fig.width=5, fig.height=6}
# Tile
# cart2 %>% 
#   select(patient_id, 
#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
#   ) %>% 
#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
#   unite(time, c("na":"me"), sep = " ") %>% 
#   filter(!is.na(value)) %>% 
#   arrange(value) %>% 
#   ggplot(aes(x= day, y= fct_reorder2(patient_id, value, day), fill= value))+
#   geom_tile(color = "white")+
#   labs(fill = NULL, x = NULL, y= NULL)+
#   theme_classic()
```

```{r}
# Alluvial
alluvial_B <- cart2 %>% 
  select(patient_id, igg_vzv_change,
         `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
  ) %>% 
  # mutate(igg_vzv_change = case_when(
  #   igg_vzv_change == 1        ~  "Acquired immunity",
  #   igg_vzv_change == 0.25        ~  "Positive overtime",
  #   igg_vzv_change == -0.25        ~  "Negative overtime",
  #   igg_vzv_change == -1        ~  "Lost immunity"
  # )) %>% 
  drop_na() %>% 
  group_by(`VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`) %>% 
  summarise(count=n()) %>%

  ggplot(aes(axis1 = `VZV IgG apheresis`, axis2= `VZV IgG D90 (1=pos, 0=neg)`,
             y = count)) +
  geom_alluvium(aes(fill = `VZV IgG apheresis`)
  )+
  geom_stratum()+
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  theme_classic()+
  ggtitle("Evolution of virus titers")
```

### C)	CMV IgG (positive=immune vs negative=not immune)
```{r}
# Histogram
# cart2 %>% 
#   
#   select(patient_id, 
#          `CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`
#   ) %>% 
#   pivot_longer(cols = `CMV IgG apheresis` : `CMV IgG D90 (1=pos, 0=neg)`) %>% 
#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
#   unite(name, c("na":"me"), sep = " ") %>% 
#   filter(!is.na(value)) %>% 
#   group_by(name, day, value) %>% 
#   summarise(count=n()) %>% 
#   mutate(perc=(count/sum(count)*100)
#   ) %>% 
#   ggplot(aes(x= day, y= perc, fill= value))+
#   geom_bar(stat = "identity")+
#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
#        fill= "Immunity")+
#   scale_y_continuous(expand = c(0, 0))+
#   theme_classic()
```

```{r, fig.width=5, fig.height=6}
# Tile
# cart2 %>% 
#   
#   select(patient_id, 
#          `CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`
#   ) %>% 
#   pivot_longer(cols = `CMV IgG apheresis` : `CMV IgG D90 (1=pos, 0=neg)`) %>% 
#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
#   unite(time, c("na":"me"), sep = " ") %>% 
#   filter(!is.na(value)) %>% 
#   arrange(value) %>% 
#   ggplot(aes(x= day, y= fct_reorder2(patient_id, value, day), fill= value))+
#   geom_tile(color = "white")+
#   labs(fill = NULL, x = NULL, y= NULL)+
#   theme_classic()
```

```{r}
# Alluvial
alluvial_C <- cart2 %>% 
  select(patient_id, igg_cmv_change,
         `CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`
  ) %>% 
  # mutate(igg_cmv_change = case_when(
  #   igg_cmv_change == 1        ~  "Acquired immunity",
  #   igg_cmv_change == 0.25        ~  "Positive overtime",
  #   igg_cmv_change == -0.25        ~  "Negative overtime",
  #   igg_cmv_change == -1        ~  "Lost immunity"
  # )) %>% 
  drop_na() %>% 
  group_by(`CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`) %>% 
  summarise(count=n()) %>%

  ggplot(aes(axis1 = `CMV IgG apheresis`, axis2= `CMV IgG D90 (1=pos, 0=neg)`,
             y = count)) +
  geom_alluvium(aes(fill = `CMV IgG apheresis`)
  )+
  geom_stratum()+
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  theme_classic()+
  ggtitle("Evolution of virus titers")
```

```{r, fig.height=12}
(alluvial_A) /
  (alluvial_B) /
  (alluvial_C) +
  plot_annotation(tag_levels = "A")
```

## Figure S2. Pneumococcal titers after ide-cel

Antibody concentration >1.0 is considered long-term protection (immune)
If antibody concentration ≤1.0 consider negative (not immune)
```{r, fig.width=12, fig.height=12}
# Histogram
# cart2 %>% 
#   select(patient_id, 
#          starts_with("Pneumo"), -ends_with("change")) %>% 
#   pivot_longer(cols = -patient_id) %>% 
#   filter(!is.na(value)) %>% 
#   mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
#   mutate(name = str_remove(name, " apheresis| D90")) %>% 
#   
#   group_by(name, day, value) %>% 
#   summarise(count=n()) %>% 
#   mutate(perc=(count/sum(count)*100)
#   ) %>% 
# 
#   ggplot(aes(x= day, y= perc, fill= value))+
#   # geom_bar(stat = "identity",
#   #          position=position_dodge2(width=0.9, preserve = "single"))+
#   geom_bar(stat = "identity")+
#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
#        fill= "Immunity")+
#   scale_y_continuous(expand = c(0, 0))+
#   theme_classic()+
#   facet_wrap(.~ name)
```

```{r, fig.width=12, fig.height=14}
# Tile
# cart2 %>% 
#   select(patient_id, 
#          starts_with("Pneumo"), -ends_with("change")) %>% 
#   pivot_longer(cols = -patient_id) %>% 
#   mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
#   mutate(name = str_remove(name, " apheresis| D90")) %>% 
#   
#   
#   filter(!is.na(value)) %>% 
#   arrange(value) %>% 
#   ggplot(aes(x= day, y= fct_reorder2(patient_id, value, day), fill= value))+
#   geom_tile(color = "white")+
#   labs(fill = NULL, x = NULL, y= NULL)+
#   theme_classic()+
#   facet_wrap(.~ name)
```

##########################

```{r, fig.width=15, fig.height=12}
library(ComplexHeatmap)
mat <- cart2 %>% 
  select(patient_id, intersect(starts_with("Pneumo"), ends_with("change"))) %>% 
  drop_na() %>% 
  # mutate(new_sort = rowSums(select(.,-patient_id), na.rm = TRUE)) %>%
  mutate(new_sort = 
           c(5,7,8,23,6,9,10,11,12,4,13,14,26,15,
             24,3,16,25,17,2,18,21,19,20,1,22)) %>%

  arrange(new_sort) %>% 
    select(-new_sort)

df5 <- t((as.matrix(mat)))

df <- df5 %>% `colnames<-`(c(.[1,])) %>% 
  .[-1,]

df <- df %>% 
sub(pattern = " 1.00", replacement = "Acquired immunity") %>% 
sub(pattern = " 0.25", replacement = "Positive overtime") %>% 
sub(pattern = "-0.25", replacement = "Negative overtime") %>% 
sub(pattern = "-1.00", replacement = "Lost immunity")

colors = structure(c("blue", "darkgrey", "lightgrey", "red"), 
                   names = c("Lost immunity", "Negative overtime", "Positive overtime", "Acquired immunity"))

ht_list <- Heatmap(df, name = "change", 
        rect_gp = gpar(col = "white", lwd = 0.1),
        column_title = "Change in titers",
        show_column_names =FALSE,
        row_names_side = "left",
        row_names_gp = gpar(fontsize = 11),
        col = colors)
draw(ht_list, heatmap_legend_side = "bottom")
# Heatmap(df, name = "change", 
#         rect_gp = gpar(col = "white", lwd = 0.1),
#         column_title = "Change in titers",
#         column_names_rot = 45,
#         column_names_gp = gpar(fontsize = 8),
#         row_names_side = "left", 
#         row_names_gp = gpar(fontsize = 10,
#                             col = c("darkgreen", "pink", "orange", rep("blue", 28))),
#         show_heatmap_legend = TRUE,
#         col = colors)
kjhkhkh
```

### 2022-04-21 RWE/RWE Manuscript analyses.Rmd
Update

@@
   ))) %>% 
+  mutate(`Length of Hospital Stay (Total Days including Readmission)` =
+           as.numeric(`Length of Hospital Stay (Total Days including Readmission)`)) %>% 
   # defining BMI categories
@@
   # )) %>% 
-  # mutate(`Anemia_7d` = case_when(
-  #   `Hb day +7` < 11.4                                              ~ "YES",
-  #   is.na(`Hb day +7`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
+  mutate(`Anemia_7d` = case_when(
+    `HgB Day 7` < 11.4                                              ~ "YES",
+    is.na(`HgB Day 7`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
   # mutate(`Anemia_14d` = case_when(
@@
   # )) %>% 
-  # mutate(`Anemia_30d` = case_when(
-  #   `Hb day +30` < 11.4                                             ~ "YES",
-  #   is.na(`Hb day +30`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Anemia_60d` = case_when(
-  #   `Hb day +60` < 11.4                                             ~ "YES",
-  #   is.na(`Hb day +60`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Anemia_90d` = case_when(
-  #   `Hb day +90` < 11.4                                             ~ "YES",
-  #   is.na(`Hb day +90`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
+  mutate(`Anemia_30d` = case_when(
+    `HgB Day 30` < 11.4                                             ~ "YES",
+    is.na(`HgB Day 30`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
+  mutate(`Anemia_60d` = case_when(
+    `HgB Day 60` < 11.4                                             ~ "YES",
+    is.na(`HgB Day 60`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
+  mutate(`Anemia_90d` = case_when(
+    `HgB Day 90` < 11.4                                             ~ "YES",
+    is.na(`HgB Day 90`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
   # mutate(gr3_Anemia_apheresis = case_when(
@@
   # )) %>% 
-  # mutate(`gr3_Anemia_7d` = case_when(
-  #   `Hb day +7` < 8                                              ~ "YES",
-  #   is.na(`Hb day +7`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
+  mutate(`gr3_Anemia_7d` = case_when(
+    `HgB Day 7` < 8                                              ~ "YES",
+    is.na(`HgB Day 7`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
   # mutate(`gr3_Anemia_14d` = case_when(
@@
   # )) %>% 
-  # mutate(`gr3_Anemia_30d` = case_when(
-  #   `Hb day +30` < 8                                             ~ "YES",
-  #   is.na(`Hb day +30`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`gr3_Anemia_60d` = case_when(
-  #   `Hb day +60` < 8                                             ~ "YES",
-  #   is.na(`Hb day +60`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`gr3_Anemia_90d` = case_when(
-  #   `Hb day +90` < 8                                             ~ "YES",
-  #   is.na(`Hb day +90`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
+  mutate(`gr3_Anemia_30d` = case_when(
+    `HgB Day 30` < 8                                             ~ "YES",
+    is.na(`HgB Day 30`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
+  mutate(`gr3_Anemia_60d` = case_when(
+    `HgB Day 60` < 8                                             ~ "YES",
+    is.na(`HgB Day 60`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
+  mutate(`gr3_Anemia_90d` = case_when(
+    `HgB Day 90` < 8                                             ~ "YES",
+    is.na(`HgB Day 90`)                                          ~ NA_character_,
+    TRUE                                                          ~ "NO"
+  )) %>%
   # 
@@
   #     `ANC Day 30` < 1.8 | 
-  #     `Hb day +30` < 11.4 | 
+  #     `HgB Day 30` < 11.4 | 
   #     `Plateletes Day 30` < 143                                             ~ "YES",
@@
   #     is.na(`ANC Day 30`) |
-  #     is.na(`Hb day +30`) |
+  #     is.na(`HgB Day 30`) |
   #     is.na(`Plateletes Day 30`)                                            ~ NA_character_,
@@
   #     `ANC Day 30` < 1 | 
-  #     `Hb day +30` < 8 | 
+  #     `HgB Day 30` < 8 | 
   #     `Plateletes Day 30` < 50                                              ~ "YES",
@@
   #     `ANC Day 90` < 1 | 
-  #     `Hb day +90` < 8 | 
+  #     `HgB Day 90` < 8 | 
   #     `Platelets Day 90` < 50                                             ~ "YES",
@@
   #     is.na(`ANC Day 90`) |
-  #     is.na(`Hb day +90`) |
+  #     is.na(`HgB Day 90`) |
   #     is.na(`Platelets Day 90`)                                            ~ NA_character_,
@@
 
+## Table X. Manufacturing failures
+```{r}
+MM_cart %>% 
+  # Exclude patients who had manufacturing cart failure or died prior cart infusion
+  select(`First manufacturing failure`, 
+         `Manufaturing failures with successfull second collection`) %>% 
+  mutate(across(everything(), ~ replace_na(., 0))) %>% 
+  tbl_summary(
+    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1,
+    missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
+<br>
+
 ## Table 1. Patient baseline characteristics
@@
          `Extramedullary Disease? (Yes, No)`, 
+         `Plasma Cell Leukemia? (yes, no)`,
+         `Amyloid? (yes, no)`,
+         POEMS,
+         `Non-secretory MM (Yes, No)`,
+
          `High Marrow Burden (>= 50%)`, 
@@
          `R-ISS at CAR-T infusion`,
-         # cyto, 
+
          `Deletion 17p prior to CAR-T infusion (yes, no)`,
@@
          `Bridging Therapy? (Yes, No)`,
+         `Number of prior lines of therapy`,
+         `Disease status at time of referral (Relapsed vs Refractory)`,
          `Prior auto SCT (yes, no)`, 
+         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+         `Prior Allo SCT (Yes, No)`,
          `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
          immuno, proteasome, dara, doubleref, tripleref, pentaref,
+
+         `Cell Dose (million cells)`,
+         `ECOG > or = 2? (Yes, No)`,
+         `ANC < 1000/uL (Yes, No)`,
+         `Hemoglobin < 8 g/dL (Yes, No)`,
+         `Platelets < 50K (Yes, No)`,
+
+         `Non-secretory MM (Yes, No)`,
+
          `Did patient met criteria for KarMMa1 pre-CAR-T?`) %>% 
@@
     type = list(
-      c(`Extramedullary Disease? (Yes, No)`, `High Marrow Burden (>= 50%)`,
-    #     cyto, 
+      c(
+      `Extramedullary Disease? (Yes, No)`, 
+      `Plasma Cell Leukemia? (yes, no)`,
+         `Amyloid? (yes, no)`,
+         POEMS,
+         `Non-secretory MM (Yes, No)`,
+      `High Marrow Burden (>= 50%)`,
+    # #     cyto, 
     `Deletion 17p prior to CAR-T infusion (yes, no)`,
@@
         `t(14:16) prior to CAR-T infusion (yes, no)`,
-        `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
+    #     `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref,
-        `Did patient met criteria for KarMMa1 pre-CAR-T?`)
+    #     `Did patient met criteria for KarMMa1 pre-CAR-T?`
+    )
       ~"categorical"),
@@
 
-## Table 2. Clinical outcomes
-**best response**
+## Table 2. Safety with Standard of Care Idecabtagene Vicleucel Event and Grade
+
 ```{r}
-tbl1 <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
+# tbl1 <- 
+  cart0 %>% 
   select(`Max CRS grade (0-5)`,
-         # `Day of onset of CRS relative to infusion`,
          `Day of Max CRS (relative to infusion)`,
-
          `Max ICANS (relative to infusion)`,
-         # `Day of onset of ICANS relative to infusion`,
-         `Day of Max ICANS (relative to infusion)`) %>% 
-  tbl_summary(type = list(
-    c(
-      `Day of Max ICANS (relative to infusion)`) ~ "continuous"),
-    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+         `Day of Max ICANS (relative to infusion)`,
+         `Length of Hospital Stay (Total Days including Readmission)`,
+         `ICU Admission? (Yes, No)`,
+         `Tocilizumab (Yes, No)`,
+         `Steroid use (Yes, No)`,
+         `Anakinra (Yes, No)`,
+
+         `Need for GCSF`,
+         `Need for TPO Agonist`
+
+         ) %>% 
+  tbl_summary(
+    # type = list(
+    # c(
+    #   `Length of Hospital Stay (Total Days including Readmission)`
+    #   ) ~ "continuous"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max}) [{p25}, {p75}]"), 
     digits = all_continuous() ~ 1,
@@
 
-tbl2 <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
-         `Anakinra (Yes, No)`) %>% 
-  tbl_summary(type = list(
-    c(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
-      `Anakinra (Yes, No)`) ~ "categorical"),
-    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-    digits = all_continuous() ~ 1) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl3 <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(#MRDneg_30days,
-         ORR_30days,
-         day30_response,
-         day30_response_group) %>% 
-  tbl_summary(#type = list(
-    # c(MRDneg_30days) ~ "categorical"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-# tbl4 <- cart0 %>% 
+# tbl2 <- cart0 %>% 
 #   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(day30_response_group == "CR or sCR") %>% 
-#   select(MRDneg_30days) %>% 
-#   tbl_summary(type = list(c(MRDneg_30days) ~ "categorical"),
-#               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
+#   select(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
+#          `Anakinra (Yes, No)`) %>% 
+#   tbl_summary(type = list(
+#     c(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
+#       `Anakinra (Yes, No)`) ~ "categorical"),
+#     statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+#     digits = all_continuous() ~ 1) %>% 
+#   bold_labels() %>% add_stat_label()
+# 
+# tbl3 <- cart0 %>% 
+#   distinct(patient_id, .keep_all = TRUE) %>% 
+#   select(#MRDneg_30days,
+#          ORR_30days,
+#          day30_response,
+#          day30_response_group) %>% 
+#   tbl_summary(#type = list(
+#     # c(MRDneg_30days) ~ "categorical"),
 #     digits = all_continuous() ~ 1,
@@
 #   bold_labels() %>% add_stat_label()
-
-tbl5 <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(#MRDneg_90days,
-         ORR_90days,
-         day90_response,
-         day90_response_group) %>% 
-  tbl_summary(#type = list(
-    # c(MRDneg_90days) ~ "categorical"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-# tbl6 <- cart0 %>% 
+# 
+# # tbl4 <- cart0 %>% 
+# #   distinct(patient_id, .keep_all = TRUE) %>% 
+# #   filter(day30_response_group == "CR or sCR") %>% 
+# #   select(MRDneg_30days) %>% 
+# #   tbl_summary(type = list(c(MRDneg_30days) ~ "categorical"),
+# #               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
+# #               digits = all_continuous() ~ 1,
+# #               missing = "no") %>% 
+# #   bold_labels() %>% add_stat_label()
+# 
+# tbl5 <- cart0 %>% 
 #   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(day90_response_group == "CR or sCR") %>% 
-#   select(MRDneg_90days) %>% 
-#   tbl_summary(type = list(c(MRDneg_90days) ~ "categorical"),
-#               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
+#   select(#MRDneg_90days,
+#          ORR_90days,
+#          day90_response,
+#          day90_response_group) %>% 
+#   tbl_summary(#type = list(
+#     # c(MRDneg_90days) ~ "categorical"),
 #     digits = all_continuous() ~ 1,
@@
 #   bold_labels() %>% add_stat_label()
-
-tbl7 <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(best_response) %>% 
-  tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"),
-              label = list(best_response ~ "best response in the first 90 days"),
-              digits = all_continuous() ~ 1,
-              missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl8 <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  filter(best_response == "CR or sCR") %>% 
-  select(MRDneg_in_best_response) %>% 
-  tbl_summary(type = list(c(MRDneg_in_best_response) ~ "categorical"),
-              label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
-              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1,
-              missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() %>%
-  gt::tab_source_note(gt::md("**
-                             **"))
+# 
+# # tbl6 <- cart0 %>% 
+# #   distinct(patient_id, .keep_all = TRUE) %>% 
+# #   filter(day90_response_group == "CR or sCR") %>% 
+# #   select(MRDneg_90days) %>% 
+# #   tbl_summary(type = list(c(MRDneg_90days) ~ "categorical"),
+# #               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
+# #               digits = all_continuous() ~ 1,
+# #               missing = "no") %>% 
+# #   bold_labels() %>% add_stat_label()
+# 
+# tbl7 <- cart0 %>% 
+#   distinct(patient_id, .keep_all = TRUE) %>% 
+#   select(best_response) %>% 
+#   tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"),
+#               label = list(best_response ~ "best response in the first 90 days"),
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>% 
+#   bold_labels() %>% add_stat_label()
+# 
+# tbl8 <- cart0 %>% 
+#   distinct(patient_id, .keep_all = TRUE) %>% 
+#   filter(best_response == "CR or sCR") %>% 
+#   select(MRDneg_in_best_response) %>% 
+#   tbl_summary(type = list(c(MRDneg_in_best_response) ~ "categorical"),
+#               label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
+#               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>% 
+#   bold_labels() %>% add_stat_label()
+# 
+# 
+# 
+# tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() %>%
+#   gt::tab_source_note(gt::md("**
+#                              **"))
 
@@
       "Hb day 0 (k/uL)",
-      "Hb day +7",
+      "HgB Day 7",
       "Hb day +14",
       "Hb day +21",
-      "Hb day +30",
-      "Hb day +60",
-      "Hb day +90"
+      "HgB Day 30",
+      "HgB Day 60",
+      "HgB Day 90"
     )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9

### 2022-04-22 RWE/RWE Manuscript analyses.Rmd
Update Rmd RWE manuscript

@@
 author: "Christelle Colin-Leitzinger"
-date: '`r Sys.Date()`
+date: '`r Sys.Date()`'
 output: 
@@
     df_print: paged
-editor_opatient_idions: 
-  chunk_output_type: console
 editor_options: 
@@
 
-.## Figure {
+. figure {
    margin-top: 25px;
@@
 
-## Table {
+table {
     margin-top: 10px;
@@
                       cache = FALSE,
-                      fig.align='center'
+                      # fig.width = 7, fig.height = 5, 
+                      fig.align='center'#, fig.show='hold'
                       )
@@
 # path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias")
-path <- getwd()
+# path <- getwd()
 MM_cart <-
-  readxl::read_xlsx(paste0(path,
-    "/RWE/FINAL 4.13.22 ASCO 2022 Myeloma CAR-T SOC Outcomes Spreadsheet.xlsx"),
+  readxl::read_xlsx(
+    "/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/RWE/FINAL 4.13.22 ASCO 2022 Myeloma CAR-T SOC Outcomes Spreadsheet.xlsx",
                     skip = 1, n_max = 198
@@
   filter(is.na(exclude_for_manufacturing_cart_failure_or_died_prior_cart_infusion)) %>%
+
+  mutate(across(c(`ANC Day 30`,
+                  `ANC Day 90`,
+                  `HgB Day 90`,
+                  `Platelets Day 90`), ~ as.numeric(.))) %>% 
+  mutate(across(c(`Need for GCSF`), ~ str_to_upper(.))) %>% 
   # Keep second infusion date for patients who had failure
@@
   select(-c(`Date of Apheresis (or # of days from apheresis to LD)`, first_date_of_apheresis)) %>% 
+  mutate(across(c(`Day of Max CRS (relative to infusion)`,
+                  `Day of Max ICANS (relative to infusion)`), ~ str_remove(., "Day +"))
+         ) %>%
 
@@
 # censored days > 100 to 100
-  mutate(across(c(#`Day of onset of CRS relative to infusion`,
-                  `Day of Max CRS (relative to infusion)`,
-                  #`Day of onset of ICANS relative to infusion`,
+  mutate(across(c(`Day of Max CRS (relative to infusion)`,
                   `Day of Max ICANS (relative to infusion)`), ~ case_when(
@@
   ) %>% 
+  mutate(Sex = case_when(
+    str_detect(Sex, "F")                                          ~ "F",
+    str_detect(Sex, "M")                                          ~ "M"
+  )) %>% 
   mutate(male_sex = case_when(
@@
   # cytogenetics
-  mutate(cyto = case_when(
+  mutate(cytogenetics = case_when(
     `Deletion 17p prior to CAR-T infusion (yes, no)` == "YES" | 
@@
       `t(4:14) prior to CAR-T infusion (yes, no)` == "NO" &
-      `t(14:16) prior to CAR-T infusion (yes, no)` == "NO"    ~ "NO"
+      `t(14:16) prior to CAR-T infusion (yes, no)` == "NO"    ~ "NO",
+    TRUE                                                      ~ NA_character_
   )) %>% 
@@
            `Max CRS grade (0-5)` >= 3                             ~ "Grade ≥3"),
-         CRS_gradecat = factor(CRS_gradecat, levels = c("No CRS", "Grade 1 or 2", "Grade ≥3"))
-  ) %>% 
+         CRS_gradecat = factor(CRS_gradecat, levels = c("No CRS", "Grade 1 or 2", "Grade ≥3")),
+         gr3_CRS = case_when(
+           CRS_gradecat == "Grade ≥3"                             ~ "Grade ≥3",
+           CRS_gradecat != "Grade ≥3"                             ~ "Grade <3",
+           TRUE                                                   ~ NA_character_
+           )) %>% 
   # mutate( = case_when(
@@
            `Max ICANS (relative to infusion)` >= 3 ~              "Grade ≥3"),
-         ICANS_gradecat = factor(ICANS_gradecat, levels = c("No ICANS", "Grade 1 or 2", "Grade ≥3"))
-  ) %>% 
+         ICANS_gradecat = factor(ICANS_gradecat, levels = c("No ICANS", "Grade 1 or 2", "Grade ≥3")),
+         gr3_ICANS = case_when(
+           ICANS_gradecat == "Grade ≥3"                             ~ "Grade ≥3",
+           ICANS_gradecat != "Grade ≥3"                             ~ "Grade <3",
+           TRUE                                                   ~ NA_character_
+         )) %>% 
   # mutate(`marrow cellularity baseline` = case_when(
@@
   )) %>% 
-  # 
-  # mutate(`cytopenia_30d` = case_when(
-  #   `WBC day +30` < 4 | 
-  #     `ANC Day 30` < 1.8 | 
-  #     `HgB Day 30` < 11.4 | 
-  #     `Plateletes Day 30` < 143                                             ~ "YES",
-  #   is.na(`WBC day +30`) |
-  #     is.na(`ANC Day 30`) |
-  #     is.na(`HgB Day 30`) |
-  #     is.na(`Plateletes Day 30`)                                            ~ NA_character_,
-  #   TRUE                                                              ~ "NO"
-  # )) %>% 
+  mutate(Neutropenia_gr1 = case_when(
+    `ANC Day 7` < 1.8 |
+    `ANC Day 30` < 1.8 |
+      `ANC Day 60` < 1.8 |
+      `ANC Day 90` < 1.8                                          ~ "YES",
+    is.na(`ANC Day 7`) |
+      is.na(`ANC Day 30`) |
+      is.na(`ANC Day 60`) |
+      is.na(`ANC Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(Neutropenia_gr2 = case_when(
+    `ANC Day 7` < 1.5 |
+    `ANC Day 30` < 1.5 |
+      `ANC Day 60` < 1.5 |
+      `ANC Day 90` < 1.5                                          ~ "YES",
+    is.na(`ANC Day 7`) |
+      is.na(`ANC Day 30`) |
+      is.na(`ANC Day 60`) |
+      is.na(`ANC Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(Neutropenia_gr3 = case_when(
+    `ANC Day 7` < 1 |
+    `ANC Day 30` < 1 |
+      `ANC Day 60` < 1 |
+      `ANC Day 90` < 1                                          ~ "YES",
+    is.na(`ANC Day 7`) |
+      is.na(`ANC Day 30`) |
+      is.na(`ANC Day 60`) |
+      is.na(`ANC Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(Neutropenia_gr4 = case_when(
+    `ANC Day 7` < 0.5 |
+    `ANC Day 30` < 0.5 |
+      `ANC Day 60` < 0.5 |
+      `ANC Day 90` < 0.5                                          ~ "YES",
+    is.na(`ANC Day 7`) |
+      is.na(`ANC Day 30`) |
+      is.na(`ANC Day 60`) |
+      is.na(`ANC Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(any_neutropenia = case_when(
+    Neutropenia_gr1 == "YES" |
+      Neutropenia_gr2 == "YES" |
+      Neutropenia_gr3 == "YES" |
+      Neutropenia_gr4 == "YES"                                          ~ "YES",
+    is.na(Neutropenia_gr1) |
+          is.na(Neutropenia_gr2) |
+    is.na(Neutropenia_gr3) |
+    is.na(Neutropenia_gr4)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(severe_neutro_30beyond = case_when(
+    `ANC Day 30` < 1 |
+      `ANC Day 60` < 1 |
+      `ANC Day 90` < 1                                          ~ "YES",
+      is.na(`ANC Day 30`) |
+      is.na(`ANC Day 60`) |
+      is.na(`ANC Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>%
+
+  mutate(Anemia_gr1 = case_when(
+      `HgB Day 7` < 11.4 |
+      `HgB Day 30` < 11.4 |
+      `HgB Day 60` < 11.4 |
+      `HgB Day 90` < 11.4                                        ~ "YES",
+      is.na(`HgB Day 7`) |
+      is.na(`HgB Day 30`) |
+      is.na(`HgB Day 60`) |
+      is.na(`HgB Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(Anemia_gr2 = case_when(
+      `HgB Day 7` < 10 |
+      `HgB Day 30` < 10 |
+      `HgB Day 60` < 10 |
+      `HgB Day 90` < 10                                        ~ "YES",
+      is.na(`HgB Day 7`) |
+      is.na(`HgB Day 30`) |
+      is.na(`HgB Day 60`) |
+      is.na(`HgB Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(Anemia_gr3 = case_when(
+      `HgB Day 7` < 8 |
+      `HgB Day 30` < 8 |
+      `HgB Day 60` < 8 |
+      `HgB Day 90` < 8                                        ~ "YES",
+      is.na(`HgB Day 7`) |
+      is.na(`HgB Day 30`) |
+      is.na(`HgB Day 60`) |
+      is.na(`HgB Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(Anemia_gr4 = case_when(
+      `HgB Day 7` < 0.1 |
+      `HgB Day 30` < 0.1 |
+      `HgB Day 60` < 0.1 |
+      `HgB Day 90` < 0.1                                        ~ "YES",
+      is.na(`HgB Day 7`) |
+      is.na(`HgB Day 30`) |
+      is.na(`HgB Day 60`) |
+      is.na(`HgB Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(severe_anemia_30beyond = case_when(
+    `HgB Day 30` < 8 |
+      `HgB Day 60` < 8 |
+      `HgB Day 90` < 8                                        ~ "YES",
+      is.na(`HgB Day 30`) |
+      is.na(`HgB Day 60`) |
+      is.na(`HgB Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>%
+
+  mutate(Thrombocytopenia_gr1 = case_when(
+      `Platelets Day 7` < 143 |
+      `Plateletes Day 30` < 143 |
+      `Platelets Day 60` < 143 |
+      `Platelets Day 90` < 143                                        ~ "YES",
+      is.na(`Platelets Day 7`) |
+      is.na(`Plateletes Day 30`) |
+      is.na(`Platelets Day 60`) |
+      is.na(`Platelets Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(Thrombocytopenia_gr2 = case_when(
+      `Platelets Day 7` < 75 |
+      `Plateletes Day 30` < 75 |
+      `Platelets Day 60` < 75 |
+      `Platelets Day 90` < 75                                        ~ "YES",
+      is.na(`Platelets Day 7`) |
+      is.na(`Plateletes Day 30`) |
+      is.na(`Platelets Day 60`) |
+      is.na(`Platelets Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(Thrombocytopenia_gr3 = case_when(
+      `Platelets Day 7` < 50 |
+      `Plateletes Day 30` < 50 |
+      `Platelets Day 60` < 50 |
+      `Platelets Day 90` < 50                                        ~ "YES",
+      is.na(`Platelets Day 7`) |
+      is.na(`Plateletes Day 30`) |
+      is.na(`Platelets Day 60`) |
+      is.na(`Platelets Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(Thrombocytopenia_gr4 = case_when(
+      `Platelets Day 7` < 25 |
+      `Plateletes Day 30` < 25 |
+      `Platelets Day 60` < 25 |
+      `Platelets Day 90` < 25                                        ~ "YES",
+      is.na(`Platelets Day 7`) |
+      is.na(`Plateletes Day 30`) |
+      is.na(`Platelets Day 60`) |
+      is.na(`Platelets Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>% 
+  mutate(severe_throm_30beyond = case_when(
+    `Plateletes Day 30` < 50 |
+      `Platelets Day 60` < 50 |
+      `Platelets Day 90` < 50                                        ~ "YES",
+    is.na(`Plateletes Day 30`) |
+      is.na(`Platelets Day 60`) |
+      is.na(`Platelets Day 90`)                                          ~ NA_character_,
+    TRUE                                          ~ "NO"
+  )) %>%
+
+  mutate(`gr3_cytopenia≥30d` = case_when(
+    `ANC Day 30` < 1 |
+      `HgB Day 30` < 8 |
+      `Plateletes Day 30` < 50 |
+      `ANC Day 60` < 1 |
+      `HgB Day 60` < 8 |
+      `Platelets Day 60` < 50 |
+      `ANC Day 90` < 1 |
+      `HgB Day 90` < 8 |
+      `Platelets Day 90` < 50                                        ~ "YES",
+    is.na(`ANC Day 30`) |
+      is.na(`HgB Day 30`) |
+      is.na(`Plateletes Day 30`) |
+      is.na(`ANC Day 60`) |
+      is.na(`HgB Day 60`) |
+      is.na(`Platelets Day 60`) |
+      is.na(`ANC Day 90`) |
+      is.na(`HgB Day 90`) |
+      is.na(`Platelets Day 90`)                                       ~ NA_character_,
+    TRUE                                                              ~ "NO"
+  )) %>% 
+  mutate(cart_cell_dose = case_when(
+    `Cell Dose (million cells)` >= 400                               ~ "≥ 400",
+    `Cell Dose (million cells)` >= 300                               ~ "≥ 300",
+    TRUE                                                             ~ NA_character_
+  )) %>% 
   # mutate(`gr3_cytopenia_30d` = case_when(
@@
   # mutate(any_infection = case_when(
-  #   `Infection (yes, no)` == 1                                    ~ "Yes",
-  #   `Infection (yes, no)` == 0                                    ~ "No"
+  #   `Infection (Yes, No)` == 1                                    ~ "Yes",
+  #   `Infection (Yes, No)` == 0                                    ~ "No"
   # )) %>%
   # mutate(any_sevinfection = case_when(
-  #   `Severe Infection (yes, no)` == 1                              ~ "Yes",
-  #   `Severe Infection (yes, no)` == 0                              ~ "No"
-  # )) %>%
+  #   `Severe Infection (Yes, No)` == 1                              ~ "Yes",
+  #   `Severe Infection (Yes, No)` == 0                              ~ "No"
+  # )) %>% 
+  mutate(baseline_ferritin = case_when(
+    `Baseline Ferritin` >= 400                                    ~ "≥ ULN at LD",
+    `Baseline Ferritin` < 400                                    ~ "Normal"
+  )) %>% 
+  mutate(baseline_crp = case_when(
+    `Baseline CRP` >= 0.5                                    ~ "≥ ULN at LD",
+    `Baseline CRP` < 0.5                                    ~ "Normal"
+  )) %>% 
+  mutate(baseline_B2M = case_when(
+    `B2M` >= 5.5                                    ~ ">= 5.5",
+    `B2M` < 5.5                                    ~ "< 5.5"
+  )) %>%
 
@@
     TRUE                             ~ NA_character_
-  ))# %>%
+  )) %>% 
+  mutate(pfs_event = case_when(
+    is.na(`Date of PD`)                                ~ 0,
+    !is.na(`Date of PD`)                               ~ 1,
+    TRUE                                               ~ NA_real_
+  )) %>%
+
+  # Code survival
+  mutate(pfs_time = coalesce(`Date of PD`, `Date of Death`, `Date of Last Contact`)) %>% 
+  mutate(days_at_pfs_from_infusion = 
+           interval(
+             start = `Date of CAR T infusion (# of days from apharesis to infusion)`, 
+             end = pfs_time)/
+           duration(n=1, units = "days")) %>%
+
+  mutate(os_event = case_when(
+    is.na(`Date of Death`)                             ~ 0,
+    !is.na(`Date of Death`)                            ~ 1,
+    TRUE                                               ~ NA_real_
+  )) %>% 
+  mutate(os_time = coalesce(`Date of Death`, `Date of Last Contact`)) %>% 
+  mutate(days_at_os_from_infusion = 
+           interval(
+             start = `Date of CAR T infusion (# of days from apharesis to infusion)`, 
+             end = os_time)/
+           duration(n=1, units = "days"))
 
@@
 cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
   select(Age, agecat, male_sex, Sex,
@@
          POEMS,
-         `Non-secretory MM (Yes, No)`,
-
+         `Non-secretory MM (Yes, No)`, ################??????????
          `High Marrow Burden (>= 50%)`, 
@@
          `R-ISS at CAR-T infusion`, 
-
+         cytogenetics,
          `Deletion 17p prior to CAR-T infusion (yes, no)`,
@@
          `Platelets < 50K (Yes, No)`, 
-
+         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
          `Non-secretory MM (Yes, No)`,
@@
          `ICU Admission? (Yes, No)`,
-         `Tocilizumab (Yes, No)`,
-         `Steroid use (Yes, No)`,
-         `Anakinra (Yes, No)`,
+         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+         any_neutropenia,
+         Neutropenia_gr1, Neutropenia_gr2, 
+         Neutropenia_gr3, Neutropenia_gr4,
+         Anemia_gr1, Anemia_gr2,
+         Anemia_gr3, Anemia_gr4,
+         Thrombocytopenia_gr1, Thrombocytopenia_gr2,
+         Thrombocytopenia_gr3, Thrombocytopenia_gr4,
+         severe_neutro_30beyond, severe_anemia_30beyond,
+         severe_throm_30beyond,
 
          `Need for GCSF`,
-         `Need for TPO Agonist`
-
+         `Need for TPO Agonist`,
+         `Stem Cell Boost`
          ) %>% 
   tbl_summary(
-    # type = list(
-    # c(
-    #   `Length of Hospital Stay (Total Days including Readmission)`
-    #   ) ~ "continuous"),
+    type = list(
+      c(`ICU Admission? (Yes, No)`,
+        `Anakinra (Yes, No)`,
+        any_neutropenia,
+         Neutropenia_gr1, Neutropenia_gr2, 
+         Neutropenia_gr3, Neutropenia_gr4,
+         Anemia_gr1, Anemia_gr2,
+         Anemia_gr3, Anemia_gr4,
+         Thrombocytopenia_gr1, Thrombocytopenia_gr2,
+         Thrombocytopenia_gr3, Thrombocytopenia_gr4,
+        severe_neutro_30beyond, severe_anemia_30beyond,
+         severe_throm_30beyond,
+        `Need for GCSF`,
+        `Need for TPO Agonist`,
+        `Stem Cell Boost`
+      ) ~ "categorical"),
     statistic=list(all_continuous() ~ "{median} ({min}, {max}) [{p25}, {p75}]"), 
@@
 
-For responses make denominator evaluable patients
-Patient who died or was lost to follow-up or had non-secretory disease would not be evaluable
-
-## Table 3. Bone marrow biopsy findings
+## Table 3.Characteristics associated with grade ≥ 3 CRS, grade ≥ 3 neurotoxicity, grade ≥ 3 cytopenias ≥ 30 days, best response of ≥ CR at 3 months, best ORR 
+```{r}
+cart0 %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (Yes, No)`, 
+         `Disease status at time of referral (Relapsed vs Refractory)`,
+         `Plasma Cell Leukemia? (yes, no)`,
+         `Amyloid? (yes, no)`,
+         POEMS,
+         `Non-secretory MM (Yes, No)`, ################??????????
+         `High Marrow Burden (>= 50%)`, 
+         `ECOG at consult`, `ECOG at LD`, 
+         `R-ISS at CAR-T infusion`, 
+         cytogenetics,
+         `Deletion 17p prior to CAR-T infusion (yes, no)`,
+         `t(4:14) prior to CAR-T infusion (yes, no)`,
+         `t(14:16) prior to CAR-T infusion (yes, no)`,
+         `Bridging Therapy? (Yes, No)`,
+         `Number of prior lines of therapy`,
+         `Prior auto SCT (yes, no)`, 
+         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+         `Prior Allo SCT (Yes, No)`,
+         Blenrep,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+         `BCMA CAR-T on trial`, `Other BCMA trial`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         cart_cell_dose,
+         `Infection (Yes, No)`,
+         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+         baseline_ferritin, baseline_crp, baseline_B2M,
+         `ECOG > or = 2? (Yes, No)`,
+         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+         `LVEF <45% (Yes, No)`,
+         `ANC < 1000/uL (Yes, No)`,
+         `Hemoglobin < 8 g/dL (Yes, No)`,
+         `Platelets < 50K (Yes, No)`, 
+         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+         `Non-secretory MM (Yes, No)`,
+         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
+         gr3_CRS
+  ) %>% 
+  tbl_summary(by = gr3_CRS,
+              type = list(
+                c(
+                  `Extramedullary Disease? (Yes, No)`, 
+                  `Plasma Cell Leukemia? (yes, no)`,
+                  `Amyloid? (yes, no)`,
+                  POEMS,
+                  `Non-secretory MM (Yes, No)`,
+                  `High Marrow Burden (>= 50%)`,
+                  `ECOG at consult`, `ECOG at LD`,
+                  cytogenetics,
+                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
+                  `t(4:14) prior to CAR-T infusion (yes, no)`,
+                  `t(14:16) prior to CAR-T infusion (yes, no)`,
+                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
+                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+                  `Prior Allo SCT (Yes, No)`,
+                  Blenrep,
+                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+                  `BCMA CAR-T on trial`, `Other BCMA trial`,
+                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
+                  `Infection (Yes, No)`,
+                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+                  `ECOG > or = 2? (Yes, No)`,
+                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+                  `LVEF <45% (Yes, No)`,
+                  `ANC < 1000/uL (Yes, No)`,
+                  `Hemoglobin < 8 g/dL (Yes, No)`,
+                  `Platelets < 50K (Yes, No)`, 
+                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+                  `Non-secretory MM (Yes, No)`,
+
+                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
+                )
+                ~"categorical"),
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  add_p() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3 CRS**")
+```
+
+```{r}
+cart0 %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (Yes, No)`, 
+         `Disease status at time of referral (Relapsed vs Refractory)`,
+         `Plasma Cell Leukemia? (yes, no)`,
+         `Amyloid? (yes, no)`,
+         POEMS,
+         `Non-secretory MM (Yes, No)`, ################??????????
+         `High Marrow Burden (>= 50%)`, 
+         `ECOG at consult`, `ECOG at LD`, 
+         `R-ISS at CAR-T infusion`, 
+         cytogenetics,
+         `Deletion 17p prior to CAR-T infusion (yes, no)`,
+         `t(4:14) prior to CAR-T infusion (yes, no)`,
+         `t(14:16) prior to CAR-T infusion (yes, no)`,
+         `Bridging Therapy? (Yes, No)`,
+         `Number of prior lines of therapy`,
+         `Prior auto SCT (yes, no)`, 
+         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+         `Prior Allo SCT (Yes, No)`,
+         Blenrep,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+         `BCMA CAR-T on trial`, `Other BCMA trial`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         cart_cell_dose,
+         `Infection (Yes, No)`,
+         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+         baseline_ferritin, baseline_crp, baseline_B2M,
+         `ECOG > or = 2? (Yes, No)`,
+         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+         `LVEF <45% (Yes, No)`,
+         `ANC < 1000/uL (Yes, No)`,
+         `Hemoglobin < 8 g/dL (Yes, No)`,
+         `Platelets < 50K (Yes, No)`, 
+         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+         `Non-secretory MM (Yes, No)`,
+         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
+         gr3_ICANS
+  ) %>% 
+  tbl_summary(by = gr3_ICANS,
+              type = list(
+                c(
+                  `Extramedullary Disease? (Yes, No)`, 
+                  `Plasma Cell Leukemia? (yes, no)`,
+                  `Amyloid? (yes, no)`,
+                  POEMS,
+                  `Non-secretory MM (Yes, No)`,
+                  `High Marrow Burden (>= 50%)`,
+                  `ECOG at consult`, `ECOG at LD`,
+                  cytogenetics,
+                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
+                  `t(4:14) prior to CAR-T infusion (yes, no)`,
+                  `t(14:16) prior to CAR-T infusion (yes, no)`,
+                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
+                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+                  `Prior Allo SCT (Yes, No)`,
+                  Blenrep,
+                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+                  `BCMA CAR-T on trial`, `Other BCMA trial`,
+                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
+                  `Infection (Yes, No)`,
+                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+                  `ECOG > or = 2? (Yes, No)`,
+                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+                  `LVEF <45% (Yes, No)`,
+                  `ANC < 1000/uL (Yes, No)`,
+                  `Hemoglobin < 8 g/dL (Yes, No)`,
+                  `Platelets < 50K (Yes, No)`, 
+                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+                  `Non-secretory MM (Yes, No)`,
+
+                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
+                )
+                ~"categorical"),
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  add_p() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3 ICANS**")
+```
+
+```{r}
+cart0 %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (Yes, No)`, 
+         `Disease status at time of referral (Relapsed vs Refractory)`,
+         `Plasma Cell Leukemia? (yes, no)`,
+         `Amyloid? (yes, no)`,
+         POEMS,
+         `Non-secretory MM (Yes, No)`, ################??????????
+         `High Marrow Burden (>= 50%)`, 
+         `ECOG at consult`, `ECOG at LD`, 
+         `R-ISS at CAR-T infusion`, 
+         cytogenetics,
+         `Deletion 17p prior to CAR-T infusion (yes, no)`,
+         `t(4:14) prior to CAR-T infusion (yes, no)`,
+         `t(14:16) prior to CAR-T infusion (yes, no)`,
+         `Bridging Therapy? (Yes, No)`,
+         `Number of prior lines of therapy`,
+         `Prior auto SCT (yes, no)`, 
+         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+         `Prior Allo SCT (Yes, No)`,
+         Blenrep,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+         `BCMA CAR-T on trial`, `Other BCMA trial`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         cart_cell_dose,
+         `Infection (Yes, No)`,
+         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+         baseline_ferritin, baseline_crp, baseline_B2M,
+         `ECOG > or = 2? (Yes, No)`,
+         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+         `LVEF <45% (Yes, No)`,
+         `ANC < 1000/uL (Yes, No)`,
+         `Hemoglobin < 8 g/dL (Yes, No)`,
+         `Platelets < 50K (Yes, No)`, 
+         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+         `Non-secretory MM (Yes, No)`,
+         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
+         `gr3_cytopenia≥30d`
+  ) %>% 
+  tbl_summary(by = `gr3_cytopenia≥30d`,
+              type = list(
+                c(
+                  `Extramedullary Disease? (Yes, No)`, 
+                  `Plasma Cell Leukemia? (yes, no)`,
+                  `Amyloid? (yes, no)`,
+                  POEMS,
+                  `Non-secretory MM (Yes, No)`,
+                  `High Marrow Burden (>= 50%)`,
+                  `ECOG at consult`, `ECOG at LD`,
+                  cytogenetics,
+                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
+                  `t(4:14) prior to CAR-T infusion (yes, no)`,
+                  `t(14:16) prior to CAR-T infusion (yes, no)`,
+                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
+                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+                  `Prior Allo SCT (Yes, No)`,
+                  Blenrep,
+                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+                  `BCMA CAR-T on trial`, `Other BCMA trial`,
+                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
+                  `Infection (Yes, No)`,
+                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+                  `ECOG > or = 2? (Yes, No)`,
+                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+                  `LVEF <45% (Yes, No)`,
+                  `ANC < 1000/uL (Yes, No)`,
+                  `Hemoglobin < 8 g/dL (Yes, No)`,
+                  `Platelets < 50K (Yes, No)`, 
+                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+                  `Non-secretory MM (Yes, No)`,
+
+                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
+                )
+                ~"categorical"),
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  add_p() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3 cytopenia**")
+```
+
+```{r}
+cart0 %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (Yes, No)`, 
+         `Disease status at time of referral (Relapsed vs Refractory)`,
+         `Plasma Cell Leukemia? (yes, no)`,
+         `Amyloid? (yes, no)`,
+         POEMS,
+         `Non-secretory MM (Yes, No)`, ################??????????
+         `High Marrow Burden (>= 50%)`, 
+         `ECOG at consult`, `ECOG at LD`, 
+         `R-ISS at CAR-T infusion`, 
+         cytogenetics,
+         `Deletion 17p prior to CAR-T infusion (yes, no)`,
+         `t(4:14) prior to CAR-T infusion (yes, no)`,
+         `t(14:16) prior to CAR-T infusion (yes, no)`,
+         `Bridging Therapy? (Yes, No)`,
+         `Number of prior lines of therapy`,
+         `Prior auto SCT (yes, no)`, 
+         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+         `Prior Allo SCT (Yes, No)`,
+         Blenrep,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+         `BCMA CAR-T on trial`, `Other BCMA trial`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         cart_cell_dose,
+         `Infection (Yes, No)`,
+         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+         baseline_ferritin, baseline_crp, baseline_B2M,
+         `ECOG > or = 2? (Yes, No)`,
+         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+         `LVEF <45% (Yes, No)`,
+         `ANC < 1000/uL (Yes, No)`,
+         `Hemoglobin < 8 g/dL (Yes, No)`,
+         `Platelets < 50K (Yes, No)`, 
+         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+         `Non-secretory MM (Yes, No)`,
+         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
+         day90_response_sCRvsOthers
+  ) %>% 
+  tbl_summary(by = day90_response_sCRvsOthers,
+              type = list(
+                c(
+                  `Extramedullary Disease? (Yes, No)`, 
+                  `Plasma Cell Leukemia? (yes, no)`,
+                  `Amyloid? (yes, no)`,
+                  POEMS,
+                  `Non-secretory MM (Yes, No)`,
+                  `High Marrow Burden (>= 50%)`,
+                  `ECOG at consult`, `ECOG at LD`,
+                  cytogenetics,
+                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
+                  `t(4:14) prior to CAR-T infusion (yes, no)`,
+                  `t(14:16) prior to CAR-T infusion (yes, no)`,
+                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
+                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+                  `Prior Allo SCT (Yes, No)`,
+                  Blenrep,
+                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+                  `BCMA CAR-T on trial`, `Other BCMA trial`,
+                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
+                  `Infection (Yes, No)`,
+                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+                  `ECOG > or = 2? (Yes, No)`,
+                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+                  `LVEF <45% (Yes, No)`,
+                  `ANC < 1000/uL (Yes, No)`,
+                  `Hemoglobin < 8 g/dL (Yes, No)`,
+                  `Platelets < 50K (Yes, No)`, 
+                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+                  `Non-secretory MM (Yes, No)`,
+
+                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
+                )
+                ~"categorical"),
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  add_p() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**day90_response_sCRvsOthers**")
+```
+
+```{r}
+cart0 %>% 
+  select(Age, agecat, male_sex, Sex,
+         `Extramedullary Disease? (Yes, No)`, 
+         `Disease status at time of referral (Relapsed vs Refractory)`,
+         `Plasma Cell Leukemia? (yes, no)`,
+         `Amyloid? (yes, no)`,
+         POEMS,
+         `Non-secretory MM (Yes, No)`, ################??????????
+         `High Marrow Burden (>= 50%)`, 
+         `ECOG at consult`, `ECOG at LD`, 
+         `R-ISS at CAR-T infusion`, 
+         cytogenetics,
+         `Deletion 17p prior to CAR-T infusion (yes, no)`,
+         `t(4:14) prior to CAR-T infusion (yes, no)`,
+         `t(14:16) prior to CAR-T infusion (yes, no)`,
+         `Bridging Therapy? (Yes, No)`,
+         `Number of prior lines of therapy`,
+         `Prior auto SCT (yes, no)`, 
+         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+         `Prior Allo SCT (Yes, No)`,
+         Blenrep,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+         `BCMA CAR-T on trial`, `Other BCMA trial`,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         cart_cell_dose,
+         `Infection (Yes, No)`,
+         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+         baseline_ferritin, baseline_crp, baseline_B2M,
+         `ECOG > or = 2? (Yes, No)`,
+         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+         `LVEF <45% (Yes, No)`,
+         `ANC < 1000/uL (Yes, No)`,
+         `Hemoglobin < 8 g/dL (Yes, No)`,
+         `Platelets < 50K (Yes, No)`, 
+         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+         `Non-secretory MM (Yes, No)`,
+         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
+         ORR_90days
+  ) %>% 
+  tbl_summary(by = ORR_90days,
+              type = list(
+                c(
+                  `Extramedullary Disease? (Yes, No)`, 
+                  `Plasma Cell Leukemia? (yes, no)`,
+                  `Amyloid? (yes, no)`,
+                  POEMS,
+                  `Non-secretory MM (Yes, No)`,
+                  `High Marrow Burden (>= 50%)`,
+                  `ECOG at consult`, `ECOG at LD`,
+                  cytogenetics,
+                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
+                  `t(4:14) prior to CAR-T infusion (yes, no)`,
+                  `t(14:16) prior to CAR-T infusion (yes, no)`,
+                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
+                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+                  `Prior Allo SCT (Yes, No)`,
+                  Blenrep,
+                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+                  `BCMA CAR-T on trial`, `Other BCMA trial`,
+                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
+                  `Infection (Yes, No)`,
+                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+                  `ECOG > or = 2? (Yes, No)`,
+                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+                  `LVEF <45% (Yes, No)`,
+                  `ANC < 1000/uL (Yes, No)`,
+                  `Hemoglobin < 8 g/dL (Yes, No)`,
+                  `Platelets < 50K (Yes, No)`, 
+                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+                  `Non-secretory MM (Yes, No)`,
+
+                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
+                )
+                ~"categorical"),
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  add_p() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**ORR_90days**")
+```
+
+## Table 4.Characteristics associated with grade ≥ 3 CRS, grade ≥ 3 neurotoxicity, grade ≥ 3 cytopenias ≥ 30 days, best response of ≥ CR at 3 months, best ORR in Multivariable Models of Idecabtagene vicleucel-treated patients.
+```{r}
+
+```
+
 ```{r}
@@
 
-## Table 4. Supportive therapies and engraftment
-Jenn
+<!-- ## Table 4. Supportive therapies and engraftment -->
+<!-- Jenn -->
 
@@
 
-## Table S1. Apheresis and product characteristics
+<!-- ## Table S1. Apheresis and product characteristics -->
 ```{r}
@@
 
-## Table S2. Cytopenias following ide-cel
-**NAs are the patients who died (black) and test was not done (grey), they are remove from the denom (%) but not from the the N**
+<!-- ## Table S2. Cytopenias following ide-cel -->
+<!-- **NAs are the patients who died (black) and test was not done (grey), they are remove from the denom (%) but not from the the N** -->
 
 ```{r}
-# tbl1 <- cart0 %>% 
+# # tbl1 <- cart0 %>% 
+# #   distinct(patient_id, .keep_all = TRUE) %>% 
+# #   select("Leukopenia" = `Leukopenia_apheresis`, 
+# #          "Grade3+ Leukopenia" = `gr3_Leukopenia_apheresis`, 
+# #          "Neutropenia" = `Neutropenia_apheresis`, 
+# #          "Grade3+ Neutropenia" = `gr3_Neutropenia_apheresis`, 
+# #          "Anemia" = `Anemia_apheresis`, 
+# #          "Grade3+ Anemia" = `gr3_Anemia_apheresis`, 
+# #          "Thrombocytopenia" = `Thrombocytopenia_apheresis`, 
+# #          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_apheresis`
+# #   ) %>% 
+# #   tbl_summary(type = list(everything() ~ "dichotomous"),
+# #             digits = all_continuous() ~ 1#,
+# #             # missing = "no"
+# #             ) %>% 
+# #   bold_labels() %>% add_stat_label() %>% 
+# #   modify_footnote(update = everything() ~ NA)
+# # 
+# # tbl2 <- cart0 %>% 
+# #   distinct(patient_id, .keep_all = TRUE) %>% 
+# #   select("Leukopenia" = `Leukopenia_-5d`, 
+# #          "Grade3+ Leukopenia" = `gr3_Leukopenia_-5d`, 
+# #          "Neutropenia" = `Neutropenia_-5d`, 
+# #          "Grade3+ Neutropenia" = `gr3_Neutropenia_-5d`,
+# #          "Anemia" = `Anemia_-5d`, 
+# #          "Grade3+ Anemia" = `gr3_Anemia_-5d`, 
+# #          "Thrombocytopenia" = `Thrombocytopenia_-5d`, 
+# #          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_-5d`
+# #   ) %>% 
+# #   tbl_summary(type = list(everything() ~ "dichotomous"),
+# #             digits = all_continuous() ~ 1#,
+# #             # missing = "no"
+# #             ) %>% 
+# #   bold_labels() %>% add_stat_label() %>% 
+# #   modify_footnote(update = everything() ~ NA)
+# # 
+# # tbl3 <- cart0 %>% 
+# #   distinct(patient_id, .keep_all = TRUE) %>% 
+# #   select("Leukopenia" = `Leukopenia_0d`, 
+# #          "Grade3+ Leukopenia" = `gr3_Leukopenia_0d`, 
+# #          "Neutropenia" = `Neutropenia_0d`, 
+# #          "Grade3+ Neutropenia" = `gr3_Neutropenia_0d`, 
+# #          "Anemia" = `Anemia_0d`, 
+# #          "Grade3+ Anemia" = `gr3_Anemia_0d`,
+# #          "Thrombocytopenia" = `Thrombocytopenia_0d`, 
+# #          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_0d`
+# #   ) %>% 
+# #   tbl_summary(type = list(everything() ~ "dichotomous"),
+# #             digits = all_continuous() ~ 1#,
+# #             # missing = "no"
+# #             ) %>% 
+# #   bold_labels() %>% add_stat_label() %>% 
+# #   modify_footnote(update = everything() ~ NA)
+# 
+# tbl4 <- cart0 %>% 
 #   distinct(patient_id, .keep_all = TRUE) %>% 
-#   select("Leukopenia" = `Leukopenia_apheresis`, 
-#          "Grade3+ Leukopenia" = `gr3_Leukopenia_apheresis`, 
-#          "Neutropenia" = `Neutropenia_apheresis`, 
-#          "Grade3+ Neutropenia" = `gr3_Neutropenia_apheresis`, 
-#          "Anemia" = `Anemia_apheresis`, 
-#          "Grade3+ Anemia" = `gr3_Anemia_apheresis`, 
-#          "Thrombocytopenia" = `Thrombocytopenia_apheresis`, 
-#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_apheresis`
+#   select(#"Leukopenia" = `Leukopenia_7d`, 
+#          # "Grade3+ Leukopenia" = `gr3_Leukopenia_7d`, 
+#          "Neutropenia" = `Neutropenia_7d`, 
+#          "Grade3+ Neutropenia" = `gr3_Neutropenia_7d`, 
+#          # "Anemia" = `Anemia_7d`, 
+#          # "Grade3+ Anemia" = `gr3_Anemia_7d`, 
+#          "Thrombocytopenia" = `Thrombocytopenia_7d`, 
+#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_7d`
 #   ) %>% 
@@
 # 
-# tbl2 <- cart0 %>% 
+# # tbl5 <- cart0 %>% 
+# #   distinct(patient_id, .keep_all = TRUE) %>% 
+# #   filter(is.na(Not_evaluable_at_14days)) %>% 
+# #   select("Leukopenia" = `Leukopenia_14d`, 
+# #          "Grade3+ Leukopenia" = `gr3_Leukopenia_14d`, 
+# #          "Neutropenia" = `Neutropenia_14d`, 
+# #          "Grade3+ Neutropenia" = `gr3_Neutropenia_14d`,
+# #          "Anemia" = `Anemia_14d`, 
+# #          "Grade3+ Anemia" = `gr3_Anemia_14d`,
+# #          "Thrombocytopenia" = `Thrombocytopenia_14d`, 
+# #          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_14d` 
+# #   ) %>% 
+# #   tbl_summary(type = list(everything() ~ "dichotomous"),
+# #             digits = all_continuous() ~ 1#,
+# #             # missing = "no"
+# #             ) %>% 
+# #   bold_labels() %>% add_stat_label() %>% 
+# #   modify_footnote(update = everything() ~ NA)
+# # 
+# # tbl6 <- cart0 %>% 
+# #   distinct(patient_id, .keep_all = TRUE) %>% 
+# #   filter(is.na(Not_evaluable_at_21days)) %>% 
+# #   select("Leukopenia" = `Leukopenia_21d`,
+# #          "Grade3+ Leukopenia" = `gr3_Leukopenia_21d`, 
+# #          "Neutropenia" = `Neutropenia_21d`, 
+# #          "Grade3+ Neutropenia" = `gr3_Neutropenia_21d`, 
+# #          "Anemia" = `Anemia_21d`, 
+# #          "Grade3+ Anemia" = `gr3_Anemia_21d`,
+# #          "Thrombocytopenia" = `Thrombocytopenia_21d`, 
+# #          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_21d`
+# #   ) %>% 
+# #   tbl_summary(type = list(everything() ~ "dichotomous"),
+# #             digits = all_continuous() ~ 1#,
+# #             # missing = "no"
+# #             ) %>% 
+# #   bold_labels() %>% add_stat_label() %>% 
+# #   modify_footnote(update = everything() ~ NA)
+# 
+# tbl7 <- cart0 %>% 
 #   distinct(patient_id, .keep_all = TRUE) %>% 
-#   select("Leukopenia" = `Leukopenia_-5d`, 
-#          "Grade3+ Leukopenia" = `gr3_Leukopenia_-5d`, 
-#          "Neutropenia" = `Neutropenia_-5d`, 
-#          "Grade3+ Neutropenia" = `gr3_Neutropenia_-5d`,
-#          "Anemia" = `Anemia_-5d`, 
-#          "Grade3+ Anemia" = `gr3_Anemia_-5d`, 
-#          "Thrombocytopenia" = `Thrombocytopenia_-5d`, 
-#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_-5d`
+#   filter(is.na(Not_evaluable_at_30days)) %>% 
+#   select(#"Leukopenia" = `Leukopenia_30d`, 
+#          # "Grade3+ Leukopenia" = `gr3_Leukopenia_30d`,
+#          "Neutropenia" = `Neutropenia_30d`, 
+#          "Grade3+ Neutropenia" = `gr3_Neutropenia_30d`,
+#          # "Anemia" = `Anemia_30d`, 
+#          # "Grade3+ Anemia" = `gr3_Anemia_30d`, 
+#          "Thrombocytopenia" = `Thrombocytopenia_30d`,
+#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_30d` 
 #   ) %>% 
@@
 # 
-# tbl3 <- cart0 %>% 
+# tbl8 <- cart0 %>% 
 #   distinct(patient_id, .keep_all = TRUE) %>% 
-#   select("Leukopenia" = `Leukopenia_0d`, 
-#          "Grade3+ Leukopenia" = `gr3_Leukopenia_0d`, 
-#          "Neutropenia" = `Neutropenia_0d`, 
-#          "Grade3+ Neutropenia" = `gr3_Neutropenia_0d`, 
-#          "Anemia" = `Anemia_0d`, 
-#          "Grade3+ Anemia" = `gr3_Anemia_0d`,
-#          "Thrombocytopenia" = `Thrombocytopenia_0d`, 
-#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_0d`
+#   filter(is.na(Not_evaluable_at_90days)) %>% 
+#   select(#"Leukopenia" = `Leukopenia_90d`, 
+#          # "Grade3+ Leukopenia" = `gr3_Leukopenia_90d`,
+#          "Neutropenia" = `Neutropenia_90d`, 
+#          "Grade3+ Neutropenia" = `gr3_Neutropenia_90d`,
+#          # "Anemia" = `Anemia_90d`,
+#          # "Grade3+ Anemia" = `gr3_Anemia_90d`,
+#          "Thrombocytopenia" = `Thrombocytopenia_90d`, 
+#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_90d`
 #   ) %>% 
@@
 #   modify_footnote(update = everything() ~ NA)
-
-tbl4 <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(#"Leukopenia" = `Leukopenia_7d`, 
-         # "Grade3+ Leukopenia" = `gr3_Leukopenia_7d`, 
-         "Neutropenia" = `Neutropenia_7d`, 
-         "Grade3+ Neutropenia" = `gr3_Neutropenia_7d`, 
-         # "Anemia" = `Anemia_7d`, 
-         # "Grade3+ Anemia" = `gr3_Anemia_7d`, 
-         "Thrombocytopenia" = `Thrombocytopenia_7d`, 
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_7d`
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-            digits = all_continuous() ~ 1#,
-            # missing = "no"
-            ) %>% 
-  bold_labels() %>% add_stat_label() %>% 
-  modify_footnote(update = everything() ~ NA)
-
-# tbl5 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_14days)) %>% 
-#   select("Leukopenia" = `Leukopenia_14d`, 
-#          "Grade3+ Leukopenia" = `gr3_Leukopenia_14d`, 
-#          "Neutropenia" = `Neutropenia_14d`, 
-#          "Grade3+ Neutropenia" = `gr3_Neutropenia_14d`,
-#          "Anemia" = `Anemia_14d`, 
-#          "Grade3+ Anemia" = `gr3_Anemia_14d`,
-#          "Thrombocytopenia" = `Thrombocytopenia_14d`, 
-#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_14d` 
-#   ) %>% 
-#   tbl_summary(type = list(everything() ~ "dichotomous"),
-#             digits = all_continuous() ~ 1#,
-#             # missing = "no"
-#             ) %>% 
-#   bold_labels() %>% add_stat_label() %>% 
-#   modify_footnote(update = everything() ~ NA)
-# 
-# tbl6 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_21days)) %>% 
-#   select("Leukopenia" = `Leukopenia_21d`,
-#          "Grade3+ Leukopenia" = `gr3_Leukopenia_21d`, 
-#          "Neutropenia" = `Neutropenia_21d`, 
-#          "Grade3+ Neutropenia" = `gr3_Neutropenia_21d`, 
-#          "Anemia" = `Anemia_21d`, 
-#          "Grade3+ Anemia" = `gr3_Anemia_21d`,
-#          "Thrombocytopenia" = `Thrombocytopenia_21d`, 
-#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_21d`
-#   ) %>% 
-#   tbl_summary(type = list(everything() ~ "dichotomous"),
-#             digits = all_continuous() ~ 1#,
-#             # missing = "no"
-#             ) %>% 
-#   bold_labels() %>% add_stat_label() %>% 
-#   modify_footnote(update = everything() ~ NA)
-
-tbl7 <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  filter(is.na(Not_evaluable_at_30days)) %>% 
-  select(#"Leukopenia" = `Leukopenia_30d`, 
-         # "Grade3+ Leukopenia" = `gr3_Leukopenia_30d`,
-         "Neutropenia" = `Neutropenia_30d`, 
-         "Grade3+ Neutropenia" = `gr3_Neutropenia_30d`,
-         # "Anemia" = `Anemia_30d`, 
-         # "Grade3+ Anemia" = `gr3_Anemia_30d`, 
-         "Thrombocytopenia" = `Thrombocytopenia_30d`,
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_30d` 
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-            digits = all_continuous() ~ 1#,
-            # missing = "no"
-            ) %>% 
-  bold_labels() %>% add_stat_label() %>% 
-  modify_footnote(update = everything() ~ NA)
-
-tbl8 <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  filter(is.na(Not_evaluable_at_90days)) %>% 
-  select(#"Leukopenia" = `Leukopenia_90d`, 
-         # "Grade3+ Leukopenia" = `gr3_Leukopenia_90d`,
-         "Neutropenia" = `Neutropenia_90d`, 
-         "Grade3+ Neutropenia" = `gr3_Neutropenia_90d`,
-         # "Anemia" = `Anemia_90d`,
-         # "Grade3+ Anemia" = `gr3_Anemia_90d`,
-         "Thrombocytopenia" = `Thrombocytopenia_90d`, 
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_90d`
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-            digits = all_continuous() ~ 1#,
-            # missing = "no"
-            ) %>% 
-  bold_labels() %>% add_stat_label() %>% 
-  modify_footnote(update = everything() ~ NA)
-
-tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), 
-          tab_spanner = c("Apheresis", "Day -5",	"Day 0",	"Day 7",	"Day 14",	"Day 21",	"Day 30",	"Day 90")) %>% as_gt() %>%
-  gt::tab_source_note(gt::md("**Not evaluable patients are removed from the denominator <br>
-                             1 patient has missing 90 days values**"))
+# 
+# tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), 
+#           tab_spanner = c("Apheresis", "Day -5",	"Day 0",	"Day 7",	"Day 14",	"Day 21",	"Day 30",	"Day 90")) %>% as_gt() %>%
+#   gt::tab_source_note(gt::md("**Not evaluable patients are removed from the denominator <br>
+#                              1 patient has missing 90 days values**"))
 ```
 
-## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30
-**Make sure that if one of wbc, anc, hb or plt is NA then cytopenia should be NA**
-```{r}
-# cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_30days)) %>% 
-#   select(Age, agecat, male_sex, Sex,
-#          `Extramedullary Disease? (Yes, No)`, 
-#          `High Marrow Burden (>= 50%)`, `ECOG at LD`, `R-ISS at CAR-T infusion`, #cyto, 
-#          `Bridging Therapy? (Yes, No)`,
-#          `Prior auto SCT (yes, no)`, 
-#          `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
-#          immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-#          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
-#          `gr3_cytopenia_30d`) %>% 
-#   tbl_summary(by = `gr3_cytopenia_30d`,
-#     type = list(
-#     `Extramedullary Disease? (Yes, No)` ~ "categorical",
-#     # cyto ~ "categorical",
-#     `Bridging Therapy? (Yes, No)` ~ "categorical",
-#     `Prior auto SCT (yes, no)` ~ "categorical",
-#     immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
-#     doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
-#     `Did patient met criteria for KarMMa1 pre-CAR-T?` ~"categorical"),
-#     
-#     statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
-#     digits = all_continuous() ~ 1
-#     ) %>% 
-#   bold_labels() %>% add_stat_label() %>% add_p() %>% 
-#   modify_footnote(update = everything() ~ NA) %>%
-#   modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
-```
-
-## Table S3. Patient characteristics by grade 3+ cytopenia at Day 90
-```{r}
-# cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_90days)) %>% 
-#   select(Age, agecat, male_sex, Sex,
-#          `Extramedullary Disease? (Yes, No)`, 
-#          `High Marrow Burden (>= 50%)`, `ECOG at LD`, `R-ISS at CAR-T infusion`, #cyto, 
-#          `Bridging Therapy? (Yes, No)`,
-#          `Prior auto SCT (yes, no)`,
-#          `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
-#          immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-#          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
-#          `gr3_cytopenia_90d`) %>% 
-#   tbl_summary(by = `gr3_cytopenia_90d`,
-#     type = list(
-#     `Extramedullary Disease? (Yes, No)` ~ "categorical",
-#     cyto ~ "categorical",
-#     `Bridging Therapy? (Yes, No)` ~ "categorical",
-#     `Prior auto SCT (yes, no)` ~ "categorical",
-#     immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
-#     doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
-#     `Did patient met criteria for KarMMa1 pre-CAR-T?` ~"categorical"),
-#     
-#     statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
-#     digits = all_continuous() ~ 1
-#     ) %>% 
-#   bold_labels() %>% add_stat_label() %>%  add_p() %>% 
-#   modify_footnote(update = everything() ~ NA) %>%
-#   modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 90?**")
-```
-
-## Table S4. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
-```{r}
-# tbl1 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_30days)) %>% 
-#   select(CRS_gradecat,
-#          `Day of onset of CRS relative to infusion`,
-#          `Day of Max CRS (relative to infusion)`, `Duration of CRS (days)`, 
-#          
-#          ICANS_gradecat,
-#          `Day of onset of ICANS relative to infusion`,
-#          `Day of Max ICANS (relative to infusion)`,
-#          `Duration of ICANS (days)`, gr3_cytopenia_30d) %>% 
-#   tbl_summary(by =`gr3_cytopenia_30d`,
-#               type = list(
-#     c(`Day of onset of CRS relative to infusion`, 
-#       `Day of Max CRS (relative to infusion)`,
-#       `Day of onset of ICANS relative to infusion`,
-#       `Day of Max ICANS (relative to infusion)`, `Duration of ICANS (days)`) ~ "continuous"),
-#     statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-#     digits = all_continuous() ~ 1,
-#     missing = "no") %>% 
-#   bold_labels() %>% add_stat_label() %>% add_p() %>% 
-#   modify_footnote(update = everything() ~ NA) %>%
-#   modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
-# 
-# tbl2 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_30days)) %>% 
-#   select(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, 
-#          `Anakinra (Yes=1, No=0)`, gr3_cytopenia_30d) %>% 
-#   tbl_summary(by =`gr3_cytopenia_30d`,
-#               type = list(
-#     c(`Steroid use (Yes=1, No=0)`, `Tocilizumab (Yes=1, No=0)`, 
-#       `Anakinra (Yes=1, No=0)`) ~ "categorical"),
-#     statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-#     digits = all_continuous() ~ 1) %>% 
-#   bold_labels() %>% add_stat_label() %>% add_p()
-# 
-# tbl3 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_30days)) %>% 
-#   select(#MRDneg_30days,
-#          ORR_30days, day30_response_sCRvsOthers,
-#          day30_response_group, gr3_cytopenia_30d) %>% 
-#   tbl_summary(by =`gr3_cytopenia_30d`,
-#     #           type = list(
-#     # c(MRDneg_30days) ~ "categorical"),
-#     digits = all_continuous() ~ 1,
-#     missing = "no") %>% 
-#   bold_labels() %>% add_stat_label() %>% add_p()
-# 
-# # tbl4 <- cart0 %>% 
-# #   distinct(patient_id, .keep_all = TRUE) %>% 
-# #   filter(is.na(Not_evaluable_at_30days)) %>% 
-# #   filter(day30_response_group == "CR or sCR") %>% 
-# #   select(MRDneg_30days, gr3_cytopenia_30d) %>% 
-# #   tbl_summary(by =`gr3_cytopenia_30d`,
-# #               type = list(c(MRDneg_30days) ~ "categorical"),
-# #               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
-# #               digits = all_continuous() ~ 1,
-# #               missing = "no") %>% 
-# #   bold_labels() %>% add_stat_label() %>% add_p()
-# 
-# tbl5 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_30days)) %>% 
-#   select(#MRDneg_90days,
-#          ORR_90days, day90_response_sCRvsOthers,
-#          day90_response_group, gr3_cytopenia_30d) %>% 
-#   tbl_summary(by =`gr3_cytopenia_30d`,
-#     #           type = list(
-#     # c(MRDneg_90days) ~ "categorical"),
-#     digits = all_continuous() ~ 1,
-#     missing = "no") %>% 
-#   bold_labels() %>% add_stat_label() %>% add_p()
-# 
-# # tbl6 <- cart0 %>% 
-# #   distinct(patient_id, .keep_all = TRUE) %>% 
-# #   filter(is.na(Not_evaluable_at_30days)) %>% 
-# #   filter(day90_response_group == "CR or sCR") %>% 
-# #   select(MRDneg_90days, gr3_cytopenia_30d) %>% 
-# #   tbl_summary(by =`gr3_cytopenia_30d`,
-# #               type = list(c(MRDneg_90days) ~ "categorical"),
-# #               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
-# #               digits = all_continuous() ~ 1,
-# #               missing = "no") %>% 
-# #   bold_labels() %>% add_stat_label() %>% add_p()
-# 
-# tbl7 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_30days)) %>% 
-#   select(best_response, gr3_cytopenia_30d) %>% 
-#   tbl_summary(by =`gr3_cytopenia_30d`,
-#               #type = list(c(MRDneg_90days) ~ "categorical"),
-#               label = list(best_response ~ "best response in the first 90 days"),
-#               digits = all_continuous() ~ 1,
-#               missing = "no") %>% 
-#   bold_labels() %>% add_stat_label() %>% add_p()
-# 
-# # tbl8 <- cart0 %>% 
-# #   distinct(patient_id, .keep_all = TRUE) %>% 
-# #   filter(is.na(Not_evaluable_at_30days)) %>% 
-# #   filter(best_response == "CR or sCR") %>% 
-# #   select(MRDneg_in_best_response, gr3_cytopenia_30d) %>% 
-# #   tbl_summary(by =`gr3_cytopenia_30d`,
-# #               type = list(c(MRDneg_in_best_response) ~ "categorical"),
-# #               label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
-# #               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-# #               digits = all_continuous() ~ 1,
-# #               missing = "no") %>% 
-# #   bold_labels() %>% add_stat_label() %>% add_p()
-# 
-# tbl_stack(list(tbl1, tbl2, tbl3, tbl5, tbl7))
-```
-
-## Table S4. Details of infections after ide-cel
-Jenn
-
-## Table S5. Patients with infections in the first 30 days by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
+### Figures
+
+## Figure 1. Response rate bar graph for day 30, day 90, Best ORR
+**Need to include MRD in the var**
 ```{r}
 cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(CRS_gradecat, ICANS_gradecat,
-         `Steroid use (Yes=1, No=0)`, 
-         `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`,
-         `Bridging Therapy? (Yes, No)`, any_infection) %>% 
-  tbl_summary(by=any_infection, 
-              type = list(all_dichotomous() ~ "categorical")) %>%
-  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
-  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Any infection**")
-
-cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(CRS_gradecat, ICANS_gradecat,
-         `Steroid use (Yes=1, No=0)`, 
-         `Tocilizumab (Yes=1, No=0)`, `Anakinra (Yes=1, No=0)`,
-         `Bridging Therapy? (Yes, No)`, any_sevinfection) %>% 
-  tbl_summary(by=any_sevinfection, 
-              type = list(all_dichotomous() ~ "categorical")) %>%
-  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
-  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
+  select(day30_response_group, day90_response_group, best_response) %>% 
+  pivot_longer(cols = everything()) %>% 
+  group_by(name, value) %>% 
+  summarise(count=n()) %>% 
+  mutate(percent=(count/sum(count)*100)
+  ) %>% 
+  filter(!is.na(value)) %>% 
+  ggplot(aes(x= name, y= percent, fill= value))+
+  geom_bar(stat = "identity")+
+  scale_fill_brewer(palette = "RdBu")+
+  # labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
+  theme_classic()
 ```
 
-## Table S6. Patients with infections in the first 100 days by cell counts and immunoglobulin levels
+Panel B: PFS Kaplan Meier (from CAR-T infusion)
+
 ```{r}
-cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(`IgG day -5`, `IgA day -5`, `IgM day -5`,
-         `WBC day -5 (k/ul)`, `ANC day -5 (k/ul)`,
-         `Eos day -5 (k/ul)`, `Monos day -5 (k/ul)`,
-         `CD3 apheresis`, `CD4 apheresis`, `CD8 apheresis`,
-         `CD56 apheresis`, `CD19 apheresis`, 
-         `CD3 day +90`, `CD4 day +90`, `CD8 day +90`,
-         `CD56 day +90`, `CD19 day +90`,
-         any_infection) %>%
-
-  tbl_summary(by = any_infection,
-
-              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1) %>% 
-  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
-  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Any infection**")
-
-cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(`IgG day -5`, `IgA day -5`, `IgM day -5`,
-         `WBC apheresis`, `ANC apheresis`,
-         `Eos apheresis`, `Monos apheresis`,
-         `CD3 apheresis`, `CD4 apheresis`, `CD8 apheresis`,
-         `CD56 apheresis`, `CD19 apheresis`, 
-         `CD3 day +90`, `CD4 day +90`, `CD8 day +90`,
-         `CD56 day +90`, `CD19 day +90`,
-         any_sevinfection) %>%
-
-  tbl_summary(by = any_sevinfection,
-
-              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1) %>% 
-  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
-  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
+ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
+                   data = cart0),
+           title = "PFS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in days)" 
+) + guides(colour = guide_legend(ncol = 2))
 ```
 
-### Figures
-
-## Figure 1. Consort diagram
-
-## Figure 2. Inflammatory markers after ide-cel
+Panel C: OS Kaplan Meier (from CAR-T infusion)
+```{r}
+ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ 1, 
+                   data = cart0),
+           title = "OS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in days)" 
+) + guides(colour = guide_legend(ncol = 2))
+```
+
+Panel D: Duration of response graph
+```{r}
+
+```
+
+## Figure 2. Consort diagram
+
+<!-- ## Figure 2. Inflammatory markers after ide-cel -->
 ```{r, fig.height=12}
-LDH <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(`LDH at Pre-Leukapheresis`, `LDH day -5`, `LDH day 0`, 
-         `LDH day +7`, `LDH day +14`, `LDH day +21`, `LDH day +30`)
-LDH_long <- gather(LDH, day, LDH_value, `LDH at Pre-Leukapheresis`:`LDH day +30`)
-LDH_long$day[LDH_long$day=="LDH at Pre-Leukapheresis"] <- "Pre"
-LDH_long$day[LDH_long$day=="LDH day -5"] <- "Day -5"
-LDH_long$day[LDH_long$day=="LDH day 0"] <- "Day 0"
-LDH_long$day[LDH_long$day=="LDH day +7"] <- "Day 7"
-LDH_long$day[LDH_long$day=="LDH day +14"] <- "Day 14"
-LDH_long$day[LDH_long$day=="LDH day +21"] <- "Day 21"
-LDH_long$day[LDH_long$day=="LDH day +30"] <- "Day 30"
-LDH_long$day <- factor(LDH_long$day, levels = c("Pre", "Day -5", "Day 0", 
-                                                "Day 7", "Day 14", "Day 21", "Day 30"))
-# ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
-#   geom_boxplot() + xlab("Days") + ylab("LDH") + 
+# LDH <- cart0 %>% 
+#   distinct(patient_id, .keep_all = TRUE) %>% 
+#   select(`LDH at Pre-Leukapheresis`, `LDH day -5`, `LDH day 0`, 
+#          `LDH day +7`, `LDH day +14`, `LDH day +21`, `LDH day +30`)
+# LDH_long <- gather(LDH, day, LDH_value, `LDH at Pre-Leukapheresis`:`LDH day +30`)
+# LDH_long$day[LDH_long$day=="LDH at Pre-Leukapheresis"] <- "Pre"
+# LDH_long$day[LDH_long$day=="LDH day -5"] <- "Day -5"
+# LDH_long$day[LDH_long$day=="LDH day 0"] <- "Day 0"
+# LDH_long$day[LDH_long$day=="LDH day +7"] <- "Day 7"
+# LDH_long$day[LDH_long$day=="LDH day +14"] <- "Day 14"
+# LDH_long$day[LDH_long$day=="LDH day +21"] <- "Day 21"
+# LDH_long$day[LDH_long$day=="LDH day +30"] <- "Day 30"
+# LDH_long$day <- factor(LDH_long$day, levels = c("Pre", "Day -5", "Day 0", 
+#                                                 "Day 7", "Day 14", "Day 21", "Day 30"))
+# # ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
+# #   geom_boxplot() + xlab("Days") + ylab("LDH") + 
+# #   geom_jitter(color= "grey")+
+# #   theme_classic() + ggtitle("LDH") + 
+# #   expand_limits(y = c(0, 7000)) + 
+# #   scale_y_break(c(1188, 4000), 
+# #                 ticklabels=c(4000, 7000), scales=0.10) 
+# 
+# # cart0$`Ferritin day +7`[cart0$`Ferritin day +7`==">33511"] <- 33511
+# # cart0$`Ferritin day +7` <- as.numeric(cart0$`Ferritin day +7`)
+# Ferritin <- cart0 %>% 
+#   distinct(patient_id, .keep_all = TRUE) %>% 
+#   select(patient_id, `Ferritin at Pre-Leukapheresis`, `Ferritin day -5`,
+#          `Ferritin day 0`, `Ferritin day +7`, `Ferritin day +14`, 
+#          `Ferritin day +21`, `Ferritin day +30`)
+# Ferritin_long <- gather(Ferritin, day, Ferritin_value, `Ferritin at Pre-Leukapheresis`:`Ferritin day +30`)
+# Ferritin_long$day[Ferritin_long$day=="Ferritin at Pre-Leukapheresis"] <- "Pre"
+# Ferritin_long$day[Ferritin_long$day=="Ferritin day -5"] <- "Day -5"
+# Ferritin_long$day[Ferritin_long$day=="Ferritin day 0"] <- "Day 0"
+# Ferritin_long$day[Ferritin_long$day=="Ferritin day +7"] <- "Day 7"
+# Ferritin_long$day[Ferritin_long$day=="Ferritin day +14"] <- "Day 14"
+# Ferritin_long$day[Ferritin_long$day=="Ferritin day +21"] <- "Day 21"
+# Ferritin_long$day[Ferritin_long$day=="Ferritin day +30"] <- "Day 30"
+# Ferritin_long$day <- factor(Ferritin_long$day, levels = c("Pre", "Day -5", "Day 0",
+#                                                           "Day 7", "Day 14", "Day 21", "Day 30"))
+# # ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
+# #   geom_boxplot() + 
+# #   xlab("Days") + ylab("Ferritin") + 
+# #   theme_classic() + ggtitle("Ferritin") + 
+# #   expand_limits(y = c(0, 34000)) +
+# #   scale_y_break(c(13600, 33000), ticklabels=c(33000, 34000), scales=0.10)
+# 
+# # cart0$`CRP Pre-Leukapheresis`[cart0$`CRP Pre-Leukapheresis`=="<0.03"] <- 0.07
+# # cart0$`CRP Pre-Leukapheresis` <- as.numeric(cart0$`CRP Pre-Leukapheresis`)
+# # cart0$`CRP day +14`[cart0$`CRP day +14`=="<0.03"] <- 0.07
+# # cart0$`CRP day +14` <- as.numeric(cart0$`CRP day +14`)
+# # cart0$`CRP day +21`[cart0$`CRP day +21`=="<0.03"] <- 0.07
+# # cart0$`CRP day +21` <- as.numeric(cart0$`CRP day +21`)
+# # cart0$`CRP day +30`[cart0$`CRP day +30`=="<0.03"] <- 0.07
+# # cart0$`CRP day +30` <- as.numeric(cart0$`CRP day +30`)
+# CRP <- cart0 %>%
+#   distinct(patient_id, .keep_all = TRUE) %>% 
+#   select(`CRP Pre-Leukapheresis`, `CRP day -5`, `CRP day 0`,
+#          `CRP day +7`, `CRP day +14`, `CRP day +21`, `CRP day +30`)
+# CRP_long <- gather(CRP, day, CRP_value, `CRP Pre-Leukapheresis`:`CRP day +30`)
+# CRP_long$day[CRP_long$day=="CRP Pre-Leukapheresis"] <- "Pre"
+# CRP_long$day[CRP_long$day=="CRP day -5"] <- "Day -5"
+# CRP_long$day[CRP_long$day=="CRP day 0"] <- "Day 0"
+# CRP_long$day[CRP_long$day=="CRP day +7"] <- "Day 7"
+# CRP_long$day[CRP_long$day=="CRP day +14"] <- "Day 14"
+# CRP_long$day[CRP_long$day=="CRP day +21"] <- "Day 21"
+# CRP_long$day[CRP_long$day=="CRP day +30"] <- "Day 30"
+# CRP_long$day <- factor(CRP_long$day, levels = c("Pre", "Day -5", "Day 0", "Day 7", "Day 14", "Day 21", "Day 30"))
+# # ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+# #   geom_boxplot() + 
+# #   xlab("Days") + ylab("CRP") + 
+# #   theme_classic() + ggtitle("CRP") + 
+# #   expand_limits(y = c(0, 20)) +
+# #   scale_y_break(c(4.55, 7.5, 9.5, 18.0), ticklabels=c(8,9,18, 20), 
+# #                 scales=c(0.10)
+# #                 )
+# 
+# # ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+# #   geom_violin() + 
+# #   xlab("Days") + ylab("CRP") + 
+# #   theme_classic() + ggtitle("CRP")+
+# #   expand_limits(y = c(0, 20)) +
+# #   scale_y_break(c(5.9, 18.0), ticklabels=c(18, 20), 
+# #                 scales=c(0.25)
+# #                 )
+# # 
+# # ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+# #   geom_violin() + 
+# #   xlab("Days") + ylab("CRP") + 
+# #   theme_classic() + ggtitle("log10 CRP") + 
+# #   expand_limits(y = c(0, 100)) +
+# #   scale_y_log10()
+# # 
+# # ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+# #   geom_violin() + 
+# #   xlab("Days") + ylab("log2 CRP") + 
+# #   theme_classic() + ggtitle("CRP") + 
+# #   # expand_limits(y = c(0, 100)) +
+# #   scale_y_continuous(trans = "log2")
+# 
+# 
+# 
+# 
+# 
+# 
+# 
+# 
+# #   geom_jitter(color= "grey")+
+# 
+# 
+# 
+# a <- ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
+#   geom_boxplot() + 
+#   xlab("Days") + ylab("LDH represented with a log2 scale") + 
+#   theme_classic() + ggtitle("LDH") + 
+#   scale_y_continuous(trans = "log2") +
+#   stat_compare_means(label.x = 5 
+#                      # aes(label = paste0("p = ", ..p.format..))
+#   #                  aes(
+#   # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
+#   )
+# 
+# b <- ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
+#   geom_boxplot() + 
+#   xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
+#   theme_classic() + ggtitle("Ferritin") + 
+#   scale_y_continuous(trans = "log2") +
+#   stat_compare_means(label.x = 5)
+# 
+# c <- ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+#   geom_boxplot() + 
+#   xlab("Days") + ylab("CRP represented with a log2 scale") + 
+#   theme_classic() + ggtitle("CRP") + 
+#   scale_y_continuous(trans = "log2") +
+#   stat_compare_means(label.x = 5)
+# 
+# (a) /
+# (b) /
+# (c)+
+# plot_annotation(tag_levels = "A")
+# 
+# a <- ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
+#   geom_boxplot() + 
 #   geom_jitter(color= "grey")+
+#   xlab("Days") + ylab("LDH represented with a log2 scale") + 
 #   theme_classic() + ggtitle("LDH") + 
-#   expand_limits(y = c(0, 7000)) + 
-#   scale_y_break(c(1188, 4000), 
-#                 ticklabels=c(4000, 7000), scales=0.10)
-
-# cart0$`Ferritin day +7`[cart0$`Ferritin day +7`==">33511"] <- 33511
-# cart0$`Ferritin day +7` <- as.numeric(cart0$`Ferritin day +7`)
-Ferritin <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(patient_id, `Ferritin at Pre-Leukapheresis`, `Ferritin day -5`,
-         `Ferritin day 0`, `Ferritin day +7`, `Ferritin day +14`, 
-         `Ferritin day +21`, `Ferritin day +30`)
-Ferritin_long <- gather(Ferritin, day, Ferritin_value, `Ferritin at Pre-Leukapheresis`:`Ferritin day +30`)
-Ferritin_long$day[Ferritin_long$day=="Ferritin at Pre-Leukapheresis"] <- "Pre"
-Ferritin_long$day[Ferritin_long$day=="Ferritin day -5"] <- "Day -5"
-Ferritin_long$day[Ferritin_long$day=="Ferritin day 0"] <- "Day 0"
-Ferritin_long$day[Ferritin_long$day=="Ferritin day +7"] <- "Day 7"
-Ferritin_long$day[Ferritin_long$day=="Ferritin day +14"] <- "Day 14"
-Ferritin_long$day[Ferritin_long$day=="Ferritin day +21"] <- "Day 21"
-Ferritin_long$day[Ferritin_long$day=="Ferritin day +30"] <- "Day 30"
-Ferritin_long$day <- factor(Ferritin_long$day, levels = c("Pre", "Day -5", "Day 0",
-                                                          "Day 7", "Day 14", "Day 21", "Day 30"))
-# ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
+#   scale_y_continuous(trans = "log2") +
+#   stat_compare_means(label.x = 5 
+#                      # aes(label = paste0("p = ", ..p.format..))
+#   #                  aes(
+#   # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
+#   )
+# 
+# b <- ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
 #   geom_boxplot() + 
-#   xlab("Days") + ylab("Ferritin") + 
+#   geom_jitter(color= "grey")+
+#   xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
 #   theme_classic() + ggtitle("Ferritin") + 
-#   expand_limits(y = c(0, 34000)) +
-#   scale_y_break(c(13600, 33000), ticklabels=c(33000, 34000), scales=0.10)
-
-# cart0$`CRP Pre-Leukapheresis`[cart0$`CRP Pre-Leukapheresis`=="<0.03"] <- 0.07
-# cart0$`CRP Pre-Leukapheresis` <- as.numeric(cart0$`CRP Pre-Leukapheresis`)
-# cart0$`CRP day +14`[cart0$`CRP day +14`=="<0.03"] <- 0.07
-# cart0$`CRP day +14` <- as.numeric(cart0$`CRP day +14`)
-# cart0$`CRP day +21`[cart0$`CRP day +21`=="<0.03"] <- 0.07
-# cart0$`CRP day +21` <- as.numeric(cart0$`CRP day +21`)
-# cart0$`CRP day +30`[cart0$`CRP day +30`=="<0.03"] <- 0.07
-# cart0$`CRP day +30` <- as.numeric(cart0$`CRP day +30`)
-CRP <- cart0 %>%
-  distinct(patient_id, .keep_all = TRUE) %>% 
-  select(`CRP Pre-Leukapheresis`, `CRP day -5`, `CRP day 0`,
-         `CRP day +7`, `CRP day +14`, `CRP day +21`, `CRP day +30`)
-CRP_long <- gather(CRP, day, CRP_value, `CRP Pre-Leukapheresis`:`CRP day +30`)
-CRP_long$day[CRP_long$day=="CRP Pre-Leukapheresis"] <- "Pre"
-CRP_long$day[CRP_long$day=="CRP day -5"] <- "Day -5"
-CRP_long$day[CRP_long$day=="CRP day 0"] <- "Day 0"
-CRP_long$day[CRP_long$day=="CRP day +7"] <- "Day 7"
-CRP_long$day[CRP_long$day=="CRP day +14"] <- "Day 14"
-CRP_long$day[CRP_long$day=="CRP day +21"] <- "Day 21"
-CRP_long$day[CRP_long$day=="CRP day +30"] <- "Day 30"
-CRP_long$day <- factor(CRP_long$day, levels = c("Pre", "Day -5", "Day 0", "Day 7", "Day 14", "Day 21", "Day 30"))
-# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
+#   scale_y_continuous(trans = "log2") +
+#   stat_compare_means(label.x = 5)
+# 
+# c <- ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
 #   geom_boxplot() + 
-#   xlab("Days") + ylab("CRP") + 
+#   geom_jitter(color= "grey")+
+#   xlab("Days") + ylab("CRP represented with a log2 scale") + 
 #   theme_classic() + ggtitle("CRP") + 
-#   expand_limits(y = c(0, 20)) +
-#   scale_y_break(c(4.55, 7.5, 9.5, 18.0), ticklabels=c(8,9,18, 20), 
-#                 scales=c(0.10)
-#                 )
-
-# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-#   geom_violin() + 
-#   xlab("Days") + ylab("CRP") + 
-#   theme_classic() + ggtitle("CRP")+
-#   expand_limits(y = c(0, 20)) +
-#   scale_y_break(c(5.9, 18.0), ticklabels=c(18, 20), 
-#                 scales=c(0.25)
-#                 )
-# 
-# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-#   geom_violin() + 
-#   xlab("Days") + ylab("CRP") + 
-#   theme_classic() + ggtitle("log10 CRP") + 
-#   expand_limits(y = c(0, 100)) +
-#   scale_y_log10()
-# 
-# ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-#   geom_violin() + 
-#   xlab("Days") + ylab("log2 CRP") + 
-#   theme_classic() + ggtitle("CRP") + 
-#   # expand_limits(y = c(0, 100)) +
-#   scale_y_continuous(trans = "log2")
-
-#   geom_jitter(color= "grey")+
-
-a <- ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
-  geom_boxplot() + 
-  xlab("Days") + ylab("LDH represented with a log2 scale") + 
-  theme_classic() + ggtitle("LDH") + 
-  scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 5 
-                     # aes(label = paste0("p = ", ..p.format..))
-  #                  aes(
-  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
-  )
-
-b <- ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
-  geom_boxplot() + 
-  xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
-  theme_classic() + ggtitle("Ferritin") + 
-  scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 5)
-
-c <- ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-  geom_boxplot() + 
-  xlab("Days") + ylab("CRP represented with a log2 scale") + 
-  theme_classic() + ggtitle("CRP") + 
-  scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 5)
-
-(a) /
-(b) /
-(c)+
-plot_annotation(tag_levels = "A")
-
-a <- ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
-  geom_boxplot() + 
-  geom_jitter(color= "grey")+
-  xlab("Days") + ylab("LDH represented with a log2 scale") + 
-  theme_classic() + ggtitle("LDH") + 
-  scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 5 
-                     # aes(label = paste0("p = ", ..p.format..))
-  #                  aes(
-  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
-  )
-
-b <- ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
-  geom_boxplot() + 
-  geom_jitter(color= "grey")+
-  xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
-  theme_classic() + ggtitle("Ferritin") + 
-  scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 5)
-
-c <- ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-  geom_boxplot() + 
-  geom_jitter(color= "grey")+
-  xlab("Days") + ylab("CRP represented with a log2 scale") + 
-  theme_classic() + ggtitle("CRP") + 
-  scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 5)
-
-(a) /
-(b) /
-(c) +
-plot_annotation(tag_levels = "A")
+#   scale_y_continuous(trans = "log2") +
+#   stat_compare_means(label.x = 5)
+# 
+# (a) /
+# (b) /
+# (c) +
+# plot_annotation(tag_levels = "A")
 ```
 
-## Figure 3. Cellular and humoral immune reconstitution after ide-cel
-**I can probably remove the x axis title on the 4 top plots**
+<!-- ## Figure 3. Cellular and humoral immune reconstitution after ide-cel -->
 ```{r, fig.width=12, fig.height=12}
-cart2 <- cart0 %>% 
-  distinct(patient_id, .keep_all = TRUE)
-# WBC
-timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 60, 90)
-WBC_fig <-
-  data.frame(timepoints,
-             t(round(
-               sapply(cart2[, c(
-                 "WBC apheresis",
-                 "WBC day -5 (k/ul)",
-                 "WBC day 0 (k/uL)",
-                 "WBC day +7",
-                 "WBC day +14",
-                 "WBC day +21",
-                 "WBC day +30",
-                 "WBC day +60",
-                 "WBC day +90"
-               )],
-               MedianCI,
-               conf.level = 0.95,
-               na.rm = TRUE), 9
-             )))
-WBC_fig <- WBC_fig %>%
-  ggplot(aes(x = timepoints, y = median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median WBC") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
-  ) + ylim(0, 6)
-
-# ANC
-ANC_fig <-
-  data.frame(timepoints, t(round(
-    sapply(cart2[, c(
-      "ANC apheresis",
-      "ANC day -5 (k/ul)",
-      "ANC day 0 (k/uL)",
-      "ANC Day 7",
-      "ANC day +14",
-      "ANC day +21",
-      "ANC Day 30",
-      "ANC Day 60",
-      "ANC Day 90"
-    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
-  )))
-ANC_fig <- ANC_fig %>% 
-  ggplot(aes(x = timepoints, y = median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median ANC") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
-  ) + 
-  ylim(0, 4)
-
-Hb_fig <-
-  data.frame(timepoints, t(round(
-    sapply(cart2[, c(
-      "Hb apheresis",
-      "Hb day -5 (k/ul)",
-      "Hb day 0 (k/uL)",
-      "HgB Day 7",
-      "Hb day +14",
-      "Hb day +21",
-      "HgB Day 30",
-      "HgB Day 60",
-      "HgB Day 90"
-    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
-  )))
-Hb_fig <- Hb_fig %>% 
-  ggplot(aes(x = timepoints, y = median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median Hb") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
-  ) + 
-  ylim(7.5, 12)
-
-# ALC
-ALC_fig <-
-  data.frame(timepoints, t(round(
-    sapply(cart2[, c(
-      "ALC apheresis",
-      "ALC day -5 (k/ul)",
-      "ALC day 0 (k/uL)",
-      "ALC day +7",
-      "ALC day +14",
-      "ALC day +21",
-      "ALC day +30",
-      "ALC day +60",
-      "ALC day +90"
-    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
-  )))
-ALC_fig <- ALC_fig %>% 
-  ggplot(aes(x = timepoints, y = median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median ALC") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
-  ) + 
-  ylim(0, 1.1)
-
-# Plt
-Plt_fig <-
-  data.frame(timepoints, t(round(
-    sapply(cart2[, c(
-      "Plt apheresis",
-      "Plt day -5 (k/ul)",
-      "Plt day 0 (k/uL)",
-      "Platelets Day 7",
-      "Plt day +14",
-      "Plt day +21",
-      "Plateletes Day 30",
-      "Platelets Day 60",
-      "Platelets Day 90"
-    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
-  )))
-Plt_fig <- Plt_fig %>% 
-  ggplot(aes(x = timepoints, y = median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median Plt") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
-  ) +
-  ylim(20, 170)
-
-# IgG
-#table(cart2$`IgG day +90`)
-#table(cart2$`IgG day +180`)
-# cart2$`IgG day +90`[cart2$`IgG day +90` == "<109"] <- 77
-# cart2$`IgG day +30`[cart2$`IgG day +30` == "<109"] <- 77
-# cart2$`IgG day -5`[cart2$`IgG day -5` == "<109"] <- 77
-# cart2$`IgG apheresis`[cart2$`IgG apheresis` == "<109"] <- 77
-# 
-# cart2$`IgG day +90` <- as.numeric(cart2$`IgG day +90`)
-# cart2$`IgG day +30` <- as.numeric(cart2$`IgG day +30`)
-# cart2$`IgG day -5` <- as.numeric(cart2$`IgG day -5`)
-# cart2$`IgG apheresis` <- as.numeric(cart2$`IgG apheresis`)
-timepoints2 <- c(-28, -5, 30, 90)
-IgG_fig <-
-  data.frame(timepoints2, t(round(
-    sapply(cart2[, c(
-      "IgG apheresis", 
-      "IgG day -5",
-      # "IgG day 0 (k/uL)", 
-      "IgG day +30", 
-      "IgG day +90")], MedianCI, conf.level =
-             0.95, na.rm = TRUE), 9
-  )))
-IgG_fig <- IgG_fig %>% 
-  ggplot(aes(x = timepoints2, y = median)) + 
-  geom_line(col = "blue") +
-  xlab("Days relative to infusion") + 
-  ylab("Median IgG") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 30, 90),
-    labels = c("Apheresis", "-5", "0", "30", "90"))# + 
-  # ylim(0, 2000)
-
-(WBC_fig | ANC_fig) /
-  (Hb_fig | ALC_fig) /
-  (Plt_fig | IgG_fig) +
-  plot_annotation(tag_levels = "A")
+# cart2 <- cart0 %>% 
+#   distinct(patient_id, .keep_all = TRUE)
+# # WBC
+# timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 60, 90)
+# WBC_fig <-
+#   data.frame(timepoints,
+#              t(round(
+#                sapply(cart2[, c(
+#                  "WBC apheresis",
+#                  "WBC day -5 (k/ul)",
+#                  "WBC day 0 (k/uL)",
+#                  "WBC day +7",
+#                  "WBC day +14",
+#                  "WBC day +21",
+#                  "WBC day +30",
+#                  "WBC day +60",
+#                  "WBC day +90"
+#                )],
+#                MedianCI,
+#                conf.level = 0.95,
+#                na.rm = TRUE), 9
+#              )))
+# WBC_fig <- WBC_fig %>%
+#   ggplot(aes(x = timepoints, y = median)) + 
+#   geom_line(col = "blue") + 
+#   xlab("Days relative to infusion") + 
+#   ylab("Median WBC") + 
+#   theme_classic() + 
+#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+#   scale_x_continuous(
+#     breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+#     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+#   ) + ylim(0, 6)
+# 
+# # ANC
+# ANC_fig <-
+#   data.frame(timepoints, t(round(
+#     sapply(cart2[, c(
+#       "ANC apheresis",
+#       "ANC day -5 (k/ul)",
+#       "ANC day 0 (k/uL)",
+#       "ANC Day 7",
+#       "ANC day +14",
+#       "ANC day +21",
+#       "ANC Day 30",
+#       "ANC Day 60",
+#       "ANC Day 90"
+#     )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+#   )))
+# ANC_fig <- ANC_fig %>% 
+#   ggplot(aes(x = timepoints, y = median)) + 
+#   geom_line(col = "blue") + 
+#   xlab("Days relative to infusion") + 
+#   ylab("Median ANC") + 
+#   theme_classic() + 
+#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+#   scale_x_continuous(
+#     breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+#     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+#   ) + 
+#   ylim(0, 4)
+# 
+# Hb_fig <-
+#   data.frame(timepoints, t(round(
+#     sapply(cart2[, c(
+#       "Hb apheresis",
+#       "Hb day -5 (k/ul)",
+#       "Hb day 0 (k/uL)",
+#       "HgB Day 7",
+#       "Hb day +14",
+#       "Hb day +21",
+#       "HgB Day 30",
+#       "HgB Day 60",
+#       "HgB Day 90"
+#     )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+#   )))
+# Hb_fig <- Hb_fig %>% 
+#   ggplot(aes(x = timepoints, y = median)) + 
+#   geom_line(col = "blue") + 
+#   xlab("Days relative to infusion") + 
+#   ylab("Median Hb") + 
+#   theme_classic() + 
+#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+#   scale_x_continuous(
+#     breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+#     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+#   ) + 
+#   ylim(7.5, 12)
+# 
+# # ALC
+# ALC_fig <-
+#   data.frame(timepoints, t(round(
+#     sapply(cart2[, c(
+#       "ALC apheresis",
+#       "ALC day -5 (k/ul)",
+#       "ALC day 0 (k/uL)",
+#       "ALC day +7",
+#       "ALC day +14",
+#       "ALC day +21",
+#       "ALC day +30",
+#       "ALC day +60",
+#       "ALC day +90"
+#     )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+#   )))
+# ALC_fig <- ALC_fig %>% 
+#   ggplot(aes(x = timepoints, y = median)) + 
+#   geom_line(col = "blue") + 
+#   xlab("Days relative to infusion") + 
+#   ylab("Median ALC") + 
+#   theme_classic() + 
+#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+#   scale_x_continuous(
+#     breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+#     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+#   ) + 
+#   ylim(0, 1.1)
+# 
+# # Plt
+# Plt_fig <-
+#   data.frame(timepoints, t(round(
+#     sapply(cart2[, c(
+#       "Plt apheresis",
+#       "Plt day -5 (k/ul)",
+#       "Plt day 0 (k/uL)",
+#       "Platelets Day 7",
+#       "Plt day +14",
+#       "Plt day +21",
+#       "Plateletes Day 30",
+#       "Platelets Day 60",
+#       "Platelets Day 90"
+#     )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+#   )))
+# Plt_fig <- Plt_fig %>% 
+#   ggplot(aes(x = timepoints, y = median)) + 
+#   geom_line(col = "blue") + 
+#   xlab("Days relative to infusion") + 
+#   ylab("Median Plt") + 
+#   theme_classic() + 
+#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+#   scale_x_continuous(
+#     breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+#     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+#   ) +
+#   ylim(20, 170)
+# 
+# # IgG
+# #table(cart2$`IgG day +90`)
+# #table(cart2$`IgG day +180`)
+# # cart2$`IgG day +90`[cart2$`IgG day +90` == "<109"] <- 77
+# # cart2$`IgG day +30`[cart2$`IgG day +30` == "<109"] <- 77
+# # cart2$`IgG day -5`[cart2$`IgG day -5` == "<109"] <- 77
+# # cart2$`IgG apheresis`[cart2$`IgG apheresis` == "<109"] <- 77
+# # 
+# # cart2$`IgG day +90` <- as.numeric(cart2$`IgG day +90`)
+# # cart2$`IgG day +30` <- as.numeric(cart2$`IgG day +30`)
+# # cart2$`IgG day -5` <- as.numeric(cart2$`IgG day -5`)
+# # cart2$`IgG apheresis` <- as.numeric(cart2$`IgG apheresis`)
+# timepoints2 <- c(-28, -5, 30, 90)
+# IgG_fig <-
+#   data.frame(timepoints2, t(round(
+#     sapply(cart2[, c(
+#       "IgG apheresis", 
+#       "IgG day -5",
+#       # "IgG day 0 (k/uL)", 
+#       "IgG day +30", 
+#       "IgG day +90")], MedianCI, conf.level =
+#              0.95, na.rm = TRUE), 9
+#   )))
+# IgG_fig <- IgG_fig %>% 
+#   ggplot(aes(x = timepoints2, y = median)) + 
+#   geom_line(col = "blue") +
+#   xlab("Days relative to infusion") + 
+#   ylab("Median IgG") + 
+#   theme_classic() + 
+#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+#   scale_x_continuous(
+#     breaks = c(-28, -5, 0, 30, 90),
+#     labels = c("Apheresis", "-5", "0", "30", "90"))# + 
+#   # ylim(0, 2000)
+# 
+# (WBC_fig | ANC_fig) /
+#   (Hb_fig | ALC_fig) /
+#   (Plt_fig | IgG_fig) +
+#   plot_annotation(tag_levels = "A")
 ```
@@
 
-## Figure 4. Cytopenias over time
-
-As discussed at meeting, rather than showing count recovery over time plan to show Grade 3+ cytopenias (Hb, Plt, ANC, WBC) over time (Day –5, Day +30, Day +60, Day +90)
-**We want grade 3 only right?**
+<!-- ## Figure 4. Cytopenias over time -->
+
+<!-- As discussed at meeting, rather than showing count recovery over time plan to show Grade 3+ cytopenias (Hb, Plt, ANC, WBC) over time (Day –5, Day +30, Day +60, Day +90) -->
+<!-- **We want grade 3 only right?** -->
 ```{r}
-# cart2 %>% 
+# a <- cart2 %>% 
 #   select(patient_id,
+#          Leukopenia_apheresis,
+#          `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
+#          Neutropenia_apheresis,
+#          `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
+#          Anemia_apheresis,
+#          `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
+#          Thrombocytopenia_apheresis,
+#          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
+#          
+#          gr3_Leukopenia_apheresis,
 #          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
+#          gr3_Neutropenia_apheresis,
 #          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
+#          gr3_Anemia_apheresis,
 #          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
+#          gr3_Thrombocytopenia_apheresis,
 #          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
 #   ) %>% 
-#   pivot_longer(cols = `gr3_Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
-#   group_by(name, value) %>% 
-#   filter(!is.na(value)) %>% 
-#   summarise(count=n()) %>% 
-#   mutate(perc=(count/sum(count)*100)
-#   ) %>% 
-#   separate("name", into = c("gr3", "name", "day"), sep = "_") %>% 
-#   filter(value == "YES") %>% 
-#   # unite(time, c("day":"me"), sep = " ") %>% 
-#   ggplot(aes(x= day, y= perc, fill= name))+
-#   geom_bar(stat = "identity",
-#            position=position_dodge(width=0.9))+
-#   scale_fill_viridis_d() +
-#   labs(fill = NULL, y = "%", title = "Grade 3+")+
-#   theme_classic()
-# 
-# cart2 %>% 
-#   select(patient_id,
-#          `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
-#          `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
-#          `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
-#          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
-#          
-#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
-#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
-#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
-#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
-#   ) %>% 
-#   pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
+#   pivot_longer(cols = `Leukopenia_apheresis`: gr3_Thrombocytopenia_90d) %>% 
 #   mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
@@
 #   separate("name2", into = c("name", "day"), sep = "_") %>% 
+#   ungroup() %>% 
 #   filter(value == "YES") %>% 
-#   # unite(time, c("day":"me"), sep = " ") %>% 
-#   ggplot(aes(x= day, y= perc, fill= name, alpha= grade))+
+#   add_row("name"="Leukopenia",  "day"="apheresis", "value"= "YES", "grade"="Any grade", "count"=0, "perc"=0) %>% 
+#   mutate(day = factor(day, levels = c("apheresis", "-5d", "30d", "60d", "90d")))
+# b <- a %>% filter(grade == "Any grade")
+# a %>% filter(grade == "Grade 3+") %>% 
+#   ggplot(aes(x= day, 
+#              y= perc, 
+#              fill= name, alpha= 1
+#              ))+
 #   geom_bar(stat = "identity",
 #            position=position_dodge(width=0.9))+
-#   scale_fill_viridis_d() + 
-#   scale_alpha_ordinal(range = c(0.5, 1))+
-#   labs(fill = NULL, y = "%")+
-#   theme_classic()
-
-a <- cart2 %>% 
-  select(patient_id,
-         Leukopenia_apheresis,
-         `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
-         Neutropenia_apheresis,
-         `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
-         Anemia_apheresis,
-         `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
-         Thrombocytopenia_apheresis,
-         `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
-
-         gr3_Leukopenia_apheresis,
-         `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
-         gr3_Neutropenia_apheresis,
-         `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
-         gr3_Anemia_apheresis,
-         `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
-         gr3_Thrombocytopenia_apheresis,
-         `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
-  ) %>% 
-  pivot_longer(cols = `Leukopenia_apheresis`: gr3_Thrombocytopenia_90d) %>% 
-  mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
-         grade = case_when(
-           grade == "gr3_"       ~ "Grade 3+",
-           TRUE                  ~ "Any grade"
-         )) %>% 
-  mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
-         name2 = coalesce(name1, name)) %>% 
-  group_by(name2, value, grade) %>% 
-  filter(!is.na(value)) %>%
-  summarise(count=n()) %>%
-  group_by(name2, grade) %>% 
-  mutate(perc=(count/sum(count)*100)
-  ) %>%
-  separate("name2", into = c("name", "day"), sep = "_") %>% 
-  ungroup() %>% 
-  filter(value == "YES") %>% 
-  add_row("name"="Leukopenia",  "day"="apheresis", "value"= "YES", "grade"="Any grade", "count"=0, "perc"=0) %>% 
-  mutate(day = factor(day, levels = c("apheresis", "-5d", "30d", "60d", "90d")))
-b <- a %>% filter(grade == "Any grade")
-a %>% filter(grade == "Grade 3+") %>% 
-  ggplot(aes(x= day, 
-             y= perc, 
-             fill= name, alpha= 1
-             ))+
-  geom_bar(stat = "identity",
-           position=position_dodge(width=0.9))+
-  geom_bar(stat = "identity",
-           position=position_dodge(width=0.9), data= b,
-           aes(x= day, y= perc, fill= name), alpha= 0.4)+
-  scale_fill_brewer(palette = "Spectral")+
-  labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
-  theme_classic()+
-  scale_alpha_continuous(limits = c(0.4,1), breaks = c(0.4,1),
-                         labels= c("Any Grade", "Grade 3+"))
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9), data= b,
+#            aes(x= day, y= perc, fill= name), alpha= 0.4)+
+#   scale_fill_brewer(palette = "Spectral")+
+#   labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
+#   theme_classic()+
+#   scale_alpha_continuous(limits = c(0.4,1), breaks = c(0.4,1),
+#                          labels= c("Any Grade", "Grade 3+"))
 ```
-
-## Figure 5. Cumulative incidence of infection and infection density
-Lauren
-```{r}
-# library(cmprsk)
-# 
-# table(cart$`Latest Day of CRS (relateive to infusion)`)
-# # cart$CRS_fup2 <- cart$CRS_fup
-# # cart$CRS_fup2[cart$CRS_fup2==30] <- NA
-# # table(cart$CRS_fup2)
-# # 
-# # cart0$CRS_fup[cart0$CRS_fup==30] <- 7
-# CRS <- 
-#  cuminc(
-#     ftime = cart0$`Latest Day of CRS (relateive to infusion)`, 
-#     fstatus = cart0$CRS_any2, 
-#     group = cart0$`Infection type`)
-# ggcompetingrisks(CRS, multiple_panels = FALSE) + 
-#   scale_linetype_manual(name="Infection type", values=1:2,#labels=c("High","Low")
-#   )+
-#   guides(col="none")
-
-```
-
-## Figure S1. Viral titers after ide-cel
-
-### A)	HSV 1/2 IgG
-
-Example from prior cytopenia paper below. We can show this data however you think best
-Interpretation: ≤0.89=negative (not immune)
-                        0.90-1.09=indeterminate (can consider negative for purposes of analysis)
-                        ≥1.10=positive (immune)
-
-```{r, echo=TRUE}
-# mutate(`IgG HSV1/2 apheresis` = case_when(
-#     `IgG HSV1/2 apheresis` < 0.9         ~ "Negative",
-#     `IgG HSV1/2 apheresis` >= 0.9 &
-#       `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
-#     `IgG HSV1/2 apheresis` >= 1.10       ~ "Positive",
-#   ))
-```
-
-```{r}
-# cart2 %>% 
-#   select(patient_id, 
-#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>% 
-#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
-#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-#   unite(time, c("na":"me"), sep = " ") %>% 
-#   # mutate(value = as.numeric(value)) %>% 
-#   mutate(day = case_when(
-#     day == "D90"        ~ 90,
-#     day == "apheresis"  ~ 0
-#   )) %>% 
-#   ggplot(aes(x= day, y= value, color= patient_id))+
-#   geom_point()+
-#   geom_line()+
-#   scale_x_continuous(
-#     breaks = c(0, 90),
-#     labels = c("Apheresis", "D90"))+
-#   scale_color_viridis_d() +
-#   labs(fill = "Patients", x = NULL)+
-#   theme_classic()
-
-# cart2 %>% 
-#   select(patient_id, 
-#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
-#   
-#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
-#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-#   unite(name, c("na":"me"), sep = " ") %>% 
-#   ggplot(aes(x= day,  fill= value))+
-#   geom_bar()
-
-# Histogram
-cart2 %>% 
-  select(patient_id, 
-         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
-  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
-  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-  unite(name, c("na":"me"), sep = " ") %>% 
-  filter(!is.na(value)) %>% 
-  group_by(name, day, value) %>% 
-  summarise(count=n()) %>% 
-  mutate(perc=(count/sum(count)*100)
-  ) %>% 
-  ggplot(aes(x= day, y= perc, fill= value))+
-  geom_bar(stat = "identity")+
-  labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
-       fill= "Immunity")+
-  scale_y_continuous(expand = c(0, 0))+
-  theme_classic()
-
-library(ggpattern)
-cart2 %>% 
-  select(patient_id, 
-         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
-  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
-  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-  unite(name, c("na":"me"), sep = " ") %>% 
-  filter(!is.na(value)) %>% 
-  group_by(name, day, value) %>% 
-  summarise(count=n()) %>% 
-  mutate(perc=(count/sum(count)*100)
-  ) %>% 
-  ggplot(aes(x= day, y= perc))+
-  geom_bar_pattern(aes(pattern = value),
-                   stat = "identity",
-    fill            = 'white', 
-    colour          = 'black')+
-  # geom_bar(stat = "identity")+
-  labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
-       fill= "Immunity")+
-  scale_y_continuous(expand = c(0, 0))+
-  theme_classic()
-
-# cart2 %>% 
-#   select(patient_id, 
-#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
-#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
-#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-#   unite(name, c("na":"me"), sep = " ") %>% 
-#   filter(!is.na(value)) %>% 
-#   group_by(name, day, value) %>% 
-#   summarise(count=n()) %>% 
-# 
-#   ggplot(aes(x= day, y= count, fill= value))+
-#   geom_bar(stat = "identity",
-#            position=position_dodge(width=0.9))
-```
-
-```{r, fig.width=5, fig.height=6}
-# # Tile
-# cart2 %>% 
-#   select(patient_id, 
-#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
-#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
-#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-#   unite(time, c("na":"me"), sep = " ") %>% 
-#   filter(!is.na(value)) %>% 
-#   arrange(value) %>% 
-#   ggplot(aes(x= day, y= fct_reorder2(patient_id, value, day), fill= value))+
-#   geom_tile(color = "white")+
-#   labs(fill = NULL, x = NULL, y= NULL)+
-#   theme_classic()
-```
-
-```{r}
-# Alluvial
-library(ggalluvial)
-
-alluvial_A <- cart2 %>% 
-  select(patient_id, igg_hsv_change,
-         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
-  # mutate(igg_hsv_change = case_when(
-  #   igg_hsv_change == 1        ~  "Acquired immunity",
-  #   igg_hsv_change == 0.25        ~  "Positive overtime",
-  #   igg_hsv_change == -0.25        ~  "Negative overtime",
-  #   igg_hsv_change == -1        ~  "Lost immunity"
-  # )) %>% 
-  drop_na() %>% 
-  group_by(`IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>% 
-  summarise(count=n()) %>%
-
-  ggplot(aes(axis1 = `IgG HSV1/2 apheresis`, axis2 = `IgG HSV1/2 D90`,
-             y = count)) +
-  geom_alluvium(aes(fill = `IgG HSV1/2 apheresis`)
-  )+
-  geom_stratum()+
-  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  theme_classic()+
-  ggtitle("Evolution of virus titers")
-```
-
-### B)	VZV IgG (positive=immune vs negative or equivocal=not immune)
-```{r}
-# cart2 %>% 
-#   mutate(`VZV IgG apheresis` = case_when(
-#     `VZV IgG apheresis` == "0"         ~ "Negative",
-#     `VZV IgG apheresis` == "1"         ~ "immune",
-#     TRUE                          ~ `VZV IgG apheresis`
-#   )) %>% 
-#   mutate(`VZV IgG D90 (1=pos, 0=neg)` = case_when(
-#     `VZV IgG D90 (1=pos, 0=neg)` == "0"         ~ "Negative",
-#     `VZV IgG D90 (1=pos, 0=neg)` == "1"         ~ "immune",
-#     TRUE                          ~ `VZV IgG D90 (1=pos, 0=neg)`
-#   )) %>% 
-#   select(patient_id, 
-#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
-#   ) %>% 
-#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
-#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-#   unite(time, c("na":"me"), sep = " ") %>% 
-#   # mutate(value = as.numeric(value)) %>% 
-#   mutate(day = case_when(
-#     day == "D90"        ~ 90,
-#     day == "apheresis"  ~ 0
-#   )) %>% 
-#   ggplot(aes(x= day, y= value, color= patient_id))+
-#   geom_point(position=position_dodge(width=0.9))+
-#   scale_x_continuous(
-#     breaks = c(0, 90),
-#     labels = c("Apheresis", "D90"))+
-#   scale_color_viridis_d() +
-#   labs(fill = "Patients", x = NULL)+
-#   theme_classic()
-
-# Histogram
-# cart2 %>% 
-#   select(patient_id, 
-#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
-#   ) %>% 
-#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
-#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-#   unite(name, c("na":"me"), sep = " ") %>% 
-#   filter(!is.na(value)) %>% 
-#   group_by(name, day, value) %>% 
-#   summarise(count=n()) %>% 
-#   mutate(perc=(count/sum(count)*100)
-#   ) %>% 
-#   ggplot(aes(x= day, y= perc, fill= value))+
-#   geom_bar(stat = "identity")+
-#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
-#        fill= "Immunity")+
-#   scale_y_continuous(expand = c(0, 0))+
-#   theme_classic()
-
-# cart2 %>% 
-#   select(patient_id, 
-#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
-#   ) %>% 
-#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
-#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-#   unite(name, c("na":"me"), sep = " ") %>% 
-#   filter(!is.na(value)) %>% 
-#   group_by(name, day, value) %>% 
-#   summarise(count=n()) %>% 
-# 
-#   ggplot(aes(x= day, y= count, fill= value))+
-#   geom_bar(stat = "identity",
-#            position=position_dodge(width=0.9))
-```
-
-```{r, fig.width=5, fig.height=6}
-# Tile
-# cart2 %>% 
-#   select(patient_id, 
-#          `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
-#   ) %>% 
-#   pivot_longer(cols = `VZV IgG apheresis`: `VZV IgG D90 (1=pos, 0=neg)`) %>% 
-#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-#   unite(time, c("na":"me"), sep = " ") %>% 
-#   filter(!is.na(value)) %>% 
-#   arrange(value) %>% 
-#   ggplot(aes(x= day, y= fct_reorder2(patient_id, value, day), fill= value))+
-#   geom_tile(color = "white")+
-#   labs(fill = NULL, x = NULL, y= NULL)+
-#   theme_classic()
-```
-
-```{r}
-# Alluvial
-alluvial_B <- cart2 %>% 
-  select(patient_id, igg_vzv_change,
-         `VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`
-  ) %>% 
-  # mutate(igg_vzv_change = case_when(
-  #   igg_vzv_change == 1        ~  "Acquired immunity",
-  #   igg_vzv_change == 0.25        ~  "Positive overtime",
-  #   igg_vzv_change == -0.25        ~  "Negative overtime",
-  #   igg_vzv_change == -1        ~  "Lost immunity"
-  # )) %>% 
-  drop_na() %>% 
-  group_by(`VZV IgG apheresis`, `VZV IgG D90 (1=pos, 0=neg)`) %>% 
-  summarise(count=n()) %>%
-
-  ggplot(aes(axis1 = `VZV IgG apheresis`, axis2= `VZV IgG D90 (1=pos, 0=neg)`,
-             y = count)) +
-  geom_alluvium(aes(fill = `VZV IgG apheresis`)
-  )+
-  geom_stratum()+
-  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  theme_classic()+
-  ggtitle("Evolution of virus titers")
-```
-
-### C)	CMV IgG (positive=immune vs negative=not immune)
-```{r}
-# Histogram
-# cart2 %>% 
-#   
-#   select(patient_id, 
-#          `CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`
-#   ) %>% 
-#   pivot_longer(cols = `CMV IgG apheresis` : `CMV IgG D90 (1=pos, 0=neg)`) %>% 
-#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-#   unite(name, c("na":"me"), sep = " ") %>% 
-#   filter(!is.na(value)) %>% 
-#   group_by(name, day, value) %>% 
-#   summarise(count=n()) %>% 
-#   mutate(perc=(count/sum(count)*100)
-#   ) %>% 
-#   ggplot(aes(x= day, y= perc, fill= value))+
-#   geom_bar(stat = "identity")+
-#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
-#        fill= "Immunity")+
-#   scale_y_continuous(expand = c(0, 0))+
-#   theme_classic()
-```
-
-```{r, fig.width=5, fig.height=6}
-# Tile
-# cart2 %>% 
-#   
-#   select(patient_id, 
-#          `CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`
-#   ) %>% 
-#   pivot_longer(cols = `CMV IgG apheresis` : `CMV IgG D90 (1=pos, 0=neg)`) %>% 
-#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-#   unite(time, c("na":"me"), sep = " ") %>% 
-#   filter(!is.na(value)) %>% 
-#   arrange(value) %>% 
-#   ggplot(aes(x= day, y= fct_reorder2(patient_id, value, day), fill= value))+
-#   geom_tile(color = "white")+
-#   labs(fill = NULL, x = NULL, y= NULL)+
-#   theme_classic()
-```
-
-```{r}
-# Alluvial
-alluvial_C <- cart2 %>% 
-  select(patient_id, igg_cmv_change,
-         `CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`
-  ) %>% 
-  # mutate(igg_cmv_change = case_when(
-  #   igg_cmv_change == 1        ~  "Acquired immunity",
-  #   igg_cmv_change == 0.25        ~  "Positive overtime",
-  #   igg_cmv_change == -0.25        ~  "Negative overtime",
-  #   igg_cmv_change == -1        ~  "Lost immunity"
-  # )) %>% 
-  drop_na() %>% 
-  group_by(`CMV IgG apheresis`, `CMV IgG D90 (1=pos, 0=neg)`) %>% 
-  summarise(count=n()) %>%
-
-  ggplot(aes(axis1 = `CMV IgG apheresis`, axis2= `CMV IgG D90 (1=pos, 0=neg)`,
-             y = count)) +
-  geom_alluvium(aes(fill = `CMV IgG apheresis`)
-  )+
-  geom_stratum()+
-  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  theme_classic()+
-  ggtitle("Evolution of virus titers")
-```
-
-```{r, fig.height=12}
-(alluvial_A) /
-  (alluvial_B) /
-  (alluvial_C) +
-  plot_annotation(tag_levels = "A")
-```
-
-## Figure S2. Pneumococcal titers after ide-cel
-
-Antibody concentration >1.0 is considered long-term protection (immune)
-If antibody concentration ≤1.0 consider negative (not immune)
-```{r, fig.width=12, fig.height=12}
-# Histogram
-# cart2 %>% 
-#   select(patient_id, 
-#          starts_with("Pneumo"), -ends_with("change")) %>% 
-#   pivot_longer(cols = -patient_id) %>% 
-#   filter(!is.na(value)) %>% 
-#   mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
-#   mutate(name = str_remove(name, " apheresis| D90")) %>% 
-#   
-#   group_by(name, day, value) %>% 
-#   summarise(count=n()) %>% 
-#   mutate(perc=(count/sum(count)*100)
-#   ) %>% 
-# 
-#   ggplot(aes(x= day, y= perc, fill= value))+
-#   # geom_bar(stat = "identity",
-#   #          position=position_dodge2(width=0.9, preserve = "single"))+
-#   geom_bar(stat = "identity")+
-#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
-#        fill= "Immunity")+
-#   scale_y_continuous(expand = c(0, 0))+
-#   theme_classic()+
-#   facet_wrap(.~ name)
-```
-
-```{r, fig.width=12, fig.height=14}
-# Tile
-# cart2 %>% 
-#   select(patient_id, 
-#          starts_with("Pneumo"), -ends_with("change")) %>% 
-#   pivot_longer(cols = -patient_id) %>% 
-#   mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
-#   mutate(name = str_remove(name, " apheresis| D90")) %>% 
-#   
-#   
-#   filter(!is.na(value)) %>% 
-#   arrange(value) %>% 
-#   ggplot(aes(x= day, y= fct_reorder2(patient_id, value, day), fill= value))+
-#   geom_tile(color = "white")+
-#   labs(fill = NULL, x = NULL, y= NULL)+
-#   theme_classic()+
-#   facet_wrap(.~ name)
-```
-
-##########################
-
-```{r, fig.width=15, fig.height=12}
-library(ComplexHeatmap)
-mat <- cart2 %>% 
-  select(patient_id, intersect(starts_with("Pneumo"), ends_with("change"))) %>% 
-  drop_na() %>% 
-  # mutate(new_sort = rowSums(select(.,-patient_id), na.rm = TRUE)) %>%
-  mutate(new_sort = 
-           c(5,7,8,23,6,9,10,11,12,4,13,14,26,15,
-             24,3,16,25,17,2,18,21,19,20,1,22)) %>%
-
-  arrange(new_sort) %>% 
-    select(-new_sort)
-
-df5 <- t((as.matrix(mat)))
-
-df <- df5 %>% `colnames<-`(c(.[1,])) %>% 
-  .[-1,]
-
-df <- df %>% 
-sub(pattern = " 1.00", replacement = "Acquired immunity") %>% 
-sub(pattern = " 0.25", replacement = "Positive overtime") %>% 
-sub(pattern = "-0.25", replacement = "Negative overtime") %>% 
-sub(pattern = "-1.00", replacement = "Lost immunity")
-
-colors = structure(c("blue", "darkgrey", "lightgrey", "red"), 
-                   names = c("Lost immunity", "Negative overtime", "Positive overtime", "Acquired immunity"))
-
-ht_list <- Heatmap(df, name = "change", 
-        rect_gp = gpar(col = "white", lwd = 0.1),
-        column_title = "Change in titers",
-        show_column_names =FALSE,
-        row_names_side = "left",
-        row_names_gp = gpar(fontsize = 11),
-        col = colors)
-draw(ht_list, heatmap_legend_side = "bottom")
-# Heatmap(df, name = "change", 
-#         rect_gp = gpar(col = "white", lwd = 0.1),
-#         column_title = "Change in titers",
-#         column_names_rot = 45,
-#         column_names_gp = gpar(fontsize = 8),
-#         row_names_side = "left", 
-#         row_names_gp = gpar(fontsize = 10,
-#                             col = c("darkgreen", "pink", "orange", rep("blue", 28))),
-#         show_heatmap_legend = TRUE,
-#         col = colors)
-kjhkhkh
-```

### 2022-04-27 RWE/RWE Manuscript analyses.Rmd
Updates RMD

@@
   )) %>% 
+  mutate(`Tocilizumab (Yes, No)` = case_when(
+    `Tocilizumab (Yes, No)` == "Siltuximab"                    ~ "YES",
+      str_detect(`Tocilizumab (Yes, No)`, "COVID")             ~ "NO",
+    TRUE                                                       ~ `Tocilizumab (Yes, No)`
+  )) %>% 
+  mutate(`Steroid use (Yes, No)` = case_when(
+    str_detect(`Steroid use (Yes, No)`, "COVID")               ~ "NO",
+    TRUE                                                       ~ `Steroid use (Yes, No)`
+  )) %>% 
+  mutate(`Disease status at time of referral (Relapsed vs Refractory)` = case_when(
+    str_detect(`Disease status at time of referral (Relapsed vs Refractory)`, "Relapse")       ~ "Relapse",
+    str_detect(`Disease status at time of referral (Relapsed vs Refractory)`, "Response")      ~ "Response",
+    TRUE                                     ~ `Disease status at time of referral (Relapsed vs Refractory)`
+  )) %>%
+
+  mutate(exclusion_criteria =  
+           rowSums(select(.,`Received investigation agent, plasmapheresis, surgery, radiation, or therapy within 14 days of apheresis (Yes, No)`:`Other BCMA trial`
+                          ) == "YES", na.rm = TRUE),
+         exclusion_criteria = case_when(
+           exclusion_criteria == 0           ~ "0",
+           exclusion_criteria == 1           ~ "1",
+           exclusion_criteria > 1            ~ "≥2"
+         )) %>% 
+  mutate(comorbidities = case_when(
+    `Renal insufficiency CrCl < 45 mL/min (Yes, No)` == "YES" |
+      `H/O Class III or IV CHF or severe nonischemic cardiomyopathy, unstable or poorly controlled angina, myocardial infarction, or ventricular arrhythmia within 6 months (Yes, No)` == "YES" |
+      `LVEF <45% (Yes, No)` == "YES" |
+      `AST/ALT >2.5 ULN (Yes, No)` == "YES" |
+      `Total Bilirubin >1.5ULN (Yes, No)` == "YES" |
+      `H/O of malignancies (Yes, No)` == "YES"                    ~ "YES",
+    `LVEF <45% (Yes, No)` == "NO" &
+      `AST/ALT >2.5 ULN (Yes, No)` == "NO" &
+      `Total Bilirubin >1.5ULN (Yes, No)` == "NO" &
+      `H/O of malignancies (Yes, No)` == "NO"                     ~ "NO",
+    TRUE                                                          ~ NA_character_
+  )) %>%
+
 # CRS 
@@
   # mutate(best_response = ) %>% 
-  # mutate(Leukopenia_apheresis = case_when(
-  #   `WBC apheresis` < 4                                           ~ "YES",
-  #   is.na(`WBC apheresis`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Leukopenia_-5d` = case_when(
-  #   `WBC day -5 (k/ul)` < 4                                       ~ "YES",
-  #   is.na(`WBC day -5 (k/ul)`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Leukopenia_0d` = case_when(
-  #   `WBC day 0 (k/uL)` < 4                                        ~ "YES",
-  #   is.na(`WBC day 0 (k/uL)`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Leukopenia_7d` = case_when(
-  #   `WBC day +7` < 4                                              ~ "YES",
-  #   is.na(`WBC day +7`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Leukopenia_14d` = case_when(
-  #   `WBC day +14` < 4                                             ~ "YES",
-  #   is.na(`WBC day +14`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Leukopenia_21d` = case_when(
-  #   `WBC day +21` < 4                                             ~ "YES",
-  #   is.na(`WBC day +21`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Leukopenia_30d` = case_when(
-  #   `WBC day +30` < 4                                             ~ "YES",
-  #   is.na(`WBC day +30`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Leukopenia_60d` = case_when(
-  #   `WBC day +60` < 4                                             ~ "YES",
-  #   is.na(`WBC day +60`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Leukopenia_90d` = case_when(
-  #   `WBC day +90` < 4                                             ~ "YES",
-  #   is.na(`WBC day +90`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(gr3_Leukopenia_apheresis = case_when(
-  #   `WBC apheresis` < 2                                           ~ "YES",
-  #   is.na(`WBC apheresis`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`gr3_Leukopenia_-5d` = case_when(
-  #   `WBC day -5 (k/ul)` < 2                                       ~ "YES",
-  #   is.na(`WBC day -5 (k/ul)`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`gr3_Leukopenia_0d` = case_when(
-  #   `WBC day 0 (k/uL)` < 2                                        ~ "YES",
-  #   is.na(`WBC day 0 (k/uL)`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`gr3_Leukopenia_7d` = case_when(
-  #   `WBC day +7` < 2                                              ~ "YES",
-  #   is.na(`WBC day +7`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`gr3_Leukopenia_14d` = case_when(
-  #   `WBC day +14` < 2                                             ~ "YES",
-  #   is.na(`WBC day +14`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`gr3_Leukopenia_21d` = case_when(
-  #   `WBC day +21` < 2                                             ~ "YES",
-  #   is.na(`WBC day +21`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`gr3_Leukopenia_30d` = case_when(
-  #   `WBC day +30` < 2                                             ~ "YES",
-  #   is.na(`WBC day +30`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`gr3_Leukopenia_60d` = case_when(
-  #   `WBC day +60` < 2                                             ~ "YES",
-  #   is.na(`WBC day +60`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`gr3_Leukopenia_90d` = case_when(
-  #   `WBC day +90` < 2                                             ~ "YES",
-  #   is.na(`WBC day +90`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>%
-
   # mutate(Neutropenia_apheresis = case_when(
@@
   mutate(Neutropenia_gr1 = case_when(
-    `ANC Day 7` < 1.8 |
-    `ANC Day 30` < 1.8 |
-      `ANC Day 60` < 1.8 |
-      `ANC Day 90` < 1.8                                          ~ "YES",
+    (`ANC Day 7` < 1.8 &
+      `ANC Day 7` > 1.5) |
+    (`ANC Day 30` < 1.8 &
+      `ANC Day 30` > 1.5) |
+      (`ANC Day 60` < 1.8 &
+      `ANC Day 60` > 1.5) |
+      (`ANC Day 90` < 1.8 &
+      `ANC Day 90` > 1.5)                                          ~ "YES",
     is.na(`ANC Day 7`) |
@@
   mutate(Neutropenia_gr2 = case_when(
-    `ANC Day 7` < 1.5 |
-    `ANC Day 30` < 1.5 |
-      `ANC Day 60` < 1.5 |
-      `ANC Day 90` < 1.5                                          ~ "YES",
+    (`ANC Day 7` < 1.5 &
+      `ANC Day 7` > 1) |
+    (`ANC Day 30` < 1.5 &
+      `ANC Day 30` > 1) |
+      (`ANC Day 60` < 1.5 &
+      `ANC Day 60` > 1) |
+      (`ANC Day 90` < 1.5 &
+      `ANC Day 90` > 1)                                          ~ "YES",
     is.na(`ANC Day 7`) |
@@
   )) %>% 
-  mutate(Neutropenia_gr4 = case_when(
-    `ANC Day 7` < 0.5 |
-    `ANC Day 30` < 0.5 |
-      `ANC Day 60` < 0.5 |
-      `ANC Day 90` < 0.5                                          ~ "YES",
-    is.na(`ANC Day 7`) |
-      is.na(`ANC Day 30`) |
-      is.na(`ANC Day 60`) |
-      is.na(`ANC Day 90`)                                          ~ NA_character_,
-    TRUE                                          ~ "NO"
-  )) %>% 
+  # mutate(Neutropenia_gr4 = case_when(
+  #   `ANC Day 7` < 0.5 |
+  #   `ANC Day 30` < 0.5 |
+  #     `ANC Day 60` < 0.5 |
+  #     `ANC Day 90` < 0.5                                          ~ "YES",
+  #   is.na(`ANC Day 7`) |
+  #     is.na(`ANC Day 30`) |
+  #     is.na(`ANC Day 60`) |
+  #     is.na(`ANC Day 90`)                                          ~ NA_character_,
+  #   TRUE                                          ~ "NO"
+  # )) %>% 
   mutate(any_neutropenia = case_when(
@@
       Neutropenia_gr2 == "YES" |
-      Neutropenia_gr3 == "YES" |
-      Neutropenia_gr4 == "YES"                                          ~ "YES",
+      Neutropenia_gr3 == "YES"                                          ~ "YES",
     is.na(Neutropenia_gr1) |
           is.na(Neutropenia_gr2) |
-    is.na(Neutropenia_gr3) |
-    is.na(Neutropenia_gr4)                                          ~ NA_character_,
+    is.na(Neutropenia_gr3)                                          ~ NA_character_,
     TRUE                                          ~ "NO"
@@
   mutate(Anemia_gr1 = case_when(
-      `HgB Day 7` < 11.4 |
-      `HgB Day 30` < 11.4 |
-      `HgB Day 60` < 11.4 |
-      `HgB Day 90` < 11.4                                        ~ "YES",
+      (`HgB Day 7` < 11.4 &
+      `HgB Day 7` > 10) |
+      (`HgB Day 30` < 11.4 &
+      `HgB Day 30` > 10) |
+      (`HgB Day 60` < 11.4 &
+      `HgB Day 60` > 10) |
+      (`HgB Day 90` < 11.4 &
+      `HgB Day 90` > 10)                                        ~ "YES",
       is.na(`HgB Day 7`) |
@@
   mutate(Anemia_gr2 = case_when(
-      `HgB Day 7` < 10 |
-      `HgB Day 30` < 10 |
-      `HgB Day 60` < 10 |
-      `HgB Day 90` < 10                                        ~ "YES",
+      (`HgB Day 7` < 10 &
+      `HgB Day 7` > 8) |
+      (`HgB Day 30` < 10 &
+      `HgB Day 30` > 8) |
+      (`HgB Day 60` < 10 &
+      `HgB Day 60` > 8) |
+      (`HgB Day 90` < 10 &
+      `HgB Day 90` > 8)                                        ~ "YES",
       is.na(`HgB Day 7`) |
@@
   )) %>% 
-  mutate(Anemia_gr4 = case_when(
-      `HgB Day 7` < 0.1 |
-      `HgB Day 30` < 0.1 |
-      `HgB Day 60` < 0.1 |
-      `HgB Day 90` < 0.1                                        ~ "YES",
-      is.na(`HgB Day 7`) |
-      is.na(`HgB Day 30`) |
-      is.na(`HgB Day 60`) |
-      is.na(`HgB Day 90`)                                          ~ NA_character_,
-    TRUE                                          ~ "NO"
-  )) %>% 
+  # mutate(Anemia_gr4 = case_when(
+  #     `HgB Day 7` < 0.1 |
+  #     `HgB Day 30` < 0.1 |
+  #     `HgB Day 60` < 0.1 |
+  #     `HgB Day 90` < 0.1                                        ~ "YES",
+  #     is.na(`HgB Day 7`) |
+  #     is.na(`HgB Day 30`) |
+  #     is.na(`HgB Day 60`) |
+  #     is.na(`HgB Day 90`)                                          ~ NA_character_,
+  #   TRUE                                          ~ "NO"
+  # )) %>% 
   mutate(severe_anemia_30beyond = case_when(
@@
   mutate(Thrombocytopenia_gr1 = case_when(
-      `Platelets Day 7` < 143 |
-      `Plateletes Day 30` < 143 |
-      `Platelets Day 60` < 143 |
-      `Platelets Day 90` < 143                                        ~ "YES",
+      (`Platelets Day 7` < 143 &
+      `Platelets Day 7` > 75) |
+      (`Plateletes Day 30` < 143 &
+      `Plateletes Day 30` > 75) |
+      (`Platelets Day 60` < 143 &
+      `Platelets Day 60` > 75) |
+      (`Platelets Day 90` < 143 &
+      `Platelets Day 90` > 75)                                        ~ "YES",
       is.na(`Platelets Day 7`) |
@@
   mutate(Thrombocytopenia_gr2 = case_when(
-      `Platelets Day 7` < 75 |
-      `Plateletes Day 30` < 75 |
-      `Platelets Day 60` < 75 |
-      `Platelets Day 90` < 75                                        ~ "YES",
+      (`Platelets Day 7` < 75 &
+      `Platelets Day 7` > 50) |
+      (`Plateletes Day 30` < 75 &
+      `Plateletes Day 30` > 50) |
+      (`Platelets Day 60` < 75 &
+      `Platelets Day 60` > 50) |
+      (`Platelets Day 90` < 75 &
+      `Platelets Day 90` > 50)                                        ~ "YES",
       is.na(`Platelets Day 7`) |
@@
   )) %>% 
-  mutate(Thrombocytopenia_gr4 = case_when(
-      `Platelets Day 7` < 25 |
-      `Plateletes Day 30` < 25 |
-      `Platelets Day 60` < 25 |
-      `Platelets Day 90` < 25                                        ~ "YES",
-      is.na(`Platelets Day 7`) |
-      is.na(`Plateletes Day 30`) |
-      is.na(`Platelets Day 60`) |
-      is.na(`Platelets Day 90`)                                          ~ NA_character_,
-    TRUE                                          ~ "NO"
-  )) %>% 
+  # mutate(Thrombocytopenia_gr4 = case_when(
+  #     `Platelets Day 7` < 25 |
+  #     `Plateletes Day 30` < 25 |
+  #     `Platelets Day 60` < 25 |
+  #     `Platelets Day 90` < 25                                        ~ "YES",
+  #     is.na(`Platelets Day 7`) |
+  #     is.na(`Plateletes Day 30`) |
+  #     is.na(`Platelets Day 60`) |
+  #     is.na(`Platelets Day 90`)                                          ~ NA_character_,
+  #   TRUE                                          ~ "NO"
+  # )) %>% 
   mutate(severe_throm_30beyond = case_when(
@@
   mutate(`Day 30 Response (sCR, CR, VGPR, PR)` = case_when(
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "evaluable")   ~ NA_character_,
-    `Day 30 Response (sCR, CR, VGPR, PR)` == "CR"	                   ~ "CR, MRD unknown",
-    `Day 30 Response (sCR, CR, VGPR, PR)` == "CR, MRD+"	             ~ "CR, MRD+",
-
-    `Day 30 Response (sCR, CR, VGPR, PR)` == "sCR, MRD+"           	 ~ "sCR, MRD+",
-    `Day 30 Response (sCR, CR, VGPR, PR)` %in% c(
-      "sCR MRD-", "sCR, MRD-")                                                         ~ "sCR, MRD-",
-
-    `Day 30 Response (sCR, CR, VGPR, PR)` %in% c(
-      "sCR", "sCR (flow neg, no clonoSEQ ID)", "sCR MRD - by flow/no clonoSEQ)",
-      "sCR, MRD- by flow/no clonoSEQ)")                                                ~ "sCR, MRD unknown",
-
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "Not")         ~ NA_character_,
     TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR)`
@@
   # )) %>% 
-  mutate(day30_response = case_when(
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "sCR")	       ~ "sCR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR")	         ~ "CR",
-    is.na(`Day 30 Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
-    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR)`
-  )) %>% 
+  mutate(day30_response = `Day 30 Response (sCR, CR, VGPR, PR)`
+  ) %>% 
   mutate(day30_response_group = case_when(
@@
     str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR")	         ~ "CR or sCR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR") &
+      str_detect(`Day 30 MRD (positive vs negative)`, "MRD-")        ~ "CR or sCR, MRD-",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR") &
+      str_detect(`Day 30 MRD (positive vs negative)`, "MRD+")        ~ "CR or sCR, MRD+",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR") &
+      is.na(`Day 30 MRD (positive vs negative)`)                     ~ "CR or sCR, MRD unknown",
     is.na(`Day 30 Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
@@
   mutate(`3 Month Response (sCR, CR, VGPR, PR)` = case_when(
-    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
-    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
+    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "SD")        ~ "SD",
     str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "evaluable")   ~ NA_character_,
-
-    `3 Month Response (sCR, CR, VGPR, PR)` %in% c(
-      "CR", "CR (no clonoSEQ/MRD as no marrow)")                                      ~ "CR, MRD unknown",
-
-    `3 Month Response (sCR, CR, VGPR, PR)` %in% c(
-      "sCR (clonoSEQ pending, flow neg)", 
-      "sCR (no clonoSEQ for MRD, flow suspicious for MRD)",
-      "sCR (no clonoSEQ, flow neg)")                                                  ~ "sCR, MRD unknown",
-
-    `3 Month Response (sCR, CR, VGPR, PR)` %in% c(
-      "sCR, MRD - (by flow+)", "sCR, MRD-	12 (24%)")                                  ~ "sCR, MRD-",
-
-    `3 Month Response (sCR, CR, VGPR, PR)` == "sCR, MRD+"	            ~	"sCR, MRD+",
-
     TRUE           ~ `3 Month Response (sCR, CR, VGPR, PR)`
@@
     str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
-    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "CR")	        ~ "CR or sCR",
+    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "CR") &
+      str_detect(`3 Month MRD (positive vs negative)`, "MRD-")        ~ "CR or sCR, MRD-",
+    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "CR") &
+      str_detect(`3 Month MRD (positive vs negative)`, "MRD+")        ~ "CR or sCR, MRD+",
+    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "CR") &
+      is.na(`3 Month MRD (positive vs negative)`)                     ~ "CR or sCR, MRD unknown",
     is.na(`3 Month Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
@@
   )) %>% 
-  mutate(day90_response = case_when(
-    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
-    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
-    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "sCR")	        ~ "sCR",
-    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "CR")	        ~ "CR",
-    is.na(`3 Month Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
-    TRUE           ~ `3 Month Response (sCR, CR, VGPR, PR)`
-  )) %>% 
+  mutate(day90_response =`3 Month Response (sCR, CR, VGPR, PR)`
+  ) %>% 
   mutate(day90_response_sCRvsOthers = case_when(
@@
   mutate(best_response = case_when(
-    day30_response_group == "CR or sCR" |
-      day90_response_group == "CR or sCR"                                             ~ "CR or sCR",
+    day30_response_group == "CR or sCR, MRD-" |
+      day90_response_group == "CR or sCR, MRD-"                        ~ "CR or sCR, MRD-",
+    day30_response_group == "CR or sCR, MRD+" |
+      day90_response_group == "CR or sCR, MRD+"                        ~ "CR or sCR, MRD+",
+    day30_response_group == "CR or sCR, MRD unknown" |
+      day90_response_group == "CR or sCR, MRD unknown"                 ~ "CR or sCR, MRD unknown",
     day30_response_group == "VGPR" |
@@
       day90_response_group == "PR"                                     ~ "PR",
+
+    day30_response_group %in% c("MR", "PD", "SD") |
+      day90_response_group %in% c("MR", "PD", "SD")                    ~ "Others",
+
     TRUE                                                               ~ NA_character_
   )) %>% 
-  mutate(MRDneg_in_best_response = case_when(
-    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD-") |
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD-")        ~ "Yes",
-    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD") |
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD")         ~ "No",
-    TRUE                             ~ NA_character_
-  )) %>% 
+  # mutate(MRDneg_in_best_response = case_when(
+  #   str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD-") |
+  #   str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD-")        ~ "Yes",
+  #   str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "MRD") |
+  #   str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD")         ~ "No",
+  #   TRUE                             ~ NA_character_
+  # )) %>% 
   mutate(pfs_event = case_when(
@@
          `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+         Blenrep,`BCMA CAR-T on trial`, `Other BCMA trial`,
          immuno, proteasome, dara, doubleref, tripleref, pentaref,
@@
          `Cell Dose (million cells)`,
+         exclusion_criteria,
+
          `ECOG > or = 2? (Yes, No)`,
@@
          `Non-secretory MM (Yes, No)`,
+         `H/O or presence of CNS pathology (epilepsy, seizure, paresis, aphasia, stroke, CNS bleed, brian injuries, dementia, Parkinson's disease, cerebellar disease, organic brain syndrome, or psychosis) (Yes, No)`,
+         `Prior Allo SCT (Yes, No)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+         comorbidities,
 
@@
         `t(14:16) prior to CAR-T infusion (yes, no)`,
-    #     `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
+    `Prior auto SCT (yes, no)`, 
+         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+         `Prior Allo SCT (Yes, No)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+         Blenrep,`BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref,
-    #     `Did patient met criteria for KarMMa1 pre-CAR-T?`
+    `ECOG > or = 2? (Yes, No)`,
+         `ANC < 1000/uL (Yes, No)`,
+         `Hemoglobin < 8 g/dL (Yes, No)`,
+         `Platelets < 50K (Yes, No)`, 
+         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+    `H/O or presence of CNS pathology (epilepsy, seizure, paresis, aphasia, stroke, CNS bleed, brian injuries, dementia, Parkinson's disease, cerebellar disease, organic brain syndrome, or psychosis) (Yes, No)`,
+        `Did patient met criteria for KarMMa1 pre-CAR-T?`
     )
@@
          Neutropenia_gr1, Neutropenia_gr2, 
-         Neutropenia_gr3, Neutropenia_gr4,
+         Neutropenia_gr3,
          Anemia_gr1, Anemia_gr2,
-         Anemia_gr3, Anemia_gr4,
+         Anemia_gr3,
          Thrombocytopenia_gr1, Thrombocytopenia_gr2,
-         Thrombocytopenia_gr3, Thrombocytopenia_gr4,
+         Thrombocytopenia_gr3,
          severe_neutro_30beyond, severe_anemia_30beyond,
@@
          Neutropenia_gr1, Neutropenia_gr2, 
-         Neutropenia_gr3, Neutropenia_gr4,
+         Neutropenia_gr3,
          Anemia_gr1, Anemia_gr2,
-         Anemia_gr3, Anemia_gr4,
+         Anemia_gr3,
          Thrombocytopenia_gr1, Thrombocytopenia_gr2,
-         Thrombocytopenia_gr3, Thrombocytopenia_gr4,
+         Thrombocytopenia_gr3,
         severe_neutro_30beyond, severe_anemia_30beyond,
@@
   modify_footnote(update = everything() ~ NA)
-
-# tbl2 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   select(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
-#          `Anakinra (Yes, No)`) %>% 
-#   tbl_summary(type = list(
-#     c(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
-#       `Anakinra (Yes, No)`) ~ "categorical"),
-#     statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-#     digits = all_continuous() ~ 1) %>% 
-#   bold_labels() %>% add_stat_label()
-# 
-# tbl3 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   select(#MRDneg_30days,
-#          ORR_30days,
-#          day30_response,
-#          day30_response_group) %>% 
-#   tbl_summary(#type = list(
-#     # c(MRDneg_30days) ~ "categorical"),
-#     digits = all_continuous() ~ 1,
-#     missing = "no") %>% 
-#   bold_labels() %>% add_stat_label()
-# 
-# # tbl4 <- cart0 %>% 
-# #   distinct(patient_id, .keep_all = TRUE) %>% 
-# #   filter(day30_response_group == "CR or sCR") %>% 
-# #   select(MRDneg_30days) %>% 
-# #   tbl_summary(type = list(c(MRDneg_30days) ~ "categorical"),
-# #               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
-# #               digits = all_continuous() ~ 1,
-# #               missing = "no") %>% 
-# #   bold_labels() %>% add_stat_label()
-# 
-# tbl5 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   select(#MRDneg_90days,
-#          ORR_90days,
-#          day90_response,
-#          day90_response_group) %>% 
-#   tbl_summary(#type = list(
-#     # c(MRDneg_90days) ~ "categorical"),
-#     digits = all_continuous() ~ 1,
-#     missing = "no") %>% 
-#   bold_labels() %>% add_stat_label()
-# 
-# # tbl6 <- cart0 %>% 
-# #   distinct(patient_id, .keep_all = TRUE) %>% 
-# #   filter(day90_response_group == "CR or sCR") %>% 
-# #   select(MRDneg_90days) %>% 
-# #   tbl_summary(type = list(c(MRDneg_90days) ~ "categorical"),
-# #               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
-# #               digits = all_continuous() ~ 1,
-# #               missing = "no") %>% 
-# #   bold_labels() %>% add_stat_label()
-# 
-# tbl7 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   select(best_response) %>% 
-#   tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"),
-#               label = list(best_response ~ "best response in the first 90 days"),
-#               digits = all_continuous() ~ 1,
-#               missing = "no") %>% 
-#   bold_labels() %>% add_stat_label()
-# 
-# tbl8 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   filter(best_response == "CR or sCR") %>% 
-#   select(MRDneg_in_best_response) %>% 
-#   tbl_summary(type = list(c(MRDneg_in_best_response) ~ "categorical"),
-#               label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
-#               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-#               digits = all_continuous() ~ 1,
-#               missing = "no") %>% 
-#   bold_labels() %>% add_stat_label()
-# 
-# 
-# 
-# tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() %>%
-#   gt::tab_source_note(gt::md("**
-#                              **"))
-
 ```
@@
 ## Figure 1. Response rate bar graph for day 30, day 90, Best ORR
-**Need to include MRD in the var**
 ```{r}
@@
   pivot_longer(cols = everything()) %>% 
+  filter(!is.na(value)) %>% 
+  mutate(value = factor(value, levels = c("CR or sCR, MRD-",
+                                        "CR or sCR, MRD+",
+                                        "CR or sCR, MRD unknown",
+                                        "VGPR", "PR", "Others"))) %>% 
   group_by(name, value) %>% 
@@
   ) %>% 
-  filter(!is.na(value)) %>% 
+  filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
   ggplot(aes(x= name, y= percent, fill= value))+
   geom_bar(stat = "identity")+
-  scale_fill_brewer(palette = "RdBu")+
-  # labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
+  scale_fill_brewer(palette = "Spectral")+
+  labs(x= NULL)+
   theme_classic()
@@
 
-<!-- ## Figure 2. Inflammatory markers after ide-cel -->
-```{r, fig.height=12}
-# LDH <- cart0 %>% 
+## Table X. Patients’ response to Idecabtagene Vicleucel
+
+```{r}
+
+tbl3 <- cart0 %>%
+  mutate(overall_response = case_when(
+    !is.na(best_response)                 ~ "YES",
+    is.na(best_response)                  ~ "NO"
+  )) %>% 
+  mutate(months_at_best_response = case_when(
+    best_response == day30_response_group     ~ 1,
+    best_response == day90_response_group     ~ 3
+  )) %>% 
+  mutate(months_at_best_CRresponse = case_when(
+    str_detect(best_response, "CR") &
+      best_response == day30_response_group     ~ 1,
+    str_detect(best_response, "CR") &
+      best_response == day90_response_group     ~ 3
+  )) %>%
+
+  select(overall_response,
+         best_response,
+
+         months_at_best_response,
+         months_at_best_CRresponse,
+
+         ORR_30days,
+         day30_response,
+         day30_response_group) %>%
+  tbl_summary(#type = list(
+    # c(MRDneg_30days) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>%
+  bold_labels() %>% add_stat_label()
+
+# tbl4 <- cart0 %>%
 #   distinct(patient_id, .keep_all = TRUE) %>%
-#   select(`LDH at Pre-Leukapheresis`, `LDH day -5`, `LDH day 0`, 
-#          `LDH day +7`, `LDH day +14`, `LDH day +21`, `LDH day +30`)
-# LDH_long <- gather(LDH, day, LDH_value, `LDH at Pre-Leukapheresis`:`LDH day +30`)
-# LDH_long$day[LDH_long$day=="LDH at Pre-Leukapheresis"] <- "Pre"
-# LDH_long$day[LDH_long$day=="LDH day -5"] <- "Day -5"
-# LDH_long$day[LDH_long$day=="LDH day 0"] <- "Day 0"
-# LDH_long$day[LDH_long$day=="LDH day +7"] <- "Day 7"
-# LDH_long$day[LDH_long$day=="LDH day +14"] <- "Day 14"
-# LDH_long$day[LDH_long$day=="LDH day +21"] <- "Day 21"
-# LDH_long$day[LDH_long$day=="LDH day +30"] <- "Day 30"
-# LDH_long$day <- factor(LDH_long$day, levels = c("Pre", "Day -5", "Day 0", 
-#                                                 "Day 7", "Day 14", "Day 21", "Day 30"))
-# # ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
-# #   geom_boxplot() + xlab("Days") + ylab("LDH") + 
-# #   geom_jitter(color= "grey")+
-# #   theme_classic() + ggtitle("LDH") + 
-# #   expand_limits(y = c(0, 7000)) + 
-# #   scale_y_break(c(1188, 4000), 
-# #                 ticklabels=c(4000, 7000), scales=0.10) 
-# 
-# # cart0$`Ferritin day +7`[cart0$`Ferritin day +7`==">33511"] <- 33511
-# # cart0$`Ferritin day +7` <- as.numeric(cart0$`Ferritin day +7`)
-# Ferritin <- cart0 %>% 
+#   filter(day30_response_group == "CR or sCR") %>%
+#   select(MRDneg_30days) %>%
+#   tbl_summary(type = list(c(MRDneg_30days) ~ "categorical"),
+#               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>%
+#   bold_labels() %>% add_stat_label()
+
+tbl5 <- cart0 %>%
+  distinct(patient_id, .keep_all = TRUE) %>%
+  select(#MRDneg_90days,
+         ORR_90days,
+         day90_response,
+         day90_response_group) %>%
+  tbl_summary(#type = list(
+    # c(MRDneg_90days) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>%
+  bold_labels() %>% add_stat_label()
+
+# tbl6 <- cart0 %>%
 #   distinct(patient_id, .keep_all = TRUE) %>%
-#   select(patient_id, `Ferritin at Pre-Leukapheresis`, `Ferritin day -5`,
-#          `Ferritin day 0`, `Ferritin day +7`, `Ferritin day +14`, 
-#          `Ferritin day +21`, `Ferritin day +30`)
-# Ferritin_long <- gather(Ferritin, day, Ferritin_value, `Ferritin at Pre-Leukapheresis`:`Ferritin day +30`)
-# Ferritin_long$day[Ferritin_long$day=="Ferritin at Pre-Leukapheresis"] <- "Pre"
-# Ferritin_long$day[Ferritin_long$day=="Ferritin day -5"] <- "Day -5"
-# Ferritin_long$day[Ferritin_long$day=="Ferritin day 0"] <- "Day 0"
-# Ferritin_long$day[Ferritin_long$day=="Ferritin day +7"] <- "Day 7"
-# Ferritin_long$day[Ferritin_long$day=="Ferritin day +14"] <- "Day 14"
-# Ferritin_long$day[Ferritin_long$day=="Ferritin day +21"] <- "Day 21"
-# Ferritin_long$day[Ferritin_long$day=="Ferritin day +30"] <- "Day 30"
-# Ferritin_long$day <- factor(Ferritin_long$day, levels = c("Pre", "Day -5", "Day 0",
-#                                                           "Day 7", "Day 14", "Day 21", "Day 30"))
-# # ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
-# #   geom_boxplot() + 
-# #   xlab("Days") + ylab("Ferritin") + 
-# #   theme_classic() + ggtitle("Ferritin") + 
-# #   expand_limits(y = c(0, 34000)) +
-# #   scale_y_break(c(13600, 33000), ticklabels=c(33000, 34000), scales=0.10)
-# 
-# # cart0$`CRP Pre-Leukapheresis`[cart0$`CRP Pre-Leukapheresis`=="<0.03"] <- 0.07
-# # cart0$`CRP Pre-Leukapheresis` <- as.numeric(cart0$`CRP Pre-Leukapheresis`)
-# # cart0$`CRP day +14`[cart0$`CRP day +14`=="<0.03"] <- 0.07
-# # cart0$`CRP day +14` <- as.numeric(cart0$`CRP day +14`)
-# # cart0$`CRP day +21`[cart0$`CRP day +21`=="<0.03"] <- 0.07
-# # cart0$`CRP day +21` <- as.numeric(cart0$`CRP day +21`)
-# # cart0$`CRP day +30`[cart0$`CRP day +30`=="<0.03"] <- 0.07
-# # cart0$`CRP day +30` <- as.numeric(cart0$`CRP day +30`)
-# CRP <- cart0 %>%
-#   distinct(patient_id, .keep_all = TRUE) %>% 
-#   select(`CRP Pre-Leukapheresis`, `CRP day -5`, `CRP day 0`,
-#          `CRP day +7`, `CRP day +14`, `CRP day +21`, `CRP day +30`)
-# CRP_long <- gather(CRP, day, CRP_value, `CRP Pre-Leukapheresis`:`CRP day +30`)
-# CRP_long$day[CRP_long$day=="CRP Pre-Leukapheresis"] <- "Pre"
-# CRP_long$day[CRP_long$day=="CRP day -5"] <- "Day -5"
-# CRP_long$day[CRP_long$day=="CRP day 0"] <- "Day 0"
-# CRP_long$day[CRP_long$day=="CRP day +7"] <- "Day 7"
-# CRP_long$day[CRP_long$day=="CRP day +14"] <- "Day 14"
-# CRP_long$day[CRP_long$day=="CRP day +21"] <- "Day 21"
-# CRP_long$day[CRP_long$day=="CRP day +30"] <- "Day 30"
-# CRP_long$day <- factor(CRP_long$day, levels = c("Pre", "Day -5", "Day 0", "Day 7", "Day 14", "Day 21", "Day 30"))
-# # ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-# #   geom_boxplot() + 
-# #   xlab("Days") + ylab("CRP") + 
-# #   theme_classic() + ggtitle("CRP") + 
-# #   expand_limits(y = c(0, 20)) +
-# #   scale_y_break(c(4.55, 7.5, 9.5, 18.0), ticklabels=c(8,9,18, 20), 
-# #                 scales=c(0.10)
-# #                 )
-# 
-# # ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-# #   geom_violin() + 
-# #   xlab("Days") + ylab("CRP") + 
-# #   theme_classic() + ggtitle("CRP")+
-# #   expand_limits(y = c(0, 20)) +
-# #   scale_y_break(c(5.9, 18.0), ticklabels=c(18, 20), 
-# #                 scales=c(0.25)
-# #                 )
-# # 
-# # ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-# #   geom_violin() + 
-# #   xlab("Days") + ylab("CRP") + 
-# #   theme_classic() + ggtitle("log10 CRP") + 
-# #   expand_limits(y = c(0, 100)) +
-# #   scale_y_log10()
-# # 
-# # ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-# #   geom_violin() + 
-# #   xlab("Days") + ylab("log2 CRP") + 
-# #   theme_classic() + ggtitle("CRP") + 
-# #   # expand_limits(y = c(0, 100)) +
-# #   scale_y_continuous(trans = "log2")
-# 
-# 
-# 
-# 
-# 
-# 
-# 
-# 
-# #   geom_jitter(color= "grey")+
-# 
-# 
-# 
-# a <- ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
-#   geom_boxplot() + 
-#   xlab("Days") + ylab("LDH represented with a log2 scale") + 
-#   theme_classic() + ggtitle("LDH") + 
-#   scale_y_continuous(trans = "log2") +
-#   stat_compare_means(label.x = 5 
-#                      # aes(label = paste0("p = ", ..p.format..))
-#   #                  aes(
-#   # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
-#   )
-# 
-# b <- ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
-#   geom_boxplot() + 
-#   xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
-#   theme_classic() + ggtitle("Ferritin") + 
-#   scale_y_continuous(trans = "log2") +
-#   stat_compare_means(label.x = 5)
-# 
-# c <- ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-#   geom_boxplot() + 
-#   xlab("Days") + ylab("CRP represented with a log2 scale") + 
-#   theme_classic() + ggtitle("CRP") + 
-#   scale_y_continuous(trans = "log2") +
-#   stat_compare_means(label.x = 5)
-# 
-# (a) /
-# (b) /
-# (c)+
-# plot_annotation(tag_levels = "A")
-# 
-# a <- ggplot(LDH_long, aes(x=day, y=LDH_value)) + 
-#   geom_boxplot() + 
-#   geom_jitter(color= "grey")+
-#   xlab("Days") + ylab("LDH represented with a log2 scale") + 
-#   theme_classic() + ggtitle("LDH") + 
-#   scale_y_continuous(trans = "log2") +
-#   stat_compare_means(label.x = 5 
-#                      # aes(label = paste0("p = ", ..p.format..))
-#   #                  aes(
-#   # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
-#   )
-# 
-# b <- ggplot(Ferritin_long, aes(x=day, y=Ferritin_value)) + 
-#   geom_boxplot() + 
-#   geom_jitter(color= "grey")+
-#   xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
-#   theme_classic() + ggtitle("Ferritin") + 
-#   scale_y_continuous(trans = "log2") +
-#   stat_compare_means(label.x = 5)
-# 
-# c <- ggplot(CRP_long, aes(x=day, y=CRP_value)) + 
-#   geom_boxplot() + 
-#   geom_jitter(color= "grey")+
-#   xlab("Days") + ylab("CRP represented with a log2 scale") + 
-#   theme_classic() + ggtitle("CRP") + 
-#   scale_y_continuous(trans = "log2") +
-#   stat_compare_means(label.x = 5)
-# 
-# (a) /
-# (b) /
-# (c) +
-# plot_annotation(tag_levels = "A")
-```
-
-<!-- ## Figure 3. Cellular and humoral immune reconstitution after ide-cel -->
-```{r, fig.width=12, fig.height=12}
-# cart2 <- cart0 %>% 
-#   distinct(patient_id, .keep_all = TRUE)
-# # WBC
-# timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 60, 90)
-# WBC_fig <-
-#   data.frame(timepoints,
-#              t(round(
-#                sapply(cart2[, c(
-#                  "WBC apheresis",
-#                  "WBC day -5 (k/ul)",
-#                  "WBC day 0 (k/uL)",
-#                  "WBC day +7",
-#                  "WBC day +14",
-#                  "WBC day +21",
-#                  "WBC day +30",
-#                  "WBC day +60",
-#                  "WBC day +90"
-#                )],
-#                MedianCI,
-#                conf.level = 0.95,
-#                na.rm = TRUE), 9
-#              )))
-# WBC_fig <- WBC_fig %>%
-#   ggplot(aes(x = timepoints, y = median)) + 
-#   geom_line(col = "blue") + 
-#   xlab("Days relative to infusion") + 
-#   ylab("Median WBC") + 
-#   theme_classic() + 
-#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-#   scale_x_continuous(
-#     breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
-#     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
-#   ) + ylim(0, 6)
-# 
-# # ANC
-# ANC_fig <-
-#   data.frame(timepoints, t(round(
-#     sapply(cart2[, c(
-#       "ANC apheresis",
-#       "ANC day -5 (k/ul)",
-#       "ANC day 0 (k/uL)",
-#       "ANC Day 7",
-#       "ANC day +14",
-#       "ANC day +21",
-#       "ANC Day 30",
-#       "ANC Day 60",
-#       "ANC Day 90"
-#     )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
-#   )))
-# ANC_fig <- ANC_fig %>% 
-#   ggplot(aes(x = timepoints, y = median)) + 
-#   geom_line(col = "blue") + 
-#   xlab("Days relative to infusion") + 
-#   ylab("Median ANC") + 
-#   theme_classic() + 
-#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-#   scale_x_continuous(
-#     breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
-#     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
-#   ) + 
-#   ylim(0, 4)
-# 
-# Hb_fig <-
-#   data.frame(timepoints, t(round(
-#     sapply(cart2[, c(
-#       "Hb apheresis",
-#       "Hb day -5 (k/ul)",
-#       "Hb day 0 (k/uL)",
-#       "HgB Day 7",
-#       "Hb day +14",
-#       "Hb day +21",
-#       "HgB Day 30",
-#       "HgB Day 60",
-#       "HgB Day 90"
-#     )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
-#   )))
-# Hb_fig <- Hb_fig %>% 
-#   ggplot(aes(x = timepoints, y = median)) + 
-#   geom_line(col = "blue") + 
-#   xlab("Days relative to infusion") + 
-#   ylab("Median Hb") + 
-#   theme_classic() + 
-#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-#   scale_x_continuous(
-#     breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
-#     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
-#   ) + 
-#   ylim(7.5, 12)
-# 
-# # ALC
-# ALC_fig <-
-#   data.frame(timepoints, t(round(
-#     sapply(cart2[, c(
-#       "ALC apheresis",
-#       "ALC day -5 (k/ul)",
-#       "ALC day 0 (k/uL)",
-#       "ALC day +7",
-#       "ALC day +14",
-#       "ALC day +21",
-#       "ALC day +30",
-#       "ALC day +60",
-#       "ALC day +90"
-#     )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
-#   )))
-# ALC_fig <- ALC_fig %>% 
-#   ggplot(aes(x = timepoints, y = median)) + 
-#   geom_line(col = "blue") + 
-#   xlab("Days relative to infusion") + 
-#   ylab("Median ALC") + 
-#   theme_classic() + 
-#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-#   scale_x_continuous(
-#     breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
-#     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
-#   ) + 
-#   ylim(0, 1.1)
-# 
-# # Plt
-# Plt_fig <-
-#   data.frame(timepoints, t(round(
-#     sapply(cart2[, c(
-#       "Plt apheresis",
-#       "Plt day -5 (k/ul)",
-#       "Plt day 0 (k/uL)",
-#       "Platelets Day 7",
-#       "Plt day +14",
-#       "Plt day +21",
-#       "Plateletes Day 30",
-#       "Platelets Day 60",
-#       "Platelets Day 90"
-#     )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
-#   )))
-# Plt_fig <- Plt_fig %>% 
-#   ggplot(aes(x = timepoints, y = median)) + 
-#   geom_line(col = "blue") + 
-#   xlab("Days relative to infusion") + 
-#   ylab("Median Plt") + 
-#   theme_classic() + 
-#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-#   scale_x_continuous(
-#     breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
-#     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
-#   ) +
-#   ylim(20, 170)
-# 
-# # IgG
-# #table(cart2$`IgG day +90`)
-# #table(cart2$`IgG day +180`)
-# # cart2$`IgG day +90`[cart2$`IgG day +90` == "<109"] <- 77
-# # cart2$`IgG day +30`[cart2$`IgG day +30` == "<109"] <- 77
-# # cart2$`IgG day -5`[cart2$`IgG day -5` == "<109"] <- 77
-# # cart2$`IgG apheresis`[cart2$`IgG apheresis` == "<109"] <- 77
-# # 
-# # cart2$`IgG day +90` <- as.numeric(cart2$`IgG day +90`)
-# # cart2$`IgG day +30` <- as.numeric(cart2$`IgG day +30`)
-# # cart2$`IgG day -5` <- as.numeric(cart2$`IgG day -5`)
-# # cart2$`IgG apheresis` <- as.numeric(cart2$`IgG apheresis`)
-# timepoints2 <- c(-28, -5, 30, 90)
-# IgG_fig <-
-#   data.frame(timepoints2, t(round(
-#     sapply(cart2[, c(
-#       "IgG apheresis", 
-#       "IgG day -5",
-#       # "IgG day 0 (k/uL)", 
-#       "IgG day +30", 
-#       "IgG day +90")], MedianCI, conf.level =
-#              0.95, na.rm = TRUE), 9
-#   )))
-# IgG_fig <- IgG_fig %>% 
-#   ggplot(aes(x = timepoints2, y = median)) + 
-#   geom_line(col = "blue") +
-#   xlab("Days relative to infusion") + 
-#   ylab("Median IgG") + 
-#   theme_classic() + 
-#   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-#   scale_x_continuous(
-#     breaks = c(-28, -5, 0, 30, 90),
-#     labels = c("Apheresis", "-5", "0", "30", "90"))# + 
-#   # ylim(0, 2000)
-# 
-# (WBC_fig | ANC_fig) /
-#   (Hb_fig | ALC_fig) /
-#   (Plt_fig | IgG_fig) +
-#   plot_annotation(tag_levels = "A")
-```
-
-<!-- <span style="color:blue">**IgG I need to fix the other 109**</span>  -->
-
-<!-- Values less than the limit of detection (<109) were considered to be 77 which is the lower limit of detection divided by the square root of 2.
-One patient had an IgG day 0 value of <320.
-As this is above the limit of detection, I used the midway point between 320 and the lower limit of detection -- 214 -- as the value instead of <320.
--->
-
-<br>
-
-<!-- ## Figure 4. Cytopenias over time -->
-
-<!-- As discussed at meeting, rather than showing count recovery over time plan to show Grade 3+ cytopenias (Hb, Plt, ANC, WBC) over time (Day –5, Day +30, Day +60, Day +90) -->
-<!-- **We want grade 3 only right?** -->
-```{r}
-# a <- cart2 %>% 
-#   select(patient_id,
-#          Leukopenia_apheresis,
-#          `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
-#          Neutropenia_apheresis,
-#          `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
-#          Anemia_apheresis,
-#          `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
-#          Thrombocytopenia_apheresis,
-#          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
-#          
-#          gr3_Leukopenia_apheresis,
-#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
-#          gr3_Neutropenia_apheresis,
-#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
-#          gr3_Anemia_apheresis,
-#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
-#          gr3_Thrombocytopenia_apheresis,
-#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
-#   ) %>% 
-#   pivot_longer(cols = `Leukopenia_apheresis`: gr3_Thrombocytopenia_90d) %>% 
-#   mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
-#          grade = case_when(
-#            grade == "gr3_"       ~ "Grade 3+",
-#            TRUE                  ~ "Any grade"
-#          )) %>% 
-#   mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
-#          name2 = coalesce(name1, name)) %>% 
-#   group_by(name2, value, grade) %>% 
-#   filter(!is.na(value)) %>%
-#   summarise(count=n()) %>%
-#   group_by(name2, grade) %>% 
-#   mutate(perc=(count/sum(count)*100)
-#   ) %>%
-#   separate("name2", into = c("name", "day"), sep = "_") %>% 
-#   ungroup() %>% 
-#   filter(value == "YES") %>% 
-#   add_row("name"="Leukopenia",  "day"="apheresis", "value"= "YES", "grade"="Any grade", "count"=0, "perc"=0) %>% 
-#   mutate(day = factor(day, levels = c("apheresis", "-5d", "30d", "60d", "90d")))
-# b <- a %>% filter(grade == "Any grade")
-# a %>% filter(grade == "Grade 3+") %>% 
-#   ggplot(aes(x= day, 
-#              y= perc, 
-#              fill= name, alpha= 1
-#              ))+
-#   geom_bar(stat = "identity",
-#            position=position_dodge(width=0.9))+
-#   geom_bar(stat = "identity",
-#            position=position_dodge(width=0.9), data= b,
-#            aes(x= day, y= perc, fill= name), alpha= 0.4)+
-#   scale_fill_brewer(palette = "Spectral")+
-#   labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
-#   theme_classic()+
-#   scale_alpha_continuous(limits = c(0.4,1), breaks = c(0.4,1),
-#                          labels= c("Any Grade", "Grade 3+"))
-```
+#   filter(day90_response_group == "CR or sCR") %>%
+#   select(MRDneg_90days) %>%
+#   tbl_summary(type = list(c(MRDneg_90days) ~ "categorical"),
+#               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>%
+#   bold_labels() %>% add_stat_label()
+
+tbl7 <- cart0 %>%
+  distinct(patient_id, .keep_all = TRUE) %>%
+  select(best_response) %>%
+  tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"),
+              label = list(best_response ~ "best response in the first 90 days"),
+              digits = all_continuous() ~ 1,
+              missing = "no") %>%
+  bold_labels() %>% add_stat_label()
+
+tbl8 <- cart0 %>%
+  distinct(patient_id, .keep_all = TRUE) %>%
+  filter(best_response == "CR or sCR") %>%
+  select(MRDneg_in_best_response) %>%
+  tbl_summary(type = list(c(MRDneg_in_best_response) ~ "categorical"),
+              label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
+              digits = all_continuous() ~ 1,
+              missing = "no") %>%
+  bold_labels() %>% add_stat_label()
+
+tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() %>%
+  gt::tab_source_note(gt::md("**
+                             **"))
+
+```

### 2022-04-28 RWE/RWE Manuscript analyses.Rmd
Add last tables and figures

@@
 
-`r emo::ji("question_mark")` **Are we setting the days >100 to 100?**
+`r emo::ji("question_mark")` **Exclusion criteria**
 
@@
   )) %>% 
+  mutate(best_MRD_response = case_when(
+    str_detect(`Day 30 MRD (positive vs negative)`, "MRD-") |
+      str_detect(`3 Month MRD (positive vs negative)`, "MRD-")         ~ "MRD-",
+    str_detect(`Day 30 MRD (positive vs negative)`, "MRD+") |
+      str_detect(`3 Month MRD (positive vs negative)`, "MRD+")         ~ "MRD+",
+    TRUE                                                               ~ NA_character_
+  )) %>% 
+  mutate(overall_response = case_when(
+    !is.na(best_response)                 ~ "Response",
+    is.na(best_response)                  ~ "No response"
+  )) %>% 
+  mutate(months_at_best_response = case_when(
+    best_response == day30_response_group     ~ 1,
+    best_response == day90_response_group     ~ 3
+  )) %>% 
+  mutate(months_at_best_CRresponse = case_when(
+    str_detect(best_response, "CR") &
+      best_response == day30_response_group     ~ 1,
+    str_detect(best_response, "CR") &
+      best_response == day90_response_group     ~ 3
+  )) %>% 
   # mutate(MRDneg_in_best_response = case_when(
@@
              end = pfs_time)/
-           duration(n=1, units = "days")) %>%
+           duration(n=1, units = "months")) %>%
 
@@
              end = os_time)/
-           duration(n=1, units = "days"))
+           duration(n=1, units = "months"))
 
@@
 ## Labeling
-# var_label(cart0) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", 
-#                          `Extramedullary Disease? (Yes, No)` = "Extramedullary disease", 
-#                          `High Marrow Burden (>= 50%)` = "High marrow burden (≥50%)",
-#                          # bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
-#                          proteasome = "Refractory to Proteasome Inhibitors", 
-#                          immuno = "Refractory to Immunomodulators", doubleref = "Double refractory", 
-#                          tripleref= "Triple refractory", pentaref= "Penta refractory",
-#                          # bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese", 
-#                          CRS_any = "Any CRS", CRS_gradecat = "CRS Grade", 
-#                          ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", cyto= "High risk cytogenetics", 
-#                          # `ECOG > or = 2? (Yes=1, No=0)` ,
-#                          `Deletion 17p prior to CAR-T infusion (yes, no)` = "Deletion 17p at Infusion", 
-#                          `t(4:14) prior to CAR-T infusion (yes, no)` = "t(4:14) at Infusion", `t(14:16) prior to CAR-T infusion (yes, no)` = "t(4:16) at Infusion", 
-#                          `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` = "Prior BCMA-directed therapy",
-#                          `Prior auto SCT (yes, no)` = "Prior autoSCT", 
-#                          `Prior Allo SCT (Yes=1, No=0)` = "Prior alloSCT",
-#                          # `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` = "Prior BCMA-directed therapy ",
-#                          dara= "Refractory to Daratumumab"#,
-#                          # best_response = "Best response in first 90 days"
-# )
+var_label(cart0) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", 
+                        # tumor_burden ="Tumor burden", 
+                        proteasome = "Refractory to Proteasome Inhibitors",
+                       immuno = "Refractory to Immunomodulators", doubleref = "Double refractory",
+                       tripleref="Triple refractory", pentaref="Penta refractory",
+                       CRS_any = "Any CRS", CRS_gradecat = "CRS Grade",
+                       ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", 
+                       `Deletion 17p prior to CAR-T infusion (yes, no)` = "Deletion 17p at Infusion",
+                       `t(4:14) prior to CAR-T infusion (yes, no)` = "t(4:14) at Infusion",
+                       `t(14:16) prior to CAR-T infusion (yes, no)` = "t(4:16) at Infusion",
+                       `Prior auto SCT (yes, no)` = "Prior auto SCT",
+                       `Extramedullary Disease? (Yes, No)` = "Extramedullary disease",
+                       dara="Refractory to Daratumumab")
 
@@
       `High Marrow Burden (>= 50%)`,
-    # #     cyto, 
+    cytogenetics,
     `Deletion 17p prior to CAR-T infusion (yes, no)`,
@@
     `H/O or presence of CNS pathology (epilepsy, seizure, paresis, aphasia, stroke, CNS bleed, brian injuries, dementia, Parkinson's disease, cerebellar disease, organic brain syndrome, or psychosis) (Yes, No)`,
+    comorbidities,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`
@@
   geom_bar(stat = "identity")+
-  scale_fill_brewer(palette = "Spectral")+
+  scale_fill_brewer(palette = "Blues")+
+  ylim(0,100)+
   labs(x= NULL)+
@@
 
-```{r}
+```{r, fig.width= 6, fig.height=6}
 ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
@@
 
-           legend.title = "", xlab = "Time (in days)" 
+           legend.title = "", xlab = "Time (in months)" 
 ) + guides(colour = guide_legend(ncol = 2))
+
+survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
+                   data = cart0)
 ```
@@
 Panel C: OS Kaplan Meier (from CAR-T infusion)
-```{r}
+```{r, fig.width= 6, fig.height=6}
 ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ 1, 
@@
 
-           legend.title = "", xlab = "Time (in days)" 
+           legend.title = "", xlab = "Time (in months)" 
 ) + guides(colour = guide_legend(ncol = 2))
+
+survfit(Surv(days_at_os_from_infusion, os_event) ~ 1, 
+                   data = cart0)
 ```
@@
 Panel D: Duration of response graph
+Waiting Tuesday
 ```{r}
@@
 
-## Table X. Patients’ response to Idecabtagene Vicleucel
+## Table 5. Patients’ response to Idecabtagene Vicleucel
 
 ```{r}
-
-tbl3 <- cart0 %>%
-  mutate(overall_response = case_when(
-    !is.na(best_response)                 ~ "YES",
-    is.na(best_response)                  ~ "NO"
-  )) %>% 
-  mutate(months_at_best_response = case_when(
-    best_response == day30_response_group     ~ 1,
-    best_response == day90_response_group     ~ 3
-  )) %>% 
-  mutate(months_at_best_CRresponse = case_when(
-    str_detect(best_response, "CR") &
-      best_response == day30_response_group     ~ 1,
-    str_detect(best_response, "CR") &
-      best_response == day90_response_group     ~ 3
-  )) %>%
-
+tbl1 <- cart0 %>%
   select(overall_response,
-         best_response,
-
-         months_at_best_response,
-         months_at_best_CRresponse,
-
-         ORR_30days,
-         day30_response,
-         day30_response_group) %>%
-  tbl_summary(#type = list(
-    # c(MRDneg_30days) ~ "categorical"),
+         best_response) %>%
+  tbl_summary(
+    label = list(overall_response ~ "overall response within 90 days", 
+                 best_response ~ "best response within 90 days"),
     digits = all_continuous() ~ 1,
@@
 
-# tbl4 <- cart0 %>%
-#   distinct(patient_id, .keep_all = TRUE) %>%
-#   filter(day30_response_group == "CR or sCR") %>%
-#   select(MRDneg_30days) %>%
-#   tbl_summary(type = list(c(MRDneg_30days) ~ "categorical"),
-#               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
+# tbl2 <- cart0 %>%
+#   filter(str_detect(best_response, "CR")) %>%
+#   select(best_MRD_response) %>%
+#   tbl_summary(#type = list(c(best_MRD_response) ~ "categorical"),
+#               # label = list(best_MRD_response ~ "best_MRD_response within CR/sCR"),
 #               digits = all_continuous() ~ 1,
@@
 
-tbl5 <- cart0 %>%
-  distinct(patient_id, .keep_all = TRUE) %>%
-  select(#MRDneg_90days,
-         ORR_90days,
-         day90_response,
-         day90_response_group) %>%
-  tbl_summary(#type = list(
-    # c(MRDneg_90days) ~ "categorical"),
+tbl3 <- cart0 %>%
+  select(months_at_best_response,
+         months_at_best_CRresponse) %>%
+  tbl_summary(
+    type = list(c(months_at_best_response, 
+                  months_at_best_CRresponse) ~ "continuous"),
+    label = list(months_at_best_response ~ "months at best response within 90 days",
+                 months_at_best_CRresponse ~ "months at best CR response within 90 days"),
     digits = all_continuous() ~ 1,
@@
 
-# tbl6 <- cart0 %>%
+tbl_stack(list(tbl1, #tbl2, 
+               tbl3)) %>% as_gt()
+
+tbl4 <- cart0 %>%
+  filter(str_detect(best_response, "CR")) %>%
+  select(best_MRD_response) %>%
+  tbl_summary(type = list(c(best_MRD_response) ~ "categorical"),
+              label = list(best_MRD_response ~ "best MRD CR response within 90 days"),
+              digits = all_continuous() ~ 1,
+              missing = "no") %>%
+  bold_labels() %>% add_stat_label()
+
+# tbl5 <- cart0 %>%
 #   distinct(patient_id, .keep_all = TRUE) %>%
-#   filter(day90_response_group == "CR or sCR") %>%
-#   select(MRDneg_90days) %>%
-#   tbl_summary(type = list(c(MRDneg_90days) ~ "categorical"),
-#               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
+#   select(#MRDneg_90days,
+#          ORR_90days,
+#          day90_response,
+#          day90_response_group) %>%
+#   tbl_summary(#type = list(
+#     # c(MRDneg_90days) ~ "categorical"),
 #     digits = all_continuous() ~ 1,
@@
 #   bold_labels() %>% add_stat_label()
-
-tbl7 <- cart0 %>%
-  distinct(patient_id, .keep_all = TRUE) %>%
-  select(best_response) %>%
-  tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"),
-              label = list(best_response ~ "best response in the first 90 days"),
-              digits = all_continuous() ~ 1,
-              missing = "no") %>%
+# 
+# 
+# 
+# tbl7 <- cart0 %>%
+#   distinct(patient_id, .keep_all = TRUE) %>%
+#   select(best_response) %>%
+#   tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"),
+#               label = list(best_response ~ "best response in the first 90 days"),
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>%
+#   bold_labels() %>% add_stat_label()
+# 
+# tbl8 <- cart0 %>%
+#   distinct(patient_id, .keep_all = TRUE) %>%
+#   filter(best_response == "CR or sCR") %>%
+#   select(MRDneg_in_best_response) %>%
+#   tbl_summary(type = list(c(MRDneg_in_best_response) ~ "categorical"),
+#               label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
+#               statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>%
+#   bold_labels() %>% add_stat_label()
+```
+
+## Figure 3: ORR (A) vs. PFS (B) stratified by KarMMa exclusion criteria.
+
+```{r}
+cart0 <- cart0 %>% 
+  rename(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T = 
+           `Did patient met criteria for KarMMa1 pre-CAR-T?`) %>% 
+  mutate(Overall = "Overall")
+```
+
+```{r, fig.width= 6, fig.height=6}
+ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
+                   data = cart0),
+           title = "PFS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
+survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
+                   data = cart0)
+```
+
+Panel C: OS Kaplan Meier (from CAR-T infusion)
+```{r, fig.width= 6, fig.height=6}
+ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
+                   data = cart0),
+           title = "OS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
+survfit(Surv(days_at_os_from_infusion, os_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
+                   data = cart0)
+```
+
+## Table 6. Cause of death in patients who received Idecabtagene vicleucel
+```{r}
+cart0 %>%
+  filter(!is.na(`Date of Death`)) %>% 
+  mutate(`Cause of death (myeloma, toxicitiy,other)` = case_when(
+    str_detect(`Cause of death (myeloma, toxicitiy,other)`, "Myeloma")      ~ "Myeloma",
+    str_detect(`Cause of death (myeloma, toxicitiy,other)`, "COVID")        ~ "COVID-19",
+    str_detect(`Cause of death (myeloma, toxicitiy,other)`, "oxicity")      ~ "Toxicity",
+    TRUE                                     ~ `Cause of death (myeloma, toxicitiy,other)`
+  )) %>% 
+  select(`Cause of death (myeloma, toxicitiy,other)`) %>%
+  tbl_summary() %>%
   bold_labels() %>% add_stat_label()
-
-tbl8 <- cart0 %>%
-  distinct(patient_id, .keep_all = TRUE) %>%
-  filter(best_response == "CR or sCR") %>%
-  select(MRDneg_in_best_response) %>%
-  tbl_summary(type = list(c(MRDneg_in_best_response) ~ "categorical"),
-              label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
-              statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
-              digits = all_continuous() ~ 1,
-              missing = "no") %>%
-  bold_labels() %>% add_stat_label()
-
-tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() %>%
-  gt::tab_source_note(gt::md("**
-                             **"))
-
-```
+```
+
+## Table 7.
+Multiple Myeloma Efficacy and Toxicity Outcomes following infusion of SOC Idecabtagene vicleucel or in KarMMa (Variables to report on ORR, ≥ CR rate, 3 month PFS rate, any CRS, grade ≥ 3 CRS, any neurotoxicity, grade ≥ 3 neurotoxicity (see lymphoma EXAMPLE table below)
+
+```{r}
+tbl0 <- cart0 %>%
+  mutate(cohort = "Overall") %>% 
+  bind_rows(., cart0 %>% 
+              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
+  mutate(cohort = case_when(
+    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
+    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
+    TRUE                 ~ cohort
+  ),
+  cohort = factor(cohort, levels = c("Overall",
+                                     "Met criteria for KarMMa1 pre-CAR-T",
+                                     "NOT et criteria for KarMMa1 pre-CAR-T"))
+  ) %>% 
+  mutate(Total = "No of patients") %>% 
+  select(Total, cohort) %>%
+
+  tbl_summary(by= Total,
+              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
+              statistic = all_categorical() ~ "{n}",
+              # percent = "row"
+              ) %>%
+  bold_labels() %>% #add_stat_label() %>% 
+  modify_header(all_stat_cols() ~ "**{level}**") %>% 
+  modify_footnote(update = everything() ~ NA)
+
+tbl1 <- cart0 %>%
+  mutate(cohort = "Overall") %>% 
+  bind_rows(., cart0 %>% 
+              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
+  mutate(cohort = case_when(
+    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
+    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
+    TRUE                 ~ cohort
+  ),
+  cohort = factor(cohort, levels = c("Overall",
+                                     "Met criteria for KarMMa1 pre-CAR-T",
+                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
+  select(ORR_30days, cohort) %>%
+  tbl_summary(by= ORR_30days,
+              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
+              statistic = all_categorical() ~ "{p}%",
+              percent = "row") %>%
+  bold_labels() %>% add_stat_label() %>% 
+  modify_header(all_stat_cols() ~ "**{level}**")
+
+tbl2 <- cart0 %>%
+  mutate(cohort = "Overall") %>% 
+  bind_rows(., cart0 %>% 
+              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
+  mutate(cohort = case_when(
+    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
+    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
+    TRUE                 ~ cohort
+  ),
+  cohort = factor(cohort, levels = c("Overall",
+                                     "Met criteria for KarMMa1 pre-CAR-T",
+                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
+  select(day30_response_sCRvsOthers, cohort) %>%
+  tbl_summary(by= day30_response_sCRvsOthers,
+              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
+              statistic = all_categorical() ~ "{p}%",
+              percent = "row") %>%
+  bold_labels() %>% add_stat_label() %>% 
+  modify_header(all_stat_cols() ~ "**{level}**")
+
+tbl3 <- cart0 %>%
+  mutate(cohort = "Overall") %>% 
+  bind_rows(., cart0 %>% 
+              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
+  mutate(cohort = case_when(
+    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
+    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
+    TRUE                 ~ cohort
+  ),
+  cohort = factor(cohort, levels = c("Overall",
+                                     "Met criteria for KarMMa1 pre-CAR-T",
+                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
+  select(CRS_any, cohort) %>%
+  tbl_summary(by= CRS_any,
+              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
+              statistic = all_categorical() ~ "{p}%",
+              percent = "row") %>%
+  bold_labels() %>% add_stat_label() %>% 
+  modify_header(all_stat_cols() ~ "**{level}**")
+
+tbl4 <- cart0 %>%
+  mutate(cohort = "Overall") %>% 
+  bind_rows(., cart0 %>% 
+              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
+  mutate(cohort = case_when(
+    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
+    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
+    TRUE                 ~ cohort
+  ),
+  cohort = factor(cohort, levels = c("Overall",
+                                     "Met criteria for KarMMa1 pre-CAR-T",
+                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
+  select(CRS_gradecat, cohort) %>%
+  tbl_summary(by= CRS_gradecat,
+              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
+              statistic = all_categorical() ~ "{p}%",
+              percent = "row") %>%
+  bold_labels() %>% add_stat_label() %>% 
+  modify_header(all_stat_cols() ~ "**{level}**")
+
+tbl5 <- cart0 %>%
+  mutate(cohort = "Overall") %>% 
+  bind_rows(., cart0 %>% 
+              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
+  mutate(cohort = case_when(
+    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
+    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
+    TRUE                 ~ cohort
+  ),
+  cohort = factor(cohort, levels = c("Overall",
+                                     "Met criteria for KarMMa1 pre-CAR-T",
+                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
+  select(ICANS_any, cohort) %>%
+  tbl_summary(by= ICANS_any,
+              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
+              statistic = all_categorical() ~ "{p}%",
+              percent = "row") %>%
+  bold_labels() %>% add_stat_label() %>% 
+  modify_header(all_stat_cols() ~ "**{level}**")
+
+tbl6 <- cart0 %>%
+  mutate(cohort = "Overall") %>% 
+  bind_rows(., cart0 %>% 
+              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
+  mutate(cohort = case_when(
+    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
+    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
+    TRUE                 ~ cohort
+  ),
+  cohort = factor(cohort, levels = c("Overall",
+                                     "Met criteria for KarMMa1 pre-CAR-T",
+                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
+  select(ICANS_gradecat, cohort) %>%
+  tbl_summary(by= ICANS_gradecat,
+              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
+              statistic = all_categorical() ~ "{p}%",
+              percent = "row") %>%
+  bold_labels() %>% add_stat_label() %>% 
+  modify_header(all_stat_cols() ~ "**{level}**")
+
+tbl_merge(list(tbl0, tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), 
+          tab_spanner = c("", "ORR at 30 days", "sCR/CR vs Others at 30 days",
+                          "CRS_any", "CRS_gradecat", "ICANS_any", "ICANS_gradecat"))
+
+# cart0 %>%
+#   select(day30_response_sCRvsOthers, CRS_any, CRS_gradecat, ICANS_any, ICANS_gradecat, Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) %>%
+#   tbl_summary() %>%
+#   bold_labels() %>% add_stat_label()
+
+# tbl1 <- cart0 %>%
+#   select(ORR_30days, day30_response_sCRvsOthers) %>%
+#   tbl_summary() %>%
+#   bold_labels() %>% add_stat_label() %>%
+#   modify_spanning_header(all_stat_cols() ~ "**Overall**")
+# 
+# tbl2 <- cart0 %>%
+#   filter(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T == "YES") %>% 
+#   select(ORR_30days, day30_response_sCRvsOthers) %>%
+#   tbl_summary() %>%
+#   bold_labels() %>% add_stat_label() %>%
+#   modify_spanning_header(all_stat_cols() ~ "**Met criteria for KarMMa1 pre-CAR-T**")
+# 
+# tbl3 <- cart0 %>%
+#   filter(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T == "NO") %>% 
+#   select(ORR_30days, day30_response_sCRvsOthers) %>%
+#   tbl_summary() %>%
+#   bold_labels() %>% add_stat_label() %>%
+#   modify_spanning_header(all_stat_cols() ~ "**NOT met criteria for KarMMa1 pre-CAR-T**")
+# 
+# tbl_merge(list(tbl1, tbl2, 
+#                tbl3), 
+#           tab_spanner = c("**Overall**", 
+#                           "**Met criteria for KarMMa1 pre-CAR-T**", 
+#                           "**NOT met criteria for KarMMa1 pre-CAR-T**")) %>% 
+#   as_gt()
+
+# Estimating median survival time
+# survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
+#                    data = cart0)
+tbl1 <- tbl_survfit(
+  cart0,
+  y = Surv(days_at_pfs_from_infusion, pfs_event),
+  include = c(Overall, Did_patient_met_criteria_for_KarMMa1_pre_CAR_T#, 
+              # CRS_any, CRS_gradecat, ICANS_any, ICANS_gradecat
+              ),
+  probs = 0.5,
+  label_header = "**Median PFS**"
+)
+# 3 month pfs rate
+
+tbl2 <- list(
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
+                   data = cart0),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
+                   data = cart0)#,
+    # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ CRS_any, 
+    #                data = cart0),
+    # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ CRS_gradecat, 
+    #                data = cart0),
+    # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ICANS_any, 
+    #                data = cart0),
+    # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ICANS_gradecat, 
+    #                data = cart0)
+  ) %>%
+  tbl_survfit(times = c(3),
+              label_header = "**PFS Rate at {time} Months**")
+
+tbl_merge(list(tbl1, tbl2))
+```

### 2022-05-04 RWE/RWE Manuscript analyses.Rmd
Fix ecog
Fix bug and change axis

@@
 
-`r emo::ji("question_mark")` **Exclusion criteria**
-
 ```{r data cleaning}
@@
   select(-c(`Date of Apheresis (or # of days from apheresis to LD)`, first_date_of_apheresis)) %>%
+
   mutate(across(c(`Day of Max CRS (relative to infusion)`,
@@
   )) %>% 
-  mutate_at(c("ECOG at consult",
-              "ECOG at LD"
-              ), 
-            ~ case_when(
-              . == 1                                              ~ "YES",
-              . == 0                                              ~ "NO",
-              TRUE                                                ~ NA_character_
-            )) %>% 
   # ECOG
@@
   mutate(exclusion_criteria =  
-           rowSums(select(.,`Received investigation agent, plasmapheresis, surgery, radiation, or therapy within 14 days of apheresis (Yes, No)`:`Other BCMA trial`
+           rowSums(select(.,`Received investigation agent, plasmapheresis, surgery, radiation, or therapy within 14 days of apheresis (Yes, No)`:`ECOG > or = 2? (Yes, No)`
                           ) == "YES", na.rm = TRUE),
@@
            interval(
-             start = `Date of CAR T infusion (# of days from apharesis to infusion)`, 
+             start = date_of_apheresis, 
              end = pfs_time)/
@@
            interval(
-             start = `Date of CAR T infusion (# of days from apharesis to infusion)`, 
+             start = date_of_apheresis, 
              end = os_time)/
@@
 ```{r, fig.width= 6, fig.height=6}
-ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
+myplot <- ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
                    data = cart0),
@@
 ) + guides(colour = guide_legend(ncol = 2))
+myplot$plot <- myplot$plot + 
+  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot$table <- myplot$table + 
+  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
 
@@
 ```{r, fig.width= 6, fig.height=6}
-ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ 1, 
+myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ 1, 
                    data = cart0),
@@
 ```{r, fig.width= 6, fig.height=6}
-ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
+myplot <- ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
                    data = cart0),
@@
 ) + guides(colour = guide_legend(ncol = 1))
+myplot$plot <- myplot$plot + 
+  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot$table <- myplot$table + 
+  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
 
@@
 ```{r, fig.width= 6, fig.height=6}
-ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
+myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
                    data = cart0),

### 2022-05-05 RWE/RWE Manuscript analyses.Rmd
Update exclusion, tables and plots

@@
 cart0 <- MM_cart %>% 
-  # Exclude patients who had manufacturing cart failure or died prior cart infusion
-  filter(is.na(exclude_for_manufacturing_cart_failure_or_died_prior_cart_infusion)) %>%
-
   mutate(across(c(`ANC Day 30`,
@@
   # ECOG
-  # mutate(`ECOG at LD` = case_when(
-  #   `ECOG at LD` == 0 | 
-  #     `ECOG at LD` == 1                       ~ "0-1",
-  #   TRUE                                                          ~ `ECOG at LD`
-  # )) %>% 
+  mutate(`ECOG at LD` = case_when(
+    `ECOG at LD` == 0 |
+      `ECOG at LD` == 1                                           ~ "0-1",
+    `ECOG at LD` %in% c(2:4)                                      ~ "2-4",
+    TRUE                                                          ~ NA_character_
+  )) %>% 
   # cytogenetics
@@
   # refractory status
-  # mutate_at(c("Lenalidomide (exposed vs. refractory)",
-  #             "Bortezomib (exposed vs. refractory)",
-  #             "Carfilzomib (exposed vs. refractory)",
-  #             "Pomalidomide (exposed vs. refractory)",
-  #             "Daratumumab (exposed vs. refractory)"), 
-  #           ~ case_when(
-  #             . == 1                                              ~ "Refractory",
-  #             . == 0                                              ~ "Exposed",
-  #             TRUE                                                ~ NA_character_
-  #           )) %>% 
+  mutate_at(c("Lenalidomide (exposed vs. refractory)",
+              "Bortezomib (exposed vs. refractory)",
+              "Carfilzomib (exposed vs. refractory)",
+              "Pomalidomide (exposed vs. refractory)",
+              "Daratumumab (exposed vs. refractory)"),
+            ~ case_when(
+              is.na(.)                                            ~ "Not Refractory",
+              TRUE                                                ~ as.character(.)
+            )) %>%
   mutate(immuno = case_when(
-    `Lenalidomide (exposed vs. refractory)` == "Exposed" &
-      `Pomalidomide (exposed vs. refractory)` == "Exposed"        ~ "NO",
     `Lenalidomide (exposed vs. refractory)` == "Refractory" |
-      `Pomalidomide (exposed vs. refractory)` == "Refractory"     ~ "YES"
+      `Pomalidomide (exposed vs. refractory)` == "Refractory"     ~ "YES",
+    TRUE        ~ "NO"
   )) %>% 
   mutate(proteasome = case_when(
-    `Bortezomib (exposed vs. refractory)` == "Exposed" &
-      `Carfilzomib (exposed vs. refractory)` == "Exposed"      ~ "NO",
     `Bortezomib (exposed vs. refractory)` == "Refractory" |
-      `Carfilzomib (exposed vs. refractory)` == "Refractory"   ~ "YES"
+      `Carfilzomib (exposed vs. refractory)` == "Refractory"   ~ "YES",
+    TRUE      ~ "NO"
   )) %>% 
@@
     `Daratumumab (exposed vs. refractory)` == "Refractory"      ~ "YES",
-    `Daratumumab (exposed vs. refractory)` == "Exposed"             ~ "NO"
+    TRUE             ~ "NO"
   )) %>% 
   mutate(doubleref = case_when(
-    proteasome == "NO" | 
-      immuno == "NO"                                              ~ "NO",
     proteasome == "YES" &
-      immuno == "YES"                                         ~ "YES"
+      immuno == "YES"                                         ~ "YES",
+    TRUE                                              ~ "NO"
   )) %>% 
   mutate(tripleref = case_when(
-    proteasome == "NO" | 
-      immuno == "NO" |
-      `Daratumumab (exposed vs. refractory)` == "Exposed"      ~ "NO",
     proteasome == "YES" &
       immuno == "YES" &
-      `Daratumumab (exposed vs. refractory)` == "Refractory"        ~ "YES"
+      `Daratumumab (exposed vs. refractory)` == "Refractory"        ~ "YES",
+    TRUE      ~ "NO"
   )) %>% 
   mutate(pentaref = case_when(
-    `Bortezomib (exposed vs. refractory)` == "Exposed" | 
-      `Carfilzomib (exposed vs. refractory)` == "Exposed" |
-      `Lenalidomide (exposed vs. refractory)` == "Exposed" | 
-      `Pomalidomide (exposed vs. refractory)` == "Exposed" | 
-      `Daratumumab (exposed vs. refractory)` == "Exposed"     ~ "NO",
     `Bortezomib (exposed vs. refractory)` == "Refractory" & 
@@
       `Pomalidomide (exposed vs. refractory)` == "Refractory" & 
-      `Daratumumab (exposed vs. refractory)` == "Refractory"  ~ "YES"
+      `Daratumumab (exposed vs. refractory)` == "Refractory"  ~ "YES",
+    TRUE     ~ "NO"
+  )) %>% 
+  mutate(number_prior_lines_therapy = case_when(
+    `Number of prior lines of therapy` <= 4           ~ "≤4",
+    `Number of prior lines of therapy` > 4            ~ ">4",
   )) %>%
@@
          CRS_gradecat = factor(CRS_gradecat, levels = c("No CRS", "Grade 1 or 2", "Grade ≥3")),
-         gr3_CRS = case_when(
-           CRS_gradecat == "Grade ≥3"                             ~ "Grade ≥3",
-           CRS_gradecat != "Grade ≥3"                             ~ "Grade <3",
+         gr2_CRS = case_when(
+           `Max CRS grade (0-5)` %in% c(0:1)                      ~ "Grade <2",
+           `Max CRS grade (0-5)` %in% c(2:3)                      ~ "Grade ≥2",
            TRUE                                                   ~ NA_character_
@@
          ICANS_gradecat = factor(ICANS_gradecat, levels = c("No ICANS", "Grade 1 or 2", "Grade ≥3")),
-         gr3_ICANS = case_when(
-           ICANS_gradecat == "Grade ≥3"                             ~ "Grade ≥3",
-           ICANS_gradecat != "Grade ≥3"                             ~ "Grade <3",
+         gr2_ICANS = case_when(
+           `Max ICANS (relative to infusion)` %in% c(0:1)         ~ "Grade <2",
+           `Max ICANS (relative to infusion)` %in% c(2:3)         ~ "Grade ≥2",
            TRUE                                                   ~ NA_character_
          )) %>%
-  # mutate(`marrow cellularity baseline` = case_when(
-  #   `marrow cellularity baseline` == "\"patchy\""                 ~ "hyper",
-  #   TRUE                                                          ~ `marrow cellularity baseline`
-  # )) %>% 
-  # mutate(`marrow cellularity day +30` = case_when(
-  #   `marrow cellularity day +30` == "aplastic"                    ~ "hypo",
-  #   TRUE                                                          ~ `marrow cellularity day +30`
-  # )) %>% 
-  # mutate(`Access type` = case_when(
-  #   `Access type` == "Femoral"                                    ~ "Non-tunneled",
-  #   `Access type` == "AVF"                                        ~ "Peripheral",
-  #   TRUE                                                          ~ `Access type`
-  # )) %>% 
-  # mutate(best_response = ) %>% 
-  # mutate(Neutropenia_apheresis = case_when(
-  #   `ANC apheresis` < 1.8                                           ~ "YES",
-  #   is.na(`ANC apheresis`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Neutropenia_-5d` = case_when(
-  #   `ANC day -5 (k/ul)` < 1.8                                        ~ "YES",
-  #   is.na(`ANC day -5 (k/ul)`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
-  # mutate(`Neutropenia_0d` = case_when(
-  #   `ANC day 0 (k/uL)` < 1.8                                        ~ "YES",
-  #   is.na(`ANC day 0 (k/uL)`)                                          ~ NA_character_,
-  #   TRUE                                                          ~ "NO"
-  # )) %>% 
+
   mutate(`Neutropenia_7d` = case_when(
@@
   )) %>% 
+  mutate(day30_response_group1 = case_when(
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
+    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "CR")          ~ "CR or sCR",
+    is.na(`Day 30 Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
+    TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR)`
+  )) %>% 
   mutate(day30_response_sCRvsOthers = case_when(
@@
   )) %>% 
+  mutate(day90_response_group1 = case_when(
+    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "VGPR")        ~ "VGPR",
+    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "PR")          ~ "PR",
+    str_detect(`3 Month Response (sCR, CR, VGPR, PR)`, "CR")          ~ "CR or sCR",
+    is.na(`3 Month Response (sCR, CR, VGPR, PR)`)                     ~ NA_character_,
+    TRUE           ~ `3 Month Response (sCR, CR, VGPR, PR)`
+  )) %>% 
   mutate(day90_response =`3 Month Response (sCR, CR, VGPR, PR)`
@@
   # )) %>% 
+  # Median follow up
+  mutate(time_leukapheresis_fup = 
+           interval(
+             start = date_of_apheresis, 
+             end = `Date of Last Contact`)/
+           duration(n=1, units = "days")) %>%
+  # Median time from leukapheresis to infusion 
+  mutate(time_leukapheresis_infusion = 
+           interval(
+             start = date_of_apheresis, 
+             end = `Date of CAR T infusion (# of days from apharesis to infusion)`)/
+           duration(n=1, units = "days")) %>%
+  # Code survival
   mutate(pfs_event = case_when(
@@
   )) %>% 
-
-  # Code survival
   mutate(pfs_time = coalesce(`Date of PD`, `Date of Death`, `Date of Last Contact`)) %>% 
@@
 #
-# # dose reduction
-# cart$`Fludarabine Dose Reduction`[cart$`Fludarabine Dose Reduction` == "YES (HD)"] <- "YES"
-# table(cart$`Fludarabine Dose Reduction`)
+
 # 
@@
          `Number of prior lines of therapy`,
+         number_prior_lines_therapy,
          `Disease status at time of referral (Relapsed vs Refractory)`,
@@
          immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-
-         `Cell Dose (million cells)`,
+         `Cell Dose (million cells)`, cart_cell_dose,
          exclusion_criteria,
@@
 
-         `Did patient met criteria for KarMMa1 pre-CAR-T?`) %>% 
+         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
+         time_leukapheresis_infusion, time_leukapheresis_fup) %>% 
   tbl_summary(
@@
 
+## From here, we excluded 38 patients
+```{r}
+cart0 %>% 
+  filter(!is.na(exclude_for_manufacturing_cart_failure_or_died_prior_cart_infusion)) %>% 
+  select(`Patients excluded` = patient_id)
+
+cart0 <- cart0 %>% 
+  # Exclude patients who had manufacturing cart failure or died prior cart infusion
+  filter(is.na(exclude_for_manufacturing_cart_failure_or_died_prior_cart_infusion))
+```
+
 ## Table 2. Safety with Standard of Care Idecabtagene Vicleucel Event and Grade
@@
 
-## Table 3.Characteristics associated with grade ≥ 3 CRS, grade ≥ 3 neurotoxicity, grade ≥ 3 cytopenias ≥ 30 days, best response of ≥ CR at 3 months, best ORR 
+## Table 3.Responses
+```{r}
+cart0 %>% 
+  select(day30_response, 
+         day30_response_group, day30_response_sCRvsOthers, 
+         day90_response, 
+         day90_response_group, day90_response_sCRvsOthers) %>% 
+  tbl_summary(missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
+
+left is day 30, top is day 90 - **restricted to patients who have a 30 day AND a 90 day response.**
+```{r}
+table(cart0$day30_response_sCRvsOthers, cart0$day90_response_sCRvsOthers)
+
+table(cart0$day30_response, cart0$day90_response)
+```
+
+```{r}
+cart0 %>% 
+  select(day90_response_group1, 
+         CRS_any) %>% 
+  tbl_summary(by= CRS_any,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p() %>% 
+  modify_footnote(update = everything() ~ NA) %>% 
+  modify_spanning_header(all_stat_cols() ~ "**Any CRS**")
+```
+
+Of the total 141 patients with a response, how many were MRD neg (N and %).
+```{r}
+cart0 %>% 
+  mutate(has_response = case_when(
+    !is.na(best_response)     ~ "Patient with responses"
+  )) %>% 
+  select(has_response, 
+         `Day 30 MRD (positive vs negative)`) %>% 
+  tbl_summary(by= has_response,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>%
+  modify_footnote(update = everything() ~ NA)
+
+cart0 %>% 
+  mutate(has_response = case_when(
+    !is.na(best_response)     ~ "Patient with responses"
+  )) %>% 
+  select(has_response, 
+         `3 Month MRD (positive vs negative)`) %>% 
+  tbl_summary(by= has_response,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>%
+  modify_footnote(update = everything() ~ NA)
+
+cart0 %>% 
+  mutate(has_response = case_when(
+    !is.na(best_response)     ~ "Patient with responses"
+  )) %>% 
+  select(has_response, 
+         best_MRD_response) %>% 
+  tbl_summary(by= has_response,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>%
+  modify_footnote(update = everything() ~ NA)
+```
+
+## Table 4.Characteristics associated with grade ≥ 3 CRS, grade ≥ 3 neurotoxicity, grade ≥ 3 cytopenias ≥ 30 days, best response of ≥ CR at 3 months, best ORR 
 ```{r}
@@
          `Number of prior lines of therapy`,
+         number_prior_lines_therapy,
          `Prior auto SCT (yes, no)`, 
@@
          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
-         gr3_CRS
+         gr2_CRS
   ) %>% 
-  tbl_summary(by = gr3_CRS,
+  tbl_summary(by = gr2_CRS,
               type = list(
@@
   modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Grade 3 CRS**")
+  modify_spanning_header(all_stat_cols() ~ "**Grade 2 CRS**")
 ```
@@
          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
-         gr3_ICANS
+         gr2_ICANS
   ) %>% 
-  tbl_summary(by = gr3_ICANS,
+  tbl_summary(by = gr2_ICANS,
               type = list(
@@
   modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Grade 3 ICANS**")
+  modify_spanning_header(all_stat_cols() ~ "**Grade 2 ICANS**")
 ```
@@
 
+```{r}
+# cart0 %>% 
+#   select(Age, agecat, male_sex, Sex,
+#          `Extramedullary Disease? (Yes, No)`, 
+#          `Disease status at time of referral (Relapsed vs Refractory)`,
+#          `Plasma Cell Leukemia? (yes, no)`,
+#          `Amyloid? (yes, no)`,
+#          POEMS,
+#          `Non-secretory MM (Yes, No)`, ################??????????
+#          `High Marrow Burden (>= 50%)`, 
+#          `ECOG at consult`, `ECOG at LD`, 
+#          `R-ISS at CAR-T infusion`, 
+#          cytogenetics,
+#          `Deletion 17p prior to CAR-T infusion (yes, no)`,
+#          `t(4:14) prior to CAR-T infusion (yes, no)`,
+#          `t(14:16) prior to CAR-T infusion (yes, no)`,
+#          `Bridging Therapy? (Yes, No)`,
+#          `Number of prior lines of therapy`,
+#          `Prior auto SCT (yes, no)`, 
+#          `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+#          `Prior Allo SCT (Yes, No)`,
+#          Blenrep,
+#          `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+#          `BCMA CAR-T on trial`, `Other BCMA trial`,
+#          immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+#          cart_cell_dose,
+#          `Infection (Yes, No)`,
+#          `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+#          baseline_ferritin, baseline_crp, baseline_B2M,
+#          `ECOG > or = 2? (Yes, No)`,
+#          `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+#          `LVEF <45% (Yes, No)`,
+#          `ANC < 1000/uL (Yes, No)`,
+#          `Hemoglobin < 8 g/dL (Yes, No)`,
+#          `Platelets < 50K (Yes, No)`, 
+#          `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+#          `Non-secretory MM (Yes, No)`,
+#          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
+#          `Number of prior lines of therapy`
+#   ) %>% 
+#   mutate(`Number of prior lines of therapy` = case_when(
+#     `Number of prior lines of therapy` <= 4           ~ "≤4",
+#     `Number of prior lines of therapy` > 4            ~ ">4",
+#   )) %>% 
+#   tbl_summary(by = `Number of prior lines of therapy`,
+#               type = list(
+#                 c(
+#                   `Extramedullary Disease? (Yes, No)`, 
+#                   `Plasma Cell Leukemia? (yes, no)`,
+#                   `Amyloid? (yes, no)`,
+#                   POEMS,
+#                   `Non-secretory MM (Yes, No)`,
+#                   `High Marrow Burden (>= 50%)`,
+#                   `ECOG at consult`, `ECOG at LD`,
+#                   cytogenetics,
+#                   `Deletion 17p prior to CAR-T infusion (yes, no)`,
+#                   `t(4:14) prior to CAR-T infusion (yes, no)`,
+#                   `t(14:16) prior to CAR-T infusion (yes, no)`,
+#                   `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
+#                   `ASCT within 12 weeks prior to apheresis (Yes, No)`,
+#                   `Prior Allo SCT (Yes, No)`,
+#                   Blenrep,
+#                   `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+#                   `BCMA CAR-T on trial`, `Other BCMA trial`,
+#                   immuno, proteasome, dara, doubleref, tripleref, pentaref,
+#                   `Infection (Yes, No)`,
+#                   `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
+#                   `ECOG > or = 2? (Yes, No)`,
+#                   `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
+#                   `LVEF <45% (Yes, No)`,
+#                   `ANC < 1000/uL (Yes, No)`,
+#                   `Hemoglobin < 8 g/dL (Yes, No)`,
+#                   `Platelets < 50K (Yes, No)`, 
+#                   `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
+#                   `Non-secretory MM (Yes, No)`,
+#                   
+#                   `Did patient met criteria for KarMMa1 pre-CAR-T?`
+#                 )
+#                 ~"categorical"),
+#               statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+#               digits = all_continuous() ~ 1
+#   ) %>% 
+#   bold_labels() %>% add_stat_label() %>% 
+#   add_p() %>% 
+#   modify_footnote(update = everything() ~ NA) %>%
+#   modify_spanning_header(all_stat_cols() ~ "**Line of therapy**")
+```
+
 ## Table 4.Characteristics associated with grade ≥ 3 CRS, grade ≥ 3 neurotoxicity, grade ≥ 3 cytopenias ≥ 30 days, best response of ≥ CR at 3 months, best ORR in Multivariable Models of Idecabtagene vicleucel-treated patients.
 ```{r}
-
+cart1 <- cart0 %>% 
+  mutate(day90_response_sCRvsOthers = case_when(
+    day90_response_sCRvsOthers == "Others"       ~ 0,
+    day90_response_sCRvsOthers == "CR or sCR"    ~ 1
+  ), 
+  day90_response_sCRvsOthers = factor(day90_response_sCRvsOthers)) %>% 
+  mutate(ORR_90days = case_when(
+    ORR_90days == "PD/SD/MR"    ~ 0,
+    ORR_90days == "ORR"         ~ 1
+  ), 
+  ORR_90days = factor(ORR_90days))
+```
+
+### CR or better
+```{r}
+glm(day90_response_sCRvsOthers ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease?
+(Yes, No)` + cart_cell_dose +
+        `ECOG at LD` + pentaref + number_prior_lines_therapy + Age,
+                data = cart1,
+    family = "binomial"(link='logit')) %>%
+            tbl_regression(exponentiate = TRUE) %>%
+            modify_spanning_header(everything() ~ "CR or sCR at 90 days vs Others")
+```
+
+### best ORR
+```{r}
+# clogit(ORR_90days ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease?
+(Yes, No)` + `Cell Dose (million cells)` +
+#         `ECOG at LD` + pentaref + Age,
+#                 data = cart1) #%>%
+            # tbl_regression(exponentiate = TRUE) %>%
+            # modify_spanning_header(everything() ~ "ORR at 90 days vs PD/SD/MR")
+```
+
+```{r}
+glm(ORR_90days ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease?
+(Yes, No)` + cart_cell_dose +
+        `ECOG at LD` + pentaref + number_prior_lines_therapy + Age,
+                data = cart1,
+    family = "binomial") %>%
+            tbl_regression(exponentiate = TRUE) %>%
+            modify_spanning_header(everything() ~ "ORR at 90 days vs PD/SD/MR")
+```
+
+### PFS
+```{r}
+coxph(Surv(time = cart0$days_at_pfs_from_infusion,
+           event = cart0$pfs_event) ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease?
+(Yes, No)` + cart_cell_dose +
+        `ECOG at LD` + pentaref + number_prior_lines_therapy + Age,
+      data =  cart0) %>%
+  tbl_regression(exponentiate = TRUE) %>%
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 ```
@@
   filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
+  mutate(name = factor(name, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
+  group_by(name) %>% 
+  mutate(n = sum(count)) %>% 
+  ungroup() %>% 
+  mutate(name =  paste0(name,'\nN = ',n)) %>% 
   ggplot(aes(x= name, y= percent, fill= value))+
   geom_bar(stat = "identity")+ 
-  scale_fill_brewer(palette = "Blues")+
+  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
+  geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
   ylim(0,100)+
@@
   theme_classic()
+
+cart0 %>% 
+  select(day30_response_group, day90_response_group, best_response) %>% 
+  pivot_longer(cols = everything()) %>% 
+  filter(!is.na(value)) %>% 
+  mutate(value = factor(value, levels = c("CR or sCR, MRD-",
+                                        "CR or sCR, MRD+",
+                                        "CR or sCR, MRD unknown",
+                                        "VGPR", "PR", "Others"))) %>% 
+  group_by(name, value) %>% 
+  summarise(count=n()) %>% 
+  mutate(percent=(count/sum(count)*100)
+  ) %>% 
+  filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
+  mutate(name = factor(name, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
+  group_by(name) %>% 
+  mutate(n = sum(count)) %>% 
+  ungroup() %>% 
+  mutate(name =  paste0(name,'\nN = ',n)) %>% 
+  ggplot(aes(x= name, y= percent, fill= value))+
+  geom_bar(stat = "identity")+ 
+  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
+  ylim(0,100)+
+  labs(x= NULL)+
+  theme_classic()
 ```
@@
 
-```{r, fig.width= 6, fig.height=6}
-myplot <- ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
+```{r, fig.width= 6, fig.height=4}
+myplot <-
+  ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
                    data = cart0),
@@
            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           legend = "none",
+           font.tickslab = c(18, "bold", "black"), 
            size = 1.5,
-
+           xlim = c(0, 12),
            pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
+           risk.table = FALSE,
+
+           ylab = "PFS probability",
+           xlab = "Time (in months)" 
 ) + guides(colour = guide_legend(ncol = 2))
@@
 Panel C: OS Kaplan Meier (from CAR-T infusion)
-```{r, fig.width= 6, fig.height=6}
+```{r, fig.width= 6, fig.height=4}
 myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ 1, 
@@
            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           legend = "none",
+           font.tickslab = c(18, "bold", "black"), 
            size = 1.5,
@@
            pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
+           risk.table = FALSE,
+
+           ylab = "OS probability",
+           xlab = "Time (in months)" 
 ) + guides(colour = guide_legend(ncol = 2))
@@
 
-```{r, fig.width= 6, fig.height=6}
+```{r, fig.width= 6, fig.height=4}
 myplot <- ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
@@
            size = 1.5,
-
+           xlim = c(0, 12),
            pval=TRUE, 
@@
            # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
+           risk.table = FALSE,
+
+           ylab = "PFS probability",
+           xlab = "Time (in months)" 
 ) + guides(colour = guide_legend(ncol = 1))
@@
 Panel C: OS Kaplan Meier (from CAR-T infusion)
-```{r, fig.width= 6, fig.height=6}
+```{r, fig.width= 6, fig.height=4}
 myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
@@
            # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
+           risk.table = FALSE,
+
+           ylab = "OS probability",
+           xlab = "Time (in months)" 
 ) + guides(colour = guide_legend(ncol = 1))
@@
   filter(!is.na(`Date of Death`)) %>% 
-  mutate(`Cause of death (myeloma, toxicitiy,other)` = case_when(
-    str_detect(`Cause of death (myeloma, toxicitiy,other)`, "Myeloma")      ~ "Myeloma",
-    str_detect(`Cause of death (myeloma, toxicitiy,other)`, "COVID")        ~ "COVID-19",
-    str_detect(`Cause of death (myeloma, toxicitiy,other)`, "oxicity")      ~ "Toxicity",
-    TRUE                                     ~ `Cause of death (myeloma, toxicitiy,other)`
-  )) %>% 
-  select(`Cause of death (myeloma, toxicitiy,other)`) %>%
+  mutate(`Cardiomyopathy/Acute systolic heart failure (EF 15-25% post CAR-T) (unknown viral illness prior to CAR-T that improved pre-infusion)` = case_when(
+    str_detect(`Cause of death (myeloma, toxicitiy,other)`, "Cardiomyopathy")      ~ "YES",
+    TRUE      ~ "NO"
+  )) %>% 
+  mutate(Myeloma = case_when(
+    str_detect(`Cause of death (myeloma, toxicitiy,other)`, "Myeloma")      ~ "YES",
+    TRUE      ~ "NO"
+  )) %>% 
+  mutate(`COVID-19` = case_when(
+    str_detect(`Cause of death (myeloma, toxicitiy,other)`, "COVID") &
+      !str_detect(`Cause of death (myeloma, toxicitiy,other)`, "Myeloma")    ~ "YES",
+    TRUE      ~ "NO"
+  )) %>% 
+  mutate(Toxicity = case_when(
+    str_detect(`Cause of death (myeloma, toxicitiy,other)`, "oxicity")      ~ "YES",
+    TRUE      ~ "NO"
+  )) %>% 
+  mutate(HLH = case_when(
+    str_detect(`Cause of death (myeloma, toxicitiy,other)`, "HLH")      ~ "YES",
+    TRUE      ~ "NO"
+  )) %>% 
+  select(`Cardiomyopathy/Acute systolic heart failure (EF 15-25% post CAR-T) (unknown viral illness prior to CAR-T that improved pre-infusion)`, `COVID-19`, HLH, Myeloma, Toxicity) %>%
   tbl_summary() %>%
@@
 ```
+1 patients had HLH and Toxicity “Toxicity - grade 5 CRS/HLH with superimposed infection”.  
+1 patient in Myeloma is "Myeloma (hypoxic resp failure with multiple lung masses, pleural fluid + PCs, strep due to cytopenias, COVID-19)".  
+1 patient is "And Myeloma, CNS".
 
@@
                                      "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
-  select(CRS_gradecat, cohort) %>%
-  tbl_summary(by= CRS_gradecat,
+  select(gr2_CRS, cohort) %>%
+  tbl_summary(by= gr2_CRS,
               # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
@@
                                      "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
-  select(ICANS_gradecat, cohort) %>%
-  tbl_summary(by= ICANS_gradecat,
+  select(gr2_ICANS, cohort) %>%
+  tbl_summary(by= gr2_ICANS,
               # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
@@
   ) %>%
-  tbl_survfit(times = c(3),
+  tbl_survfit(times = c(3, 6),
               label_header = "**PFS Rate at {time} Months**")

### 2022-05-11 RWE/RWE Manuscript analyses_05112022.Rmd
Full update

--- 2022-05-05 RWE/RWE Manuscript analyses.Rmd
@@
 ```{r load}
-# path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias")
+# path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias", "MM_CARTcell_cytopenia")
 # path <- getwd()
@@
 ```{r data cleaning}
+# per Doris e-mail communication on 5/6/22, remove Utah8 from the very beginning - should not be in any analyses
+MM_cart <- MM_cart %>% filter(patient_id != "Utah8")
 cart0 <- MM_cart %>% 
@@
   mutate(number_prior_lines_therapy = case_when(
-    `Number of prior lines of therapy` <= 4           ~ "≤4",
-    `Number of prior lines of therapy` > 4            ~ ">4",
+    `Number of prior lines of therapy` <= 4           ~ "4",
+    `Number of prior lines of therapy` > 4            ~ ">4"
   )) %>%
@@
          CRS_gradecat = factor(CRS_gradecat, levels = c("No CRS", "Grade 1 or 2", "Grade ≥3")),
-         gr2_CRS = case_when(
-           `Max CRS grade (0-5)` %in% c(0:1)                      ~ "Grade <2",
-           `Max CRS grade (0-5)` %in% c(2:3)                      ~ "Grade ≥2",
+         gr3_CRS = case_when(
+           `Max CRS grade (0-5)` %in% c(0:2)                      ~ "Grade <3",
+           `Max CRS grade (0-5)` %in% c(3:5)                      ~ "Grade ≥3",
            TRUE                                                   ~ NA_character_
@@
          gr2_ICANS = case_when(
-           `Max ICANS (relative to infusion)` %in% c(0:1)         ~ "Grade <2",
-           `Max ICANS (relative to infusion)` %in% c(2:3)         ~ "Grade ≥2",
+           `Max ICANS (relative to infusion)` %in% c(0:2)         ~ "Grade <3",
+           `Max ICANS (relative to infusion)` %in% c(3:5)         ~ "Grade ≥3",
            TRUE                                                   ~ NA_character_
@@
     `Cell Dose (million cells)` >= 400                               ~ "≥ 400",
-    `Cell Dose (million cells)` >= 300                               ~ "≥ 300",
+    `Cell Dose (million cells)` < 400                               ~ "< 400",
     TRUE                                                             ~ NA_character_
@@
 
+    TRUE                                                               ~ NA_character_
+  )) %>% 
+  mutate(best_CRorbetter = case_when(
+    best_response == "VGPR" |
+      best_response == "PR" |
+      best_response == "Others"                    ~ "< CR",
+    best_response == "CR or sCR, MRD-" |
+      best_response == "CR or sCR, MRD+" |
+      best_response == "CR or sCR, MRD unknown"  ~    "CR or better", 
+    TRUE                                                               ~ NA_character_
+  )) %>%  
+  mutate(best_ORRcollapsed = case_when(
+    best_response == "Others"                    ~ "< PR",
+    best_response == "CR or sCR, MRD-" |
+      best_response == "CR or sCR, MRD+" |
+      best_response == "CR or sCR, MRD unknown" |  
+      best_response == "VGPR" |
+      best_response == "PR"                      ~    "PR or better", 
     TRUE                                                               ~ NA_character_
@@
                        `Extramedullary Disease? (Yes, No)` = "Extramedullary disease",
-                       dara="Refractory to Daratumumab")
+                       dara="Refractory to Daratumumab", cytogenetics = "High-risk cytogenetics",
+                       male_sex = "Male sex", number_prior_lines_therapy = "Number of prior lines of therapy (4 vs. >4)",
+                       cart_cell_dose = "Cell dose (<400 vs. ≥400)", exclusion_criteria = "Number of KarMMa1 exclusion criteria",
+                       comorbidities = "Any comorbid conditions", time_leukapheresis_infusion = "Time from leukapheresis to infusion, days",
+                       time_leukapheresis_fup = "Time from leukapheresis to end of follow-up, days", 
+                       best_ORRcollapsed = "Best ORR at ≤ 90 days", best_CRorbetter = "Best CR or better at ≤ 90 days")
 
@@
 
-### Tables
+# Tables
 
@@
 
-## From here, we excluded 38 patients
+## From here, we excluded 37 patients
 ```{r}
@@
          day90_response, 
-         day90_response_group, day90_response_sCRvsOthers) %>% 
+         day90_response_group, day90_response_sCRvsOthers,
+         best_CRorbetter, best_ORRcollapsed) %>% 
   tbl_summary(missing = "no") %>% 
@@
   modify_spanning_header(all_stat_cols() ~ "**Any CRS**")
+
+cart0 %>% 
+  select(day30_response_group1, day90_response_group1, 
+         best_CRorbetter, best_ORRcollapsed,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
+  tbl_summary(by= `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p() %>% 
+  modify_footnote(update = everything() ~ NA) %>% 
+  modify_spanning_header(all_stat_cols() ~ "**Any Prior treatment BCMA**")
+
 ```
@@
          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
-         gr2_CRS
+         gr3_CRS
   ) %>% 
-  tbl_summary(by = gr2_CRS,
+  tbl_summary(by = gr3_CRS,
               type = list(
@@
   modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Grade 2 CRS**")
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3 CRS**")
 ```
@@
   modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Grade 2 ICANS**")
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3 ICANS**")
 ```
@@
          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
-         day90_response_sCRvsOthers
+         best_CRorbetter
   ) %>% 
-  tbl_summary(by = day90_response_sCRvsOthers,
+  tbl_summary(by = best_CRorbetter,
               type = list(
@@
   modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**day90_response_sCRvsOthers**")
+  modify_spanning_header(all_stat_cols() ~ "**Best CR or better at ≤ day 90**")
 ```
@@
          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
-         ORR_90days
+         best_ORRcollapsed
   ) %>% 
-  tbl_summary(by = ORR_90days,
+  tbl_summary(by = best_ORRcollapsed,
               type = list(
@@
   modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**ORR_90days**")
+  modify_spanning_header(all_stat_cols() ~ "**Best ORR at ≤ day 90**")
 ```
@@
 cart1 <- cart0 %>% 
-  mutate(day90_response_sCRvsOthers = case_when(
-    day90_response_sCRvsOthers == "Others"       ~ 0,
-    day90_response_sCRvsOthers == "CR or sCR"    ~ 1
+  mutate(best_CRorbetter = case_when(
+    best_CRorbetter == "< CR"       ~ 0,
+    best_CRorbetter == "CR or better"    ~ 1
   ), 
-  day90_response_sCRvsOthers = factor(day90_response_sCRvsOthers)) %>% 
-  mutate(ORR_90days = case_when(
-    ORR_90days == "PD/SD/MR"    ~ 0,
-    ORR_90days == "ORR"         ~ 1
+  best_CRorbetter = factor(best_CRorbetter)) %>% 
+  mutate(best_ORRcollapsed = case_when(
+    best_ORRcollapsed == "< PR"    ~ 0,
+    best_ORRcollapsed == "PR or better"         ~ 1
   ), 
-  ORR_90days = factor(ORR_90days))
+  best_ORRcollapsed = factor(best_ORRcollapsed))
 ```
@@
 ```{r}
-glm(day90_response_sCRvsOthers ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease?
+glm(best_CRorbetter ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease?
 (Yes, No)` + cart_cell_dose +
-        `ECOG at LD` + pentaref + number_prior_lines_therapy + Age,
+        `ECOG at LD` + pentaref + Age,
                 data = cart1,
     family = "binomial"(link='logit')) %>%  
-            tbl_regression(exponentiate = TRUE) %>%
-            modify_spanning_header(everything() ~ "CR or sCR at 90 days vs Others")
+            tbl_regression(exponentiate = TRUE) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
+            modify_spanning_header(everything() ~ "**Best CR or better vs. < CR**") %>%
+            bold_p(t = .05) 
 ```
@@
 ```{r}
-glm(ORR_90days ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease?
+glm(best_ORRcollapsed ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease?
 (Yes, No)` + cart_cell_dose +
-        `ECOG at LD` + pentaref + number_prior_lines_therapy + Age,
+        `ECOG at LD` + pentaref + Age,
                 data = cart1,
     family = "binomial") %>%
-            tbl_regression(exponentiate = TRUE) %>%
-            modify_spanning_header(everything() ~ "ORR at 90 days vs PD/SD/MR")
+            tbl_regression(exponentiate = TRUE) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
+            modify_spanning_header(everything() ~ "**Best ORR vs. < PR**") %>%
+            bold_p(t = .05) 
 ```
@@
 (Yes, No)` + cart_cell_dose +
-        `ECOG at LD` + pentaref + number_prior_lines_therapy + Age,
+        `ECOG at LD` + pentaref + Age,
       data =  cart0) %>%
   tbl_regression(exponentiate = TRUE) %>%
-  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
+  modify_spanning_header(everything() ~ "**PFS**") 
 ```
@@
 
-### Figures
+# Figures
 
 ## Figure 1. Response rate bar graph for day 30, day 90, Best ORR
+### Panel A
 ```{r}
@@
   ) %>% 
-  filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
-  mutate(name = factor(name, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
   group_by(name) %>% 
@@
   ungroup() %>% 
+  filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
+  mutate(name = factor(name, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
   mutate(name =  paste0(name,'\nN = ',n)) %>% 
@@
 
-Panel B: PFS Kaplan Meier (from CAR-T infusion)
-
-```{r, fig.width= 6, fig.height=4}
+### Panel B: PFS Kaplan Meier (from CAR-T infusion)
+
+```{r, fig.width= 6, fig.height=6}
 myplot <-
@@
            xlim = c(0, 12),
-           pval=TRUE, 
-           risk.table = FALSE,
-
+           #pval=TRUE, 
+           risk.table = TRUE,
+           break.time.by = 3,
+           legend.title = "",
            ylab = "PFS probability",
-           xlab = "Time (in months)" 
+           xlab = "Time (in months)", ggtheme = theme_classic(), palette = c("Set1")  
 ) + guides(colour = guide_legend(ncol = 2))
-myplot$plot <- myplot$plot + 
-  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
-myplot$table <- myplot$table + 
-  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$plot <- myplot$plot + 
+#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$table <- myplot$table + 
+#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
 myplot
@@
 
-Panel C: OS Kaplan Meier (from CAR-T infusion)
-```{r, fig.width= 6, fig.height=4}
+The 6-month PFS is:
+```{r}
+summary(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
+                   data = cart0), times = 6)
+```
+
+### Panel C: OS Kaplan Meier (from CAR-T infusion)
+```{r, fig.width= 6, fig.height=6}
 myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ 1, 
@@
            size = 1.5,
-
-           pval=TRUE, 
-           risk.table = FALSE,
-
+           #pval=TRUE, 
+           risk.table = TRUE,
+           break.time.by = 3,
+           legend.title = "",
            ylab = "OS probability",
-           xlab = "Time (in months)" 
+           xlab = "Time (in months)", ggtheme = theme_classic(), palette = c("Set1") 
 ) + guides(colour = guide_legend(ncol = 2))
-myplot$plot <- myplot$plot + 
-  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
-myplot$table <- myplot$table + 
-  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$plot <- myplot$plot + 
+  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$table <- myplot$table + 
+  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
 myplot
@@
 
-Panel D: Duration of response graph
-Waiting Tuesday
-```{r}
-
+The 6-month OS is:
+```{r}
+summary(survfit(Surv(days_at_os_from_infusion, os_event) ~ 1, 
+                   data = cart0), times = 6)
+```
+
+### Panel D: Duration of response graph
+Limit to the patients who have a response
+```{r}
+cart1 <- cart0 %>% 
+  filter(!is.na(best_CRorbetter)) %>% 
+  mutate(added = case_when(
+    day30_response_group %in% c("CR or sCR, MRD-",
+                                "CR or sCR, MRD+", 
+                                "CR or sCR, MRD unknown",
+                                "VGPR", "PR")       ~ 30,
+    day90_response_group %in% c("CR or sCR, MRD-",
+                                "CR or sCR, MRD+", 
+                                "CR or sCR, MRD unknown",
+                                "VGPR", "PR")      ~ 90
+  )) %>% 
+  mutate(response_date = case_when(
+    day30_response_group %in% c("CR or sCR, MRD-",
+                                "CR or sCR, MRD+", 
+                                "CR or sCR, MRD unknown",
+                                "VGPR", "PR")       ~ `Date of CAR T infusion (# of days from apharesis to infusion)` + days(30),
+    day90_response_group %in% c("CR or sCR, MRD-",
+                                "CR or sCR, MRD+", 
+                                "CR or sCR, MRD unknown",
+                                "VGPR", "PR")      ~ `Date of CAR T infusion (# of days from apharesis to infusion)` + days(90)
+    )) %>% 
+  mutate(months_at_pfs_from_response =
+           interval(
+             start = response_date,
+             end = pfs_time)/
+           duration(n=1, units = "months"))
+
+ggsurvplot(survfit(Surv(months_at_pfs_from_response, pfs_event) ~ 1, 
+                   data = cart1),
+           title = "Duration of response", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           legend = "none",
+           font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+           xlim = c(0, 12),
+           #pval=TRUE, 
+           risk.table = TRUE,
+           break.time.by = 3,
+           legend.title = "",
+           ylab = "Duration of response (probability)",
+           xlab = "Time since earliest response (months)", ggtheme = theme_classic(), palette = c("Set1")  
+) + guides(colour = guide_legend(ncol = 2))
+
+survfit(Surv(months_at_pfs_from_response, pfs_event) ~ 1, 
+                   data = cart1)
 ```
@@
 ## Figure 2. Consort diagram
+Lauren
+<br>
 
@@
 
-```{r, fig.width= 6, fig.height=4}
+```{r, fig.width= 6, fig.height=6}
 myplot <- ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
@@
            # palette = c("black", "green","blue", "red"), 
-           risk.table = FALSE,
-
+           risk.table = TRUE,
            ylab = "PFS probability",
-           xlab = "Time (in months)" 
+           xlab = "Time (in months)", 
+           break.time.by = 3,
+           risk.table.col = "strata",
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "Met KarMMa1 criteria",
+           legend.labs = c("No", "Yes")
 ) + guides(colour = guide_legend(ncol = 1))
-myplot$plot <- myplot$plot + 
-  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
-myplot$table <- myplot$table + 
-  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$plot <- myplot$plot + 
+  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$table <- myplot$table + 
+  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12)) + legend_title=""
 myplot
@@
 Panel C: OS Kaplan Meier (from CAR-T infusion)
-```{r, fig.width= 6, fig.height=4}
+```{r, fig.width= 6, fig.height=6}
 myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
@@
            # palette = c("black", "green","blue", "red"), 
-           risk.table = FALSE,
-
+           risk.table = TRUE,
+           break.time.by = 3,
+           risk.table.col = "strata",
            ylab = "OS probability",
-           xlab = "Time (in months)" 
+           xlab = "Time (in months)", 
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "Met KarMMa1 criteria",
+           legend.labs = c("No", "Yes")
 ) + guides(colour = guide_legend(ncol = 1))
-myplot$plot <- myplot$plot + 
-  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
-myplot$table <- myplot$table + 
-  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$plot <- myplot$plot + 
+  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$table <- myplot$table + 
+  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
 myplot
@@
 survfit(Surv(days_at_os_from_infusion, os_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
+                   data = cart0)
+```
+
+## Figure 4: OS and PFS stratified by any BCMA. 
+```{r}
+cart0 <- cart0 %>% 
+  rename(AnyBCMA = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
+  mutate(Overall = "Overall")
+```
+
+```{r, fig.width= 6, fig.height=6}
+myplot <- ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ AnyBCMA,
+                   data = cart0),
+           title = "PFS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+           xlim = c(0, 12),
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           risk.table = TRUE,
+           break.time.by = 3,
+           risk.table.col = "strata",
+           ylab = "PFS probability",
+           xlab = "Time (in months)", 
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "Any BCMA therapy",
+           legend.labs = c("No", "Yes")
+) + guides(colour = guide_legend(ncol = 1))
+#myplot$plot <- myplot$plot + 
+  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
+
+survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ AnyBCMA, 
+                   data = cart0)
+```
+
+```{r, fig.width= 6, fig.height=6}
+myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ AnyBCMA, 
+                   data = cart0),
+           title = "OS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           risk.table = TRUE,
+           break.time.by = 3,
+           risk.table.col = "strata",
+           ylab = "OS probability",
+           xlab = "Time (in months)", 
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "Any BCMA therapy",
+           legend.labs = c("No", "Yes")
+) + guides(colour = guide_legend(ncol = 1))
+#myplot$plot <- myplot$plot + 
+  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$table <- myplot$table + 
+  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
+
+survfit(Surv(days_at_os_from_infusion, os_event) ~ AnyBCMA, 
+                   data = cart0)
+```
+
+## Figure 4a: OS and PFS stratified by Blenrep. 
+```{r, fig.width= 6, fig.height=6}
+myplot <- ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ Blenrep,
+                   data = cart0),
+           title = "PFS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+           xlim = c(0, 12),
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           risk.table = TRUE,
+           break.time.by = 3,
+           risk.table.col = "strata",
+           ylab = "PFS probability",
+           xlab = "Time (in months)", 
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "Blenrep",
+           legend.labs = c("No", "Yes")
+) + guides(colour = guide_legend(ncol = 1))
+#myplot$plot <- myplot$plot + 
+ # scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
+
+survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ Blenrep, 
+                   data = cart0)
+```
+
+```{r, fig.width= 6, fig.height=6}
+myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ Blenrep, 
+                   data = cart0),
+           title = "OS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           risk.table = TRUE,
+           break.time.by = 3,
+           risk.table.col = "strata",
+           ylab = "OS probability",
+           xlab = "Time (in months)", 
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "Blenrep",
+           legend.labs = c("No", "Yes")
+) + guides(colour = guide_legend(ncol = 1))
+#myplot$plot <- myplot$plot + 
+  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$table <- myplot$table + 
+  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
+
+survfit(Surv(days_at_os_from_infusion, os_event) ~ Blenrep, 
+                   data = cart0)
+```
+
+## Figure 4b: OS and PFS stratified by BCMA CAR-T on trial 
+```{r}
+cart0 <- cart0 %>% 
+  rename(BCMA_ontrial = `BCMA CAR-T on trial`) %>% 
+  mutate(Overall = "Overall")
+```
+
+```{r, fig.width= 6, fig.height=6}
+myplot <- ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ BCMA_ontrial,
+                   data = cart0),
+           title = "PFS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+           xlim = c(0, 12),
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           risk.table = TRUE,
+           break.time.by = 3,
+           risk.table.col = "strata",
+           ylab = "PFS probability",
+           xlab = "Time (in months)", 
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "BCMA CAR-T on trial",
+           legend.labs = c("No", "Yes")
+) + guides(colour = guide_legend(ncol = 1))
+#myplot$plot <- myplot$plot + 
+ # scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
+
+survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ BCMA_ontrial, 
+                   data = cart0)
+```
+
+```{r, fig.width= 6, fig.height=6}
+myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ BCMA_ontrial, 
+                   data = cart0),
+           title = "OS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           risk.table = TRUE,
+           break.time.by = 3,
+           risk.table.col = "strata",
+           ylab = "OS probability",
+           xlab = "Time (in months)", 
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "BCMA CAR-T on trial",
+           legend.labs = c("No", "Yes")
+) + guides(colour = guide_legend(ncol = 1))
+#myplot$plot <- myplot$plot + 
+ # scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$table <- myplot$table + 
+ # scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
+
+survfit(Surv(days_at_os_from_infusion, os_event) ~ BCMA_ontrial, 
+                   data = cart0)
+```
+
+## Figure 4c: OS and PFS stratified by other BCMA trial 
+```{r}
+cart0 <- cart0 %>% 
+  rename(BCMA_other = `Other BCMA trial`) %>% 
+  mutate(Overall = "Overall")
+```
+
+```{r, fig.width= 6, fig.height=6}
+myplot <- ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ BCMA_other,
+                   data = cart0),
+           title = "PFS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+           xlim = c(0, 12),
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           risk.table = TRUE,
+           break.time.by = 3,
+           risk.table.col = "strata",
+           ylab = "PFS probability",
+           xlab = "Time (in months)", 
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "Other BCMA trial",
+           legend.labs = c("No", "Yes")
+) + guides(colour = guide_legend(ncol = 1))
+#myplot$plot <- myplot$plot + 
+#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
+
+survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ BCMA_other, 
+                   data = cart0)
+```
+
+```{r, fig.width= 6, fig.height=6}
+myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ BCMA_other, 
+                   data = cart0),
+           title = "OS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           risk.table = TRUE,
+           break.time.by = 3,
+           risk.table.col = "strata",
+           ylab = "OS probability",
+           xlab = "Time (in months)", 
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "Other BCMA trial",
+           legend.labs = c("No", "Yes")
+) + guides(colour = guide_legend(ncol = 1))
+#myplot$plot <- myplot$plot + 
+#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$table <- myplot$table + 
+#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
+
+survfit(Surv(days_at_os_from_infusion, os_event) ~ BCMA_other, 
+                   data = cart0)
+```
+
+## Figure 5: OS and PFS stratified by high-risk cytogenetics 
+```{r, fig.width= 6, fig.height=6}
+myplot <- ggsurvplot(survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ cytogenetics,
+                   data = cart0),
+           title = "PFS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+           xlim = c(0, 12),
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           risk.table = TRUE,
+           break.time.by = 3,
+           risk.table.col = "strata",
+           ylab = "PFS probability",
+           xlab = "Time (in months)", 
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "High-risk cytogenetics",
+           legend.labs = c("No", "Yes")
+) + guides(colour = guide_legend(ncol = 1))
+#myplot$plot <- myplot$plot + 
+#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
+
+survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ cytogenetics, 
+                   data = cart0)
+```
+
+```{r, fig.width= 6, fig.height=6}
+myplot <- ggsurvplot(survfit(Surv(days_at_os_from_infusion, os_event) ~ cytogenetics, 
+                   data = cart0),
+           title = "OS from date of infusion", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           risk.table = TRUE,
+           break.time.by = 3,
+           risk.table.col = "strata",
+           ylab = "OS probability",
+           xlab = "Time (in months)", 
+           ggtheme = theme_classic(), palette = c("Set1"),
+           legend.title = "High-risk cytogenetics",
+           legend.labs = c("No", "Yes")
+) + guides(colour = guide_legend(ncol = 1))
+#myplot$plot <- myplot$plot + 
+#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+#myplot$table <- myplot$table + 
+#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
+myplot
+
+survfit(Surv(days_at_os_from_infusion, os_event) ~ cytogenetics, 
                    data = cart0)
@@
               # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
-              statistic = all_categorical() ~ "{n}",
+              statistic = all_categorical() ~ "{n}"
               # percent = "row"
@@
                                      "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
-  select(gr2_CRS, cohort) %>%
-  tbl_summary(by= gr2_CRS,
+  select(gr3_CRS, cohort) %>%
+  tbl_summary(by= gr3_CRS,
               # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
@@
 #                    data = cart0)
+```
+
+```{r}
+cart1 <- cart0 %>% 
+  janitor::clean_names()
+```
+
+```{r}
 tbl1 <- tbl_survfit(
-  cart0,
+  cart1,
   y = Surv(days_at_pfs_from_infusion, pfs_event),
-  include = c(Overall, Did_patient_met_criteria_for_KarMMa1_pre_CAR_T#, 
+  include = c(overall, did_patient_met_criteria_for_kar_m_ma1_pre_car_t#, 
               # CRS_any, CRS_gradecat, ICANS_any, ICANS_gradecat
@@
 )
+
 # 3 month pfs rate
-
 tbl2 <- list(
     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
-                   data = cart0),
-    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
-                   data = cart0)#,
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ did_patient_met_criteria_for_kar_m_ma1_pre_car_t, 
+                   data = cart1),
+
+    # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ age, 
+    #                data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ agecat, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ male_sex, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ sex, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ extramedullary_disease_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ disease_status_at_time_of_referral_relapsed_vs_refractory, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ plasma_cell_leukemia_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ amyloid_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ poems, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ non_secretory_mm_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ high_marrow_burden_50_percent, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ecog_at_consult, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ecog_at_ld, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ r_iss_at_car_t_infusion, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ cytogenetics, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ deletion_17p_prior_to_car_t_infusion_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ t_4_14_prior_to_car_t_infusion_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ t_14_16_prior_to_car_t_infusion_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ bridging_therapy_yes_no, 
+                   data = cart1),
+    # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ number_of_prior_lines_of_therapy, 
+    #                data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ number_prior_lines_therapy, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ prior_auto_sct_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ asct_within_12_weeks_prior_to_apheresis_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ prior_allo_sct_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ blenrep, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ any_bcma, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ bcma_ontrial, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ bcma_other, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ immuno, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ proteasome, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ doubleref, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ tripleref, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ pentaref, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ cart_cell_dose, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ infection_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ tocilizumab_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ steroid_use_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ anakinra_yes_no, 
+                   data = cart1),
+
+    # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ baseline_ferritin, 
+    #                data = cart1),
+    # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ baseline_crp, 
+    #                data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ baseline_b2m, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ecog_or_2_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ renal_insufficiency_cr_cl_45_m_l_min_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ lvef_45_percent_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ anc_1000_u_l_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ hemoglobin_8_g_d_l_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ platelets_50k_yes_no, 
+                   data = cart1),
+    survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ h_o_or_presence_of_plasma_cell_leukemia_waldenstroms_poems_or_amyloidosis_yes_no, 
+                   data = cart1)
+
     # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ CRS_any,
-    #                data = cart0),
+    #                data = cart1),
     # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ CRS_gradecat,
-    #                data = cart0),
+    #                data = cart1),
     # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ICANS_any,
-    #                data = cart0),
+    #                data = cart1),
     # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ICANS_gradecat,
-    #                data = cart0)
+    #                data = cart1)
   ) %>%
   tbl_survfit(times = c(3, 6),
-              label_header = "**PFS Rate at {time} Months**")
+              label_header = "**PFS Rate at {time} Months**",
+              type = list(
+                c(age
+                ) ~ "continuous"))
 

### 2022-05-13 RWE/RWE Manuscript analyses_.Rmd
Modify plot, add variables

--- 2022-05-11 RWE/RWE Manuscript analyses_05112022.Rmd
@@
            duration(n=1, units = "days")) %>%
+  mutate(time_infusion_fup = 
+           interval(
+             start = `Date of CAR T infusion (# of days from apharesis to infusion)`, 
+             end = `Date of Last Contact`)/
+           duration(n=1, units = "days")) %>%
   # Median time from leukapheresis to infusion 
@@
            interval(
-             start = date_of_apheresis, 
+             start = `Date of CAR T infusion (# of days from apharesis to infusion)`, 
              end = pfs_time)/
@@
            interval(
-             start = date_of_apheresis, 
+             start = `Date of CAR T infusion (# of days from apharesis to infusion)`, 
              end = os_time)/
@@
                        cart_cell_dose = "Cell dose (<400 vs. ≥400)", exclusion_criteria = "Number of KarMMa1 exclusion criteria",
-                       comorbidities = "Any comorbid conditions", time_leukapheresis_infusion = "Time from leukapheresis to infusion, days",
+                       comorbidities = "Any comorbid conditions", 
+                       time_leukapheresis_infusion = "Time from leukapheresis to infusion, days",
                        time_leukapheresis_fup = "Time from leukapheresis to end of follow-up, days", 
+                       time_infusion_fup = "Time from infusion to end of follow-up, days", 
                        best_ORRcollapsed = "Best ORR at ≤ 90 days", best_CRorbetter = "Best CR or better at ≤ 90 days")
@@
          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
-         time_leukapheresis_infusion, time_leukapheresis_fup) %>% 
+         time_leukapheresis_infusion, time_infusion_fup,
+         time_leukapheresis_fup) %>% 
   tbl_summary(
@@
   ) %>% 
+  filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
+  mutate(name = factor(name, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
   group_by(name) %>% 
@@
   ungroup() %>% 
-  filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
-  mutate(name = factor(name, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
   mutate(name =  paste0(name,'\nN = ',n)) %>% 
@@
   theme_classic()
+
+cart0 %>% 
+  select(day30_response_group, day90_response_group, best_response, 
+         any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
+  pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
+  filter(!is.na(status)) %>% 
+  mutate(status = factor(status, levels = c("CR or sCR, MRD-",
+                                        "CR or sCR, MRD+",
+                                        "CR or sCR, MRD unknown",
+                                        "VGPR", "PR", "Others"))) %>%
+  group_by(any_bcma, response, status) %>% 
+  summarise(count=n()) %>% 
+  mutate(percent=(count/sum(count)*100)
+  ) %>% 
+  # Count N 
+  group_by(response) %>% 
+  mutate(N = sum(count)) %>% 
+  ungroup() %>% 
+  filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
+  mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
+  mutate(response =  paste0(response,'\nN = ',N)) %>%
+
+  ggplot(aes(x= any_bcma, y= percent, fill= status))+
+  geom_bar(stat = "identity")+ 
+  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
+  geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
+  ylim(0,100)+
+  labs(x= NULL)+
+  theme_classic()+
+  facet_wrap(. ~ response)
+
+cart0 %>% 
+  select(day30_response_group, day90_response_group, best_response, 
+         any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
+  pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
+  filter(!is.na(status)) %>% 
+  mutate(status = factor(status, levels = c("CR or sCR, MRD-",
+                                        "CR or sCR, MRD+",
+                                        "CR or sCR, MRD unknown",
+                                        "VGPR", "PR", "Others"))) %>%
+  group_by(any_bcma, response, status) %>% 
+  summarise(count=n()) %>% 
+  mutate(percent=(count/sum(count)*100)
+  ) %>% 
+  # Count N 
+  group_by(response) %>% 
+  mutate(N = sum(count)) %>% 
+  ungroup() %>% 
+  filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
+  mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
+  mutate(response =  paste0(response,'\nN = ',N)) %>%
+
+  ggplot(aes(x= any_bcma, y= percent, fill= status))+
+  geom_bar(stat = "identity")+ 
+  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
+  # geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
+  ylim(0,100)+
+  theme_classic()+
+  facet_wrap(. ~ response)
+
+cart0 %>% 
+  select(day30_response_group, day90_response_group, best_response, 
+         any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
+  pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
+  filter(!is.na(status)) %>% 
+  mutate(status = factor(status, levels = c("CR or sCR, MRD-",
+                                        "CR or sCR, MRD+",
+                                        "CR or sCR, MRD unknown",
+                                        "VGPR", "PR", "Others"))) %>%
+  group_by(any_bcma, response, status) %>% 
+  summarise(count=n()) %>% 
+  mutate(percent=(count/sum(count)*100)
+  ) %>% 
+  # Count N 
+  group_by(response) %>% 
+  mutate(N = sum(count)) %>% 
+  ungroup() %>% 
+  filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
+  mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
+  mutate(response =  paste0(response,'\nN = ',N)) %>%
+
+  ggplot(aes(x= (interaction(any_bcma, response)), y= percent, fill= status))+
+  geom_bar(stat = "identity")+ 
+  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
+  geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
+  ylim(0,100)+
+  labs(x= NULL)+
+  theme_classic()
+
+cart0 %>% 
+  select(day30_response_group, day90_response_group, best_response, 
+         any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
+  pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
+  filter(!is.na(status)) %>% 
+  mutate(status = factor(status, levels = c("CR or sCR, MRD-",
+                                        "CR or sCR, MRD+",
+                                        "CR or sCR, MRD unknown",
+                                        "VGPR", "PR", "Others"))) %>%
+  group_by(any_bcma, response, status) %>% 
+  summarise(count=n()) %>% 
+  mutate(percent=(count/sum(count)*100)
+  ) %>% 
+  # Count N 
+  group_by(response) %>% 
+  mutate(N = sum(count)) %>% 
+  ungroup() %>% 
+  filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
+  mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
+  mutate(response =  paste0(response,'\nN = ',N)) %>%
+
+  ggplot(aes(x= (interaction(any_bcma, response)), y= percent, fill= status))+
+  geom_bar(stat = "identity")+ 
+  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
+  ylim(0,100)+
+  theme_classic()
+
+# a <- cart0 %>% 
+#   select(day30_response_group, day90_response_group, best_response, 
+#          any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
+#   pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
+#   filter(!is.na(status)) %>% 
+#   mutate(status = factor(status, levels = c("CR or sCR, MRD-",
+#                                         "CR or sCR, MRD+",
+#                                         "CR or sCR, MRD unknown",
+#                                         "VGPR", "PR", "Others"))) %>%
+#   group_by(any_bcma, response, status) %>% 
+#   summarise(count=n()) %>% 
+#   mutate(percent=(count/sum(count)*100)
+#   ) %>% 
+#   # Count N 
+#   group_by(response) %>% 
+#   mutate(N = sum(count)) %>% 
+#   ungroup() %>% 
+#   filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
+#   mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
+#   mutate(response =  paste0(response,'\nN = ',N))
+# 
+# b <- a %>% filter(any_bcma == "NO")
+# a %>% filter(any_bcma == "YES") %>% 
+#   ggplot(aes(x= name, y= percent, fill= value))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9)
+#            )+
+#   # geom_bar(stat = "identity",
+#   #          # position=position_dodge(width=0.9), 
+#   #          data= b,
+#   #          aes(x= name, y= percent, fill= value), alpha= 0.4)+
+#   scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
+#   ylim(0,100)+
+#   labs(x= NULL)+
+#   theme_classic()
+# 
+# a %>% filter(any_bcma == "YES") %>% 
+#   ggplot(aes(x= name, y= percent, fill= value))+
+#   geom_col(stat = "identity",
+#            # position=position_dodge(width=0.9)
+#            )+
+#   geom_col(stat = "identity",
+#            # position=position_dodge(width=0.9),
+#            data= b,
+#            aes(x= name, y= percent, fill= value), alpha= 0.4)+
+#   scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
+#   ylim(0,100)+
+#   labs(x= NULL)+
+#   theme_classic()
 ```
@@
            size = 1.5,
+           xlim = c(0, 12),
            #pval=TRUE, 
@@
              end = pfs_time)/
-           duration(n=1, units = "months"))
+           duration(n=1, units = "months")) %>% 
+  rename(any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`)
 
@@
            font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.x = c(14, "bold", "black"), font.y = c(14, "bold", "black"), 
            legend = "none",
@@
                    data = cart1)
+
+# ggsurvplot(survfit(Surv(months_at_pfs_from_response, pfs_event) ~ any_bcma, 
+#                    data = cart1),
+#            title = "Duration of response", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(14, "bold", "black"), font.y = c(14, "bold", "black"), 
+#            legend = "top", legend.title = "Any BCMA therap",
+#            legend.labs = c("No", "Yes"),
+#            font.legend = c(14, "bold", "black"),
+#            font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            xlim = c(0, 12),
+#            pval=TRUE,
+#            risk.table = TRUE,
+#            risk.table.col = "strata",
+#            break.time.by = 3,
+#            ylab = "Duration of response (probability)",
+#            xlab = "Time since earliest response (months)", ggtheme = theme_classic(), palette = c("Set1")  
+# ) + guides(colour = guide_legend(ncol = 2))
 ```
@@
     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ did_patient_met_criteria_for_kar_m_ma1_pre_car_t, 
-                   data = cart1),
-
-    # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ age, 
-    #                data = cart1),
+                   data = cart1)
+  ) %>%
+  tbl_survfit(times = c(3, 6),
+              label_header = "**PFS Rate at {time} Months**")
+
+tbl_merge(list(tbl1, tbl2))
+```
+
+Extra PFS analysis
+```{r}
+tbl1 <- tbl_survfit(
+  cart1,
+  y = Surv(days_at_pfs_from_infusion, pfs_event),
+  include = c(agecat, male_sex, sex, extramedullary_disease_yes_no, 
+              disease_status_at_time_of_referral_relapsed_vs_refractory, 
+              plasma_cell_leukemia_yes_no, amyloid_yes_no, poems, 
+              non_secretory_mm_yes_no, high_marrow_burden_50_percent, 
+              ecog_at_consult, ecog_at_ld, r_iss_at_car_t_infusion, 
+              cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no, 
+              t_4_14_prior_to_car_t_infusion_yes_no, 
+              t_14_16_prior_to_car_t_infusion_yes_no, 
+              bridging_therapy_yes_no, number_prior_lines_therapy, 
+              prior_auto_sct_yes_no, 
+              asct_within_12_weeks_prior_to_apheresis_yes_no, 
+              prior_allo_sct_yes_no, blenrep, any_bcma, bcma_ontrial, 
+              bcma_other, immuno, proteasome, doubleref, tripleref, 
+              pentaref, cart_cell_dose, infection_yes_no, tocilizumab_yes_no, 
+              steroid_use_yes_no, anakinra_yes_no, baseline_b2m, ecog_or_2_yes_no, 
+              renal_insufficiency_cr_cl_45_m_l_min_yes_no, lvef_45_percent_yes_no, 
+              anc_1000_u_l_yes_no, hemoglobin_8_g_d_l_yes_no, platelets_50k_yes_no,
+              h_o_or_presence_of_plasma_cell_leukemia_waldenstroms_poems_or_amyloidosis_yes_no
+              ),
+  probs = 0.5,
+  label_header = "**Median PFS**"
+)
+
+# 3 month pfs rate
+tbl2 <- list(
     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ agecat, 
@@
   tbl_survfit(times = c(3, 6),
-              label_header = "**PFS Rate at {time} Months**",
-              type = list(
-                c(age
-                ) ~ "continuous"))
+              label_header = "**PFS Rate at {time} Months**")
 
@@
 ```
+
+P-value log rank
+```{r}
+cart1 %>% 
+  select(agecat, male_sex, sex, extramedullary_disease_yes_no, 
+              disease_status_at_time_of_referral_relapsed_vs_refractory,
+              plasma_cell_leukemia_yes_no, amyloid_yes_no, poems,
+              non_secretory_mm_yes_no, high_marrow_burden_50_percent,
+              ecog_at_consult, ecog_at_ld, r_iss_at_car_t_infusion,
+              cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no,
+              t_4_14_prior_to_car_t_infusion_yes_no,
+              t_14_16_prior_to_car_t_infusion_yes_no,
+              bridging_therapy_yes_no, number_prior_lines_therapy,
+              prior_auto_sct_yes_no) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = cart1$days_at_pfs_from_infusion, event = cart1$pfs_event)),
+                 exponentiate = TRUE) %>% 
+    modify_column_hide(c(stat_n, estimate, ci)) %>% 
+    bold_p(t = .05)# %>% add_nevent(location = "level") %>% add_n(location = "level")
+
+cart1 %>% 
+  select(asct_within_12_weeks_prior_to_apheresis_yes_no, 
+              prior_allo_sct_yes_no, blenrep, any_bcma, bcma_ontrial, 
+              bcma_other, immuno, proteasome, doubleref, tripleref, 
+              pentaref, cart_cell_dose, infection_yes_no, tocilizumab_yes_no, 
+              steroid_use_yes_no, anakinra_yes_no, baseline_b2m, ecog_or_2_yes_no, 
+              renal_insufficiency_cr_cl_45_m_l_min_yes_no, lvef_45_percent_yes_no, 
+              anc_1000_u_l_yes_no, hemoglobin_8_g_d_l_yes_no, platelets_50k_yes_no,
+              h_o_or_presence_of_plasma_cell_leukemia_waldenstroms_poems_or_amyloidosis_yes_no) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = cart1$days_at_pfs_from_infusion, event = cart1$pfs_event)),
+                 exponentiate = TRUE) %>% 
+    modify_column_hide(c(stat_n, estimate, ci)) %>% 
+    bold_p(t = .05)# %>% add_nevent(location = "level") %>% add_n(location = "level")
+```

### 2022-05-25 ide_cel/Manuscript analyses.Rmd
Add response to co-authors

@@
 ```{r library}
+library(here)
 library(tidyverse)
@@
 Characteristics <-
-  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
+  readxl::read_xlsx(paste0(here(), "/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx"),
                     sheet = "Characteristics", skip = 1, n_max = 54) %>% 
@@
 Counts <-
-  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
+  readxl::read_xlsx(paste0(here(), "/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx"),
                     sheet = "Counts") %>% 
@@
 Infections <-
-  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
+  readxl::read_xlsx(paste0(here(), "/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx"),
                     sheet = "Infections") %>% 
@@
 Support <-
-  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
+  readxl::read_xlsx(paste0(here(), "/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx"),
                     sheet = "Support",
@@
 Pneumo_titers <-
-  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
+  readxl::read_xlsx(paste0(here(), "/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx"),
                     sheet = "Pneumo Titers") %>% 
@@
 Other_titers <-
-  readxl::read_xlsx("/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx",
+  readxl::read_xlsx(paste0(here(), "/ide_cel/CytopeniaManuscriptData_4.13.22.xlsx"),
                     sheet = "Other Titers") %>% 
   mutate(MRN = as.character(MRN))
+Bridging <- 
+  readxl::read_xlsx(paste0(here(), "/ide_cel/CytopeniaManuscriptData_5.21.xlsx"),
+                    sheet = "Characteristics", skip = 1, n_max = 54) %>% 
+  mutate(MRN = as.character(MRN),
+         MRN = coalesce(MRN, PT)) %>% 
+  select(PT, MRN, `Days from last bridging to CAR-T infusion`)
 ```
@@
   select(-`Date of leukapheresis.y`, `Date of leukapheresis` = `Date of leukapheresis.x`) %>% 
-  full_join(., Other_titers, by = c("PT", "MRN"))
+  full_join(., Other_titers, by = c("PT", "MRN")) %>% 
+  full_join(., Bridging, by = c("PT", "MRN"))
 ```
@@
               . == 0                                              ~ "Exposed",
-              TRUE                                                ~ NA_character_
+              is.na(.)                                            ~ "Not Refractory"
             )) %>% 
   mutate(immuno = case_when(
-    `Lenalidomide (exposed=0 vs. refractory=1)` == "Exposed" &
-      `Pomalidomide (exposed=0 vs. refractory=1)` == "Exposed"        ~ "NO",
     `Lenalidomide (exposed=0 vs. refractory=1)` == "Refractory" |
-      `Pomalidomide (exposed=0 vs. refractory=1)` == "Refractory"     ~ "YES"
+      `Pomalidomide (exposed=0 vs. refractory=1)` == "Refractory"     ~ "YES",
+    TRUE        ~ "NO"
   )) %>% 
   mutate(proteasome = case_when(
-    `Bortezomib (exposed=0 vs. refractory=1)` == "Exposed" &
-      `Carfilzomib (exposed=0 vs. refractory=1)` == "Exposed"      ~ "NO",
     `Bortezomib (exposed=0 vs. refractory=1)` == "Refractory" |
-      `Carfilzomib (exposed=0 vs. refractory=1)` == "Refractory"   ~ "YES"
+      `Carfilzomib (exposed=0 vs. refractory=1)` == "Refractory"   ~ "YES",
+    TRUE      ~ "NO"
   )) %>% 
@@
     `Daratumumab (exposed=0 vs. refractory=1)` == "Refractory"      ~ "YES",
-    `Daratumumab (exposed=0 vs. refractory=1)` == "Exposed"             ~ "NO"
+    TRUE             ~ "NO"
   )) %>% 
   mutate(doubleref = case_when(
-    proteasome == "NO" | 
-      immuno == "NO"                                              ~ "NO",
     proteasome == "YES" &
-      immuno == "YES"                                         ~ "YES"
+      immuno == "YES"                                         ~ "YES",
+    TRUE                                              ~ "NO"
   )) %>% 
   mutate(tripleref = case_when(
-    proteasome == "NO" | 
-      immuno == "NO" |
-      `Daratumumab (exposed=0 vs. refractory=1)` == "Exposed"      ~ "NO",
     proteasome == "YES" &
       immuno == "YES" &
-      `Daratumumab (exposed=0 vs. refractory=1)` == "Refractory"        ~ "YES"
+      `Daratumumab (exposed=0 vs. refractory=1)` == "Refractory"        ~ "YES",
+    TRUE      ~ "NO"
   )) %>% 
   mutate(pentaref = case_when(
-    `Bortezomib (exposed=0 vs. refractory=1)` == "Exposed" | 
-      `Carfilzomib (exposed=0 vs. refractory=1)` == "Exposed" |
-      `Lenalidomide (exposed=0 vs. refractory=1)` == "Exposed" | 
-      `Pomalidomide (exposed=0 vs. refractory=1)` == "Exposed" | 
-      `Daratumumab (exposed=0 vs. refractory=1)` == "Exposed"     ~ "NO",
     `Bortezomib (exposed=0 vs. refractory=1)` == "Refractory" & 
@@
       `Pomalidomide (exposed=0 vs. refractory=1)` == "Refractory" & 
-      `Daratumumab (exposed=0 vs. refractory=1)` == "Refractory"  ~ "YES"
+      `Daratumumab (exposed=0 vs. refractory=1)` == "Refractory"  ~ "YES",
+    TRUE     ~ "NO"
+  )) %>% 
+  mutate(number_prior_lines_therapy = case_when(
+    `Number of prior lines of therapy` <= 4           ~ "4",
+    `Number of prior lines of therapy` > 4            ~ ">4"
   )) %>%
@@
     `IgG HSV1/2 apheresis` >= 0.9 &
-      `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
+      `IgG HSV1/2 apheresis` < 1.10      ~ "Indeterminate",
     `IgG HSV1/2 apheresis` >= 1.10       ~ "Positive",
@@
     `IgG HSV1/2 D90` >= 0.9 &
-      `IgG HSV1/2 D90` < 1.10      ~ "indeterminate",
+      `IgG HSV1/2 D90` < 1.10      ~ "Indeterminate",
     `IgG HSV1/2 D90` >= 1.10       ~ "Positive",
   )) %>% 
+  mutate_at(c("IgG HSV1/2 apheresis",
+              "IgG HSV1/2 D90"),
+            ~ factor(., levels = c("Positive", "Indeterminate", "Negative"))) %>%
+
   mutate_at(c("VZV IgG apheresis",
@@
               . == 0                                              ~ "Negative",
-              . == "Equivocal"                                    ~ "Negative",
-              TRUE                                                ~ as.character(.)
-            )) %>% 
-  mutate_at(c("IgG HSV1/2 apheresis",
-              "IgG HSV1/2 D90",
-              "VZV IgG apheresis",
+              . == "Equivocal"                                    ~ "Equivocal"
+            )) %>% 
+  mutate_at(c("VZV IgG apheresis",
               "VZV IgG D90 (1=pos, 0=neg)",
@@
               "CMV IgG D90 (1=pos, 0=neg)"),
-            ~ factor(., levels = c("Positive", "Negative"))) %>% 
+            ~ factor(., levels = c("Positive", "Negative", "Equivocal"))) %>% 
   mutate(across(starts_with("Pneumo"), ~ case_when(
@@
   filter(is.na(Not_evaluable_at_30days)) %>% 
-  select(
+  select(`Circulating Plasma Cells? (yes=1, no=0)`,
+         number_prior_lines_therapy,
+         `Days from last bridging to CAR-T infusion`,
+         "Lenalidomide (exposed=0 vs. refractory=1)",
+              "Bortezomib (exposed=0 vs. refractory=1)",
+              "Carfilzomib (exposed=0 vs. refractory=1)",
+              "Pomalidomide (exposed=0 vs. refractory=1)",
+              "Daratumumab (exposed=0 vs. refractory=1)",
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         cytopenia_apheresis,`cytopenia_-5d`,
+         `marrow % cellularity day +30`,
+
          Age, agecat, male_sex, Sex,
@@
   filter(is.na(Not_evaluable_at_90days)) %>% 
-  select(Age, agecat, male_sex, Sex,
+  select(`Circulating Plasma Cells? (yes=1, no=0)`,
+         number_prior_lines_therapy,
+         `Days from last bridging to CAR-T infusion`,
+         "Lenalidomide (exposed=0 vs. refractory=1)",
+              "Bortezomib (exposed=0 vs. refractory=1)",
+              "Carfilzomib (exposed=0 vs. refractory=1)",
+              "Pomalidomide (exposed=0 vs. refractory=1)",
+              "Daratumumab (exposed=0 vs. refractory=1)",
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         cytopenia_apheresis,`cytopenia_-5d`,
+         `marrow % cellularity day +90`,
+
+         Age, agecat, male_sex, Sex,
          `Extramedullary Disease? (yes=1, no=0)`, 
@@
          `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
-         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
          `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
@@
   filter(is.na(Not_evaluable_at_30days)) %>% 
-  select(CRS_gradecat,
+  select(`Total cell dose (million cells)`,
+         CRS_gradecat,
          `Day of onset of CRS relative to infusion`,
@@
   distinct(MRN, .keep_all = TRUE) %>% 
-  select(CRS_gradecat, ICANS_gradecat,
+  select(number_prior_lines_therapy,
+         `Prior auto SCT (yes=1, no=0)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
+         `Received alkylating therapy with bridging (Yes=1, No=0)`,
+         `Days from last bridging to CAR-T infusion`,
+         `Total cell dose (million cells)`,
+         "Need for G-CSF post infus (Yes, No)",
+         "CD34 stem cell boost",
+         "Need for IVIG (Yes, No)",
+
+         CRS_gradecat, ICANS_gradecat,
          `Steroid use (Yes=1, No=0)`, 
@@
 cart1 %>% 
-  distinct(MRN, .keep_all = TRUE) %>% 
-  select(CRS_gradecat, ICANS_gradecat,
+  arrange(MRN, desc(any_infection), desc(any_sevinfection)) %>%
+  distinct(MRN, .keep_all = TRUE) %>% 
+  select(number_prior_lines_therapy,
+         `Prior auto SCT (yes=1, no=0)`,
+         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
+         `Received alkylating therapy with bridging (Yes=1, No=0)`,
+         `Days from last bridging to CAR-T infusion`,
+         `Total cell dose (million cells)`,
+         "Need for G-CSF post infus (Yes, No)",
+         "CD34 stem cell boost",
+         "Need for IVIG (Yes, No)",
+
+         CRS_gradecat, ICANS_gradecat,
          `Steroid use (Yes=1, No=0)`, 
@@
 cart1 %>% 
+  arrange(MRN, desc(any_infection), desc(any_sevinfection)) %>%
   distinct(MRN, .keep_all = TRUE) %>% 
@@
 **I can probably remove the x axis title on the 4 top plots**
-```{r, fig.width=12, fig.height=12}
+```{r timeserie, fig.width=12, fig.height=12}
 cart2 <- cart1 %>% 
@@
 
-(WBC_fig | ANC_fig) /
-  (Hb_fig | ALC_fig) /
-  (Plt_fig | IgG_fig) +
+# CD4
+timepoints3 <- c(-28, 30, 90)
+CD4_fig <-
+  data.frame(timepoints3, t(round(
+    sapply(cart2[, c(
+      "CD4 apheresis",
+      "CD4 day +30",
+      "CD4 day +90"
+    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+  )))
+CD4_fig <- CD4_fig %>% 
+  ggplot(aes(x = timepoints3, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD4") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90),
+    labels = c("Apheresis", "30", "90")
+  )
+
+#CD8
+CD8_fig <-
+  data.frame(timepoints3, t(round(
+    sapply(cart2[, c(
+      "CD8 apheresis",
+      "CD8 day +30",
+      "CD8 day +90"
+    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+  )))
+CD8_fig <- CD8_fig %>% 
+  ggplot(aes(x = timepoints3, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD8") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90),
+    labels = c("Apheresis", "30", "90")
+  )
+
+#CD19
+CD19_fig <-
+  data.frame(timepoints3, t(round(
+    sapply(cart2[, c(
+      "CD19 apheresis",
+      "CD19 day +30",
+      "CD19 day +90"
+    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
+  )))
+CD19_fig <- CD19_fig %>% 
+  ggplot(aes(x = timepoints3, y = median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD19") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90),
+    labels = c("Apheresis", "30", "90")
+  )
+
+(WBC_fig | ANC_fig | CD4_fig) /
+  (Hb_fig | ALC_fig | CD8_fig) /
+  (Plt_fig | IgG_fig | CD19_fig) +
+  plot_annotation(tag_levels = "A")
+```
+<br>
+
+Aggregated median
+```{r timeserie aggreagate med}
+timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 60, 90)
+a <- cart2 %>% 
+  select(Site, "WBC apheresis",
+                 "WBC day -5 (k/ul)",
+                 "WBC day 0 (k/uL)",
+                 "WBC day +7",
+                 "WBC day +14",
+                 "WBC day +21",
+                 "WBC day +30",
+                 "WBC day +60",
+                 "WBC day +90") %>% 
+  group_by(Site) %>% 
+  summarise(across(.cols = everything(), list(mean = MedianCI) , na.rm = TRUE)) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 1), .before = 1) %>% 
+  ungroup() %>% select(-Site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(mean = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median WBC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  )
+
+b <- cart2 %>% 
+  select(Site, "ANC apheresis",
+      "ANC day -5 (k/ul)",
+      "ANC day 0 (k/uL)",
+      "ANC day +7",
+      "ANC day +14",
+      "ANC day +21",
+      "ANC day +30",
+      "ANC day +60",
+      "ANC day +90") %>% 
+  group_by(Site) %>% 
+  summarise(across(.cols = everything(), list(mean = MedianCI) , na.rm = TRUE)) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 1), .before = 1) %>% 
+  ungroup() %>% select(-Site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(mean = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median ANC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  )
+
+c <- cart2 %>% 
+  select(Site, "Hb apheresis",
+      "Hb day -5 (k/ul)",
+      "Hb day 0 (k/uL)",
+      "Hb day +7",
+      "Hb day +14",
+      "Hb day +21",
+      "Hb day +30",
+      "Hb day +60",
+      "Hb day +90") %>% 
+  group_by(Site) %>% 
+  summarise(across(.cols = everything(), list(mean = MedianCI) , na.rm = TRUE)) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 1), .before = 1) %>% 
+  ungroup() %>% select(-Site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(mean = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median Hb") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  )
+
+d <- cart2 %>% 
+  select(Site, "ALC apheresis",
+      "ALC day -5 (k/ul)",
+      "ALC day 0 (k/uL)",
+      "ALC day +7",
+      "ALC day +14",
+      "ALC day +21",
+      "ALC day +30",
+      "ALC day +60",
+      "ALC day +90") %>% 
+  group_by(Site) %>% 
+  summarise(across(.cols = everything(), list(mean = MedianCI) , na.rm = TRUE)) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 1), .before = 1) %>% 
+  ungroup() %>% select(-Site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(mean = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median ALC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  )
+
+e <- cart2 %>% 
+  select(Site, "Plt apheresis",
+      "Plt day -5 (k/ul)",
+      "Plt day 0 (k/uL)",
+      "Plt day +7",
+      "Plt day +14",
+      "Plt day +21",
+      "Plt day +30",
+      "Plt day +60",
+      "Plt day +90") %>% 
+  group_by(Site) %>% 
+  summarise(across(.cols = everything(), list(mean = MedianCI) , na.rm = TRUE)) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 1), .before = 1) %>% 
+  ungroup() %>% select(-Site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(mean = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median Plt") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  )
+
+timepoints2 <- c(-28, -5, 30, 90)
+f <- cart2 %>% 
+  select(Site, "IgG apheresis", 
+      "IgG day -5",
+      # "IgG day 0 (k/uL)", 
+      "IgG day +30", 
+      "IgG day +90") %>% 
+  group_by(Site) %>% 
+  summarise(across(.cols = everything(), list(mean = MedianCI) , na.rm = TRUE)) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 1), .before = 1) %>% 
+  ungroup() %>% select(-Site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(mean = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints2) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median Plt") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 30, 90),
+    labels = c("Apheresis", "-5", "0", "30", "90")
+  )
+
+timepoints3 <- c(-28, 30, 90)
+g <- cart2 %>% 
+  select(Site, "CD4 apheresis",
+      "CD4 day +30",
+      "CD4 day +90") %>% 
+  group_by(Site) %>% 
+  summarise(across(.cols = everything(), list(mean = MedianCI) , na.rm = TRUE)) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 1), .before = 1) %>% 
+  ungroup() %>% select(-Site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(mean = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints3) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD4") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90),
+    labels = c("Apheresis", "30", "90")
+  )
+h <- cart2 %>% 
+  select(Site, "CD8 apheresis",
+      "CD8 day +30",
+      "CD8 day +90") %>% 
+  group_by(Site) %>% 
+  summarise(across(.cols = everything(), list(mean = MedianCI) , na.rm = TRUE)) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 1), .before = 1) %>% 
+  ungroup() %>% select(-Site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(mean = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints3) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD8") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90),
+    labels = c("Apheresis", "30", "90")
+  )
+i <- cart2 %>% 
+  select(Site, "CD19 apheresis",
+      "CD19 day +30",
+      "CD19 day +90") %>% 
+  group_by(Site) %>% 
+  summarise(across(.cols = everything(), list(mean = MedianCI) , na.rm = TRUE)) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 1), .before = 1) %>% 
+  ungroup() %>% select(-Site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(mean = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints3) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD19") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90),
+    labels = c("Apheresis", "30", "90")
+  )
+
+(a | b | g) /
+  (c | d | h) /
+  (e | f | i) +
   plot_annotation(tag_levels = "A")
@@
   scale_fill_brewer(palette = "Spectral")+
-  # scale_fill_manual(values = c("#D7191C", "#FDAE61", "violet", "#ABDDA4", "#2B83BA"))+
   labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
@@
                          labels= c("Any Grade", "Grade 3+"))
+
+a %>% filter(grade == "Grade 3+") %>% 
+  ggplot(aes(x= day, 
+             y= perc, 
+             fill= name, 
+             ))+
+  geom_bar(stat = "identity",
+           position=position_dodge(width=0.9))+
+  scale_fill_brewer(palette = "Spectral")+
+  ylim(0, 100)+
+  labs(fill = NULL, x= NULL, y = "%")+
+  theme_classic()
+
+a %>%
+  ggplot(aes(x= grade, 
+             y= perc, 
+             fill= name,
+             alpha= grade
+             ))+
+  geom_bar(stat = "identity",
+           position=position_dodge(width=0.9))+
+  scale_fill_brewer(palette = "Spectral")+
+  labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
+  theme_classic()+
+  scale_alpha_discrete(range = c(0.7, 1),
+                       labels= c("Any Grade", "Grade 3+"))+
+  facet_wrap(. ~ day)
 ```
@@
 ### A)	HSV 1/2 IgG
-
-Example from prior cytopenia paper below. We can show this data however you think best
-Interpretation: ≤0.89=negative (not immune)
-                        0.90-1.09=indeterminate (can consider negative for purposes of analysis)
-                        ≥1.10=positive (immune)
-
-```{r, echo=TRUE}
-# mutate(`IgG HSV1/2 apheresis` = case_when(
-#     `IgG HSV1/2 apheresis` < 0.9         ~ "Negative",
-#     `IgG HSV1/2 apheresis` >= 0.9 &
-#       `IgG HSV1/2 apheresis` < 1.10      ~ "indeterminate",
-#     `IgG HSV1/2 apheresis` >= 1.10       ~ "Positive",
-#   ))
-```
 
@@
 # Histogram
-cart2 %>% 
-  select(PT, 
-         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
-  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
-  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-  unite(name, c("na":"me"), sep = " ") %>% 
-  filter(!is.na(value)) %>% 
-  group_by(name, day, value) %>% 
-  summarise(count=n()) %>% 
-  mutate(perc=(count/sum(count)*100)
-  ) %>% 
-  ggplot(aes(x= day, y= perc, fill= value))+
-  geom_bar(stat = "identity")+
-  labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
-       fill= "Immunity")+
-  scale_y_continuous(expand = c(0, 0))+
-  theme_classic()
-
-library(ggpattern)
-cart2 %>% 
-  select(PT, 
-         `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
-  pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
-  separate("name", into = c("na", "me", "day"), sep = " ") %>% 
-  unite(name, c("na":"me"), sep = " ") %>% 
-  filter(!is.na(value)) %>% 
-  group_by(name, day, value) %>% 
-  summarise(count=n()) %>% 
-  mutate(perc=(count/sum(count)*100)
-  ) %>% 
-  ggplot(aes(x= day, y= perc))+
-  geom_bar_pattern(aes(pattern = value),
-                   stat = "identity",
-    fill            = 'white', 
-    colour          = 'black')+
+# cart2 %>% 
+#   select(PT, 
+#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
+#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(name, c("na":"me"), sep = " ") %>% 
+#   filter(!is.na(value)) %>% 
+#   group_by(name, day, value) %>% 
+#   summarise(count=n()) %>% 
+#   mutate(perc=(count/sum(count)*100)
+#   ) %>% 
+#   ggplot(aes(x= day, y= perc, fill= value))+
 #   geom_bar(stat = "identity")+
-  labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
-       fill= "Immunity")+
-  scale_y_continuous(expand = c(0, 0))+
-  theme_classic()
+#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
+#        fill= "Immunity")+
+#   scale_y_continuous(expand = c(0, 0))+
+#   theme_classic()
+# 
+# library(ggpattern)
+# cart2 %>% 
+#   select(PT, 
+#          `IgG HSV1/2 apheresis`, `IgG HSV1/2 D90`) %>%
+#   pivot_longer(cols = `IgG HSV1/2 apheresis` : `IgG HSV1/2 D90`) %>% 
+#   separate("name", into = c("na", "me", "day"), sep = " ") %>% 
+#   unite(name, c("na":"me"), sep = " ") %>% 
+#   filter(!is.na(value)) %>% 
+#   group_by(name, day, value) %>% 
+#   summarise(count=n()) %>% 
+#   mutate(perc=(count/sum(count)*100)
+#   ) %>% 
+#   ggplot(aes(x= day, y= perc))+
+#   geom_bar_pattern(aes(pattern = value),
+#                    stat = "identity",
+#     fill            = 'white', 
+#     colour          = 'black')+
+#   # geom_bar(stat = "identity")+
+#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
+#        fill= "Immunity")+
+#   scale_y_continuous(expand = c(0, 0))+
+#   theme_classic()
 
@@
 ```{r, fig.width=15, fig.height=12}
-ghgghjg
-```
+# ghgghjg
+```

### 2022-05-26 ide_cel/Manuscript analyses.Rmd
Add figures, variables in tables + run with new data

@@
   ))) %>% 
+  mutate(`marrow % cellularity day +30` = as.numeric(`marrow % cellularity day +30`)) %>% 
+  mutate(`marrow % cellularity day +90` = as.numeric(`marrow % cellularity day +90`)) %>% 
   # defining BMI categories
@@
   mutate_at(c("Extramedullary Disease? (yes=1, no=0)",
+              "Circulating Plasma Cells? (yes=1, no=0)",
               "High Marrow Burden? (yes=1, no=0)",
@@
   )) %>% 
-
+  # Day 30 response
   mutate(`Day 30 Response (sCR, CR, VGPR, PR)` = case_when(
     str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "evaluable")   ~ NA_character_,
-    # `Day 30 Response (sCR, CR, VGPR, PR)` == "CR"	                   ~ "CR, MRD unknown",
-    # `Day 30 Response (sCR, CR, VGPR, PR)` == "CR, MRD+"	             ~ "CR, MRD+",
-    # 
-    # `Day 30 Response (sCR, CR, VGPR, PR)` == "sCR, MRD+"           	 ~ "sCR, MRD+",
-    # `Day 30 Response (sCR, CR, VGPR, PR)` %in% c(
-    #   "sCR MRD-", "sCR, MRD-")                                                         ~ "sCR, MRD-",
-    # 
-    # `Day 30 Response (sCR, CR, VGPR, PR)` %in% c(
-    #   "sCR", "sCR (flow neg, no clonoSEQ ID)", "sCR MRD - by flow/no clonoSEQ)",
-    #   "sCR, MRD- by flow/no clonoSEQ)")                                                ~ "sCR, MRD unknown",
-
     TRUE           ~ `Day 30 Response (sCR, CR, VGPR, PR)`
@@
   )) %>% 
-
   mutate_at(c("Day 30 MRD (Pos=1, Neg=0)",
@@
   )) %>% 
-
+  # Day 90 response
   mutate(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` = case_when(
-    # str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "VGPR")        ~ "VGPR",
-    # str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "PR")          ~ "PR",
     str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "evaluable")   ~ NA_character_,
-
-    # `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
-    #   "CR", "CR (no clonoSEQ/MRD as no marrow)")                                      ~ "CR, MRD unknown",
-    # 
-    # `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
-    #   "sCR (clonoSEQ pending, flow neg)", 
-    #   "sCR (no clonoSEQ for MRD, flow suspicious for MRD)",
-    #   "sCR (no clonoSEQ, flow neg)")                                                  ~ "sCR, MRD unknown",
-    # 
-    # `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` %in% c(
-    #   "sCR, MRD - (by flow+)", "sCR, MRD-	12 (24%)")                                  ~ "sCR, MRD-",
-    # 
-    # `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)` == "sCR, MRD+"	            ~	"sCR, MRD+",
-
     TRUE           ~ `Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`
@@
   )) %>% 
+  # Best response
+  mutate(ORR_as_best_response = case_when(
+    ORR_30days == "ORR" |
+    ORR_90days == "ORR"                       ~ "ORR"
+  )) %>% 
   mutate(best_response = case_when(
@@
   )) %>%
+
   mutate(MRDneg_in_best_response = case_when(
-    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD-") |
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD-")        ~ "Yes",
-    str_detect(`Day 90 response (sCR, CR, VGPR, PR and MRD+ vs MRD-)`, "MRD") |
-    str_detect(`Day 30 Response (sCR, CR, VGPR, PR)`, "MRD")         ~ "No",
+    `Day 30 MRD (Pos=1, Neg=0)` ==  "Negative" |
+      `Day 90 MRD (Pos=1, Neg=0)` ==  "Negative"                     ~ "Negative",
+    `Day 30 MRD (Pos=1, Neg=0)` ==  "Positive" |
+      `Day 90 MRD (Pos=1, Neg=0)` ==  "Positive"                     ~ "Positive",
     TRUE                             ~ NA_character_
@@
 }
-
-# # CrCl
-# table(cart$`Baseline CrCl`)
-# cart$crcl[cart$`Baseline CrCl` == ">70" | cart$`Baseline CrCl` == "60.8" | cart$`Baseline CrCl` == "62" | cart$`Baseline CrCl` == "67"] <- ">60"
-# cart$crcl[cart$`Baseline CrCl` == "25" | cart$`Baseline CrCl` == "27" | cart$`Baseline CrCl` == "34" | cart$`Baseline CrCl` == "41" | cart$`Baseline CrCl` == "43" | cart$`Baseline CrCl` == "50" | cart$`Baseline CrCl` == "54" | cart$`Baseline CrCl` == "55"] <- "≤60"
-# table(cart$crcl)
-# # CRS
-# table(cart$`Max CRS grade (0-5)`)
-# as.factor(cart$`Max CRS grade (0-5)`)
-# table(cart$`Duration of CRS (days)`)
-# table(cart$`Duration of ICANS (days)`)
-# # steroid use
-# table(cart$`Steroid use(Yes, No)`)
-# 
-# 
-# 
-# # dose reduction
-# cart$`Fludarabine Dose Reduction`[cart$`Fludarabine Dose Reduction` == "YES (HD)"] <- "YES"
-# table(cart$`Fludarabine Dose Reduction`)
-# 
-# # RSS
-# table(cart$`R-ISS at CAR-T Infusion`)
-# cart$`R-ISS at CAR-T Infusion`[cart$`R-ISS at CAR-T Infusion` == "R-ISS  II"] <- "R-ISS II"
-
-# day 30 + MRD for figure
-#table(tct$day30_response_revised, tct$MRD_status, useNA= "ifany")
-#table(tct$day30_response_revised, tct$day30_response, useNA= "ifany")
-#tct$ORR_MRD <- case_when(#tct$day30_response_revised== "SD" ~ "SD",
-                         #tct$day30_response_revised== "PD" ~ "PD",
-                         #tct$day30_response_revised== "MR" ~ "MR",
-#                         tct$day30_response_revised== "PR" ~ "PR",
-                         #tct$day30_response_revised== "PR" & tct$MRD_status== "Positive" ~ "PR and MRD-Positive",
-                         #tct$day30_response_revised== "PR" & is.na(tct$MRD_status) ~ "PR and MRD unknown",
-#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Negative" ~ "sCR and MRD-Negative",
-#                         tct$day30_response_revised== "sCR" & tct$MRD_status== "Positive" ~ "sCR and MRD-Positive")
-#table(tct$ORR_MRD)
 ```
@@
                          `Extramedullary Disease? (yes=1, no=0)` = "Extramedullary disease", 
+                         `Circulating Plasma Cells? (yes=1, no=0)` = "Circulating Plasma Cells?",
                          `High Marrow Burden? (yes=1, no=0)` = "High marrow burden (≥50%)",
@@
 ## Table 2. Clinical outcomes
-**best response**
 ```{r}
@@
   distinct(MRN, .keep_all = TRUE) %>% 
-  select(best_response) %>% 
+  select(best_response, MRDneg_in_best_response) %>% 
   tbl_summary(#type = list(c(`Day 90 MRD (Pos=1, Neg=0)`) ~ "categorical"),
@@
 ## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30
-**Make sure that if one of wbc, anc, hb or plt is NA then cytopenia should be NA**
 ```{r}
@@
          `Extramedullary Disease? (yes=1, no=0)`, 
-         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, cyto, 
+         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, 
+         `R-ISS at CAR-T Infusion`, cyto, 
          `Bridging Therapy (Yes=1, No=0)`,
@@
               type = list(
-    `Extramedullary Disease? (yes=1, no=0)` ~ "categorical",
-    cyto ~ "categorical",
-    `Bridging Therapy (Yes=1, No=0)` ~ "categorical",
-    `Received alkylating therapy with bridging (Yes=1, No=0)` ~ "categorical",
-    `Prior auto SCT (yes=1, no=0)` ~ "categorical",
-    immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
-    doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
-    `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)` ~"categorical"),
+                c(`Extramedullary Disease? (yes=1, no=0)`,
+                  `Circulating Plasma Cells? (yes=1, no=0)`,
+                  cytopenia_apheresis,`cytopenia_-5d`,
+                  cyto,
+                  `Bridging Therapy (Yes=1, No=0)`,
+                  `Received alkylating therapy with bridging (Yes=1, No=0)`,
+                  `Prior auto SCT (yes=1, no=0)`,
+                  immuno, proteasome, dara,
+                  doubleref, tripleref, pentaref,
+                `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`)
+                ~"categorical",
+                `marrow % cellularity day +30` ~ "continuous"),
 
@@
          `marrow % cellularity day +90`,
-
          Age, agecat, male_sex, Sex,
@@
               type = list(
-    `Extramedullary Disease? (yes=1, no=0)` ~ "categorical",
-    cyto ~ "categorical",
-    `Bridging Therapy (Yes=1, No=0)` ~ "categorical",
-    `Received alkylating therapy with bridging (Yes=1, No=0)` ~ "categorical",
-    `Prior auto SCT (yes=1, no=0)` ~ "categorical",
-    immuno ~ "categorical", proteasome ~ "categorical", dara ~ "categorical",
-    doubleref ~ "categorical", tripleref ~ "categorical", pentaref ~ "categorical",
-    `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)` ~"categorical"),
+                c(`Extramedullary Disease? (yes=1, no=0)`,
+                  `Circulating Plasma Cells? (yes=1, no=0)`,
+                  cytopenia_apheresis,`cytopenia_-5d`,
+                  cyto,
+                  `Bridging Therapy (Yes=1, No=0)`,
+                  `Received alkylating therapy with bridging (Yes=1, No=0)`,
+                  `Prior auto SCT (yes=1, no=0)`,
+                  immuno, proteasome, dara,
+                  doubleref, tripleref, pentaref,
+                  `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`)
+                ~ "categorical",
+                `marrow % cellularity day +90` ~ "continuous"),
 
@@
          `CD56 apheresis`, `CD19 apheresis`, 
+         `IgG day +90`, `IgA day +90`, `IgM day +90`,
+         `WBC day +90`, `ANC day +90`,
+         `Eos day +90`, `Monos day +90`,
          `CD3 day +90`, `CD4 day +90`, `CD8 day +90`,
@@
          any_infection) %>% 
-
   tbl_summary(by = any_infection,
-
               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
@@
   select(`IgG day -5`, `IgA day -5`, `IgM day -5`,
+         `WBC day -5 (k/ul)`, `ANC day -5 (k/ul)`,
+         `Eos day -5 (k/ul)`, `Monos day -5 (k/ul)`,
          `WBC apheresis`, `ANC apheresis`,
@@
          any_sevinfection) %>% 
-
   tbl_summary(by = any_sevinfection,
-
               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
@@
   modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
+```
+
+## Table SX. Immunoglobulin levels excluding patients with that type of myeloma
+```{r}
+cart1 %>% 
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(`Myeloma sub-type` != "IgG" | is.na(`Myeloma sub-type`)) %>% 
+  select(`IgG day -5`, `IgG day +30`,
+         `IgG day +90`, any_infection) %>% 
+  tbl_summary(by = any_infection,
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  add_p() %>% bold_labels() %>% add_stat_label() %>% 
+  add_overall() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any infection**")
+
+cart1 %>% 
+  arrange(MRN, desc(any_infection), desc(any_sevinfection)) %>%
+  distinct(MRN, .keep_all = TRUE) %>% 
+  filter(`Myeloma sub-type` != "IgG" | is.na(`Myeloma sub-type`)) %>% 
+  select(`IgG day -5`, `IgG day +30`,
+         `IgG day +90`, any_sevinfection) %>% 
+  tbl_summary(by = any_sevinfection,
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  add_p() %>% bold_labels() %>% add_stat_label() %>% 
   modify_footnote(update = everything() ~ NA) %>%
@@
 ## Figure 3. Cellular and humoral immune reconstitution after ide-cel
-**I can probably remove the x axis title on the 4 top plots**
 ```{r timeserie, fig.width=12, fig.height=12}
@@
   )))
+ANC_fig
 ANC_fig <- ANC_fig %>% 
@@
 
-# IgG
-#table(cart2$`IgG day +90`)
-#table(cart2$`IgG day +180`)
-# cart2$`IgG day +90`[cart2$`IgG day +90` == "<109"] <- 77
-# cart2$`IgG day +30`[cart2$`IgG day +30` == "<109"] <- 77
-# cart2$`IgG day -5`[cart2$`IgG day -5` == "<109"] <- 77
-# cart2$`IgG apheresis`[cart2$`IgG apheresis` == "<109"] <- 77
-# 
-# cart2$`IgG day +90` <- as.numeric(cart2$`IgG day +90`)
-# cart2$`IgG day +30` <- as.numeric(cart2$`IgG day +30`)
-# cart2$`IgG day -5` <- as.numeric(cart2$`IgG day -5`)
-# cart2$`IgG apheresis` <- as.numeric(cart2$`IgG apheresis`)
 timepoints2 <- c(-28, -5, 30, 90)
@@
 Aggregated median
-```{r timeserie aggreagate med}
+```{r timeserie aggreagate med, fig.width=12, fig.height=12}
 timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 60, 90)
-a <- cart2 %>% 
+WBC_agg <- cart2 %>% 
   select(Site, "WBC apheresis",
@@
 
-b <- cart2 %>% 
+b1 <- cart2 %>% 
   select(Site, "ANC apheresis",
@@
   pivot_wider(names_from = type, values_from = value) %>% 
-  mutate(timepoints = timepoints) %>% 
+  mutate(timepoints = timepoints)
+ANC_agg <- b1 %>% 
   ggplot(aes(x = timepoints, y = Median)) + 
@@
   ) 
-
-c <- cart2 %>% 
+b1
+
+Hb_agg <- cart2 %>% 
   select(Site, "Hb apheresis",
@@
 
-d <- cart2 %>% 
+ALC_agg <- cart2 %>% 
   select(Site, "ALC apheresis",
@@
 
-e <- cart2 %>% 
+Plt_agg <- cart2 %>% 
   select(Site, "Plt apheresis",
@@
 timepoints2 <- c(-28, -5, 30, 90)
-f <- cart2 %>% 
+IgG_agg <- cart2 %>% 
   select(Site, "IgG apheresis", 
@@
 timepoints3 <- c(-28, 30, 90)
-g <- cart2 %>% 
+CD4_fig <- cart2 %>% 
   select(Site, "CD4 apheresis",
@@
   )
-h <- cart2 %>% 
+CD8_fig <- cart2 %>% 
   select(Site, "CD8 apheresis",
@@
   )
-i <- cart2 %>% 
+CD19_fig <- cart2 %>% 
   select(Site, "CD19 apheresis",
@@
 
-(a | b | g) /
-  (c | d | h) /
-  (e | f | i) +
+(WBC_agg | ANC_agg | CD4_fig) /
+  (Hb_agg | ALC_agg | CD8_fig) /
+  (Plt_agg | IgG_agg | CD19_fig) +
   plot_annotation(tag_levels = "A")
@@
   ) %>% 
-  # mutate(igg_vzv_change = case_when(
-  #   igg_vzv_change == 1        ~  "Acquired immunity",
-  #   igg_vzv_change == 0.25        ~  "Positive overtime",
-  #   igg_vzv_change == -0.25        ~  "Negative overtime",
-  #   igg_vzv_change == -1        ~  "Lost immunity"
-  # )) %>% 
   drop_na() %>% 
@@
   ) %>% 
-  # mutate(igg_cmv_change = case_when(
-  #   igg_cmv_change == 1        ~  "Acquired immunity",
-  #   igg_cmv_change == 0.25        ~  "Positive overtime",
-  #   igg_cmv_change == -0.25        ~  "Negative overtime",
-  #   igg_cmv_change == -1        ~  "Lost immunity"
-  # )) %>% 
   drop_na() %>% 
@@
   geom_stratum()+
+  geom_segment(aes(x=1.17, y=12, xend=1.83, yend=12), 
+               color= "white", size=0.3)+
   geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
@@
 
-##########################
-
 ```{r, fig.width=15, fig.height=12}

### 2022-05-27 ide_cel/Manuscript analyses.Rmd
Add var in tables

@@
   select(`Circulating Plasma Cells? (yes=1, no=0)`,
+         `Number of prior lines of therapy`,
          number_prior_lines_therapy,
@@
          immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-         cytopenia_apheresis,`cytopenia_-5d`,
          `marrow % cellularity day +30`,
@@
          `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
-         cytopenia_apheresis, `cytopenia_-5d`, gr3_cytopenia_apheresis, `gr3_cytopenia_-5d`,
+         cytopenia_apheresis, Neutropenia_apheresis,
+         Anemia_apheresis,Thrombocytopenia_apheresis,
+         `cytopenia_-5d`, `Neutropenia_-5d`,
+         `Anemia_-5d`, `Thrombocytopenia_-5d`,
+         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
          `gr3_cytopenia_30d`) %>% 
@@
                   doubleref, tripleref, pentaref,
+                  cytopenia_apheresis, Neutropenia_apheresis,
+                  Anemia_apheresis,Thrombocytopenia_apheresis,
+                  `cytopenia_-5d`, `Neutropenia_-5d`,
+                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
+                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                   `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`)
                 ~"categorical",
-                `marrow % cellularity day +30` ~ "continuous"),
+                c(`Number of prior lines of therapy`, `marrow % cellularity day +30`)
+                ~ "continuous"),
 
@@
          immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-         cytopenia_apheresis,`cytopenia_-5d`,
          `marrow % cellularity day +90`,
@@
          `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
+         cytopenia_apheresis, Neutropenia_apheresis,
+         Anemia_apheresis,Thrombocytopenia_apheresis,
+         `cytopenia_-5d`, `Neutropenia_-5d`,
+         `Anemia_-5d`, `Thrombocytopenia_-5d`,
+         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
          `gr3_cytopenia_90d`) %>% 
@@
                   doubleref, tripleref, pentaref,
+                  cytopenia_apheresis, Neutropenia_apheresis,
+                  Anemia_apheresis,Thrombocytopenia_apheresis,
+                  `cytopenia_-5d`, `Neutropenia_-5d`,
+                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
+                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                   `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`)
                 ~ "categorical",
-                `marrow % cellularity day +90` ~ "continuous"),
-
+                c(`Number of prior lines of therapy`, `marrow % cellularity day +90`)
+                ~ "continuous"),
               statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 

### 2022-06-01 ide_cel/Manuscript analyses.Rmd
Update

@@
   select(number_prior_lines_therapy,
+         `Number of prior lines of therapy`,
          `Prior auto SCT (yes=1, no=0)`,
@@
   tbl_summary(by=any_infection, 
-              type = list(all_dichotomous() ~ "categorical")) %>%
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              type = list(all_dichotomous() ~ "categorical", 
+                          `Number of prior lines of therapy` ~ "continuous")) %>%
   add_p() %>%  bold_labels() %>% add_stat_label() %>% 
@@
   tbl_summary(by=any_sevinfection, 
-              type = list(all_dichotomous() ~ "categorical")) %>%
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              type = list(all_dichotomous() ~ "categorical", 
+                          `Number of prior lines of therapy` ~ "continuous")) %>%
   add_p() %>%  bold_labels() %>% add_stat_label() %>% 

### 2022-06-02 RWE/RWE Manuscript analyses_.Rmd
Update

@@
 ```{r load}
-# path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias", "MM_CARTcell_cytopenia")
-# path <- getwd()
 MM_cart <-
-  readxl::read_xlsx(
-    "/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/RWE/FINAL 4.13.22 ASCO 2022 Myeloma CAR-T SOC Outcomes Spreadsheet.xlsx",
+  readxl::read_xlsx(paste0(here(), "/RWE/FINAL 4.13.22 ASCO 2022 Myeloma CAR-T SOC Outcomes Spreadsheet.xlsx"),
                     skip = 1, n_max = 198

### 2022-07-07 ide_cel/Manuscript analyses.Rmd
Add multivariate analysis and forest plot

@@
 **We want grade 3 only right?**
-```{r}
+```{r, fig.width=12, fig.height=7}
 # cart2 %>% 
@@
                          labels= c("Any Grade", "Grade 3+"))
+####################################################################################################
+# a %>% filter(grade == "Grade 3+") %>% 
+#   ggplot(aes(x= day, 
+#              y= perc, 
+#              fill= name, 
+#              ))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))+
+#   geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 4.5,
+#             position = position_dodge(width=0.9)
+#             )+
+#   
+#   scale_fill_brewer(palette = "Spectral")+
+#   ylim(0, 100)+
+#   labs(fill = NULL, x= NULL, y = "%")+
+#   theme_classic(base_size = 14)
 
@@
            position=position_dodge(width=0.9))+
+  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 5,
+            position = position_dodge(width=0.9), vjust=-1.5
+            )+
+
   scale_fill_brewer(palette = "Spectral")+
@@
   labs(fill = NULL, x= NULL, y = "%")+
-  theme_classic()
-
-a %>%
-  ggplot(aes(x= grade, 
-             y= perc, 
-             fill= name,
-             alpha= grade
-             ))+
-  geom_bar(stat = "identity",
-           position=position_dodge(width=0.9))+
-  scale_fill_brewer(palette = "Spectral")+
-  labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
-  theme_classic()+
-  scale_alpha_discrete(range = c(0.7, 1),
-                       labels= c("Any Grade", "Grade 3+"))+
-  facet_wrap(. ~ day)
+  theme_classic(base_size = 14)+
+  theme(legend.position="bottom")
+
+# a %>% filter(grade == "Grade 3+") %>% 
+#   ggplot(aes(x= day, 
+#              y= perc, 
+#              fill= name, 
+#              ))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))+
+#   geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 4.5,
+#             position = position_dodge(width=0.9), fontface='bold'
+#             )+
+#   
+#   scale_fill_brewer(palette = "Spectral")+
+#   ylim(0, 100)+
+#   labs(fill = NULL, x= NULL, y = "%")+
+#   theme_classic(base_size = 14)
+
+# a %>% filter(grade == "Grade 3+") %>% 
+#   ggplot(aes(x= day, 
+#              y= perc, 
+#              fill= name, 
+#              ))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))+
+#   geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 4.5,
+#             position = position_dodge(width=0.9), color= "grey27"
+#             )+
+#   
+#   scale_fill_brewer(palette = "Spectral")+
+#   ylim(0, 100)+
+#   labs(fill = NULL, x= NULL, y = "%")+
+#   theme_classic(base_size = 14)
+
+# a %>% filter(grade == "Grade 3+") %>% 
+#   ggplot(aes(x= day, 
+#              y= perc, 
+#              fill= name, 
+#              ))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))+
+#   geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 5,
+#             position = position_dodge(width=0.9)
+#             )+
+#   
+#   scale_fill_brewer(palette = "Spectral")+
+#   ylim(0, 100)+
+#   labs(fill = NULL, x= NULL, y = "%")+
+#   theme_classic(base_size = 14)+
+#   theme(legend.position="bottom")
+# a %>%
+#   ggplot(aes(x= grade, 
+#              y= perc, 
+#              fill= name,
+#              alpha= grade
+#              ))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))+
+#   scale_fill_brewer(palette = "Spectral")+
+#   labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
+#   theme_classic()+
+#   scale_alpha_discrete(range = c(0.7, 1),
+#                        labels= c("Any Grade", "Grade 3+"))+
+#   facet_wrap(. ~ day)
 ```
@@
 
+## MVA
+```{r}
+cart3 <- cart2 %>% 
+  filter(is.na(Not_evaluable_at_90days)) %>%
+  mutate(gr3_cytopenia_30d = case_when(
+    gr3_cytopenia_30d == "NO"    ~ 0,
+    gr3_cytopenia_30d == "YES"   ~ 1
+  )) %>% 
+  mutate(gr3_cytopenia_90d = case_when(
+    gr3_cytopenia_90d == "NO"    ~ 0,
+    gr3_cytopenia_90d == "YES"   ~ 1
+  )) %>% 
+  mutate(
+         CRS_grade2 = case_when(
+           `Max CRS grade (0-5)` < 2                              ~ "No CRS or Grade < 2",
+           `Max CRS grade (0-5)` >= 2                             ~ "Grade ≥2"),
+         CRS_grade2 = factor(CRS_grade2, levels = c("No CRS or Grade < 2", "Grade ≥2"))
+  )
+
+# glm(gr3_cytopenia_30d ~ `High Marrow Burden? (yes=1, no=0)` + `gr3_cytopenia_-5d` + CRS_grade2 + `Steroid use (Yes=1, No=0)` + `Number of prior lines of therapy`,
+#     data = cart3,
+#     family = "binomial") %>%
+#   tbl_regression(exponentiate = TRUE, 
+#                  intercept = TRUE) %>%
+#   add_nevent(location = "level") %>% add_n(location = "level") %>%
+#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 30**") %>%
+#   bold_p(t = .05) 
+# 
+# glm(gr3_cytopenia_90d ~ `High Marrow Burden? (yes=1, no=0)` + `gr3_cytopenia_-5d` + CRS_grade2 + `Steroid use (Yes=1, No=0)` + `Number of prior lines of therapy`,
+#     data = cart3,
+#     family = "binomial") %>%
+#   tbl_regression(exponentiate = TRUE, 
+#                  intercept = TRUE) %>%
+#   add_nevent(location = "level") %>% add_n(location = "level") %>%
+#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
+#   bold_p(t = .05) 
+# 
+# glm(gr3_cytopenia_30d ~ `High Marrow Burden? (yes=1, no=0)` + CRS_grade2 + `Steroid use (Yes=1, No=0)` + `Number of prior lines of therapy`,
+#     data = cart3,
+#     family = "binomial") %>%
+#   tbl_regression(exponentiate = TRUE, 
+#                  intercept = TRUE) %>%
+#   add_nevent(location = "level") %>% add_n(location = "level") %>%
+#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 30**") %>%
+#   bold_p(t = .05)
+
+glm(gr3_cytopenia_90d ~ `High Marrow Burden? (yes=1, no=0)` + `gr3_cytopenia_-5d` + CRS_grade2 + `Steroid use (Yes=1, No=0)` + `Number of prior lines of therapy`,
+    data = cart3,
+    family = "binomial") %>%
+  tbl_regression(exponentiate = TRUE, 
+                 intercept = TRUE) %>%
+  add_nevent(location = "level") %>% add_n(location = "level") %>%
+  modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
+  bold_p(t = .05) 
+```
+
+```{r}
+forest_p <- 
+  glm(gr3_cytopenia_90d ~ `High Marrow Burden? (yes=1, no=0)` + `gr3_cytopenia_-5d` + CRS_grade2 + `Steroid use (Yes=1, No=0)` + `Number of prior lines of therapy`,
+    data = cart3,
+    family = "binomial") %>%
+  tbl_regression(exponentiate = TRUE) %>%
+  as_tibble() %>% 
+  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
+  fill(OR, `95% CI`, .direction = "up") %>% 
+  filter(!str_detect(Characteristic, "YES|NO|CRS_grade2|No CRS")) %>% 
+  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
+  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
+  mutate(name= c("High marrow burden (≥50%)",
+                 "Grade ≥ 3 Cytopenia at Day -5",
+                 "Grade ≥ 2 CRS",
+                 "Steroid use",
+                 "Number of prior lines of therapy"
+                 ))
+
+ggplot(data=forest_p, aes(y=name, x=OR, xmin=lower, xmax=upper)) +
+  geom_point() + 
+  geom_errorbarh(height=.1) +
+  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
+  theme_classic()+
+  scale_x_log10(breaks = c(0, 0.25, 0.5, 1, 2.5, 5, 10, 40))+
+  labs(y="")
+```
+
 ```{r, fig.width=15, fig.height=12}

### 2022-11-10 RWE/RWE-Manuscript-analyses_UPDATES.Rmd
New analysis Rmd

---
title: "Real World Manuscript Analyses - UPDATED"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type= "text/css">

. figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

```{r library}
#library(here)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(gtsummary)
library(labelled)
library(DescTools)
library(patchwork)
library(ggbreak)
library(survival)
library(survminer)
```

```{r load}
MM_cart <-
  readxl::read_xlsx("/Volumes/Peres_Research/Myeloma/Cytopenias/R code/MM_CARTcell_cytopenia/RWE/FINAL 4.13.22 ASCO 2022 Myeloma CAR-T SOC Outcomes Spreadsheet.xlsx",
                    skip = 1, n_max = 198
                    ) %>% 
  rename(patient_id = `PT Identifier (DO NOT USE PHI)`)
survdata <- read_csv("/Volumes/Peres_Research/Myeloma/Cytopenias/R code/MM_CARTcell_cytopenia/RWE/Survival_Responses_07122022_v3.csv")
survdata$patient_id <- survdata$`PT Identifier (DO NOT USE PHI)`
kumc_bridging <- read_csv("/Volumes/Peres_Research/Myeloma/Cytopenias/R code/MM_CARTcell_cytopenia/RWE/Kansas_bridging.csv")
consort <- read_csv("/Volumes/Peres_Research/Myeloma/ASH abstracts/Consortium data_07122022.csv")
consort <- consort %>% select(`PT Identifier (DO NOT USE PHI)`, `Date of Death`, `Date of PD`, `Date of Last Contact`, `Response to bridging therapy (CR, VGPR, PR, SD, PR)`, `Cause of death (myeloma, toxicitiy, unrelated)`)
consortall <- merge(consort, kumc_bridging, by="PT Identifier (DO NOT USE PHI)", all.x=TRUE)
consortall <- consortall %>% mutate(response_bridging2 = case_when(
    !is.na(response_bridging) ~ response_bridging,
    is.na(response_bridging) ~ `Response to bridging therapy (CR, VGPR, PR, SD, PR)`
)) %>% mutate(datedeath = `Date of Death`) %>%
  mutate(datePD = `Date of PD`) %>%
  mutate(datelastcontact = `Date of Last Contact`) %>%
  mutate(causedeath = `Cause of death (myeloma, toxicitiy, unrelated)`) %>%
  mutate(`PT Identifier (DO NOT USE PHI)` = ifelse(`PT Identifier (DO NOT USE PHI)`=="LCI-10= LCI-9 (2nd attempt)", "LCI-9 (LCI-10)", `PT Identifier (DO NOT USE PHI)`)) %>% mutate(patient_id = `PT Identifier (DO NOT USE PHI)`)
consortall <- consortall %>% select(patient_id, datedeath, datePD, datelastcontact, response_bridging2, causedeath)
alldata <- merge(MM_cart, survdata, by="patient_id", all.x=TRUE)
alldata <- merge(alldata, consortall, by="patient_id", all.x=TRUE)
rm("consort", "consortall", "kumc_bridging")
```

```{r data cleaning}
# per Doris e-mail communication on 5/6/22, remove Utah8 from the very beginning - should not be in any analyses
alldata <- alldata %>% filter(patient_id != "Utah8")
cart0 <- alldata
cart0$pfs_time = as.Date(cart0$pfs_time, format = "%m/%d/%y")  
cart0$os_time = as.Date(cart0$os_time, format = "%m/%d/%y")  
cart0$`Total Bilirubin >1.5ULN (Yes, No)` = ifelse(cart0$`Total Bilirubin >1.5ULN (Yes, No)` == "No", "NO", cart0$`Total Bilirubin >1.5ULN (Yes, No)`)
cart0 <- cart0 %>% 
  mutate(`ANC Day 30` = case_when(
    `ANC Day 30` == "ND" ~ 0,
    is.na(`ANC Day 30`) ~ NA_real_,
    TRUE ~ as.numeric(`ANC Day 30`))) %>%
      mutate(`ANC Day 90` = case_when(
       `ANC Day 90`== "NA" ~ NA_real_,
       is.na(`ANC Day 90`) ~ NA_real_,
        TRUE ~ as.numeric(`ANC Day 90`)
      )) %>%
  mutate(`HgB Day 90` = case_when(
    `HgB Day 90`=="NA" ~ NA_real_,
    is.na(`HgB Day 90`) ~ NA_real_,
    TRUE ~ as.numeric(`HgB Day 90`)
  )) %>%
  mutate(`Platelets Day 90` = case_when(
    `Platelets Day 90`=="NA" ~ NA_real_,
    is.na(`Platelets Day 90`) ~ NA_real_,
    TRUE ~ as.numeric(`Platelets Day 90`)
  )) %>% 
  mutate(`ANC Day 7` = case_when(
    `ANC Day 7` > 100 ~ `ANC Day 7`/1000,
    TRUE ~ `ANC Day 7`
  )) %>%
  mutate(`ANC Day 30` = case_when(
    `ANC Day 30` > 100 ~ `ANC Day 30`/1000,
    TRUE ~ `ANC Day 30`
  )) %>%
  mutate(`ANC Day 60` = case_when(
    `ANC Day 60` > 100 ~ `ANC Day 60`/1000,
    TRUE ~ `ANC Day 60`
  )) %>%
  mutate(`ANC Day 90` = case_when(
    `ANC Day 90` > 100 ~ `ANC Day 90`/1000,
    TRUE ~ `ANC Day 90`
  )) %>%
  mutate(`Need for GCSF` = str_to_upper(`Need for GCSF`))  %>% 
  # Keep second infusion date for patients who had failure
  separate(`Date of Apheresis (or # of days from apheresis to LD)`, 
           into= c("first_date_of_apheresis", "date_of_apheresis"), sep = ", 2nd-|; 2nd - ", remove = FALSE) %>% 
  mutate(first_date_of_apheresis = str_remove(first_date_of_apheresis, "1st - |1st-"),
         first_date_of_apheresis = as.Date(as.numeric(first_date_of_apheresis),
                                             origin = "1899-12-30"),
         date_of_apheresis = parse_date_time(date_of_apheresis, "mdy"),
         date_of_apheresis = coalesce(date_of_apheresis, first_date_of_apheresis)
         ) %>% 
  select(-c(`Date of Apheresis (or # of days from apheresis to LD)`, first_date_of_apheresis)) %>%

  mutate(across(c(`Day of Max CRS (relative to infusion)`,
                  `Day of Max ICANS (relative to infusion)`), ~ str_remove(., "Day +"))
         ) %>%

###########################################################################
###########################################################################
###########################################################################
###########################################################################
###########################################################################
###########################################################################

# censored days > 100 to 100
  mutate(across(c(`Day of Max CRS (relative to infusion)`,
                  `Day of Max ICANS (relative to infusion)`), ~ case_when(
    . > 100                                                       ~ 100,
    TRUE                                                          ~ as.numeric(.)
  ))) %>% 
  mutate(`Length of Hospital Stay (Total Days including Readmission)` =
           as.numeric(`Length of Hospital Stay (Total Days including Readmission)`)) %>% 
  # defining BMI categories
  # mutate(bmicat = case_when(
  #   `BMI at apheresis` < 25             ~ "< 25 kg/m2",
  #   `BMI at apheresis` >= 25 & 
  #     cart$`BMI at apheresis` < 30      ~ "25 to < 30 kg/m2",
  #   `BMI at apheresis` >= 30            ~ "≥ 30 kg/m2"
  # ),
  # bmicat = factor(bmicat, levels = c("< 25 kg/m2", "25 to < 30 kg/m2", "≥ 30 kg/m2"))
  # ) %>% 
  # mutate(bmicat2 = case_when(
  #   `BMI at apheresis` < 25             ~ "< 25 kg/m2",
  #   `BMI at apheresis` >= 25            ~ "≥ 25 kg/m2"
  # ),
  # bmicat2 = factor(bmicat2, levels = c("< 25 kg/m2", "≥ 25 kg/m2"))
  # ) %>% 
  # age categories
  mutate(agecat = case_when(
    Age < 65                            ~ "< 65 years",
    Age >= 65                           ~ "≥ 65 years"
  ),
  agecat = factor(agecat, levels = c("< 65 years", "≥ 65 years"))
  ) %>% 
  mutate(Sex = case_when(
    str_detect(Sex, "F")                                          ~ "F",
    str_detect(Sex, "M")                                          ~ "M"
  )) %>% 
  mutate(male_sex = case_when(
    Sex == "M"                                                    ~ 1,
    TRUE                                                          ~ 0
  )) %>% 
  # ECOG
  mutate(`ECOG at LD` = case_when(
    `ECOG at LD` == 0 |
      `ECOG at LD` == 1                                           ~ "0-1",
    `ECOG at LD` %in% c(2:4)                                      ~ "2-4",
    TRUE                                                          ~ NA_character_
  )) %>% 
  # cytogenetics
  mutate(cytogenetics = case_when(
    `Deletion 17p prior to CAR-T infusion (yes, no)` == "YES" | 
      `t(4:14) prior to CAR-T infusion (yes, no)` == "YES" | 
      `t(14:16) prior to CAR-T infusion (yes, no)` == "YES"   ~ "YES",
    `Deletion 17p prior to CAR-T infusion (yes, no)` == "NO" &
      `t(4:14) prior to CAR-T infusion (yes, no)` == "NO" &
      `t(14:16) prior to CAR-T infusion (yes, no)` == "NO"    ~ "NO",
    TRUE                                                      ~ NA_character_
  )) %>% 
  # refractory status
  mutate_at(c("Lenalidomide (exposed vs. refractory)",
              "Bortezomib (exposed vs. refractory)",
              "Carfilzomib (exposed vs. refractory)",
              "Pomalidomide (exposed vs. refractory)",
              "Daratumumab (exposed vs. refractory)"),
            ~ case_when(
              is.na(.)                                            ~ "Not Refractory",
              TRUE                                                ~ as.character(.)
            )) %>%
  mutate(immuno = case_when(
    `Lenalidomide (exposed vs. refractory)` == "Refractory" |
      `Pomalidomide (exposed vs. refractory)` == "Refractory"     ~ "YES",
    TRUE        ~ "NO"
  )) %>% 
  mutate(proteasome = case_when(
    `Bortezomib (exposed vs. refractory)` == "Refractory" |
      `Carfilzomib (exposed vs. refractory)` == "Refractory"   ~ "YES",
    TRUE      ~ "NO"
  )) %>% 
  mutate(dara = case_when(
    `Daratumumab (exposed vs. refractory)` == "Refractory"      ~ "YES",
    TRUE             ~ "NO"
  )) %>% 
  mutate(doubleref = case_when(
    proteasome == "YES" &
      immuno == "YES"                                         ~ "YES",
    TRUE                                              ~ "NO"
  )) %>% 
  mutate(tripleref = case_when(
    proteasome == "YES" &
      immuno == "YES" &
      `Daratumumab (exposed vs. refractory)` == "Refractory"        ~ "YES",
    TRUE      ~ "NO"
  )) %>% 
  mutate(pentaref = case_when(
    `Bortezomib (exposed vs. refractory)` == "Refractory" & 
      `Carfilzomib (exposed vs. refractory)` == "Refractory" &
      `Lenalidomide (exposed vs. refractory)` == "Refractory" & 
      `Pomalidomide (exposed vs. refractory)` == "Refractory" & 
      `Daratumumab (exposed vs. refractory)` == "Refractory"  ~ "YES",
    TRUE     ~ "NO"
  )) %>% 
  mutate(number_prior_lines_therapy = case_when(
    `Number of prior lines of therapy` <= 4           ~ "4",
    `Number of prior lines of therapy` > 4            ~ ">4"
  )) %>%
  mutate(`Tocilizumab (Yes, No)` = case_when(
    `Tocilizumab (Yes, No)` == "Siltuximab"                    ~ "YES",
      str_detect(`Tocilizumab (Yes, No)`, "COVID")             ~ "NO",
    TRUE                                                       ~ `Tocilizumab (Yes, No)`
  )) %>% 
  mutate(`Steroid use (Yes, No)` = case_when(
    str_detect(`Steroid use (Yes, No)`, "COVID")               ~ "NO",
    TRUE                                                       ~ `Steroid use (Yes, No)`
  )) %>% 
  mutate(`Disease status at time of referral (Relapsed vs Refractory)` = case_when(
    str_detect(`Disease status at time of referral (Relapsed vs Refractory)`, "Relapse")       ~ "Relapse",
    str_detect(`Disease status at time of referral (Relapsed vs Refractory)`, "Response")      ~ "Response",
    TRUE                                     ~ `Disease status at time of referral (Relapsed vs Refractory)`
  )) %>%

  mutate(exclusion_criteria =  
           rowSums(select(.,`Received investigation agent, plasmapheresis, surgery, radiation, or therapy within 14 days of apheresis (Yes, No)`:`ECOG > or = 2? (Yes, No)`
                          ) == "YES", na.rm = TRUE),
         exclusion_criteria = case_when(
           exclusion_criteria == 0           ~ "0",
           exclusion_criteria == 1           ~ "1",
           exclusion_criteria > 1            ~ "≥2"
         )) %>% 
  mutate(comorbidities = case_when(
    `Renal insufficiency CrCl < 45 mL/min (Yes, No)` == "YES" |
      `H/O Class III or IV CHF or severe nonischemic cardiomyopathy, unstable or poorly controlled angina, myocardial infarction, or ventricular arrhythmia within 6 months (Yes, No)` == "YES" |
      `LVEF <45% (Yes, No)` == "YES" |
      `AST/ALT >2.5 ULN (Yes, No)` == "YES" |
      `Total Bilirubin >1.5ULN (Yes, No)` == "YES" |
      `H/O of malignancies (Yes, No)` == "YES"                    ~ "YES",
    `LVEF <45% (Yes, No)` == "NO" &
      `AST/ALT >2.5 ULN (Yes, No)` == "NO" &
      `Total Bilirubin >1.5ULN (Yes, No)` == "NO" &
      `H/O of malignancies (Yes, No)` == "NO"                     ~ "NO",
    TRUE                                                          ~ NA_character_
  )) %>%

# CRS 
  mutate(CRS_any = ifelse(`Max CRS grade (0-5)` == 0, "NO", "YES"),
         CRS_any2 = ifelse(CRS_any== "NO", 0, 1),
         CRS_gradecat = case_when(
           `Max CRS grade (0-5)` == 0                             ~ "No CRS",
           `Max CRS grade (0-5)` == 1                             ~ "Grade 1 or 2",
           `Max CRS grade (0-5)` == 2                             ~ "Grade 1 or 2",
           `Max CRS grade (0-5)` >= 3                             ~ "Grade ≥3"),
         CRS_gradecat = factor(CRS_gradecat, levels = c("No CRS", "Grade 1 or 2", "Grade ≥3")),
         gr3_CRS = case_when(
           `Max CRS grade (0-5)` %in% c(0:2)                      ~ "Grade <3",
           `Max CRS grade (0-5)` %in% c(3:5)                      ~ "Grade ≥3",
           TRUE                                                   ~ NA_character_
           )) %>% 
  # mutate( = case_when(
  #    == 30                ~ NA,
  #   TRUE                          ~ CRS_fup
  # )) %>% 
  # ICANS 
  mutate(ICANS_any = ifelse(`Max ICANS (relative to infusion)` == 0, "NO", "YES"),
         ICANS_any2 = ifelse(ICANS_any == "NO", 0, 1),
         ICANS_gradecat = case_when(
           `Max ICANS (relative to infusion)` == 0 ~              "No ICANS",
           `Max ICANS (relative to infusion)` == 1 ~              "Grade 1 or 2",
           `Max ICANS (relative to infusion)` == 2 ~              "Grade 1 or 2",
           `Max ICANS (relative to infusion)` >= 3 ~              "Grade ≥3"),
         ICANS_gradecat = factor(ICANS_gradecat, levels = c("No ICANS", "Grade 1 or 2", "Grade ≥3")),
         gr2_ICANS = case_when(
           `Max ICANS (relative to infusion)` %in% c(0:1)         ~ "Grade <2",
           `Max ICANS (relative to infusion)` %in% c(2:5)         ~ "Grade ≥2",
           TRUE                                                   ~ NA_character_
         )) %>%

  mutate(`Neutropenia_7d` = case_when(
    `ANC Day 7` < 1.8                                              ~ "YES",
    is.na(`ANC Day 7`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  # mutate(`Neutropenia_14d` = case_when(
  #   `ANC day +14` < 1.8                                             ~ "YES",
  #   is.na(`ANC day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Neutropenia_21d` = case_when(
  #   `ANC day +21` < 1.8                                             ~ "YES",
  #   is.na(`ANC day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`Neutropenia_30d` = case_when(
    `ANC Day 30` < 1.8                                             ~ "YES",
    is.na(`ANC Day 30`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  mutate(`Neutropenia_60d` = case_when(
    `ANC Day 60` < 1.8                                             ~ "YES",
    is.na(`ANC Day 60`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  mutate(`Neutropenia_90d` = case_when(
    `ANC Day 90` < 1.8                                             ~ "YES",
    is.na(`ANC Day 90`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  # mutate(gr3_Neutropenia_apheresis = case_when(
  #   `ANC apheresis` < 1                                           ~ "YES",
  #   is.na(`ANC apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Neutropenia_-5d` = case_when(
  #   `ANC day -5 (k/ul)` < 1                                        ~ "YES",
  #   is.na(`ANC day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Neutropenia_0d` = case_when(
  #   `ANC day 0 (k/uL)` < 1                                        ~ "YES",
  #   is.na(`ANC day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`gr3_Neutropenia_7d` = case_when(
    `ANC Day 7` < 1                                              ~ "YES",
    is.na(`ANC Day 7`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  # mutate(`gr3_Neutropenia_14d` = case_when(
  #   `ANC day +14` < 1                                             ~ "YES",
  #   is.na(`ANC day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Neutropenia_21d` = case_when(
  #   `ANC day +21` < 1                                             ~ "YES",
  #   is.na(`ANC day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`gr3_Neutropenia_30d` = case_when(
    `ANC Day 30` < 1                                             ~ "YES",
    is.na(`ANC Day 30`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  mutate(`gr3_Neutropenia_60d` = case_when(
    `ANC Day 60` < 1                                             ~ "YES",
    is.na(`ANC Day 60`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  mutate(`gr3_Neutropenia_90d` = case_when(
    `ANC Day 90` < 1                                             ~ "YES",
    is.na(`ANC Day 90`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%

  # mutate(Anemia_apheresis = case_when(
  #   `Hb apheresis` < 11.4                                           ~ "YES",
  #   is.na(`Hb apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Anemia_-5d` = case_when(
  #   `Hb day -5 (k/ul)` < 11.4                                        ~ "YES",
  #   is.na(`Hb day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Anemia_0d` = case_when(
  #   `Hb day 0 (k/uL)` < 11.4                                        ~ "YES",
  #   is.na(`Hb day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`Anemia_7d` = case_when(
    `HgB Day 7` < 11.4                                              ~ "YES",
    is.na(`HgB Day 7`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  # mutate(`Anemia_14d` = case_when(
  #   `Hb day +14` < 11.4                                             ~ "YES",
  #   is.na(`Hb day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Anemia_21d` = case_when(
  #   `Hb day +21` < 11.4                                             ~ "YES",
  #   is.na(`Hb day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`Anemia_30d` = case_when(
    `HgB Day 30` < 11.4                                             ~ "YES",
    is.na(`HgB Day 30`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`Anemia_60d` = case_when(
    `HgB Day 60` < 11.4                                             ~ "YES",
    is.na(`HgB Day 60`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`Anemia_90d` = case_when(
    `HgB Day 90` < 11.4                                             ~ "YES",
    is.na(`HgB Day 90`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  # mutate(gr3_Anemia_apheresis = case_when(
  #   `Hb apheresis` < 8                                           ~ "YES",
  #   is.na(`Hb apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Anemia_-5d` = case_when(
  #   `Hb day -5 (k/ul)` < 8                                        ~ "YES",
  #   is.na(`Hb day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Anemia_0d` = case_when(
  #   `Hb day 0 (k/uL)` < 8                                        ~ "YES",
  #   is.na(`Hb day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`gr3_Anemia_7d` = case_when(
    `HgB Day 7` < 8                                              ~ "YES",
    is.na(`HgB Day 7`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  # mutate(`gr3_Anemia_14d` = case_when(
  #   `Hb day +14` < 8                                             ~ "YES",
  #   is.na(`Hb day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Anemia_21d` = case_when(
  #   `Hb day +21` < 8                                             ~ "YES",
  #   is.na(`Hb day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`gr3_Anemia_30d` = case_when(
    `HgB Day 30` < 8                                             ~ "YES",
    is.na(`HgB Day 30`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`gr3_Anemia_60d` = case_when(
    `HgB Day 60` < 8                                             ~ "YES",
    is.na(`HgB Day 60`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`gr3_Anemia_90d` = case_when(
    `HgB Day 90` < 8                                             ~ "YES",
    is.na(`HgB Day 90`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  # 
  # mutate(Thrombocytopenia_apheresis = case_when(
  #   `Plt apheresis` < 143                                           ~ "YES",
  #   is.na(`Plt apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Thrombocytopenia_-5d` = case_when(
  #   `Plt day -5 (k/ul)` < 143                                        ~ "YES",
  #   is.na(`Plt day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Thrombocytopenia_0d` = case_when(
  #   `Plt day 0 (k/uL)` < 143                                        ~ "YES",
  #   is.na(`Plt day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`Thrombocytopenia_7d` = case_when(
    `Platelets Day 7` < 143                                              ~ "YES",
    is.na(`Platelets Day 7`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  # mutate(`Thrombocytopenia_14d` = case_when(
  #   `Plt day +14` < 143                                             ~ "YES",
  #   is.na(`Plt day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`Thrombocytopenia_21d` = case_when(
  #   `Plt day +21` < 143                                             ~ "YES",
  #   is.na(`Plt day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`Thrombocytopenia_30d` = case_when(
    `Plateletes Day 30` < 143                                             ~ "YES",
    is.na(`Plateletes Day 30`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`Thrombocytopenia_60d` = case_when(
    `Platelets Day 60` < 143                                             ~ "YES",
    is.na(`Platelets Day 60`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`Thrombocytopenia_90d` = case_when(
    `Platelets Day 90` < 143                                             ~ "YES",
    is.na(`Platelets Day 90`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  # mutate(gr3_Thrombocytopenia_apheresis = case_when(
  #   `Plt apheresis` < 50                                           ~ "YES",
  #   is.na(`Plt apheresis`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Thrombocytopenia_-5d` = case_when(
  #   `Plt day -5 (k/ul)` < 50                                        ~ "YES",
  #   is.na(`Plt day -5 (k/ul)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Thrombocytopenia_0d` = case_when(
  #   `Plt day 0 (k/uL)` < 50                                        ~ "YES",
  #   is.na(`Plt day 0 (k/uL)`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`gr3_Thrombocytopenia_7d` = case_when(
    `Platelets Day 7` < 50                                              ~ "YES",
    is.na(`Platelets Day 7`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  # mutate(`gr3_Thrombocytopenia_14d` = case_when(
  #   `Plt day +14` < 50                                             ~ "YES",
  #   is.na(`Plt day +14`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  # mutate(`gr3_Thrombocytopenia_21d` = case_when(
  #   `Plt day +21` < 50                                             ~ "YES",
  #   is.na(`Plt day +21`)                                          ~ NA_character_,
  #   TRUE                                                          ~ "NO"
  # )) %>% 
  mutate(`gr3_Thrombocytopenia_30d` = case_when(
    `Plateletes Day 30` < 50                                             ~ "YES",
    is.na(`Plateletes Day 30`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`gr3_Thrombocytopenia_60d` = case_when(
    `Platelets Day 60` < 50                                             ~ "YES",
    is.na(`Platelets Day 60`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>%
  mutate(`gr3_Thrombocytopenia_90d` = case_when(
    `Platelets Day 90` < 50                                             ~ "YES",
    is.na(`Platelets Day 90`)                                          ~ NA_character_,
    TRUE                                                          ~ "NO"
  )) %>% 
  mutate(Neutropenia_gr1 = case_when(
    (`ANC Day 7` < 1.8 &
      `ANC Day 7` > 1.5) |
    (`ANC Day 30` < 1.8 &
      `ANC Day 30` > 1.5) |
      (`ANC Day 60` < 1.8 &
      `ANC Day 60` > 1.5) |
      (`ANC Day 90` < 1.8 &
      `ANC Day 90` > 1.5)                                          ~ "YES",
    is.na(`ANC Day 7`) |
      is.na(`ANC Day 30`) |
      is.na(`ANC Day 60`) |
      is.na(`ANC Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  mutate(Neutropenia_gr2 = case_when(
    (`ANC Day 7` < 1.5 &
      `ANC Day 7` > 1) |
    (`ANC Day 30` < 1.5 &
      `ANC Day 30` > 1) |
      (`ANC Day 60` < 1.5 &
      `ANC Day 60` > 1) |
      (`ANC Day 90` < 1.5 &
      `ANC Day 90` > 1)                                          ~ "YES",
    is.na(`ANC Day 7`) |
      is.na(`ANC Day 30`) |
      is.na(`ANC Day 60`) |
      is.na(`ANC Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  mutate(Neutropenia_gr3 = case_when(
    `ANC Day 7` < 1 |
    `ANC Day 30` < 1 |
      `ANC Day 60` < 1 |
      `ANC Day 90` < 1                                          ~ "YES",
    is.na(`ANC Day 7`) |
      is.na(`ANC Day 30`) |
      is.na(`ANC Day 60`) |
      is.na(`ANC Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  # mutate(Neutropenia_gr4 = case_when(
  #   `ANC Day 7` < 0.5 |
  #   `ANC Day 30` < 0.5 |
  #     `ANC Day 60` < 0.5 |
  #     `ANC Day 90` < 0.5                                          ~ "YES",
  #   is.na(`ANC Day 7`) |
  #     is.na(`ANC Day 30`) |
  #     is.na(`ANC Day 60`) |
  #     is.na(`ANC Day 90`)                                          ~ NA_character_,
  #   TRUE                                          ~ "NO"
  # )) %>% 
  mutate(any_neutropenia = case_when(
    Neutropenia_gr1 == "YES" |
      Neutropenia_gr2 == "YES" |
      Neutropenia_gr3 == "YES"                                          ~ "YES",
    is.na(Neutropenia_gr1) |
          is.na(Neutropenia_gr2) |
    is.na(Neutropenia_gr3)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  mutate(severe_neutro_30beyond = case_when(
    `ANC Day 30` < 1 |
      `ANC Day 60` < 1 |
      `ANC Day 90` < 1                                          ~ "YES",
      is.na(`ANC Day 30`) |
      is.na(`ANC Day 60`) |
      is.na(`ANC Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>%

  mutate(Anemia_gr1 = case_when(
      (`HgB Day 7` < 11.4 &
      `HgB Day 7` > 10) |
      (`HgB Day 30` < 11.4 &
      `HgB Day 30` > 10) |
      (`HgB Day 60` < 11.4 &
      `HgB Day 60` > 10) |
      (`HgB Day 90` < 11.4 &
      `HgB Day 90` > 10)                                        ~ "YES",
      is.na(`HgB Day 7`) |
      is.na(`HgB Day 30`) |
      is.na(`HgB Day 60`) |
      is.na(`HgB Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  mutate(Anemia_gr2 = case_when(
      (`HgB Day 7` < 10 &
      `HgB Day 7` > 8) |
      (`HgB Day 30` < 10 &
      `HgB Day 30` > 8) |
      (`HgB Day 60` < 10 &
      `HgB Day 60` > 8) |
      (`HgB Day 90` < 10 &
      `HgB Day 90` > 8)                                        ~ "YES",
      is.na(`HgB Day 7`) |
      is.na(`HgB Day 30`) |
      is.na(`HgB Day 60`) |
      is.na(`HgB Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  mutate(Anemia_gr3 = case_when(
      `HgB Day 7` < 8 |
      `HgB Day 30` < 8 |
      `HgB Day 60` < 8 |
      `HgB Day 90` < 8                                        ~ "YES",
      is.na(`HgB Day 7`) |
      is.na(`HgB Day 30`) |
      is.na(`HgB Day 60`) |
      is.na(`HgB Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  # mutate(Anemia_gr4 = case_when(
  #     `HgB Day 7` < 0.1 |
  #     `HgB Day 30` < 0.1 |
  #     `HgB Day 60` < 0.1 |
  #     `HgB Day 90` < 0.1                                        ~ "YES",
  #     is.na(`HgB Day 7`) |
  #     is.na(`HgB Day 30`) |
  #     is.na(`HgB Day 60`) |
  #     is.na(`HgB Day 90`)                                          ~ NA_character_,
  #   TRUE                                          ~ "NO"
  # )) %>% 
  mutate(severe_anemia_30beyond = case_when(
    `HgB Day 30` < 8 |
      `HgB Day 60` < 8 |
      `HgB Day 90` < 8                                        ~ "YES",
      is.na(`HgB Day 30`) |
      is.na(`HgB Day 60`) |
      is.na(`HgB Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>%

  mutate(Thrombocytopenia_gr1 = case_when(
      (`Platelets Day 7` < 143 &
      `Platelets Day 7` > 75) |
      (`Plateletes Day 30` < 143 &
      `Plateletes Day 30` > 75) |
      (`Platelets Day 60` < 143 &
      `Platelets Day 60` > 75) |
      (`Platelets Day 90` < 143 &
      `Platelets Day 90` > 75)                                        ~ "YES",
      is.na(`Platelets Day 7`) |
      is.na(`Plateletes Day 30`) |
      is.na(`Platelets Day 60`) |
      is.na(`Platelets Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  mutate(Thrombocytopenia_gr2 = case_when(
      (`Platelets Day 7` < 75 &
      `Platelets Day 7` > 50) |
      (`Plateletes Day 30` < 75 &
      `Plateletes Day 30` > 50) |
      (`Platelets Day 60` < 75 &
      `Platelets Day 60` > 50) |
      (`Platelets Day 90` < 75 &
      `Platelets Day 90` > 50)                                        ~ "YES",
      is.na(`Platelets Day 7`) |
      is.na(`Plateletes Day 30`) |
      is.na(`Platelets Day 60`) |
      is.na(`Platelets Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  mutate(Thrombocytopenia_gr3 = case_when(
      `Platelets Day 7` < 50 |
      `Plateletes Day 30` < 50 |
      `Platelets Day 60` < 50 |
      `Platelets Day 90` < 50                                        ~ "YES",
      is.na(`Platelets Day 7`) |
      is.na(`Plateletes Day 30`) |
      is.na(`Platelets Day 60`) |
      is.na(`Platelets Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  # mutate(Thrombocytopenia_gr4 = case_when(
  #     `Platelets Day 7` < 25 |
  #     `Plateletes Day 30` < 25 |
  #     `Platelets Day 60` < 25 |
  #     `Platelets Day 90` < 25                                        ~ "YES",
  #     is.na(`Platelets Day 7`) |
  #     is.na(`Plateletes Day 30`) |
  #     is.na(`Platelets Day 60`) |
  #     is.na(`Platelets Day 90`)                                          ~ NA_character_,
  #   TRUE                                          ~ "NO"
  # )) %>% 
  mutate(severe_throm_30beyond = case_when(
    `Plateletes Day 30` < 50 |
      `Platelets Day 60` < 50 |
      `Platelets Day 90` < 50                                        ~ "YES",
    is.na(`Plateletes Day 30`) |
      is.na(`Platelets Day 60`) |
      is.na(`Platelets Day 90`)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  mutate(any_anemia = case_when(
    Anemia_gr1 == "YES" |
      Anemia_gr2 == "YES" |
      Anemia_gr3 == "YES"                                          ~ "YES",
    is.na(Anemia_gr1) |
          is.na(Anemia_gr2) |
    is.na(Anemia_gr3)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  mutate(any_thrombo = case_when(
    Thrombocytopenia_gr1 == "YES" |
      Thrombocytopenia_gr2 == "YES" |
      Thrombocytopenia_gr3 == "YES"                                          ~ "YES",
    is.na(Thrombocytopenia_gr1) |
          is.na(Thrombocytopenia_gr2) |
    is.na(Thrombocytopenia_gr3)                                          ~ NA_character_,
    TRUE                                          ~ "NO"
  )) %>% 
  mutate(`gr3_cytopenia≥30d` = case_when(
    `ANC Day 30` < 1 |
      `HgB Day 30` < 8 |
      `Plateletes Day 30` < 50 |
      `ANC Day 60` < 1 |
      `HgB Day 60` < 8 |
      `Platelets Day 60` < 50 |
      `ANC Day 90` < 1 |
      `HgB Day 90` < 8 |
      `Platelets Day 90` < 50                                        ~ "YES",
    is.na(`ANC Day 30`) |
      is.na(`HgB Day 30`) |
      is.na(`Plateletes Day 30`) |
      is.na(`ANC Day 60`) |
      is.na(`HgB Day 60`) |
      is.na(`Platelets Day 60`) |
      is.na(`ANC Day 90`) |
      is.na(`HgB Day 90`) |
      is.na(`Platelets Day 90`)                                       ~ NA_character_,
    TRUE                                                              ~ "NO"
  )) %>% 
  mutate(cart_cell_dose = case_when(
    `Cell Dose (million cells)` >= 400                               ~ "≥ 400",
    `Cell Dose (million cells)` < 400                               ~ "< 400",
    TRUE                                                             ~ NA_character_
  )) %>% mutate(cart_cell_dose_v2 = case_when(
    `Cell Dose (million cells)` >= 400                               ~ "≥ 400",
    `Cell Dose (million cells)` < 400 & `Cell Dose (million cells)` >= 300      ~ "300 to < 400",
    `Cell Dose (million cells)` < 300 ~ "< 300",
    TRUE                                                             ~ NA_character_
  )) %>%
  # mutate(`gr3_cytopenia_30d` = case_when(
  #   `WBC day +30` < 2 | 
  #     `ANC Day 30` < 1 | 
  #     `HgB Day 30` < 8 | 
  #     `Plateletes Day 30` < 50                                              ~ "YES",
  #   is.na(`WBC day +30`) |
  #     is.na(`ANC Day 30`) |
  #     is.na(`HgB Day 30`) |
  #     is.na(`Plateletes Day 30`)                                            ~ NA_character_,
  #   TRUE                                                              ~ "NO"
  # )) %>% 
  # mutate(`gr3_cytopenia_90d` = case_when(
  #   `WBC day +90` < 2 | 
  #     `ANC Day 90` < 1 | 
  #     `HgB Day 90` < 8 | 
  #     `Platelets Day 90` < 50                                             ~ "YES",
  #   is.na(`WBC day +90`) |
  #     is.na(`ANC Day 90`) |
  #     is.na(`HgB Day 90`) |
  #     is.na(`Platelets Day 90`)                                            ~ NA_character_,
  #   TRUE                                                              ~ "NO"
  # )) %>% 
  # mutate(any_infection = case_when(
  #   `Infection (Yes, No)` == 1                                    ~ "Yes",
  #   `Infection (Yes, No)` == 0                                    ~ "No"
  # )) %>%
  # mutate(any_sevinfection = case_when(
  #   `Severe Infection (Yes, No)` == 1                              ~ "Yes",
  #   `Severe Infection (Yes, No)` == 0                              ~ "No"
  # )) %>% 
  mutate(baseline_ferritin = case_when(
    `Baseline Ferritin` >= 400                                    ~ "≥ ULN at LD",
    `Baseline Ferritin` < 400                                    ~ "Normal"
  )) %>% 
  mutate(baseline_crp = case_when(
    `Baseline CRP` >= 0.5                                    ~ "≥ ULN at LD",
    `Baseline CRP` < 0.5                                    ~ "Normal"
  )) %>% 
  mutate(baseline_B2M = case_when(
    `B2M` >= 5.5                                    ~ ">= 5.5",
    `B2M` < 5.5                                    ~ "< 5.5"
  )) %>%
  mutate(day30response_v2 = case_when(
    is.na(day30response) ~ day30response_NAreason,
    TRUE ~ day30response
  )) %>%
  mutate(mon3response_v2 = case_when(
    is.na(mon3response) ~ mon3response_NAreason,
    TRUE ~ mon3response
  )) %>%
  mutate(mon3response_v2 = ifelse(mon3response_v2 =="3 months not reached", NA_character_, mon3response_v2)) %>%
  mutate(ORR_30days_v2 = case_when(
    is.na(ORR_30days) ~ day30response_NAreason,
    TRUE ~ ORR_30days
  )) %>%
  mutate(ORR_3mon_v2 = case_when(
    is.na(ORR_3mon) ~ mon3response_NAreason,
    TRUE ~ ORR_3mon
  )) %>%
  mutate(ORR_3mon_v2 = ifelse(ORR_3mon_v2 =="3 months not reached", NA_character_, ORR_3mon_v2)) %>%
  mutate(day30response_MRD_sCRandCR_v2 = case_when(
    is.na(day30response_MRD_sCRandCR) ~ day30response_NAreason,
    TRUE ~ day30response_MRD_sCRandCR
  )) %>% 
  mutate(mon3response_MRD_sCRandCR_v2 = case_when(
    is.na(mon3response_MRD_sCRandCR) ~ mon3response_NAreason,
    TRUE ~ mon3response_MRD_sCRandCR
  )) %>% mutate(mon3response_MRD_sCRandCR_v2 = ifelse(mon3response_MRD_sCRandCR_v2 =="3 months not reached", NA_character_, mon3response_MRD_sCRandCR_v2)) %>%
  mutate(CRorbetter_30days_v2 = case_when(
    is.na(CRorbetter_30days) ~ day30response_NAreason,
    TRUE ~ CRorbetter_30days
  )) %>%
  mutate(CRorbetter_3mon_v2 = case_when(
    is.na(CRorbetter_3mon) ~ mon3response_NAreason,
    TRUE ~ CRorbetter_3mon
  )) %>% mutate(CRorbetter_3mon_v2 = ifelse(CRorbetter_3mon_v2 =="3 months not reached", NA_character_, CRorbetter_3mon_v2)) %>%
  mutate(bestresponse = case_when(
    day30response == "sCR or CR" | mon3response == "sCR or CR" ~ "sCR or CR",
    day30response == "VGPR" | mon3response == "VGPR" ~ "VGPR",
    day30response == "PR" | mon3response == "PR" ~ "PR",
    day30response == "SD" | mon3response == "SD" ~ "SD",
    day30response == "PD" | mon3response == "PD" ~ "PD",
    TRUE ~ NA_character_
  )) %>% mutate(bestresponse_v2 = case_when(
    is.na(bestresponse) & day30response_v2 == "Not evaluable by IMWG" & mon3response_v2 == "Not evaluable by IMWG" ~ "Not evaluable by IMWG",
    is.na(bestresponse) & day30response_v2 == "Died or progressed before day 30" & mon3response_v2 == "Died or progressed before 3 months" ~ "Died or progressed before day 30",
    TRUE ~ bestresponse
  )) %>% mutate(bestresponse_MRD_sCRandCR = case_when(
    day30response_MRD_sCRandCR == "sCR or CR, MRD-" | mon3response_MRD_sCRandCR == "sCR or CR, MRD-" ~ "sCR or CR, MRD-",
    day30response_MRD_sCRandCR == "sCR or CR, MRD+" | mon3response_MRD_sCRandCR == "sCR or CR, MRD+" ~ "sCR or CR, MRD+",
    day30response_MRD_sCRandCR == "sCR or CR, MRD unknown" | mon3response_MRD_sCRandCR == "sCR or CR, MRD unknown" ~ "sCR or CR, MRD unknown",
    TRUE ~ bestresponse
  )) %>% mutate(bestresponse_MRD_sCRandCR_v2 = case_when(
    is.na(bestresponse_MRD_sCRandCR) & day30response_v2 == "Not evaluable by IMWG" & mon3response_v2 == "Not evaluable by IMWG" ~ "Not evaluable by IMWG",
    is.na(bestresponse_MRD_sCRandCR) & day30response_v2 == "Died or progressed before day 30" & mon3response_v2 == "Died or progressed before 3 months" ~ "Died or progressed before day 30",
    TRUE ~ bestresponse_MRD_sCRandCR
  )) %>% mutate(bestORR = case_when(
    str_detect(bestresponse, "CR")    ~ "ORR",
    str_detect(bestresponse, "PR")    ~ "ORR",
    bestresponse=="SD" | bestresponse=="PD" ~ "SD/PD",
    TRUE                                                        ~ NA_character_
  )) %>% mutate(bestORR_v2 = case_when(
    is.na(bestORR) & day30response_v2 == "Not evaluable by IMWG" & mon3response_v2 == "Not evaluable by IMWG" ~ "Not evaluable by IMWG",
    is.na(bestORR) & day30response_v2 == "Died or progressed before day 30" & mon3response_v2 == "Died or progressed before 3 months" ~ "Died or progressed before day 30",
    TRUE ~ bestORR
  )) %>% mutate(bestCRorbetter = case_when(
    str_detect(bestresponse, "CR")   ~ "CR or better",
   is.na(bestresponse)               ~ NA_character_,
    TRUE                                                        ~ "< CR"
  )) %>% mutate(bestCRorbetter_v2 = case_when(
    is.na(bestCRorbetter) & day30response_v2 == "Not evaluable by IMWG" & mon3response_v2 == "Not evaluable by IMWG" ~ "Not evaluable by IMWG",
    is.na(bestCRorbetter) & day30response_v2 == "Died or progressed before day 30" & mon3response_v2 == "Died or progressed before 3 months" ~ "Died or progressed before day 30",
    TRUE ~ bestCRorbetter
  )) %>% mutate(bestMRD = case_when(
    MRD_30days == "MRD-" | MRD_3mon == "MRD-" ~ "MRD-",
    MRD_30days == "MRD+" & MRD_3mon == "MRD+" ~ "MRD+",
    TRUE ~ NA_character_
  )) %>%
  mutate(bestORR_alt = case_when(
    is.na(bestORR) ~ "SD/PD",
    TRUE ~ bestORR
  )) %>%
  mutate(bestCRorbetter_alt = case_when(
    is.na(bestCRorbetter) ~ "< CR",
    TRUE ~ bestCRorbetter
  )) %>%
  mutate(response_bridging2 = case_when(
    str_detect(response_bridging2, "SD") ~ "SD",
    response_bridging2 == "VGCR" ~ "VGPR",
    response_bridging2 == "MR" ~ "SD",
    TRUE ~ response_bridging2
  )) %>% mutate(bridging_response = case_when(
    `Bridging Therapy? (Yes, No)` == "YES" ~ response_bridging2,
    `Bridging Therapy? (Yes, No)` == "NO" ~ NA_character_,
    TRUE ~ NA_character_
  )) %>% mutate(bridging_response_ORR = case_when(
    bridging_response == "CR" | bridging_response == "PR" | bridging_response == "VGPR" ~ "PR or better",
    bridging_response == "PD" | bridging_response == "SD" ~ "SD/PD",
    TRUE ~ NA_character_
  )) %>% mutate(bridging_response2 = case_when(
    `Bridging Therapy? (Yes, No)` == "YES" & is.na(response_bridging2) ~ "Unknown response",
    `Bridging Therapy? (Yes, No)` == "YES" & !is.na(response_bridging2) ~ response_bridging2,
    `Bridging Therapy? (Yes, No)` == "NO" ~ NA_character_,
    TRUE ~ NA_character_
  )) %>% mutate(bridging_response_ORR2 = case_when(
    bridging_response2 == "Unknown response" ~ "Unknown response",
    bridging_response2 == "CR" | bridging_response2 == "PR" | bridging_response2 == "VGPR" ~ "PR or better",
    bridging_response2 == "PD" | bridging_response2 == "SD" ~ "SD/PD",
    TRUE ~ NA_character_
  )) %>% mutate(subtype = case_when(
    str_detect(`Myeloma sub-type`, "LC") ~ "Light chain",
    `Myeloma sub-type` == "IgG Oligosecretory" ~ NA_character_,
    `Myeloma sub-type` == "Non-secretory" ~ NA_character_,
    TRUE ~ "Heavy chain"
  )) %>% mutate(subtype_v2 = case_when(
    str_detect(`Myeloma sub-type`, "LC") ~ "Light chain",
    `Myeloma sub-type` == "IgG Oligosecretory" ~ "Oligo/Non-secretory",
    `Myeloma sub-type` == "Non-secretory" ~ "Oligo/Non-secretory",
    TRUE ~ "Intact immunoglobulin"
  )) %>%
  mutate(causedeath_cat = case_when(
  str_detect(causedeath, "loma") ~ "Myeloma",
  str_detect(causedeath, "prog") ~ "Myeloma",
  str_detect(causedeath, "ardiac") ~ "Cardiac",
  str_detect(causedeath, "OVID") ~ "COVID-19",
  str_detect(causedeath, "HLH") ~ "HLH",
  str_detect(causedeath, "oxicit") ~ "Toxicity",
  causedeath == "PENDING" ~ "Unknown",
   TRUE ~ causedeath
)) %>%
  mutate(causedeath_cat2 = case_when(
    causedeath_cat == "Unknown" ~ NA_character_,
    TRUE ~ causedeath_cat
  )) %>%
  mutate(time_apheresis_fup = 
           interval(
             start = date_of_apheresis, 
             end = os_time)/
           duration(n=1, units = "days")) %>%
  mutate(apheresis_infusion_time = 
           interval(
             start = date_of_apheresis, 
             end = `Date of CAR T infusion (# of days from apharesis to infusion)`)/
           duration(n=1, units = "days")) %>%
  mutate(mo_pfs_from_apheresis = 
           interval(
             start = date_of_apheresis,
             end = pfs_time)/
           duration(n=1, units = "months")) %>%
  mutate(mo_os_from_apheresis =
           interval(
             start = date_of_apheresis,
             end = os_time)/
           duration(n=1, units = "months"))
```

```{r}
## Labeling
var_label(cart0) <- list(Age = "Patient Age", agecat = "Patient Age - Categories", 
                        # tumor_burden ="Tumor burden", 
                        proteasome = "Refractory to Proteasome Inhibitors",
                       immuno = "Refractory to Immunomodulators", doubleref = "Double refractory",
                       tripleref="Triple refractory", pentaref="Penta refractory",
                       CRS_any = "Any CRS", CRS_gradecat = "CRS Grade",
                       ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", 
                       `Deletion 17p prior to CAR-T infusion (yes, no)` = "Deletion 17p at Infusion",
                       `t(4:14) prior to CAR-T infusion (yes, no)` = "t(4:14) at Infusion",
                       `t(14:16) prior to CAR-T infusion (yes, no)` = "t(4:16) at Infusion",
                       `Prior auto SCT (yes, no)` = "Prior auto SCT",
                       `Extramedullary Disease? (Yes, No)` = "Extramedullary disease",
                       dara="Refractory to Daratumumab", cytogenetics = "High-risk cytogenetics",
                       male_sex = "Male sex", number_prior_lines_therapy = "Number of prior lines of therapy (4 vs. >4)",
                       cart_cell_dose = "Cell dose (<400 vs. ≥400)", cart_cell_dose_v2 = "Cell dose (<300, 300 to <400, ≥400)", 
                       exclusion_criteria = "Number of KarMMa1 exclusion criteria",
                       comorbidities = "Any comorbid conditions", day30response = "Day 30 Response - Evaluable patients",
                       day30response_v2 = "Day 30 Response - All patients", mon3response = "Day 90 Response - Evaluable patients",
                       mon3response_v2 = "Day 90 Response - All patients", day30response_NAreason = "Day 30 NA responses", 
                       day30response_MRD_sCRandCR = "Day 30 Response with MRD - Evaluable patients", ORR_30days = "Day 30 ORR - Evaluable patients", 
                       CRorbetter_30days = "Day 30 CR or better - Evaluable patients",mon3response_NAreason = "Day 90 NA response", 
                       mon3response_MRD_sCRandCR = "Day 90 Response with MRD - Evaluable patients", ORR_3mon = "Day 90 ORR - Evaluable patients", 
                       CRorbetter_3mon = "Day 90 CR or better - Evaluable patients", bestresponse = "Best Response - Evaluable patients", 
                       bestresponse_MRD_sCRandCR = "Best Response with MRD - Evaluable patients", bestORR = "Best ORR - Evaluable patients", 
                       bestCRorbetter = "Best CR or better - Evaluable patients", day30response_MRD_sCRandCR_v2 = "Day 30 Response with MRD - All patients",
                       ORR_30days_v2 = "Day 30 ORR - All patients", CRorbetter_30days_v2 = "Day 30 CR or better - All patients",
                       mon3response_MRD_sCRandCR_v2 = "Day 90 Response with MRD - All patients", ORR_3mon_v2 = "Day 90 ORR - All patients", 
                       CRorbetter_3mon_v2 = "Day 90 CR or better - All patients", bestresponse_v2 = "Best response - All patients", 
                       bestresponse_MRD_sCRandCR_v2 = "Best response with MRD - All patients", bestORR_v2 = "Best ORR - All patients", 
                       bestCRorbetter_v2 = "Best CR or better - All patients", bestORR_alt = "Best ORR - All patients with Died/Not evaluable/Unk as SD/PD", 
                       bestCRorbetter_alt = "Best CR or better - All patients with Died/Not evaluable/Unk as < CR", causedeath = "Cause of Death",
                       causedeath_cat = "Cause of Death - Collapsed", causedeath_cat = "Cause of Death - Collapsed with Unknown as NA",
                       time_infusion_fup = "Time from infusion to last follow-up, days", time_apheresis_fup = "Time from apheresis to last follow-up, days",
                       apheresis_infusion_time = "Time from apheresis to infusion, days", subtype = "Myeloma subtype - oligo/non-secretory NA", subtype_v2 = "Myeloma subtype", bridging_response2 = "Response to bridging therapy", bridging_response_ORR2 = "Response to bridging therapy - ORR")

```

<br>

# Tables

## Table X. Manufacturing failures
```{r}
alldata %>%
  # Exclude patients who had manufacturing cart failure or died prior cart infusion
  select(`First manufacturing failure`,
         `Manufaturing failures with successfull second collection`) %>%
  mutate(across(everything(), ~ replace_na(., 0))) %>%
  tbl_summary(
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
    digits = all_continuous() ~ 1,
    missing = "no"
  ) %>%
  bold_labels() %>% add_stat_label() %>%
  modify_footnote(update = everything() ~ NA)
```
<br>

## Table 1A. Patient baseline characteristics (N=196)
```{r}
cart0 %>% 
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, subtype_v2,
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`, bridging_response2, bridging_response_ORR2,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         Blenrep,`BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         `Cell Dose (million cells)`, cart_cell_dose, cart_cell_dose_v2,
         exclusion_criteria,

         `ECOG > or = 2? (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `H/O or presence of CNS pathology (epilepsy, seizure, paresis, aphasia, stroke, CNS bleed, brian injuries, dementia, Parkinson's disease, cerebellar disease, organic brain syndrome, or psychosis) (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         comorbidities,

         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         time_apheresis_fup, time_infusion_fup,
         apheresis_infusion_time
         ) %>% 
  tbl_summary(
    type = list(
      c(
      `Extramedullary Disease? (Yes, No)`, 
      `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`,
      `High Marrow Burden (>= 50%)`,
    cytogenetics,
    `Deletion 17p prior to CAR-T infusion (yes, no)`,
        `t(4:14) prior to CAR-T infusion (yes, no)`,
        `t(14:16) prior to CAR-T infusion (yes, no)`,
    `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         Blenrep,`BCMA CAR-T on trial`, `Other BCMA trial`,
        immuno, proteasome, dara, doubleref, tripleref, pentaref,
    `ECOG > or = 2? (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
    `H/O or presence of CNS pathology (epilepsy, seizure, paresis, aphasia, stroke, CNS bleed, brian injuries, dementia, Parkinson's disease, cerebellar disease, organic brain syndrome, or psychosis) (Yes, No)`,
    comorbidities,
        `Did patient met criteria for KarMMa1 pre-CAR-T?`,
    `Renal insufficiency CrCl < 45 mL/min (Yes, No)`
    )
      ~"categorical"),

    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## From here, we excluded 37 patients
```{r}
cart0 %>% 
  filter(!is.na(exclude_for_manufacturing_cart_failure_or_died_prior_cart_infusion)) %>% 
  select(`Patients excluded` = patient_id)

cart0 <- cart0 %>% 
  # Exclude patients who had manufacturing cart failure or died prior cart infusion
  filter(is.na(exclude_for_manufacturing_cart_failure_or_died_prior_cart_infusion))
```

## Table 1B. Patient baseline characteristics (N=159)
```{r}
cart0 %>% 
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, subtype_v2,
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`, bridging_response2, bridging_response_ORR2,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         Blenrep,`BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         `Cell Dose (million cells)`, cart_cell_dose, cart_cell_dose_v2,
         exclusion_criteria,

         `ECOG > or = 2? (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `H/O or presence of CNS pathology (epilepsy, seizure, paresis, aphasia, stroke, CNS bleed, brian injuries, dementia, Parkinson's disease, cerebellar disease, organic brain syndrome, or psychosis) (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         comorbidities,

         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         time_apheresis_fup, time_infusion_fup,
         apheresis_infusion_time
         ) %>% 
  tbl_summary(
    type = list(
      c(
      `Extramedullary Disease? (Yes, No)`, 
      `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`,
      `High Marrow Burden (>= 50%)`,
    cytogenetics,
    `Deletion 17p prior to CAR-T infusion (yes, no)`,
        `t(4:14) prior to CAR-T infusion (yes, no)`,
        `t(14:16) prior to CAR-T infusion (yes, no)`,
    `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         Blenrep,`BCMA CAR-T on trial`, `Other BCMA trial`,
        immuno, proteasome, dara, doubleref, tripleref, pentaref,
    `ECOG > or = 2? (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
    `H/O or presence of CNS pathology (epilepsy, seizure, paresis, aphasia, stroke, CNS bleed, brian injuries, dementia, Parkinson's disease, cerebellar disease, organic brain syndrome, or psychosis) (Yes, No)`,
    comorbidities,
        `Did patient met criteria for KarMMa1 pre-CAR-T?`,
    `Renal insufficiency CrCl < 45 mL/min (Yes, No)`
    )
      ~"categorical"),

    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## Table 2. Safety with Standard of Care Idecabtagene Vicleucel Event and Grade - Without missings

```{r}
# tbl1 <- 
  cart0 %>% 
  select(`Max CRS grade (0-5)`,
         `Day of Max CRS (relative to infusion)`,
         `Max ICANS (relative to infusion)`,
         `Day of Max ICANS (relative to infusion)`,
         `Length of Hospital Stay (Total Days including Readmission)`,
         `ICU Admission? (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         any_neutropenia,
         Neutropenia_gr1, Neutropenia_gr2, 
         Neutropenia_gr3, any_anemia,
         Anemia_gr1, Anemia_gr2,
         Anemia_gr3, any_thrombo,
         Thrombocytopenia_gr1, Thrombocytopenia_gr2,
         Thrombocytopenia_gr3,
         severe_neutro_30beyond, severe_anemia_30beyond,
         severe_throm_30beyond,
          `Need for GCSF`,
         `Need for TPO Agonist`,
         `Stem Cell Boost`
         ) %>% 
  tbl_summary(
    type = list(
      c(`ICU Admission? (Yes, No)`,
        `Anakinra (Yes, No)`,
        any_neutropenia,
         Neutropenia_gr1, Neutropenia_gr2, 
         Neutropenia_gr3, any_anemia,
         Anemia_gr1, Anemia_gr2,
         Anemia_gr3, any_thrombo,
         Thrombocytopenia_gr1, Thrombocytopenia_gr2,
         Thrombocytopenia_gr3,
        severe_neutro_30beyond, severe_anemia_30beyond,
         severe_throm_30beyond,
        `Need for GCSF`,
        `Need for TPO Agonist`,
        `Stem Cell Boost`
      ) ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max}) [{p25}, {p75}]"), 
    digits = all_continuous() ~ 1,
    missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## Table 2. Safety with Standard of Care Idecabtagene Vicleucel Event and Grade - With missings

```{r}
# tbl1 <- 
  cart0 %>% 
  select(`Max CRS grade (0-5)`,
         `Day of Max CRS (relative to infusion)`,
         `Max ICANS (relative to infusion)`,
         `Day of Max ICANS (relative to infusion)`,
         `Length of Hospital Stay (Total Days including Readmission)`,
         `ICU Admission? (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         any_neutropenia,
         Neutropenia_gr1, Neutropenia_gr2, 
         Neutropenia_gr3, any_anemia,
         Anemia_gr1, Anemia_gr2,
         Anemia_gr3, any_thrombo,
         Thrombocytopenia_gr1, Thrombocytopenia_gr2,
         Thrombocytopenia_gr3,
         severe_neutro_30beyond, severe_anemia_30beyond,
         severe_throm_30beyond,
          `Need for GCSF`,
         `Need for TPO Agonist`,
         `Stem Cell Boost`
         ) %>% 
  tbl_summary(
    type = list(
      c(`ICU Admission? (Yes, No)`,
        `Anakinra (Yes, No)`,
        any_neutropenia,
         Neutropenia_gr1, Neutropenia_gr2, 
         Neutropenia_gr3, any_anemia,
         Anemia_gr1, Anemia_gr2,
         Anemia_gr3, any_thrombo,
         Thrombocytopenia_gr1, Thrombocytopenia_gr2,
         Thrombocytopenia_gr3,
        severe_neutro_30beyond, severe_anemia_30beyond,
         severe_throm_30beyond,
        `Need for GCSF`,
        `Need for TPO Agonist`,
        `Stem Cell Boost`
      ) ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max}) [{p25}, {p75}]"), 
    digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## Table 3A.Responses - EVALUABLE PATIENTS (Prior manuscript version)
The prior version of the manuscript examined responses only among evaluable patients - so excluding patients who died or progressed before the time point of interest, were not evaluable by IMWG, had missing data, or did not make it to the time point of interest. In this case, 148 patients were included in the denominator for D30, 129 patients for D90, and 153 patients for best response.  
```{r}
cart0 %>% 
  select(day30response, 
         day30response_NAreason, day30response_MRD_sCRandCR,
         ORR_30days, CRorbetter_30days, 
         mon3response, 
         mon3response_NAreason, mon3response_MRD_sCRandCR,
         ORR_3mon, CRorbetter_3mon,
         bestresponse, bestresponse_MRD_sCRandCR,
         bestORR, bestCRorbetter
         ) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## Table 3B.Responses - ALL PTS THAT MADE IT TO THE TIME POINT OF INTEREST
All of the 159 patients either had an event of interest or made it to D30. 149 patients either had an event of interest or made it to D90. For best response, all 159 patients were included.
```{r}
cart0 %>% 
  select(day30response_v2, day30response_MRD_sCRandCR_v2,
         ORR_30days_v2, CRorbetter_30days_v2,
         mon3response_v2, mon3response_MRD_sCRandCR_v2,
         ORR_3mon_v2, CRorbetter_3mon_v2,
         bestresponse_v2, bestresponse_MRD_sCRandCR_v2,
         bestORR_v2, bestCRorbetter_v2,
         bestORR_alt, bestCRorbetter_alt
         ) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

Patients with MRD by clonoseq (excludes Kansas, MDACC, Utah and Levine)
```{r}
cart0 %>% filter(!(str_detect(patient_id, "MDACC"))) %>%
  filter(!(str_detect(patient_id, "KUMC"))) %>%
  filter(!(str_detect(patient_id, "Utah"))) %>%
  filter(!(str_detect(patient_id, "LCI"))) %>%
  select(day30response_v2, day30response_MRD_sCRandCR_v2,
         ORR_30days_v2, CRorbetter_30days_v2,
         mon3response_v2, mon3response_MRD_sCRandCR_v2,
         ORR_3mon_v2, CRorbetter_3mon_v2,
         bestresponse_v2, bestresponse_MRD_sCRandCR_v2,
         bestORR_v2, bestCRorbetter_v2,
         bestORR_alt, bestCRorbetter_alt
         ) %>% 
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

Among patients with a response of SD or better at day 30, here is the evolution of responses at Day 90:
```{r}
cart0 %>% filter(!is.na(day30response)) %>% filter(!is.na(mon3response_v2)) %>% filter(day30response != "PD") %>%
  select(day30response_v2, mon3response_v2) %>% tbl_summary(by=mon3response_v2) %>% bold_labels() %>% 
  modify_footnote(update = everything() ~ NA)
```

```{r}
cart0 %>% 
  select(mon3response, mon3response_v2, 
         CRS_any) %>% 
  tbl_summary(by= CRS_any,
              missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>% 
  modify_spanning_header(all_stat_cols() ~ "**Any CRS**")

cart0 %>% 
  select(day30response, day30response_v2, mon3response, mon3response_v2, bestresponse, bestresponse_v2,
         bestORR, bestORR_v2, bestORR_alt, bestCRorbetter, bestCRorbetter_v2, bestCRorbetter_alt,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
  tbl_summary(by= `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
              missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>% 
  modify_spanning_header(all_stat_cols() ~ "**Any Prior treatment BCMA**")

```

Of the 159 patients with a response, how many are MRD neg (N and %).
```{r}
# cart0 %>% 
#   mutate(has_response = case_when(
#     !is.na(best_response)     ~ "Patient with responses"
#   )) %>% 
#   select(has_response, 
#          `Day 30 MRD (positive vs negative)`) %>% 
#   tbl_summary(by= has_response,
#               missing = "no") %>% 
#   bold_labels() %>% add_stat_label() %>%
#   modify_footnote(update = everything() ~ NA)
# 
# cart0 %>% 
#   mutate(has_response = case_when(
#     !is.na(best_response)     ~ "Patient with responses"
#   )) %>% 
#   select(has_response, 
#          `3 Month MRD (positive vs negative)`) %>% 
#   tbl_summary(by= has_response,
#               missing = "no") %>% 
#   bold_labels() %>% add_stat_label() %>%
#   modify_footnote(update = everything() ~ NA)
# 
# cart0 %>% 
#   mutate(has_response = case_when(
#     !is.na(best_response)     ~ "Patient with responses"
#   )) %>% 
#   select(has_response, 
#          best_MRD_response) %>% 
#   tbl_summary(by= has_response,
#               missing = "no") %>% 
#   bold_labels() %>% add_stat_label() %>%
#   modify_footnote(update = everything() ~ NA)

cart0 %>%
  select(MRD_30days, MRD_3mon, bestMRD) %>%
  tbl_summary(missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>%
  modify_footnote(update = everything() ~ NA)
```

## Table 3C. CR rates by light chain disease
Two patients are listed as NA for these analyses - one non-secretory and one oligosecretory.
```{r}
cart0 %>% 
  select(CRorbetter_30days, CRorbetter_30days_v2, CRorbetter_3mon, CRorbetter_3mon_v2, bestCRorbetter, bestCRorbetter_v2, bestCRorbetter_alt,
         subtype) %>% 
  tbl_summary(by= subtype,
              missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>% 
  modify_spanning_header(all_stat_cols() ~ "**Myeloma subtype**")
```

## Table 4.Characteristics associated with grade ≥ 3 CRS, grade ≥ 3 neurotoxicity, grade ≥ 3 cytopenias ≥ 30 days, best response of ≥ CR at 3 months, best ORR 
```{r}
cart0 %>% 
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         Blenrep,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         `BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cart_cell_dose,
         `Infection (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         baseline_ferritin, baseline_crp, baseline_B2M,
         `ECOG > or = 2? (Yes, No)`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         `LVEF <45% (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         gr3_CRS
  ) %>% 
  tbl_summary(by = gr3_CRS,
              type = list(
                c(
                  `Extramedullary Disease? (Yes, No)`, 
                  `Plasma Cell Leukemia? (yes, no)`,
                  `Amyloid? (yes, no)`,
                  POEMS,
                  `Non-secretory MM (Yes, No)`,
                  `High Marrow Burden (>= 50%)`,
                  `ECOG at consult`, `ECOG at LD`,
                  cytogenetics,
                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
                  `t(4:14) prior to CAR-T infusion (yes, no)`,
                  `t(14:16) prior to CAR-T infusion (yes, no)`,
                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
                  `Prior Allo SCT (Yes, No)`,
                  Blenrep,
                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
                  `BCMA CAR-T on trial`, `Other BCMA trial`,
                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
                  `Infection (Yes, No)`,
                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
                  `ECOG > or = 2? (Yes, No)`,
                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
                  `LVEF <45% (Yes, No)`,
                  `ANC < 1000/uL (Yes, No)`,
                  `Hemoglobin < 8 g/dL (Yes, No)`,
                  `Platelets < 50K (Yes, No)`, 
                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
                  `Non-secretory MM (Yes, No)`,

                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
                )
                ~"categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              percent = "row"
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Grade 3 CRS**")
```

```{r}
cart0 %>% 
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         Blenrep,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         `BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cart_cell_dose,
         `Infection (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         baseline_ferritin, baseline_crp, baseline_B2M,
         `ECOG > or = 2? (Yes, No)`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         `LVEF <45% (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         gr2_ICANS
  ) %>% 
  tbl_summary(by = gr2_ICANS,
              type = list(
                c(
                  `Extramedullary Disease? (Yes, No)`, 
                  `Plasma Cell Leukemia? (yes, no)`,
                  `Amyloid? (yes, no)`,
                  POEMS,
                  `Non-secretory MM (Yes, No)`,
                  `High Marrow Burden (>= 50%)`,
                  `ECOG at consult`, `ECOG at LD`,
                  cytogenetics,
                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
                  `t(4:14) prior to CAR-T infusion (yes, no)`,
                  `t(14:16) prior to CAR-T infusion (yes, no)`,
                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
                  `Prior Allo SCT (Yes, No)`,
                  Blenrep,
                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
                  `BCMA CAR-T on trial`, `Other BCMA trial`,
                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
                  `Infection (Yes, No)`,
                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
                  `ECOG > or = 2? (Yes, No)`,
                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
                  `LVEF <45% (Yes, No)`,
                  `ANC < 1000/uL (Yes, No)`,
                  `Hemoglobin < 8 g/dL (Yes, No)`,
                  `Platelets < 50K (Yes, No)`, 
                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
                  `Non-secretory MM (Yes, No)`,

                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
                )
                ~"categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              percent = "row"
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Grade 2 ICANS**")
```

```{r}
cart0 %>% 
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         Blenrep,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         `BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cart_cell_dose,
         `Infection (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         baseline_ferritin, baseline_crp, baseline_B2M,
         `ECOG > or = 2? (Yes, No)`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         `LVEF <45% (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         `gr3_cytopenia≥30d`
  ) %>% 
  tbl_summary(by = `gr3_cytopenia≥30d`,
              type = list(
                c(
                  `Extramedullary Disease? (Yes, No)`, 
                  `Plasma Cell Leukemia? (yes, no)`,
                  `Amyloid? (yes, no)`,
                  POEMS,
                  `Non-secretory MM (Yes, No)`,
                  `High Marrow Burden (>= 50%)`,
                  `ECOG at consult`, `ECOG at LD`,
                  cytogenetics,
                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
                  `t(4:14) prior to CAR-T infusion (yes, no)`,
                  `t(14:16) prior to CAR-T infusion (yes, no)`,
                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
                  `Prior Allo SCT (Yes, No)`,
                  Blenrep,
                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
                  `BCMA CAR-T on trial`, `Other BCMA trial`,
                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
                  `Infection (Yes, No)`,
                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
                  `ECOG > or = 2? (Yes, No)`,
                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
                  `LVEF <45% (Yes, No)`,
                  `ANC < 1000/uL (Yes, No)`,
                  `Hemoglobin < 8 g/dL (Yes, No)`,
                  `Platelets < 50K (Yes, No)`, 
                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
                  `Non-secretory MM (Yes, No)`,

                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
                )
                ~"categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              percent = "row"
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Grade 3 cytopenia**")
```

Including the 6 patients who either died or progressed before Day 30 (n=4) or were non-evaluable by IMWG (n=2) as < CR.

```{r}
cart0 %>% 
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         Blenrep,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         `BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cart_cell_dose,
         `Infection (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         baseline_ferritin, baseline_crp, baseline_B2M,
         `ECOG > or = 2? (Yes, No)`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         `LVEF <45% (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         bestCRorbetter_alt
  ) %>% 
  tbl_summary(by = bestCRorbetter_alt,
              type = list(
                c(
                  `Extramedullary Disease? (Yes, No)`, 
                  `Plasma Cell Leukemia? (yes, no)`,
                  `Amyloid? (yes, no)`,
                  POEMS,
                  `Non-secretory MM (Yes, No)`,
                  `High Marrow Burden (>= 50%)`,
                  `ECOG at consult`, `ECOG at LD`,
                  cytogenetics,
                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
                  `t(4:14) prior to CAR-T infusion (yes, no)`,
                  `t(14:16) prior to CAR-T infusion (yes, no)`,
                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
                  `Prior Allo SCT (Yes, No)`,
                  Blenrep,
                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
                  `BCMA CAR-T on trial`, `Other BCMA trial`,
                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
                  `Infection (Yes, No)`,
                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
                  `ECOG > or = 2? (Yes, No)`,
                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
                  `LVEF <45% (Yes, No)`,
                  `ANC < 1000/uL (Yes, No)`,
                  `Hemoglobin < 8 g/dL (Yes, No)`,
                  `Platelets < 50K (Yes, No)`, 
                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
                  `Non-secretory MM (Yes, No)`,

                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
                )
                ~"categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              percent = "row"
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Best CR or better at ≤ day 90**")
```

Including the 6 patients who either died or progressed before Day 30 (n=4) or were non-evaluable by IMWG (n=2) as SD/PD.

```{r}
cart0 %>% 
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         Blenrep,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         `BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cart_cell_dose,
         `Infection (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         baseline_ferritin, baseline_crp, baseline_B2M,
         `ECOG > or = 2? (Yes, No)`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         `LVEF <45% (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         bestORR_alt
  ) %>% 
  tbl_summary(by = bestORR_alt,
              type = list(
                c(
                  `Extramedullary Disease? (Yes, No)`, 
                  `Plasma Cell Leukemia? (yes, no)`,
                  `Amyloid? (yes, no)`,
                  POEMS,
                  `Non-secretory MM (Yes, No)`,
                  `High Marrow Burden (>= 50%)`,
                  `ECOG at consult`, `ECOG at LD`,
                  cytogenetics,
                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
                  `t(4:14) prior to CAR-T infusion (yes, no)`,
                  `t(14:16) prior to CAR-T infusion (yes, no)`,
                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
                  `Prior Allo SCT (Yes, No)`,
                  Blenrep,
                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
                  `BCMA CAR-T on trial`, `Other BCMA trial`,
                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
                  `Infection (Yes, No)`,
                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
                  `ECOG > or = 2? (Yes, No)`,
                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
                  `LVEF <45% (Yes, No)`,
                  `ANC < 1000/uL (Yes, No)`,
                  `Hemoglobin < 8 g/dL (Yes, No)`,
                  `Platelets < 50K (Yes, No)`, 
                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
                  `Non-secretory MM (Yes, No)`,

                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
                )
                ~"categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              percent = "row"
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Best ORR at ≤ day 90**")
```

```{r}
# cart0 %>% 
#   select(Age, agecat, male_sex, Sex,
#          `Extramedullary Disease? (Yes, No)`, 
#          `Disease status at time of referral (Relapsed vs Refractory)`,
#          `Plasma Cell Leukemia? (yes, no)`,
#          `Amyloid? (yes, no)`,
#          POEMS,
#          `Non-secretory MM (Yes, No)`, ################??????????
#          `High Marrow Burden (>= 50%)`, 
#          `ECOG at consult`, `ECOG at LD`, 
#          `R-ISS at CAR-T infusion`, 
#          cytogenetics,
#          `Deletion 17p prior to CAR-T infusion (yes, no)`,
#          `t(4:14) prior to CAR-T infusion (yes, no)`,
#          `t(14:16) prior to CAR-T infusion (yes, no)`,
#          `Bridging Therapy? (Yes, No)`,
#          `Number of prior lines of therapy`,
#          `Prior auto SCT (yes, no)`, 
#          `ASCT within 12 weeks prior to apheresis (Yes, No)`,
#          `Prior Allo SCT (Yes, No)`,
#          Blenrep,
#          `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
#          `BCMA CAR-T on trial`, `Other BCMA trial`,
#          immuno, proteasome, dara, doubleref, tripleref, pentaref, 
#          cart_cell_dose,
#          `Infection (Yes, No)`,
#          `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
#          baseline_ferritin, baseline_crp, baseline_B2M,
#          `ECOG > or = 2? (Yes, No)`,
#          `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
#          `LVEF <45% (Yes, No)`,
#          `ANC < 1000/uL (Yes, No)`,
#          `Hemoglobin < 8 g/dL (Yes, No)`,
#          `Platelets < 50K (Yes, No)`, 
#          `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
#          `Non-secretory MM (Yes, No)`,
#          `Did patient met criteria for KarMMa1 pre-CAR-T?`,
#          `Number of prior lines of therapy`
#   ) %>% 
#   mutate(`Number of prior lines of therapy` = case_when(
#     `Number of prior lines of therapy` <= 4           ~ "≤4",
#     `Number of prior lines of therapy` > 4            ~ ">4",
#   )) %>% 
#   tbl_summary(by = `Number of prior lines of therapy`,
#               type = list(
#                 c(
#                   `Extramedullary Disease? (Yes, No)`, 
#                   `Plasma Cell Leukemia? (yes, no)`,
#                   `Amyloid? (yes, no)`,
#                   POEMS,
#                   `Non-secretory MM (Yes, No)`,
#                   `High Marrow Burden (>= 50%)`,
#                   `ECOG at consult`, `ECOG at LD`,
#                   cytogenetics,
#                   `Deletion 17p prior to CAR-T infusion (yes, no)`,
#                   `t(4:14) prior to CAR-T infusion (yes, no)`,
#                   `t(14:16) prior to CAR-T infusion (yes, no)`,
#                   `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
#                   `ASCT within 12 weeks prior to apheresis (Yes, No)`,
#                   `Prior Allo SCT (Yes, No)`,
#                   Blenrep,
#                   `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
#                   `BCMA CAR-T on trial`, `Other BCMA trial`,
#                   immuno, proteasome, dara, doubleref, tripleref, pentaref,
#                   `Infection (Yes, No)`,
#                   `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
#                   `ECOG > or = 2? (Yes, No)`,
#                   `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
#                   `LVEF <45% (Yes, No)`,
#                   `ANC < 1000/uL (Yes, No)`,
#                   `Hemoglobin < 8 g/dL (Yes, No)`,
#                   `Platelets < 50K (Yes, No)`, 
#                   `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
#                   `Non-secretory MM (Yes, No)`,
#                   
#                   `Did patient met criteria for KarMMa1 pre-CAR-T?`
#                 )
#                 ~"categorical"),
#               statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
#               digits = all_continuous() ~ 1
#   ) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   add_p() %>% 
#   modify_footnote(update = everything() ~ NA) %>%
#   modify_spanning_header(all_stat_cols() ~ "**Line of therapy**")
```

## Table 4.Characteristics associated with grade ≥ 3 CRS, grade ≥ 3 neurotoxicity, grade ≥ 3 cytopenias ≥ 30 days, best response of ≥ CR at 3 months, best ORR in Multivariable Models of Idecabtagene vicleucel-treated patients.

Including the 6 patients who either died or progressed before Day 30 (n=4) or were non-evaluable by IMWG (n=2) as SD/PD for best ORR and as < CR for best CR or better.

```{r}
cart1 <- cart0 %>% 
  mutate(bestCRorbetter_model = case_when(
    bestCRorbetter_alt == "< CR"       ~ 0,
    bestCRorbetter_alt == "CR or better"    ~ 1
  ), 
  bestCRorbetter_model = factor(bestCRorbetter_model)) %>% 
  mutate(bestORR_model = case_when(
    bestORR_alt == "SD/PD"    ~ 0,
    bestORR_alt == "ORR"         ~ 1
  ), 
  bestORR_model = factor(bestORR_model))
```

### CR or better
```{r}
glm(bestCRorbetter_model ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease? (Yes, No)` + cart_cell_dose +
        `ECOG at LD` + pentaref + Age + `Number of prior lines of therapy`,
                data = cart1,
    family = "binomial"(link='logit')) %>%  
            tbl_regression(exponentiate = TRUE) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
            modify_spanning_header(everything() ~ "**Best CR or better vs. < CR**") %>%
            bold_p(t = .05) 
```

### best ORR
```{r}
# clogit(ORR_90days ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease? (Yes, No)` + `Cell Dose (million cells)` +
#         `ECOG at LD` + pentaref + Age,
#                 data = cart1) #%>%
            # tbl_regression(exponentiate = TRUE) %>%
            # modify_spanning_header(everything() ~ "ORR at 90 days vs PD/SD/MR")
```

```{r}
glm(bestORR_model ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease? (Yes, No)` + cart_cell_dose +
        `ECOG at LD` + pentaref + Age + `Number of prior lines of therapy`,
                data = cart1,
    family = "binomial") %>%
            tbl_regression(exponentiate = TRUE) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
            modify_spanning_header(everything() ~ "**Best ORR vs. < PR**") %>%
            bold_p(t = .05) 
```

### PFS
```{r}
coxph(Surv(time = cart0$mo_pfs_from_infusion,
           event = cart0$pfs_event) ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease? (Yes, No)` + cart_cell_dose +
        `ECOG at LD` + pentaref + Age + `Number of prior lines of therapy`,
      data =  cart0) %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
  modify_spanning_header(everything() ~ "**PFS**")

print(paste("Checking the proportional hazard assumption for the model above:")) 
fit <- coxph(Surv(time = cart0$mo_pfs_from_infusion,
           event = cart0$pfs_event) ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease? (Yes, No)` + cart_cell_dose +
        `ECOG at LD` + pentaref + Age + `Number of prior lines of therapy`,
      data =  cart0)
temp <- cox.zph(fit)
print(temp$table)
plot(temp)

print(paste("High-risk cytogenetics violates proportional hazards and has been included as a strata term in the model:"))
fit <- coxph(Surv(time = cart0$mo_pfs_from_infusion,
           event = cart0$pfs_event) ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + strata(cytogenetics) + `Extramedullary Disease? (Yes, No)` + cart_cell_dose +
        `ECOG at LD` + pentaref + Age + `Number of prior lines of therapy`,
      data =  cart0)
temp <- cox.zph(fit)
print(temp$table)
plot(temp)

print(paste("Putting high-risk cytogenetics as a strata term resolves the proportional hazards assumption issue. Here are the results from that model:"))
coxph(Surv(time = cart0$mo_pfs_from_infusion,
           event = cart0$pfs_event) ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics + `Extramedullary Disease? (Yes, No)` + cart_cell_dose +
        `ECOG at LD` + pentaref + Age + `Number of prior lines of therapy`,
      data =  cart0) %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
  modify_spanning_header(everything() ~ "**PFS**")

print(paste("If we want a HR for cytogenetics, we will have to split the data into two time points where the hazard changes in time (around 8 months). Then we will have two HRs for cytogenetics, one from 0 to 8 months and one >8 months:"))
cart0.split <- survSplit(Surv(mo_pfs_from_infusion, pfs_event) ~ ., data=cart0, cut=c(8),episode="tgroup",id="id")
cart0.split$cytogenetics <- factor(cart0.split$cytogenetics, levels = c("YES", "NO"))
coxph(Surv(tstart, mo_pfs_from_infusion, pfs_event) ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics:strata(tgroup) + `Extramedullary Disease? (Yes, No)` + cart_cell_dose +
        `ECOG at LD` + pentaref + Age + `Number of prior lines of therapy`,
      data =  cart0.split) %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
  modify_spanning_header(everything() ~ "**PFS**")

print(paste("Checking the proportional hazard of this model:"))
fit <- coxph(Surv(tstart, mo_pfs_from_infusion, pfs_event) ~ `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)` + cytogenetics:strata(tgroup) + `Extramedullary Disease? (Yes, No)` + cart_cell_dose +
        `ECOG at LD` + pentaref + Age + `Number of prior lines of therapy`,
      data =  cart0.split)
temp <- cox.zph(fit)
print(temp$table)
plot(temp)
print(paste("No violation of proportional hazards"))
```

## Comparison of pt characteristics for pts included vs. not included in MVA
```{r}
cart0 %>% mutate(included = case_when(
  is.na(cytogenetics) | is.na(cart_cell_dose) | is.na(`ECOG at LD`) ~ "Excluded",
  TRUE ~ "Included"
)) %>%
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         Blenrep,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         `BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cart_cell_dose,
         `Infection (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         baseline_ferritin, baseline_crp, baseline_B2M,
         `ECOG > or = 2? (Yes, No)`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         `LVEF <45% (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         time_infusion_fup, time_apheresis_fup, apheresis_infusion_time,
         included
  ) %>% 
  tbl_summary(by = included,
              type = list(
                c(
                  `Extramedullary Disease? (Yes, No)`, 
                  `Plasma Cell Leukemia? (yes, no)`,
                  `Amyloid? (yes, no)`,
                  POEMS,
                  `Non-secretory MM (Yes, No)`,
                  `High Marrow Burden (>= 50%)`,
                  `ECOG at consult`, `ECOG at LD`,
                  cytogenetics,
                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
                  `t(4:14) prior to CAR-T infusion (yes, no)`,
                  `t(14:16) prior to CAR-T infusion (yes, no)`,
                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
                  `Prior Allo SCT (Yes, No)`,
                  Blenrep,
                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
                  `BCMA CAR-T on trial`, `Other BCMA trial`,
                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
                  `Infection (Yes, No)`,
                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
                  `ECOG > or = 2? (Yes, No)`,
                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
                  `LVEF <45% (Yes, No)`,
                  `ANC < 1000/uL (Yes, No)`,
                  `Hemoglobin < 8 g/dL (Yes, No)`,
                  `Platelets < 50K (Yes, No)`, 
                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
                  `Non-secretory MM (Yes, No)`,

                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
                )
                ~"categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Included in MVA**")
```

## Re-running the univariable analyses only including pts in the MVA
```{r}
cart0 %>% mutate(included = case_when(
  is.na(cytogenetics) | is.na(cart_cell_dose) | is.na(`ECOG at LD`) ~ "Excluded",
  TRUE ~ "Included"
)) %>% filter(included == "Included") %>%
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         Blenrep,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         `BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cart_cell_dose,
         `Infection (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         baseline_ferritin, baseline_crp, baseline_B2M,
         `ECOG > or = 2? (Yes, No)`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         `LVEF <45% (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         gr3_CRS
  ) %>% 
  tbl_summary(by = gr3_CRS,
              type = list(
                c(
                  `Extramedullary Disease? (Yes, No)`, 
                  `Plasma Cell Leukemia? (yes, no)`,
                  `Amyloid? (yes, no)`,
                  POEMS,
                  `Non-secretory MM (Yes, No)`,
                  `High Marrow Burden (>= 50%)`,
                  `ECOG at consult`, `ECOG at LD`,
                  cytogenetics,
                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
                  `t(4:14) prior to CAR-T infusion (yes, no)`,
                  `t(14:16) prior to CAR-T infusion (yes, no)`,
                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
                  `Prior Allo SCT (Yes, No)`,
                  Blenrep,
                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
                  `BCMA CAR-T on trial`, `Other BCMA trial`,
                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
                  `Infection (Yes, No)`,
                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
                  `ECOG > or = 2? (Yes, No)`,
                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
                  `LVEF <45% (Yes, No)`,
                  `ANC < 1000/uL (Yes, No)`,
                  `Hemoglobin < 8 g/dL (Yes, No)`,
                  `Platelets < 50K (Yes, No)`, 
                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
                  `Non-secretory MM (Yes, No)`,

                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
                )
                ~"categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              percent = "row"
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Grade 3 CRS**")
```

```{r}
cart0 %>% mutate(included = case_when(
  is.na(cytogenetics) | is.na(cart_cell_dose) | is.na(`ECOG at LD`) ~ "Excluded",
  TRUE ~ "Included"
)) %>% filter(included == "Included") %>%
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         Blenrep,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         `BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cart_cell_dose,
         `Infection (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         baseline_ferritin, baseline_crp, baseline_B2M,
         `ECOG > or = 2? (Yes, No)`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         `LVEF <45% (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         gr2_ICANS
  ) %>% 
  tbl_summary(by = gr2_ICANS,
              type = list(
                c(
                  `Extramedullary Disease? (Yes, No)`, 
                  `Plasma Cell Leukemia? (yes, no)`,
                  `Amyloid? (yes, no)`,
                  POEMS,
                  `Non-secretory MM (Yes, No)`,
                  `High Marrow Burden (>= 50%)`,
                  `ECOG at consult`, `ECOG at LD`,
                  cytogenetics,
                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
                  `t(4:14) prior to CAR-T infusion (yes, no)`,
                  `t(14:16) prior to CAR-T infusion (yes, no)`,
                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
                  `Prior Allo SCT (Yes, No)`,
                  Blenrep,
                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
                  `BCMA CAR-T on trial`, `Other BCMA trial`,
                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
                  `Infection (Yes, No)`,
                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
                  `ECOG > or = 2? (Yes, No)`,
                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
                  `LVEF <45% (Yes, No)`,
                  `ANC < 1000/uL (Yes, No)`,
                  `Hemoglobin < 8 g/dL (Yes, No)`,
                  `Platelets < 50K (Yes, No)`, 
                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
                  `Non-secretory MM (Yes, No)`,

                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
                )
                ~"categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              percent = "row"
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Grade 3 ICANS**")
```

```{r}
cart0 %>% mutate(included = case_when(
  is.na(cytogenetics) | is.na(cart_cell_dose) | is.na(`ECOG at LD`) ~ "Excluded",
  TRUE ~ "Included"
)) %>% filter(included == "Included") %>%
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         Blenrep,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         `BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cart_cell_dose,
         `Infection (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         baseline_ferritin, baseline_crp, baseline_B2M,
         `ECOG > or = 2? (Yes, No)`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         `LVEF <45% (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         `gr3_cytopenia≥30d`
  ) %>% 
  tbl_summary(by = `gr3_cytopenia≥30d`,
              type = list(
                c(
                  `Extramedullary Disease? (Yes, No)`, 
                  `Plasma Cell Leukemia? (yes, no)`,
                  `Amyloid? (yes, no)`,
                  POEMS,
                  `Non-secretory MM (Yes, No)`,
                  `High Marrow Burden (>= 50%)`,
                  `ECOG at consult`, `ECOG at LD`,
                  cytogenetics,
                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
                  `t(4:14) prior to CAR-T infusion (yes, no)`,
                  `t(14:16) prior to CAR-T infusion (yes, no)`,
                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
                  `Prior Allo SCT (Yes, No)`,
                  Blenrep,
                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
                  `BCMA CAR-T on trial`, `Other BCMA trial`,
                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
                  `Infection (Yes, No)`,
                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
                  `ECOG > or = 2? (Yes, No)`,
                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
                  `LVEF <45% (Yes, No)`,
                  `ANC < 1000/uL (Yes, No)`,
                  `Hemoglobin < 8 g/dL (Yes, No)`,
                  `Platelets < 50K (Yes, No)`, 
                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
                  `Non-secretory MM (Yes, No)`,

                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
                )
                ~"categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              percent = "row"
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Grade 3 cytopenia**")
```

Including the 6 patients who either died or progressed before Day 30 (n=4) or were non-evaluable by IMWG (n=2) as < CR.

```{r}
cart0 %>% mutate(included = case_when(
  is.na(cytogenetics) | is.na(cart_cell_dose) | is.na(`ECOG at LD`) ~ "Excluded",
  TRUE ~ "Included"
)) %>% filter(included == "Included") %>%
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         Blenrep,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         `BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cart_cell_dose,
         `Infection (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         baseline_ferritin, baseline_crp, baseline_B2M,
         `ECOG > or = 2? (Yes, No)`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         `LVEF <45% (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         bestCRorbetter_alt
  ) %>% 
  tbl_summary(by = bestCRorbetter_alt,
              type = list(
                c(
                  `Extramedullary Disease? (Yes, No)`, 
                  `Plasma Cell Leukemia? (yes, no)`,
                  `Amyloid? (yes, no)`,
                  POEMS,
                  `Non-secretory MM (Yes, No)`,
                  `High Marrow Burden (>= 50%)`,
                  `ECOG at consult`, `ECOG at LD`,
                  cytogenetics,
                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
                  `t(4:14) prior to CAR-T infusion (yes, no)`,
                  `t(14:16) prior to CAR-T infusion (yes, no)`,
                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
                  `Prior Allo SCT (Yes, No)`,
                  Blenrep,
                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
                  `BCMA CAR-T on trial`, `Other BCMA trial`,
                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
                  `Infection (Yes, No)`,
                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
                  `ECOG > or = 2? (Yes, No)`,
                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
                  `LVEF <45% (Yes, No)`,
                  `ANC < 1000/uL (Yes, No)`,
                  `Hemoglobin < 8 g/dL (Yes, No)`,
                  `Platelets < 50K (Yes, No)`, 
                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
                  `Non-secretory MM (Yes, No)`,

                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
                )
                ~"categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              percent = "row"
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Best CR or better at ≤ day 90**")
```

Including the 6 patients who either died or progressed before Day 30 (n=4) or were non-evaluable by IMWG (n=2) as SD/PD.

```{r}
cart0 %>% mutate(included = case_when(
  is.na(cytogenetics) | is.na(cart_cell_dose) | is.na(`ECOG at LD`) ~ "Excluded",
  TRUE ~ "Included"
)) %>% filter(included == "Included") %>%
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`, ################??????????
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         cytogenetics,
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         Blenrep,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         `BCMA CAR-T on trial`, `Other BCMA trial`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cart_cell_dose,
         `Infection (Yes, No)`,
         `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
         baseline_ferritin, baseline_crp, baseline_B2M,
         `ECOG > or = 2? (Yes, No)`,
         `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
         `LVEF <45% (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`, 
         `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
         `Non-secretory MM (Yes, No)`,
         `Did patient met criteria for KarMMa1 pre-CAR-T?`,
         bestORR_alt
  ) %>% 
  tbl_summary(by = bestORR_alt,
              type = list(
                c(
                  `Extramedullary Disease? (Yes, No)`, 
                  `Plasma Cell Leukemia? (yes, no)`,
                  `Amyloid? (yes, no)`,
                  POEMS,
                  `Non-secretory MM (Yes, No)`,
                  `High Marrow Burden (>= 50%)`,
                  `ECOG at consult`, `ECOG at LD`,
                  cytogenetics,
                  `Deletion 17p prior to CAR-T infusion (yes, no)`,
                  `t(4:14) prior to CAR-T infusion (yes, no)`,
                  `t(14:16) prior to CAR-T infusion (yes, no)`,
                  `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
                  `ASCT within 12 weeks prior to apheresis (Yes, No)`,
                  `Prior Allo SCT (Yes, No)`,
                  Blenrep,
                  `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
                  `BCMA CAR-T on trial`, `Other BCMA trial`,
                  immuno, proteasome, dara, doubleref, tripleref, pentaref,
                  `Infection (Yes, No)`,
                  `Tocilizumab (Yes, No)`, `Steroid use (Yes, No)`, `Anakinra (Yes, No)`,
                  `ECOG > or = 2? (Yes, No)`,
                  `Renal insufficiency CrCl < 45 mL/min (Yes, No)`,
                  `LVEF <45% (Yes, No)`,
                  `ANC < 1000/uL (Yes, No)`,
                  `Hemoglobin < 8 g/dL (Yes, No)`,
                  `Platelets < 50K (Yes, No)`, 
                  `H/O or presence of Plasma cell leukemia, Waldenstrom's, POEMS, or amyloidosis (Yes, No)`,
                  `Non-secretory MM (Yes, No)`,

                  `Did patient met criteria for KarMMa1 pre-CAR-T?`
                )
                ~"categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              percent = "row"
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Best ORR at ≤ day 90**")
```

```{r}
# tbl1 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select("marrow cellularity" = `marrow cellularity baseline`, 
#          "marrow cellularity (%)" = `marrow cellularity baseline (%)`,
#          "% CD138 positive by IHC" = `marrow CD138 baseline (%)`, 
#          "Fibrosis grade" = `marrow fibrosis baseline`, 
#          "Dysplasia present" = `marrow dysplasia baseline`
#   ) %>% 
#   tbl_summary(type = list(
#     c(#`marrow cellularity baseline (%)`, `marrow CD138 baseline (%)`, 
#       `Fibrosis grade`) ~ "continuous"
#   ),
#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#             digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# tbl2 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select("marrow cellularity" = `marrow cellularity day +30`, 
#          "marrow cellularity (%)" = `marrow % cellularity day +30`,
#          "% CD138 positive by IHC" = `marrow %CD138 day +30`, 
#          "Fibrosis grade" = `marrow fibrosis day +30`, 
#          "Dysplasia present" = `marrow dysplasia day +30`
#   ) %>% 
#   mutate(`marrow cellularity (%)` = as.numeric(`marrow cellularity (%)`)) %>% 
#   mutate(`% CD138 positive by IHC` = as.numeric(`% CD138 positive by IHC`)) %>% 
#   mutate(`Fibrosis grade` = as.numeric(`Fibrosis grade`)) %>% 
#   mutate(`Dysplasia present` = as.numeric(`Dysplasia present`)) %>% 
#   tbl_summary(type = list(
#     c(`marrow cellularity (%)`, `% CD138 positive by IHC`, 
#       `Fibrosis grade`) ~ "continuous"
#   ),
#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#             digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# tbl3 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select("marrow cellularity" = `marrow cellularity day +90`, 
#          "marrow cellularity (%)" = `marrow % cellularity day +90`,
#          "% CD138 positive by IHC" = `marrow %CD138 day +90`, 
#          "Fibrosis grade" = `marrow fibrosis day +90`, 
#          "Dysplasia present" = `marrow dysplasia day +90`
#   ) %>% 
#   mutate(`marrow cellularity (%)` = as.numeric(`marrow cellularity (%)`)) %>% 
#   mutate(`% CD138 positive by IHC` = as.numeric(`% CD138 positive by IHC`)) %>% 
#   mutate(`Fibrosis grade` = as.numeric(`Fibrosis grade`)) %>% 
#   mutate(`Dysplasia present` = as.numeric(`Dysplasia present`)) %>% 
#   tbl_summary(type = list(
#     c(`marrow cellularity (%)`, `% CD138 positive by IHC`, 
#       `Fibrosis grade`) ~ "continuous"
#   ),
#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#             digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# tbl_merge(list(tbl1, tbl2, tbl3), tab_spanner = c("Baseline", "Day 30", "Day 90"))
```

<!-- ## Table 4. Supportive therapies and engraftment -->
<!-- Jenn -->

```{r}
# cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select(`Need for G-CSF post infus (Yes, No)`, `First Day of GCSF`, `Last Day of GCSF`,
#          `CD34 stem cell boost`, `Day of stem cell boost`, `Boost cell dose (million cells)`,
#          `Engraftment Day`,
#          `RBC transfusion within 7d post CART`, `Plt transfusion within 7d post CART`, 
#          `RBC transfusion >7d post CART`, `Plt transfusion >7d post CART`,
#          `Need for IVIG (Yes, No)`, `First day of IVIG`, `Last day of IVIG`
#   ) %>% 
#   tbl_summary(type = list(
#     c(`Day of stem cell boost`, `Boost cell dose (million cells)`,
#     `Last day of IVIG`) ~ "continuous",
#     c(`Need for G-CSF post infus (Yes, No)`,
#       `CD34 stem cell boost`,
#       `RBC transfusion within 7d post CART`, `Plt transfusion within 7d post CART`, 
#          `RBC transfusion >7d post CART`, `Plt transfusion >7d post CART`,
#       `Need for IVIG (Yes, No)`) ~ "categorical"
#   ),
#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#             digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
```

<!-- ## Table S1. Apheresis and product characteristics -->
```{r}
# cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select(TBV, `Whole blood processed (mL)`,
#          `Final collection volume (mL)`, 
#          `TBV processed`, 
#          `Access type`, `Final collection volume (mL)`,
#          `Run time (min)`,
#          `Time from apheresis to CAR-T infusion (days)`, `Total bags`,
#          `Total dose volume (mL)`, `Total cell dose (million cells)`
#          
#   ) %>% 
#   tbl_summary(type = list(c(TBV, `Total bags`) ~ "continuous"),
#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#             digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
```

<!-- ## Table S2. Cytopenias following ide-cel -->
<!-- **NAs are the patients who died (black) and test was not done (grey), they are remove from the denom (%) but not from the the N** -->

```{r}
# # tbl1 <- cart0 %>% 
# #   distinct(patient_id, .keep_all = TRUE) %>% 
# #   select("Leukopenia" = `Leukopenia_apheresis`, 
# #          "Grade3+ Leukopenia" = `gr3_Leukopenia_apheresis`, 
# #          "Neutropenia" = `Neutropenia_apheresis`, 
# #          "Grade3+ Neutropenia" = `gr3_Neutropenia_apheresis`, 
# #          "Anemia" = `Anemia_apheresis`, 
# #          "Grade3+ Anemia" = `gr3_Anemia_apheresis`, 
# #          "Thrombocytopenia" = `Thrombocytopenia_apheresis`, 
# #          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_apheresis`
# #   ) %>% 
# #   tbl_summary(type = list(everything() ~ "dichotomous"),
# #             digits = all_continuous() ~ 1#,
# #             # missing = "no"
# #             ) %>% 
# #   bold_labels() %>% add_stat_label() %>% 
# #   modify_footnote(update = everything() ~ NA)
# # 
# # tbl2 <- cart0 %>% 
# #   distinct(patient_id, .keep_all = TRUE) %>% 
# #   select("Leukopenia" = `Leukopenia_-5d`, 
# #          "Grade3+ Leukopenia" = `gr3_Leukopenia_-5d`, 
# #          "Neutropenia" = `Neutropenia_-5d`, 
# #          "Grade3+ Neutropenia" = `gr3_Neutropenia_-5d`,
# #          "Anemia" = `Anemia_-5d`, 
# #          "Grade3+ Anemia" = `gr3_Anemia_-5d`, 
# #          "Thrombocytopenia" = `Thrombocytopenia_-5d`, 
# #          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_-5d`
# #   ) %>% 
# #   tbl_summary(type = list(everything() ~ "dichotomous"),
# #             digits = all_continuous() ~ 1#,
# #             # missing = "no"
# #             ) %>% 
# #   bold_labels() %>% add_stat_label() %>% 
# #   modify_footnote(update = everything() ~ NA)
# # 
# # tbl3 <- cart0 %>% 
# #   distinct(patient_id, .keep_all = TRUE) %>% 
# #   select("Leukopenia" = `Leukopenia_0d`, 
# #          "Grade3+ Leukopenia" = `gr3_Leukopenia_0d`, 
# #          "Neutropenia" = `Neutropenia_0d`, 
# #          "Grade3+ Neutropenia" = `gr3_Neutropenia_0d`, 
# #          "Anemia" = `Anemia_0d`, 
# #          "Grade3+ Anemia" = `gr3_Anemia_0d`,
# #          "Thrombocytopenia" = `Thrombocytopenia_0d`, 
# #          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_0d`
# #   ) %>% 
# #   tbl_summary(type = list(everything() ~ "dichotomous"),
# #             digits = all_continuous() ~ 1#,
# #             # missing = "no"
# #             ) %>% 
# #   bold_labels() %>% add_stat_label() %>% 
# #   modify_footnote(update = everything() ~ NA)
# 
# tbl4 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select(#"Leukopenia" = `Leukopenia_7d`, 
#          # "Grade3+ Leukopenia" = `gr3_Leukopenia_7d`, 
#          "Neutropenia" = `Neutropenia_7d`, 
#          "Grade3+ Neutropenia" = `gr3_Neutropenia_7d`, 
#          # "Anemia" = `Anemia_7d`, 
#          # "Grade3+ Anemia" = `gr3_Anemia_7d`, 
#          "Thrombocytopenia" = `Thrombocytopenia_7d`, 
#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_7d`
#   ) %>% 
#   tbl_summary(type = list(everything() ~ "dichotomous"),
#             digits = all_continuous() ~ 1#,
#             # missing = "no"
#             ) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# # tbl5 <- cart0 %>% 
# #   distinct(patient_id, .keep_all = TRUE) %>% 
# #   filter(is.na(Not_evaluable_at_14days)) %>% 
# #   select("Leukopenia" = `Leukopenia_14d`, 
# #          "Grade3+ Leukopenia" = `gr3_Leukopenia_14d`, 
# #          "Neutropenia" = `Neutropenia_14d`, 
# #          "Grade3+ Neutropenia" = `gr3_Neutropenia_14d`,
# #          "Anemia" = `Anemia_14d`, 
# #          "Grade3+ Anemia" = `gr3_Anemia_14d`,
# #          "Thrombocytopenia" = `Thrombocytopenia_14d`, 
# #          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_14d` 
# #   ) %>% 
# #   tbl_summary(type = list(everything() ~ "dichotomous"),
# #             digits = all_continuous() ~ 1#,
# #             # missing = "no"
# #             ) %>% 
# #   bold_labels() %>% add_stat_label() %>% 
# #   modify_footnote(update = everything() ~ NA)
# # 
# # tbl6 <- cart0 %>% 
# #   distinct(patient_id, .keep_all = TRUE) %>% 
# #   filter(is.na(Not_evaluable_at_21days)) %>% 
# #   select("Leukopenia" = `Leukopenia_21d`,
# #          "Grade3+ Leukopenia" = `gr3_Leukopenia_21d`, 
# #          "Neutropenia" = `Neutropenia_21d`, 
# #          "Grade3+ Neutropenia" = `gr3_Neutropenia_21d`, 
# #          "Anemia" = `Anemia_21d`, 
# #          "Grade3+ Anemia" = `gr3_Anemia_21d`,
# #          "Thrombocytopenia" = `Thrombocytopenia_21d`, 
# #          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_21d`
# #   ) %>% 
# #   tbl_summary(type = list(everything() ~ "dichotomous"),
# #             digits = all_continuous() ~ 1#,
# #             # missing = "no"
# #             ) %>% 
# #   bold_labels() %>% add_stat_label() %>% 
# #   modify_footnote(update = everything() ~ NA)
# 
# tbl7 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(is.na(Not_evaluable_at_30days)) %>% 
#   select(#"Leukopenia" = `Leukopenia_30d`, 
#          # "Grade3+ Leukopenia" = `gr3_Leukopenia_30d`,
#          "Neutropenia" = `Neutropenia_30d`, 
#          "Grade3+ Neutropenia" = `gr3_Neutropenia_30d`,
#          # "Anemia" = `Anemia_30d`, 
#          # "Grade3+ Anemia" = `gr3_Anemia_30d`, 
#          "Thrombocytopenia" = `Thrombocytopenia_30d`,
#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_30d` 
#   ) %>% 
#   tbl_summary(type = list(everything() ~ "dichotomous"),
#             digits = all_continuous() ~ 1#,
#             # missing = "no"
#             ) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# tbl8 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(is.na(Not_evaluable_at_90days)) %>% 
#   select(#"Leukopenia" = `Leukopenia_90d`, 
#          # "Grade3+ Leukopenia" = `gr3_Leukopenia_90d`,
#          "Neutropenia" = `Neutropenia_90d`, 
#          "Grade3+ Neutropenia" = `gr3_Neutropenia_90d`,
#          # "Anemia" = `Anemia_90d`,
#          # "Grade3+ Anemia" = `gr3_Anemia_90d`,
#          "Thrombocytopenia" = `Thrombocytopenia_90d`, 
#          "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_90d`
#   ) %>% 
#   tbl_summary(type = list(everything() ~ "dichotomous"),
#             digits = all_continuous() ~ 1#,
#             # missing = "no"
#             ) %>% 
#   bold_labels() %>% add_stat_label() %>% 
#   modify_footnote(update = everything() ~ NA)
# 
# tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), 
#           tab_spanner = c("Apheresis", "Day -5",	"Day 0",	"Day 7",	"Day 14",	"Day 21",	"Day 30",	"Day 90")) %>% as_gt() %>%
#   gt::tab_source_note(gt::md("**Not evaluable patients are removed from the denominator <br>
#                              1 patient has missing 90 days values**"))
```

# Figures

## Figure 1. Response rate bar graph for day 30, day 90, Best ORR
### Panel A
```{r}
# cart0 %>% 
#   select(day30_response_group, day90_response_group, best_response) %>% 
#   pivot_longer(cols = everything()) %>% 
#   filter(!is.na(value)) %>% 
#   mutate(value = factor(value, levels = c("CR or sCR, MRD-",
#                                         "CR or sCR, MRD+",
#                                         "CR or sCR, MRD unknown",
#                                         "VGPR", "PR", "Others"))) %>% 
#   group_by(name, value) %>% 
#   summarise(count=n()) %>% 
#   mutate(percent=(count/sum(count)*100)
#   ) %>% 
#   filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
#   mutate(name = factor(name, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
#   group_by(name) %>% 
#   mutate(n = sum(count)) %>% 
#   ungroup() %>% 
#   mutate(name =  paste0(name,'\nN = ',n)) %>% 
#   ggplot(aes(x= name, y= percent, fill= value))+
#   geom_bar(stat = "identity")+ 
#   scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
#   geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
#   ylim(0,100)+
#   labs(x= NULL)+
#   theme_classic()

panelA_fig1 <- cart0 %>% 
  select(day30response_MRD_sCRandCR_v2, mon3response_MRD_sCRandCR_v2, bestresponse_MRD_sCRandCR_v2) %>% 
  pivot_longer(cols = everything()) %>% 
  filter(!is.na(value)) %>% 
  group_by(name, value) %>% 
  summarise(count=n()) %>% 
  mutate(Percent=(count/sum(count)*100)
  ) %>% 
  filter(str_detect(value, "CR") | str_detect(value, "PR")) %>% 
  mutate(name = factor(name, levels = c("day30response_MRD_sCRandCR_v2", "mon3response_MRD_sCRandCR_v2", "bestresponse_MRD_sCRandCR_v2"))) %>% 
  group_by(name) %>% 
  mutate(n = sum(count)) %>% 
  ungroup() %>% 
  mutate(value = str_replace(value, "sCR or CR", "CR or sCR")) %>% 
  mutate(value = factor(value, levels = c("CR or sCR, MRD-",
                                        "CR or sCR, MRD+",
                                        "CR or sCR, MRD unknown",
                                        "VGPR", "PR"))) %>% 
  #mutate(name =  paste0(name,'\nN = ',n)) %>% 
  ggplot(aes(x= name, y= Percent, fill= value))+
  geom_bar(stat = "identity", width=0.6)+ 
  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
  scale_x_discrete(labels=c("day30response_MRD_sCRandCR_v2" = "Day 30, N=159", 
                            "mon3response_MRD_sCRandCR_v2" = "Day 90, N=149",
                            "bestresponse_MRD_sCRandCR_v2" = "Best ORR, N=159"))+ 
  ylim(0,100)+
  labs(x= NULL)+
  theme_classic() + 
  theme(legend.position='bottom',
        legend.title = element_blank())
panelA_fig1
ggsave("Response rate bar graph for day 30, day 90, Best ORR.pdf",
       width = 9,
       height = 7)

# cart0 %>% 
#   select(day30_response_group, day90_response_group, best_response, 
#          any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
#   pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
#   filter(!is.na(status)) %>% 
#   mutate(status = factor(status, levels = c("CR or sCR, MRD-",
#                                         "CR or sCR, MRD+",
#                                         "CR or sCR, MRD unknown",
#                                         "VGPR", "PR", "Others"))) %>%
#   group_by(any_bcma, response, status) %>% 
#   summarise(count=n()) %>% 
#   mutate(percent=(count/sum(count)*100)
#   ) %>% 
#   # Count N 
#   group_by(response) %>% 
#   mutate(N = sum(count)) %>% 
#   ungroup() %>% 
#   filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
#   mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
#   mutate(response =  paste0(response,'\nN = ',N)) %>% 
#   
#   ggplot(aes(x= any_bcma, y= percent, fill= status))+
#   geom_bar(stat = "identity")+ 
#   scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
#   geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
#   ylim(0,100)+
#   labs(x= NULL)+
#   theme_classic()+
#   facet_wrap(. ~ response)

panelF_fig4 <- cart0 %>% 
  select(day30response_MRD_sCRandCR_v2, mon3response_MRD_sCRandCR_v2, bestresponse_MRD_sCRandCR_v2, 
         any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
  pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
  filter(!is.na(status)) %>% 
  mutate(status = factor(status, levels = c("sCR or CR, MRD-",
                                        "sCR or CR, MRD+",
                                        "sCR or CR, MRD unknown",
                                        "VGPR", "PR"))) %>%
  group_by(any_bcma, response, status) %>% 
  summarise(count=n()) %>% 
  mutate(Percent=(count/sum(count)*100)
  ) %>% 
  # Count N 
  group_by(response) %>% 
  mutate(N = sum(count)) %>% 
  ungroup() %>% 
  filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
  mutate(response = case_when(
    response == "day30response_MRD_sCRandCR_v2" ~ "Day 30, N=159", 
    response == "mon3response_MRD_sCRandCR_v2" ~ "Day 90, N=149",
    response == "bestresponse_MRD_sCRandCR_v2" ~ "Best ORR, N=159"
  )) %>% 
  mutate(response = factor(response, levels = c("Day 30, N=159", "Day 90, N=149", "Best ORR, N=159"))) %>% 
    mutate(status = str_replace(status, "sCR or CR", "CR or sCR"),
           status = factor(status, levels = c("CR or sCR, MRD-",
                                        "CR or sCR, MRD+",
                                        "CR or sCR, MRD unknown",
                                        "VGPR", "PR"))) %>%

  #mutate(response =  paste0(response,'\nN = ',N)) %>% 
  ggplot(aes(x= any_bcma, y= Percent, fill= status))+
  geom_bar(stat = "identity", width=0.4)+ 
  scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
  labs(x=NULL)+
  # geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
  ylim(0,100)+
  theme_classic()+ theme(legend.position='bottom',
        legend.title = element_blank()) +
  facet_wrap(. ~ response,  strip.position = "bottom")+
  theme(strip.background = element_blank(), strip.placement = "outside")
panelF_fig4
ggsave("Fig5 panel F.pdf",
       width = 9,
       height = 7)
# cart0 %>% 
#   select(day30_response_group, day90_response_group, best_response, 
#          any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
#   pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
#   filter(!is.na(status)) %>% 
#   mutate(status = factor(status, levels = c("CR or sCR, MRD-",
#                                         "CR or sCR, MRD+",
#                                         "CR or sCR, MRD unknown",
#                                         "VGPR", "PR", "Others"))) %>%
#   group_by(any_bcma, response, status) %>% 
#   summarise(count=n()) %>% 
#   mutate(percent=(count/sum(count)*100)
#   ) %>% 
#   # Count N 
#   group_by(response) %>% 
#   mutate(N = sum(count)) %>% 
#   ungroup() %>% 
#   filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
#   mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
#   mutate(response =  paste0(response,'\nN = ',N)) %>% 
#   
#   ggplot(aes(x= (interaction(any_bcma, response)), y= percent, fill= status))+
#   geom_bar(stat = "identity")+ 
#   scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
#   geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
#   ylim(0,100)+
#   labs(x= NULL)+
#   theme_classic()
# 
# cart0 %>% 
#   select(day30_response_group, day90_response_group, best_response, 
#          any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
#   pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
#   filter(!is.na(status)) %>% 
#   mutate(status = factor(status, levels = c("CR or sCR, MRD-",
#                                         "CR or sCR, MRD+",
#                                         "CR or sCR, MRD unknown",
#                                         "VGPR", "PR", "Others"))) %>%
#   group_by(any_bcma, response, status) %>% 
#   summarise(count=n()) %>% 
#   mutate(percent=(count/sum(count)*100)
#   ) %>% 
#   # Count N 
#   group_by(response) %>% 
#   mutate(N = sum(count)) %>% 
#   ungroup() %>% 
#   filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
#   mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
#   mutate(response =  paste0(response,'\nN = ',N)) %>% 
#   
#   ggplot(aes(x= (interaction(any_bcma, response)), y= percent, fill= status))+
#   geom_bar(stat = "identity")+ 
#   scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
#   ylim(0,100)+
#   theme_classic()

# a <- cart0 %>% 
#   select(day30_response_group, day90_response_group, best_response, 
#          any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
#   pivot_longer(cols = -any_bcma, names_to = "response", values_to = "status") %>% 
#   filter(!is.na(status)) %>% 
#   mutate(status = factor(status, levels = c("CR or sCR, MRD-",
#                                         "CR or sCR, MRD+",
#                                         "CR or sCR, MRD unknown",
#                                         "VGPR", "PR", "Others"))) %>%
#   group_by(any_bcma, response, status) %>% 
#   summarise(count=n()) %>% 
#   mutate(percent=(count/sum(count)*100)
#   ) %>% 
#   # Count N 
#   group_by(response) %>% 
#   mutate(N = sum(count)) %>% 
#   ungroup() %>% 
#   filter(str_detect(status, "CR") | str_detect(status, "PR")) %>% 
#   mutate(response = factor(response, levels = c("day30_response_group", "day90_response_group", "best_response"))) %>% 
#   mutate(response =  paste0(response,'\nN = ',N))
# 
# b <- a %>% filter(any_bcma == "NO")
# a %>% filter(any_bcma == "YES") %>% 
#   ggplot(aes(x= name, y= percent, fill= value))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9)
#            )+
#   # geom_bar(stat = "identity",
#   #          # position=position_dodge(width=0.9), 
#   #          data= b,
#   #          aes(x= name, y= percent, fill= value), alpha= 0.4)+
#   scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
#   ylim(0,100)+
#   labs(x= NULL)+
#   theme_classic()
# 
# a %>% filter(any_bcma == "YES") %>% 
#   ggplot(aes(x= name, y= percent, fill= value))+
#   geom_col(stat = "identity",
#            # position=position_dodge(width=0.9)
#            )+
#   geom_col(stat = "identity",
#            # position=position_dodge(width=0.9),
#            data= b,
#            aes(x= name, y= percent, fill= value), alpha= 0.4)+
#   scale_fill_manual(values = c("lightsteelblue2","steelblue2", "steelblue","thistle", "darkgray"))+
#   ylim(0,100)+
#   labs(x= NULL)+
#   theme_classic()
```

### Panel B: PFS Kaplan Meier (from CAR-T infusion)

```{r, fig.width= 6, fig.height=6}
panelB_fig1 <-
  ggsurvplot(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ 1, 
                   data = cart0),
           #title = "PFS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           legend = "none",
           font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           #pval=TRUE, 
           risk.table = TRUE,
           break.time.by = 3,
           legend.title = "",
           ylab = "PFS probability",
           xlab = "Time (in months)", ggtheme = theme_classic(), palette = c("Set1")  
) + guides(colour = guide_legend(ncol = 2))
#myplot$plot <- myplot$plot + 
#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
panelB_fig1
# ggsave("Panel B PFS Kaplan Meier.pdf",
#        width = 6,
#        height = 7) # Only save the risk table, use the export tab

survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ 1, 
                   data = cart0)
```

The 6-month PFS is:
```{r}
summary(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ 1, 
                   data = cart0), times = 6)

#summary(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ 1, 
#                   data = cart0), times = 12)
```

### Panel C: OS Kaplan Meier (from CAR-T infusion)
```{r, fig.width= 6, fig.height=6}
panelC_fig1 <- ggsurvplot(survfit(Surv(mo_os_from_infusion, os_event) ~ 1, 
                   data = cart0),
           #title = "OS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           legend = "none",
           font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           #pval=TRUE, 
           risk.table = TRUE,
           break.time.by = 3,
           legend.title = "",
           ylab = "OS probability",
           xlab = "Time (in months)", ggtheme = theme_classic(), palette = c("Set1") 
) + guides(colour = guide_legend(ncol = 2))
#myplot$plot <- myplot$plot + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
panelC_fig1

survfit(Surv(mo_os_from_infusion, os_event) ~ 1, 
                   data = cart0)
```

The 6-month OS is:
```{r}
summary(survfit(Surv(mo_os_from_infusion, os_event) ~ 1, 
                   data = cart0), times = 6)

summary(survfit(Surv(mo_os_from_infusion, os_event) ~ 1, 
                   data = cart0), times = 12)
```

### Panel D: Duration of response graph
There are 134 patients that have a best response of PR or better that are included in this figure.
```{r, fig.width= 6, fig.height=6}
cart1 <- cart0 %>% 
  mutate(added = case_when(
    day30response_MRD_sCRandCR_v2 %in% c("sCR or CR, MRD-",
                                "sCR or CR, MRD+", 
                                "sCR or CR, MRD unknown",
                                "VGPR", "PR")       ~ 30,
    mon3response_MRD_sCRandCR_v2 %in% c("sCR or CR, MRD-",
                                "sCR or CR, MRD+", 
                                "sCR or CR, MRD unknown",
                                "VGPR", "PR")      ~ 90
  )) %>% 
  mutate(response_date = case_when(
    day30response_MRD_sCRandCR_v2 %in% c("sCR or CR, MRD-",
                                "sCR or CR, MRD+", 
                                "sCR or CR, MRD unknown",
                                "VGPR", "PR")       ~ `Date of CAR T infusion (# of days from apharesis to infusion)` + days(30),
    mon3response_MRD_sCRandCR_v2 %in% c("sCR or CR, MRD-",
                                "sCR or CR, MRD+", 
                                "sCR or CR, MRD unknown",
                                "VGPR", "PR")      ~ `Date of CAR T infusion (# of days from apharesis to infusion)` + days(90)
    )) %>%
  mutate(months_at_pfs_from_response =
           interval(
             start = response_date,
             end = pfs_time)/
           duration(n=1, units = "months")) %>% 
  rename(any_bcma = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`)

panelD_fig1 <- ggsurvplot(survfit(Surv(months_at_pfs_from_response, pfs_event) ~ 1, 
                   data = cart1),
           #title = "Duration of response", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(14, "bold", "black"), font.y = c(14, "bold", "black"), 
           legend = "none",
           font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           #pval=TRUE, 
           risk.table = TRUE,
           break.time.by = 3,
           legend.title = "",
           ylab = "Duration of response (probability)",
           xlab = "Time since earliest response (months)", ggtheme = theme_classic(), palette = c("Set1")  
) + guides(colour = guide_legend(ncol = 2))
panelD_fig1

survfit(Surv(months_at_pfs_from_response, pfs_event) ~ 1, 
                   data = cart1)

# ggsurvplot(survfit(Surv(months_at_pfs_from_response, pfs_event) ~ any_bcma, 
#                    data = cart1),
#            title = "Duration of response", 
#            # font.main = c(24, "bold", "black"), 
#            font.x = c(14, "bold", "black"), font.y = c(14, "bold", "black"), 
#            legend = "top", legend.title = "Any BCMA therap",
#            legend.labs = c("No", "Yes"),
#            font.legend = c(14, "bold", "black"),
#            font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            xlim = c(0, 12),
#            pval=TRUE,
#            risk.table = TRUE,
#            risk.table.col = "strata",
#            break.time.by = 3,
#            ylab = "Duration of response (probability)",
#            xlab = "Time since earliest response (months)", ggtheme = theme_classic(), palette = c("Set1")  
# ) + guides(colour = guide_legend(ncol = 2))
```

```{r}
layout <- "
AB
AB
AB
AB
AB
AB
AC
DE
DE
DE
DE
DE
DE
DE
FG
"

panelA_fig1 + panelB_fig1$plot +
  panelB_fig1$table+
  panelC_fig1$plot + panelD_fig1$plot +
  panelC_fig1$table + panelD_fig1$table +
  plot_layout(design = layout)
ggsave("Fig1.pdf",
       width = 12,
       height = 9)
```

Among the 134 patients with a best ORR of PR or better, the median time to response is:
```{r}
cart2 <- cart1 %>% filter(bestORR_alt == "ORR") %>%
  mutate(time_infusion_bestORR = response_date - `Date of CAR T infusion (# of days from apharesis to infusion)`) 
median(cart2$time_infusion_bestORR)
range(cart2$time_infusion_bestORR)
```

Among the 67 patients with a best CR or better, the median time to response is:
```{r}
cart2 <- cart1 %>% filter(bestCRorbetter_alt == "CR or better") %>%
  mutate(time_infusion_bestCR = response_date - `Date of CAR T infusion (# of days from apharesis to infusion)`)
median(cart2$time_infusion_bestCR)
range(cart2$time_infusion_bestCR)
```

### Panel E: PFS Kaplan Meier (from apheresis)

```{r, fig.width= 6, fig.height=6}
myplot <-
  ggsurvplot(survfit(Surv(mo_pfs_from_apheresis, pfs_event) ~ 1, 
                   data = cart0),
           #title = "PFS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           legend = "none",
           font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           #pval=TRUE, 
           risk.table = TRUE,
           break.time.by = 3,
           legend.title = "",
           ylab = "PFS probability",
           xlab = "Time (in months)", ggtheme = theme_classic(), palette = c("Set1")  
) + guides(colour = guide_legend(ncol = 2))
#myplot$plot <- myplot$plot + 
#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
myplot

survfit(Surv(mo_pfs_from_apheresis, pfs_event) ~ 1, 
                   data = cart0)
```

The 6-month PFS is:
```{r}
summary(survfit(Surv(mo_pfs_from_apheresis, pfs_event) ~ 1, 
                   data = cart0), times = 6)
```

### Panel F: OS Kaplan Meier (from apheresis)
```{r, fig.width= 6, fig.height=6}
myplot <- ggsurvplot(survfit(Surv(mo_os_from_apheresis, os_event) ~ 1, 
                   data = cart0),
           #title = "OS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           legend = "none",
           font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13.45),
           #pval=TRUE, 
           risk.table = TRUE,
           break.time.by = 3,
           legend.title = "",
           ylab = "OS probability",
           xlab = "Time (in months)", ggtheme = theme_classic(), palette = c("Set1") 
) + guides(colour = guide_legend(ncol = 2))
#myplot$plot <- myplot$plot + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
myplot

survfit(Surv(mo_os_from_apheresis, os_event) ~ 1, 
                   data = cart0)
```

The 6-month OS is:
```{r}
summary(survfit(Surv(mo_os_from_apheresis, os_event) ~ 1, 
                   data = cart0), times = 6)
```

## Figure 2. Consort diagram
Lauren
<br>

<!-- ## Table 5. Patients’ response to Idecabtagene Vicleucel -->

<!-- ```{r} -->
<!-- tbl1 <- cart0 %>% -->
<!--   select(overall_response, -->
<!--          best_response) %>% -->
<!--   tbl_summary( -->
<!--     label = list(overall_response ~ "overall response within 90 days",  -->
<!--                  best_response ~ "best response within 90 days"), -->
<!--     digits = all_continuous() ~ 1, -->
<!--     missing = "no") %>% -->
<!--   bold_labels() %>% add_stat_label() -->

<!-- # tbl2 <- cart0 %>% -->
<!-- #   filter(str_detect(best_response, "CR")) %>% -->
<!-- #   select(best_MRD_response) %>% -->
<!-- #   tbl_summary(#type = list(c(best_MRD_response) ~ "categorical"), -->
<!-- #               # label = list(best_MRD_response ~ "best_MRD_response within CR/sCR"), -->
<!-- #               digits = all_continuous() ~ 1, -->
<!-- #               missing = "no") %>% -->
<!-- #   bold_labels() %>% add_stat_label() -->

<!-- tbl3 <- cart0 %>% -->
<!--   select(months_at_best_response, -->
<!--          months_at_best_CRresponse) %>% -->
<!--   tbl_summary( -->
<!--     type = list(c(months_at_best_response,  -->
<!--                   months_at_best_CRresponse) ~ "continuous"), -->
<!--     label = list(months_at_best_response ~ "months at best response within 90 days", -->
<!--                  months_at_best_CRresponse ~ "months at best CR response within 90 days"), -->
<!--     digits = all_continuous() ~ 1, -->
<!--     missing = "no") %>% -->
<!--   bold_labels() %>% add_stat_label() -->

<!-- tbl_stack(list(tbl1, #tbl2,  -->
<!--                tbl3)) %>% as_gt() -->

<!-- tbl4 <- cart0 %>% -->
<!--   filter(str_detect(best_response, "CR")) %>% -->
<!--   select(best_MRD_response) %>% -->
<!--   tbl_summary(type = list(c(best_MRD_response) ~ "categorical"), -->
<!--               label = list(best_MRD_response ~ "best MRD CR response within 90 days"), -->
<!--               digits = all_continuous() ~ 1, -->
<!--               missing = "no") %>% -->
<!--   bold_labels() %>% add_stat_label() -->

<!-- # tbl5 <- cart0 %>% -->
<!-- #   distinct(patient_id, .keep_all = TRUE) %>% -->
<!-- #   select(#MRDneg_90days, -->
<!-- #          ORR_90days, -->
<!-- #          day90_response, -->
<!-- #          day90_response_group) %>% -->
<!-- #   tbl_summary(#type = list( -->
<!-- #     # c(MRDneg_90days) ~ "categorical"), -->
<!-- #     digits = all_continuous() ~ 1, -->
<!-- #     missing = "no") %>% -->
<!-- #   bold_labels() %>% add_stat_label() -->
<!-- #  -->
<!-- #  -->
<!-- #  -->
<!-- # tbl7 <- cart0 %>% -->
<!-- #   distinct(patient_id, .keep_all = TRUE) %>% -->
<!-- #   select(best_response) %>% -->
<!-- #   tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"), -->
<!-- #               label = list(best_response ~ "best response in the first 90 days"), -->
<!-- #               digits = all_continuous() ~ 1, -->
<!-- #               missing = "no") %>% -->
<!-- #   bold_labels() %>% add_stat_label() -->
<!-- #  -->
<!-- # tbl8 <- cart0 %>% -->
<!-- #   distinct(patient_id, .keep_all = TRUE) %>% -->
<!-- #   filter(best_response == "CR or sCR") %>% -->
<!-- #   select(MRDneg_in_best_response) %>% -->
<!-- #   tbl_summary(type = list(c(MRDneg_in_best_response) ~ "categorical"), -->
<!-- #               label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"), -->
<!-- #               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), -->
<!-- #               digits = all_continuous() ~ 1, -->
<!-- #               missing = "no") %>% -->
<!-- #   bold_labels() %>% add_stat_label() -->
<!-- ``` -->

## Figure 3: ORR (A) vs. PFS (B) stratified by KarMMa exclusion criteria.

```{r}
cart0 <- cart0 %>% 
  rename(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T = 
           `Did patient met criteria for KarMMa1 pre-CAR-T?`) %>% 
  mutate(Overall = "Overall")
```

```{r, fig.width= 6, fig.height=6}
panelA_fig3 <- ggsurvplot(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
                   data = cart0),
           #title = "PFS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           ylab = "PFS probability",
           xlab = "Time (in months)", 
           break.time.by = 3,
           risk.table.col = "strata",
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "Met KarMMa1 criteria",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12)) + legend_title=""
panelA_fig3

survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
                   data = cart0)
```

Panel C: OS Kaplan Meier (from CAR-T infusion)
```{r, fig.width= 6, fig.height=6}
panelB_fig3 <- ggsurvplot(survfit(Surv(mo_os_from_infusion, os_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
                   data = cart0),
           #title = "OS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           break.time.by = 3,
           risk.table.col = "strata",
           ylab = "OS probability",
           xlab = "Time (in months)", 
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "Met KarMMa1 criteria",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
panelB_fig3

survfit(Surv(mo_os_from_infusion, os_event) ~ Did_patient_met_criteria_for_KarMMa1_pre_CAR_T, 
                   data = cart0)
```

```{r}
layout <- "
AB
AB
AB
AB
AB
AB
CD
"

panelA_fig3$plot +
  panelB_fig3$plot + 
  panelA_fig3$table +
  panelB_fig3$table + 
  plot_layout(design = layout)
ggsave("Fig3.pdf",
       width = 12,
       height = 5)
```

## Figure 4: OS and PFS stratified by any BCMA. 
```{r}
cart0 <- cart0 %>% 
  rename(AnyBCMA = `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`) %>% 
  mutate(Overall = "Overall")
```

```{r, fig.width= 6, fig.height=6}
panelA_fig4 <- ggsurvplot(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ AnyBCMA,
                   data = cart0),
           #title = "PFS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           break.time.by = 3,
           risk.table.col = "strata",
           ylab = "PFS probability",
           xlab = "Time (in months)", 
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "Any BCMA therapy",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
panelA_fig4

survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ AnyBCMA, 
                   data = cart0)
```

```{r, fig.width= 6, fig.height=6}
panelB_fig4 <- ggsurvplot(survfit(Surv(mo_os_from_infusion, os_event) ~ AnyBCMA, 
                   data = cart0),
           #title = "OS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           break.time.by = 3,
           risk.table.col = "strata",
           ylab = "OS probability",
           xlab = "Time (in months)", 
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "Any BCMA therapy",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
panelB_fig4

survfit(Surv(mo_os_from_infusion, os_event) ~ AnyBCMA, 
                   data = cart0)
```

## Figure 4a: OS and PFS stratified by Blenrep. 
```{r, fig.width= 6, fig.height=6}
panelC_fig4 <- ggsurvplot(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ Blenrep,
                   data = cart0),
           #title = "PFS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           break.time.by = 3,
           risk.table.col = "strata",
           ylab = "PFS probability",
           xlab = "Time (in months)", 
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "Belantamab mafodotin",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
 # scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
panelC_fig4

survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ Blenrep, 
                   data = cart0)
```

```{r, fig.width= 6, fig.height=6}
myplot <- ggsurvplot(survfit(Surv(mo_os_from_infusion, os_event) ~ Blenrep, 
                   data = cart0),
           #title = "OS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           break.time.by = 3,
           risk.table.col = "strata",
           ylab = "OS probability",
           xlab = "Time (in months)", 
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "Belantamab mafodotin",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
  #scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
myplot

survfit(Surv(mo_os_from_infusion, os_event) ~ Blenrep, 
                   data = cart0)
```

## Figure 4b: OS and PFS stratified by BCMA CAR-T on trial 
```{r}
cart0 <- cart0 %>% 
  rename(BCMA_ontrial = `BCMA CAR-T on trial`) %>% 
  mutate(Overall = "Overall")
```

```{r, fig.width= 6, fig.height=6}
panelE_fig4 <- ggsurvplot(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ BCMA_ontrial,
                   data = cart0),
           #title = "PFS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           break.time.by = 3,
           risk.table.col = "strata",
           ylab = "PFS probability",
           xlab = "Time (in months)", 
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "BCMA CAR T on trial",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
 # scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
panelE_fig4

survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ BCMA_ontrial, 
                   data = cart0)
```

```{r, fig.width= 6, fig.height=6}
myplot <- ggsurvplot(survfit(Surv(mo_os_from_infusion, os_event) ~ BCMA_ontrial, 
                   data = cart0),
           #title = "OS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           break.time.by = 3,
           risk.table.col = "strata",
           ylab = "OS probability",
           xlab = "Time (in months)", 
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "BCMA CAR T on trial",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
 # scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
 # scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
myplot

survfit(Surv(mo_os_from_infusion, os_event) ~ BCMA_ontrial, 
                   data = cart0)
```

## Figure 4c: OS and PFS stratified by other BCMA trial 
```{r}
cart0 <- cart0 %>% 
  rename(BCMA_other = `Other BCMA trial`) %>% 
  mutate(Overall = "Overall")
```

```{r, fig.width= 6, fig.height=6}
panelD_fig4 <- ggsurvplot(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ BCMA_other,
                   data = cart0),
           #title = "PFS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, pval.coord = c(9,0.25),
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           break.time.by = 3,
           risk.table.col = "strata",
           ylab = "PFS probability",
           xlab = "Time (in months)", 
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "BCMA BiTE on trial",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
panelD_fig4

survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ BCMA_other, 
                   data = cart0)
```

```{r, fig.width= 6, fig.height=6}
# myplot <- ggsurvplot(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ BCMA_other,
#                    data = cart0),
#            #title = "PFS from date of infusion", 
#            # font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            xlim = c(0, 13),
#            #pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            risk.table = TRUE,
#            break.time.by = 3,
#            risk.table.col = "strata",
#            ylab = "PFS probability",
#            xlab = "Time (in months)", 
#            ggtheme = theme_classic(), palette = c("Set1"),
#            legend = "bottom",
#            legend.title = "BCMA BiTE on trial",
#            legend.labs = c("No", "Yes")
# ) + guides(colour = guide_legend(ncol = 1))
# #myplot$plot <- myplot$plot + 
# #  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
# myplot
```

```{r, fig.width= 6, fig.height=6}
myplot <- ggsurvplot(survfit(Surv(mo_os_from_infusion, os_event) ~ BCMA_other, 
                   data = cart0),
           #title = "OS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           break.time.by = 3,
           risk.table.col = "strata",
           ylab = "OS probability",
           xlab = "Time (in months)", 
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "BCMA BiTE on trial",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
myplot

survfit(Surv(mo_os_from_infusion, os_event) ~ BCMA_other, 
                   data = cart0)
```

```{r}
layout <- "
ABC
ABC
ABC
ABC
ABC
ABC
EFG
HIJ
HIJ
HIJ
HIJ
HIJ
HIJ
KLJ
"

panelA_fig4$plot + panelB_fig4$plot + panelC_fig4$plot +
  panelA_fig4$table + panelB_fig4$table + panelC_fig4$table +
  panelD_fig4$plot + panelE_fig4$plot + panelF_fig4 +
  panelD_fig4$table + panelE_fig4$table +
  plot_layout(design = layout)
ggsave("Fig4.pdf",
       width = 18,
       height = 9)
```

## Figure 5: OS and PFS stratified by high-risk cytogenetics 
```{r, fig.width= 6, fig.height=6}
myplot <- ggsurvplot(survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ cytogenetics,
                   data = cart0),
           #title = "PFS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           break.time.by = 3,
           risk.table.col = "strata",
           ylab = "PFS probability",
           xlab = "Time (in months)", 
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "High-risk cytogenetics",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
myplot

survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ cytogenetics, 
                   data = cart0)
```

```{r, fig.width= 6, fig.height=6}
myplot <- ggsurvplot(survfit(Surv(mo_os_from_infusion, os_event) ~ cytogenetics, 
                   data = cart0),
           #title = "OS from date of infusion", 
           # font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,
           xlim = c(0, 13),
           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           risk.table = TRUE,
           break.time.by = 3,
           risk.table.col = "strata",
           ylab = "OS probability",
           xlab = "Time (in months)", 
           ggtheme = theme_classic(), palette = c("Set1"),
           legend = "bottom",
           legend.title = "High-risk cytogenetics",
           legend.labs = c("No", "Yes")
) + guides(colour = guide_legend(ncol = 1))
#myplot$plot <- myplot$plot + 
#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
#myplot$table <- myplot$table + 
#  scale_x_continuous(breaks = c(0, 3, 6, 9, 12))
myplot

survfit(Surv(mo_os_from_infusion, os_event) ~ cytogenetics, 
                   data = cart0)
```

## Table 6. Cause of death

There are 30 patients that died - two patients have an unknown cause of death and the cause of death for the other 28 patients is provided below. I included both the collapsed cause of death variable as well as the actual responses provided by the sites if you would like to double check how I have categorized cause of death for the collapsed variable.

The patient that died of HLH has concomitant grade 5 CRS.

```{r}
cart0 %>%
  filter(!is.na(datedeath)) %>% 
  select(causedeath_cat, causedeath_cat2, causedeath) %>%
  tbl_summary() %>%
  bold_labels() %>% add_stat_label()
```

## Table 7. Multiple Myeloma Efficacy and Toxicity Outcomes following infusion of SOC Idecabtagene vicleucel or in KarMMa (Variables to report on ORR, ≥ CR rate, 3 month PFS rate, any CRS, grade ≥ 3 CRS, any neurotoxicity, grade ≥ 3 neurotoxicity (see lymphoma EXAMPLE table below)
```{r}
tbl0 <- cart0 %>%
  mutate(cohort = "Overall") %>% 
  bind_rows(., cart0 %>% 
              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
  mutate(cohort = case_when(
    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
    TRUE                 ~ cohort
  ),
  cohort = factor(cohort, levels = c("Overall",
                                     "Met criteria for KarMMa1 pre-CAR-T",
                                     "NOT et criteria for KarMMa1 pre-CAR-T"))
  ) %>% 
  mutate(Total = "No of patients") %>% 
  select(Total, cohort) %>%

  tbl_summary(by= Total,
              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
              statistic = all_categorical() ~ "{n}"
              # percent = "row"
              ) %>%
  bold_labels() %>% #add_stat_label() %>% 
  modify_header(all_stat_cols() ~ "**{level}**") %>% 
  modify_footnote(update = everything() ~ NA)

tbl1 <- cart0 %>%
  mutate(cohort = "Overall") %>% 
  bind_rows(., cart0 %>% 
              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
  mutate(cohort = case_when(
    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
    TRUE                 ~ cohort
  ),
  cohort = factor(cohort, levels = c("Overall",
                                     "Met criteria for KarMMa1 pre-CAR-T",
                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
  select(bestORR_alt, cohort) %>%
  tbl_summary(by= bestORR_alt,
              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
              statistic = all_categorical() ~ "{p}%",
              percent = "row") %>%
  bold_labels() %>% add_stat_label() %>% 
  modify_header(all_stat_cols() ~ "**{level}**")

tbl2 <- cart0 %>%
  mutate(cohort = "Overall") %>% 
  bind_rows(., cart0 %>% 
              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
  mutate(cohort = case_when(
    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
    TRUE                 ~ cohort
  ),
  cohort = factor(cohort, levels = c("Overall",
                                     "Met criteria for KarMMa1 pre-CAR-T",
                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
  select(bestCRorbetter_alt, cohort) %>%
  tbl_summary(by= bestCRorbetter_alt,
              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
              statistic = all_categorical() ~ "{p}%",
              percent = "row") %>%
  bold_labels() %>% add_stat_label() %>% 
  modify_header(all_stat_cols() ~ "**{level}**")

tbl3 <- cart0 %>%
  mutate(cohort = "Overall") %>% 
  bind_rows(., cart0 %>% 
              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
  mutate(cohort = case_when(
    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
    TRUE                 ~ cohort
  ),
  cohort = factor(cohort, levels = c("Overall",
                                     "Met criteria for KarMMa1 pre-CAR-T",
                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
  select(CRS_any, cohort) %>%
  tbl_summary(by= CRS_any,
              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
              statistic = all_categorical() ~ "{p}%",
              percent = "row") %>%
  bold_labels() %>% add_stat_label() %>% 
  modify_header(all_stat_cols() ~ "**{level}**")

tbl4 <- cart0 %>%
  mutate(cohort = "Overall") %>% 
  bind_rows(., cart0 %>% 
              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
  mutate(cohort = case_when(
    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
    TRUE                 ~ cohort
  ),
  cohort = factor(cohort, levels = c("Overall",
                                     "Met criteria for KarMMa1 pre-CAR-T",
                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
  select(gr3_CRS, cohort) %>%
  tbl_summary(by= gr3_CRS,
              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
              statistic = all_categorical() ~ "{p}%",
              percent = "row") %>%
  bold_labels() %>% add_stat_label() %>% 
  modify_header(all_stat_cols() ~ "**{level}**")

tbl5 <- cart0 %>%
  mutate(cohort = "Overall") %>% 
  bind_rows(., cart0 %>% 
              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
  mutate(cohort = case_when(
    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
    TRUE                 ~ cohort
  ),
  cohort = factor(cohort, levels = c("Overall",
                                     "Met criteria for KarMMa1 pre-CAR-T",
                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
  select(ICANS_any, cohort) %>%
  tbl_summary(by= ICANS_any,
              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
              statistic = all_categorical() ~ "{p}%",
              percent = "row") %>%
  bold_labels() %>% add_stat_label() %>% 
  modify_header(all_stat_cols() ~ "**{level}**")

tbl6 <- cart0 %>%
  mutate(cohort = "Overall") %>% 
  bind_rows(., cart0 %>% 
              rename(cohort = Did_patient_met_criteria_for_KarMMa1_pre_CAR_T)) %>% 
  mutate(cohort = case_when(
    cohort == "YES"   ~ "Met criteria for KarMMa1 pre-CAR-T",
    cohort == "NO"   ~ "NOT et criteria for KarMMa1 pre-CAR-T",
    TRUE                 ~ cohort
  ),
  cohort = factor(cohort, levels = c("Overall",
                                     "Met criteria for KarMMa1 pre-CAR-T",
                                     "NOT et criteria for KarMMa1 pre-CAR-T"))) %>% 
  select(gr2_ICANS, cohort) %>%
  tbl_summary(by= gr2_ICANS,
              # type = list(c(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) ~ "categorical"),
              statistic = all_categorical() ~ "{p}%",
              percent = "row") %>%
  bold_labels() %>% add_stat_label() %>% 
  modify_header(all_stat_cols() ~ "**{level}**")

tbl_merge(list(tbl0, tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), 
          tab_spanner = c("", "Best ORR", "Best CR or better",
                          "Any CRS", "Severe CRS", "Any ICANS", "Severe ICANS"))

# cart0 %>%
#   select(day30_response_sCRvsOthers, CRS_any, CRS_gradecat, ICANS_any, ICANS_gradecat, Did_patient_met_criteria_for_KarMMa1_pre_CAR_T) %>%
#   tbl_summary() %>%
#   bold_labels() %>% add_stat_label()

# tbl1 <- cart0 %>%
#   select(ORR_30days, day30_response_sCRvsOthers) %>%
#   tbl_summary() %>%
#   bold_labels() %>% add_stat_label() %>%
#   modify_spanning_header(all_stat_cols() ~ "**Overall**")
# 
# tbl2 <- cart0 %>%
#   filter(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T == "YES") %>% 
#   select(ORR_30days, day30_response_sCRvsOthers) %>%
#   tbl_summary() %>%
#   bold_labels() %>% add_stat_label() %>%
#   modify_spanning_header(all_stat_cols() ~ "**Met criteria for KarMMa1 pre-CAR-T**")
# 
# tbl3 <- cart0 %>%
#   filter(Did_patient_met_criteria_for_KarMMa1_pre_CAR_T == "NO") %>% 
#   select(ORR_30days, day30_response_sCRvsOthers) %>%
#   tbl_summary() %>%
#   bold_labels() %>% add_stat_label() %>%
#   modify_spanning_header(all_stat_cols() ~ "**NOT met criteria for KarMMa1 pre-CAR-T**")
# 
# tbl_merge(list(tbl1, tbl2, 
#                tbl3), 
#           tab_spanner = c("**Overall**", 
#                           "**Met criteria for KarMMa1 pre-CAR-T**", 
#                           "**NOT met criteria for KarMMa1 pre-CAR-T**")) %>% 
#   as_gt()

# Estimating median survival time
# survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ 1, 
#                    data = cart0)
```

```{r}
cart1 <- cart0 %>% 
  janitor::clean_names()
```

```{r}
tbl1 <- tbl_survfit(
  cart1,
  y = Surv(mo_pfs_from_infusion, pfs_event),
  include = c(overall, did_patient_met_criteria_for_kar_m_ma1_pre_car_t#, 
              # CRS_any, CRS_gradecat, ICANS_any, ICANS_gradecat
              ),
  probs = 0.5,
  label_header = "**Median PFS**"
)

# 3 month pfs rate
tbl2 <- list(
    survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ 1, 
                   data = cart1),
    survfit(Surv(mo_pfs_from_infusion, pfs_event) ~ did_patient_met_criteria_for_kar_m_ma1_pre_car_t, 
                   data = cart1)
  ) %>%
  tbl_survfit(times = c(3, 6),
              label_header = "**PFS Rate at {time} Months**")

tbl_merge(list(tbl1, tbl2))
```

<!-- Extra PFS analysis -->
<!-- ```{r} -->
<!-- tbl1 <- tbl_survfit( -->
<!--   cart1, -->
<!--   y = Surv(days_at_pfs_from_infusion, pfs_event), -->
<!--   include = c(agecat, male_sex, sex, extramedullary_disease_yes_no,  -->
<!--               disease_status_at_time_of_referral_relapsed_vs_refractory,  -->
<!--               plasma_cell_leukemia_yes_no, amyloid_yes_no, poems,  -->
<!--               non_secretory_mm_yes_no, high_marrow_burden_50_percent,  -->
<!--               ecog_at_consult, ecog_at_ld, r_iss_at_car_t_infusion,  -->
<!--               cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no,  -->
<!--               t_4_14_prior_to_car_t_infusion_yes_no,  -->
<!--               t_14_16_prior_to_car_t_infusion_yes_no,  -->
<!--               bridging_therapy_yes_no, number_prior_lines_therapy,  -->
<!--               prior_auto_sct_yes_no,  -->
<!--               asct_within_12_weeks_prior_to_apheresis_yes_no,  -->
<!--               prior_allo_sct_yes_no, blenrep, any_bcma, bcma_ontrial,  -->
<!--               bcma_other, immuno, proteasome, doubleref, tripleref,  -->
<!--               pentaref, cart_cell_dose, infection_yes_no, tocilizumab_yes_no,  -->
<!--               steroid_use_yes_no, anakinra_yes_no, baseline_b2m, ecog_or_2_yes_no,  -->
<!--               renal_insufficiency_cr_cl_45_m_l_min_yes_no, lvef_45_percent_yes_no,  -->
<!--               anc_1000_u_l_yes_no, hemoglobin_8_g_d_l_yes_no, platelets_50k_yes_no, -->
<!--               h_o_or_presence_of_plasma_cell_leukemia_waldenstroms_poems_or_amyloidosis_yes_no -->
<!--               ), -->
<!--   probs = 0.5, -->
<!--   label_header = "**Median PFS**" -->
<!-- ) -->

<!-- # 3 month pfs rate -->
<!-- tbl2 <- list( -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ agecat,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ male_sex,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ sex,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ extramedullary_disease_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ disease_status_at_time_of_referral_relapsed_vs_refractory,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ plasma_cell_leukemia_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ amyloid_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ poems,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ non_secretory_mm_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ high_marrow_burden_50_percent,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ecog_at_consult,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ecog_at_ld,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ r_iss_at_car_t_infusion,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ cytogenetics,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ deletion_17p_prior_to_car_t_infusion_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ t_4_14_prior_to_car_t_infusion_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ t_14_16_prior_to_car_t_infusion_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ bridging_therapy_yes_no,  -->
<!--                    data = cart1), -->
<!--     # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ number_of_prior_lines_of_therapy,  -->
<!--     #                data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ number_prior_lines_therapy,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ prior_auto_sct_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ asct_within_12_weeks_prior_to_apheresis_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ prior_allo_sct_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ blenrep,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ any_bcma,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ bcma_ontrial,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ bcma_other,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ immuno,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ proteasome,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ doubleref,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ tripleref,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ pentaref,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ cart_cell_dose,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ infection_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ tocilizumab_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ steroid_use_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ anakinra_yes_no,  -->
<!--                    data = cart1), -->

<!--     # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ baseline_ferritin,  -->
<!--     #                data = cart1), -->
<!--     # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ baseline_crp,  -->
<!--     #                data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ baseline_b2m,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ecog_or_2_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ renal_insufficiency_cr_cl_45_m_l_min_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ lvef_45_percent_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ anc_1000_u_l_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ hemoglobin_8_g_d_l_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ platelets_50k_yes_no,  -->
<!--                    data = cart1), -->
<!--     survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ h_o_or_presence_of_plasma_cell_leukemia_waldenstroms_poems_or_amyloidosis_yes_no,  -->
<!--                    data = cart1) -->

<!--     # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ CRS_any, -->
<!--     #                data = cart1), -->
<!--     # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ CRS_gradecat, -->
<!--     #                data = cart1), -->
<!--     # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ICANS_any, -->
<!--     #                data = cart1), -->
<!--     # survfit(Surv(days_at_pfs_from_infusion, pfs_event) ~ ICANS_gradecat, -->
<!--     #                data = cart1) -->
<!--   ) %>% -->
<!--   tbl_survfit(times = c(3, 6), -->
<!--               label_header = "**PFS Rate at {time} Months**") -->

<!-- tbl_merge(list(tbl1, tbl2)) -->
<!-- ``` -->

<!-- P-value log rank -->
<!-- ```{r} -->
<!-- cart1 %>%  -->
<!--   select(agecat, male_sex, sex, extramedullary_disease_yes_no,  -->
<!--               disease_status_at_time_of_referral_relapsed_vs_refractory, -->
<!--               plasma_cell_leukemia_yes_no, amyloid_yes_no, poems, -->
<!--               non_secretory_mm_yes_no, high_marrow_burden_50_percent, -->
<!--               ecog_at_consult, ecog_at_ld, r_iss_at_car_t_infusion, -->
<!--               cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no, -->
<!--               t_4_14_prior_to_car_t_infusion_yes_no, -->
<!--               t_14_16_prior_to_car_t_infusion_yes_no, -->
<!--               bridging_therapy_yes_no, number_prior_lines_therapy, -->
<!--               prior_auto_sct_yes_no) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = cart1$days_at_pfs_from_infusion, event = cart1$pfs_event)), -->
<!--                  exponentiate = TRUE) %>%  -->
<!--     modify_column_hide(c(stat_n, estimate, ci)) %>%  -->
<!--     bold_p(t = .05)# %>% add_nevent(location = "level") %>% add_n(location = "level") -->

<!-- cart1 %>%  -->
<!--   select(asct_within_12_weeks_prior_to_apheresis_yes_no,  -->
<!--               prior_allo_sct_yes_no, blenrep, any_bcma, bcma_ontrial,  -->
<!--               bcma_other, immuno, proteasome, doubleref, tripleref,  -->
<!--               pentaref, cart_cell_dose, infection_yes_no, tocilizumab_yes_no,  -->
<!--               steroid_use_yes_no, anakinra_yes_no, baseline_b2m, ecog_or_2_yes_no,  -->
<!--               renal_insufficiency_cr_cl_45_m_l_min_yes_no, lvef_45_percent_yes_no,  -->
<!--               anc_1000_u_l_yes_no, hemoglobin_8_g_d_l_yes_no, platelets_50k_yes_no, -->
<!--               h_o_or_presence_of_plasma_cell_leukemia_waldenstroms_poems_or_amyloidosis_yes_no) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = cart1$days_at_pfs_from_infusion, event = cart1$pfs_event)), -->
<!--                  exponentiate = TRUE) %>%  -->
<!--     modify_column_hide(c(stat_n, estimate, ci)) %>%  -->
<!--     bold_p(t = .05)# %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- ``` -->

### 2023-11-22 cilta_cel/Manuscript analyses.Rmd
Add Rmd analysis

---
title: "Manuscript analyses"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type= "text/css">

.## Figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

## Table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(here)
library(tidyverse)
library(ggplot2)
library(gtsummary)
library(labelled)
library(DescTools)
library(patchwork)
library(ggbreak)
# library(survival)
library(survminer)
theme_set(theme_classic())
theme_gtsummary_compact()
```

```{r load}
# path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias")

Characteristics <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "CHARACTERISTICS AND OUTCOMES ", skip = 1)
Counts <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "COUNTS")
Infections <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "INFECTIONS")
Support <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "SUPPORT")
Pneumo_titers <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "BACTERIAL AND VIRAL TITERS")
Apheresis <- 
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "APHERESIS")
```

```{r join}
cart <- full_join(Characteristics, Counts, by = "PT Identifier") %>% 
  full_join(., Infections, by = "PT Identifier") %>% 
  full_join(., Support, by = "PT Identifier") %>% 
  full_join(., Pneumo_titers, by = "PT Identifier") %>% 
  # select(-`Date of leukapheresis.y`, `Date of leukapheresis` = `Date of leukapheresis.x`) %>% 
  full_join(., Apheresis, by = "PT Identifier") %>% 
  janitor::clean_names()
```

```{r exploratory function}
# check_data <- function(data){
#   
#   for(i in 1:length(colnames(data))) {
#     
#     if(class(data[[i]]) == "factor" | class(data[[i]]) == "character") {
#       
#       # print(data[i])
#       print(colnames(data[i]))
#       print(table(data[[i]]))
#     }
#     
#   }
# }
# 
# check_data(cart[2:50])
# check_data(cart[51:100])
# check_data(cart[101:150])
# check_data(cart[151:200]) # has < : "CRP Pre-Leukapheresis", "IgG day -5", "IgA day -5", "IgM day -5"
# check_data(cart[201:250]) # has < :"CRP day +21", "IgG day +30", "IgA day +30", "IgM day +30", "marrow_percent_cd138_day_30", "marrow % cellularity day +30", "CRP day +30", "CD19 day +90", "IgG day +90", "IgA day +90", "IgM day +90", "marrow %CD138 day +90", 
# # has > : "CD8 day +30", "CRP day +90"
# check_data(cart[251:300]) # has < : "CD19 day +180", "IgG day +180", "IgA day +180", "IgM day +180", "marrow % cellularity day +180", "CRP day +180"
# # has > : "marrow %CD138 day +180"
# check_data(cart[1:44, 301:353]) # need to see patient in Moffitt
```

```{r data cleaning}
cart <- cart %>% 
  # Fix letter case and missing
  mutate(across(where(is.character), ~ str_replace(., "NE|ND|N/A|Not done", NA_character_))) %>%
  mutate(across(c(where(is.character),
                  -c("r_iss_at_car_t_infusion")), 
                ~ str_to_sentence(.) )) %>%
  mutate(across(where(is.character), ~ str_replace(., "Unknown|unknown", NA_character_))) %>%
  # Create site variable
  mutate(site = case_when(
    str_detect(pt_identifier, "MCC") ~ "Moffitt",
    str_detect(pt_identifier, "CCT") ~ "Stanford",
    str_detect(pt_identifier, "KUMC") ~ "KUMC",
    str_detect(pt_identifier, "MDA") ~ "MD Anderson?",
    str_detect(pt_identifier, "Utah") ~ "Utah"
  )) %>%

  mutate(across(c("bm_plasma_cell_percent_at_pre_ld",
                  "high_marrow_burden_50_percent",
                  "marrow_percent_cd138_day_30",
                  # "marrow fibrosis day +30 (0, 1, 2, 3)",
                  # "marrow dysplasia day +30 (yes/no)"
                  "marrow_cellularity_baseline_normo_hypo_hyper",
                  "marrow_cellularity_day_30_normo_hypo_hyper",
                  "marrow_cellularity_day_90_normo_hypo_hyper",
                  "marrow_fibrosis_baseline_0_1_2_3",
                  "marrow_fibrosis_day_30_0_1_2_3",
                  "marrow_fibrosis_day_90_0_1_2_3",
                  "marrow_fibrosis_day_180_0_1_2_3",
                  "marrow_percent_cellularity_day_90",
                  # "marrow dysplasia day +90 (yes/no)",
                  "b2_microglobulin_day_180"), 
                ~ str_replace(., "Suboptimal", NA_character_))) %>%
  mutate(across(c("response_to_bridging_chemotherapy"), 
                ~ str_replace(., "Not evaluable", NA_character_)))
  # Marrow ----
cart1 <- cart %>% 
  mutate(marrow_cellularity_baseline_normo_hypo_hyper = case_when(
    marrow_cellularity_baseline_normo_hypo_hyper == "\"patchy\""                 ~ "hyper",
    TRUE                                                          ~ marrow_cellularity_baseline_normo_hypo_hyper
  )) %>%
  mutate(marrow_cellularity_day_30_normo_hypo_hyper = case_when(
    marrow_cellularity_day_30_normo_hypo_hyper == "aplastic"                    ~ "hypo",
    TRUE                                                          ~ marrow_cellularity_day_30_normo_hypo_hyper
  )) %>%
  # Separate variable cellularity
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Variable"                         ~ "Yes"
  ), .names = "is_variable_{.col}")) %>% 
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Pauci"                            ~ "Hypo",
    . == "Variable"                         ~ NA_character_,
    TRUE                                    ~ .
  ))) %>%

  mutate(across(c(starts_with("marrow_dysplasia_") & ends_with("yes_no")), ~ case_when(
    . == "0"                                ~ "No",
    . == "1"                                ~ "Yes",
    TRUE                                    ~ .
  ))) %>% 
  # mutate(marrow_percent_cellularity_day_30 = as.numeric(marrow_percent_cellularity_day_30)) %>% 
  # mutate(marrow_percent_cellularity_day_90 = as.numeric(marrow_percent_cellularity_day_90)) %>%

  # Age categories----
  mutate(agecat = case_when(
    age < 65                            ~ "< 65 years",
    age >= 65                           ~ "≥ 65 years"
  ),
  agecat = factor(agecat, levels = c("< 65 years", "≥ 65 years"))
  ) %>% 
  # Sex categories----
  mutate(sex = case_when(
    str_detect(sex, "M")                                          ~ "Male",
    TRUE                                                          ~ "Female"
  )) %>% 
  mutate(male_sex = case_when(
    str_detect(sex, "M")                                          ~ 1,
    TRUE                                                          ~ 0
  )) %>% 
  # Convert 0/1 to No/Yes----
  mutate_at(c(
              # "bm_plasma_cell_percent_at_pre_ld",
              # "high_marrow_burden_50_percent",
              # "ECOG > or = 2? (Yes, No)",
              # deletion_17p_prior_to_car_t_infusion_yes_no,
              # "t_4_14_prior_to_car_t_infusion_yes_no",
              # "t_14_16_prior_to_car_t_infusion_yes_no",
              # "steroid_use_yes_no", "tocilizumab_yes_no", "anakinra_yes_no",
              # "Bridging Therapy (Yes=1, No=0)",
              # "Received alkylating therapy with bridging (Yes=1, No=0)",
              # "Prior auto SCT (yes, no)",
              # "Prior Allo SCT within 6 months before apheresis",
              # "Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)",
              "need_for_g_csf_post_infus_yes_1_no_0",
              "need_for_ivig_yes_1_no_0",
              "cd34_stem_cell_boost_yes_1_no_0",
              "rbc_transfusion_within_30d_post_cart_yes_1_no_0", "plt_transfusion_within_30d_post_cart_yes_1_no_0", 
              "rbc_transfusion_30d_post_cart_yes_1_no_0", "plt_transfusion_30d_post_cart_yes_1_no_0"), 
            ~ case_when(
              . == 1                                              ~ "Yes",
              . == 0                                              ~ "No",
              TRUE                                                ~ NA_character_
            )) %>% 
  # ECOG
  # mutate(ecog_at_ld = case_when(
  #   ecog_at_ld == 0 | 
  #     ecog_at_ld == 1                       ~ "0-1",
  #   TRUE                                                          ~ ecog_at_ld
  # )) %>%

  # Cytogenetics ----
  mutate(cytogenetics = case_when(
    deletion_17p_prior_to_car_t_infusion_yes_no == "Yes" | 
      t_4_14_prior_to_car_t_infusion_yes_no == "Yes" | 
      t_14_16_prior_to_car_t_infusion_yes_no == "Yes"             ~ "Yes",
    deletion_17p_prior_to_car_t_infusion_yes_no == "No" &
      t_4_14_prior_to_car_t_infusion_yes_no == "No" &
      t_14_16_prior_to_car_t_infusion_yes_no == "No"               ~ "No",
    TRUE                                                           ~ NA_character_
  )) %>%

  # Refractory status ----
  mutate(immuno = case_when(
    lenalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" |
      pomalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory"           ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(proteasome = case_when(
    bortezomib_exposed_vs_refractory_vs_not_exposed == "Refractory" |
      carfilzomib_exposed_vs_refractory_vs_not_exposed == "Refractory"            ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(dara = case_when(
    daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed == "Refractory"            ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(doubleref = case_when(
    proteasome == "Yes" &
      immuno == "Yes"                                              ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(tripleref = case_when(
    proteasome == "Yes" &
      immuno == "Yes" &
      daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed == "Refractory"          ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(pentaref = case_when(
    bortezomib_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      carfilzomib_exposed_vs_refractory_vs_not_exposed == "Refractory" &
      lenalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      pomalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed == "Refractory"          ~ "Yes",
    TRUE                                                           ~ "No"
  )) %>% 
  mutate(number_prior_lines_therapy = case_when(
    number_of_prior_lines_of_therapy <= 4                        ~ "≤ 4",
    number_of_prior_lines_of_therapy > 4                         ~ "> 4"
  )) %>%

  # CRS ----
  # censored days > 100 to 100
  # mutate(across(c(`Day of onset of CRS relative to infusion`,
  #                 `Day of Max CRS (relative to infusion)`,
  #                 `Day of onset of ICANS relative to infusion`,
  #                 `Day of Max ICANS (relative to infusion)`), ~ case_when(
  #   . > 100                                                       ~ 100,
  #   TRUE                                                          ~ as.numeric(.)
  # ))) %>% 
  mutate(CRS_any = ifelse(max_crs_grade_0_5 == 0, "No", "Yes"),
       CRS_any2 = ifelse(CRS_any == "No", 0, 1),
       CRS_gradecat = case_when(
         max_crs_grade_0_5 == 0                             ~ "No CRS",
         max_crs_grade_0_5 == 1                             ~ "Grade 1 or 2",
         max_crs_grade_0_5 == 2                             ~ "Grade 1 or 2",
         max_crs_grade_0_5 >= 3                             ~ "Grade ≥3"),
       CRS_gradecat = factor(CRS_gradecat, levels = c("No CRS", "Grade 1 or 2", "Grade ≥3")),
       gr3_CRS = case_when(
         max_crs_grade_0_5 %in% c(0:2)                      ~ "Grade <3",
         max_crs_grade_0_5 %in% c(3:5)                      ~ "Grade ≥3",
         TRUE                                                   ~ NA_character_
       )) %>% 
  mutate(gr2_CRS = case_when(
    max_crs_grade_0_5 %in% c(0:1)                      ~ "Grade <2",
    max_crs_grade_0_5 %in% c(2:5)                      ~ "Grade ≥2",
    TRUE                                               ~ NA_character_
  )) %>%
  mutate(day_of_onset_crs_relative_to_infusion = 
           interval(start = date_of_car_t_infusion, end = date_of_onset_of_crs) /
           duration(n =1, unit = "days")
  ) %>% 
  mutate(day_of_max_crs_relative_to_infusion = 
           interval(start = date_of_car_t_infusion, end = date_of_max_crs) /
           duration(n =1, unit = "days")
  ) %>% 
  mutate(day_of_onset_icans_relative_to_infusion = 
           interval(start = date_of_car_t_infusion, end = date_of_onset_of_icans) /
           duration(n =1, unit = "days")
  ) %>% 
  mutate(day_of_max_icans_relative_to_infusion = 
           interval(start = date_of_car_t_infusion, end = date_of_max_icans) /
           duration(n =1, unit = "days")
  ) %>%

  # ICANS 
  mutate(ICANS_any = ifelse(max_icans == 0, "No", "Yes"),
       ICANS_any2 = ifelse(ICANS_any == "No", 0, 1),
       ICANS_gradecat = case_when(
         max_icans == 0                                ~ "No ICANS",
         max_icans == 1                                ~ "Grade 1 or 2",
         max_icans == 2                                ~ "Grade 1 or 2",
         max_icans >= 3                                ~ "Grade ≥3"),
       ICANS_gradecat = factor(ICANS_gradecat, levels = c("No ICANS", "Grade 1 or 2", "Grade ≥3")),
       gr3_ICANS = case_when(
         max_icans %in% c(0:2)                         ~ "Grade <3",
         max_icans %in% c(3:5)                         ~ "Grade ≥3",
         TRUE                                          ~ NA_character_
       )) %>% 
  mutate(gr2_ICANS = case_when(
    max_icans %in% c(0:1)                              ~ "Grade <2",
    max_icans %in% c(2:5)                              ~ "Grade ≥2",
    TRUE                                               ~ NA_character_
  )) %>%

  # Infection ----
  mutate(any_infection = infection_yes_1_no_0
  ) %>% 
  mutate(any_sevinfection = severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0
  )

  # mutate(access_type = case_when(
  #   access_type == "Femoral"                                    ~ "Non-tunneled",
  #   access_type == "AVF"                                        ~ "Peripheral",
  #   TRUE                                                          ~ access_type
  # )) %>% 
cart1 <- cart1 %>% 
  # Leukopenia ----
  mutate(Leukopenia_apheresis = case_when(
    wbc_apheresis < 4                                           ~ "Yes",
    is.na(wbc_apheresis)                                        ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(`Leukopenia_-5d` = case_when(
    wbc_day_5 < 4                                               ~ "Yes",
    is.na(wbc_day_5)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Leukopenia_0d = case_when(
    wbc_day_0_k_u_l < 4                                         ~ "Yes",
    is.na(wbc_day_0_k_u_l)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Leukopenia_7d = case_when(
    wbc_day_7 < 4                                               ~ "Yes",
    is.na(wbc_day_7)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Leukopenia_14d = case_when(
    wbc_day_14 < 4                                              ~ "Yes",
    is.na(wbc_day_14)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Leukopenia_21d = case_when(
    wbc_day_21 < 4                                              ~ "Yes",
    is.na(wbc_day_21)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Leukopenia_30d = case_when(
    wbc_day_30 < 4                                              ~ "Yes",
    is.na(wbc_day_30)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  # mutate(Leukopenia_60d = case_when(
  #   wbc_day_60 < 4                                             ~ "Yes",
  #   is.na(wbc_day_60)                                          ~ NA_character_,
  #   TRUE                                                          ~ "No"
  # )) %>% 
  mutate(Leukopenia_90d = case_when(
    wbc_day_90 < 4                                              ~ "Yes",
    is.na(wbc_day_90)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Leukopenia_180d = case_when(
    wbc_day_180 < 4                                             ~ "Yes",
    is.na(wbc_day_180)                                          ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Leukopenia_apheresis = case_when(
    wbc_apheresis < 2                                           ~ "Yes",
    is.na(wbc_apheresis)                                        ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(`gr3_Leukopenia_-5d` = case_when(
    wbc_day_5 < 2                                               ~ "Yes",
    is.na(wbc_day_5)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Leukopenia_0d = case_when(
    wbc_day_0_k_u_l < 2                                         ~ "Yes",
    is.na(wbc_day_0_k_u_l)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Leukopenia_7d = case_when(
    wbc_day_7 < 2                                               ~ "Yes",
    is.na(wbc_day_7)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Leukopenia_14d = case_when(
    wbc_day_14 < 2                                              ~ "Yes",
    is.na(wbc_day_14)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Leukopenia_21d = case_when(
    wbc_day_21 < 2                                              ~ "Yes",
    is.na(wbc_day_21)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Leukopenia_30d = case_when(
    wbc_day_30 < 2                                              ~ "Yes",
    is.na(wbc_day_30)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  # mutate(gr3_Leukopenia_60d = case_when(
  #   wbc_day_60 < 2                                             ~ "Yes",
  #   is.na(wbc_day_60)                                          ~ NA_character_,
  #   TRUE                                                          ~ "No"
  # )) %>% 
  mutate(gr3_Leukopenia_90d = case_when(
    wbc_day_90 < 2                                              ~ "Yes",
    is.na(wbc_day_90)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Leukopenia_180d = case_when(
    wbc_day_180 < 2                                             ~ "Yes",
    is.na(wbc_day_180)                                          ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%

  # Neutropenia ----
  mutate(Neutropenia_apheresis = case_when(
    anc_apheresis < 1.8                                         ~ "Yes",
    is.na(anc_apheresis)                                        ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(`Neutropenia_-5d` = case_when(
    anc_day_5_k_ul < 1.8                                        ~ "Yes",
    is.na(anc_day_5_k_ul)                                       ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Neutropenia_0d = case_when(
    anc_day_0_k_u_l < 1.8                                       ~ "Yes",
    is.na(anc_day_0_k_u_l)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Neutropenia_7d = case_when(
    anc_day_7 < 1.8                                             ~ "Yes",
    is.na(anc_day_7)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Neutropenia_14d = case_when(
    anc_day_14 < 1.8                                            ~ "Yes",
    is.na(anc_day_14)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Neutropenia_21d = case_when(
    anc_day_21 < 1.8                                            ~ "Yes",
    is.na(anc_day_21)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Neutropenia_30d = case_when(
    anc_day_30 < 1.8                                            ~ "Yes",
    is.na(anc_day_30)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  # mutate(Neutropenia_60d = case_when(
  #   anc_day_60 < 1.8                                             ~ "Yes",
  #   is.na(anc_day_60)                                          ~ NA_character_,
  #   TRUE                                                          ~ "No"
  # )) %>% 
  mutate(Neutropenia_90d = case_when(
    anc_day_90 < 1.8                                            ~ "Yes",
    is.na(anc_day_90)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Neutropenia_180d = case_when(
    anc_day_180 < 1.8                                           ~ "Yes",
    is.na(anc_day_180)                                          ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Neutropenia_apheresis = case_when(
    anc_apheresis < 1                                           ~ "Yes",
    is.na(anc_apheresis)                                        ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(`gr3_Neutropenia_-5d` = case_when(
    anc_day_5_k_ul < 1                                          ~ "Yes",
    is.na(anc_day_5_k_ul)                                       ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Neutropenia_0d = case_when(
    anc_day_0_k_u_l < 1                                         ~ "Yes",
    is.na(anc_day_0_k_u_l)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Neutropenia_7d = case_when(
    anc_day_7 < 1                                               ~ "Yes",
    is.na(anc_day_7)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Neutropenia_14d = case_when(
    anc_day_14 < 1                                              ~ "Yes",
    is.na(anc_day_14)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Neutropenia_21d = case_when(
    anc_day_21 < 1                                              ~ "Yes",
    is.na(anc_day_21)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Neutropenia_30d = case_when(
    anc_day_30 < 1                                              ~ "Yes",
    is.na(anc_day_30)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  # mutate(gr3_Neutropenia_60d = case_when(
  #   anc_day_60 < 1                                             ~ "Yes",
  #   is.na(anc_day_60)                                          ~ NA_character_,
  #   TRUE                                                          ~ "No"
  # )) %>% 
  mutate(gr3_Neutropenia_90d = case_when(
    anc_day_90 < 1                                              ~ "Yes",
    is.na(anc_day_90)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Neutropenia_180d = case_when(
    anc_day_180 < 1                                             ~ "Yes",
    is.na(anc_day_180)                                          ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Neutropenia_gr1 = case_when(
    (anc_day_7 < 1.8 &
       anc_day_7 > 1.5) |
      (anc_day_30 < 1.8 &
         anc_day_30 > 1.5) |
      # (anc_day_60 < 1.8 &
      #    anc_day_60 > 1.5) |
      (anc_day_180 < 1.8 &
         anc_day_180 > 1.5) |
      (anc_day_90 < 1.8 &
         anc_day_90 > 1.5)                                      ~ "Yes",
    is.na(anc_day_7) |
      is.na(anc_day_30) |
      # is.na(anc_day_60) |
      is.na(anc_day_90)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Neutropenia_gr2 = case_when(
    (anc_day_7 < 1.5 &
       anc_day_7 > 1) |
      (anc_day_30 < 1.5 &
         anc_day_30 > 1) |
      (anc_day_180 < 1.5 &
         anc_day_180 > 1) |
      # (anc_day_60 < 1.5 &
      #    anc_day_60 > 1) |
      (anc_day_90 < 1.5 &
         anc_day_90 > 1)                                        ~ "Yes",
    is.na(anc_day_7) |
      is.na(anc_day_30) |
      # is.na(anc_day_60) |
      is.na(anc_day_90)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Neutropenia_gr3 = case_when(
    anc_day_7 < 1 |
      anc_day_30 < 1 |
      anc_day_180 < 1 |
      # anc_day_60 < 1 |
      anc_day_90 < 1                                            ~ "Yes",
    is.na(anc_day_7) |
      is.na(anc_day_30) |
      is.na(anc_day_180) |
      # is.na(anc_day_60) |
      is.na(anc_day_90)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(any_neutropenia = case_when(
    Neutropenia_gr1 == "Yes" |
      Neutropenia_gr2 == "Yes" |
      Neutropenia_gr3 == "Yes"                                  ~ "Yes",
    is.na(Neutropenia_gr1) |
      is.na(Neutropenia_gr2) |
      is.na(Neutropenia_gr3)                                    ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(severe_neutro_30beyond = case_when(
    anc_day_30 < 1 |
    anc_day_180 < 1 |
      # anc_day_60 < 1 |
      anc_day_90 < 1                                            ~ "Yes",
    is.na(anc_day_30) |
    is.na(anc_day_180) |
      # is.na(anc_day_60) |
      is.na(anc_day_90)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%

  # Anemia ----
  mutate(Anemia_apheresis = case_when(
    hb_apheresis < 11.4                                         ~ "Yes",
    is.na(hb_apheresis)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(`Anemia_-5d` = case_when(
    hb_day_5 < 11.4                                             ~ "Yes",
    is.na(hb_day_5)                                             ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Anemia_0d = case_when(
    hb_day_0_k_u_l < 11.4                                       ~ "Yes",
    is.na(hb_day_0_k_u_l)                                       ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Anemia_7d = case_when(
    hb_day_7 < 11.4                                             ~ "Yes",
    is.na(hb_day_7)                                             ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  mutate(Anemia_14d = case_when(
    hb_day_14 < 11.4                                            ~ "Yes",
    is.na(hb_day_14)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Anemia_21d = case_when(
    hb_day_21 < 11.4                                            ~ "Yes",
    is.na(hb_day_21)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Anemia_30d = case_when(
    hb_day_30 < 11.4                                            ~ "Yes",
    is.na(hb_day_30)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  # mutate(Anemia_60d = case_when(
  #   hb_day_60 < 11.4                                             ~ "Yes",
  #   is.na(hb_day_60)                                          ~ NA_character_,
  #   TRUE                                                          ~ "No"
  # )) %>%
  mutate(Anemia_90d = case_when(
    hb_day_90 < 11.4                                            ~ "Yes",
    is.na(hb_day_90)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%             
  mutate(Anemia_180d = case_when(
    hb_day_180 < 11.4                                           ~ "Yes",
    is.na(hb_day_180)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  mutate(gr3_Anemia_apheresis = case_when(
    hb_apheresis < 8                                            ~ "Yes",
    is.na(hb_apheresis)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(`gr3_Anemia_-5d` = case_when(
    hb_day_5 < 8                                                ~ "Yes",
    is.na(hb_day_5)                                             ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Anemia_0d = case_when(
    hb_day_0_k_u_l < 8                                          ~ "Yes",
    is.na(hb_day_0_k_u_l)                                       ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Anemia_7d = case_when(
    hb_day_7 < 8                                                ~ "Yes",
    is.na(hb_day_7)                                             ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  mutate(gr3_Anemia_14d = case_when(
    hb_day_14 < 8                                               ~ "Yes",
    is.na(hb_day_14)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Anemia_21d = case_when(
    hb_day_21 < 8                                               ~ "Yes",
    is.na(hb_day_21)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Anemia_30d = case_when(
    hb_day_30 < 8                                               ~ "Yes",
    is.na(hb_day_30)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  # mutate(gr3_Anemia_60d = case_when(
  #   hb_day_60 < 8                                             ~ "Yes",
  #   is.na(hb_day_60)                                          ~ NA_character_,
  #   TRUE                                                          ~ "No"
  # )) %>%
  mutate(gr3_Anemia_90d = case_when(
    hb_day_90 < 8                                               ~ "Yes",
    is.na(hb_day_90)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  mutate(gr3_Anemia_180d = case_when(
    hb_day_180 < 8                                              ~ "Yes",
    is.na(hb_day_180)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  mutate(Anemia_gr1 = case_when(
    (hb_day_7 < 11.4 &
       hb_day_7 > 10) |
      (hb_day_30 < 11.4 &
         hb_day_30 > 10) |
      # (hb_day_60 < 11.4 &
         # hb_day_60 > 10) |
      (hb_day_180 < 11.4 &
         hb_day_180 > 10) |
      (hb_day_90 < 11.4 &
         hb_day_90 > 10)                                        ~ "Yes",
    is.na(hb_day_7) |
      is.na(hb_day_30) |
      # is.na(hb_day_60) |
      is.na(hb_day_90)                                          ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Anemia_gr2 = case_when(
    (hb_day_7 < 10 &
       hb_day_7 > 8) |
      (hb_day_30 < 10 &
         hb_day_30 > 8) |
      # (hb_day_60 < 10 &
         # hb_day_60 > 8) |
      (hb_day_180 < 10 &
         hb_day_180 > 8) |
      (hb_day_90 < 10 &
         hb_day_90 > 8)                                         ~ "Yes",
    is.na(hb_day_7) |
      is.na(hb_day_30) |
      # is.na(hb_day_60) |
      is.na(hb_day_90)                                          ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Anemia_gr3 = case_when(
    hb_day_7 < 8 |
      hb_day_30 < 8 |
      # hb_day_60 < 8 |
      hb_day_180 < 8 |
      hb_day_90 < 8                                             ~ "Yes",
    is.na(hb_day_7) |
      is.na(hb_day_30) |
      # is.na(hb_day_60) |
      is.na(hb_day_180) |
      is.na(hb_day_90)                                          ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(severe_anemia_30beyond = case_when(
    hb_day_30 < 8 |
      # hb_day_60 < 8 |
      hb_day_180 < 8 |
      hb_day_90 < 8                                             ~ "Yes",
    is.na(hb_day_30) |
      # is.na(hb_day_60) |
      is.na(hb_day_180) |
      is.na(hb_day_90)                                          ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(any_anemia = case_when(
    Anemia_gr1 == "Yes" |
      Anemia_gr2 == "Yes" |
      Anemia_gr3 == "Yes"                                       ~ "Yes",
    is.na(Anemia_gr1) |
      is.na(Anemia_gr2) |
      is.na(Anemia_gr3)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%

  # Thrombocytopenia----
  mutate(Thrombocytopenia_apheresis = case_when(
    plt_apheresis < 143                                         ~ "Yes",
    is.na(plt_apheresis)                                        ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(`Thrombocytopenia_-5d` = case_when(
    plt_day_5_k_ul < 143                                        ~ "Yes",
    is.na(plt_day_5_k_ul)                                       ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Thrombocytopenia_0d = case_when(
    plt_day_0_k_u_l < 143                                       ~ "Yes",
    is.na(plt_day_0_k_u_l)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Thrombocytopenia_7d = case_when(
    plt_day_7 < 143                                             ~ "Yes",
    is.na(plt_day_7)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  mutate(Thrombocytopenia_14d = case_when(
    plt_day_14 < 143                                            ~ "Yes",
    is.na(plt_day_14)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Thrombocytopenia_21d = case_when(
    plt_day_21 < 143                                            ~ "Yes",
    is.na(plt_day_21)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Thrombocytopenia_30d = case_when(
    plt_day_30 < 143                                            ~ "Yes",
    is.na(plt_day_30)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  # mutate(Thrombocytopenia_60d = case_when(
  #   plt_day_60 < 143                                             ~ "Yes",
  #   is.na(plt_day_60)                                          ~ NA_character_,
  #   TRUE                                                          ~ "No"
  # )) %>%
  mutate(Thrombocytopenia_90d = case_when(
    plt_day_90 < 143                                            ~ "Yes",
    is.na(plt_day_90)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  mutate(Thrombocytopenia_180d = case_when(
    plt_day_180 < 143                                           ~ "Yes",
    is.na(plt_day_180)                                          ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  mutate(gr3_Thrombocytopenia_apheresis = case_when(
    plt_apheresis < 50                                          ~ "Yes",
    is.na(plt_apheresis)                                        ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(`gr3_Thrombocytopenia_-5d` = case_when(
    plt_day_5_k_ul < 50                                         ~ "Yes",
    is.na(plt_day_5_k_ul)                                       ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Thrombocytopenia_0d = case_when(
    plt_day_0_k_u_l < 50                                        ~ "Yes",
    is.na(plt_day_0_k_u_l)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Thrombocytopenia_7d = case_when(
    plt_day_7 < 50                                              ~ "Yes",
    is.na(plt_day_7)                                            ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  mutate(gr3_Thrombocytopenia_14d = case_when(
    plt_day_14 < 50                                             ~ "Yes",
    is.na(plt_day_14)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Thrombocytopenia_21d = case_when(
    plt_day_21 < 50                                             ~ "Yes",
    is.na(plt_day_21)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Thrombocytopenia_30d = case_when(
    plt_day_30 < 50                                             ~ "Yes",
    is.na(plt_day_30)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  # mutate(gr3_Thrombocytopenia_60d = case_when(
  #   plt_day_60 < 50                                             ~ "Yes",
  #   is.na(plt_day_60)                                          ~ NA_character_,
  #   TRUE                                                          ~ "No"
  # )) %>%
  mutate(gr3_Thrombocytopenia_90d = case_when(
    plt_day_90 < 50                                             ~ "Yes",
    is.na(plt_day_90)                                           ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_Thrombocytopenia_180d = case_when(
    plt_day_180 < 50                                            ~ "Yes",
    is.na(plt_day_180)                                          ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Thrombocytopenia_gr1 = case_when(
    (plt_day_7 < 143 &
       plt_day_7 > 75) |
      (plt_day_30 < 143 &
         plt_day_30 > 75) |
      # (plt_day_60 < 143 &
         # plt_day_60 > 75) |
      (plt_day_180 < 143 &
         plt_day_180 > 75) |
      (plt_day_90 < 143 &
         plt_day_90 > 75)                                       ~ "Yes",
    is.na(plt_day_7) |
      is.na(plt_day_30) |
      # is.na(plt_day_60) |
      is.na(plt_day_180) |
      is.na(plt_day_90)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Thrombocytopenia_gr2 = case_when(
    (plt_day_7 < 75 &
       plt_day_7 > 50) |
      (plt_day_30 < 75 &
         plt_day_30 > 50) |
      # (plt_day_60 < 75 &
         # plt_day_60 > 50) |
      (plt_day_180 < 75 &
         plt_day_180 > 50) |
      (plt_day_90 < 75 &
         plt_day_90 > 50)                                       ~ "Yes",
    is.na(plt_day_7) |
      is.na(plt_day_30) |
      # is.na(plt_day_60) |
      is.na(plt_day_180) |
      is.na(plt_day_90)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(Thrombocytopenia_gr3 = case_when(
    plt_day_7 < 50 |
      plt_day_30 < 50 |
      # plt_day_60 < 50 |
      plt_day_180 < 50 |
      plt_day_90 < 50                                           ~ "Yes",
    is.na(plt_day_7) |
      is.na(plt_day_30) |
      is.na(plt_day_180) |
      # is.na(plt_day_60) |
      is.na(plt_day_90)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(severe_throm_30beyond = case_when(
    plt_day_30 < 50 |
      # plt_day_60 < 50 |
      plt_day_180 < 50 |
      plt_day_90 < 50                                           ~ "Yes",
    is.na(plt_day_30) |
      # is.na(plt_day_60) |
      is.na(plt_day_180) |
      is.na(plt_day_90)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(any_thrombo = case_when(
    Thrombocytopenia_gr1 == "Yes" |
      Thrombocytopenia_gr2 == "Yes" |
      Thrombocytopenia_gr3 == "Yes"                             ~ "Yes",
    is.na(Thrombocytopenia_gr1) |
      is.na(Thrombocytopenia_gr2) |
      is.na(Thrombocytopenia_gr3)                               ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%

  # Cytopenia ----
  mutate(cytopenia_apheresis = case_when(
    wbc_apheresis < 4 | 
      anc_apheresis < 1.8 | 
      hb_apheresis < 11.4 | 
      plt_apheresis < 143                                       ~ "Yes",
    is.na(wbc_apheresis) |
      is.na(anc_apheresis) |
      is.na(hb_apheresis) |
      is.na(plt_apheresis)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(`cytopenia_-5d` = case_when(
    wbc_day_5 < 4 | 
      anc_day_5_k_ul < 1.8 | 
      hb_day_5 < 11.4 | 
      plt_day_5_k_ul < 143                                      ~ "Yes",
    is.na(wbc_day_5) |
      is.na(anc_day_5_k_ul) |
      is.na(hb_day_5) |
      is.na(plt_day_5_k_ul)                                     ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(cytopenia_0d = case_when(
    wbc_day_0_k_u_l < 4 | 
      anc_day_0_k_u_l < 1.8 | 
      hb_day_0_k_u_l < 11.4 | 
      plt_day_0_k_u_l < 143                                     ~ "Yes",
    is.na(wbc_day_0_k_u_l) |
      is.na(anc_day_0_k_u_l) |
      is.na(hb_day_0_k_u_l) |
      is.na(plt_day_0_k_u_l)                                    ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(cytopenia_d7 = case_when(
    Anemia_7d == "Yes" | Thrombocytopenia_7d == "Yes" | 
      Neutropenia_7d == "Yes"                                   ~ "Yes",
    is.na(Anemia_7d) | is.na(Thrombocytopenia_7d) | 
      is.na(Neutropenia_7d)                                     ~ NA_character_,
    TRUE ~ "No"
  )) %>%
  mutate(cytopenia_14d = case_when(
    wbc_day_14 < 4 | 
      anc_day_14 < 1.8 | 
      hb_day_14 < 11.4 | 
      plt_day_14 < 143                                          ~ "Yes",
    is.na(wbc_day_14) |
      is.na(anc_day_14) |
      is.na(hb_day_14) |
      is.na(plt_day_14)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(cytopenia_21d = case_when(
    wbc_day_21 < 4 | 
      anc_day_21 < 1.8 | 
      hb_day_21 < 11.4 | 
      plt_day_21 < 143                                          ~ "Yes",
    is.na(wbc_day_21) |
      is.na(anc_day_21) |
      is.na(hb_day_21) |
      is.na(plt_day_21)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(cytopenia_d30 = case_when(
    Anemia_30d == "Yes" | Thrombocytopenia_30d == "Yes" | 
      Neutropenia_30d == "Yes"                                  ~ "Yes",
    is.na(Anemia_30d) | is.na(Thrombocytopenia_30d) | 
      is.na(Neutropenia_30d)                                    ~ NA_character_,
    TRUE ~ "No"
  )) %>%
  # mutate(cytopenia_d60 = case_when(
  #   Anemia_60d == "Yes" | Thrombocytopenia_60d == "Yes" | Neutropenia_60d == "Yes" ~ "Yes",
  #   is.na(Anemia_60d) | is.na(Thrombocytopenia_60d) | is.na(Neutropenia_60d) ~ NA_character_,
  #   TRUE ~ "No"
  # )) %>%
  mutate(cytopenia_d90 = case_when(
    Anemia_90d == "Yes" | Thrombocytopenia_90d == "Yes" | 
      Neutropenia_90d == "Yes"                                  ~ "Yes",
    is.na(Anemia_90d) | is.na(Thrombocytopenia_90d) | 
      is.na(Neutropenia_90d)                                    ~ NA_character_,
    TRUE ~ "No"
  )) %>%
  mutate(cytopenia_d180 = case_when(
    Anemia_180d == "Yes" | Thrombocytopenia_180d == "Yes" | 
      Neutropenia_180d == "Yes"                                 ~ "Yes",
    is.na(Anemia_180d) | is.na(Thrombocytopenia_180d) | 
      is.na(Neutropenia_180d)                                   ~ NA_character_,
    TRUE ~ "No"
  )) %>%

  mutate(`gr3_cytopenia_≥30d` = case_when(
    anc_day_30 < 1 |
      hb_day_30 < 8 |
      plt_day_30 < 50 |
      # anc_day_60 < 1 |
      # hb_day_60 < 8 |
      # plt_day_60 < 50 |
      anc_day_180 < 1 |
      hb_day_180 < 8 |
      plt_day_180 < 50 |
      anc_day_90 < 1 |
      hb_day_90 < 8 |
      plt_day_90 < 50                                           ~ "Yes",
    is.na(anc_day_30) |
      is.na(hb_day_30) |
      is.na(plt_day_30) |
      # is.na(anc_day_60) |
      # is.na(hb_day_60) |
      # is.na(plt_day_60) |
      is.na(anc_day_180) |
      is.na(hb_day_180) |
      is.na(plt_day_180) |
      is.na(anc_day_90) |
      is.na(hb_day_90) |
      is.na(plt_day_90)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
   mutate(gr3_cytopenia_apheresis = case_when(
    wbc_apheresis < 2 | 
      anc_apheresis < 1 | 
      hb_apheresis < 8 | 
      plt_apheresis < 50                                        ~ "Yes",
    is.na(wbc_apheresis) |
      is.na(anc_apheresis) |
      is.na(hb_apheresis) |
      is.na(plt_apheresis)                                      ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(`gr3_cytopenia_-5d` = case_when(
    wbc_day_5 < 2 | 
      anc_day_5_k_ul < 1 | 
      hb_day_5 < 8 | 
      plt_day_5_k_ul < 50                                       ~ "Yes",
    is.na(wbc_day_5) |
      is.na(anc_day_5_k_ul) |
      is.na(hb_day_5) |
      is.na(plt_day_5_k_ul)                                     ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_cytopenia_0d = case_when(
    wbc_day_0_k_u_l < 2 | 
      anc_day_0_k_u_l < 1 | 
      hb_day_0_k_u_l < 8 | 
      plt_day_0_k_u_l < 50                                      ~ "Yes",
    is.na(wbc_day_0_k_u_l) |
      is.na(anc_day_0_k_u_l) |
      is.na(hb_day_0_k_u_l) |
      is.na(plt_day_0_k_u_l)                                    ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_cytopenia_d7 = case_when(
    gr3_Anemia_7d == "Yes" | gr3_Thrombocytopenia_7d == "Yes" | 
      gr3_Neutropenia_7d == "Yes"                               ~ "Yes",
    is.na(gr3_Anemia_7d) | is.na(gr3_Thrombocytopenia_7d) | 
      is.na(gr3_Neutropenia_7d)                                 ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  mutate(gr3_cytopenia_14d = case_when(
    wbc_day_14 < 2 | 
      anc_day_14 < 1 | 
      hb_day_14 < 8 | 
      plt_day_14 < 50                                           ~ "Yes",
    is.na(wbc_day_14) |
      is.na(anc_day_14) |
      is.na(hb_day_14) |
      is.na(plt_day_14)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_cytopenia_21d = case_when(
    wbc_day_21 < 2 | 
      anc_day_21 < 1 | 
      hb_day_21 < 8 | 
      plt_day_21 < 50                                           ~ "Yes",
    is.na(wbc_day_21) |
      is.na(anc_day_21) |
      is.na(hb_day_21) |
      is.na(plt_day_21)                                         ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_cytopenia_d30 = case_when(
    gr3_Anemia_30d == "Yes" | gr3_Thrombocytopenia_30d == "Yes" | 
      gr3_Neutropenia_30d == "Yes"                              ~ "Yes",
    is.na(gr3_Anemia_30d) | is.na(gr3_Thrombocytopenia_30d) | 
      is.na(gr3_Neutropenia_30d)                                ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>%
  # mutate(gr3_cytopenia_d60 = case_when(
  #   gr3_Anemia_60d == "Yes" | gr3_Thrombocytopenia_60d == "Yes" | gr3_Neutropenia_60d == "Yes" ~ "Yes",
  #   is.na(gr3_Anemia_60d) | is.na(gr3_Thrombocytopenia_60d) | is.na(gr3_Neutropenia_60d) ~ NA_character_,
  #   TRUE ~ "No"
  # )) %>%
  mutate(gr3_cytopenia_d90 = case_when(
    gr3_Anemia_90d == "Yes" | gr3_Thrombocytopenia_90d == "Yes" | 
      gr3_Neutropenia_90d == "Yes"                              ~ "Yes",
    is.na(gr3_Anemia_90d) | is.na(gr3_Thrombocytopenia_90d) | 
      is.na(gr3_Neutropenia_90d)                                ~ NA_character_,
    TRUE                                                        ~ "No"
  )) %>% 
  mutate(gr3_cytopenia_d180 = case_when(
    gr3_Anemia_180d == "Yes" | gr3_Thrombocytopenia_180d == "Yes" |
      gr3_Neutropenia_180d == "Yes"                             ~ "Yes",
    is.na(gr3_Anemia_180d) | is.na(gr3_Thrombocytopenia_180d) |
      is.na(gr3_Neutropenia_180d)                               ~ NA_character_,
    TRUE                                                        ~ "No"
  ))

cart2 <- cart1 %>% 
  # MRD----
  mutate_at(c("day_30_mrd_by_clono_seq_positive_vs_negative",
              "day_30_mrd_by_flow_positive_vs_negative",
              "x3_month_mrd_by_clono_seq_positive_vs_negative",
              "x3_month_mrd_by_flow_positive_vs_negative"),
            ~ case_when(
              . == "Positive"                                     ~ "Positive",
              . == "Negative"                                     ~ "Negative",
              TRUE                                                ~ NA_character_
            )) %>%
  mutate(MRD_30days = coalesce(day_30_mrd_by_clono_seq_positive_vs_negative, 
                               day_30_mrd_by_flow_positive_vs_negative
  )) %>%
  mutate(MRD_90days = coalesce(x3_month_mrd_by_clono_seq_positive_vs_negative,
                               x3_month_mrd_by_flow_positive_vs_negative
  )) %>%

  # Day 30 response ----
  mutate(day_30_response_s_cr_cr_vgpr_pr_sd_pd = case_when(
    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "evaluable")   ~ NA_character_,
    TRUE           ~ day_30_response_s_cr_cr_vgpr_pr_sd_pd
  )) %>% 
  mutate(ORR_30days = case_when(
    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "CR")   ~ "ORR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "PR")   ~ "ORR",
    is.na(day_30_response_s_cr_cr_vgpr_pr_sd_pd)              ~ NA_character_,
    TRUE                                                                        ~ "PD/SD/MR"
  )) %>% 
  mutate(day30_response = case_when(
    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "sCR")	       ~ "sCR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	         ~ "CR",
    is.na(day_30_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
    TRUE           ~ day_30_response_s_cr_cr_vgpr_pr_sd_pd
  )) %>% 
  mutate(day30_response_group = case_when(
    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	         ~ "CR or sCR",
    is.na(day_30_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
    TRUE           ~ day_30_response_s_cr_cr_vgpr_pr_sd_pd
  )) %>% 
  mutate(day30_response_sCRvsOthers = case_when(
    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	         ~ "CR or sCR",
    is.na(day_30_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
    TRUE           ~ "Others"
  )) %>% 
  # Day 90 response ----
  mutate(x3_month_response_s_cr_cr_vgpr_pr_sd_pd = case_when(
    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, 
               "evaluable|done")                                     ~ NA_character_,
    TRUE           ~ x3_month_response_s_cr_cr_vgpr_pr_sd_pd
  )) %>% 
  mutate(ORR_90days = case_when(
    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")    ~ "ORR",
    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "PR")    ~ "ORR",
    is.na(x3_month_response_s_cr_cr_vgpr_pr_sd_pd)               ~ NA_character_,
    TRUE                                                                        ~ "PD/SD/MR"
  )) %>% 
  mutate(day90_response_group = case_when(
    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	        ~ "CR or sCR",
    is.na(x3_month_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
    TRUE           ~ x3_month_response_s_cr_cr_vgpr_pr_sd_pd
  )) %>% 
  mutate(day90_response = case_when(
    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "sCR")	        ~ "sCR",
    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	        ~ "CR",
    is.na(x3_month_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
    TRUE           ~ x3_month_response_s_cr_cr_vgpr_pr_sd_pd
  )) %>% 
  mutate(day90_response_sCRvsOthers = case_when(
    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	         ~ "CR or sCR",
    is.na(x3_month_response_s_cr_cr_vgpr_pr_sd_pd)                      ~ NA_character_,
    TRUE           ~ "Others"
  )) %>% 
  # Best response
  mutate(ORR_as_best_response = case_when(
    ORR_30days == "ORR" |
    ORR_90days == "ORR"                       ~ "ORR"
  )) %>% 
  mutate(best_response = case_when(
    day30_response_group == "CR or sCR" |
      day90_response_group == "CR or sCR"                                             ~ "CR or sCR",
    day30_response_group == "VGPR" |
      day90_response_group == "VGPR"                                                  ~ "VGPR",
    day30_response_group == "PR" |
      day90_response_group == "PR"                                                    ~ "PR",
    TRUE                                                                        ~ NA_character_
  )) %>%

  mutate(MRDneg_in_best_response = case_when(
    day_30_mrd_by_clono_seq_positive_vs_negative ==  "Negative" |
      MRD_90days ==  "Negative"                     ~ "Negative",
    day_30_mrd_by_clono_seq_positive_vs_negative ==  "Positive" |
      MRD_90days ==  "Positive"                     ~ "Positive",
    TRUE                             ~ NA_character_
  ))

  # Titers ----
  # mutate(ig_g_hsv1_2_apheresis = case_when(
  #   ig_g_hsv1_2_apheresis < 0.9         ~ "Negative",
  #   ig_g_hsv1_2_apheresis >= 0.9 &
  #     ig_g_hsv1_2_apheresis < 1.10      ~ "Indeterminate",
  #   ig_g_hsv1_2_apheresis >= 1.10       ~ "Positive",
  # )) %>%
  # mutate(ig_g_hsv1_2_d90 = case_when(
  #   ig_g_hsv1_2_d90 < 0.9         ~ "Negative",
  #   ig_g_hsv1_2_d90 >= 0.9 &
  #     ig_g_hsv1_2_d90 < 1.10      ~ "Indeterminate",
  #   ig_g_hsv1_2_d90 >= 1.10       ~ "Positive",
  # )) %>% 
  # mutate_at(c("ig_g_hsv1_2_apheresis",
  #             "ig_g_hsv1_2_d90"),
  #           ~ factor(., levels = c("Positive", "Indeterminate", "Negative"))) %>%
  # 
  # mutate_at(c("vzv_ig_g_apheresis",
  #             "vzv_ig_g_d90",
  #             "cmv_ig_g_apheresis",
  #             "cmv_ig_g_d90"), 
  #           ~ case_when(
  #             . == 1                                              ~ "Positive",
  #             . == 0                                              ~ "Negative",
  #             . == "Equivocal"                                    ~ "Equivocal"
  #           )) %>% 
  # mutate_at(c("vzv_ig_g_apheresis",
  #             "vzv_ig_g_d90",
  #             "cmv_ig_g_apheresis",
  #             "cmv_ig_g_d90"),
  #           ~ factor(., levels = c("Positive", "Negative", "Equivocal"))) %>% 
  # mutate(across(starts_with("Pneumo"), ~ case_when(
  #   . <= 1                                                    ~ "Negative",
  #   . > 1                                                     ~ "Positive"
  # ))) %>%

#   mutate(igg_hsv_change = case_when(
#     ig_g_hsv1_2_apheresis == "Positive" &
#       ig_g_hsv1_2_d90 == "Negative"         ~ -1,
#     ig_g_hsv1_2_apheresis == "Negative" &
#       ig_g_hsv1_2_d90 == "Positive"         ~ 1,
#     ig_g_hsv1_2_apheresis == "Negative" &
#       ig_g_hsv1_2_d90 == "Negative"         ~ -0.25,
#     ig_g_hsv1_2_apheresis == "Positive" &
#       ig_g_hsv1_2_d90 == "Positive"         ~ 0.25
#   )) %>% 
#   mutate(igg_vzv_change = case_when(
#     `vzv_ig_g_apheresis` == "Positive" &
#       `vzv_ig_g_d90` == "Negative"               ~ -1,
#     `vzv_ig_g_apheresis` == "Negative" &
#       `vzv_ig_g_d90` == "Positive"               ~ 1,
#     `vzv_ig_g_apheresis` == "Negative" &
#       `vzv_ig_g_d90` == "Negative"               ~ -0.25,
#     `vzv_ig_g_apheresis` == "Positive" &
#       `vzv_ig_g_d90` == "Positive"               ~ 0.25
#   )) %>% 
#   mutate(igg_cmv_change = case_when(
#     `cmv_ig_g_apheresis` == "Positive" &
#       `cmv_ig_g_d90` == "Negative"               ~ -1,
#     `cmv_ig_g_apheresis` == "Negative" &
#       `cmv_ig_g_d90` == "Positive"               ~ 1,
#     `cmv_ig_g_apheresis` == "Negative" &
#       `cmv_ig_g_d90` == "Negative"               ~ -0.25,
#     `cmv_ig_g_apheresis` == "Positive" &
#       `cmv_ig_g_d90` == "Positive"               ~ 0.25
#   ))
#   
# # Create Pneumo titers change value
# for (i in colnames(cart1 %>%
#                    select(c(starts_with("Pneumo"))))) {
# 
#   pneumo_type <-
#     str_match(i, ".*(apheresis|D90)")[, 1] %>% 
#     # str_replace_all(., " ", "_") %>% 
#     str_remove(., " apheresis| D90")
#   
#   pneumo_subset <- cart1 %>% select(PT, starts_with(pneumo_type))
#   
#   pneumo_type <-
#     str_replace_all(pneumo_type, " ", "_")
#   # day <-
#   #   str_match(i, ".*(apheresis|D90)")[, 2]
#  
#   name <- paste0(pneumo_type, "_", "change")
# 
#   cart1[[paste0(pneumo_type, "_", "change")]] <-  case_when(
#     pneumo_subset[2] == "Positive" &
#       pneumo_subset[3] == "Negative"               ~ -1,
#     pneumo_subset[2] == "Negative" &
#       pneumo_subset[3] == "Positive"               ~ 1,
#     pneumo_subset[2] == "Negative" &
#       pneumo_subset[3] == "Negative"               ~ -0.25,
#     pneumo_subset[2] == "Positive" &
#       pneumo_subset[3] == "Positive"               ~ 0.25
#   )
# }
```

```{r}
## Labeling
var_label(cart1) <- list(age = "Patient age", agecat = "Patient age - Categories", 
                         extramedullary_disease_yes_no = "Extramedullary disease",
                         # bm_plasma_cell_percent_at_pre_ld = "Circulating Plasma Cells?",
                         high_marrow_burden_50_percent = "High marrow burden (≥50%)",
                         # `ECOG > or = 2? (Yes, No)` ,
                         r_iss_at_car_t_infusion = "ISS at cart infusion",
                         cytogenetics = "High risk cytogenetics", 
                         deletion_17p_prior_to_car_t_infusion_yes_no = "Deletion 17p at Infusion", 
                         t_4_14_prior_to_car_t_infusion_yes_no = "t(4:14) at Infusion", 
                         t_14_16_prior_to_car_t_infusion_yes_no = "t(4:16) at Infusion", 
                         bridging_therapy_yes_no = "Bridging Therapy",
                         prior_auto_sct_yes_no = "Prior autoSCT", 
                         prior_allo_sct_within_6_months_before_apheresis = "Prior alloSCT",
                         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no = "Prior BCMA-directed therapy",
                         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no = "Prior BCMA-directed therapy ",
                         # bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
                         proteasome = "Refractory to Proteasome Inhibitors", 
                         lenalidomide_exposed_vs_refractory_vs_not_exposed = "Refractory to Lenalidomide",
                         bortezomib_exposed_vs_refractory_vs_not_exposed = "Refractory to Bortezomib", 
                         carfilzomib_exposed_vs_refractory_vs_not_exposed = "Refractory to Carfilzomib", 
                         pomalidomide_exposed_vs_refractory_vs_not_exposed = "Refractory to Pomalidomide",
                         dara = "Refractory to Daratumumab or Isatuximab",
                         immuno = "Refractory to Immunomodulators", doubleref = "Double refractory", 
                         tripleref= "Triple refractory", pentaref= "Penta refractory",
                         # bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese", 
                         CRS_any = "Any CRS", CRS_gradecat = "CRS Grade", 
                         ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", 
                         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no =
                           "Did patient meet cartitude criteria"#,
                         # best_response = "Best response in first 90 days"
)

```
<br>

### 2023-12-14 cilta_cel/Manuscript analyses.Rmd
Add analyses + more cleaning

@@
 # check_data(cart[101:150])
-# check_data(cart[151:200]) # has < : "CRP Pre-Leukapheresis", "IgG day -5", "IgA day -5", "IgM day -5"
-# check_data(cart[201:250]) # has < :"CRP day +21", "IgG day +30", "IgA day +30", "IgM day +30", "marrow_percent_cd138_day_30", "marrow % cellularity day +30", "CRP day +30", "CD19 day +90", "IgG day +90", "IgA day +90", "IgM day +90", "marrow %CD138 day +90",
-# # has > : "CD8 day +30", "CRP day +90"
-# check_data(cart[251:300]) # has < : "CD19 day +180", "IgG day +180", "IgA day +180", "IgM day +180", "marrow % cellularity day +180", "CRP day +180"
-# # has > : "marrow %CD138 day +180"
+# check_data(cart[151:200]) # has < : "CRP Pre-Leukapheresis", 
+# check_data(cart[201:250]) # has < :"CRP day +21",  "CRP day +30", 
+# # has > :  "CRP day +90"
+# check_data(cart[251:300]) # has < : "CRP day +180"
 # check_data(cart[1:44, 301:353]) # need to see patient in Moffitt
@@
 cart <- cart %>% 
+  # General ----
   # Fix letter case and missing
@@
   mutate(across(c(where(is.character),
-                  -c("r_iss_at_car_t_infusion")), 
+                  -c("pt_identifier",
+                     "r_iss_at_car_t_infusion")), 
                 ~ str_to_sentence(.) )) %>%
+  mutate(across(c(contains("vgpr"), "response_to_bridging_chemotherapy"
+                  ), 
+                ~ str_to_upper(.) )) %>%
+
   mutate(across(where(is.character), ~ str_replace(., "Unknown|unknown", NA_character_))) %>%
@@
   )) %>%
-
-  mutate(across(c("bm_plasma_cell_percent_at_pre_ld",
+  # Suboptimal is NA
+  mutate(across(c(#"bm_plasma_cell_percent_at_pre_ld",
                   "high_marrow_burden_50_percent",
-                  "marrow_percent_cd138_day_30",
-                  # "marrow fibrosis day +30 (0, 1, 2, 3)",
-                  # "marrow dysplasia day +30 (yes/no)"
-                  "marrow_cellularity_baseline_normo_hypo_hyper",
-                  "marrow_cellularity_day_30_normo_hypo_hyper",
-                  "marrow_cellularity_day_90_normo_hypo_hyper",
-                  "marrow_fibrosis_baseline_0_1_2_3",
-                  "marrow_fibrosis_day_30_0_1_2_3",
-                  "marrow_fibrosis_day_90_0_1_2_3",
-                  "marrow_fibrosis_day_180_0_1_2_3",
-                  "marrow_percent_cellularity_day_90",
-                  # "marrow dysplasia day +90 (yes/no)",
+                  contains("normo_hypo_hyper"),
+                  contains("fibrosis"),
+                  contains("dysplasia"),
                   "b2_microglobulin_day_180"), 
                 ~ str_replace(., "Suboptimal", NA_character_))) %>%
+  # Are numerical - also remove "Suboptimal"
+  mutate(across(c(starts_with("marrow_fibrosis"),
+                  starts_with("ldh_")
+                  ), 
+                ~ as.numeric(.))) %>%
   mutate(across(c("response_to_bridging_chemotherapy"), 
-                ~ str_replace(., "Not evaluable", NA_character_)))
+                ~ str_replace(., "Not evaluable", NA_character_))) %>% 
+  # Convert 0/1 to No/Yes
+  mutate_at(c("infection_yes_1_no_0",
+              "severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0",
+              # "bm_plasma_cell_percent_at_pre_ld",
+              # "high_marrow_burden_50_percent",
+              # "ECOG > or = 2? (Yes, No)",
+              # deletion_17p_prior_to_car_t_infusion_yes_no,
+              # "t_4_14_prior_to_car_t_infusion_yes_no",
+              # "t_14_16_prior_to_car_t_infusion_yes_no",
+              # "steroid_use_yes_no", "tocilizumab_yes_no", "anakinra_yes_no",
+              # "Bridging Therapy (Yes=1, No=0)",
+              # "Received alkylating therapy with bridging (Yes=1, No=0)",
+              "need_for_g_csf_post_infus_yes_1_no_0",
+              "need_for_ivig_yes_1_no_0",
+              "cd34_stem_cell_boost_yes_1_no_0",
+              "rbc_transfusion_within_30d_post_cart_yes_1_no_0", "plt_transfusion_within_30d_post_cart_yes_1_no_0", 
+              "rbc_transfusion_30d_post_cart_yes_1_no_0", "plt_transfusion_30d_post_cart_yes_1_no_0"), 
+            ~ case_when(
+              . == 1                                              ~ "Yes",
+              . == 0                                              ~ "No",
+              TRUE                                                ~ NA_character_
+            )) %>% 
   # Marrow ----
-cart1 <- cart %>% 
   mutate(marrow_cellularity_baseline_normo_hypo_hyper = case_when(
@@
     TRUE                                    ~ .
-  ))) %>% 
-  # mutate(marrow_percent_cellularity_day_30 = as.numeric(marrow_percent_cellularity_day_30)) %>% 
-  # mutate(marrow_percent_cellularity_day_90 = as.numeric(marrow_percent_cellularity_day_90)) %>%
-
+  )))
+
+# Fix the "<" and ">" to take the min or max or each column including numbers next to the signs----
+# Also replace "Suboptimal" by NA
+vec_col <- c("bm_plasma_cell_percent_at_pre_ld",
+
+             "marrow_cellularity_baseline_percent",
+             "marrow_percent_cellularity_day_30",
+             "marrow_percent_cellularity_day_90",
+             "marrow_percent_cellularity_day_180",
+
+             "marrow_cd138_baseline_percent",
+             "marrow_percent_cd138_day_30",
+             "marrow_percent_cd138_day_90",
+             "marrow_percent_cd138_day_180",
+
+             "wbc_day_7", "plt_day_7",
+
+             "ig_g_apheresis",
+             "ig_g_day_5", "ig_g_day_30", "ig_g_day_90",
+             "ig_a_day_5", "ig_a_day_30", "ig_a_day_90",
+             "ig_m_day_5", "ig_m_day_30", "ig_m_day_90",
+
+             "cd8_apheresis", "cd8_day_30", 
+             "cd8_day_90", "cd8_day_180", 
+             "cd19_apheresis", "cd19_day_30",
+             "cd19_day_90", "cd19_day_180",
+
+             "ferritin_day_7", 
+             "crp_pre_leukapheresis", "crp_day_0",
+             "crp_day_7", "crp_day_14", "crp_day_21",
+             "crp_day_30", "crp_day_90", "crp_day_180",
+
+             "ig_g_hsv1_2_apheresis", "ig_g_hsv1_2_d90",
+             "ig_g_hsv1_2_d180"
+             )
+class(cart) <- "data.frame"
+
+for (i in vec_col) {
+
+  if (class(cart[, i]) == "character") {
+
+    cart <- cart %>% 
+      mutate(wo_sign = as.numeric(str_remove(cart[, i], ">|<"))) %>% 
+      mutate(!!i := case_when(
+        str_detect(cart[, i], ">")                 ~ max(wo_sign, na.rm = TRUE),
+        str_detect(cart[, i], "<")                 ~ min(wo_sign, na.rm = TRUE),
+        TRUE                                         ~ as.numeric(wo_sign)
+      )) %>% 
+      select(-c(wo_sign))
+  }
+}
+
+# has < : "CRP Pre-Leukapheresis", "IgG day -5", "IgA day -5", "IgM day -5"
+# has < :"CRP day +21", "IgG day +30", "IgA day +30", "IgM day +30", "marrow_percent_cd138_day_30", "marrow % cellularity day +30", "CRP day +30", "CD19 day +90", "IgG day +90", "IgA day +90", "IgM day +90", "marrow %CD138 day +90",
+# # has > : "CD8 day +30", "CRP day +90"
+# has < : "CD19 day +180", "IgG day +180", "IgA day +180", "IgM day +180", "marrow % cellularity day +180", "CRP day +180"
+# # has > : "marrow %CD138 day +180"
+
+cart <- cart %>% 
+  # Demographics ----
+  rename_at(vars(contains("race")), ~ "race") %>% 
+  rename_at(vars(contains("ethnicity")), ~ "ethnicity") %>% 
+  mutate(ethnicity = case_when(
+    str_detect(ethnicity, "Non|Not")            ~ "Non-Hispanic/Latino",
+    is.na(ethnicity)                            ~ NA_character_,
+    TRUE                                        ~ "Hispanic/Latino"
+  )) %>% 
+  mutate(race = case_when(
+    str_detect(race, "Other")                   ~ "Other",
+    str_detect(race, "Black")                   ~ "Black",
+    TRUE                                        ~ race
+  )) %>% 
+  mutate(race_eth = case_when(
+    ethnicity == "Hispanic/Latino"                ~ "Hispanic (any race)",
+    TRUE ~ race
+  )) %>% 
   # Age categories----
@@
   )) %>%
-  # Convert 0/1 to No/Yes----
-  mutate_at(c(
-              # "bm_plasma_cell_percent_at_pre_ld",
-              # "high_marrow_burden_50_percent",
-              # "ECOG > or = 2? (Yes, No)",
-              # deletion_17p_prior_to_car_t_infusion_yes_no,
-              # "t_4_14_prior_to_car_t_infusion_yes_no",
-              # "t_14_16_prior_to_car_t_infusion_yes_no",
-              # "steroid_use_yes_no", "tocilizumab_yes_no", "anakinra_yes_no",
-              # "Bridging Therapy (Yes=1, No=0)",
-              # "Received alkylating therapy with bridging (Yes=1, No=0)",
-              # "Prior auto SCT (yes, no)",
-              # "Prior Allo SCT within 6 months before apheresis",
-              # "Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)",
-              "need_for_g_csf_post_infus_yes_1_no_0",
-              "need_for_ivig_yes_1_no_0",
-              "cd34_stem_cell_boost_yes_1_no_0",
-              "rbc_transfusion_within_30d_post_cart_yes_1_no_0", "plt_transfusion_within_30d_post_cart_yes_1_no_0", 
-              "rbc_transfusion_30d_post_cart_yes_1_no_0", "plt_transfusion_30d_post_cart_yes_1_no_0"), 
-            ~ case_when(
-              . == 1                                              ~ "Yes",
-              . == 0                                              ~ "No",
-              TRUE                                                ~ NA_character_
-            )) %>% 
+
   # ECOG
@@
 
+  # Myeloma
+  mutate(oligo_or_non_secretory = case_when(
+    oligo_or_non_secretory == "Non-Secretory" ~ "Yes",
+    oligo_or_non_secretory == "Oligosecretory" ~ "Yes",
+    oligo_or_non_secretory == "Unknown" ~ NA_character_,
+    TRUE ~ oligo_or_non_secretory
+  )) %>%
+  # mutate(oligo_or_non_secretory_yes_no = case_when( # is "oligo_or_non_secretory_yes_no" now
+  #   `Yes, Oligo or Yes, Non-Secretory` == "Non-Secretory" ~ "Yes",
+  #   `Yes, Oligo or Yes, Non-Secretory` == "Oligosecretory" ~ "Yes",
+  #   `Yes, Oligo or Yes, Non-Secretory` == "Oligo-secretory" ~ "Yes",
+  #   TRUE ~ `Yes, Oligo or Yes, Non-Secretory`
+  # )) %>%
+  mutate(subtype = case_when(
+    oligo_or_non_secretory_yes_no == "Yes" ~ "Oligo/non-secretory",
+    myeloma_involved_heavy_chain == "None (Light Chain Restricted)" | 
+     myeloma_involved_light_chain == "Lambda" & 
+      is.na(myeloma_involved_heavy_chain) ~ "Light chain only",
+    myeloma_involved_heavy_chain != "None (Light Chain Restricted)" 
+                   ~ "Intact immunoglobulin (Heavy + Light)",
+    TRUE           ~ NA_character_ 
+  )) %>%
   # Cytogenetics ----
@@
   # Refractory status ----
+  mutate(lenalidomide_exposed_vs_refractory_vs_not_exposed = case_when(
+    str_detect(
+      lenalidomide_exposed_vs_refractory_vs_not_exposed, "Ref")     ~ "Refractory",
+    TRUE           ~ lenalidomide_exposed_vs_refractory_vs_not_exposed
+  )) %>% 
   mutate(immuno = case_when(
@@
     number_of_prior_lines_of_therapy > 4                         ~ "> 4"
-  )) %>%
-
+  ))
+```
+
+```{r Baseline labs}
+cart1 <- cart %>% 
+  # Baseline labs ----
+  mutate(baseline_ferritin_cat = case_when(
+    baseline_ferritin_pre_ld >= 400                                      ~ "≥ ULN at LD (≥ 400)",
+    baseline_ferritin_pre_ld < 400                                       ~ "Normal (< 400)"
+  ), baseline_ferritin_cat = 
+    factor(baseline_ferritin_cat, levels = c("Normal (< 400)",
+                                             "≥ ULN at LD (≥ 400)"))) %>% 
+  mutate(baseline_crp_cat = case_when(
+    baseline_crp_pre_ld  >= 0.5                                           ~ "≥ ULN at LD (≥ 0.5)",
+    baseline_crp_pre_ld  < 0.5                                            ~ "Normal (< 0.5)"
+  ), baseline_crp_cat = 
+    factor(baseline_crp_cat, levels = c("Normal (< 0.5)",
+                                        "≥ ULN at LD (≥ 0.5)"))) %>% 
+  mutate(baseline_B2M = case_when(
+    baseline_b2m_pre_ld >= 5.5                                    ~ "≥ 5.5",
+    baseline_b2m_pre_ld < 5.5                                     ~ "< 5.5"
+  )) %>%
+  mutate(cart_cell_dose = case_when(
+    cell_dose_million_cells >= 0.7                                ~ "≥ 0.7",
+    cell_dose_million_cells < 0.7                                 ~ "< 0.7",
+    TRUE                                                          ~ NA_character_
+  ),cart_cell_dose = 
+    factor(cart_cell_dose, levels = c("≥ 0.7", 
+                                      "< 0.7")))
+```
+
+```{r toxicities}
+cart2 <- cart1 %>% 
 # CRS ----
-  # censored days > 100 to 100
-  # mutate(across(c(`Day of onset of CRS relative to infusion`,
-  #                 `Day of Max CRS (relative to infusion)`,
-  #                 `Day of onset of ICANS relative to infusion`,
-  #                 `Day of Max ICANS (relative to infusion)`), ~ case_when(
-  #   . > 100                                                       ~ 100,
-  #   TRUE                                                          ~ as.numeric(.)
-  # ))) %>% 
   mutate(CRS_any = ifelse(max_crs_grade_0_5 == 0, "No", "Yes"),
@@
   ) %>% 
-
-  # ICANS 
+  # censored days > 100 to 100
+  mutate(across(c(day_of_onset_crs_relative_to_infusion,
+                  day_of_max_crs_relative_to_infusion,
+                  day_of_onset_icans_relative_to_infusion,
+                  day_of_max_icans_relative_to_infusion), ~ case_when(
+    . > 100                                                       ~ 100,
+    TRUE                                                          ~ as.numeric(.)
+  ))) %>%
+
+  # ICANS ----
   mutate(ICANS_any = ifelse(max_icans == 0, "No", "Yes"),
@@
   )) %>% 
-
-  # Infection ----
-  mutate(any_infection = infection_yes_1_no_0
-  ) %>% 
-  mutate(any_sevinfection = severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0
-  )
-
-  # mutate(access_type = case_when(
-  #   access_type == "Femoral"                                    ~ "Non-tunneled",
-  #   access_type == "AVF"                                        ~ "Peripheral",
-  #   TRUE                                                          ~ access_type
-  # )) %>% 
-cart1 <- cart1 %>% 
+  # BCMA ----
+  mutate(Prior_bcma_therapy = case_when(
+    str_detect
+    (prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no, "Yes")
+                                                                  ~ "Yes",
+    TRUE                                                          ~ "No"
+  )) %>% 
   # Leukopenia ----
@@
   )) %>% 
-  mutate(cytopenia_d7 = case_when(
+  mutate(cytopenia_7d = case_when(
     Anemia_7d == "Yes" | Thrombocytopenia_7d == "Yes" | 
@@
   )) %>% 
-  mutate(cytopenia_d30 = case_when(
+  mutate(cytopenia_30d = case_when(
     Anemia_30d == "Yes" | Thrombocytopenia_30d == "Yes" | 
@@
   # )) %>%
-  mutate(cytopenia_d90 = case_when(
+  mutate(cytopenia_90d = case_when(
     Anemia_90d == "Yes" | Thrombocytopenia_90d == "Yes" | 
@@
   )) %>%
-  mutate(cytopenia_d180 = case_when(
+  mutate(cytopenia_180d = case_when(
     Anemia_180d == "Yes" | Thrombocytopenia_180d == "Yes" | 
@@
   )) %>% 
-  mutate(gr3_cytopenia_d7 = case_when(
-    gr3_Anemia_7d == "Yes" | gr3_Thrombocytopenia_7d == "Yes" | 
+  mutate(gr3_cytopenia_7d = case_when(
+    gr3_Anemia_7d == "Yes" | 
+      gr3_Thrombocytopenia_7d == "Yes" | 
       gr3_Neutropenia_7d == "Yes"                               ~ "Yes",
-    is.na(gr3_Anemia_7d) | is.na(gr3_Thrombocytopenia_7d) | 
+    is.na(gr3_Anemia_7d) | 
+      is.na(gr3_Thrombocytopenia_7d) | 
       is.na(gr3_Neutropenia_7d)                                 ~ NA_character_,
@@
   )) %>% 
-  mutate(gr3_cytopenia_d30 = case_when(
-    gr3_Anemia_30d == "Yes" | gr3_Thrombocytopenia_30d == "Yes" | 
+  mutate(gr3_cytopenia_30d = case_when(
+    gr3_Anemia_30d == "Yes" | 
+      gr3_Thrombocytopenia_30d == "Yes" | 
       gr3_Neutropenia_30d == "Yes"                              ~ "Yes",
-    is.na(gr3_Anemia_30d) | is.na(gr3_Thrombocytopenia_30d) | 
+    is.na(gr3_Anemia_30d) | 
+      is.na(gr3_Thrombocytopenia_30d) | 
       is.na(gr3_Neutropenia_30d)                                ~ NA_character_,
@@
   )) %>%
-  # mutate(gr3_cytopenia_d60 = case_when(
+  # mutate(gr3_cytopenia_60d = case_when(
   #   gr3_Anemia_60d == "Yes" | gr3_Thrombocytopenia_60d == "Yes" | gr3_Neutropenia_60d == "Yes" ~ "Yes",
@@
   # )) %>%
-  mutate(gr3_cytopenia_d90 = case_when(
-    gr3_Anemia_90d == "Yes" | gr3_Thrombocytopenia_90d == "Yes" | 
+  mutate(gr3_cytopenia_90d = case_when(
+    gr3_Anemia_90d == "Yes" | 
+      gr3_Thrombocytopenia_90d == "Yes" | 
       gr3_Neutropenia_90d == "Yes"                              ~ "Yes",
-    is.na(gr3_Anemia_90d) | is.na(gr3_Thrombocytopenia_90d) | 
+    is.na(gr3_Anemia_90d) | 
+      is.na(gr3_Thrombocytopenia_90d) | 
       is.na(gr3_Neutropenia_90d)                                ~ NA_character_,
@@
   )) %>% 
-  mutate(gr3_cytopenia_d180 = case_when(
-    gr3_Anemia_180d == "Yes" | gr3_Thrombocytopenia_180d == "Yes" |
+  mutate(gr3_cytopenia_180d = case_when(
+    gr3_Anemia_180d == "Yes" | 
+      gr3_Thrombocytopenia_180d == "Yes" |
       gr3_Neutropenia_180d == "Yes"                             ~ "Yes",
-    is.na(gr3_Anemia_180d) | is.na(gr3_Thrombocytopenia_180d) |
+    is.na(gr3_Anemia_180d) | 
+      is.na(gr3_Thrombocytopenia_180d) |
       is.na(gr3_Neutropenia_180d)                               ~ NA_character_,
@@
   ))
-
-cart2 <- cart1 %>% 
+```
+
+```{r survival}
+cart3 <- cart2 %>% 
+  # infusion
+  mutate(notinfused = case_when(
+    !is.na(date_of_car_t_infusion) | 
+      !is.na(time_from_apheresis_to_car_t_infusion_days)          ~ "Yes",
+    TRUE                                                          ~ "No"
+  )) #%>% 
+  # mutate(time_aph_infusion = 
+  #          interval(
+  #            start = date_of_apheresis_or_number_of_days_from_apheresis_to_ld, 
+  #            end = time_from_apheresis_to_car_t_infusion_days)/
+  #          duration(n=1, units = "days"))
+
+  # Day 30 response ----
+# cart3 <- cart2 %>% 
+#   select(pt_identifier, starts_with("date"))
+cart4 <- cart3 %>% 
+  mutate(date_of_onset_of_delayed_neurotoxicity1 = 
+           str_extract(date_of_onset_of_delayed_neurotoxicity, "([:digit:]*)/([:digit:]*)/([:digit:]*)")) %>% 
+  mutate(date_of_pd = as.Date(as.numeric(date_of_pd),
+                                             origin = "1899-12-30")
+
+  )
+
+cart5 <- cart4 %>% 
+  mutate(across(c(starts_with("date")#,
+                  # starts_with("day_of_max_"), contains("_dt"), 
+                  # ends_with("date")
+  ),
+  ~ as.Date(., format = "%m/%d/%y")
+  )) %>% 
+  # pfs
+  mutate(pfs_event = case_when(
+    !is.na(date_of_pd) | !is.na(date_of_death)         ~ 1,
+    TRUE                                               ~ 0
+  )) %>% 
+  mutate(pfs_date = coalesce(date_of_pd, date_of_death, date_of_last_contact)) %>% 
+  mutate(pfs_from_infusion_months = 
+           interval(
+             start = date_of_car_t_infusion, 
+             end = pfs_date)/
+           duration(n=1, units = "months")) %>% 
+  # os 
+  mutate(os_event = case_when(
+    !is.na(date_of_death)                              ~ 1,
+    TRUE                                               ~ 0
+  )) %>% 
+  mutate(os_date = coalesce(date_of_death, date_of_last_contact)) %>% 
+  mutate(os_from_infusion_months = 
+           interval(
+             start = date_of_car_t_infusion, 
+             end = os_date)/
+           duration(n=1, units = "months"))
+```
+
+```{r response}
+cart6 <- cart5 %>%   
+  # mutate(day_30_response_s_cr_cr_vgpr_pr_sd_pd = case_when(
+  #   str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "evaluable")   ~ NA_character_,
+  #   TRUE           ~ day_30_response_s_cr_cr_vgpr_pr_sd_pd
+  # )) %>% 
+  mutate(day30_response = case_when(
+    (os_event == 1 | pfs_event == 1) & 
+      pfs_from_infusion_months < 1                                   ~ "Died or progressed before day 30",
+    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "EVAL")        ~ NA_character_,
+    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
+    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
+    # str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "UCR")	       ~ "UCR",
+    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "CR")          ~ "sCR or CR",
+    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "MR") |
+      str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "SD")        ~ "SD",
+    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "PD")          ~ "PD",
+    is.na(day_30_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
+    TRUE           ~ day_30_response_s_cr_cr_vgpr_pr_sd_pd
+  )) %>% 
+  mutate(day30_response_v2 = case_when(
+    str_detect(day30_response, "Died")                               ~ "PD",
+    is.na(day30_response)                                            ~ NA_character_,
+    TRUE           ~ day30_response
+  )) %>% 
+  mutate(ORR_30days = case_when(
+    str_detect(day30_response_v2, "CR|PR")                           ~ "ORR",
+    is.na(day_30_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
+    TRUE                                                             ~ "PD/SD/MR"
+  )) %>% 
+  mutate(CRorbetter_30days = case_when(
+    str_detect(day30_response_v2, "CR")	                             ~ "sCR or CR",
+    is.na(day30_response_v2)                                         ~ NA_character_,
+    TRUE                                                             ~ "Others"
+  )) %>% 
+  # Day 90 response ----
+  mutate(mon3_response = case_when(
+    day30_response_v2 == "PD"                                        ~ "PD",
+    (os_event == 1 | pfs_event == 1) & 
+      pfs_from_infusion_months < 3                                   ~ "Died or progressed before 3 months",
+    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "EVAL")      ~ NA_character_,
+    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")      ~ "VGPR",
+    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "PR")        ~ "PR",
+    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	       ~ "sCR or CR",
+    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "MR") |
+      str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "SD")      ~ "SD",
+    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "PD")       ~ "PD",
+    is.na(x3_month_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
+    TRUE           ~ x3_month_response_s_cr_cr_vgpr_pr_sd_pd
+  )) %>% 
+  mutate(mon3_response_v2 = case_when(
+    str_detect(mon3_response, "Died")                              ~ "PD",
+    is.na(mon3_response)                                           ~ NA_character_,
+    TRUE           ~ mon3_response
+  )) %>% 
+  mutate(ORR_mon3 = case_when(
+    str_detect(mon3_response_v2, "CR|PR")                          ~ "ORR",
+    is.na(mon3_response_v2)                                        ~ NA_character_,
+    TRUE                                                            ~ "PD/SD/MR"
+  )) %>% 
+  mutate(CRorbetter_mon3 = case_when(
+    mon3_response_v2 == "sCR or CR"                        	      ~ "sCR or CR",
+    is.na(mon3_response_v2)                                        ~ NA_character_,
+    TRUE                                                            ~ "Others"
+  )) %>% 
+    # Month 6 response ----
+  mutate(mon6_response = case_when(
+    mon3_response_v2 == "PD"                                        ~ "PD",
+    (os_event == 1 | pfs_event == 1) & 
+      pfs_from_infusion_months < 6                                     ~ "Died or progressed before 3 months",
+    str_detect(x6_month_response_s_cr_cr_vgpr_pr_sd_pd, "EVAL")        ~ NA_character_,
+    str_detect(x6_month_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
+    str_detect(x6_month_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
+    str_detect(x6_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	         ~ "sCR or CR",
+    str_detect(x6_month_response_s_cr_cr_vgpr_pr_sd_pd, "MR") |
+      str_detect(x6_month_response_s_cr_cr_vgpr_pr_sd_pd, "SD")        ~ "SD",
+    str_detect(x6_month_response_s_cr_cr_vgpr_pr_sd_pd, "PD")          ~ "PD",
+    is.na(x6_month_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
+    TRUE           ~ x6_month_response_s_cr_cr_vgpr_pr_sd_pd
+  )) %>% 
+  mutate(mon6_response_v2 = case_when(
+    str_detect(mon6_response, "Died")                                 ~ "PD",
+    is.na(mon6_response)                                              ~ NA_character_,
+    TRUE           ~ mon6_response
+  )) %>% 
+  mutate(ORR_mon6 = case_when(
+    str_detect(mon6_response_v2, "CR|PR")                             ~ "ORR",
+    is.na(mon6_response_v2)                                           ~ NA_character_,
+    TRUE                                                               ~ "PD/SD/MR"
+  )) %>% 
+  mutate(CRorbetter_mon6 = case_when(
+    mon6_response_v2 == "sCR or CR"                        	       ~ "sCR or CR",
+    is.na(mon6_response_v2)                                         ~ NA_character_,
+    TRUE                                                             ~ "Others"
+  )) %>% 
+    # Month 9 response ----
+  mutate(mon9_response = case_when(
+    mon6_response_v2 == "PD"                                        ~ "PD",
+    (os_event == 1 | pfs_event == 1) & 
+      pfs_from_infusion_months < 9                                     ~ "Died or progressed before 9 months",
+    str_detect(x9_month_response_s_cr_cr_vgpr_pr_sd_pd, "EVAL")        ~ NA_character_,
+    str_detect(x9_month_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
+    str_detect(x9_month_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
+    str_detect(x9_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	         ~ "sCR or CR",
+    str_detect(x9_month_response_s_cr_cr_vgpr_pr_sd_pd, "MR") |
+      str_detect(x9_month_response_s_cr_cr_vgpr_pr_sd_pd, "SD")        ~ "SD",
+    str_detect(x9_month_response_s_cr_cr_vgpr_pr_sd_pd, "PD")          ~ "PD",
+    is.na(x9_month_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
+    TRUE           ~ x9_month_response_s_cr_cr_vgpr_pr_sd_pd
+  )) %>% 
+    mutate(mon9_response_v2 = case_when(
+      str_detect(mon9_response, "Died")                                 ~ "PD",
+      is.na(mon9_response)                                              ~ NA_character_,
+      TRUE           ~ mon9_response
+    )) %>% 
+    mutate(ORR_mon9 = case_when(
+      str_detect(mon9_response_v2, "CR|PR")                             ~ "ORR",
+      is.na(mon9_response_v2)                                           ~ NA_character_,
+      TRUE                                                               ~ "PD/SD/MR"
+    )) %>% 
+    mutate(CRorbetter_mon9 = case_when(
+      mon9_response_v2 == "sCR or CR"                        	       ~ "sCR or CR",
+      is.na(mon9_response_v2)                                         ~ NA_character_,
+      TRUE                                                             ~ "Others"
+    )) %>% 
+    # Month 12 response ----
+  mutate(mon12_response = case_when(
+    mon9_response_v2 == "PD"                                        ~ "PD",
+    (os_event == 1 | pfs_event == 1) & 
+      pfs_from_infusion_months < 12                                     ~ "Died or progressed before 12 months",
+    str_detect(x12_month_response_s_cr_cr_vgpr_pr_sd_pd, "EVAL")        ~ NA_character_,
+    str_detect(x12_month_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
+    str_detect(x12_month_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
+    str_detect(x12_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	         ~ "sCR or CR",
+    str_detect(x12_month_response_s_cr_cr_vgpr_pr_sd_pd, "MR") |
+      str_detect(x12_month_response_s_cr_cr_vgpr_pr_sd_pd, "SD")        ~ "SD",
+    str_detect(x12_month_response_s_cr_cr_vgpr_pr_sd_pd, "PD")          ~ "PD",
+    is.na(x12_month_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
+    TRUE           ~ x12_month_response_s_cr_cr_vgpr_pr_sd_pd
+  )) %>% 
+    mutate(mon12_response_v2 = case_when(
+      str_detect(mon12_response, "Died")                                 ~ "PD",
+      is.na(mon12_response)                                              ~ NA_character_,
+      TRUE           ~ mon12_response
+    )) %>% 
+    mutate(ORR_mon12 = case_when(
+      str_detect(mon12_response_v2, "CR|PR")                             ~ "ORR",
+      is.na(mon12_response_v2)                                           ~ NA_character_,
+      TRUE                                                               ~ "PD/SD/MR"
+    )) %>% 
+    mutate(CRorbetter_mon12 = case_when(
+      mon12_response_v2 == "sCR or CR"                        	       ~ "sCR or CR",
+      is.na(mon12_response_v2)                                         ~ NA_character_,
+      TRUE                                                             ~ "Others"
+    )) %>% 
+    # Best response
+  mutate(ORR_as_best_response = case_when(
+    ORR_30days == "ORR" |
+    ORR_mon3 == "ORR" |
+    ORR_mon6 == "ORR" |
+    ORR_mon9 == "ORR" |
+    ORR_mon12 == "ORR"                                            ~ "ORR"
+  )) %>% 
+  mutate(best_CRorbetter = case_when(
+     CRorbetter_30days == "sCR or CR" | 
+       CRorbetter_mon3 == "sCR or CR" | 
+       CRorbetter_mon6 == "sCR or CR" | 
+       CRorbetter_mon9 == "sCR or CR" | 
+       CRorbetter_mon12 == "sCR or CR"                            ~ "sCR or CR",
+     is.na(CRorbetter_30days) & 
+       is.na(CRorbetter_mon3) & 
+       is.na(CRorbetter_mon6) & 
+       is.na(CRorbetter_mon9) & 
+       is.na(CRorbetter_mon12) ~ NA_character_, 
+     TRUE                                                         ~ "< CR"
+   ))  %>%
+  mutate(best_response = case_when(
+    day30_response_v2 == "sCR or CR" |
+      mon3_response_v2 == "sCR or CR" |
+      mon6_response_v2 == "sCR or CR" |
+      mon9_response_v2 == "sCR or CR" |
+      mon12_response_v2 == "sCR or CR"                            ~ "sCR or CR",
+    day30_response_v2 == "VGPR" |
+      mon3_response_v2 == "VGPR" |
+      mon6_response_v2 == "VGPR" |
+      mon9_response_v2 == "VGPR" |
+      mon12_response_v2 == "VGPR"                                 ~ "VGPR",
+    day30_response_v2 == "PR" |
+      mon3_response_v2 == "PR" |
+      mon6_response_v2 == "PR" |
+      mon9_response_v2 == "PR" |
+      mon12_response_v2 == "PR"                                   ~ "PR",
+    day30_response_v2 == "SD" |
+      mon3_response_v2 == "SD" |
+      mon6_response_v2 == "SD" |
+      mon9_response_v2 == "SD" |
+      mon12_response_v2 == "SD"                                   ~ "SD",
+    day30_response_v2 == "PD" |
+      mon3_response_v2 == "PD" |
+      mon6_response_v2 == "PD" |
+      mon9_response_v2 == "PD" |
+      mon12_response_v2 == "PD"                                   ~ "PD",
+    TRUE                                                          ~ NA_character_
+  )) %>% 
   # MRD----
-  mutate_at(c("day_30_mrd_by_clono_seq_positive_vs_negative",
-              "day_30_mrd_by_flow_positive_vs_negative",
-              "x3_month_mrd_by_clono_seq_positive_vs_negative",
-              "x3_month_mrd_by_flow_positive_vs_negative"),
+  mutate(across(c(contains("mrd_by_")),
             ~ case_when(
@@
               TRUE                                                ~ NA_character_
-            )) %>%
-  mutate(MRD_30days = coalesce(day_30_mrd_by_clono_seq_positive_vs_negative, 
+            ))) %>%
+  mutate(MRD_day30 = coalesce(day_30_mrd_by_clono_seq_positive_vs_negative, 
                                day_30_mrd_by_flow_positive_vs_negative
   )) %>%
-  mutate(MRD_90days = coalesce(x3_month_mrd_by_clono_seq_positive_vs_negative,
+  mutate(MRD_mon3 = coalesce(x3_month_mrd_by_clono_seq_positive_vs_negative,
                                x3_month_mrd_by_flow_positive_vs_negative
   )) %>% 
-
-  # Day 30 response ----
-  mutate(day_30_response_s_cr_cr_vgpr_pr_sd_pd = case_when(
-    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "evaluable")   ~ NA_character_,
-    TRUE           ~ day_30_response_s_cr_cr_vgpr_pr_sd_pd
-  )) %>% 
-  mutate(ORR_30days = case_when(
-    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "CR")   ~ "ORR",
-    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "PR")   ~ "ORR",
-    is.na(day_30_response_s_cr_cr_vgpr_pr_sd_pd)              ~ NA_character_,
-    TRUE                                                                        ~ "PD/SD/MR"
-  )) %>% 
-  mutate(day30_response = case_when(
-    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
-    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
-    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "sCR")	       ~ "sCR",
-    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	         ~ "CR",
-    is.na(day_30_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
-    TRUE           ~ day_30_response_s_cr_cr_vgpr_pr_sd_pd
-  )) %>% 
-  mutate(day30_response_group = case_when(
-    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
-    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
-    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	         ~ "CR or sCR",
-    is.na(day_30_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
-    TRUE           ~ day_30_response_s_cr_cr_vgpr_pr_sd_pd
-  )) %>% 
-  mutate(day30_response_sCRvsOthers = case_when(
-    str_detect(day_30_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	         ~ "CR or sCR",
-    is.na(day_30_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
-    TRUE           ~ "Others"
-  )) %>% 
-  # Day 90 response ----
-  mutate(x3_month_response_s_cr_cr_vgpr_pr_sd_pd = case_when(
-    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, 
-               "evaluable|done")                                     ~ NA_character_,
-    TRUE           ~ x3_month_response_s_cr_cr_vgpr_pr_sd_pd
-  )) %>% 
-  mutate(ORR_90days = case_when(
-    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")    ~ "ORR",
-    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "PR")    ~ "ORR",
-    is.na(x3_month_response_s_cr_cr_vgpr_pr_sd_pd)               ~ NA_character_,
-    TRUE                                                                        ~ "PD/SD/MR"
-  )) %>% 
-  mutate(day90_response_group = case_when(
-    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
-    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
-    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	        ~ "CR or sCR",
-    is.na(x3_month_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
-    TRUE           ~ x3_month_response_s_cr_cr_vgpr_pr_sd_pd
-  )) %>% 
-  mutate(day90_response = case_when(
-    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "VGPR")        ~ "VGPR",
-    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "PR")          ~ "PR",
-    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "sCR")	        ~ "sCR",
-    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	        ~ "CR",
-    is.na(x3_month_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
-    TRUE           ~ x3_month_response_s_cr_cr_vgpr_pr_sd_pd
-  )) %>% 
-  mutate(day90_response_sCRvsOthers = case_when(
-    str_detect(x3_month_response_s_cr_cr_vgpr_pr_sd_pd, "CR")	         ~ "CR or sCR",
-    is.na(x3_month_response_s_cr_cr_vgpr_pr_sd_pd)                      ~ NA_character_,
-    TRUE           ~ "Others"
-  )) %>% 
-  # Best response
-  mutate(ORR_as_best_response = case_when(
-    ORR_30days == "ORR" |
-    ORR_90days == "ORR"                       ~ "ORR"
-  )) %>% 
-  mutate(best_response = case_when(
-    day30_response_group == "CR or sCR" |
-      day90_response_group == "CR or sCR"                                             ~ "CR or sCR",
-    day30_response_group == "VGPR" |
-      day90_response_group == "VGPR"                                                  ~ "VGPR",
-    day30_response_group == "PR" |
-      day90_response_group == "PR"                                                    ~ "PR",
-    TRUE                                                                        ~ NA_character_
-  )) %>%
-
-  mutate(MRDneg_in_best_response = case_when(
-    day_30_mrd_by_clono_seq_positive_vs_negative ==  "Negative" |
-      MRD_90days ==  "Negative"                     ~ "Negative",
-    day_30_mrd_by_clono_seq_positive_vs_negative ==  "Positive" |
-      MRD_90days ==  "Positive"                     ~ "Positive",
+  mutate(MRD_mon6 = coalesce(x6_month_mrd_by_clono_seq_positive_vs_negative,
+                               x6_month_mrd_by_flow_positive_vs_negative
+  )) %>%
+  mutate(MRD_mon9 = coalesce(x9_month_mrd_by_clono_seq_positive_vs_negative,
+                               x9_month_mrd_by_flow_positive_vs_negative
+  )) %>% 
+  mutate(MRD_mon12 = coalesce(x12_month_mrd_by_clono_seq_positive_vs_negative,
+                               x12_month_mrd_by_flow_positive_vs_negative
+  )) %>% 
+  mutate(response_MRD_day30 = case_when(
+    day30_response_v2 == "sCR or CR" & 
+      MRD_day30 == "Negative"                                     ~ "sCR or CR, MRD-",
+    day30_response_v2 == "sCR or CR" & 
+      MRD_day30 == "Positive"                                     ~ "sCR or CR, MRD+",
+    day30_response_v2 == "sCR or CR" & 
+      is.na(MRD_day30)                                            ~ "sCR or CR, MRD unknown",
+    TRUE ~ day30_response_v2
+  )) %>%
+  mutate(response_MRD_mon3 = case_when(
+    mon3_response_v2 == "sCR or CR" & 
+      MRD_mon3 == "Negative"                                      ~ "sCR or CR, MRD-",
+    mon3_response_v2 == "sCR or CR" & 
+      MRD_mon3 == "Positive"                                      ~ "sCR or CR, MRD+",
+    mon3_response_v2 == "sCR or CR" & 
+      is.na(MRD_mon3)                                             ~ "sCR or CR, MRD unknown",
+    TRUE ~ mon3_response_v2
+  )) %>%
+  mutate(response_MRD_mon6 = case_when(
+    mon6_response_v2 == "sCR or CR" & 
+      MRD_mon6 == "Negative"                                      ~ "sCR or CR, MRD-",
+    mon6_response_v2 == "sCR or CR" & 
+      MRD_mon6 == "Positive"                                      ~ "sCR or CR, MRD+",
+    mon6_response_v2 == "sCR or CR" & 
+      is.na(MRD_mon6)                                             ~ "sCR or CR, MRD unknown",
+    TRUE ~ mon6_response_v2
+  )) %>%
+  mutate(response_MRD_mon9 = case_when(
+    mon9_response_v2 == "sCR or CR" & 
+      MRD_mon9 == "Negative"                                      ~ "sCR or CR, MRD-",
+    mon9_response_v2 == "sCR or CR" & 
+      MRD_mon9 == "Positive"                                      ~ "sCR or CR, MRD+",
+    mon9_response_v2 == "sCR or CR" & 
+      is.na(MRD_mon9)                                             ~ "sCR or CR, MRD unknown",
+    TRUE ~ mon9_response_v2
+  )) %>%
+  mutate(response_MRD_mon12 = case_when(
+    mon12_response_v2 == "sCR or CR" & 
+      MRD_mon12 == "Negative"                                      ~ "sCR or CR, MRD-",
+    mon12_response_v2 == "sCR or CR" & 
+      MRD_mon12 == "Positive"                                      ~ "sCR or CR, MRD+",
+    mon12_response_v2 == "sCR or CR" & 
+      is.na(MRD_mon12)                                             ~ "sCR or CR, MRD unknown",
+    TRUE ~ mon12_response_v2
+  )) %>% 
+  mutate(best_response_MRD = case_when (
+    response_MRD_day30 == "sCR or CR, MRD-" | 
+      response_MRD_mon3 == "sCR or CR, MRD-" | 
+      response_MRD_mon6 == "sCR or CR, MRD-" | 
+      response_MRD_mon9 == "sCR or CR, MRD-" | 
+      response_MRD_mon12 == "sCR or CR, MRD-"                      ~ "sCR or CR, MRD-",
+     response_MRD_day30 == "sCR or CR, MRD+" | 
+      response_MRD_mon3 == "sCR or CR, MRD+" | 
+      response_MRD_mon6 == "sCR or CR, MRD+" | 
+      response_MRD_mon9 == "sCR or CR, MRD+" | 
+      response_MRD_mon12 == "sCR or CR, MRD+"                      ~ "sCR or CR, MRD+",
+     response_MRD_day30 == "sCR or CR, MRD unknown" | 
+      response_MRD_mon3 == "sCR or CR, MRD unknown" | 
+      response_MRD_mon6 == "sCR or CR, MRD unknown" | 
+      response_MRD_mon9 == "sCR or CR, MRD unknown" | 
+      response_MRD_mon12 == "sCR or CR, MRD unknown"               ~ "sCR or CR, MRD unknown",
+    TRUE ~ best_response
+  )) %>%
+  # mutate(MRDneg_in_best_response = case_when(
+  #   MRD_day30 ==  "Negative" |
+  #     MRD_mon3 ==  "Negative" |
+  #     MRD_mon6 ==  "Negative" |
+  #     MRD_mon9 ==  "Negative" |
+  #     MRD_mon12 ==  "Negative"                                    ~ "Negative",
+  #   MRD_day30 ==  "Positive" |
+  #   MRD_mon3 ==  "Positive" |
+  #   MRD_mon6 ==  "Positive" |
+  #   MRD_mon9 ==  "Positive" |
+  #     MRD_mon12 ==  "Positive"                                    ~ "Positive",
+#   TRUE                                                          ~ NA_character_
+# )) %>% 
+  mutate(bridging_response = case_when(
+    response_to_bridging_chemotherapy == "MR" |
+      response_to_bridging_chemotherapy == "SD/MR" |
+      response_to_bridging_chemotherapy == "SD" |
+      response_to_bridging_chemotherapy == "PD" |
+      response_to_bridging_chemotherapy == "No" ~ "SD/PD",
+    response_to_bridging_chemotherapy == "CR" |
+      response_to_bridging_chemotherapy == "PR" |
+      response_to_bridging_chemotherapy == "VGPR" ~ "PR or better",
+    response_to_bridging_chemotherapy == "Not Evaluable" |
+      response_to_bridging_chemotherapy == "ND" |
+      response_to_bridging_chemotherapy == "Unknown" ~ NA_character_,
     TRUE ~ NA_character_ 
   ))
-
+```
+
+```{r infection}
+cart6 <- cart6 %>%
+  # Infection ----
+  mutate(any_infection = infection_yes_1_no_0
+  ) %>%
+  mutate(any_sevinfection = severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0
+  ) %>% 
+  mutate(time_from_infusion_to_infection_days = 
+           interval(
+             start = date_of_car_t_infusion, 
+             end = date_of_infection)/
+           duration(n=1, units = "days"))
+
+  # mutate(access_type = case_when(
+  #   access_type == "Femoral"                                    ~ "Non-tunneled",
+  #   access_type == "AVF"                                        ~ "Peripheral",
+  #   TRUE                                                          ~ access_type
+  # )) %>% 
+# cart7 <- cart6 %>% 
+#   mutate(infection = case_when(
+#     notinfused=="YES" ~ NA_character_,
+#     notinfused=="NO" & is.na(`Infection Type`) & is.na(`Infection (Yes, No)`) ~ NA_character_,
+#     notinfused=="NO" & `Infection Type` == "No" ~ "No", 
+#     notinfused=="NO" & `Infection Type` != "No" ~ "Yes",
+#     notinfused=="NO" & is.na(`Infection Type`) ~ "No",
+#     TRUE ~ NA_character_
+#   )) %>%
+#   mutate(HLH = case_when(
+#     notinfused=="YES" ~ NA_character_,
+#     notinfused=="NO" & `HLH/HLH-Like Toxicities?`=="Yes" ~ "Yes",
+#     TRUE ~ "No"
+#   )) %>%
+#   mutate(infection_type = case_when(
+#     infection=="No" | is.na(infection) ~ NA_character_,
+#     infection=="Yes" & `Infection Details (specific infection, ie. E.coli bacteremia, etc.)` == "fungus was unidentified" ~ "Fungal",
+#     infection== "Yes" & `Infection Details (specific infection, ie. E.coli bacteremia, etc.)` == "E. coli bacteremia and Salmonella GI infection treated with ceftriaxone x 7 days" ~ "Bacterial",
+#     infection=="Yes" & `Infection Type`=="bacterial + viral" ~ "Bacterial + Viral",
+#     infection=="Yes" & `Infection Type`=="viral" ~ "Viral",
+#     infection=="Yes" & `Infection Type`=="All of the above" ~ "Bacterial, Viral, and Fungal",
+#     infection=="Yes" & `Infection Type`=="Bacterial; Viral; Bacterial" ~ "Bacterial + Viral",
+#     infection=="Yes" & `Infection Type`=="Viral; Bacterial; Bacterial" ~ "Bacterial + Viral",
+#     TRUE ~ `Infection Type`
+#   )) %>% 
+#   mutate(infection_severity = case_when(
+#      infection=="No" | is.na(infection) ~ NA_character_,
+#      infection=="Yes" & is.na(`Infection Severity (Severe = hospitalization or requiring IV antibiotics)`) ~ NA_character_,
+#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="severe" ~ "Severe",
+#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="Yes" ~ "Severe",
+#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="non-severe" ~ "Not severe",
+#     infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="Non-Severe" ~ "Not severe",
+#     TRUE ~ `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`
+#   )) %>%
+#   mutate(infection_type = factor(infection_type, levels = c("Bacterial", "Fungal", "Viral", "Bacterial + Fungal", "Bacterial + Viral", "Bacterial, Viral, and Fungal")))
+```
+
+```{r delayed NT}
+cilta <- cart6 %>%
+  mutate(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no = case_when(
+    is.na(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no) 
+                                                                  ~ "No",
+    TRUE           ~ other_delayed_non_parkinsonian_neurologic_toxicity_yes_no
+  )) %>%
+  mutate(parkinsonian_neurotoxicity_yes_no = case_when(
+    parkinsonian_neurotoxicity_yes_no == "Yes" & 
+      what_non_parkinsonian_neurotoxicity == "Bell's palsy"       ~ "No",
+    is.na(parkinsonian_neurotoxicity_yes_no) ~ "No",
+    TRUE ~ parkinsonian_neurotoxicity_yes_no
+  )) %>%
+  mutate(delayed_neuro = case_when(
+    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" |
+      parkinsonian_neurotoxicity_yes_no == "Yes"                  ~ "Yes",
+    TRUE                                                          ~ "No"
+  )) %>%
+  mutate(delayed_neuro_type = case_when(
+    what_non_parkinsonian_neurotoxicity == 
+      "Posterior reversible encephalopathy syndrome (PRES) and parkinsonism" 
+                                                                  ~ "Parkinsonian/PRES",
+    parkinsonian_neurotoxicity_yes_no == "Yes"                    ~ "Parkinsonian",
+    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
+      str_detect(what_non_parkinsonian_neurotoxicity, "alsy")     ~ "Bell's palsy",
+    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
+      str_detect(what_non_parkinsonian_neurotoxicity, "alsey")    ~ "Bell's palsy", 
+    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
+      str_detect(what_non_parkinsonian_neurotoxicity, "droop")    ~ "Bell's palsy", 
+    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
+      str_detect(what_non_parkinsonian_neurotoxicity, "PRES")    ~ "PRES", 
+    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
+      str_detect(what_non_parkinsonian_neurotoxicity, "dysautonomia") 
+                                                                 ~ "Dysautonomia",
+    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
+      str_detect(what_non_parkinsonian_neurotoxicity, "plopia")    
+                                                                  ~ "Diplopia",
+    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
+      str_detect(what_non_parkinsonian_neurotoxicity, "Polyneuropathy") 
+                                                                  ~ "Polyneuropathy",
+    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
+      is.na(what_non_parkinsonian_neurotoxicity)                  ~ "Unknown type",
+    TRUE                                                          ~ NA_character_
+  )) 
+```
+
+```{r titers}
 # Titers ----
-  # mutate(ig_g_hsv1_2_apheresis = case_when(
-  #   ig_g_hsv1_2_apheresis < 0.9         ~ "Negative",
-  #   ig_g_hsv1_2_apheresis >= 0.9 &
-  #     ig_g_hsv1_2_apheresis < 1.10      ~ "Indeterminate",
-  #   ig_g_hsv1_2_apheresis >= 1.10       ~ "Positive",
-  # )) %>%
-  # mutate(ig_g_hsv1_2_d90 = case_when(
-  #   ig_g_hsv1_2_d90 < 0.9         ~ "Negative",
-  #   ig_g_hsv1_2_d90 >= 0.9 &
-  #     ig_g_hsv1_2_d90 < 1.10      ~ "Indeterminate",
-  #   ig_g_hsv1_2_d90 >= 1.10       ~ "Positive",
-  # )) %>% 
-  # mutate_at(c("ig_g_hsv1_2_apheresis",
-  #             "ig_g_hsv1_2_d90"),
-  #           ~ factor(., levels = c("Positive", "Indeterminate", "Negative"))) %>%
-  # 
+cilta <- cilta %>% 
+  mutate(ig_g_hsv1_2_apheresis = case_when(
+    ig_g_hsv1_2_apheresis < 0.9         ~ "Negative",
+    ig_g_hsv1_2_apheresis >= 0.9 &
+      ig_g_hsv1_2_apheresis < 1.10      ~ "Indeterminate",
+    ig_g_hsv1_2_apheresis >= 1.10       ~ "Positive"
+  )) %>%
+  mutate(ig_g_hsv1_2_d90 = case_when(
+    ig_g_hsv1_2_d90 < 0.9         ~ "Negative",
+    ig_g_hsv1_2_d90 >= 0.9 &
+      ig_g_hsv1_2_d90 < 1.10      ~ "Indeterminate",
+    ig_g_hsv1_2_d90 >= 1.10       ~ "Positive"
+  )) %>%
+  mutate_at(c("ig_g_hsv1_2_apheresis",
+              "ig_g_hsv1_2_d90"),
+            ~ factor(., levels = c("Positive", "Indeterminate", "Negative"))) %>%
+
   # mutate_at(c("vzv_ig_g_apheresis",
@@
   #           ~ factor(., levels = c("Positive", "Negative", "Equivocal"))) %>%
-  # mutate(across(starts_with("Pneumo"), ~ case_when(
-  #   . <= 1                                                    ~ "Negative",
-  #   . > 1                                                     ~ "Positive"
-  # ))) %>%
-
-#   mutate(igg_hsv_change = case_when(
-#     ig_g_hsv1_2_apheresis == "Positive" &
-#       ig_g_hsv1_2_d90 == "Negative"         ~ -1,
-#     ig_g_hsv1_2_apheresis == "Negative" &
-#       ig_g_hsv1_2_d90 == "Positive"         ~ 1,
-#     ig_g_hsv1_2_apheresis == "Negative" &
-#       ig_g_hsv1_2_d90 == "Negative"         ~ -0.25,
-#     ig_g_hsv1_2_apheresis == "Positive" &
-#       ig_g_hsv1_2_d90 == "Positive"         ~ 0.25
-#   )) %>% 
-#   mutate(igg_vzv_change = case_when(
-#     `vzv_ig_g_apheresis` == "Positive" &
-#       `vzv_ig_g_d90` == "Negative"               ~ -1,
-#     `vzv_ig_g_apheresis` == "Negative" &
-#       `vzv_ig_g_d90` == "Positive"               ~ 1,
-#     `vzv_ig_g_apheresis` == "Negative" &
-#       `vzv_ig_g_d90` == "Negative"               ~ -0.25,
-#     `vzv_ig_g_apheresis` == "Positive" &
-#       `vzv_ig_g_d90` == "Positive"               ~ 0.25
-#   )) %>% 
-#   mutate(igg_cmv_change = case_when(
-#     `cmv_ig_g_apheresis` == "Positive" &
-#       `cmv_ig_g_d90` == "Negative"               ~ -1,
-#     `cmv_ig_g_apheresis` == "Negative" &
-#       `cmv_ig_g_d90` == "Positive"               ~ 1,
-#     `cmv_ig_g_apheresis` == "Negative" &
-#       `cmv_ig_g_d90` == "Negative"               ~ -0.25,
-#     `cmv_ig_g_apheresis` == "Positive" &
-#       `cmv_ig_g_d90` == "Positive"               ~ 0.25
-#   ))
-#   
-# # Create Pneumo titers change value
-# for (i in colnames(cart1 %>%
-#                    select(c(starts_with("Pneumo"))))) {
-# 
-#   pneumo_type <-
-#     str_match(i, ".*(apheresis|D90)")[, 1] %>% 
-#     # str_replace_all(., " ", "_") %>% 
-#     str_remove(., " apheresis| D90")
-#   
-#   pneumo_subset <- cart1 %>% select(PT, starts_with(pneumo_type))
-#   
-#   pneumo_type <-
-#     str_replace_all(pneumo_type, " ", "_")
-#   # day <-
-#   #   str_match(i, ".*(apheresis|D90)")[, 2]
-#  
-#   name <- paste0(pneumo_type, "_", "change")
-# 
-#   cart1[[paste0(pneumo_type, "_", "change")]] <-  case_when(
-#     pneumo_subset[2] == "Positive" &
-#       pneumo_subset[3] == "Negative"               ~ -1,
-#     pneumo_subset[2] == "Negative" &
-#       pneumo_subset[3] == "Positive"               ~ 1,
-#     pneumo_subset[2] == "Negative" &
-#       pneumo_subset[3] == "Negative"               ~ -0.25,
-#     pneumo_subset[2] == "Positive" &
-#       pneumo_subset[3] == "Positive"               ~ 0.25
-#   )
-# }
-```
-
-```{r}
-## Labeling
-var_label(cart1) <- list(age = "Patient age", agecat = "Patient age - Categories", 
+  mutate(across(starts_with("pneumo"), ~ case_when(
+    . <= 1                                                    ~ "Negative",
+    . > 1                                                     ~ "Positive"
+  ))) %>%
+  mutate(igg_hsv_change = case_when(
+    ig_g_hsv1_2_apheresis == "Positive" &
+      ig_g_hsv1_2_d90 == "Negative"         ~ -1,
+    ig_g_hsv1_2_apheresis == "Negative" &
+      ig_g_hsv1_2_d90 == "Positive"         ~ 1,
+    ig_g_hsv1_2_apheresis == "Negative" &
+      ig_g_hsv1_2_d90 == "Negative"         ~ -0.25,
+    ig_g_hsv1_2_apheresis == "Positive" &
+      ig_g_hsv1_2_d90 == "Positive"         ~ 0.25
+  )) %>%
+  mutate(igg_vzv_change = case_when(
+    vzv_ig_g_apheresis == "Positive" &
+      vzv_ig_g_d90 == "Negative"               ~ -1,
+    vzv_ig_g_apheresis == "Negative" &
+      vzv_ig_g_d90 == "Positive"               ~ 1,
+    vzv_ig_g_apheresis == "Negative" &
+      vzv_ig_g_d90 == "Negative"               ~ -0.25,
+    vzv_ig_g_apheresis == "Positive" &
+      vzv_ig_g_d90 == "Positive"               ~ 0.25
+  )) %>%
+  mutate(igg_cmv_change = case_when(
+    cmv_ig_g_apheresis == "Positive" &
+      cmv_ig_g_d90 == "Negative"               ~ -1,
+    cmv_ig_g_apheresis == "Negative" &
+      cmv_ig_g_d90 == "Positive"               ~ 1,
+    cmv_ig_g_apheresis == "Negative" &
+      cmv_ig_g_d90 == "Negative"               ~ -0.25,
+    cmv_ig_g_apheresis == "Positive" &
+      cmv_ig_g_d90 == "Positive"               ~ 0.25
+  ))
+
+# Create Pneumo titers change value
+for (i in colnames(cilta %>%
+                   select(c(starts_with("pneumo") & 
+                            (ends_with("apheresis") | ends_with("d90"))
+                   )))) {
+
+  pneumo_type <-
+    str_match(i, "(.*)(apheresis|d90)")[, 1] %>%
+    str_remove(., "_apheresis|_d90")
+
+  pneumo_subset <- cilta %>% select(pt_identifier, starts_with(pneumo_type) & 
+                                      (ends_with("apheresis") | ends_with("d90")))
+
+  name <- paste0(pneumo_type, "_", "change")
+
+  cilta <- cilta %>% 
+    mutate(!!paste0(pneumo_type, "_", "change") := case_when(
+      pneumo_subset[2] == "Positive" &
+        pneumo_subset[3] == "Negative"               ~ -1,
+      pneumo_subset[2] == "Negative" &
+        pneumo_subset[3] == "Positive"               ~ 1,
+      pneumo_subset[2] == "Negative" &
+        pneumo_subset[3] == "Negative"               ~ -0.25,
+      pneumo_subset[2] == "Positive" &
+        pneumo_subset[3] == "Positive"               ~ 0.25
+    ))
+
+}
+```
+
+```{r Labeling}
+## Labeling ----
+var_label(cilta) <- list(age = "Patient age", agecat = "Patient age - Categories", 
+                         male_sex = "Male Sex", sex = "Sex",
+                         race_eth = "Race and ethnicity",
                          extramedullary_disease_yes_no = "Extramedullary disease",
-                         # bm_plasma_cell_percent_at_pre_ld = "Circulating Plasma Cells?",
+                         bm_plasma_cell_percent_at_pre_ld = "Circulating Plasma Cells?",
                          high_marrow_burden_50_percent = "High marrow burden (≥50%)",
+                         ecog_at_ld = "ECOG at LD",
                          # `ECOG > or = 2? (Yes, No)` ,
@@
                          t_14_16_prior_to_car_t_infusion_yes_no = "t(4:16) at Infusion", 
+                         number_of_prior_lines_of_therapy = "Number of prior lines of therapy",
+                         number_prior_lines_therapy = "Number of prior lines of therapy (cat)",
                          bridging_therapy_yes_no = "Bridging Therapy",
@@
                          # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no = "Prior BCMA-directed therapy",
-                         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no = "Prior BCMA-directed therapy ",
+                         Prior_bcma_therapy = "Prior BCMA-directed therapy",
+                         need_for_g_csf_post_infus_yes_1_no_0 = "Need for gCSF post infusion",
+                         need_for_ivig_yes_1_no_0 = "Need for IVIG",
+                         cd34_stem_cell_boost_yes_1_no_0 = "CD34 stem cell boost",
                          # bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
+                         steroid_use_yes_no = "Steroid Use", tocilizumab_yes_no = "Tocilizumab Use", 
+                         anakinra_yes_no = "Anakinra Use",
                          proteasome = "Refractory to Proteasome Inhibitors", 
@@
                          ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", 
+                         day_of_onset_crs_relative_to_infusion = "Day of onset of CRS relative to infusion",
+                         day_of_max_crs_relative_to_infusion = "Day of Max CRS (relative to infusion)",
+                         duration_of_crs_days = "Duration of CRS (days)", 
+                         day_of_onset_icans_relative_to_infusion = "Day of onset of ICANS relative to infusion",
+                         day_of_max_icans_relative_to_infusion = "Day of Max ICANS (relative to infusion)",
+                         duration_of_icans_days = "Duration of ICANS (days)", 
+                         delayed_neuro = "Delayed Neurotoxicity",
+                         parkinsonian_neurotoxicity_yes_no = "Parkinsonian Neurotoxicity",
+                         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no = 
+                           "Other/Delayed Non-Parkinsonian Neurologic Toxicity",
+                         delayed_neuro_type = "Delayed Neurotoxicity Type",
+
+                         tbv = "TBV", whole_blood_processed_m_l = "Whole blood processed (mL)",
+                         final_collection_volume_m_l = "Final collection volume (mL)", 
+                         tbv_processed = "TBV processed", 
+                         access_type = "Access type", total_bags = "Total bags",
+                         run_time_min = "Run time (min)",
+                         time_from_apheresis_to_car_t_infusion_days = "Time from apheresis to CAR-T infusion (days)", 
+                         total_dose_volume_m_l = "Total dose volume (mL)", 
+                         cell_dose_million_cells = "Total cell dose (million cells)",
                          did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no =
@@
 <br>
+
+### Tables
+Patients evaluable at each time point
+```{r}
+day7 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(os_from_infusion_months > (7 / 30.417)) %>% 
+  select(pt_identifier) %>% 
+  tbl_summary(missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+day14 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(os_from_infusion_months > (14 / 30.417)) %>% 
+  select(pt_identifier) %>% 
+  tbl_summary(missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+day21 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(os_from_infusion_months > (21 / 30.417)) %>% 
+  select(pt_identifier) %>% 
+  tbl_summary(missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+day30 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(os_from_infusion_months > (30 / 30.417)) %>% 
+  select(pt_identifier) %>% 
+  tbl_summary(missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+day90 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(os_from_infusion_months > 3) %>% 
+  select(pt_identifier) %>% 
+  tbl_summary(missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+day180 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(os_from_infusion_months > 6) %>% 
+  select(pt_identifier) %>% 
+  tbl_summary(missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+tbl_merge(list(day7, day14, day21, day30, day90, day180), 
+          tab_spanner = c("day7", "day14", "day21", "day30", "day90", "day180"))
+```
+
+```{r}
+cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(notinfused) %>% 
+  tbl_summary(missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+```
+
+## Table 1. Patient baseline characteristics
+```{r}
+cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(age, agecat, male_sex, sex,
+         extramedullary_disease_yes_no, 
+         high_marrow_burden_50_percent, ecog_at_ld, 
+         r_iss_at_car_t_infusion, 
+         cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no,
+         t_4_14_prior_to_car_t_infusion_yes_no,
+         t_14_16_prior_to_car_t_infusion_yes_no,
+         bridging_therapy_yes_no,
+         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
+         Prior_bcma_therapy,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no) %>% 
+  tbl_summary(
+    type = list(
+      c(agecat, sex, 
+        extramedullary_disease_yes_no, high_marrow_burden_50_percent,
+        cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no,
+        t_4_14_prior_to_car_t_infusion_yes_no,
+        t_14_16_prior_to_car_t_infusion_yes_no,
+        bridging_therapy_yes_no, prior_auto_sct_yes_no,
+        Prior_bcma_therapy,
+        # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+        immuno, proteasome, dara, doubleref, tripleref, pentaref,
+        did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
+      ~"categorical"),
+
+    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>% 
+  modify_footnote(update = everything() ~ NA)
+```
+
+## Table 2. Clinical outcomes
+```{r}
+tbl1 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(max_crs_grade_0_5,
+         day_of_onset_crs_relative_to_infusion,
+         day_of_max_crs_relative_to_infusion,
+         duration_of_crs_days, 
+         max_icans,
+         day_of_onset_icans_relative_to_infusion,
+         day_of_max_icans_relative_to_infusion,
+         duration_of_icans_days,
+         delayed_neuro,
+         parkinsonian_neurotoxicity_yes_no,
+         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
+         delayed_neuro_type) %>% 
+  tbl_summary(type = list(
+    c(day_of_onset_crs_relative_to_infusion,
+         day_of_max_crs_relative_to_infusion,
+         duration_of_crs_days,
+      day_of_onset_icans_relative_to_infusion,
+         day_of_max_icans_relative_to_infusion,
+         duration_of_icans_days) ~ "continuous",
+    c(delayed_neuro,
+         parkinsonian_neurotoxicity_yes_no,
+         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no) 
+    ~ "categorical"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
+    digits = all_continuous() ~ 1,
+    missing = "no"
+    ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl2 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(steroid_use_yes_no, tocilizumab_yes_no, 
+         anakinra_yes_no) %>% 
+  tbl_summary(type = list(
+    c(steroid_use_yes_no, tocilizumab_yes_no, 
+      anakinra_yes_no) ~ "categorical"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1
+    ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl3 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(MRD_day30,
+         ORR_30days,
+         day30_response,
+         day30_response_v2) %>% 
+  tbl_summary(type = list(
+    c(MRD_day30) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl4 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(day30_response_v2 == "sCR or CR") %>% 
+  select(MRD_day30) %>% 
+  tbl_summary(type = list(
+    c(MRD_day30) ~ "categorical"),
+    label = list(MRD_day30 ~ 
+                   "MRD_day30 within CR/sCR"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl5 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(MRD_mon3,
+         ORR_mon3,
+         mon3_response,
+         mon3_response_v2) %>% 
+  tbl_summary(type = list(
+    c(MRD_mon3) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl6 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(mon3_response_v2 == "sCR or CR") %>% 
+  select(MRD_mon3) %>% 
+  tbl_summary(type = list(c(MRD_mon3) ~ "categorical"),
+              label = list(MRD_mon3 ~ "MRD_mon3 within CR/sCR"),
+              digits = all_continuous() ~ 1,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl7 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(best_response, best_response_MRD) %>% 
+  tbl_summary(#type = list(c(MRD_mon3) ~ "categorical"),
+              # label = list(best_response ~ "best response in the first 90 days"),
+              digits = all_continuous() ~ 1,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl8 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(best_response == "sCR or CR") %>% 
+  select(best_response_MRD) %>% 
+  tbl_summary(type = list(c(best_response_MRD) ~ "categorical"),
+              label = list(best_response_MRD ~ "best_response_MRD within CR/sCR"),
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() #%>%
+  # gt::tab_source_note(gt::md("**At 30days: <br>
+  #                            1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
+  #                            1 patients was not evaluated. <br>
+  #                            At 90days: <br>
+  #                            1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
+  #                            1 patient is not Heme not evaluable; <br>
+  #                            2 patients were not evaluated; <br>
+  #                            1 patients is not evaluable by death**"))
+
+```
+
+<!-- For responses make denominator evaluable patients -->
+<!-- Patient who died or was lost to follow-up or had non-secretory disease would not be evaluable -->
+
+## Table 3. Bone marrow biopsy findings
+```{r}
+tbl1 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select("marrow cellularity" = marrow_cellularity_baseline_normo_hypo_hyper, 
+         "marrow cellularity (%)" = marrow_cellularity_baseline_percent,
+         "% CD138 positive by IHC" = marrow_cd138_baseline_percent,
+         "is cellularity variable?"= contains("marrow_cellularity_baseline") & contains("is_variable_"),
+         "Fibrosis grade" = marrow_fibrosis_baseline_0_1_2_3, 
+         "Dysplasia present" = marrow_dysplasia_baseline_yes_no
+  ) %>% 
+  tbl_summary(type = list(
+    c("marrow cellularity (%)", "% CD138 positive by IHC",
+      "Fibrosis grade") ~ "continuous",
+    c("Dysplasia present") ~ "categorical"
+  ),
+  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+  digits = all_continuous() ~ 1,
+  missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl2 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select("marrow cellularity" = marrow_cellularity_day_30_normo_hypo_hyper, 
+         "marrow cellularity (%)" = marrow_percent_cellularity_day_30,
+         "% CD138 positive by IHC" = marrow_percent_cd138_day_30, 
+         "is cellularity variable?"= contains("marrow_cellularity_day_30") & contains("is_variable_"),
+         "Fibrosis grade" = marrow_fibrosis_day_30_0_1_2_3, 
+         "Dysplasia present" = marrow_dysplasia_day_30_yes_no
+  ) %>% 
+  tbl_summary(type = list(
+    c("marrow cellularity (%)", "% CD138 positive by IHC",
+      "Fibrosis grade") ~ "continuous",
+    c("Dysplasia present") ~ "categorical"
+  ),
+  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+  digits = all_continuous() ~ 1,
+  missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl3 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select("marrow cellularity" = marrow_cellularity_day_90_normo_hypo_hyper, 
+         "marrow cellularity (%)" = marrow_percent_cellularity_day_90,
+         "% CD138 positive by IHC" = marrow_percent_cd138_day_90, 
+         "is cellularity variable?"= contains("marrow_cellularity_day_90") & contains("is_variable_"),
+         "Fibrosis grade" = marrow_fibrosis_day_90_0_1_2_3, 
+         "Dysplasia present" = marrow_dysplasia_day_90_yes_no
+  ) %>% 
+  tbl_summary(type = list(
+    c("marrow cellularity (%)", "% CD138 positive by IHC",
+      "Fibrosis grade") ~ "continuous",
+    c("Dysplasia present") ~ "categorical"
+  ),
+  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+  digits = all_continuous() ~ 1,
+  missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl4 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select("marrow cellularity" = marrow_cellularity_day_180_normo_hypo_hyper, 
+         "marrow cellularity (%)" = marrow_percent_cellularity_day_180,
+         "% CD138 positive by IHC" = marrow_percent_cd138_day_180, 
+         "is cellularity variable?"= contains("marrow_cellularity_day_180") & contains("is_variable_"),
+         "Fibrosis grade" = marrow_fibrosis_day_180_0_1_2_3, 
+         "Dysplasia present" = marrow_dysplasia_day_180_yes_no
+  ) %>% 
+  tbl_summary(type = list(
+    c("marrow cellularity (%)", "% CD138 positive by IHC",
+      "Fibrosis grade") ~ "continuous",
+    c("Dysplasia present") ~ "categorical"
+  ),
+  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+  digits = all_continuous() ~ 1,
+  missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl_merge(list(tbl1, tbl2, tbl3, tbl4), 
+          tab_spanner = c("Baseline", "Day 30", "Day 90", "Day 180"))
+```
+
+## Table 4. Supportive therapies and engraftment
+Jenn did it for the ide-cel paper
+
+```{r}
+# cart1 %>% 
+#   distinct(pt_identifier, .keep_all = TRUE) %>% 
+#   select(`need_for_g_csf_post_infus_yes_1_no_0`, `First Day of GCSF`, `Last Day of GCSF`,
+#          `cd34_stem_cell_boost_yes_1_no_0`, `Day of stem cell boost`, `cell_dose_million_cells`,
+#          `Engraftment Day`,
+#          `rbc_transfusion_within_30d_post_cart_yes_1_no_0`, `plt_transfusion_within_30d_post_cart_yes_1_no_0`, 
+#          `rbc_transfusion_30d_post_cart_yes_1_no_0`, `plt_transfusion_30d_post_cart_yes_1_no_0`,
+#          `need_for_ivig_yes_1_no_0`, `First day of IVIG`, `Last day of IVIG`
+#   ) %>% 
+#   tbl_summary(type = list(
+#     c(`Day of stem cell boost`, `cell_dose_million_cells`,
+#     `Last day of IVIG`) ~ "continuous",
+#     c(`need_for_g_csf_post_infus_yes_1_no_0`,
+#       `cd34_stem_cell_boost_yes_1_no_0`,
+#       `rbc_transfusion_within_30d_post_cart_yes_1_no_0`, `plt_transfusion_within_30d_post_cart_yes_1_no_0`, 
+#          `rbc_transfusion_30d_post_cart_yes_1_no_0`, `plt_transfusion_30d_post_cart_yes_1_no_0`,
+#       `need_for_ivig_yes_1_no_0`) ~ "categorical"
+#   ),
+#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+#             digits = all_continuous() ~ 1) %>% 
+#   bold_labels() %>% add_stat_label()
+```
+
+## Table S1. Apheresis and product characteristics
+```{r}
+cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(tbv, whole_blood_processed_m_l,
+         final_collection_volume_m_l, 
+         tbv_processed, 
+         access_type,
+         run_time_min,
+         time_from_apheresis_to_car_t_infusion_days, total_bags,
+         total_dose_volume_m_l, cell_dose_million_cells
+  ) %>% 
+  tbl_summary(type = list(
+    c(tbv, total_bags) ~ "continuous"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1,
+  missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+```
+
+## Table S2. Cytopenias following ide-cel
+
+```{r}
+tbl1 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select("Leukopenia" = Leukopenia_apheresis, 
+         "Grade3+ Leukopenia" = gr3_Leukopenia_apheresis, 
+         "Neutropenia" = Neutropenia_apheresis, 
+         "Grade3+ Neutropenia" = gr3_Neutropenia_apheresis, 
+         "Anemia" = Anemia_apheresis, 
+         "Grade3+ Anemia" = gr3_Anemia_apheresis, 
+         "Thrombocytopenia" = Thrombocytopenia_apheresis, 
+         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_apheresis,
+         "Any Cytopenia" = cytopenia_apheresis,
+         "Grade3+ Cytopenia" = gr3_cytopenia_apheresis
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl2 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select("Leukopenia" = `Leukopenia_-5d`, 
+         "Grade3+ Leukopenia" = `gr3_Leukopenia_-5d`, 
+         "Neutropenia" = `Neutropenia_-5d`, 
+         "Grade3+ Neutropenia" = `gr3_Neutropenia_-5d`,
+         "Anemia" = `Anemia_-5d`, 
+         "Grade3+ Anemia" = `gr3_Anemia_-5d`, 
+         "Thrombocytopenia" = `Thrombocytopenia_-5d`, 
+         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_-5d`,
+         "Any Cytopenia" = `cytopenia_-5d`,
+         "Grade3+ Cytopenia" = `gr3_cytopenia_-5d`
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl3 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select("Leukopenia" = Leukopenia_0d, 
+         "Grade3+ Leukopenia" = gr3_Leukopenia_0d, 
+         "Neutropenia" = Neutropenia_0d, 
+         "Grade3+ Neutropenia" = gr3_Neutropenia_0d, 
+         "Anemia" = Anemia_0d, 
+         "Grade3+ Anemia" = gr3_Anemia_0d,
+         "Thrombocytopenia" = Thrombocytopenia_0d, 
+         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_0d,
+         "Any Cytopenia" = cytopenia_0d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_0d
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl4 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select("Leukopenia" = Leukopenia_7d, 
+         "Grade3+ Leukopenia" = gr3_Leukopenia_7d, 
+         "Neutropenia" = Neutropenia_7d, 
+         "Grade3+ Neutropenia" = gr3_Neutropenia_7d, 
+         "Anemia" = Anemia_7d, 
+         "Grade3+ Anemia" = gr3_Anemia_7d, 
+         "Thrombocytopenia" = Thrombocytopenia_7d, 
+         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_7d,
+         "Any Cytopenia" = cytopenia_7d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_7d
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl5 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_14days)) %>% ######################### Fix evaluable---------- here
+  filter(os_from_infusion_months > (14 / 30.417)) %>% 
+select("Leukopenia" = Leukopenia_14d, 
+       "Grade3+ Leukopenia" = gr3_Leukopenia_14d, 
+       "Neutropenia" = Neutropenia_14d, 
+       "Grade3+ Neutropenia" = gr3_Neutropenia_14d,
+       "Anemia" = Anemia_14d, 
+       "Grade3+ Anemia" = gr3_Anemia_14d,
+       "Thrombocytopenia" = Thrombocytopenia_14d, 
+       "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_14d,
+       "Any Cytopenia" = cytopenia_14d,
+       "Grade3+ Cytopenia" = gr3_cytopenia_14d
+) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl6 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_21days)) %>% 
+  filter(os_from_infusion_months > (21 / 30.417)) %>% 
+  select("Leukopenia" = Leukopenia_21d,
+         "Grade3+ Leukopenia" = gr3_Leukopenia_21d, 
+         "Neutropenia" = Neutropenia_21d, 
+         "Grade3+ Neutropenia" = gr3_Neutropenia_21d, 
+         "Anemia" = Anemia_21d, 
+         "Grade3+ Anemia" = gr3_Anemia_21d,
+         "Thrombocytopenia" = Thrombocytopenia_21d, 
+         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_21d,
+         "Any Cytopenia" = cytopenia_21d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_21d
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl7 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% 
+  filter(os_from_infusion_months > (30 / 30.417)) %>% 
+  select("Leukopenia" = Leukopenia_30d, 
+         "Grade3+ Leukopenia" = gr3_Leukopenia_30d,
+         "Neutropenia" = Neutropenia_30d, 
+         "Grade3+ Neutropenia" = gr3_Neutropenia_30d,
+         "Anemia" = Anemia_30d, 
+         "Grade3+ Anemia" = gr3_Anemia_30d, 
+         "Thrombocytopenia" = Thrombocytopenia_30d,
+         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_30d,
+         "Any Cytopenia" = cytopenia_30d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_30d
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl8 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_90days)) %>% 
+  filter(os_from_infusion_months > 3) %>% 
+  select("Leukopenia" = Leukopenia_90d, 
+         "Grade3+ Leukopenia" = gr3_Leukopenia_90d,
+         "Neutropenia" = Neutropenia_90d, 
+         "Grade3+ Neutropenia" = gr3_Neutropenia_90d,
+         "Anemia" = Anemia_90d,
+         "Grade3+ Anemia" = gr3_Anemia_90d,
+         "Thrombocytopenia" = Thrombocytopenia_90d, 
+         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_90d,
+         "Any Cytopenia" = cytopenia_90d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_90d
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl9 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_180days)) %>% 
+  filter(os_from_infusion_months > 6) %>% 
+  select("Leukopenia" = Leukopenia_180d, 
+         "Grade3+ Leukopenia" = gr3_Leukopenia_180d,
+         "Neutropenia" = Neutropenia_180d, 
+         "Grade3+ Neutropenia" = gr3_Neutropenia_180d,
+         "Anemia" = Anemia_180d,
+         "Grade3+ Anemia" = gr3_Anemia_180d,
+         "Thrombocytopenia" = Thrombocytopenia_180d, 
+         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_180d,
+         "Any Cytopenia" = cytopenia_180d,
+         "Grade3+ Cytopenia" = gr3_cytopenia_180d
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8, tbl9), 
+          tab_spanner = c("Apheresis", "Day -5", "Day 0", 
+                          "Day 7", "Day 14", "Day 21",
+                          "Day 30", "Day 90", "Day 180")) %>% as_gt() #%>%
+# gt::tab_source_note(gt::md("**Not evaluable patients are removed from the denominator <br>
+#                            1 patient has missing 90 days values**"))
+```
+
+## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30
+```{r}
+cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(bm_plasma_cell_percent_at_pre_ld,
+         number_of_prior_lines_of_therapy,
+         number_prior_lines_therapy,
+         # `Days from last bridging to CAR-T infusion`,         ################# Not in data?
+         lenalidomide_exposed_vs_refractory_vs_not_exposed,
+         bortezomib_exposed_vs_refractory_vs_not_exposed,
+         carfilzomib_exposed_vs_refractory_vs_not_exposed,
+         pomalidomide_exposed_vs_refractory_vs_not_exposed,
+         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         "Marrow Cellularity (%) at Day30" = marrow_percent_cellularity_day_30,
+         age, agecat, male_sex, sex,
+         extramedullary_disease_yes_no, 
+         high_marrow_burden_50_percent, ecog_at_ld, 
+         r_iss_at_car_t_infusion, cytogenetics, 
+         bridging_therapy_yes_no,
+         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
+         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
+         Prior_bcma_therapy,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
+         cytopenia_apheresis, Neutropenia_apheresis,
+         Anemia_apheresis,Thrombocytopenia_apheresis,
+         `cytopenia_-5d`, `Neutropenia_-5d`,
+         `Anemia_-5d`, `Thrombocytopenia_-5d`,
+         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
+         gr3_cytopenia_30d) %>% 
+  tbl_summary(by = gr3_cytopenia_30d,
+              type = list(
+                c(extramedullary_disease_yes_no,
+                  bm_plasma_cell_percent_at_pre_ld,
+                  cytopenia_apheresis,`cytopenia_-5d`,
+                  cytogenetics,
+                  bridging_therapy_yes_no,
+                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+                  prior_auto_sct_yes_no,
+                  Prior_bcma_therapy,
+                  immuno, proteasome, dara,
+                  doubleref, tripleref, pentaref,
+                  cytopenia_apheresis, Neutropenia_apheresis,
+                  Anemia_apheresis,Thrombocytopenia_apheresis,
+                  `cytopenia_-5d`, `Neutropenia_-5d`,
+                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
+                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
+                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
+                ~"categorical",
+                c(bm_plasma_cell_percent_at_pre_ld,
+                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
+                ~ "continuous"),
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>% add_p() %>% 
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
+```
+
+## Table S3. Patient characteristics by grade 3+ cytopenia at Day 90
+```{r}
+cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_90days)) %>%  ######################### Fix evaluable----------
+  select(bm_plasma_cell_percent_at_pre_ld,
+         number_of_prior_lines_of_therapy,
+         number_prior_lines_therapy,
+         # `Days from last bridging to CAR-T infusion`,
+         lenalidomide_exposed_vs_refractory_vs_not_exposed,
+         bortezomib_exposed_vs_refractory_vs_not_exposed,
+         carfilzomib_exposed_vs_refractory_vs_not_exposed,
+         pomalidomide_exposed_vs_refractory_vs_not_exposed,
+         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         "Marrow Cellularity (%) at Day90" = marrow_percent_cellularity_day_90,
+         age, agecat, male_sex, sex,
+         extramedullary_disease_yes_no, 
+         high_marrow_burden_50_percent, ecog_at_ld, r_iss_at_car_t_infusion, cytogenetics, 
+         bridging_therapy_yes_no,
+         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
+         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
+         Prior_bcma_therapy,
+         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
+         cytopenia_apheresis, Neutropenia_apheresis,
+         Anemia_apheresis,Thrombocytopenia_apheresis,
+         `cytopenia_-5d`, `Neutropenia_-5d`,
+         `Anemia_-5d`, `Thrombocytopenia_-5d`,
+         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
+         gr3_cytopenia_90d) %>% 
+  tbl_summary(by = gr3_cytopenia_90d,
+              type = list(
+                c(extramedullary_disease_yes_no,
+                  bm_plasma_cell_percent_at_pre_ld,
+                  cytopenia_apheresis,`cytopenia_-5d`,
+                  cytogenetics,
+                  bridging_therapy_yes_no,
+                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+                  prior_auto_sct_yes_no,
+                  immuno, proteasome, dara,
+                  doubleref, tripleref, pentaref,
+                  cytopenia_apheresis, Neutropenia_apheresis,
+                  Anemia_apheresis,Thrombocytopenia_apheresis,
+                  `cytopenia_-5d`, `Neutropenia_-5d`,
+                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
+                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
+                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
+                ~ "categorical",
+                c(bm_plasma_cell_percent_at_pre_ld,
+                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day90`)
+                ~ "continuous"),
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>%  add_p() %>% 
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 90?**")
+```
+
+## Table S4. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
+```{r}
+tbl1 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(cell_dose_million_cells,
+         CRS_gradecat,
+         day_of_onset_crs_relative_to_infusion,
+         day_of_max_crs_relative_to_infusion,
+         duration_of_crs_days, 
+         ICANS_gradecat,
+         day_of_onset_icans_relative_to_infusion,
+         day_of_max_icans_relative_to_infusion,
+         duration_of_icans_days, 
+         delayed_neuro,
+         parkinsonian_neurotoxicity_yes_no,
+         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
+         delayed_neuro_type,
+         gr3_cytopenia_30d) %>% 
+  tbl_summary(by = gr3_cytopenia_30d,
+              type = list(
+                c(day_of_onset_crs_relative_to_infusion,
+                  day_of_max_crs_relative_to_infusion,
+                  duration_of_crs_days,
+                  day_of_onset_icans_relative_to_infusion,
+                  day_of_max_icans_relative_to_infusion,
+                  duration_of_icans_days) ~ "continuous",
+                c(delayed_neuro,
+                  other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
+                  parkinsonian_neurotoxicity_yes_no) ~ "categorical"),
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p() %>% 
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
+
+tbl2 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(steroid_use_yes_no, tocilizumab_yes_no, 
+         anakinra_yes_no, gr3_cytopenia_30d) %>% 
+  tbl_summary(by = gr3_cytopenia_30d,
+              type = list(
+    c(steroid_use_yes_no, tocilizumab_yes_no, 
+      anakinra_yes_no) ~ "categorical"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl3 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(#day_30_mrd_by_clono_seq_positive_vs_negative,
+         ORR_30days, CRorbetter_30days,
+         day30_response_v2, gr3_cytopenia_30d) %>% 
+  tbl_summary(by = gr3_cytopenia_30d,
+    #           type = list(
+    # c(day_30_mrd_by_clono_seq_positive_vs_negative) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
+
+# tbl4 <- cart1 %>% 
+#   distinct(pt_identifier, .keep_all = TRUE) %>% 
+#   filter(is.na(Not_evaluable_at_30days)) %>% 
+#   filter(day30_response_v2 == "sCR or CR") %>% 
+#   select(day_30_mrd_by_clono_seq_positive_vs_negative, gr3_cytopenia_30d) %>% 
+#   tbl_summary(by =gr3_cytopenia_30d,
+#               type = list(c(day_30_mrd_by_clono_seq_positive_vs_negative) ~ "categorical"),
+#               label = list(day_30_mrd_by_clono_seq_positive_vs_negative ~ "day_30_mrd_by_clono_seq_positive_vs_negative within CR/sCR"),
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>% 
+#   bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl5 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(#MRD_mon3,
+         ORR_mon3, CRorbetter_mon3,
+         mon3_response_v2, gr3_cytopenia_30d) %>% 
+  tbl_summary(by = gr3_cytopenia_30d,
+    #           type = list(
+    # c(MRD_mon3) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
+
+# tbl6 <- cart1 %>% 
+#   distinct(pt_identifier, .keep_all = TRUE) %>% 
+#   filter(is.na(Not_evaluable_at_30days)) %>% 
+#   filter(mon3_response_v2 == "sCR or CR") %>% 
+#   select(MRD_mon3, gr3_cytopenia_30d) %>% 
+#   tbl_summary(by =gr3_cytopenia_30d,
+#               type = list(c(MRD_mon3) ~ "categorical"),
+#               label = list(MRD_mon3 ~ "MRD_mon3 within CR/sCR"),
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>% 
+#   bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl7 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(best_response, gr3_cytopenia_30d) %>% 
+  tbl_summary(by = gr3_cytopenia_30d,
+              #type = list(c(MRD_mon3) ~ "categorical"),
+              label = list(best_response ~ "best response in the first 90 days"),
+              digits = all_continuous() ~ 1,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
+
+# tbl8 <- cart1 %>% 
+#   distinct(pt_identifier, .keep_all = TRUE) %>% 
+#   filter(is.na(Not_evaluable_at_30days)) %>% 
+#   filter(best_response == "sCR or CR") %>% 
+#   select(MRDneg_in_best_response, gr3_cytopenia_30d) %>% 
+#   tbl_summary(by =gr3_cytopenia_30d,
+#               type = list(c(MRDneg_in_best_response) ~ "categorical"),
+#               label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
+#               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+#               digits = all_continuous() ~ 1,
+#               missing = "no") %>% 
+#   bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl_stack(list(tbl1, tbl2, tbl3, tbl5, tbl7))
+```
+
+## Table S4. Details of infections after ide-cel
+Jenn
+
+## Table S5. Patients with infections in the first 30 days by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
+```{r}
+cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(number_prior_lines_therapy,
+         number_of_prior_lines_of_therapy,
+         prior_auto_sct_yes_no,
+         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
+         Prior_bcma_therapy,
+         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+         # `Days from last bridging to CAR-T infusion`,
+         cell_dose_million_cells,
+         need_for_g_csf_post_infus_yes_1_no_0,
+         cd34_stem_cell_boost_yes_1_no_0,
+         need_for_ivig_yes_1_no_0,
+
+         CRS_gradecat, ICANS_gradecat,
+         delayed_neuro,
+         parkinsonian_neurotoxicity_yes_no,
+         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
+         delayed_neuro_type,
+         steroid_use_yes_no, 
+         tocilizumab_yes_no, anakinra_yes_no,
+         bridging_therapy_yes_no, any_infection) %>% 
+  tbl_summary(by= any_infection, 
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              type = list(all_dichotomous() ~ "categorical", 
+                          number_of_prior_lines_of_therapy ~ "continuous")) %>%
+  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any infection**")
+
+cilta %>% 
+  arrange(pt_identifier, desc(any_infection), desc(any_sevinfection)) %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(number_prior_lines_therapy,
+         number_of_prior_lines_of_therapy,
+         prior_auto_sct_yes_no,
+         Prior_bcma_therapy,
+         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+         # `Days from last bridging to CAR-T infusion`,
+         cell_dose_million_cells,
+         need_for_g_csf_post_infus_yes_1_no_0,
+         cd34_stem_cell_boost_yes_1_no_0,
+         need_for_ivig_yes_1_no_0,
+
+         CRS_gradecat, ICANS_gradecat,
+         delayed_neuro,
+         parkinsonian_neurotoxicity_yes_no,
+         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
+         delayed_neuro_type,
+         steroid_use_yes_no, 
+         tocilizumab_yes_no, anakinra_yes_no,
+         bridging_therapy_yes_no, any_sevinfection) %>% 
+  tbl_summary(by=any_sevinfection, 
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              type = list(all_dichotomous() ~ "categorical", 
+                          number_of_prior_lines_of_therapy ~ "continuous")) %>%
+  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
+```
+
+## Table S6. Patients with infections in the first 100 days by cell counts and immunoglobulin levels
+CCT5019-0512 has a time to infection but no in Any Infection but yes in Any Severe Infection
+```{r}
+cilta %>%
+  filter(time_from_infusion_to_infection_days <= 100 |
+           any_infection == "No") %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(ig_g_day_5, ig_a_day_5, ig_m_day_5,
+         wbc_day_5, anc_day_5_k_ul,
+         # `Eos day -5 (k/ul)`, `Monos day -5 (k/ul)`, 
+         # `CD3 apheresis`, `CD56 apheresis`, 
+         cd4_apheresis, cd8_apheresis,
+         cd19_apheresis, 
+         ig_g_day_90, ig_a_day_90, ig_m_day_90,
+         wbc_day_90, anc_day_90,
+         # `Eos day +90`, `Monos day +90`,
+         # `CD3 day +90`, `CD56 day +90`, 
+         cd4_day_90, cd8_day_90,
+         cd19_day_90,
+         any_infection) %>% 
+  tbl_summary(by = any_infection,
+              type = list(everything() ~ "continuous"),
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1) %>% 
+  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any infection**")
+
+cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 100 |
+           any_sevinfection == "No") %>% 
+  arrange(pt_identifier, desc(any_infection), desc(any_sevinfection)) %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(ig_g_day_5, ig_a_day_5, ig_m_day_5,
+         wbc_day_5, anc_day_5_k_ul,
+         # `Eos day -5 (k/ul)`, `Monos day -5 (k/ul)`, 
+         # `CD3 apheresis`, `CD56 apheresis`, 
+         cd4_apheresis, cd8_apheresis,
+         cd19_apheresis, 
+         ig_g_day_90, ig_a_day_90, ig_m_day_90,
+         wbc_day_90, anc_day_90,
+         # `Eos day +90`, `Monos day +90`,
+         # `CD3 day +90`, `CD56 day +90`, 
+         cd4_day_90, cd8_day_90,
+         cd19_day_90,
+         any_sevinfection) %>% 
+  tbl_summary(by = any_sevinfection,
+              type = list(everything() ~ "continuous"),
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1) %>% 
+  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
+```
+
+## Table SX. Immunoglobulin levels excluding patients with that type of myeloma 
+(myeloma_involved_heavy_chain != "Igg")
+Should I limit to infections in the first 100 days?
+```{r}
+cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(myeloma_involved_heavy_chain != "Igg" | is.na(myeloma_involved_heavy_chain)) %>% 
+  select(ig_g_day_5, ig_g_day_30,
+         ig_g_day_90, any_infection) %>% 
+  tbl_summary(by = any_infection,
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  add_p() %>% bold_labels() %>% add_stat_label() %>% 
+  add_overall() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any infection**")
+
+cilta %>% 
+  arrange(pt_identifier, desc(any_infection), desc(any_sevinfection)) %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(myeloma_involved_heavy_chain != "Igg" | is.na(myeloma_involved_heavy_chain)) %>% 
+  select(ig_g_day_5, ig_g_day_30,
+         ig_g_day_90, any_sevinfection) %>% 
+  tbl_summary(by = any_sevinfection,
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  add_p() %>% bold_labels() %>% add_stat_label() %>% 
+  add_overall() %>% 
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
+```
+
+### Figures
+```{r}
+fig_dat <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE)
+```
+
+## Figure 1. Consort diagram
+
+## Figure 2. Inflammatory markers after ide-cel
+
+```{r, fig.height=12}
+LDH <- fig_dat %>% 
+  select(pt_identifier, starts_with("ldh_")) %>% 
+  pivot_longer(cols = -c(pt_identifier)) %>% 
+  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
+         day = case_when(
+           str_detect(name, "apheresis")            ~ "-28",
+           str_detect(name, "pretreatment")         ~ "-28",
+           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
+         ), 
+         day = case_when(
+           day == 5                                 ~ "-5",
+           TRUE                                     ~ day
+         ),
+         day = factor(day, levels = c("-28", "-5", "0", 
+                                      "7", "14", "21", "30", "90", "180"))) %>% 
+  ggplot(aes(x=day, y=value)) + 
+  geom_boxplot() + 
+  xlab("Days") + ylab("LDH represented with a log2 scale") + 
+  theme_classic() + ggtitle("LDH") + 
+  scale_y_continuous(trans = "log2") +
+  stat_compare_means(label.x = 5 
+                     # aes(label = paste0("p = ", ..p.format..))
+  #                  aes(
+  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
+  )
+
+# cart1$`Ferritin day +7`[cart1$`Ferritin day +7`==">33511"] <- 33511
+# cart1$`Ferritin day +7` <- as.numeric(cart1$`Ferritin day +7`)
+Ferritin <- fig_dat %>% 
+  select(pt_identifier, starts_with("ferritin_")) %>% 
+  pivot_longer(cols = -c(pt_identifier)) %>% 
+  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
+         day = case_when(
+           str_detect(name, "apheresis")            ~ "-28",
+           str_detect(name, "pretreatment")         ~ "-28",
+           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
+         ), 
+         day = case_when(
+           day == 5                                 ~ "-5",
+           TRUE                                     ~ day
+         ),
+         day = factor(day, levels = c("-28", "-5", "0", 
+                                      "7", "14", "21", "30", "90", "180"))) %>% 
+  ggplot(aes(x=day, y=value)) + 
+  geom_boxplot() + 
+  xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
+  theme_classic() + ggtitle("Ferritin") + 
+  scale_y_continuous(trans = "log2") +
+  stat_compare_means(label.x = 5 
+                     # aes(label = paste0("p = ", ..p.format..))
+  #                  aes(
+  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
+  )
+
+# cart1$`CRP Pre-Leukapheresis`[cart1$`CRP Pre-Leukapheresis`=="<0.03"] <- 0.07
+# cart1$`CRP Pre-Leukapheresis` <- as.numeric(cart1$`CRP Pre-Leukapheresis`)
+# cart1$`CRP day +14`[cart1$`CRP day +14`=="<0.03"] <- 0.07
+# cart1$`CRP day +14` <- as.numeric(cart1$`CRP day +14`)
+# cart1$`CRP day +21`[cart1$`CRP day +21`=="<0.03"] <- 0.07
+# cart1$`CRP day +21` <- as.numeric(cart1$`CRP day +21`)
+# cart1$`CRP day +30`[cart1$`CRP day +30`=="<0.03"] <- 0.07
+# cart1$`CRP day +30` <- as.numeric(cart1$`CRP day +30`)
+CRP <- fig_dat %>% 
+  select(pt_identifier, starts_with("crp_")) %>% 
+  pivot_longer(cols = -c(pt_identifier)) %>% 
+  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
+         day = case_when(
+           str_detect(name, "apheresis")            ~ "-28",
+           str_detect(name, "pretreatment")         ~ "-28",
+           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
+         ), 
+         day = case_when(
+           day == 5                                 ~ "-5",
+           TRUE                                     ~ day
+         ),
+         day = factor(day, levels = c("-28", "-5", "0", 
+                                      "7", "14", "21", "30", "90", "180"))) %>% 
+  ggplot(aes(x=day, y=value)) + 
+  geom_boxplot() + 
+  xlab("Days") + ylab("CRP represented with a log2 scale") + 
+  theme_classic() + ggtitle("CRP") + 
+  scale_y_continuous(trans = "log2") +
+  stat_compare_means(label.x = 5 
+                     # aes(label = paste0("p = ", ..p.format..))
+  #                  aes(
+  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
+  )
+
+(LDH) /
+(Ferritin) /
+(CRP)+
+plot_annotation(tag_levels = "A")
+```
+
+## Figure 3. Cellular and humoral immune reconstitution after ide-cel
+```{r timeserie, fig.width=12, fig.height=12}
+# WBC
+val <- fig_dat %>% reframe(wbc_apheresis = MedianCI(wbc_apheresis, conf.level = 0.95, na.rm = TRUE),
+                  wbc_day_5 = MedianCI(wbc_day_5, conf.level = 0.95, na.rm = TRUE),
+                  wbc_day_0_k_u_l = MedianCI(wbc_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE),
+                  wbc_day_7 = MedianCI(wbc_day_7, conf.level = 0.95, na.rm = TRUE),
+                  wbc_day_14 = MedianCI(wbc_day_14, conf.level = 0.95, na.rm = TRUE),
+                  wbc_day_21 = MedianCI(wbc_day_21, conf.level = 0.95, na.rm = TRUE),
+                  wbc_day_30 = MedianCI(wbc_day_30, conf.level = 0.95, na.rm = TRUE),
+                  wbc_day_90 = MedianCI(wbc_day_90, conf.level = 0.95, na.rm = TRUE),
+                  wbc_day_180 = MedianCI(wbc_day_180, conf.level = 0.95, na.rm = TRUE))
+timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
+WBC_fig <-
+  data.frame(timepoints,
+             t(val))
+
+WBC_fig <-
+  WBC_fig %>%
+  ggplot(aes(x = timepoints, y = X1, group = 1)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median WBC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  ) #+ ylim(0, 6)
+
+# ANC
+val <- fig_dat %>% reframe(anc_apheresis = MedianCI(anc_apheresis, conf.level = 0.95, na.rm = TRUE),
+                  anc_day_5_k_ul = MedianCI(anc_day_5_k_ul, conf.level = 0.95, na.rm = TRUE),
+                  anc_day_0_k_u_l = MedianCI(anc_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE),
+                  anc_day_7 = MedianCI(anc_day_7, conf.level = 0.95, na.rm = TRUE),
+                  anc_day_14 = MedianCI(anc_day_14, conf.level = 0.95, na.rm = TRUE),
+                  anc_day_21 = MedianCI(anc_day_21, conf.level = 0.95, na.rm = TRUE),
+                  anc_day_30 = MedianCI(anc_day_30, conf.level = 0.95, na.rm = TRUE),
+                  anc_day_90 = MedianCI(anc_day_90, conf.level = 0.95, na.rm = TRUE),
+                  anc_day_180 = MedianCI(anc_day_180, conf.level = 0.95, na.rm = TRUE))
+timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
+ANC_fig <-
+  data.frame(timepoints,
+             t(val))
+
+ANC_fig <- ANC_fig %>% 
+  ggplot(aes(x = timepoints, y = X1, group = 1)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median ANC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  ) #+ ylim(0, 6)
+
+# HB
+val <- fig_dat %>% reframe(hb_apheresis = MedianCI(hb_apheresis, conf.level = 0.95, na.rm = TRUE),
+                  hb_day_5 = MedianCI(hb_day_5, conf.level = 0.95, na.rm = TRUE),
+                  hb_day_0_k_u_l = MedianCI(hb_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE),
+                  hb_day_7 = MedianCI(hb_day_7, conf.level = 0.95, na.rm = TRUE),
+                  hb_day_14 = MedianCI(hb_day_14, conf.level = 0.95, na.rm = TRUE),
+                  hb_day_21 = MedianCI(hb_day_21, conf.level = 0.95, na.rm = TRUE),
+                  hb_day_30 = MedianCI(hb_day_30, conf.level = 0.95, na.rm = TRUE),
+                  hb_day_90 = MedianCI(hb_day_90, conf.level = 0.95, na.rm = TRUE),
+                  hb_day_180 = MedianCI(hb_day_180, conf.level = 0.95, na.rm = TRUE))
+timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
+Hb_fig <-
+  data.frame(timepoints,
+             t(val))
+
+Hb_fig <- Hb_fig %>% 
+  ggplot(aes(x = timepoints, y = X1, group = 1)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median Hb") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  ) # +ylim(7.5, 12)
+
+# ALC
+val <- fig_dat %>% reframe(alc_apheresis = MedianCI(alc_apheresis, conf.level = 0.95, na.rm = TRUE),
+                  alc_day_5_k_ul = MedianCI(alc_day_5_k_ul, conf.level = 0.95, na.rm = TRUE),
+                  alc_day_0_k_u_l = MedianCI(alc_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE),
+                  alc_day_7 = MedianCI(alc_day_7, conf.level = 0.95, na.rm = TRUE),
+                  alc_day_14 = MedianCI(alc_day_14, conf.level = 0.95, na.rm = TRUE),
+                  alc_day_21 = MedianCI(alc_day_21, conf.level = 0.95, na.rm = TRUE),
+                  alc_day_30 = MedianCI(alc_day_30, conf.level = 0.95, na.rm = TRUE),
+                  alc_day_90 = MedianCI(alc_day_90, conf.level = 0.95, na.rm = TRUE),
+                  alc_day_180 = MedianCI(alc_day_180, conf.level = 0.95, na.rm = TRUE))
+timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
+ALC_fig <-
+  data.frame(timepoints,
+             t(val))
+
+ALC_fig <- ALC_fig %>% 
+  ggplot(aes(x = timepoints, y = X1, group = 1)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median ALC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  ) # + ylim(0, 1.1)
+
+# Plt
+val <- fig_dat %>% reframe(plt_apheresis = MedianCI(plt_apheresis, conf.level = 0.95, na.rm = TRUE),
+                  plt_day_5_k_ul = MedianCI(plt_day_5_k_ul, conf.level = 0.95, na.rm = TRUE),
+                  plt_day_0_k_u_l = MedianCI(plt_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE),
+                  plt_day_7 = MedianCI(plt_day_7, conf.level = 0.95, na.rm = TRUE),
+                  plt_day_14 = MedianCI(plt_day_14, conf.level = 0.95, na.rm = TRUE),
+                  plt_day_21 = MedianCI(plt_day_21, conf.level = 0.95, na.rm = TRUE),
+                  plt_day_30 = MedianCI(plt_day_30, conf.level = 0.95, na.rm = TRUE),
+                  plt_day_90 = MedianCI(plt_day_90, conf.level = 0.95, na.rm = TRUE),
+                  plt_day_180 = MedianCI(plt_day_180, conf.level = 0.95, na.rm = TRUE))
+timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
+Plt_fig <-
+  data.frame(timepoints,
+             t(val))
+
+Plt_fig <- Plt_fig %>% 
+  ggplot(aes(x = timepoints, y = X1, group = 1)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median Plt") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+  ) # + ylim(20, 170)
+
+# IgG
+timepoints2 <- c(-28, -5, 30, 90, 180)
+val <- fig_dat %>% reframe(ig_g_apheresis = MedianCI(ig_g_apheresis, conf.level = 0.95, na.rm = TRUE),
+                  ig_g_day_5 = MedianCI(ig_g_day_5, conf.level = 0.95, na.rm = TRUE),
+                  ig_g_day_30 = MedianCI(ig_g_day_30, conf.level = 0.95, na.rm = TRUE),
+                  ig_g_day_90 = MedianCI(ig_g_day_90, conf.level = 0.95, na.rm = TRUE),
+                  ig_g_day_180 = MedianCI(ig_g_day_180, conf.level = 0.95, na.rm = TRUE))
+IgG_fig <-
+  data.frame(timepoints2,
+             t(val))
+
+IgG_fig <- IgG_fig %>% 
+  ggplot(aes(x = timepoints2, y = X1, group = 1)) + 
+  geom_line(col = "blue") +
+  xlab("Days relative to infusion") + 
+  ylab("Median IgG") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 30, 90, 180),
+    labels = c("Apheresis", "-5", "0", "30", "90", "180"))# + 
+  # ylim(0, 2000)
+
+# CD4
+timepoints3 <- c(-28, 30, 90, 180)
+val <- fig_dat %>% reframe(cd4_apheresis = MedianCI(cd4_apheresis, conf.level = 0.95, na.rm = TRUE),
+                  cd4_day_30 = MedianCI(cd4_day_30, conf.level = 0.95, na.rm = TRUE),
+                  cd4_day_90 = MedianCI(cd4_day_90, conf.level = 0.95, na.rm = TRUE),
+                  cd4_day_180 = MedianCI(cd4_day_180, conf.level = 0.95, na.rm = TRUE))
+CD4_fig <-
+  data.frame(timepoints3,
+             t(val))
+
+CD4_fig <- CD4_fig %>% 
+  ggplot(aes(x = timepoints3, y = X1, group = 1)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD4") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90, 180),
+    labels = c("Apheresis", "30", "90", "180")
+  )
+
+#CD8
+timepoints3 <- c(-28, 30, 90, 180)
+val <- fig_dat %>% reframe(cd8_apheresis = MedianCI(cd8_apheresis, conf.level = 0.95, na.rm = TRUE),
+                  cd8_day_30 = MedianCI(cd8_day_30, conf.level = 0.95, na.rm = TRUE),
+                  cd8_day_90 = MedianCI(cd8_day_90, conf.level = 0.95, na.rm = TRUE),
+                  cd8_day_180 = MedianCI(cd8_day_180, conf.level = 0.95, na.rm = TRUE))
+CD8_fig <-
+  data.frame(timepoints3,
+             t(val))
+
+CD8_fig <- CD8_fig %>% 
+  ggplot(aes(x = timepoints3, y = X1, group = 1)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD8") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90, 180),
+    labels = c("Apheresis", "30", "90", "180")
+  )
+
+#CD19
+timepoints3 <- c(-28, 30, 90, 180)
+val <- fig_dat %>% reframe(cd19_apheresis = MedianCI(cd19_apheresis, conf.level = 0.95, na.rm = TRUE),
+                  cd19_day_30 = MedianCI(cd19_day_30, conf.level = 0.95, na.rm = TRUE),
+                  cd19_day_90 = MedianCI(cd19_day_90, conf.level = 0.95, na.rm = TRUE),
+                  cd19_day_180 = MedianCI(cd19_day_180, conf.level = 0.95, na.rm = TRUE))
+CD19_fig <-
+  data.frame(timepoints3,
+             t(val))
+
+CD19_fig <- CD19_fig %>% 
+  ggplot(aes(x = timepoints3, y = X1, group = 1)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD19") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90, 180),
+    labels = c("Apheresis", "30", "90", "180")
+  )
+
+(WBC_fig | ANC_fig | CD4_fig) /
+  (Hb_fig | ALC_fig | CD8_fig) /
+  (Plt_fig | IgG_fig | CD19_fig) +
+  plot_annotation(tag_levels = "A")
+```
+<br>
+
+Aggregated median
+```{r timeserie aggreagate med, fig.width=12, fig.height=12}
+fig_dat <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE)
+
+timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
+WBC_agg <- fig_dat %>% 
+  select(site, starts_with("wbc_")) %>% 
+  group_by(site) %>% 
+  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
+  ungroup() %>% select(-site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median WBC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
+  )
+
+ANC_agg <- fig_dat %>% 
+  select(site, starts_with("anc_"), -anc_0_75_x_10_9_l_0_75_k_u_l) %>% 
+  group_by(site) %>% 
+  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
+  ungroup() %>% select(-site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median ANC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
+  )
+
+Hb_agg <- fig_dat %>% 
+  select(site, starts_with("hb_")) %>% 
+  group_by(site) %>% 
+  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
+  ungroup() %>% select(-site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median Hb") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
+  )
+
+ALC_agg <- fig_dat %>% 
+  select(site, starts_with("alc_"), -alc_0_3_x_10_9_l_0_3k_u_l) %>% 
+  group_by(site) %>% 
+  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
+  ungroup() %>% select(-site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median ALC") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
+  )
+
+Plt_agg <- fig_dat %>% 
+  select(site, starts_with("plt_"), -c(starts_with("plt_transfusion"))) %>% 
+  group_by(site) %>% 
+  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
+  ungroup() %>% select(-site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median Plt") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
+  )
+
+timepoints2 <- c(-28, -5, 30, 90, 180)
+IgG_agg <- fig_dat %>% 
+  select(site, ig_g_apheresis, starts_with("ig_g_day")) %>% 
+  group_by(site) %>% 
+  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
+  ungroup() %>% select(-site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints2) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median Plt") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, -5, 0, 30, 90, 180),
+    labels = c("Apheresis", "-5", "0", "30", "90", "180")
+  )
+
+timepoints3 <- c(-28, 30, 90, 180)
+CD4_fig <- fig_dat %>% 
+  select(site, starts_with("cd4_")) %>% 
+  group_by(site) %>% 
+  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
+  ungroup() %>% select(-site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints3) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD4") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90, 180),
+    labels = c("Apheresis", "30", "90", "180")
+  )
+CD8_fig <- fig_dat %>% 
+  select(site, starts_with("cd8_")) %>% 
+  group_by(site) %>% 
+  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
+  ungroup() %>% select(-site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints3) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD8") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90, 180),
+    labels = c("Apheresis", "30", "90", "180")
+  )
+CD19_fig <- fig_dat %>% 
+  select(site, starts_with("cd19_")) %>% 
+  group_by(site) %>% 
+  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
+  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
+  ungroup() %>% select(-site) %>% 
+  group_by(type) %>% 
+  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_longer(cols = -type, names_to = 'Type') %>% 
+  pivot_wider(names_from = type, values_from = value) %>% 
+  mutate(timepoints = timepoints3) %>% 
+  ggplot(aes(x = timepoints, y = Median)) + 
+  geom_line(col = "blue") + 
+  xlab("Days relative to infusion") + 
+  ylab("Median CD19") + 
+  theme_classic() + 
+  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
+  scale_x_continuous(
+    breaks = c(-28, 30, 90, 180),
+    labels = c("Apheresis", "30", "90", "180")
+  )
+
+(WBC_agg | ANC_agg | CD4_fig) /
+  (Hb_agg | ALC_agg | CD8_fig) /
+  (Plt_agg | IgG_agg | CD19_fig) +
+  plot_annotation(tag_levels = "A")
+```
+
+<!-- <span style="color:blue">**IgG I need to fix the other 109**</span>  -->
+
+<!-- Values less than the limit of detection (<109) were considered to be 77 which is the lower limit of detection divided by the square root of 2.
+One patient had an IgG day 0 value of <320.
+As this is above the limit of detection, I used the midway point between 320 and the lower limit of detection -- 214 -- as the value instead of <320.
+-->
+
+<br>
+
+## Figure 4. Cytopenias over time
+
+```{r, fig.width=12, fig.height=7}
+# fig_dat %>% 
+#   select(PT,
+#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
+#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
+#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
+#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
+#   ) %>% 
+#   pivot_longer(cols = `gr3_Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
+#   group_by(name, value) %>% 
+#   filter(!is.na(value)) %>% 
+#   summarise(count=n()) %>% 
+#   mutate(perc=(count/sum(count)*100)
+#   ) %>% 
+#   separate("name", into = c("gr3", "name", "day"), sep = "_") %>% 
+#   filter(value == "Yes") %>% 
+#   # unite(time, c("day":"me"), sep = " ") %>% 
+#   ggplot(aes(x= day, y= perc, fill= name))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))+
+#   scale_fill_viridis_d() +
+#   labs(fill = NULL, y = "%", title = "Grade 3+")+
+#   theme_classic()
+# 
+# fig_dat %>% 
+#   select(PT,
+#          `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
+#          `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
+#          `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
+#          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
+#          
+#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
+#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
+#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
+#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
+#   ) %>% 
+#   pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
+#   mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
+#          grade = case_when(
+#            grade == "gr3_"       ~ "Grade 3+",
+#            TRUE                  ~ "Any grade"
+#          )) %>% 
+#   mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
+#          name2 = coalesce(name1, name)) %>% 
+#   group_by(name2, value, grade) %>% 
+#   filter(!is.na(value)) %>% 
+#   summarise(count=n()) %>%
+#   group_by(name2, grade) %>% 
+#   mutate(perc=(count/sum(count)*100)
+#   ) %>%
+#   separate("name2", into = c("name", "day"), sep = "_") %>% 
+#   filter(value == "Yes") %>% 
+#   # unite(time, c("day":"me"), sep = " ") %>% 
+#   ggplot(aes(x= day, y= perc, fill= name, alpha= grade))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))+
+#   scale_fill_viridis_d() + 
+#   scale_alpha_ordinal(range = c(0.5, 1))+
+#   labs(fill = NULL, y = "%")+
+#   theme_classic()
+
+a <- fig_dat %>% 
+  select(pt_identifier,
+         Leukopenia_apheresis,
+         `Leukopenia_-5d`, Leukopenia_30d, #Leukopenia_60d,
+         Leukopenia_90d,
+         Neutropenia_apheresis,
+         `Neutropenia_-5d`, Neutropenia_30d, #Neutropenia_60d,
+         Neutropenia_90d,
+         Anemia_apheresis,
+         `Anemia_-5d`, Anemia_30d, #Anemia_60d, 
+         Anemia_90d,
+         Thrombocytopenia_apheresis,
+         `Thrombocytopenia_-5d`, Thrombocytopenia_30d, #Thrombocytopenia_60d, 
+         Thrombocytopenia_90d,
+         cytopenia_apheresis, `cytopenia_-5d`, cytopenia_30d,# cytopenia_60d, 
+         cytopenia_90d,
+
+         gr3_Leukopenia_apheresis,
+         `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, #gr3_Leukopenia_60d, 
+         gr3_Leukopenia_90d,
+         gr3_Neutropenia_apheresis,
+         `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, #gr3_Neutropenia_60d, 
+         gr3_Neutropenia_90d,
+         gr3_Anemia_apheresis,
+         `gr3_Anemia_-5d`, gr3_Anemia_30d, #gr3_Anemia_60d, 
+         gr3_Anemia_90d,
+         gr3_Thrombocytopenia_apheresis,
+         `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, #gr3_Thrombocytopenia_60d, 
+         gr3_Thrombocytopenia_90d,
+         gr3_cytopenia_apheresis, `gr3_cytopenia_-5d`, gr3_cytopenia_30d, #gr3_cytopenia_60d, 
+         gr3_cytopenia_90d
+  ) %>% 
+  pivot_longer(cols = Neutropenia_apheresis: gr3_cytopenia_90d) %>% 
+  mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
+         grade = case_when(
+           grade == "gr3_"       ~ "Grade 3+",
+           TRUE                  ~ "Any grade"
+         )) %>% 
+  mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
+         name2 = coalesce(name1, name)) %>% 
+  group_by(name2, value, grade) %>% 
+  filter(!is.na(value)) %>%
+  summarise(count=n()) %>%
+  group_by(name2, grade) %>% 
+  mutate(perc=(count/sum(count)*100)
+  ) %>%
+  separate("name2", into = c("name", "day"), sep = "_") %>% 
+  ungroup() %>% 
+  filter(value == "Yes") %>% 
+  # add_row("name"="Leukopenia",  "day"="apheresis", "value"= "Yes", "grade"="Any grade", "count"=0, "perc"=0) %>% 
+  mutate(day = factor(day, levels = c("apheresis", "-5d", "30d", "60d", "90d"))) %>% 
+  mutate(name = str_replace(name, "^cytopenia", "Any Cytopenia")) %>% 
+  mutate(name = factor(name, levels = c("Anemia", "Neutropenia", "Thrombocytopenia", "Any Cytopenia")))
+
+b <- a %>% filter(grade == "Any grade")
+a %>% filter(grade == "Grade 3+") %>% 
+  ggplot(aes(x= day, 
+             y= perc, 
+             fill= name, alpha= 1
+             ))+
+  geom_bar(stat = "identity",
+           position=position_dodge(width=0.9))+
+  geom_bar(stat = "identity",
+           position=position_dodge(width=0.9), data= b,
+           aes(x= day, y= perc, fill= name), alpha= 0.4)+
+  scale_fill_brewer(palette = "Spectral")+
+  labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
+  theme_classic()+
+  scale_alpha_continuous(limits = c(0.4,1), breaks = c(0.4,1),
+                         labels= c("Any Grade", "Grade 3+"))
+####################################################################################################
+# a %>% filter(grade == "Grade 3+") %>% 
+#   ggplot(aes(x= day, 
+#              y= perc, 
+#              fill= name, 
+#              ))+
+#   geom_bar(stat = "identity",
+#            position=position_dodge(width=0.9))+
+#   geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 4.5,
+#             position = position_dodge(width=0.9)
+#             )+
+#   
+#   scale_fill_brewer(palette = "Spectral")+
+#   ylim(0, 100)+
+#   labs(fill = NULL, x= NULL, y = "%")+
+#   theme_classic(base_size = 14)
+
+a %>% filter(grade == "Grade 3+") %>% 
+  ggplot(aes(x= day, 
+             y= perc, 
+             fill= name, 
+             ))+
+  geom_bar(stat = "identity",
+           position=position_dodge(width=0.9))+
+  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 5,
+            position = position_dodge(width=0.9), vjust=-1.5
+            )+
+
+  scale_fill_brewer(palette = "Spectral")+
+  ylim(0, 100)+
+  labs(fill = NULL, x= NULL, y = "%")+
+  theme_classic(base_size = 14)+
+  theme(legend.position="bottom")
+
+```
+
+## Figure 5. Cumulative incidence of infection and infection density
+```{r}
+library(tidycmprsk)
+library(ggsurvfit)
+
+risk_comp <- cilta %>% 
+  mutate(event_type = case_when(
+    infection_type_bacterial_viral_fungal_parasitic == "Bacterial"      ~ "Bacterial",
+    infection_type_bacterial_viral_fungal_parasitic == "Fungal"         ~ "Fungal",
+    infection_type_bacterial_viral_fungal_parasitic == "Viral"          ~ "Viral",
+    is.na(infection_type_bacterial_viral_fungal_parasitic)              ~ "None"
+  )) %>% 
+  mutate(event_type =
+           factor(event_type, levels= c("None","Bacterial","Fungal", "Viral"))) %>%
+  mutate(date_of_event = interval(start = date_of_car_t_infusion, 
+                                  end = date_of_infection) / 
+           duration(n = 1, units = "days"),
+         date_of_event = case_when(
+      is.na(date_of_event)             ~ 300,
+      TRUE                             ~ date_of_event))
+
+cum_inc <- cuminc(Surv(date_of_event, event_type) ~ 1, data = risk_comp) %>% 
+  ggcuminc(outcome = c("Bacterial", "Fungal", "Viral"), 
+           geom_step(linewidth=10)) +
+  ylim(c(0, 1)) + 
+  labs(
+    x = "Days"
+  )+
+  add_risktable()
+cum_inc
+
+cuminc(Surv(date_of_event, event_type) ~ 1, data = risk_comp) %>% 
+  ggcuminc(outcome = c("Bacterial", "Fungal", "Viral"), 
+           geom_step(linewidth=10)) +
+  ylim(c(0, 0.25)) +
+  labs(
+    x = "Days"
+  )+
+  add_risktable()
+```
+
+## Figure S1. Viral titers after ide-cel
+Focus on MCC patients / I didn't use day 180 as they are less values but I can add it if you want.
+```{r}
+moffitt_subset <- fig_dat %>% filter(site == "Moffitt")
+```
+
+### A)	HSV 1/2 IgG
+See below
+```{r}
+# Alluvial
+library(ggalluvial)
+
+alluvial_A <- moffitt_subset %>% 
+  select(pt_identifier, igg_hsv_change,
+         ig_g_hsv1_2_apheresis, ig_g_hsv1_2_d90) %>%
+  drop_na() %>%
+  group_by(ig_g_hsv1_2_apheresis, ig_g_hsv1_2_d90) %>% 
+  summarise(count=n()) %>%
+
+  ggplot(aes(axis1 = ig_g_hsv1_2_apheresis, axis2 = ig_g_hsv1_2_d90,
+             y = count)) +
+  geom_alluvium(aes(fill = ig_g_hsv1_2_apheresis)
+  )+
+  geom_stratum()+
+  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+  theme_classic()+
+  ggtitle("Evolution of virus titers")
+```
+
+### B)	VZV IgG (positive=immune vs negative or equivocal=not immune)
+See below
+```{r}
+# Alluvial
+alluvial_B <- moffitt_subset %>% 
+  select(pt_identifier, igg_vzv_change,
+         vzv_ig_g_apheresis, vzv_ig_g_d90
+  ) %>% 
+  drop_na() %>% 
+  group_by(vzv_ig_g_apheresis, vzv_ig_g_d90) %>% 
+  summarise(count=n()) %>%
+
+  ggplot(aes(axis1 = vzv_ig_g_apheresis, axis2= vzv_ig_g_d90,
+             y = count)) +
+  geom_alluvium(aes(fill = vzv_ig_g_apheresis)
+  )+
+  geom_stratum()+
+  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+  theme_classic()+
+  ggtitle("Evolution of virus titers")
+```
+
+### C)	CMV IgG (positive=immune vs negative=not immune)
+```{r}
+alluvial_C <- moffitt_subset %>% 
+  select(pt_identifier, igg_cmv_change,
+         cmv_ig_g_apheresis, cmv_ig_g_d90
+  ) %>% 
+  drop_na() %>% 
+  group_by(cmv_ig_g_apheresis, cmv_ig_g_d90) %>% 
+  summarise(count=n()) %>%
+
+  ggplot(aes(axis1 = cmv_ig_g_apheresis, axis2= cmv_ig_g_d90,
+             y = count)) +
+  geom_alluvium(aes(fill = cmv_ig_g_apheresis)
+  )+
+  geom_stratum()+
+  geom_segment(aes(x=1.17, y=12, xend=1.83, yend=12), 
+               color= "white", size=0.3)+
+  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+  theme_classic()+
+  ggtitle("Evolution of virus titers")
+```
+
+```{r, fig.height=12}
+(alluvial_A) /
+  (alluvial_B) /
+  (alluvial_C) +
+  plot_annotation(tag_levels = "A")
+```
+
+## Figure S2. Pneumococcal titers after ide-cel
+
+Antibody concentration >1.0 is considered long-term protection (immune)
+If antibody concentration ≤1.0 consider negative (not immune)
+```{r, fig.width=12, fig.height=12}
+# Histogram
+# fig_dat %>% 
+#   select(PT, 
+#          starts_with("Pneumo"), -ends_with("change")) %>% 
+#   pivot_longer(cols = -PT) %>% 
+#   filter(!is.na(value)) %>% 
+#   mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
+#   mutate(name = str_remove(name, " apheresis| D90")) %>% 
+#   
+#   group_by(name, day, value) %>% 
+#   summarise(count=n()) %>% 
+#   mutate(perc=(count/sum(count)*100)
+#   ) %>% 
+# 
+#   ggplot(aes(x= day, y= perc, fill= value))+
+#   # geom_bar(stat = "identity",
+#   #          position=position_dodge2(width=0.9, preserve = "single"))+
+#   geom_bar(stat = "identity")+
+#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
+#        fill= "Immunity")+
+#   scale_y_continuous(expand = c(0, 0))+
+#   theme_classic()+
+#   facet_wrap(.~ name)
+```
+
+```{r, fig.width=12, fig.height=14}
+# Tile
+# fig_dat %>% 
+#   select(PT, 
+#          starts_with("Pneumo"), -ends_with("change")) %>% 
+#   pivot_longer(cols = -PT) %>% 
+#   mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
+#   mutate(name = str_remove(name, " apheresis| D90")) %>% 
+#   
+#   
+#   filter(!is.na(value)) %>% 
+#   arrange(value) %>% 
+#   ggplot(aes(x= day, y= fct_reorder2(PT, value, day), fill= value))+
+#   geom_tile(color = "white")+
+#   labs(fill = NULL, x = NULL, y= NULL)+
+#   theme_classic()+
+#   facet_wrap(.~ name)
+```
+
+```{r, fig.width=15, fig.height=12}
+library(ComplexHeatmap)
+mat <- moffitt_subset %>% 
+  select(pt_identifier, 
+         intersect(starts_with("pneumo"), ends_with("change"))) %>% 
+  drop_na() #%>% 
+  # mutate(new_sort = 
+  #          c(6,10,11,26,8,
+  #            12,24,13,31,
+  #            14,15, 5,9, 16,
+  #            17,30,18,27, 2,
+  #            7,4,19,29,20,
+  #            3, 21, 25, 22, 
+  #            23,1,28),
+  #        .before = 2) %>%
+  # 
+  # arrange(new_sort) %>% 
+  #   select(-new_sort)
+
+df5 <- t((as.matrix(mat)))
+
+df <- df5 %>% `colnames<-`(c(.[1,])) %>% 
+  .[-1,]
+
+df <- df %>% 
+sub(pattern = " 1.00", replacement = "Acquired immunity") %>% 
+sub(pattern = " 0.25", replacement = "Positive overtime") %>% 
+sub(pattern = "-0.25", replacement = "Negative overtime") %>% 
+sub(pattern = "-1.00", replacement = "Lost immunity")
+
+colors = structure(c("blue", "darkgrey", "lightgrey", "red"), 
+                   names = c("Lost immunity", "Negative overtime", "Positive overtime", "Acquired immunity"))
+
+ht_list <- Heatmap(df, name = "change", 
+        rect_gp = gpar(col = "white", lwd = 0.1),
+        column_title = "Change in titers",
+        show_column_names =FALSE,
+        row_names_side = "left",
+        row_names_gp = gpar(fontsize = 11),
+        col = colors)
+draw(ht_list, heatmap_legend_side = "bottom")
+```
+
+## MVA and forest plot
+Limit to evaluable patients at day 90
+```{r}
+mva_dat <- fig_dat %>% 
+  filter(os_from_infusion_months > 3) %>% 
+  mutate(gr3_cytopenia_30d = case_when(
+    gr3_cytopenia_30d == "No"    ~ 0,
+    gr3_cytopenia_30d == "Yes"   ~ 1
+  )) %>% 
+  mutate(gr3_cytopenia_90d = case_when(
+    gr3_cytopenia_90d == "No"    ~ 0,
+    gr3_cytopenia_90d == "Yes"   ~ 1
+  )) %>% 
+  mutate(CRS_grade2 = case_when(
+    max_crs_grade_0_5 < 2                              ~ "No CRS or Grade < 2",
+    max_crs_grade_0_5 >= 2                             ~ "Grade ≥2"),
+    CRS_grade2 = factor(CRS_grade2, levels = c("No CRS or Grade < 2", "Grade ≥2"))
+  )
+
+# glm(gr3_cytopenia_30d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + CRS_grade2 + steroid_use_yes_no + number_of_prior_lines_of_therapy,
+#     data = mva_dat,
+#     family = "binomial") %>%
+#   tbl_regression(exponentiate = TRUE, 
+#                  intercept = TRUE) %>%
+#   add_nevent(location = "level") %>% add_n(location = "level") %>%
+#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 30**") %>%
+#   bold_p(t = .05) 
+# 
+# glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + CRS_grade2 + steroid_use_yes_no + number_of_prior_lines_of_therapy,
+#     data = mva_dat,
+#     family = "binomial") %>%
+#   tbl_regression(exponentiate = TRUE, 
+#                  intercept = TRUE) %>%
+#   add_nevent(location = "level") %>% add_n(location = "level") %>%
+#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
+#   bold_p(t = .05) 
+# 
+# glm(gr3_cytopenia_30d ~ high_marrow_burden_50_percent + CRS_grade2 + steroid_use_yes_no + number_of_prior_lines_of_therapy,
+#     data = mva_dat,
+#     family = "binomial") %>%
+#   tbl_regression(exponentiate = TRUE, 
+#                  intercept = TRUE) %>%
+#   add_nevent(location = "level") %>% add_n(location = "level") %>%
+#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 30**") %>%
+#   bold_p(t = .05)
+
+glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + CRS_grade2 + steroid_use_yes_no + number_of_prior_lines_of_therapy,
+    data = mva_dat,
+    family = "binomial") %>%
+  tbl_regression(exponentiate = TRUE, 
+                 intercept = TRUE) %>%
+  add_nevent(location = "level") %>% add_n(location = "level") %>%
+  modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
+  bold_p(t = .05) 
+```
+
+```{r}
+forest_p <- 
+  glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + CRS_grade2 + steroid_use_yes_no + number_of_prior_lines_of_therapy,
+    data = mva_dat,
+    family = "binomial") %>%
+  tbl_regression(exponentiate = TRUE) %>%
+  as_tibble() %>% 
+  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
+  fill(OR, `95% CI`, .direction = "up") %>% 
+  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
+  filter(Characteristic %in% c("High marrow burden (≥50%)",
+                 "gr3_cytopenia_-5d",
+                 "CRS_grade2",
+                 "Steroid Use",
+                 "Number of prior lines of therapy") ) %>% 
+  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
+  mutate(name= c("High marrow burden (≥50%)",
+                 "Grade ≥ 3 Cytopenia at Day -5",
+                 "Grade ≥ 2 CRS",
+                 "Steroid use",
+                 "Number of prior lines of therapy"
+                 ))
+
+ggplot(data=forest_p, aes(y=name, x=OR, xmin=lower, xmax=upper)) +
+  geom_point() + 
+  geom_errorbarh(height=.1) +
+  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
+  theme_classic()+
+  scale_x_log10(breaks = c(0, 0.25, 0.5, 1, 2.5, 5, 10, 40))+
+  labs(y="")
+```
+
+```{r, fig.width=15, fig.height=12}
+# ghgghjg
+```

### 2023-12-18 cilta_cel/Manuscript analyses.Rmd
Updates

@@
              "ig_g_apheresis",
-             "ig_g_day_5", "ig_g_day_30", "ig_g_day_90",
-             "ig_a_day_5", "ig_a_day_30", "ig_a_day_90",
-             "ig_m_day_5", "ig_m_day_30", "ig_m_day_90",
-
-             "cd8_apheresis", "cd8_day_30", 
-             "cd8_day_90", "cd8_day_180", 
-             "cd19_apheresis", "cd19_day_30",
-             "cd19_day_90", "cd19_day_180",
+             "ig_g_day_5", "ig_g_day_30", "ig_g_day_90", "ig_g_day_180",
+             "ig_a_day_5", "ig_a_day_30", "ig_a_day_90", "ig_a_day_180",
+             "ig_m_day_5", "ig_m_day_30", "ig_m_day_90", "ig_m_day_180",
+
+             "cd8_apheresis", "cd8_day_30", "cd8_day_90", "cd8_day_180", 
+             "cd19_apheresis", "cd19_day_30", "cd19_day_90", "cd19_day_180",
 
@@
 }
-
-# has < : "CRP Pre-Leukapheresis", "IgG day -5", "IgA day -5", "IgM day -5"
-# has < :"CRP day +21", "IgG day +30", "IgA day +30", "IgM day +30", "marrow_percent_cd138_day_30", "marrow % cellularity day +30", "CRP day +30", "CD19 day +90", "IgG day +90", "IgA day +90", "IgM day +90", "marrow %CD138 day +90",
-# # has > : "CD8 day +30", "CRP day +90"
-# has < : "CD19 day +180", "IgG day +180", "IgA day +180", "IgM day +180", "marrow % cellularity day +180", "CRP day +180"
-# # has > : "marrow %CD138 day +180"
-
+```
+
+```{r fix neutropenia values}
+cart <- cart %>% 
+  mutate(across(c(starts_with("anc_"), 
+                  -anc_0_75_x_10_9_l_0_75_k_u_l), 
+                ~ . / 1000))
+```
+
+```{r data cleaning2}
 cart <- cart %>% 
@@
                                                                   ~ "Parkinsonian/PRES",
+    what_non_parkinsonian_neurotoxicity == 
+      "Posterior reversible encephalopathy syndrome (pres); progressive multifocal leukoencephalopathy (pml)" 
+                                                                  ~ "PRES/PML",
     parkinsonian_neurotoxicity_yes_no == "Yes"                    ~ "Parkinsonian",
@@
       is.na(what_non_parkinsonian_neurotoxicity)                  ~ "Unknown type",
-    TRUE                                                          ~ NA_character_
+    TRUE                                                          ~ what_non_parkinsonian_neurotoxicity
   )) 
@@
                          # `ECOG > or = 2? (Yes, No)` ,
-                         r_iss_at_car_t_infusion = "ISS at cart infusion",
+                         r_iss_at_car_t_infusion = "R-ISS at cart infusion",
                          cytogenetics = "High risk cytogenetics", 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(notinfused) %>% 
+  select(`infused?` = notinfused) %>% 
   tbl_summary(missing = "no") %>% 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(max_crs_grade_0_5,
+  select(max_crs_grade_0_5, CRS_gradecat,
          day_of_onset_crs_relative_to_infusion,
@@
          duration_of_crs_days, 
-         max_icans,
+         max_icans, ICANS_gradecat,
          day_of_onset_icans_relative_to_infusion,
@@
 
-## Table 3. Bone marrow biopsy findings
+## Bone marrow biopsy findings
 ```{r}
@@
 
-## Table 4. Supportive therapies and engraftment
+## Supportive therapies and engraftment
 Jenn did it for the ide-cel paper
@@
 
-## Table S1. Apheresis and product characteristics
+## Apheresis and product characteristics
 ```{r}
@@
 
-## Table S2. Cytopenias following ide-cel
+## Table 3. Cytopenias following ide-cel
 
@@
 
-## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30
+## Patient characteristics by grade 3+ cytopenia at Day 30
 ```{r}
@@
 
-## Table S3. Patient characteristics by grade 3+ cytopenia at Day 90
+## Patient characteristics by grade 3+ cytopenia at Day 90
 ```{r}
@@
 
-## Table S4. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
+## CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
 ```{r}
@@
          ORR_30days, CRorbetter_30days,
-         day30_response_v2, gr3_cytopenia_30d) %>% 
+         # day30_response_v2, 
+         gr3_cytopenia_30d) %>% 
   tbl_summary(by = gr3_cytopenia_30d,
@@
          ORR_mon3, CRorbetter_mon3,
-         mon3_response_v2, gr3_cytopenia_30d) %>% 
+         # mon3_response_v2, 
+         gr3_cytopenia_30d) %>% 
   tbl_summary(by = gr3_cytopenia_30d,
@@
 
-## Table S4. Details of infections after ide-cel
+## Details of infections after ide-cel
 Jenn
 
-## Table S5. Patients with infections in the first 30 days by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
+## Patients with infections in the first 30 days by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
 ```{r}
@@
 
-## Table S6. Patients with infections in the first 100 days by cell counts and immunoglobulin levels
+## Patients with infections in the first 100 days by cell counts and immunoglobulin levels
 CCT5019-0512 has a time to infection but no in Any Infection but yes in Any Severe Infection
@@
 
-## Table SX. Immunoglobulin levels excluding patients with that type of myeloma 
+## Immunoglobulin levels excluding patients with that type of myeloma 
 (myeloma_involved_heavy_chain != "Igg")
@@
 
-## Figure 3. Cellular and humoral immune reconstitution after ide-cel
+## Figure 3. Cellular and humoral immune reconstitution after cilta-cel
 ```{r timeserie, fig.width=12, fig.height=12}
@@
     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
   ) #+ ylim(0, 6)
@@
     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
   ) # +ylim(7.5, 12)
@@
     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
   ) # + ylim(0, 1.1)
@@
     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
+    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
   ) # + ylim(20, 170)
@@
   scale_x_continuous(
-    breaks = c(-28, -5, 0, 30, 90, 180),
-    labels = c("Apheresis", "-5", "0", "30", "90", "180"))# + 
+    breaks = c(-28, -5, 30, 90, 180),
+    labels = c("Apheresis", "-5", "30", "90", "180"))# + 
   # ylim(0, 2000)
@@
 
-Aggregated median
-```{r timeserie aggreagate med, fig.width=12, fig.height=12}
-fig_dat <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE)
-
-timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
-WBC_agg <- fig_dat %>% 
-  select(site, starts_with("wbc_")) %>% 
-  group_by(site) %>% 
-  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
-  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
-  ungroup() %>% select(-site) %>% 
-  group_by(type) %>% 
-  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  pivot_longer(cols = -type, names_to = 'Type') %>% 
-  pivot_wider(names_from = type, values_from = value) %>% 
-  mutate(timepoints = timepoints) %>% 
-  ggplot(aes(x = timepoints, y = Median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median WBC") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  )
-
-ANC_agg <- fig_dat %>% 
-  select(site, starts_with("anc_"), -anc_0_75_x_10_9_l_0_75_k_u_l) %>% 
-  group_by(site) %>% 
-  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
-  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
-  ungroup() %>% select(-site) %>% 
-  group_by(type) %>% 
-  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  pivot_longer(cols = -type, names_to = 'Type') %>% 
-  pivot_wider(names_from = type, values_from = value) %>% 
-  mutate(timepoints = timepoints) %>% 
-  ggplot(aes(x = timepoints, y = Median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median ANC") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  )
-
-Hb_agg <- fig_dat %>% 
-  select(site, starts_with("hb_")) %>% 
-  group_by(site) %>% 
-  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
-  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
-  ungroup() %>% select(-site) %>% 
-  group_by(type) %>% 
-  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  pivot_longer(cols = -type, names_to = 'Type') %>% 
-  pivot_wider(names_from = type, values_from = value) %>% 
-  mutate(timepoints = timepoints) %>% 
-  ggplot(aes(x = timepoints, y = Median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median Hb") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  )
-
-ALC_agg <- fig_dat %>% 
-  select(site, starts_with("alc_"), -alc_0_3_x_10_9_l_0_3k_u_l) %>% 
-  group_by(site) %>% 
-  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
-  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
-  ungroup() %>% select(-site) %>% 
-  group_by(type) %>% 
-  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  pivot_longer(cols = -type, names_to = 'Type') %>% 
-  pivot_wider(names_from = type, values_from = value) %>% 
-  mutate(timepoints = timepoints) %>% 
-  ggplot(aes(x = timepoints, y = Median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median ALC") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  )
-
-Plt_agg <- fig_dat %>% 
-  select(site, starts_with("plt_"), -c(starts_with("plt_transfusion"))) %>% 
-  group_by(site) %>% 
-  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
-  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
-  ungroup() %>% select(-site) %>% 
-  group_by(type) %>% 
-  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  pivot_longer(cols = -type, names_to = 'Type') %>% 
-  pivot_wider(names_from = type, values_from = value) %>% 
-  mutate(timepoints = timepoints) %>% 
-  ggplot(aes(x = timepoints, y = Median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median Plt") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  )
-
-timepoints2 <- c(-28, -5, 30, 90, 180)
-IgG_agg <- fig_dat %>% 
-  select(site, ig_g_apheresis, starts_with("ig_g_day")) %>% 
-  group_by(site) %>% 
-  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
-  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
-  ungroup() %>% select(-site) %>% 
-  group_by(type) %>% 
-  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  pivot_longer(cols = -type, names_to = 'Type') %>% 
-  pivot_wider(names_from = type, values_from = value) %>% 
-  mutate(timepoints = timepoints2) %>% 
-  ggplot(aes(x = timepoints, y = Median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median Plt") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 30, 90, 180),
-    labels = c("Apheresis", "-5", "0", "30", "90", "180")
-  )
-
-timepoints3 <- c(-28, 30, 90, 180)
-CD4_fig <- fig_dat %>% 
-  select(site, starts_with("cd4_")) %>% 
-  group_by(site) %>% 
-  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
-  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
-  ungroup() %>% select(-site) %>% 
-  group_by(type) %>% 
-  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  pivot_longer(cols = -type, names_to = 'Type') %>% 
-  pivot_wider(names_from = type, values_from = value) %>% 
-  mutate(timepoints = timepoints3) %>% 
-  ggplot(aes(x = timepoints, y = Median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median CD4") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, 30, 90, 180),
-    labels = c("Apheresis", "30", "90", "180")
-  )
-CD8_fig <- fig_dat %>% 
-  select(site, starts_with("cd8_")) %>% 
-  group_by(site) %>% 
-  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
-  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
-  ungroup() %>% select(-site) %>% 
-  group_by(type) %>% 
-  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  pivot_longer(cols = -type, names_to = 'Type') %>% 
-  pivot_wider(names_from = type, values_from = value) %>% 
-  mutate(timepoints = timepoints3) %>% 
-  ggplot(aes(x = timepoints, y = Median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median CD8") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, 30, 90, 180),
-    labels = c("Apheresis", "30", "90", "180")
-  )
-CD19_fig <- fig_dat %>% 
-  select(site, starts_with("cd19_")) %>% 
-  group_by(site) %>% 
-  reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>% 
-  mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>% 
-  ungroup() %>% select(-site) %>% 
-  group_by(type) %>% 
-  summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  pivot_longer(cols = -type, names_to = 'Type') %>% 
-  pivot_wider(names_from = type, values_from = value) %>% 
-  mutate(timepoints = timepoints3) %>% 
-  ggplot(aes(x = timepoints, y = Median)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median CD19") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, 30, 90, 180),
-    labels = c("Apheresis", "30", "90", "180")
-  )
-
-(WBC_agg | ANC_agg | CD4_fig) /
-  (Hb_agg | ALC_agg | CD8_fig) /
-  (Plt_agg | IgG_agg | CD19_fig) +
-  plot_annotation(tag_levels = "A")
-```
+<!-- Aggregated median -->
+<!-- ```{r timeserie aggreagate med, fig.width=12, fig.height=12} -->
+<!-- fig_dat <- cilta %>%  -->
+<!--   distinct(pt_identifier, .keep_all = TRUE) -->
+
+<!-- timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180) -->
+<!-- WBC_agg <- fig_dat %>%  -->
+<!--   select(site, starts_with("wbc_")) %>%  -->
+<!--   group_by(site) %>%  -->
+<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
+<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
+<!--   ungroup() %>% select(-site) %>%  -->
+<!--   group_by(type) %>%  -->
+<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
+<!--   ungroup() %>%  -->
+<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
+<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
+<!--   mutate(timepoints = timepoints) %>%  -->
+<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
+<!--   geom_line(col = "blue") +  -->
+<!--   xlab("Days relative to infusion") +  -->
+<!--   ylab("Median WBC") +  -->
+<!--   theme_classic() +  -->
+<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
+<!--   scale_x_continuous( -->
+<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
+<!--     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180") -->
+<!--   ) -->
+
+<!-- ANC_agg <- fig_dat %>%  -->
+<!--   select(site, starts_with("anc_"), -anc_0_75_x_10_9_l_0_75_k_u_l) %>%  -->
+<!--   group_by(site) %>%  -->
+<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
+<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
+<!--   ungroup() %>% select(-site) %>%  -->
+<!--   group_by(type) %>%  -->
+<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
+<!--   ungroup() %>%  -->
+<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
+<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
+<!--   mutate(timepoints = timepoints) %>%  -->
+<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
+<!--   geom_line(col = "blue") +  -->
+<!--   xlab("Days relative to infusion") +  -->
+<!--   ylab("Median ANC") +  -->
+<!--   theme_classic() +  -->
+<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
+<!--   scale_x_continuous( -->
+<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
+<!--     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180") -->
+<!--   )  -->
+
+<!-- Hb_agg <- fig_dat %>%  -->
+<!--   select(site, starts_with("hb_")) %>%  -->
+<!--   group_by(site) %>%  -->
+<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
+<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
+<!--   ungroup() %>% select(-site) %>%  -->
+<!--   group_by(type) %>%  -->
+<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
+<!--   ungroup() %>%  -->
+<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
+<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
+<!--   mutate(timepoints = timepoints) %>%  -->
+<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
+<!--   geom_line(col = "blue") +  -->
+<!--   xlab("Days relative to infusion") +  -->
+<!--   ylab("Median Hb") +  -->
+<!--   theme_classic() +  -->
+<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
+<!--   scale_x_continuous( -->
+<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
+<!--     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180") -->
+<!--   )  -->
+
+<!-- ALC_agg <- fig_dat %>%  -->
+<!--   select(site, starts_with("alc_"), -alc_0_3_x_10_9_l_0_3k_u_l) %>%  -->
+<!--   group_by(site) %>%  -->
+<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
+<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
+<!--   ungroup() %>% select(-site) %>%  -->
+<!--   group_by(type) %>%  -->
+<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
+<!--   ungroup() %>%  -->
+<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
+<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
+<!--   mutate(timepoints = timepoints) %>%  -->
+<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
+<!--   geom_line(col = "blue") +  -->
+<!--   xlab("Days relative to infusion") +  -->
+<!--   ylab("Median ALC") +  -->
+<!--   theme_classic() +  -->
+<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
+<!--   scale_x_continuous( -->
+<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
+<!--     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180") -->
+<!--   )  -->
+
+<!-- Plt_agg <- fig_dat %>%  -->
+<!--   select(site, starts_with("plt_"), -c(starts_with("plt_transfusion"))) %>%  -->
+<!--   group_by(site) %>%  -->
+<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
+<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
+<!--   ungroup() %>% select(-site) %>%  -->
+<!--   group_by(type) %>%  -->
+<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
+<!--   ungroup() %>%  -->
+<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
+<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
+<!--   mutate(timepoints = timepoints) %>%  -->
+<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
+<!--   geom_line(col = "blue") +  -->
+<!--   xlab("Days relative to infusion") +  -->
+<!--   ylab("Median Plt") +  -->
+<!--   theme_classic() +  -->
+<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
+<!--   scale_x_continuous( -->
+<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
+<!--     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180") -->
+<!--   ) -->
+
+<!-- timepoints2 <- c(-28, -5, 30, 90, 180) -->
+<!-- IgG_agg <- fig_dat %>%  -->
+<!--   select(site, ig_g_apheresis, starts_with("ig_g_day")) %>%  -->
+<!--   group_by(site) %>%  -->
+<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
+<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
+<!--   ungroup() %>% select(-site) %>%  -->
+<!--   group_by(type) %>%  -->
+<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
+<!--   ungroup() %>%  -->
+<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
+<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
+<!--   mutate(timepoints = timepoints2) %>%  -->
+<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
+<!--   geom_line(col = "blue") +  -->
+<!--   xlab("Days relative to infusion") +  -->
+<!--   ylab("Median Plt") +  -->
+<!--   theme_classic() +  -->
+<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
+<!--   scale_x_continuous( -->
+<!--     breaks = c(-28, -5, 0, 30, 90, 180), -->
+<!--     labels = c("Apheresis", "-5", "0", "30", "90", "180") -->
+<!--   ) -->
+
+<!-- timepoints3 <- c(-28, 30, 90, 180) -->
+<!-- CD4_fig <- fig_dat %>%  -->
+<!--   select(site, starts_with("cd4_")) %>%  -->
+<!--   group_by(site) %>%  -->
+<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
+<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
+<!--   ungroup() %>% select(-site) %>%  -->
+<!--   group_by(type) %>%  -->
+<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
+<!--   ungroup() %>%  -->
+<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
+<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
+<!--   mutate(timepoints = timepoints3) %>%  -->
+<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
+<!--   geom_line(col = "blue") +  -->
+<!--   xlab("Days relative to infusion") +  -->
+<!--   ylab("Median CD4") +  -->
+<!--   theme_classic() +  -->
+<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
+<!--   scale_x_continuous( -->
+<!--     breaks = c(-28, 30, 90, 180), -->
+<!--     labels = c("Apheresis", "30", "90", "180") -->
+<!--   ) -->
+<!-- CD8_fig <- fig_dat %>%  -->
+<!--   select(site, starts_with("cd8_")) %>%  -->
+<!--   group_by(site) %>%  -->
+<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
+<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
+<!--   ungroup() %>% select(-site) %>%  -->
+<!--   group_by(type) %>%  -->
+<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
+<!--   ungroup() %>%  -->
+<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
+<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
+<!--   mutate(timepoints = timepoints3) %>%  -->
+<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
+<!--   geom_line(col = "blue") +  -->
+<!--   xlab("Days relative to infusion") +  -->
+<!--   ylab("Median CD8") +  -->
+<!--   theme_classic() +  -->
+<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
+<!--   scale_x_continuous( -->
+<!--     breaks = c(-28, 30, 90, 180), -->
+<!--     labels = c("Apheresis", "30", "90", "180") -->
+<!--   ) -->
+<!-- CD19_fig <- fig_dat %>%  -->
+<!--   select(site, starts_with("cd19_")) %>%  -->
+<!--   group_by(site) %>%  -->
+<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
+<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
+<!--   ungroup() %>% select(-site) %>%  -->
+<!--   group_by(type) %>%  -->
+<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
+<!--   ungroup() %>%  -->
+<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
+<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
+<!--   mutate(timepoints = timepoints3) %>%  -->
+<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
+<!--   geom_line(col = "blue") +  -->
+<!--   xlab("Days relative to infusion") +  -->
+<!--   ylab("Median CD19") +  -->
+<!--   theme_classic() +  -->
+<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
+<!--   scale_x_continuous( -->
+<!--     breaks = c(-28, 30, 90, 180), -->
+<!--     labels = c("Apheresis", "30", "90", "180") -->
+<!--   ) -->
+
+<!-- (WBC_agg | ANC_agg | CD4_fig) / -->
+<!--   (Hb_agg | ALC_agg | CD8_fig) / -->
+<!--   (Plt_agg | IgG_agg | CD19_fig) + -->
+<!--   plot_annotation(tag_levels = "A") -->
+<!-- ``` -->
 
@@
   separate("name2", into = c("name", "day"), sep = "_") %>% 
-  ungroup() %>% 
-  filter(value == "Yes") %>% 
+  ungroup()
+
+# We want to plot the Yes patients 
+# but filtering filter(value == "Yes") leave blanks if all patients are NO
+# Code to fix it is :
+c <- a %>% 
+  arrange(name, day, grade, desc(value)) %>%  # desc to have yes first
+  distinct(name, day, grade, .keep_all = TRUE) %>% 
+  mutate(count = case_when(
+    value == "No"           ~ 0,
+    TRUE                    ~ count
+  ), perc = case_when(
+    value == "No"           ~ 0,
+    TRUE                    ~ perc
+  )) %>%
+
+  # filter(value == "Yes") %>% 
   # add_row("name"="Leukopenia",  "day"="apheresis", "value"= "Yes", "grade"="Any grade", "count"=0, "perc"=0) %>% 
@@
   mutate(name = str_replace(name, "^cytopenia", "Any Cytopenia")) %>% 
-  mutate(name = factor(name, levels = c("Anemia", "Neutropenia", "Thrombocytopenia", "Any Cytopenia")))
-
-b <- a %>% filter(grade == "Any grade")
-a %>% filter(grade == "Grade 3+") %>% 
+  mutate(name = factor(name, levels = c("Anemia", "Neutropenia", "Thrombocytopenia", "Any Cytopenia"))) %>% 
+  filter(!is.na(name))
+
+b <- c %>% filter(grade == "Any grade")
+c %>% filter(grade == "Grade 3+") %>% 
   ggplot(aes(x= day, 
@@
 
-a %>% filter(grade == "Grade 3+") %>% 
+c %>% filter(grade == "Grade 3+") %>% 
   ggplot(aes(x= day, 
@@
   theme(legend.position="bottom")
-
 ```

### 2024-01-04 cilta_cel/Manuscript analyses.Rmd
Updates

@@
                   "high_marrow_burden_50_percent",
-                  contains("normo_hypo_hyper"),
+                  # contains("normo_hypo_hyper"),
                   contains("fibrosis"),
@@
     factor(cart_cell_dose, levels = c("≥ 0.7", 
-                                      "< 0.7")))
+                                      "< 0.7"))) %>% 
+  mutate(access_type = case_when(
+    str_detect(access_type, "^C|catheter")                          ~ "Central venous catheter",
+    str_detect(access_type, "^P")                                 ~ "Peripheral",
+    TRUE                                                          ~ access_type
+  ))
 ```
@@
 
-  # mutate(access_type = case_when(
-  #   access_type == "Femoral"                                    ~ "Non-tunneled",
-  #   access_type == "AVF"                                        ~ "Peripheral",
-  #   TRUE                                                          ~ access_type
-  # )) %>% 
 # cart7 <- cart6 %>% 
@@
   mutate(delayed_neuro_type = case_when(
+    what_non_parkinsonian_neurotoxicity == "Aidp"                 ~ "Polyneuropathy",
     what_non_parkinsonian_neurotoxicity == 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(age, agecat, male_sex, sex,
+  select(os_from_infusion_months, age, agecat, male_sex, sex,
          extramedullary_disease_yes_no, 
@@
          "Marrow Cellularity (%) at Day30" = marrow_percent_cellularity_day_30,
-         age, agecat, male_sex, sex,
+         os_from_infusion_months, age, agecat, male_sex, sex,
          extramedullary_disease_yes_no, 
@@
          "Marrow Cellularity (%) at Day90" = marrow_percent_cellularity_day_90,
+         os_from_infusion_months,
          age, agecat, male_sex, sex,
@@
 
-## Details of infections after ide-cel
-Jenn
-
-## Patients with infections in the first 30 days by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
+## Table S8.Details of infections after ide-cel
+```{r infection details 30 first days}
+tbl1 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
+  tbl_summary() %>%
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = c("Fungal", "Viral")) %>%
+  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>%
+  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
+  modify_column_indent(columns = label, undo = TRUE) %>% 
+  bold_levels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Infections in the first 30 days**")
+
+tbl1_1 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  filter(infection_type_bacterial_viral_fungal_parasitic == "Bacterial") %>%
+  select(infection_type_details) %>% 
+  tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
+  remove_row_type(infection_type_details, type = "header")
+
+tbl2 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
+  tbl_summary() %>%
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = c("Bacterial", "Viral")) %>% 
+  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
+  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
+  bold_levels() %>%
+  modify_column_indent(columns = label, undo = TRUE)
+
+tbl2_1 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  filter(infection_type_bacterial_viral_fungal_parasitic == "Fungal") %>%
+  select(infection_type_details) %>% 
+  tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
+  remove_row_type(infection_type_details, type = "header")
+
+tbl3 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
+  tbl_summary() %>%
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = c("Bacterial", "Fungal")) %>% 
+  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
+  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
+  bold_levels() %>%
+  modify_column_indent(columns = label, undo = TRUE)
+
+tbl3_1 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  filter(infection_type_bacterial_viral_fungal_parasitic == "Viral") %>%
+  select(infection_type_details) %>% 
+  tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
+  remove_row_type(infection_type_details, type = "header")
+
+tbl_stack(list(tbl1, tbl1_1, tbl2, tbl2_1, tbl3, tbl3_1))
+```
+
+```{r infection details between 31 - 100 days}
+tbl1 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days > 30 &
+           time_from_infusion_to_infection_days <= 100) %>% 
+  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
+  tbl_summary() %>%
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = c("Fungal", "Viral")) %>%
+  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>%
+  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
+  modify_column_indent(columns = label, undo = TRUE) %>% 
+  bold_levels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Infections day 31 – 100**")
+
+tbl1_1 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days > 30 &
+           time_from_infusion_to_infection_days <= 100) %>% 
+  filter(infection_type_bacterial_viral_fungal_parasitic == "Bacterial") %>%
+  select(infection_type_details) %>% 
+  tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
+  remove_row_type(infection_type_details, type = "header")
+
+tbl2 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days > 30 &
+           time_from_infusion_to_infection_days <= 100) %>% 
+  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
+  tbl_summary() %>%
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = c("Bacterial", "Viral")) %>% 
+  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
+  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
+  bold_levels() %>%
+  modify_column_indent(columns = label, undo = TRUE)
+
+# tbl2_1 <- cilta %>% 
+#   filter(time_from_infusion_to_infection_days > 30 &
+#            time_from_infusion_to_infection_days <= 100) %>% 
+#   filter(infection_type_bacterial_viral_fungal_parasitic == "Fungal") %>%
+#   select(infection_type_details) %>% 
+#   tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
+#   remove_row_type(infection_type_details, type = "header")
+
+tbl3 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days > 30 &
+           time_from_infusion_to_infection_days <= 100) %>% 
+  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
+  tbl_summary() %>%
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = c("Bacterial", "Fungal")) %>% 
+  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
+  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
+  bold_levels() %>%
+  modify_column_indent(columns = label, undo = TRUE)
+
+tbl3_1 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days > 30 &
+           time_from_infusion_to_infection_days <= 100) %>% 
+  filter(infection_type_bacterial_viral_fungal_parasitic == "Viral") %>%
+  select(infection_type_details) %>% 
+  tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
+  remove_row_type(infection_type_details, type = "header")
+
+tbl_stack(list(tbl1, tbl1_1, #tbl2,# tbl2_1, 
+               tbl3, tbl3_1))
+```
+
+```{r infection details after 100 days}
+tbl1 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days > 100) %>% 
+  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
+  tbl_summary() %>%
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = c("Fungal", "Viral")) %>%
+  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>%
+  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
+  modify_column_indent(columns = label, undo = TRUE) %>% 
+  bold_levels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
+  modify_footnote(update = everything() ~ NA) %>%
+  modify_spanning_header(all_stat_cols() ~ "**Infections after day 100**")
+
+tbl1_1 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days > 100) %>% 
+  filter(infection_type_bacterial_viral_fungal_parasitic == "Bacterial") %>%
+  select(infection_type_details) %>% 
+  tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
+  remove_row_type(infection_type_details, type = "header")
+
+# tbl2 <- cilta %>% 
+#   filter(time_from_infusion_to_infection_days > 100) %>% 
+#   select(infection_type_bacterial_viral_fungal_parasitic) %>% 
+#   tbl_summary() %>%
+#   remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+#                   type= "level",
+#                   level_value = c("Bacterial", "Viral")) %>% 
+#   remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
+#   add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
+#   bold_levels() %>%
+#   modify_column_indent(columns = label, undo = TRUE)
+# 
+# tbl2_1 <- cilta %>% 
+#   filter(time_from_infusion_to_infection_days > 100) %>% 
+#   filter(infection_type_bacterial_viral_fungal_parasitic == "Fungal") %>%
+#   select(infection_type_details) %>% 
+#   tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
+#   remove_row_type(infection_type_details, type = "header")
+
+tbl3 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days > 100) %>% 
+  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
+  tbl_summary() %>%
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = c("Bacterial", "Fungal")) %>% 
+  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
+  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
+  bold_levels() %>%
+  modify_column_indent(columns = label, undo = TRUE)
+
+tbl3_1 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days > 100) %>% 
+  filter(infection_type_bacterial_viral_fungal_parasitic == "Viral") %>%
+  select(infection_type_details) %>% 
+  tbl_summary(statistic = infection_type_details ~ c("{n}")) %>% 
+  remove_row_type(infection_type_details, type = "header")
+
+tbl_stack(list(tbl1, tbl1_1, #tbl2, tbl2_1, 
+               tbl3, tbl3_1))
+```
+
+## Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
 ```{r}
@@
 
-## Patients with infections in the first 100 days by cell counts and immunoglobulin levels
-CCT5019-0512 has a time to infection but no in Any Infection but yes in Any Severe Infection
+## Patients with infections by cell counts and immunoglobulin levels
 ```{r}
 cilta %>%
-  filter(time_from_infusion_to_infection_days <= 100 |
-           any_infection == "No") %>% 
+  filter(any_infection == "No") %>% 
   distinct(pt_identifier, .keep_all = TRUE) %>% 
@@
 cilta %>% 
-  filter(time_from_infusion_to_infection_days <= 100 |
-           any_sevinfection == "No") %>% 
+  filter(any_sevinfection == "No") %>% 
   arrange(pt_identifier, desc(any_infection), desc(any_sevinfection)) %>%
@@
 (myeloma_involved_heavy_chain != "Igg")
-Should I limit to infections in the first 100 days?
 ```{r}
@@
   scale_fill_brewer(palette = "Spectral")+
-  ylim(0, 100)+
+  ylim(0, 60)+
   labs(fill = NULL, x= NULL, y = "%")+
@@
              y = count)) +
-  geom_alluvium(aes(fill = vzv_ig_g_apheresis)
+  geom_alluvium(aes(fill = vzv_ig_g_apheresis), 
+                color = c("transparent", "transparent", "white", "transparent", "transparent", "transparent")
   )+
@@
   geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+  # geom_hline(yintercept = 5, color = "blue")+
   theme_classic()+
@@
          intersect(starts_with("pneumo"), ends_with("change"))) %>% 
-  drop_na() #%>% 
-  # mutate(new_sort = 
-  #          c(6,10,11,26,8,
-  #            12,24,13,31,
-  #            14,15, 5,9, 16,
-  #            17,30,18,27, 2,
-  #            7,4,19,29,20,
-  #            3, 21, 25, 22, 
-  #            23,1,28),
-  #        .before = 2) %>%
-  # 
-  # arrange(new_sort) %>% 
-  #   select(-new_sort)
+  drop_na() %>% 
+  mutate(new_sort =
+           c(4,3,12,31,13,14,9,15,5,6,8,10,32,16,18,17,19,30,2,1,20,21,40,22),
+         .before = 2) %>%
+
+  arrange(new_sort) %>%
+    select(-new_sort)
 
@@
         column_title = "Change in titers",
-        show_column_names =FALSE,
+        # show_column_names =FALSE,
         row_names_side = "left",

### 2024-01-12 cilta_cel/Manuscript analyses.Rmd
Update code, add tables and plots

@@
                     sheet = "APHERESIS")
+id_to_modify_neurotox <- 
+  read_csv(
+    paste0(here(), 
+           "/cilta_cel/patient id who had icans and delayed neurotox - need to change neurotox type to PRES.csv"))
 ```
@@
               "rbc_transfusion_within_30d_post_cart_yes_1_no_0", "plt_transfusion_within_30d_post_cart_yes_1_no_0", 
-              "rbc_transfusion_30d_post_cart_yes_1_no_0", "plt_transfusion_30d_post_cart_yes_1_no_0"), 
+              "rbc_transfusion_30d_post_cart_yes_1_no_0", "plt_transfusion_30d_post_cart_yes_1_no_0",
+              "tpo_agonist_post_cart_yes_1_no_0"), 
             ~ case_when(
@@
   )) %>% 
-
+  mutate(gain_amp1q21 = case_when(
+    gain_amp1q21 == "No"                                           ~ "No",
+    !is.na(gain_amp1q21)                                           ~ "Yes"
+  )) %>% 
   # Refractory status ----
@@
     TRUE                                                          ~ access_type
+  )) %>% 
+  # Supportive therapies and neutrophil recovery----
+  mutate(neutrophil_recovery_ANC_never_below_500 = case_when(
+    day_of_neutrophil_recovery == "Anc never <500"               ~ "Yes",
+    day_of_neutrophil_recovery == "No neutropenia"               ~ "Yes"
+  )) %>% 
+  mutate(neutrophil_recovery_did_not_recover = case_when(
+    day_of_neutrophil_recovery == "Deceased"                     ~ "Yes",
+    day_of_neutrophil_recovery == "Pd prior to anc recovery"     ~ "Yes"
+  )) %>% 
+  mutate(day_of_neutrophil_recovery_ = case_when(
+    site == "KUMC"                                               ~ as.numeric(day_of_neutrophil_recovery)
+  )) %>% 
+  mutate(across(c("last_date_of_gcsf", "day_of_neutrophil_recovery",
+                  "last_date_of_ivig"), 
+         ~ as.Date(as.numeric(.), origin = "1899-12-30"))) %>% 
+  mutate(first_day_of_gcsf = interval(
+             start = date_of_car_t_infusion, 
+             end = first_date_of_gcsf)/
+           duration(n=1, units = "days"
+  )) %>%
+  mutate(last_day_of_gcsf = interval(
+             start = date_of_car_t_infusion, 
+             end = last_date_of_gcsf)/
+           duration(n=1, units = "days"
+  )) %>%
+  mutate(day_of_stem_cell_boost = interval(
+             start = date_of_car_t_infusion, 
+             end = date_of_stem_cell_boost)/
+           duration(n=1, units = "days"
+  )) %>%
+  mutate(day_of_neutrophil_recovery = interval(
+             start = date_of_car_t_infusion, 
+             end = day_of_neutrophil_recovery)/
+           duration(n=1, units = "days"
+  ), day_of_neutrophil_recovery = coalesce(day_of_neutrophil_recovery_, day_of_neutrophil_recovery)) %>% 
+  select(-day_of_neutrophil_recovery_) %>% 
+  mutate(transfusion_postCART = case_when(
+    rbc_transfusion_within_30d_post_cart_yes_1_no_0 == "Yes" |
+      plt_transfusion_within_30d_post_cart_yes_1_no_0 == "Yes" |
+      rbc_transfusion_30d_post_cart_yes_1_no_0 == "Yes" |
+      plt_transfusion_30d_post_cart_yes_1_no_0 == "Yes"              ~ "Yes"
+  )) %>% 
+  mutate(first_day_of_tpo_agonist = interval(
+             start = date_of_car_t_infusion, 
+             end = first_date_of_tpo_agonist)/
+           duration(n=1, units = "days"
+  )) %>%
+  mutate(last_day_of_tpo_agonist = interval(
+             start = date_of_car_t_infusion, 
+             end = last_date_of_tpo_agonist)/
+           duration(n=1, units = "days"
+  )) %>% 
+  mutate(first_day_of_ivig = interval(
+             start = date_of_car_t_infusion, 
+             end = first_date_of_ivig)/
+           duration(n=1, units = "days"
+  )) %>%
+  mutate(last_day_of_ivig = interval(
+             start = date_of_car_t_infusion, 
+             end = last_date_of_ivig)/
+           duration(n=1, units = "days"
   ))
+
 ```
@@
     str_detect(day30_response_v2, "CR|PR")                           ~ "ORR",
-    is.na(day_30_response_s_cr_cr_vgpr_pr_sd_pd)                     ~ NA_character_,
+    is.na(day30_response_v2)                                         ~ NA_character_,
     TRUE                                                             ~ "PD/SD/MR"
@@
     ORR_mon9 == "ORR" |
-    ORR_mon12 == "ORR"                                            ~ "ORR"
+    ORR_mon12 == "ORR"                                            ~ "ORR",
+    is.na(ORR_30days) & 
+      is.na(ORR_mon3) & 
+      is.na(ORR_mon6) & 
+      is.na(ORR_mon9) &
+      is.na(ORR_mon12)                                            ~ NA_character_, 
+     TRUE                                                         ~ "SD/PD"
   )) %>% 
@@
       mon12_response_v2 == "PD"                                   ~ "PD",
+    TRUE                                                          ~ NA_character_
+  )) %>% 
+  mutate(best_ORRcollapsed = case_when(
+    str_detect(best_response, "CR|PR")                            ~ "PR or better", 
+    str_detect(best_response, "SD|PD")                            ~ "< PR",
     TRUE                                                          ~ NA_character_
@@
 cilta <- cart6 %>%
+  mutate(what_non_parkinsonian_neurotoxicity = case_when(
+    what_non_parkinsonian_neurotoxicity == "Delayed icans, hippocampal sclerosis/gliosis"
+                                                                  ~ "cerebral edema/PRES",
+    TRUE                                                          ~ what_non_parkinsonian_neurotoxicity
+  )) %>% 
   mutate(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no = case_when(
@@
   mutate(parkinsonian_neurotoxicity_yes_no = case_when(
+    str_detect(pt_identifier, id_to_modify_neurotox$id)           ~ "No",
     parkinsonian_neurotoxicity_yes_no == "Yes" & 
@@
   mutate(delayed_neuro_type = case_when(
+    str_detect(pt_identifier, id_to_modify_neurotox$id)           ~ "PRES",
+    what_non_parkinsonian_neurotoxicity == "cerebral edema/PRES"
+                                                                  ~ "PRES",
     what_non_parkinsonian_neurotoxicity == "Aidp"                 ~ "Polyneuropathy",
     what_non_parkinsonian_neurotoxicity == 
-      "Posterior reversible encephalopathy syndrome (PRES) and parkinsonism" 
+      "Posterior reversible encephalopathy syndrome (pres) and parkinsonism" 
                                                                   ~ "Parkinsonian/PRES",
@@
 cilta <- cilta %>% 
-  mutate(ig_g_hsv1_2_apheresis = case_when(
-    ig_g_hsv1_2_apheresis < 0.9         ~ "Negative",
-    ig_g_hsv1_2_apheresis >= 0.9 &
-      ig_g_hsv1_2_apheresis < 1.10      ~ "Indeterminate",
-    ig_g_hsv1_2_apheresis >= 1.10       ~ "Positive"
-  )) %>%
-  mutate(ig_g_hsv1_2_d90 = case_when(
-    ig_g_hsv1_2_d90 < 0.9         ~ "Negative",
-    ig_g_hsv1_2_d90 >= 0.9 &
-      ig_g_hsv1_2_d90 < 1.10      ~ "Indeterminate",
-    ig_g_hsv1_2_d90 >= 1.10       ~ "Positive"
-  )) %>%
+  mutate(across(c(starts_with("ig_g_hsv1_2")), ~ case_when(
+    . < 0.9         ~ "Negative",
+    . >= 0.9 &
+      . < 1.10      ~ "Indeterminate",
+    . >= 1.10       ~ "Positive"
+  ))) %>%
+
+  # mutate(ig_g_hsv1_2_apheresis = case_when(
+  #   ig_g_hsv1_2_apheresis < 0.9         ~ "Negative",
+  #   ig_g_hsv1_2_apheresis >= 0.9 &
+  #     ig_g_hsv1_2_apheresis < 1.10      ~ "Indeterminate",
+  #   ig_g_hsv1_2_apheresis >= 1.10       ~ "Positive"
+  # )) %>%
+  # mutate(ig_g_hsv1_2_d90 = case_when(
+  #   ig_g_hsv1_2_d90 < 0.9         ~ "Negative",
+  #   ig_g_hsv1_2_d90 >= 0.9 &
+  #     ig_g_hsv1_2_d90 < 1.10      ~ "Indeterminate",
+  #   ig_g_hsv1_2_d90 >= 1.10       ~ "Positive"
+  # )) %>%
+  # mutate(ig_g_hsv1_2_d180 = case_when(
+  #   ig_g_hsv1_2_d180 < 0.9         ~ "Negative",
+  #   ig_g_hsv1_2_d180 >= 0.9 &
+  #     ig_g_hsv1_2_d180 < 1.10      ~ "Indeterminate",
+  #   ig_g_hsv1_2_d180 >= 1.10       ~ "Positive"
+  # )) %>%
   mutate_at(c("ig_g_hsv1_2_apheresis",
-              "ig_g_hsv1_2_d90"),
+              "ig_g_hsv1_2_d90",
+              "ig_g_hsv1_2_d180"),
             ~ factor(., levels = c("Positive", "Indeterminate", "Negative"))) %>%
@@
                          race_eth = "Race and ethnicity",
+                         os_from_infusion_months = "Follow-up time from infusion (months)",
                          extramedullary_disease_yes_no = "Extramedullary disease",
@@
                          r_iss_at_car_t_infusion = "R-ISS at cart infusion",
-                         cytogenetics = "High risk cytogenetics", 
+                         cytogenetics = "High risk cytogenetics (not include gain 1q)", 
                          deletion_17p_prior_to_car_t_infusion_yes_no = "Deletion 17p at Infusion", 
@@
                          t_14_16_prior_to_car_t_infusion_yes_no = "t(4:16) at Infusion", 
+                         gain_amp1q21 = "Gain/amp 1q21",
                          number_of_prior_lines_of_therapy = "Number of prior lines of therapy",
@@
                          Prior_bcma_therapy = "Prior BCMA-directed therapy",
-                         need_for_g_csf_post_infus_yes_1_no_0 = "Need for gCSF post infusion",
-                         need_for_ivig_yes_1_no_0 = "Need for IVIG",
+                         need_for_g_csf_post_infus_yes_1_no_0 = "Granulocyte colony stimulating factor (G-CSF)",
+                         need_for_ivig_yes_1_no_0 = "Intravenous immunoglobulin (IVIG)",
                          cd34_stem_cell_boost_yes_1_no_0 = "CD34 stem cell boost",
+                         day_of_neutrophil_recovery = "Day of neutrophil recovery",
+                         transfusion_postCART = "Transfusion post-CAR T",
+                         tpo_agonist_post_cart_yes_1_no_0 = "Thrombopoietin (TPO) agonist",
                          # bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
@@
                          cell_dose_million_cells = "Total cell dose (million cells)",
+                         best_ORRcollapsed = "Best ORR at ≤ 12 months",
                          did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no =
@@
 Patients evaluable at each time point
-```{r}
+```{r evaluable}
 day7 <- cilta %>% 
@@
 
-```{r}
+```{r infused}
 cilta %>% 
@@
 ## Table 1. Patient baseline characteristics
-```{r}
+```{r Table 1}
 cilta %>% 
@@
          t_4_14_prior_to_car_t_infusion_yes_no,
-         t_14_16_prior_to_car_t_infusion_yes_no,
+         t_14_16_prior_to_car_t_infusion_yes_no, gain_amp1q21,
          bridging_therapy_yes_no,
@@
         t_4_14_prior_to_car_t_infusion_yes_no,
-        t_14_16_prior_to_car_t_infusion_yes_no,
+        t_14_16_prior_to_car_t_infusion_yes_no, gain_amp1q21,
         bridging_therapy_yes_no, prior_auto_sct_yes_no,
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(best_response, best_response_MRD) %>% 
+  select(ORR_as_best_response, best_ORRcollapsed,
+         best_response, best_response_MRD) %>% 
   tbl_summary(#type = list(c(MRD_mon3) ~ "categorical"),
@@
 
-## Bone marrow biopsy findings
-```{r}
-tbl1 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select("marrow cellularity" = marrow_cellularity_baseline_normo_hypo_hyper, 
-         "marrow cellularity (%)" = marrow_cellularity_baseline_percent,
-         "% CD138 positive by IHC" = marrow_cd138_baseline_percent,
-         "is cellularity variable?"= contains("marrow_cellularity_baseline") & contains("is_variable_"),
-         "Fibrosis grade" = marrow_fibrosis_baseline_0_1_2_3, 
-         "Dysplasia present" = marrow_dysplasia_baseline_yes_no
-  ) %>% 
-  tbl_summary(type = list(
-    c("marrow cellularity (%)", "% CD138 positive by IHC",
-      "Fibrosis grade") ~ "continuous",
-    c("Dysplasia present") ~ "categorical"
-  ),
-  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-  digits = all_continuous() ~ 1,
-  missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl2 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select("marrow cellularity" = marrow_cellularity_day_30_normo_hypo_hyper, 
-         "marrow cellularity (%)" = marrow_percent_cellularity_day_30,
-         "% CD138 positive by IHC" = marrow_percent_cd138_day_30, 
-         "is cellularity variable?"= contains("marrow_cellularity_day_30") & contains("is_variable_"),
-         "Fibrosis grade" = marrow_fibrosis_day_30_0_1_2_3, 
-         "Dysplasia present" = marrow_dysplasia_day_30_yes_no
-  ) %>% 
-  tbl_summary(type = list(
-    c("marrow cellularity (%)", "% CD138 positive by IHC",
-      "Fibrosis grade") ~ "continuous",
-    c("Dysplasia present") ~ "categorical"
-  ),
-  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-  digits = all_continuous() ~ 1,
-  missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl3 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select("marrow cellularity" = marrow_cellularity_day_90_normo_hypo_hyper, 
-         "marrow cellularity (%)" = marrow_percent_cellularity_day_90,
-         "% CD138 positive by IHC" = marrow_percent_cd138_day_90, 
-         "is cellularity variable?"= contains("marrow_cellularity_day_90") & contains("is_variable_"),
-         "Fibrosis grade" = marrow_fibrosis_day_90_0_1_2_3, 
-         "Dysplasia present" = marrow_dysplasia_day_90_yes_no
-  ) %>% 
-  tbl_summary(type = list(
-    c("marrow cellularity (%)", "% CD138 positive by IHC",
-      "Fibrosis grade") ~ "continuous",
-    c("Dysplasia present") ~ "categorical"
-  ),
-  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-  digits = all_continuous() ~ 1,
-  missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl4 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select("marrow cellularity" = marrow_cellularity_day_180_normo_hypo_hyper, 
-         "marrow cellularity (%)" = marrow_percent_cellularity_day_180,
-         "% CD138 positive by IHC" = marrow_percent_cd138_day_180, 
-         "is cellularity variable?"= contains("marrow_cellularity_day_180") & contains("is_variable_"),
-         "Fibrosis grade" = marrow_fibrosis_day_180_0_1_2_3, 
-         "Dysplasia present" = marrow_dysplasia_day_180_yes_no
-  ) %>% 
-  tbl_summary(type = list(
-    c("marrow cellularity (%)", "% CD138 positive by IHC",
-      "Fibrosis grade") ~ "continuous",
-    c("Dysplasia present") ~ "categorical"
-  ),
-  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-  digits = all_continuous() ~ 1,
-  missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl_merge(list(tbl1, tbl2, tbl3, tbl4), 
-          tab_spanner = c("Baseline", "Day 30", "Day 90", "Day 180"))
-```
-
-## Supportive therapies and engraftment
-Jenn did it for the ide-cel paper
-
-```{r}
-# cart1 %>% 
-#   distinct(pt_identifier, .keep_all = TRUE) %>% 
-#   select(`need_for_g_csf_post_infus_yes_1_no_0`, `First Day of GCSF`, `Last Day of GCSF`,
-#          `cd34_stem_cell_boost_yes_1_no_0`, `Day of stem cell boost`, `cell_dose_million_cells`,
-#          `Engraftment Day`,
-#          `rbc_transfusion_within_30d_post_cart_yes_1_no_0`, `plt_transfusion_within_30d_post_cart_yes_1_no_0`, 
-#          `rbc_transfusion_30d_post_cart_yes_1_no_0`, `plt_transfusion_30d_post_cart_yes_1_no_0`,
-#          `need_for_ivig_yes_1_no_0`, `First day of IVIG`, `Last day of IVIG`
-#   ) %>% 
-#   tbl_summary(type = list(
-#     c(`Day of stem cell boost`, `cell_dose_million_cells`,
-#     `Last day of IVIG`) ~ "continuous",
-#     c(`need_for_g_csf_post_infus_yes_1_no_0`,
-#       `cd34_stem_cell_boost_yes_1_no_0`,
-#       `rbc_transfusion_within_30d_post_cart_yes_1_no_0`, `plt_transfusion_within_30d_post_cart_yes_1_no_0`, 
-#          `rbc_transfusion_30d_post_cart_yes_1_no_0`, `plt_transfusion_30d_post_cart_yes_1_no_0`,
-#       `need_for_ivig_yes_1_no_0`) ~ "categorical"
-#   ),
-#             statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-#             digits = all_continuous() ~ 1) %>% 
-#   bold_labels() %>% add_stat_label()
-```
-
-## Apheresis and product characteristics
-```{r}
+## Table S3. Apheresis and product characteristics
+```{r Apheresis and product characteristics}
 cilta %>% 
@@
 ## Table 3. Cytopenias following ide-cel
-
-```{r}
+```{r Table 3}
 tbl1 <- cilta %>% 
@@
 
+## Table 4. Bone marrow biopsy findings
+```{r Table 4}
+tbl1 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select("marrow cellularity" = marrow_cellularity_baseline_normo_hypo_hyper, 
+         "marrow cellularity (%)" = marrow_cellularity_baseline_percent,
+         "% CD138 positive by IHC" = marrow_cd138_baseline_percent,
+         "is cellularity variable?"= contains("marrow_cellularity_baseline") & contains("is_variable_"),
+         "Fibrosis grade" = marrow_fibrosis_baseline_0_1_2_3, 
+         "Dysplasia present" = marrow_dysplasia_baseline_yes_no
+  ) %>% 
+  tbl_summary(type = list(
+    c("marrow cellularity (%)", "% CD138 positive by IHC",
+      "Fibrosis grade") ~ "continuous",
+    c("Dysplasia present") ~ "categorical"
+  ),
+  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+  digits = all_continuous() ~ 1,
+  missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl2 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(os_from_infusion_months > (30 / 30.417)) %>% 
+  select("marrow cellularity" = marrow_cellularity_day_30_normo_hypo_hyper, 
+         "marrow cellularity (%)" = marrow_percent_cellularity_day_30,
+         "% CD138 positive by IHC" = marrow_percent_cd138_day_30, 
+         "is cellularity variable?"= contains("marrow_cellularity_day_30") & contains("is_variable_"),
+         "Fibrosis grade" = marrow_fibrosis_day_30_0_1_2_3, 
+         "Dysplasia present" = marrow_dysplasia_day_30_yes_no
+  ) %>% 
+  tbl_summary(type = list(
+    c("marrow cellularity (%)", "% CD138 positive by IHC",
+      "Fibrosis grade") ~ "continuous",
+    c("Dysplasia present") ~ "categorical"
+  ),
+  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+  digits = all_continuous() ~ 1,
+  missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl3 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(os_from_infusion_months > 3) %>% 
+  select("marrow cellularity" = marrow_cellularity_day_90_normo_hypo_hyper, 
+         "marrow cellularity (%)" = marrow_percent_cellularity_day_90,
+         "% CD138 positive by IHC" = marrow_percent_cd138_day_90, 
+         "is cellularity variable?"= contains("marrow_cellularity_day_90") & contains("is_variable_"),
+         "Fibrosis grade" = marrow_fibrosis_day_90_0_1_2_3, 
+         "Dysplasia present" = marrow_dysplasia_day_90_yes_no
+  ) %>% 
+  tbl_summary(type = list(
+    c("marrow cellularity (%)", "% CD138 positive by IHC",
+      "Fibrosis grade") ~ "continuous",
+    c("Dysplasia present") ~ "categorical"
+  ),
+  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+  digits = all_continuous() ~ 1,
+  missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl4 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(os_from_infusion_months > 6) %>% 
+  select("marrow cellularity" = marrow_cellularity_day_180_normo_hypo_hyper, 
+         "marrow cellularity (%)" = marrow_percent_cellularity_day_180,
+         "% CD138 positive by IHC" = marrow_percent_cd138_day_180, 
+         "is cellularity variable?"= contains("marrow_cellularity_day_180") & contains("is_variable_"),
+         "Fibrosis grade" = marrow_fibrosis_day_180_0_1_2_3, 
+         "Dysplasia present" = marrow_dysplasia_day_180_yes_no
+  ) %>% 
+  tbl_summary(type = list(
+    c("marrow cellularity (%)", "% CD138 positive by IHC",
+      "Fibrosis grade") ~ "continuous",
+    c("Dysplasia present") ~ "categorical"
+  ),
+  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+  digits = all_continuous() ~ 1,
+  missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl_merge(list(tbl1, tbl2, tbl3, tbl4), 
+          tab_spanner = c("Baseline", "Day 30", "Day 90", "Day 180"))
+```
+
+## Table 5. Supportive therapies and engraftment
+
+```{r Table 5. Supportive therapies and engraftment}
+tbl1 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(need_for_g_csf_post_infus_yes_1_no_0) %>%
+  tbl_summary() %>%
+  bold_labels() %>% add_stat_label()
+
+tbl1_1 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(first_day_of_gcsf, last_day_of_gcsf) %>%
+  tbl_summary(type = list(
+    everything() ~ "continuous"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>%
+  add_stat_label()
+
+tbl2 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(cd34_stem_cell_boost_yes_1_no_0) %>%
+  tbl_summary() %>%
+  bold_labels() %>% add_stat_label()
+
+tbl2_1 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(day_of_stem_cell_boost, boost_cell_dose_million_cells) %>%
+  tbl_summary(type = list(
+    everything() ~ "continuous"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>%
+  add_stat_label()
+
+tbl3 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(day_of_neutrophil_recovery) %>%
+  tbl_summary(statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>%
+  bold_labels() %>% add_stat_label()
+
+tbl3_1 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(neutrophil_recovery_ANC_never_below_500, neutrophil_recovery_did_not_recover) %>%
+  tbl_summary(type = list(
+    everything() ~ "dichotomous"),
+    missing = "no") %>%
+  add_stat_label()
+
+tbl4 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(transfusion_postCART) %>%
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+    missing = "no") %>%
+  bold_labels() %>% add_stat_label()
+
+tbl4_1 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(rbc_transfusion_within_30d_post_cart_yes_1_no_0, plt_transfusion_within_30d_post_cart_yes_1_no_0,
+         rbc_transfusion_30d_post_cart_yes_1_no_0, plt_transfusion_30d_post_cart_yes_1_no_0) %>%
+  tbl_summary(
+    missing = "no") %>%
+  add_stat_label()
+
+tbl5 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(tpo_agonist_post_cart_yes_1_no_0) %>%
+  tbl_summary(
+    missing = "no") %>%
+  bold_labels() %>% add_stat_label()
+
+tbl5_1 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(first_day_of_tpo_agonist, last_day_of_tpo_agonist) %>%
+  tbl_summary(type = list(
+    everything() ~ "continuous"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>%
+  add_stat_label()
+
+tbl6 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(need_for_ivig_yes_1_no_0) %>%
+  tbl_summary() %>%
+  bold_labels() %>% add_stat_label()
+
+tbl6_1 <- cilta %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(first_day_of_ivig, last_day_of_ivig) %>%
+  tbl_summary(type = list(
+    everything() ~ "continuous"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>%
+  add_stat_label()
+
+tbl_stack(list(tbl1, tbl1_1, tbl2, tbl2_1, tbl3, tbl3_1,
+               tbl4, tbl4_1, tbl5, tbl5_1, tbl6, tbl6_1))
+```
+
 ## Patient characteristics by grade 3+ cytopenia at Day 30
-```{r}
+```{r Patient characteristics by grade 3+ cytopenia at Day 30}
 cilta %>% 
@@
 ## Patient characteristics by grade 3+ cytopenia at Day 90
-```{r}
+```{r Patient characteristics by grade 3+ cytopenia at Day 90}
 cilta %>% 
@@
 ## CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
-```{r}
+```{r CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30}
 tbl1 <- cilta %>% 
@@
   # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(best_response, gr3_cytopenia_30d) %>% 
+  select(best_response, best_ORRcollapsed,
+         gr3_cytopenia_30d) %>% 
   tbl_summary(by = gr3_cytopenia_30d,
@@
 ## Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
-```{r}
+```{r Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy}
 cilta %>% 
@@
 ## Patients with infections by cell counts and immunoglobulin levels
-```{r}
+```{r Patients with infections by cell counts and immunoglobulin levels}
 cilta %>%
@@
 (myeloma_involved_heavy_chain != "Igg")
-```{r}
+```{r Immunoglobulin levels excluding patients with that type of myeloma}
 cilta %>% 
@@
 ### Figures
-```{r}
+```{r fig_dat}
 fig_dat <- cilta %>% 
@@
 
-```{r, fig.height=12}
+```{r Figure 2. Inflammatory markers after ide-cel, fig.height=12}
 LDH <- fig_dat %>% 
@@
 
-```{r, fig.width=12, fig.height=7}
+```{r Figure 4. Cytopenias over time, fig.width=12, fig.height=7}
 # fig_dat %>% 
@@
          `Leukopenia_-5d`, Leukopenia_30d, #Leukopenia_60d,
-         Leukopenia_90d,
+         Leukopenia_90d, Leukopenia_180d,
          Neutropenia_apheresis,
          `Neutropenia_-5d`, Neutropenia_30d, #Neutropenia_60d,
-         Neutropenia_90d,
+         Neutropenia_90d, Neutropenia_180d,
          Anemia_apheresis,
          `Anemia_-5d`, Anemia_30d, #Anemia_60d, 
-         Anemia_90d,
+         Anemia_90d, Anemia_180d,
          Thrombocytopenia_apheresis,
          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, #Thrombocytopenia_60d, 
-         Thrombocytopenia_90d,
+         Thrombocytopenia_90d, Thrombocytopenia_180d,
          cytopenia_apheresis, `cytopenia_-5d`, cytopenia_30d,# cytopenia_60d, 
-         cytopenia_90d,
+         cytopenia_90d, cytopenia_180d,
 
@@
          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, #gr3_Leukopenia_60d, 
-         gr3_Leukopenia_90d,
+         gr3_Leukopenia_90d, gr3_Leukopenia_180d,
          gr3_Neutropenia_apheresis,
          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, #gr3_Neutropenia_60d, 
-         gr3_Neutropenia_90d,
+         gr3_Neutropenia_90d, gr3_Neutropenia_180d,
          gr3_Anemia_apheresis,
          `gr3_Anemia_-5d`, gr3_Anemia_30d, #gr3_Anemia_60d, 
-         gr3_Anemia_90d,
+         gr3_Anemia_90d, gr3_Anemia_180d,
          gr3_Thrombocytopenia_apheresis,
          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, #gr3_Thrombocytopenia_60d, 
-         gr3_Thrombocytopenia_90d,
+         gr3_Thrombocytopenia_90d, gr3_Thrombocytopenia_180d,
          gr3_cytopenia_apheresis, `gr3_cytopenia_-5d`, gr3_cytopenia_30d, #gr3_cytopenia_60d, 
-         gr3_cytopenia_90d
+         gr3_cytopenia_90d, gr3_cytopenia_180d
   ) %>% 
-  pivot_longer(cols = Neutropenia_apheresis: gr3_cytopenia_90d) %>% 
+  pivot_longer(cols = Neutropenia_apheresis: gr3_cytopenia_180d) %>% 
   mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
@@
   # add_row("name"="Leukopenia",  "day"="apheresis", "value"= "Yes", "grade"="Any grade", "count"=0, "perc"=0) %>% 
-  mutate(day = factor(day, levels = c("apheresis", "-5d", "30d", "60d", "90d"))) %>% 
+  mutate(day = factor(day, levels = c("apheresis", "-5d", "30d", "60d", "90d", "180d"))) %>% 
   mutate(name = str_replace(name, "^cytopenia", "Any Cytopenia")) %>% 
@@
                          labels= c("Any Grade", "Grade 3+"))
-####################################################################################################
-# a %>% filter(grade == "Grade 3+") %>% 
-#   ggplot(aes(x= day, 
-#              y= perc, 
-#              fill= name, 
-#              ))+
-#   geom_bar(stat = "identity",
-#            position=position_dodge(width=0.9))+
-#   geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 4.5,
-#             position = position_dodge(width=0.9)
-#             )+
-#   
-#   scale_fill_brewer(palette = "Spectral")+
-#   ylim(0, 100)+
-#   labs(fill = NULL, x= NULL, y = "%")+
-#   theme_classic(base_size = 14)
 
@@
 ## Figure 5. Cumulative incidence of infection and infection density
-```{r}
+```{r Figure 5}
 library(tidycmprsk)
@@
 risk_comp <- cilta %>%
+  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
   mutate(event_type = case_when(
@@
     infection_type_bacterial_viral_fungal_parasitic == "Viral"          ~ "Viral",
-    is.na(infection_type_bacterial_viral_fungal_parasitic)              ~ "None"
+    is.na(infection_type_bacterial_viral_fungal_parasitic)              ~ NA_character_
   )) %>%
   mutate(event_type =
-           factor(event_type, levels= c("None","Bacterial","Fungal", "Viral"))) %>%
+           factor(event_type, levels= c("Bacterial","Fungal", "Viral"))) %>%
+  mutate(infection_event = case_when(
+    is.na(event_type)                        ~ 0,
+    !is.na(event_type)                       ~ 1
+  )) %>% 
+  # mutate(event_type = case_when(
+  #   is.na(event_type)                        ~ "N",
+  #   TRUE ~ event_type
+  # )) %>% 
   mutate(date_of_event = interval(start = date_of_car_t_infusion,
@@
          date_of_event = case_when(
-      is.na(date_of_event)             ~ 300,
-      TRUE                             ~ date_of_event))
-
-cum_inc <- cuminc(Surv(date_of_event, event_type) ~ 1, data = risk_comp) %>% 
-  ggcuminc(outcome = c("Bacterial", "Fungal", "Viral"), 
-           geom_step(linewidth=10)) +
-  ylim(c(0, 1)) + 
-  labs(
-    x = "Days"
-  )+
-  add_risktable()
-cum_inc
-
-cuminc(Surv(date_of_event, event_type) ~ 1, data = risk_comp) %>% 
-  ggcuminc(outcome = c("Bacterial", "Fungal", "Viral"), 
-           geom_step(linewidth=10)) +
-  ylim(c(0, 0.25)) +
-  labs(
-    x = "Days"
-  )+
-  add_risktable()
+      is.na(date_of_event)             ~ os_from_infusion_days,
+      TRUE                             ~ date_of_event)) %>% 
+  select(pt_identifier, date_of_event, infection_event, event_type, os_from_infusion_days, os_event, race) 
+# 
+# cum_inc <- cuminc(risk_comp$date_of_event, risk_comp$event_type)
+# timepoints(cum_inc, times = c(0, 100, 200, 300, 400))$est
+# 
+# ggcompetingrisks(fit = cum_inc, multiple_panels = F, xlab = "Days", ylab = "Cumulative incidence of event",title = "Competing Risks Analysis"
+#                  )
+
+# cum_inc <- cuminc(Surv(date_of_event, infection_event) ~ 1, data = b) %>%
+#   ggcuminc(outcome = c("Bacterial", "Fungal", "Viral"),
+#            geom_step(linewidth=10)) +
+#   ylim(c(0, 1)) +
+#   labs(
+#     x = "Days"
+#   )+
+#   add_risktable()
+# cum_inc
+# 
+# survfit2(Surv(date_of_event, event_type) ~ 1, data = a) %>%
+#   ggcuminc(outcome = c("Viral", "Fungal")#,
+#            # geom_step(linewidth=10)
+#            ) +
+#   # ylim(c(0, 0.25)) +
+#   labs(
+#     x = "Days"
+#   )+
+#   add_risktable()
+```
+
+```{r ggsurvplot combine}
+# risk_comp <- risk_comp %>% 
+#   filter(date_of_event > 0) 
+# a <- risk_comp %>% 
+#   arrange(pt_identifier, desc(infection_event)) %>% 
+#   distinct(pt_identifier, .keep_all = TRUE)
+# 
+# # OS
+# os <- survfit(Surv(os_from_infusion_days, os_event) ~ 1, data=a)
+# ggsurvplot(survfit(Surv(os_from_infusion_days, os_event) ~ 1, 
+#                    data=a),
+#            title = "OS Analysis",
+#            fun = "event",
+#            
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+# 
+#            xlab = "Time in days", 
+#            palette = "orange",
+#            legend = "top",
+#            legend.title = "",
+#            # pval = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# )
+# 
+# # Overall infections
+# ov_inf <- survfit(Surv(date_of_event, infection_event) ~ 1, data=a)
+# ggsurvplot(survfit(Surv(date_of_event, infection_event) ~ 1, 
+#                    data=a),
+#            title = "Cumulative Incidence Analysis",
+#            fun = "event",
+#            
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+# 
+#            xlab = "Time in days",
+#            legend = "top",
+#            legend.title = "",
+#            legend.labs = c("Overall infections"),
+#            # pval = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# )
+# 
+# # By infection types
+# ggsurvplot(survfit(Surv(date_of_event, infection_event) ~ event_type, 
+#                    data=a),
+#            title = "Cumulative Incidence Analysis",
+#            fun = "event",
+#            
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+# 
+#            xlab = "Time in days",
+#            legend = "top",
+#            legend.title = "",
+#            # legend.labs = c("Bact", "Fungal"),
+#            # palette = c("blue", "green", "purple", "red"),
+#            pval = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# ) + guides(colour = guide_legend(ncol = 1))
+# 
+# 
+# 
+# 
+# 
+# b <- risk_comp %>% 
+#   mutate(event_type =
+#            factor(event_type, levels= c("Bacterial"))) %>%
+#   mutate(infection_event = case_when(
+#     event_type == "Bacterial"     ~ 1,
+#     TRUE                          ~ 0
+#   )) %>% 
+#   arrange(pt_identifier, desc(event_type)) %>% 
+#   distinct(pt_identifier, .keep_all = TRUE)
+# 
+# bact_inf <- survfit(Surv(date_of_event, infection_event) ~ 1, data=b)
+# ggsurvplot(survfit(Surv(date_of_event, infection_event) ~ 1, 
+#                    data=b),
+#            title = "Cumulative Incidence Analysis",
+#            fun = "event",
+#            
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+# 
+#            xlab = "Time in days",
+#            legend = "top",
+#            legend.title = "",
+#            legend.labs = c("Bacterial"),
+#            # palette = c("blue", "green", "purple", "red"),
+#            # pval = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# ) + guides(colour = guide_legend(ncol = 1))
+# 
+# b <- risk_comp %>% 
+#   mutate(event_type =
+#            factor(event_type, levels= c("Viral"))) %>%
+#   # mutate(date_of_event = case_when(
+#     # pt_identifier == ""   ~ 385,
+#     # TRUE                          ~ date_of_event
+#     # )) %>%
+#   mutate(infection_event = case_when(
+#     # pt_identifier == "" ~ 0,
+#     event_type == "Viral"     ~ 1,
+#     TRUE                          ~ 0
+#   )) %>% 
+#   arrange(pt_identifier, desc(event_type)) %>% 
+#   distinct(pt_identifier, .keep_all = TRUE)
+# 
+# viral_inf <- survfit(Surv(date_of_event, infection_event) ~ 1, data=b)
+# ggsurvplot(survfit(Surv(date_of_event, infection_event) ~ 1, 
+#                    data=b),
+#            title = "Cumulative Incidence Analysis",
+#            fun = "event",
+#            
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+# 
+#            xlab = "Time in days",
+#            legend = "top",
+#            legend.title = "",
+#            legend.labs = c("Viral"),
+#            # palette = c("blue", "green", "purple", "red"),
+#            # pval = TRUE,
+#            cumevents = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# ) + guides(colour = guide_legend(ncol = 1))
+# 
+# ggsurvfit(viral_inf, type = "risk") +
+#   labs(
+#     x = "Days",
+#     y = "Event-free proportion"
+#   ) +
+#   add_censor_mark()
+# 
+# survfit2(Surv(date_of_event, infection_event) ~ 1, b) %>%
+#   ggcuminc(outcome = "Viral") +
+#   add_confidence_interval() +
+#   add_risktable() +
+#   scale_ggsurvfit()
+# 
+# 
+# risk_comp %>% 
+#   filter(event_type == "Viral") %>%
+#   arrange(date_of_event) %>% 
+#   distinct(pt_identifier, .keep_all = TRUE) %>% 
+#   mutate(n = cumsum(infection_event)) %>% 
+#   mutate(n2 = n / 105) %>%
+#   ggplot(aes(x = date_of_event, y = n2))+
+#   geom_step()+
+#   ylim(0,1)
+# 
+# 
+# 
+# 
+# 
+# 
+# 
+# 
+# 
+# 
+# 
+# # Fungal
+# b <- risk_comp %>% 
+#   mutate(event_type =
+#            factor(event_type, levels= c("Fungal"))) %>%
+#   mutate(infection_event = case_when(
+#     event_type == "Fungal"     ~ 1,
+#     TRUE                          ~ 0
+#   )) %>% 
+#   arrange(pt_identifier, desc(event_type)) %>% 
+#   distinct(pt_identifier, .keep_all = TRUE)
+# 
+# fungal_inf <- survfit(Surv(date_of_event, infection_event) ~ 1, data=b)
+# ggsurvplot(survfit(Surv(date_of_event, infection_event) ~ 1, 
+#                    data=b),
+#            title = "Cumulative Incidence Analysis",
+#            fun = "event",
+#            
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+# 
+#            xlab = "Time in days",
+#            legend = "top",
+#            legend.title = "",
+#            legend.labs = c("Fungal"),
+#            # palette = c("blue", "green", "purple", "red"),
+#            # pval = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# ) + guides(colour = guide_legend(ncol = 1))
+# 
+# # inf_by_type <- survfit(Surv(date_of_event, infection_event) ~ 1, data=risk_comp)
+# 
+# fit <- list(Overall_infections = ov_inf, OS = os, 
+#             Bacterial = bact_inf,
+#             Viral = viral_inf,
+#             Fungal = fungal_inf
+#             )
+# ggsurvplot_combine(fit, risk_comp, combine = TRUE,
+#                    fun = "event",
+#                    legend.title = "",
+#                    ylim = c(0,1)
+#                    ) + 
+#   guides(colour = guide_legend(ncol = 1))
+# 
+# 
+# fit <- list(By_type = inf_by_type, OS = os)
+# ggsurvplot_combine(fit, risk_comp, combine = TRUE,
+#                    fun = "cumhaz") + 
+#   guides(colour = guide_legend(ncol = 1))
+# 
+# 
+# fit <- list(Overall_infections = ov_inf, By_type = inf_by_type, OS = os)
+# ggsurvplot_combine(fit, risk_comp, combine = TRUE,
+#                    fun = "cumhaz") + 
+#   guides(colour = guide_legend(ncol = 1))
 ```
@@
 Focus on MCC patients / I didn't use day 180 as they are less values but I can add it if you want.
-```{r}
+```{r Figure S1. Viral titers after ide-cel}
+fig_dat <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE)
 moffitt_subset <- fig_dat %>% filter(site == "Moffitt")
@@
 See below
-```{r}
+```{r HSV 1/2 IgG}
 # Alluvial
@@
 See below
-```{r}
+```{r VZV IgG}
 # Alluvial
@@
 ### C)	CMV IgG (positive=immune vs negative=not immune)
-```{r}
+```{r CMV IgG}
 alluvial_C <- moffitt_subset %>% 
@@
   geom_stratum()+
-  geom_segment(aes(x=1.17, y=12, xend=1.83, yend=12), 
-               color= "white", size=0.3)+
+  # geom_segment(aes(x=1.17, y=12, xend=1.83, yend=12), 
+  #              color= "white", size=0.3)+
   geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
@@
 
-```{r, fig.height=12}
+```{r alluvial combine, fig.height=12}
 (alluvial_A) /
-  (alluvial_B) /
-  (alluvial_C) +
+  (alluvial_B) + #/
+  # (alluvial_C) +
+  plot_annotation(tag_levels = "A")
+```
+
+### A)	HSV 1/2 IgG with day 180
+See below
+```{r HSV 1/2 IgG with day 180}
+# Alluvial
+library(ggalluvial)
+
+alluvial_A <- moffitt_subset %>% 
+  select(pt_identifier, igg_hsv_change,
+         ig_g_hsv1_2_apheresis, ig_g_hsv1_2_d90, ig_g_hsv1_2_d180) %>%
+  drop_na() %>%
+  group_by(ig_g_hsv1_2_apheresis, ig_g_hsv1_2_d90, ig_g_hsv1_2_d180) %>% 
+  summarise(count=n()) %>%
+
+  ggplot(aes(axis1 = ig_g_hsv1_2_apheresis, axis2 = ig_g_hsv1_2_d90, axis3 = ig_g_hsv1_2_d180,
+             y = count)) +
+  geom_alluvium(aes(fill = ig_g_hsv1_2_apheresis)
+  )+
+  geom_stratum()+
+  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+  theme_classic()+
+  ggtitle("Evolution of virus titers")
+```
+12 patients don't have data at day 180.
+
+### B)	VZV IgG (positive=immune vs negative or equivocal=not immune) with day 180
+See below
+```{r VZV IgG with day 180}
+# Alluvial
+alluvial_B <- moffitt_subset %>% 
+  select(pt_identifier, igg_vzv_change,
+         vzv_ig_g_apheresis, vzv_ig_g_d90, vzv_ig_g_d180
+  ) %>% 
+  drop_na() %>% 
+  group_by(vzv_ig_g_apheresis, vzv_ig_g_d90, vzv_ig_g_d180) %>% 
+  summarise(count=n()) %>%
+
+  ggplot(aes(axis1 = vzv_ig_g_apheresis, axis2= vzv_ig_g_d90, axis3 = vzv_ig_g_d180,
+             y = count)) +
+  geom_alluvium(aes(fill = vzv_ig_g_apheresis)
+  )+
+  geom_stratum()+
+  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+  # geom_hline(yintercept = 5, color = "blue")+
+  theme_classic()+
+  ggtitle("Evolution of virus titers")
+```
+11 patients don't have data at day 180.
+
+```{r alluvial day 180 combine, fig.height=12}
+(alluvial_A) /
+  (alluvial_B) + #/
+  # (alluvial_C) 
   plot_annotation(tag_levels = "A")
@@
 
-```{r, fig.width=15, fig.height=12}
+```{r Figure S2. Pneumococcal titers after ide-cel, fig.width=15, fig.height=12}
 library(ComplexHeatmap)
@@
 Limit to evaluable patients at day 90
-```{r}
+```{r MVA and forest plot}
 mva_dat <- fig_dat %>% 
@@
 
-glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + CRS_grade2 + steroid_use_yes_no + number_of_prior_lines_of_therapy,
+glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + 
+      steroid_use_yes_no + number_of_prior_lines_of_therapy + baseline_ferritin_cat,
     data = mva_dat,
@@
 
-```{r}
+```{r forest plot}
 forest_p <- 
-  glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + CRS_grade2 + steroid_use_yes_no + number_of_prior_lines_of_therapy,
+  glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` +
+        steroid_use_yes_no + number_of_prior_lines_of_therapy + baseline_ferritin_cat,
     data = mva_dat,
@@
                  "gr3_cytopenia_-5d",
-                 "CRS_grade2",
+                 "baseline_ferritin_cat",
                  "Steroid Use",
@@
   mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
-  mutate(name= c("High marrow burden (≥50%)",
-                 "Grade ≥ 3 Cytopenia at Day -5",
-                 "Grade ≥ 2 CRS",
-                 "Steroid use",
-                 "Number of prior lines of therapy"
+  mutate(name= case_when(
+    Characteristic == "High marrow burden (≥50%)"      ~ "High marrow burden (≥50%)",
+    Characteristic == "gr3_cytopenia_-5d"      ~ "Grade ≥ 3 Cytopenia at Day -5",
+    Characteristic == "Steroid Use"      ~ "Steroid use",
+    Characteristic == "Number of prior lines of therapy"      ~ "Number of prior lines of therapy",
+    Characteristic == "baseline_ferritin_cat"      ~ "Baseline ferritin"
   ))
@@
 
-```{r, fig.width=15, fig.height=12}
-# ghgghjg
-```
+## Survival analysis - KM by gr3_cytopenia_90d
+```{r Survival analysis - KM by gr3_cytopenia_90d}
+surv_dat <- fig_dat %>% 
+  mutate(ORR_as_best_response = case_when(
+    ORR_as_best_response == "ORR"         ~ "ORR",
+    is.na(ORR_as_best_response)           ~ "never ORR"
+  ))
+
+library(survival)
+ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ gr3_cytopenia_90d, 
+                   data=surv_dat),
+           title = "PFS Analysis",
+           font.main = c(20, "bold", "black"),
+           font.x = c(18, "bold", "black"),
+           font.y = c(18, "bold", "black"),
+           font.legend = c(16, "black"),
+           font.tickslab = c(16, "bold", "black"),
+           size = 1.5,
+
+           xlab = "Time in months",
+           legend = "top",
+           legend.title = "",
+           pval = TRUE,
+           conf.int = FALSE,
+           # Censor
+           censor = TRUE
+) + guides(colour = guide_legend(ncol = 1))
+
+coxph(Surv(time = surv_dat$pfs_from_infusion_months, 
+                   event = surv_dat$pfs_event) ~ gr3_cytopenia_90d, 
+              data = surv_dat)  %>% 
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% 
+  add_nevent(location = "level") %>% add_n(location = "level")
+
+ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ gr3_cytopenia_90d, 
+                   data=surv_dat),
+           title = "OS Analysis",
+           font.main = c(20, "bold", "black"),
+           font.x = c(18, "bold", "black"),
+           font.y = c(18, "bold", "black"),
+           font.legend = c(16, "black"),
+           font.tickslab = c(16, "bold", "black"),
+           size = 1.5,
+
+           xlab = "Time in months",
+           legend = "top",
+           legend.title = "",
+           pval = TRUE,
+           conf.int = FALSE,
+           # Censor
+           censor = TRUE
+) + guides(colour = guide_legend(ncol = 1))
+
+coxph(Surv(time = surv_dat$os_from_infusion_months, 
+                   event = surv_dat$os_event) ~ gr3_cytopenia_90d, 
+              data = surv_dat)  %>% 
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% 
+  add_nevent(location = "level") %>% add_n(location = "level")
+```
+
+## Survival analysis - KM by ORR_as_best_response
+```{r Survival analysis - KM by ORR_as_best_response}
+ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ ORR_as_best_response, 
+                   data=surv_dat),
+           title = "PFS Analysis",
+           font.main = c(20, "bold", "black"),
+           font.x = c(18, "bold", "black"),
+           font.y = c(18, "bold", "black"),
+           font.legend = c(16, "black"),
+           font.tickslab = c(16, "bold", "black"),
+           size = 1.5,
+
+           xlab = "Time in months",
+           legend = "top",
+           legend.title = "",
+           pval = TRUE,
+           conf.int = FALSE,
+           # Censor
+           censor = TRUE
+) + guides(colour = guide_legend(ncol = 1))
+
+coxph(Surv(time = surv_dat$pfs_from_infusion_months, 
+                   event = surv_dat$pfs_event) ~ ORR_as_best_response, 
+              data = surv_dat)  %>% 
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% 
+  add_nevent(location = "level") %>% add_n(location = "level")
+
+ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ ORR_as_best_response, 
+                   data=surv_dat),
+           title = "OS Analysis",
+           font.main = c(20, "bold", "black"),
+           font.x = c(18, "bold", "black"),
+           font.y = c(18, "bold", "black"),
+           font.legend = c(16, "black"),
+           font.tickslab = c(16, "bold", "black"),
+           size = 1.5,
+
+           xlab = "Time in months",
+           legend = "top",
+           legend.title = "",
+           pval = TRUE,
+           conf.int = FALSE,
+           # Censor
+           censor = TRUE
+) + guides(colour = guide_legend(ncol = 1))
+
+coxph(Surv(time = surv_dat$os_from_infusion_months, 
+                   event = surv_dat$os_event) ~ ORR_as_best_response, 
+              data = surv_dat)  %>% 
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% 
+  add_nevent(location = "level") %>% add_n(location = "level")
+```
+
+```{r glm}
+mva_dat <- surv_dat %>% 
+  filter(os_from_infusion_months > 3) %>% 
+  mutate(ORR_as_best_response = case_when(
+    ORR_as_best_response == "ORR"         ~ 1,
+    ORR_as_best_response == "never ORR"   ~ 0
+  ))
+
+glm(ORR_as_best_response ~ gr3_cytopenia_90d,
+    data = mva_dat,
+    family = "binomial") %>%
+  tbl_regression(exponentiate = TRUE, 
+                 intercept = TRUE) %>%
+  add_nevent(location = "level") %>% add_n(location = "level") %>%
+  modify_spanning_header(everything() ~ "**ORR_as_best_response**") %>%
+  bold_p(t = .05) 
+```

### 2024-01-18 cilta_cel/Manuscript analyses.Rmd
Fix MVA and UVA

@@
     ORR_as_best_response == "ORR"         ~ "ORR",
-    is.na(ORR_as_best_response)           ~ "never ORR"
+    ORR_as_best_response == "SD/PD"       ~ "never ORR",
+    # TRUE                                  ~ "never ORR"
   ))
@@
 
+## UVA best ORR by gr3 cytopenia at day 90
+I was unable to perform the analyses investigating severe cytopenias at D90 and best response because everyone with severe cytopenias had an event.
 ```{r glm}
 mva_dat <- surv_dat %>% 
-  filter(os_from_infusion_months > 3) %>% 
+  # filter(os_from_infusion_months > 3) %>% 
   mutate(ORR_as_best_response = case_when(
@@
 
-glm(ORR_as_best_response ~ gr3_cytopenia_90d,
-    data = mva_dat,
-    family = "binomial") %>%
-  tbl_regression(exponentiate = TRUE, 
-                 intercept = TRUE) %>%
-  add_nevent(location = "level") %>% add_n(location = "level") %>%
-  modify_spanning_header(everything() ~ "**ORR_as_best_response**") %>%
-  bold_p(t = .05) 
-```
+# glm(ORR_as_best_response ~ gr3_cytopenia_90d,
+#     data = mva_dat,
+#     family = "binomial") %>%
+#   tbl_regression(exponentiate = TRUE, 
+#                  intercept = TRUE) %>%
+#   add_nevent(location = "level") %>% add_n(location = "level") %>%
+#   modify_spanning_header(everything() ~ "**ORR_as_best_response**") %>%
+#   bold_p(t = .05) 
+```

### 2024-01-26 cilta_cel/Manuscript analyses.Rmd
Add infection categories, HLH, violin plots replacing cumulative incidence plots, ...

@@
            "/cilta_cel/patient id who had icans and delayed neurotox - need to change neurotox type to PRES.csv"))
+
+infections_cat <- 
+  read_csv(
+    paste0(here(), 
+           "/cilta_cel/Infections categorized.csv")) %>% 
+  distinct() %>% 
+  purrr::keep(~!all(is.na(.))) %>% 
+  rename("infection_type_cat" = `...14`) %>% 
+  drop_na(infection_type_details) %>% 
+  add_row(infection_type_bacterial_viral_fungal_parasitic = "Bacterial", 
+          infection_type_details = "Pna, unknown organism (covid -) resulting in ards and death",
+          infection_type_cat = "Respiratory infections")
+
+viral_cat <- 
+  read_csv(
+    paste0(here(), 
+           "/cilta_cel/Infections categorized.csv DKH.csv")) %>% 
+  distinct() %>% 
+  janitor::clean_names() %>% 
+  select(-c(x4,x5))
+
+HLH <-
+  readxl::read_xlsx(paste0(here(), "/cilta_cel/HLH.xlsx"))
 ```
@@
   full_join(., Apheresis, by = "PT Identifier") %>% 
+  left_join(., HLH, by = c("PT Identifier" = "PT Identifier (DO NOT USE PHI)")) %>% 
   janitor::clean_names()
@@
                 ~ str_to_sentence(.) )) %>% 
+  # Merge with infection and viral group here afetr str_to_sentence
+  left_join(., infections_cat,
+            by = c("infection_type_bacterial_viral_fungal_parasitic", "infection_type_details")) %>%
+  left_join(., viral_cat,
+            by = c("infection_type_bacterial_viral_fungal_parasitic", "infection_type_details")) %>%
   mutate(across(c(contains("vgpr"), "response_to_bridging_chemotherapy"
@@
 
-  mutate(across(where(is.character), ~ str_replace(., "Unknown|unknown", NA_character_))) %>%
+  mutate(across(where(is.character), 
+                ~ str_replace(., "^Unknown$|^unknown$|^UNKNOWN$", NA_character_))) %>%
   # Create site variable
@@
   )) %>% 
-  mutate(day_of_neutrophil_recovery_ = case_when(
+  mutate(day_of_neutrophil_recovery_KUMC = case_when(
     site == "KUMC"                                               ~ as.numeric(day_of_neutrophil_recovery)
+  )) %>% 
+  mutate(ivig_last_date_beyond_pd = case_when(
+    last_date_of_ivig == "Beyond pd"       ~ "Yes"
   )) %>% 
@@
          ~ as.Date(as.numeric(.), origin = "1899-12-30"))) %>% 
+  mutate(date_of_neutrophil_recovery = day_of_neutrophil_recovery,
+         date_of_neutrophil_recovery = case_when(
+           date_of_neutrophil_recovery < date_of_car_t_infusion    ~ NA_Date_,
+           TRUE                                                    ~ date_of_neutrophil_recovery
+         )) %>% 
+  mutate(day_of_neutrophil_recovery = interval(
+             start = date_of_car_t_infusion, 
+             end = date_of_neutrophil_recovery)/
+           duration(n=1, units = "days"
+  ), day_of_neutrophil_recovery = coalesce(day_of_neutrophil_recovery_KUMC, day_of_neutrophil_recovery)) %>% 
   mutate(first_day_of_gcsf = interval(
@@
   )) %>%
-  mutate(day_of_neutrophil_recovery = interval(
-             start = date_of_car_t_infusion, 
-             end = day_of_neutrophil_recovery)/
-           duration(n=1, units = "days"
-  ), day_of_neutrophil_recovery = coalesce(day_of_neutrophil_recovery_, day_of_neutrophil_recovery)) %>% 
-  select(-day_of_neutrophil_recovery_) %>% 
   mutate(transfusion_postCART = case_when(
@@
            duration(n=1, units = "days"
+  ), first_day_of_ivig = case_when(
+    first_day_of_ivig >= 0                                         ~ first_day_of_ivig,
+    TRUE                                                           ~ NA_real_
+  )) %>% 
+  mutate(last_date_of_ivig = case_when(
+    ivig_last_date_beyond_pd == "Yes"                              ~ as.Date(as.numeric(date_of_pd),origin = "1899-12-30"),
+    TRUE                                                           ~ last_date_of_ivig
   )) %>% 
@@
            duration(n=1, units = "days"
+  ), last_day_of_ivig = case_when(
+    last_day_of_ivig >= 0                                          ~ last_day_of_ivig,
+    TRUE                                                           ~ NA_real_
+    )) %>% 
+  mutate(need_for_ivig_yes_1_no_0 = case_when(
+    first_date_of_ivig < date_of_car_t_infusion |
+      last_date_of_ivig < date_of_car_t_infusion                   ~ "No",
+    TRUE                                                           ~ need_for_ivig_yes_1_no_0
   ))
@@
   mutate(Neutropenia_7d = case_when(
+    date_of_neutrophil_recovery < date_of_car_t_infusion        ~ "No",
     anc_day_7 < 1.8                                             ~ "Yes",
@@
   mutate(gr3_Neutropenia_7d = case_when(
+    date_of_neutrophil_recovery < date_of_car_t_infusion        ~ "No",
     anc_day_7 < 1                                               ~ "Yes",
@@
   mutate(Neutropenia_gr1 = case_when(
+    date_of_neutrophil_recovery < date_of_car_t_infusion        ~ "No",
     (anc_day_7 < 1.8 &
@@
   mutate(Neutropenia_gr2 = case_when(
+    date_of_neutrophil_recovery < date_of_car_t_infusion        ~ "No",
     (anc_day_7 < 1.5 &
@@
   mutate(Neutropenia_gr3 = case_when(
+    date_of_neutrophil_recovery < date_of_car_t_infusion        ~ "No",
     anc_day_7 < 1 |
@@
   # Infection ----
-  mutate(any_infection = infection_yes_1_no_0
-  ) %>%
-  mutate(any_sevinfection = severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0
-  ) %>% 
   mutate(time_from_infusion_to_infection_days = 
@@
              end = date_of_infection)/
-           duration(n=1, units = "days"))
+           duration(n=1, units = "days"), 
+         time_from_infusion_to_infection_days = case_when(
+    time_from_infusion_to_infection_days >= 0     ~ time_from_infusion_to_infection_days,
+    TRUE                                          ~ NA_real_
+    )) %>% 
+  mutate(any_infection = case_when(
+    time_from_infusion_to_infection_days >= 0     ~ infection_yes_1_no_0,
+    TRUE                                          ~ "No"
+  )) %>%
+  mutate(any_sevinfection = case_when(
+    time_from_infusion_to_infection_days >= 0     ~ severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0,
+    TRUE                                          ~ "No"
+  )) %>% 
+  mutate(across(c("infection_type_details", "infection_type_bacterial_viral_fungal_parasitic",
+                  "infection_type_cat"), ~ case_when(
+    time_from_infusion_to_infection_days >= 0     ~ .,
+    TRUE                                          ~ NA_character_
+  )))
 
@@
                                                                   ~ "PRES",
-    what_non_parkinsonian_neurotoxicity == "Aidp"                 ~ "Polyneuropathy",
+    what_non_parkinsonian_neurotoxicity == "Aidp" |
+      what_non_parkinsonian_neurotoxicity == "Slowed cognition"   ~ "Polyneuropathy",
     what_non_parkinsonian_neurotoxicity == 
@@
                          delayed_neuro_type = "Delayed Neurotoxicity Type",
+                         hlh = "HLH", hlh_hlh_like_toxicities = "HLH/HLH-Like Toxicities?",
 
@@
          other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
-         delayed_neuro_type) %>% 
+         delayed_neuro_type,
+         hlh, hlh_hlh_like_toxicities) %>% 
   tbl_summary(type = list(
@@
 
-## Patient characteristics by grade 3+ cytopenia at Day 30
+## Table S4. Patient characteristics by grade 3+ cytopenia at Day 30
 ```{r Patient characteristics by grade 3+ cytopenia at Day 30}
@@
 
-## Patient characteristics by grade 3+ cytopenia at Day 90
+## Table S5. Patient characteristics by grade 3+ cytopenia at Day 90
 ```{r Patient characteristics by grade 3+ cytopenia at Day 90}
@@
 
-## CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
+## Table S6. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
 ```{r CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30}
@@
          delayed_neuro_type,
+         hlh, hlh_hlh_like_toxicities,
          gr3_cytopenia_30d) %>% 
@@
 
-## Table S8.Details of infections after ide-cel
+## Table S8. Details of infections after ide-cel
+Patients can be counted multiple times if multiple infections.
 ```{r infection details 30 first days}
@@
 
-## Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
+## Table S9. Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
 ```{r Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy}
 cilta %>% 
+  arrange(pt_identifier, desc(any_infection)) %>% 
   distinct(pt_identifier, .keep_all = TRUE) %>% 
@@
          delayed_neuro_type,
+         hlh, hlh_hlh_like_toxicities,
          steroid_use_yes_no, 
@@
 
-## Patients with infections by cell counts and immunoglobulin levels
+## Table S10 A-B. Patients with infections by cell counts and immunoglobulin levels
 ```{r Patients with infections by cell counts and immunoglobulin levels}
 cilta %>%
-  filter(any_infection == "No") %>% 
+  arrange(pt_identifier, desc(any_infection)) %>% 
   distinct(pt_identifier, .keep_all = TRUE) %>% 
@@
 cilta %>% 
-  filter(any_sevinfection == "No") %>% 
   arrange(pt_identifier, desc(any_infection), desc(any_sevinfection)) %>%
@@
 
-## Immunoglobulin levels excluding patients with that type of myeloma 
+## Table S10 C-D. Immunoglobulin levels excluding patients with that type of myeloma 
 (myeloma_involved_heavy_chain != "Igg")
@@
 cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
   filter(myeloma_involved_heavy_chain != "Igg" | is.na(myeloma_involved_heavy_chain)) %>% 
+  arrange(pt_identifier, desc(any_infection)) %>%
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
   select(ig_g_day_5, ig_g_day_30,
@@
 cilta %>% 
+  filter(myeloma_involved_heavy_chain != "Igg" | is.na(myeloma_involved_heavy_chain)) %>% 
   arrange(pt_identifier, desc(any_infection), desc(any_sevinfection)) %>%
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(myeloma_involved_heavy_chain != "Igg" | is.na(myeloma_involved_heavy_chain)) %>% 
   select(ig_g_day_5, ig_g_day_30,
@@
 
-## Figure 2. Inflammatory markers after ide-cel
+## Figure S1. Inflammatory markers after ide-cel
 
@@
 
-## Figure 3. Cellular and humoral immune reconstitution after cilta-cel
+## Figure 2. Cellular and humoral immune reconstitution after cilta-cel
 ```{r timeserie, fig.width=12, fig.height=12}
@@
 
-## Figure 4. Cytopenias over time
+## Figure 3. Cytopenias over time
 
@@
 
-## Figure 5. Cumulative incidence of infection and infection density
+## Figure 4. Cumulative incidence of infection and infection density
 ```{r Figure 5}
@@
 
-## Figure S1. Viral titers after ide-cel
+```{r violin plot}
+cilta %>%
+  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
+  select(pt_identifier, any_infection, any_sevinfection, date_of_infection, 
+         time_from_infusion_to_infection_days, infection_type_bacterial_viral_fungal_parasitic,
+         infection_type_cat) %>% 
+  mutate(any_sevinfection = case_when(
+    any_sevinfection == "Yes"           ~ "Severe"
+  )) %>% 
+  mutate(any_infection = case_when(
+    any_sevinfection == "Severe"        ~ NA_character_,
+    any_infection == "Yes"              ~ "Not severe"
+  )) %>% 
+  pivot_longer(cols = c(any_infection, any_sevinfection), 
+               names_to = "Infection", 
+               values_to = "Infection severity") %>% 
+  drop_na(`Infection severity`) %>% 
+  mutate(infection_type_cat = str_replace(infection_type_cat, " \\+ ", " and ")) %>% 
+  separate_wider_delim(cols = infection_type_cat, delim = " and ",
+                       names = c("infection_type_cat1", "infection_type_cat2"), 
+                       too_few = "align_start", too_many = "merge", 
+                       cols_remove = TRUE) %>% 
+  pivot_longer(cols = c(infection_type_cat1, infection_type_cat2), 
+               names_to = NULL, 
+               values_to = "Infection categories") %>% 
+  drop_na(`Infection categories`) %>% 
+  ggplot(aes(x = infection_type_bacterial_viral_fungal_parasitic, 
+             y = time_from_infusion_to_infection_days))+
+  geom_violin()+
+  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
+  # geom_point(aes(color = `Infection severity`), position = "jitter")
+  labs(x = NULL, y = "Infection onset time (days)")+
+  scale_color_manual(values = c("black", "red"))+
+  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))
+
+cilta %>%
+  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
+  select(pt_identifier, any_infection, any_sevinfection, date_of_infection, 
+         time_from_infusion_to_infection_days,
+         infection_type_cat) %>% 
+  mutate(any_sevinfection = case_when(
+    any_sevinfection == "Yes"           ~ "Severe"
+  )) %>% 
+  mutate(any_infection = case_when(
+    any_sevinfection == "Severe"        ~ NA_character_,
+    any_infection == "Yes"              ~ "Not severe"
+  )) %>% 
+  pivot_longer(cols = c(any_infection, any_sevinfection), 
+               names_to = "Infection", 
+               values_to = "Infection severity") %>% 
+  drop_na(`Infection severity`) %>% 
+  mutate(infection_type_cat = str_replace(infection_type_cat, "and Respiratory infection", "and Respiratory infections")) %>% 
+  mutate(infection_type_cat = str_replace(infection_type_cat, " \\+ ", " and ")) %>% 
+  separate_wider_delim(cols = infection_type_cat, delim = " and ",
+                       names = c("infection_type_cat1", "infection_type_cat2"), 
+                       too_few = "align_start", too_many = "merge", 
+                       cols_remove = TRUE) %>% 
+  pivot_longer(cols = c(infection_type_cat1, infection_type_cat2), 
+               names_to = NULL, 
+               values_to = "Infection categories") %>% 
+  drop_na(`Infection categories`) %>% 
+  ggplot(aes(x = `Infection categories`, 
+             y = time_from_infusion_to_infection_days))+
+  geom_violin()+
+  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
+  # geom_point(aes(color = `Infection severity`), position = "jitter")
+  labs(x = NULL, y = "Infection onset time (days)")+
+  scale_color_manual(values = c("black", "red"))+
+  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
+  coord_flip()
+
+cilta %>%
+  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>%
+  filter(infection_type_bacterial_viral_fungal_parasitic == "Viral") %>%
+  select(pt_identifier, any_infection, any_sevinfection, date_of_infection,
+         time_from_infusion_to_infection_days,
+         viral_category) %>%
+  mutate(any_sevinfection = case_when(
+    any_sevinfection == "Yes"           ~ "Severe"
+  )) %>%
+  mutate(any_infection = case_when(
+    any_sevinfection == "Severe"        ~ NA_character_,
+    any_infection == "Yes"              ~ "Not severe"
+  )) %>%
+  pivot_longer(cols = c(any_infection, any_sevinfection),
+               names_to = "Infection",
+               values_to = "Infection severity") %>%
+  drop_na(`Infection severity`) %>%
+  mutate(viral_category = str_replace(viral_category, ", ", " And ")) %>% 
+  mutate(viral_category = str_replace(viral_category, "Rhinovius", "Rhinovirus")) %>% 
+  mutate(viral_category = str_replace(viral_category, "parainfluenza", "Parainfluenza")) %>% 
+  mutate(viral_category = str_replace(viral_category, "Metapneurmovirus", "Metapneumovirus")) %>% 
+  mutate(viral_category = str_remove(viral_category, "\\? ")) %>% 
+  separate_wider_delim(cols = viral_category, delim = " And ",
+                       names = c("viral_category1", "viral_category2"), 
+                       too_few = "align_start", too_many = "merge", 
+                       cols_remove = FALSE) %>% 
+  pivot_longer(cols = c(viral_category1, viral_category2), 
+               names_to = NULL, 
+               values_to = "Viral categories") %>% 
+  drop_na(`Viral categories`) %>% 
+  ggplot(aes(x = `Viral categories`,
+             y = time_from_infusion_to_infection_days))+
+  geom_violin()+
+  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
+  labs(x = NULL, y = "Infection onset time (days)")+
+  scale_color_manual(values = c("black", "red"))+
+  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
+  coord_flip()
+```
+
+## Figure S3. Viral titers after ide-cel
 Focus on MCC patients / I didn't use day 180 as they are less values but I can add it if you want.
@@
 
-## Figure S2. Pneumococcal titers after ide-cel
+## Figure S4. Pneumococcal titers after ide-cel
 
@@
 
-## MVA and forest plot
+## Table S7 and Figure S2. MVA and forest plot
 Limit to evaluable patients at day 90
@@
 
-```{r forest plot}
+```{r forest plot 5}
 forest_p <- 
@@
 
+```{r MVA 3}
+glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + 
+      number_of_prior_lines_of_therapy,
+    data = mva_dat,
+    family = "binomial") %>%
+  tbl_regression(exponentiate = TRUE, 
+                 intercept = TRUE) %>%
+  add_nevent(location = "level") %>% add_n(location = "level") %>%
+  modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
+  bold_p(t = .05) 
+```
+
+```{r forest plot 3}
+forest_p <- 
+  glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` +
+        number_of_prior_lines_of_therapy,
+    data = mva_dat,
+    family = "binomial") %>%
+  tbl_regression(exponentiate = TRUE) %>%
+  as_tibble() %>% 
+  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
+  fill(OR, `95% CI`, .direction = "up") %>% 
+  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
+  filter(Characteristic %in% c("High marrow burden (≥50%)",
+                 "gr3_cytopenia_-5d",
+                 "Number of prior lines of therapy") ) %>% 
+  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
+  mutate(name= case_when(
+    Characteristic == "High marrow burden (≥50%)"      ~ "High marrow burden (≥50%)",
+    Characteristic == "gr3_cytopenia_-5d"      ~ "Grade ≥ 3 Cytopenia at Day -5",
+    # Characteristic == "Steroid Use"      ~ "Steroid use",
+    Characteristic == "Number of prior lines of therapy"      ~ "Number of prior lines of therapy"
+    # Characteristic == "baseline_ferritin_cat"      ~ "Baseline ferritin"
+  ))
+
+ggplot(data=forest_p, aes(y=name, x=OR, xmin=lower, xmax=upper)) +
+  geom_point() + 
+  geom_errorbarh(height=.1) +
+  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
+  theme_classic()+
+  scale_x_log10(breaks = c(0, 0.25, 0.5, 1, 2.5, 5, 10, 40))+
+  labs(y="")
+```
+
 ## Survival analysis - KM by gr3_cytopenia_90d

### 2024-01-31 cilta_cel/Manuscript analyses.Rmd
Add help code to build the consort + fix bug

@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(os_from_infusion_months > (7 / 30.417)) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (7 / 30.417)) %>% 
   select(pt_identifier) %>% 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(os_from_infusion_months > (14 / 30.417)) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (14 / 30.417)) %>% 
   select(pt_identifier) %>% 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(os_from_infusion_months > (21 / 30.417)) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (21 / 30.417)) %>% 
   select(pt_identifier) %>% 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(os_from_infusion_months > (30 / 30.417)) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (30 / 30.417)) %>% 
   select(pt_identifier) %>% 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(os_from_infusion_months > 3) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > 3) %>% 
   select(pt_identifier) %>% 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(os_from_infusion_months > 6) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > 6) %>% 
   select(pt_identifier) %>% 
@@
   bold_labels() %>% add_stat_label()
-tbl_merge(list(day7, day14, day21, day30, day90, day180), 
-          tab_spanner = c("day7", "day14", "day21", "day30", "day90", "day180"))
+mon12 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > 12) %>% 
+  select(pt_identifier) %>% 
+  tbl_summary(missing = "no") %>% 
+  bold_labels() %>% add_stat_label()
+tbl_merge(list(day7, day14, day21, day30, day90, day180, mon12), 
+          tab_spanner = c("day7", "day14", "day21", "day30", "day90", "day180", "month12"))
 ```
@@
 ## Figure 1. Consort diagram
+This will help for creating the figure. It shows the patients who had PD or died with info of the event.
+```{r}
+fig_dat %>% 
+  mutate(pfs_from_infusion_days = 
+           interval(
+             start = date_of_car_t_infusion, 
+             end = pfs_date)/
+           duration(n=1, units = "days")) %>% 
+  filter(os_event == 1 | pfs_event == 1) %>% 
+  mutate(event_at = case_when(
+    !is.na(date_of_pd) & pfs_from_infusion_months < 1        ~ "had pd",
+    !is.na(date_of_pd) & pfs_from_infusion_months < 3        ~ "had pd",
+    !is.na(date_of_pd) & pfs_from_infusion_months < 6        ~ "had pd",
+    !is.na(date_of_pd) & pfs_from_infusion_months < 12       ~ "had pd",
+    os_event == 1 & pfs_from_infusion_months < 1        ~ "died",
+    os_event == 1 & pfs_from_infusion_months < 3        ~ "died",
+    os_event == 1 & pfs_from_infusion_months < 6        ~ "died",
+    os_event == 1 & pfs_from_infusion_months < 12       ~ "died",
+  )) %>% 
+  mutate(phrase = paste("Patient", pt_identifier, event_at, "at day", pfs_from_infusion_days)
+  ) %>% 
+  arrange(pfs_from_infusion_days) %>% 
+  select(phrase, `cause of death` = cause_of_death_myeloma_toxicitiy_unrelated,
+         `CRS grade` = max_crs_grade_0_5, `delayed neurotoxicity` = delayed_neuro_type)
+```
 

### 2024-03-28 cilta_cel/Manuscript analyses.Rmd
Add hlh, days and duration, tables by icaht, ...

@@
     . == "Pauci"                            ~ "Hypo",
-    . == "Variable"                         ~ NA_character_,
+    . == "Variable"                         ~ "Variable", # NA_character_,
     TRUE                                    ~ .
@@
   mutate(agecat = case_when(
-    age < 65                            ~ "< 65 years",
-    age >= 65                           ~ "≥ 65 years"
+    age < 70                                         ~ "< 70 years",
+    age >= 70                                        ~ "≥ 70 years"
   ),
-  agecat = factor(agecat, levels = c("< 65 years", "≥ 65 years"))
+  agecat = factor(agecat, levels = c("< 70 years", "≥ 70 years"))
   ) %>% 
@@
     str_detect(sex, "M")                             ~ "Male",
-    TRUE                                                          ~ "Female"
+    !is.na(sex)                                      ~ "Female"
   )) %>% 
   mutate(male_sex = case_when(
-    str_detect(sex, "M")                                          ~ 1,
-    TRUE                                                          ~ 0
+    sex == "Male"                                    ~ 1,
+    sex == "Female"                                  ~ 0
   )) %>%
@@
   # ECOG
-  # mutate(ecog_at_ld = case_when(
-  #   ecog_at_ld == 0 | 
-  #     ecog_at_ld == 1                       ~ "0-1",
-  #   TRUE                                                          ~ ecog_at_ld
-  # )) %>%
+  mutate(ecog_at_ld = case_when(
+    ecog_at_ld == 0 |
+      ecog_at_ld == 1                                ~ "0-1",
+    ecog_at_ld %in% c(2:4)                           ~ "2-4"
+  )) %>%
 
@@
     !is.na(gain_amp1q21)                                           ~ "Yes"
+  )) %>% 
+  mutate(cytogenetics_incl_1q = case_when(
+    cytogenetics == "Yes" | 
+      gain_amp1q21 == "Yes"                                        ~ "Yes",
+    deletion_17p_prior_to_car_t_infusion_yes_no == "No" &
+      t_4_14_prior_to_car_t_infusion_yes_no == "No" &
+      t_14_16_prior_to_car_t_infusion_yes_no == "No" &
+      gain_amp1q21 == "No"                                         ~ "No",
+    TRUE                                                           ~ NA_character_
   )) %>% 
@@
   )) %>%
+  mutate(gcsf_duration = last_day_of_gcsf - first_day_of_gcsf) %>% 
   mutate(day_of_stem_cell_boost = interval(
@@
   )) %>% 
+  mutate(tpo_duration = last_day_of_tpo_agonist - first_day_of_tpo_agonist) %>% 
   mutate(first_day_of_ivig = interval(
@@
     )) %>% 
+  mutate(ivig_duration = last_day_of_ivig - first_day_of_ivig) %>% 
   mutate(need_for_ivig_yes_1_no_0 = case_when(
@@
     TRUE                                          ~ NA_character_
-  )))
+  ))) %>% 
+  mutate(overall_hlh = case_when(
+    hlh == "Yes" |
+    hlh_hlh_like_toxicities == "Yes"              ~ "Yes",
+    hlh == "No" &
+    hlh_hlh_like_toxicities == "No"               ~ "No"
+  ))
 
@@
 #     TRUE ~ NA_character_
-#   )) %>%
-#   mutate(HLH = case_when(
-#     notinfused=="YES" ~ NA_character_,
-#     notinfused=="NO" & `HLH/HLH-Like Toxicities?`=="Yes" ~ "Yes",
-#     TRUE ~ "No"
 #   )) %>%
@@
 
+```{r new cytopenia score}
+cilta <- cilta %>% 
+  mutate(plt_score = case_when(
+    plt_day_5_k_ul > 175                             ~ 0,
+    plt_day_5_k_ul >= 75                             ~ 1,
+    plt_day_5_k_ul < 175                             ~ 2
+  )) %>% 
+  mutate(anc_score = case_when(
+    (anc_day_5_k_ul * 1000) >= 1200                  ~ 0,
+    (anc_day_5_k_ul * 1000) < 1200                   ~ 1
+  )) %>% 
+  mutate(hb_score = case_when(
+    hb_day_5 >= 9                                    ~ 0,
+    hb_day_5 < 9                                     ~ 1
+  )) %>% 
+  mutate(crp_score = case_when(
+    # Jenn comment : CRP=3 should be 1 point
+    crp_pre_leukapheresis >= 3                       ~ 1,
+    crp_pre_leukapheresis < 3                        ~ 0
+  )) %>% 
+  mutate(ferritin_score = case_when(
+    ferritin_at_pre_leukapheresis < 650              ~ 0,
+    ferritin_at_pre_leukapheresis <= 2000            ~ 1,
+    ferritin_at_pre_leukapheresis > 2000             ~ 2
+  )) %>% 
+  # Need to make 2 different sum for when pre LD data is NA
+  mutate(ht_sum_score_with_missing = rowSums(
+    select(.,plt_score:ferritin_score), 
+                            na.rm = TRUE
+  )) %>% 
+  mutate(ht_sum_score = rowSums(
+    select(.,plt_score:ferritin_score), 
+                            na.rm = FALSE
+  )) %>% 
+  mutate(ht_score = case_when(
+    # If pre LD data is NA but score is ≥ 2 then we can still include as High
+    (is.na(crp_score) |
+       is.na(ferritin_score)) &
+      ht_sum_score_with_missing >= 2                 ~ "High",
+    ht_sum_score < 2                                 ~ "Low",
+    ht_sum_score >= 2                                ~ "High"
+  ), ht_score = factor(ht_score, levels = c("Low", "High"))) %>% 
+  mutate(early_icaht_cat = case_when(
+    # ANC ≤ 100 at three consecutive timepoints
+    (((anc_day_0_k_u_l * 1000) <= 100 &
+        (anc_day_7 * 1000) <= 100 &
+        (anc_day_14 * 1000) <= 100) |
+       ((anc_day_7 * 1000) <= 100 &
+          (anc_day_14 * 1000) <= 100 &
+          (anc_day_21 * 1000) <= 100) |
+       ((anc_day_14 * 1000) <= 100 &
+          (anc_day_21 * 1000) <= 100 &
+          (anc_day_30 * 1000) <= 100)) |
+      # ANC never above 500 in first 30 days
+      ((anc_day_0_k_u_l * 1000) <= 500 &
+         (anc_day_7 * 1000) <= 500 &
+         (anc_day_14 * 1000) <= 500 &
+         (anc_day_21 * 1000) <= 500 &
+         (anc_day_30 * 1000) <= 500)                 ~ "Grade 4",
+
+    # ANC ≤ 500 at three consecutive timepoints
+    ((anc_day_0_k_u_l * 1000) <= 500 &
+       (anc_day_7 * 1000) <= 500 &
+       (anc_day_14 * 1000) <= 500) |
+      ((anc_day_7 * 1000) <= 500 &
+         (anc_day_14 * 1000) <= 500 &
+         (anc_day_21 * 1000) <= 500) |
+      ((anc_day_14 * 1000) <= 500 &
+         (anc_day_21 * 1000) <= 500 &
+         (anc_day_30 * 1000) <= 500) |
+      # ANC ≤ 100 at two consecutive timepoints
+      ((anc_day_0_k_u_l * 1000) <= 100 &
+         (anc_day_7 * 1000) <= 100) |
+      ((anc_day_7 * 1000) <= 100 &
+         (anc_day_14 * 1000) <= 100) |
+      ((anc_day_14 * 1000) <= 100 &
+         (anc_day_21 * 1000) <= 100) |
+      ((anc_day_21 * 1000) <= 100 &
+         (anc_day_30 * 1000) <= 100)                 ~ "Grade 3",
+
+    # ANC ≤ 500 at two consecutive timepoints
+    ((anc_day_0_k_u_l * 1000) <= 500 &
+       (anc_day_7 * 1000) <= 500) |
+      ((anc_day_7 * 1000) <= 500 &
+         (anc_day_14 * 1000) <= 500) |
+      ((anc_day_14 * 1000) <= 500 &
+         (anc_day_21 * 1000) <= 500) |
+      ((anc_day_21 * 1000) <= 500 &
+         (anc_day_30 * 1000) <= 500)                 ~ "Grade 2",
+
+    # ANC ≤ 500 at one timepoint
+    (anc_day_0_k_u_l * 1000) <= 500 |
+      (anc_day_7 * 1000) <= 500 |
+      (anc_day_14 * 1000) <= 500 |
+      (anc_day_21 * 1000) <= 500 |
+      (anc_day_30 * 1000) <= 500                     ~ "Grade 1",
+    !is.na(anc_day_0_k_u_l) &
+      !is.na(anc_day_7) &
+      !is.na(anc_day_14) &
+      !is.na(anc_day_21) &
+      !is.na(anc_day_30)                             ~ "No early ICAHT"
+  )) %>% 
+  mutate(any_early_icaht = case_when(
+    early_icaht_cat == "No early ICAHT"              ~ "No",
+    TRUE                                             ~ "Yes"
+  )) %>% 
+  mutate(gr3_early_icaht = case_when(
+    early_icaht_cat == "No early ICAHT"              ~ "No",
+    early_icaht_cat == "Grade 3" |
+      early_icaht_cat == "Grade 4"                   ~ "Yes",
+    TRUE                                             ~ "No"
+  )) %>% 
+  mutate(late_icaht_cat = case_when(
+    (anc_day_90 * 1000) <= 100                       ~ "Grade 4",
+    (anc_day_90 * 1000) <= 500                       ~ "Grade 3",
+    (anc_day_90 * 1000) <= 1000                      ~ "Grade 2",
+    (anc_day_90 * 1000) <= 1500                      ~ "Grade 1",
+    !is.na(anc_day_90)                               ~ "No late ICAHT"
+  )) %>% 
+  mutate(any_late_icaht = case_when(
+    late_icaht_cat == "No late ICAHT"                ~ "No",
+    !is.na(late_icaht_cat)                           ~ "Yes",
+    TRUE                                             ~ NA_character_
+  )) %>% 
+  mutate(gr3_late_icaht = case_when(
+    late_icaht_cat == "Grade 3" |
+      late_icaht_cat == "Grade 4"                    ~ "Yes",
+    !is.na(late_icaht_cat)                           ~ "No",
+    TRUE                                             ~ NA_character_
+  ))# %>% 
+  # mutate_at(c("anc_day_0_k_u_l", "anc_day_7", 
+  #             "anc_day_14", "anc_day_21",
+  #             "anc_day_30", "anc_day_90"), ~ . * 1000)
+a <- cilta %>% select(pt_identifier, anc_day_0_k_u_l, anc_day_7, anc_day_14, anc_day_21, anc_day_30, early_icaht_cat, any_early_icaht, gr3_early_icaht, late_icaht_cat,  any_late_icaht, gr3_late_icaht, anc_day_90)
+a <- cilta %>% select(pt_identifier,  plt_score, plt_day_5_k_ul, anc_score, anc_day_5_k_ul, hb_score, hb_day_5, crp_score, crp_pre_leukapheresis, ferritin_score, ferritin_at_pre_leukapheresis, ht_score, ht_sum_score, ht_sum_score_with_missing)
+```
+
 ```{r Labeling}
@@
                          cytogenetics = "High risk cytogenetics (not include gain 1q)", 
+                         cytogenetics_incl_1q = "High risk cytogenetics (including gain 1q)",
                          deletion_17p_prior_to_car_t_infusion_yes_no = "Deletion 17p at Infusion", 
@@
                          hlh = "HLH", hlh_hlh_like_toxicities = "HLH/HLH-Like Toxicities?",
-
+                         overall_hlh = "Combined HLHs",
                          tbv = "TBV", whole_blood_processed_m_l = "Whole blood processed (mL)",
@@
                          best_ORRcollapsed = "Best ORR at ≤ 12 months",
+
+                         ht_score = "CAR-HEMATOTOX score",
+                         any_early_icaht = "Any Early ICAHT",
+                         gr3_early_icaht = "Grade3+ Early ICAHT",
+                         any_late_icaht = "Any Late ICAHT",
+                         gr3_late_icaht = "Grade3+ Late ICAHT",
+
                          did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no =
@@
          r_iss_at_car_t_infusion, 
-         cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no,
+         cytogenetics, cytogenetics_incl_1q,
+         deletion_17p_prior_to_car_t_infusion_yes_no,
          t_4_14_prior_to_car_t_infusion_yes_no,
@@
          immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no) %>% 
+         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
+         ht_score, early_icaht_cat, any_early_icaht,
+         gr3_early_icaht, 
+         late_icaht_cat, any_late_icaht,
+         gr3_late_icaht) %>% 
   tbl_summary(
@@
         extramedullary_disease_yes_no, high_marrow_burden_50_percent,
-        cytogenetics, deletion_17p_prior_to_car_t_infusion_yes_no,
+        cytogenetics, cytogenetics_incl_1q,
+        deletion_17p_prior_to_car_t_infusion_yes_no,
         t_4_14_prior_to_car_t_infusion_yes_no,
@@
         immuno, proteasome, dara, doubleref, tripleref, pentaref,
-        did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
+        did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
+        ht_score, early_icaht_cat, any_early_icaht,
+         gr3_early_icaht, 
+         late_icaht_cat, any_late_icaht,
+         gr3_late_icaht)
       ~"categorical"),
@@
          delayed_neuro_type,
-         hlh, hlh_hlh_like_toxicities) %>% 
+         hlh, hlh_hlh_like_toxicities,
+         overall_hlh) %>% 
   tbl_summary(type = list(
@@
       parkinsonian_neurotoxicity_yes_no,
-         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no) 
+      other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
+      hlh, hlh_hlh_like_toxicities,
+      overall_hlh) 
     ~ "categorical"),
@@
 
-## Table 3. Cytopenias following ide-cel
+## Table 3 A-B. Cytopenias following ide-cel
+Evaluable patients (who survived and did not progressed) are included for each time points.
 ```{r Table 3}
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (7 / 30.417)) %>% 
   select("Leukopenia" = Leukopenia_7d, 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_14days)) %>% ######################### Fix evaluable---------- here
-  filter(os_from_infusion_months > (14 / 30.417)) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (14 / 30.417)) %>% 
 select("Leukopenia" = Leukopenia_14d, 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_21days)) %>% 
-  filter(os_from_infusion_months > (21 / 30.417)) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (21 / 30.417)) %>% 
   select("Leukopenia" = Leukopenia_21d,
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% 
-  filter(os_from_infusion_months > (30 / 30.417)) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (30 / 30.417)) %>% 
   select("Leukopenia" = Leukopenia_30d, 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_90days)) %>% 
-  filter(os_from_infusion_months > 3) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > 3) %>% 
   select("Leukopenia" = Leukopenia_90d, 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_180days)) %>% 
-  filter(os_from_infusion_months > 6) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > 6) %>% 
   select("Leukopenia" = Leukopenia_180d, 
@@
 
+```{r}
+tbl1 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(any_early_icaht, 
+         gr3_early_icaht, 
+         any_late_icaht, 
+         gr3_late_icaht
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl2 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(any_early_icaht, 
+         gr3_early_icaht, 
+         any_late_icaht, 
+         gr3_late_icaht
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl3 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  select(any_early_icaht, 
+         gr3_early_icaht, 
+         any_late_icaht, 
+         gr3_late_icaht
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl4 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (7 / 30.417)) %>% 
+  select(any_early_icaht, 
+         gr3_early_icaht, 
+         any_late_icaht, 
+         gr3_late_icaht
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl5 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (14 / 30.417)) %>% 
+select(any_early_icaht, 
+         gr3_early_icaht, 
+         any_late_icaht, 
+         gr3_late_icaht
+) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl6 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (21 / 30.417)) %>% 
+  select(any_early_icaht, 
+         gr3_early_icaht, 
+         any_late_icaht, 
+         gr3_late_icaht
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl7 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (30 / 30.417)) %>% 
+  select(any_early_icaht, 
+         gr3_early_icaht, 
+         any_late_icaht, 
+         gr3_late_icaht
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl8 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > 3) %>% 
+  select(any_early_icaht, 
+         gr3_early_icaht, 
+         any_late_icaht, 
+         gr3_late_icaht
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl9 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > 6) %>% 
+  select(any_early_icaht, 
+         gr3_early_icaht, 
+         any_late_icaht, 
+         gr3_late_icaht
+  ) %>% 
+  tbl_summary(type = list(everything() ~ "dichotomous"),
+              digits = all_continuous() ~ 1,
+              missing = "no"
+  ) %>% 
+  bold_labels() %>% add_stat_label()
+
+tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8, tbl9), 
+          tab_spanner = c("Apheresis", "Day -5", "Day 0", 
+                          "Day 7", "Day 14", "Day 21",
+                          "Day 30", "Day 90", "Day 180"))
+```
+
 ## Table 4. Bone marrow biopsy findings
@@
          "% CD138 positive by IHC" = marrow_cd138_baseline_percent,
-         "is cellularity variable?"= contains("marrow_cellularity_baseline") & contains("is_variable_"),
+         # "is cellularity variable?"= contains("marrow_cellularity_baseline") & contains("is_variable_"),
          "Fibrosis grade" = marrow_fibrosis_baseline_0_1_2_3, 
@@
   statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-  digits = all_continuous() ~ 1,
-  missing = "no") %>% 
+  digits = all_continuous() ~ 1#,
+  # missing = "no"
+  ) %>% 
   bold_labels() %>% add_stat_label()
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(os_from_infusion_months > (30 / 30.417)) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > (30 / 30.417)) %>% 
   select("marrow cellularity" = marrow_cellularity_day_30_normo_hypo_hyper, 
@@
          "% CD138 positive by IHC" = marrow_percent_cd138_day_30, 
-         "is cellularity variable?"= contains("marrow_cellularity_day_30") & contains("is_variable_"),
+         # "is cellularity variable?"= contains("marrow_cellularity_day_30") & contains("is_variable_"),
          "Fibrosis grade" = marrow_fibrosis_day_30_0_1_2_3, 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(os_from_infusion_months > 3) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > 3) %>% 
   select("marrow cellularity" = marrow_cellularity_day_90_normo_hypo_hyper, 
@@
          "% CD138 positive by IHC" = marrow_percent_cd138_day_90, 
-         "is cellularity variable?"= contains("marrow_cellularity_day_90") & contains("is_variable_"),
+         # "is cellularity variable?"= contains("marrow_cellularity_day_90") & contains("is_variable_"),
          "Fibrosis grade" = marrow_fibrosis_day_90_0_1_2_3, 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(os_from_infusion_months > 6) %>% 
+  filter(pfs_event == 0 | pfs_from_infusion_months > 6) %>% 
   select("marrow cellularity" = marrow_cellularity_day_180_normo_hypo_hyper, 
@@
          "% CD138 positive by IHC" = marrow_percent_cd138_day_180, 
-         "is cellularity variable?"= contains("marrow_cellularity_day_180") & contains("is_variable_"),
+         # "is cellularity variable?"= contains("marrow_cellularity_day_180") & contains("is_variable_"),
          "Fibrosis grade" = marrow_fibrosis_day_180_0_1_2_3, 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(first_day_of_gcsf, last_day_of_gcsf) %>%
+  select(first_day_of_gcsf, last_day_of_gcsf,
+         gcsf_duration) %>%
   tbl_summary(type = list(
@@
   distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(first_day_of_tpo_agonist, last_day_of_tpo_agonist) %>%
+  select(first_day_of_tpo_agonist, last_day_of_tpo_agonist,
+         tpo_duration) %>%
   tbl_summary(type = list(
@@
   distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(first_day_of_ivig, last_day_of_ivig) %>%
+  select(first_day_of_ivig, last_day_of_ivig,
+         ivig_duration) %>%
   tbl_summary(type = list(
@@
 
-## Table S4. Patient characteristics by grade 3+ cytopenia at Day 30
+## Table S4a. Patient characteristics by grade 3+ cytopenia at Day 30
 ```{r Patient characteristics by grade 3+ cytopenia at Day 30}
@@
          high_marrow_burden_50_percent, ecog_at_ld, 
-         r_iss_at_car_t_infusion, cytogenetics, 
+         r_iss_at_car_t_infusion, 
+         cytogenetics, cytogenetics_incl_1q,
          bridging_therapy_yes_no,
@@
          `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
+         ht_score,
          gr3_cytopenia_30d) %>% 
@@
                   cytopenia_apheresis,`cytopenia_-5d`,
-                  cytogenetics,
+                  cytogenetics, cytogenetics_incl_1q,
                   bridging_therapy_yes_no,
@@
                   `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
+                  ht_score,
                   did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
@@
 
-## Table S5. Patient characteristics by grade 3+ cytopenia at Day 90
+## Table S4b. Patient characteristics by ANY early ICAHT
+```{r Patient characteristics by grade 3+ early ICAHT}
+cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(bm_plasma_cell_percent_at_pre_ld,
+         number_of_prior_lines_of_therapy,
+         number_prior_lines_therapy,
+         # `Days from last bridging to CAR-T infusion`,         ################# Not in data?
+         lenalidomide_exposed_vs_refractory_vs_not_exposed,
+         bortezomib_exposed_vs_refractory_vs_not_exposed,
+         carfilzomib_exposed_vs_refractory_vs_not_exposed,
+         pomalidomide_exposed_vs_refractory_vs_not_exposed,
+         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         "Marrow Cellularity (%) at Day30" = marrow_percent_cellularity_day_30,
+         os_from_infusion_months, age, agecat, male_sex, sex,
+         extramedullary_disease_yes_no, 
+         high_marrow_burden_50_percent, ecog_at_ld, 
+         r_iss_at_car_t_infusion, 
+         cytogenetics, cytogenetics_incl_1q,
+         bridging_therapy_yes_no,
+         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
+         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
+         Prior_bcma_therapy,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
+         cytopenia_apheresis, Neutropenia_apheresis,
+         Anemia_apheresis,Thrombocytopenia_apheresis,
+         `cytopenia_-5d`, `Neutropenia_-5d`,
+         `Anemia_-5d`, `Thrombocytopenia_-5d`,
+         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
+         ht_score,
+         any_early_icaht) %>% 
+  tbl_summary(by = any_early_icaht,
+              type = list(
+                c(extramedullary_disease_yes_no,
+                  bm_plasma_cell_percent_at_pre_ld,
+                  cytopenia_apheresis,`cytopenia_-5d`,
+                  cytogenetics, cytogenetics_incl_1q,
+                  bridging_therapy_yes_no,
+                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+                  prior_auto_sct_yes_no,
+                  Prior_bcma_therapy,
+                  immuno, proteasome, dara,
+                  doubleref, tripleref, pentaref,
+                  cytopenia_apheresis, Neutropenia_apheresis,
+                  Anemia_apheresis,Thrombocytopenia_apheresis,
+                  `cytopenia_-5d`, `Neutropenia_-5d`,
+                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
+                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
+                  ht_score,
+                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
+                ~"categorical",
+                c(bm_plasma_cell_percent_at_pre_ld,
+                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
+                ~ "continuous"),
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>% add_p() %>% 
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Early ICAHT**")
+```
+
+## Table S5a. Patient characteristics by grade 3+ cytopenia at Day 90
 ```{r Patient characteristics by grade 3+ cytopenia at Day 90}
@@
          extramedullary_disease_yes_no, 
-         high_marrow_burden_50_percent, ecog_at_ld, r_iss_at_car_t_infusion, cytogenetics, 
+         high_marrow_burden_50_percent, ecog_at_ld, r_iss_at_car_t_infusion, 
+         cytogenetics, cytogenetics_incl_1q,
          bridging_therapy_yes_no,
@@
          `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
+         ht_score,
          gr3_cytopenia_90d) %>% 
@@
 
-## Table S6. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
+## Table S5b. Patient characteristics by ANY late ICAHT
+```{r Patient characteristics by grade 3+ late ICAHT}
+cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_90days)) %>%  ######################### Fix evaluable----------
+  select(bm_plasma_cell_percent_at_pre_ld,
+         number_of_prior_lines_of_therapy,
+         number_prior_lines_therapy,
+         # `Days from last bridging to CAR-T infusion`,
+         lenalidomide_exposed_vs_refractory_vs_not_exposed,
+         bortezomib_exposed_vs_refractory_vs_not_exposed,
+         carfilzomib_exposed_vs_refractory_vs_not_exposed,
+         pomalidomide_exposed_vs_refractory_vs_not_exposed,
+         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
+         "Marrow Cellularity (%) at Day90" = marrow_percent_cellularity_day_90,
+         os_from_infusion_months,
+         age, agecat, male_sex, sex,
+         extramedullary_disease_yes_no, 
+         high_marrow_burden_50_percent, ecog_at_ld, r_iss_at_car_t_infusion, 
+         cytogenetics, cytogenetics_incl_1q,
+         bridging_therapy_yes_no,
+         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
+         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
+         Prior_bcma_therapy,
+         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
+         cytopenia_apheresis, Neutropenia_apheresis,
+         Anemia_apheresis,Thrombocytopenia_apheresis,
+         `cytopenia_-5d`, `Neutropenia_-5d`,
+         `Anemia_-5d`, `Thrombocytopenia_-5d`,
+         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
+         ht_score,
+         any_late_icaht) %>% 
+  tbl_summary(by = any_late_icaht,
+              type = list(
+                c(extramedullary_disease_yes_no,
+                  bm_plasma_cell_percent_at_pre_ld,
+                  cytopenia_apheresis,`cytopenia_-5d`,
+                  cytogenetics, cytogenetics_incl_1q,
+                  bridging_therapy_yes_no,
+                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
+                  prior_auto_sct_yes_no,
+                  immuno, proteasome, dara,
+                  doubleref, tripleref, pentaref,
+                  cytopenia_apheresis, Neutropenia_apheresis,
+                  Anemia_apheresis,Thrombocytopenia_apheresis,
+                  `cytopenia_-5d`, `Neutropenia_-5d`,
+                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
+                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
+                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
+                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
+                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
+                  ht_score,
+                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
+                ~ "categorical",
+                c(bm_plasma_cell_percent_at_pre_ld,
+                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day90`)
+                ~ "continuous"),
+              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
+              digits = all_continuous() ~ 1
+  ) %>% 
+  bold_labels() %>% add_stat_label() %>%  add_p() %>% 
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Late ICAHT**")
+```
+
+## Table S6a. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
 ```{r CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30}
@@
          hlh, hlh_hlh_like_toxicities,
+         overall_hlh,
          gr3_cytopenia_30d) %>% 
@@
                   other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
-                  parkinsonian_neurotoxicity_yes_no) ~ "categorical"),
+                  parkinsonian_neurotoxicity_yes_no,
+                  hlh, hlh_hlh_like_toxicities,
+                  overall_hlh) ~ "categorical"),
               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
@@
 #   bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl_stack(list(tbl1, tbl2, tbl3, tbl5, tbl7))
+```
+
+## Table S6b. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by ANY early ICAHT
+```{r CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ early ICAHT}
+tbl1 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(cell_dose_million_cells,
+         CRS_gradecat,
+         day_of_onset_crs_relative_to_infusion,
+         day_of_max_crs_relative_to_infusion,
+         duration_of_crs_days, 
+         ICANS_gradecat,
+         day_of_onset_icans_relative_to_infusion,
+         day_of_max_icans_relative_to_infusion,
+         duration_of_icans_days, 
+         delayed_neuro,
+         parkinsonian_neurotoxicity_yes_no,
+         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
+         delayed_neuro_type,
+         hlh, hlh_hlh_like_toxicities,
+         overall_hlh,
+         any_early_icaht) %>% 
+  tbl_summary(by = any_early_icaht,
+              type = list(
+                c(day_of_onset_crs_relative_to_infusion,
+                  day_of_max_crs_relative_to_infusion,
+                  duration_of_crs_days,
+                  day_of_onset_icans_relative_to_infusion,
+                  day_of_max_icans_relative_to_infusion,
+                  duration_of_icans_days) ~ "continuous",
+                c(delayed_neuro,
+                  other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
+                  parkinsonian_neurotoxicity_yes_no,
+                  hlh, hlh_hlh_like_toxicities,
+                  overall_hlh) ~ "categorical"),
+              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p() %>% 
+  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Early ICAHT**")
+
+tbl2 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(steroid_use_yes_no, tocilizumab_yes_no, 
+         anakinra_yes_no, any_early_icaht) %>% 
+  tbl_summary(by = any_early_icaht,
+              type = list(
+    c(steroid_use_yes_no, tocilizumab_yes_no, 
+      anakinra_yes_no) ~ "categorical"),
+    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
+    digits = all_continuous() ~ 1) %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl3 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(#day_30_mrd_by_clono_seq_positive_vs_negative,
+         ORR_30days, CRorbetter_30days,
+         # day30_response_v2, 
+         any_early_icaht) %>% 
+  tbl_summary(by = any_early_icaht,
+    #           type = list(
+    # c(day_30_mrd_by_clono_seq_positive_vs_negative) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl5 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(#MRD_mon3,
+         ORR_mon3, CRorbetter_mon3,
+         # mon3_response_v2, 
+         any_early_icaht) %>% 
+  tbl_summary(by = any_early_icaht,
+    #           type = list(
+    # c(MRD_mon3) ~ "categorical"),
+    digits = all_continuous() ~ 1,
+    missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
+
+tbl7 <- cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
+  select(best_response, best_ORRcollapsed,
+         any_early_icaht) %>% 
+  tbl_summary(by = any_early_icaht,
+              #type = list(c(MRD_mon3) ~ "categorical"),
+              label = list(best_response ~ "best response in the first 90 days"),
+              digits = all_continuous() ~ 1,
+              missing = "no") %>% 
+  bold_labels() %>% add_stat_label() %>% add_p()
 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(number_prior_lines_therapy,
+  select(os_from_infusion_months, age, agecat, male_sex, sex,
+         extramedullary_disease_yes_no, 
+         high_marrow_burden_50_percent, ecog_at_ld, 
+         r_iss_at_car_t_infusion, 
+         cytogenetics, cytogenetics_incl_1q,
+         deletion_17p_prior_to_car_t_infusion_yes_no,
+         t_4_14_prior_to_car_t_infusion_yes_no,
+         t_14_16_prior_to_car_t_infusion_yes_no, gain_amp1q21,
+         bridging_therapy_yes_no,
+         number_prior_lines_therapy,
          number_of_prior_lines_of_therapy,
-         prior_auto_sct_yes_no,
-         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
+         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
          Prior_bcma_therapy,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref,
+         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
          # `Received alkylating therapy with bridging (Yes=1, No=0)`,
@@
          hlh, hlh_hlh_like_toxicities,
+         overall_hlh,
          steroid_use_yes_no, 
@@
   distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(number_prior_lines_therapy,
+  select(os_from_infusion_months, age, agecat, male_sex, sex,
+         extramedullary_disease_yes_no, 
+         high_marrow_burden_50_percent, ecog_at_ld, 
+         r_iss_at_car_t_infusion, 
+         cytogenetics, cytogenetics_incl_1q,
+         deletion_17p_prior_to_car_t_infusion_yes_no,
+         t_4_14_prior_to_car_t_infusion_yes_no,
+         t_14_16_prior_to_car_t_infusion_yes_no, gain_amp1q21,
+         bridging_therapy_yes_no,
+         number_prior_lines_therapy,
          number_of_prior_lines_of_therapy,
-         prior_auto_sct_yes_no,
+         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
          Prior_bcma_therapy,
+         immuno, proteasome, dara, doubleref, tripleref, pentaref,
+         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
          # `Received alkylating therapy with bridging (Yes=1, No=0)`,
@@
          cd4_day_90, cd8_day_90,
-         cd19_day_90,
+         cd19_day_90, ht_score,
          any_infection) %>% 
   tbl_summary(by = any_infection,
-              type = list(everything() ~ "continuous"),
+              type = list(-ht_score ~ "continuous"),
               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
@@
          cd4_day_90, cd8_day_90,
-         cd19_day_90,
+         cd19_day_90, ht_score,
          any_sevinfection) %>% 
   tbl_summary(by = any_sevinfection,
-              type = list(everything() ~ "continuous"),
+              type = list(-ht_score ~ "continuous"),
               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
@@
   select(phrase, `cause of death` = cause_of_death_myeloma_toxicitiy_unrelated,
-         `CRS grade` = max_crs_grade_0_5, `delayed neurotoxicity` = delayed_neuro_type)
+         `CRS grade` = max_crs_grade_0_5, max_icans, delayed_neuro, `delayed neurotoxicity` = delayed_neuro_type, parkinsonian_neurotoxicity_yes_no, what_non_parkinsonian_neurotoxicity, infection_type_bacterial_viral_fungal_parasitic,  `infection details` = infection_type_details)
+
+a <- fig_dat %>% 
+  mutate(pfs_from_infusion_days = 
+           interval(
+             start = date_of_car_t_infusion, 
+             end = pfs_date)/
+           duration(n=1, units = "days")) %>% 
+  filter(os_event == 1 | pfs_event == 1) %>% 
+  mutate(event_at = case_when(
+    !is.na(date_of_pd) & pfs_from_infusion_months < 1        ~ "had pd",
+    !is.na(date_of_pd) & pfs_from_infusion_months < 3        ~ "had pd",
+    !is.na(date_of_pd) & pfs_from_infusion_months < 6        ~ "had pd",
+    !is.na(date_of_pd) & pfs_from_infusion_months < 12       ~ "had pd",
+    os_event == 1 & pfs_from_infusion_months < 1        ~ "died",
+    os_event == 1 & pfs_from_infusion_months < 3        ~ "died",
+    os_event == 1 & pfs_from_infusion_months < 6        ~ "died",
+    os_event == 1 & pfs_from_infusion_months < 12       ~ "died",
+  )) %>% 
+  filter(event_at == "died") %>% 
+  arrange(pfs_from_infusion_days) %>% 
+  select(pt_identifier, event_at, pfs_from_infusion_days, `cause of death` = cause_of_death_myeloma_toxicitiy_unrelated,
+         `CRS grade` = max_crs_grade_0_5, max_icans, delayed_neuro, `delayed neurotoxicity` = delayed_neuro_type, parkinsonian_neurotoxicity_yes_no, what_non_parkinsonian_neurotoxicity, infection_type_bacterial_viral_fungal_parasitic,  `infection details` = infection_type_details)
+write_csv(a, paste0(here::here(), "/cilta_cel/cause of death cilta-cel data.csv"))
 ```
@@
   scale_color_manual(values = c("black", "red"))+
-  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
-  coord_flip()
+  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))#+
+  # coord_flip()
 
@@
   scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
-  coord_flip()
+  # coord_flip()
+  theme(axis.text.x = element_text(angle = 45, 
+                                   hjust = 1#,
+                                   # vjust = 0.5
+                                   ))
 ```
@@
 ## Table S7 and Figure S2. MVA and forest plot
-Limit to evaluable patients at day 90
+Limit to evaluable patients at day 90 (For Grade 3+ Cytopenia at days 90 MVA)
 ```{r MVA and forest plot}
@@
   )) %>% 
+  mutate(any_late_icaht = case_when(
+    any_late_icaht == "No"    ~ 0,
+    any_late_icaht == "Yes"   ~ 1
+  )) %>% 
   mutate(CRS_grade2 = case_when(
@@
 
+glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + ht_score + 
+      number_of_prior_lines_of_therapy,
+    data = mva_dat,
+    family = "binomial") %>%
+  tbl_regression(exponentiate = TRUE, 
+                 intercept = TRUE) %>%
+  add_nevent(location = "level") %>% add_n(location = "level") %>%
+  modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
+  bold_p(t = .05)
+glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + ht_score,
+    data = mva_dat,
+    family = "binomial") %>%
+  tbl_regression(exponentiate = TRUE, 
+                 intercept = TRUE) %>%
+  add_nevent(location = "level") %>% add_n(location = "level") %>%
+  modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
+  bold_p(t = .05)
+
+```
+
+```{r}
+mva_dat_icaht <- fig_dat %>% 
+  mutate(any_late_icaht = case_when(
+    any_late_icaht == "No"    ~ 0,
+    any_late_icaht == "Yes"   ~ 1
+  ))
+
+glm(any_late_icaht ~ high_marrow_burden_50_percent + ht_score + 
+      number_of_prior_lines_of_therapy,
+    data = mva_dat_icaht,
+    family = "binomial") %>%
+  tbl_regression(exponentiate = TRUE, 
+                 intercept = TRUE) %>%
+  add_nevent(location = "level") %>% add_n(location = "level") %>%
+  modify_spanning_header(everything() ~ "**Any late ICAHT**") %>%
+  bold_p(t = .05)
+glm(any_late_icaht ~ high_marrow_burden_50_percent + ht_score,
+    data = mva_dat_icaht,
+    family = "binomial") %>%
+  tbl_regression(exponentiate = TRUE, 
+                 intercept = TRUE) %>%
+  add_nevent(location = "level") %>% add_n(location = "level") %>%
+  modify_spanning_header(everything() ~ "**Any late ICAHT**") %>%
+  bold_p(t = .05)
+
+```
+
+older MVA
+```{r}
 # glm(gr3_cytopenia_30d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + CRS_grade2 + steroid_use_yes_no + number_of_prior_lines_of_therapy,
@@
 
-ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ gr3_cytopenia_90d, 
-                   data=surv_dat),
-           title = "OS Analysis",
-           font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
-           size = 1.5,
-
-           xlab = "Time in months",
-           legend = "top",
-           legend.title = "",
-           pval = TRUE,
-           conf.int = FALSE,
-           # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
-
-coxph(Surv(time = surv_dat$os_from_infusion_months, 
-                   event = surv_dat$os_event) ~ gr3_cytopenia_90d, 
-              data = surv_dat)  %>% 
-  tbl_regression(exponentiate = TRUE) %>% 
-  bold_p(t = .05) %>% 
-  add_nevent(location = "level") %>% add_n(location = "level")
+# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ gr3_cytopenia_90d, 
+#                    data=surv_dat),
+#            title = "OS Analysis",
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+# 
+#            xlab = "Time in months",
+#            legend = "top",
+#            legend.title = "",
+#            pval = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# ) + guides(colour = guide_legend(ncol = 1))
+# 
+# coxph(Surv(time = surv_dat$os_from_infusion_months, 
+#                    event = surv_dat$os_event) ~ gr3_cytopenia_90d, 
+#               data = surv_dat)  %>% 
+#   tbl_regression(exponentiate = TRUE) %>% 
+#   bold_p(t = .05) %>% 
+#   add_nevent(location = "level") %>% add_n(location = "level")
 ```
@@
 
-ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ ORR_as_best_response, 
+# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ ORR_as_best_response, 
+#                    data=surv_dat),
+#            title = "OS Analysis",
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+# 
+#            xlab = "Time in months",
+#            legend = "top",
+#            legend.title = "",
+#            pval = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# ) + guides(colour = guide_legend(ncol = 1))
+# 
+# coxph(Surv(time = surv_dat$os_from_infusion_months, 
+#                    event = surv_dat$os_event) ~ ORR_as_best_response, 
+#               data = surv_dat)  %>% 
+#   tbl_regression(exponentiate = TRUE) %>% 
+#   bold_p(t = .05) %>% 
+#   add_nevent(location = "level") %>% add_n(location = "level")
+```
+
+## Survival analysis - KM by gr3 cytopenia at day 30
+```{r Survival analysis - KM by gr3_cytopenia_30d}
+ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ gr3_cytopenia_30d, 
                    data=surv_dat),
-           title = "OS Analysis",
+           title = "PFS Analysis",
            font.main = c(20, "bold", "black"),
@@
 
-coxph(Surv(time = surv_dat$os_from_infusion_months, 
-                   event = surv_dat$os_event) ~ ORR_as_best_response, 
+coxph(Surv(time = surv_dat$pfs_from_infusion_months, 
+                   event = surv_dat$pfs_event) ~ gr3_cytopenia_30d, 
               data = surv_dat)  %>% 
@@
   add_nevent(location = "level") %>% add_n(location = "level")
-```
-
-## UVA best ORR by gr3 cytopenia at day 90
-I was unable to perform the analyses investigating severe cytopenias at D90 and best response because everyone with severe cytopenias had an event.
-```{r glm}
-mva_dat <- surv_dat %>% 
-  # filter(os_from_infusion_months > 3) %>% 
-  mutate(ORR_as_best_response = case_when(
-    ORR_as_best_response == "ORR"         ~ 1,
-    ORR_as_best_response == "never ORR"   ~ 0
-  ))
-
-# glm(ORR_as_best_response ~ gr3_cytopenia_90d,
-#     data = mva_dat,
-#     family = "binomial") %>%
-#   tbl_regression(exponentiate = TRUE, 
-#                  intercept = TRUE) %>%
-#   add_nevent(location = "level") %>% add_n(location = "level") %>%
-#   modify_spanning_header(everything() ~ "**ORR_as_best_response**") %>%
-#   bold_p(t = .05) 
-```
+
+# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ gr3_cytopenia_30d, 
+#                    data=surv_dat),
+#            title = "OS Analysis",
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+# 
+#            xlab = "Time in months",
+#            legend = "top",
+#            legend.title = "",
+#            pval = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# ) + guides(colour = guide_legend(ncol = 1))
+# 
+# coxph(Surv(time = surv_dat$os_from_infusion_months, 
+#                    event = surv_dat$os_event) ~ gr3_cytopenia_30d, 
+#               data = surv_dat)  %>% 
+#   tbl_regression(exponentiate = TRUE) %>% 
+#   bold_p(t = .05) %>% 
+#   add_nevent(location = "level") %>% add_n(location = "level")
+```
+
+## Survival analysis - KM by CAR-HEMATOTOX score
+```{r Survival analysis - KM by ht_score}
+ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ ht_score, 
+                   data=surv_dat),
+           title = "PFS Analysis",
+           font.main = c(20, "bold", "black"),
+           font.x = c(18, "bold", "black"),
+           font.y = c(18, "bold", "black"),
+           font.legend = c(16, "black"),
+           font.tickslab = c(16, "bold", "black"),
+           size = 1.5,
+
+           xlab = "Time in months",
+           legend = "top",
+           legend.title = "",
+           pval = TRUE,
+           conf.int = FALSE,
+           # Censor
+           censor = TRUE
+) + guides(colour = guide_legend(ncol = 1))
+
+coxph(Surv(time = surv_dat$pfs_from_infusion_months, 
+                   event = surv_dat$pfs_event) ~ ht_score, 
+              data = surv_dat)  %>% 
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% 
+  add_nevent(location = "level") %>% add_n(location = "level")
+
+# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ ht_score, 
+#                    data=surv_dat),
+#            title = "OS Analysis",
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+# 
+#            xlab = "Time in months",
+#            legend = "top",
+#            legend.title = "",
+#            pval = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# ) + guides(colour = guide_legend(ncol = 1))
+# 
+# coxph(Surv(time = surv_dat$os_from_infusion_months, 
+#                    event = surv_dat$os_event) ~ ht_score, 
+#               data = surv_dat)  %>% 
+#   tbl_regression(exponentiate = TRUE) %>% 
+#   bold_p(t = .05) %>% 
+#   add_nevent(location = "level") %>% add_n(location = "level")
+```
+
+## Survival analysis - KM by ANY early ICAHT
+```{r Survival analysis - KM by gr3_early_icaht}
+ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ any_early_icaht,
+                   data=surv_dat),
+           title = "PFS Analysis",
+           font.main = c(20, "bold", "black"),
+           font.x = c(18, "bold", "black"),
+           font.y = c(18, "bold", "black"),
+           font.legend = c(16, "black"),
+           font.tickslab = c(16, "bold", "black"),
+           size = 1.5,
+
+           xlab = "Time in months",
+           legend = "top",
+           legend.title = "",
+           pval = TRUE,
+           conf.int = FALSE,
+           # Censor
+           censor = TRUE
+) + guides(colour = guide_legend(ncol = 1))
+
+coxph(Surv(time = surv_dat$pfs_from_infusion_months,
+                   event = surv_dat$pfs_event) ~ any_early_icaht,
+              data = surv_dat)  %>%
+  tbl_regression(exponentiate = TRUE) %>%
+  bold_p(t = .05) %>%
+  add_nevent(location = "level") %>% add_n(location = "level")
+
+# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ gr3_early_icaht,
+#                    data=surv_dat),
+#            title = "OS Analysis",
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+#
+#            xlab = "Time in months",
+#            legend = "top",
+#            legend.title = "",
+#            pval = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# ) + guides(colour = guide_legend(ncol = 1))
+#
+# coxph(Surv(time = surv_dat$os_from_infusion_months,
+#                    event = surv_dat$os_event) ~ gr3_early_icaht,
+#               data = surv_dat)  %>%
+#   tbl_regression(exponentiate = TRUE) %>%
+#   bold_p(t = .05) %>%
+#   add_nevent(location = "level") %>% add_n(location = "level")
+```
+
+## Survival analysis - KM by ANY late ICAHT
+```{r Survival analysis - KM by gr3_late_icaht}
+ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ any_late_icaht,
+                   data=surv_dat),
+           title = "PFS Analysis",
+           font.main = c(20, "bold", "black"),
+           font.x = c(18, "bold", "black"),
+           font.y = c(18, "bold", "black"),
+           font.legend = c(16, "black"),
+           font.tickslab = c(16, "bold", "black"),
+           size = 1.5,
+
+           xlab = "Time in months",
+           legend = "top",
+           legend.title = "",
+           pval = TRUE,
+           conf.int = FALSE,
+           # Censor
+           censor = TRUE
+) + guides(colour = guide_legend(ncol = 1))
+
+coxph(Surv(time = surv_dat$pfs_from_infusion_months,
+                   event = surv_dat$pfs_event) ~ any_late_icaht,
+              data = surv_dat)  %>%
+  tbl_regression(exponentiate = TRUE) %>%
+  bold_p(t = .05) %>%
+  add_nevent(location = "level") %>% add_n(location = "level")
+
+# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ gr3_late_icaht,
+#                    data=surv_dat),
+#            title = "OS Analysis",
+#            font.main = c(20, "bold", "black"),
+#            font.x = c(18, "bold", "black"),
+#            font.y = c(18, "bold", "black"),
+#            font.legend = c(16, "black"),
+#            font.tickslab = c(16, "bold", "black"),
+#            size = 1.5,
+#
+#            xlab = "Time in months",
+#            legend = "top",
+#            legend.title = "",
+#            pval = TRUE,
+#            conf.int = FALSE,
+#            # Censor
+#            censor = TRUE
+# ) + guides(colour = guide_legend(ncol = 1))
+#
+# coxph(Surv(time = surv_dat$os_from_infusion_months,
+#                    event = surv_dat$os_event) ~ gr3_late_icaht,
+#               data = surv_dat)  %>%
+#   tbl_regression(exponentiate = TRUE) %>%
+#   bold_p(t = .05) %>%
+#   add_nevent(location = "level") %>% add_n(location = "level")
+```
+
+<!-- ## UVA best ORR by gr3 cytopenia at day 90 -->
+<!-- I was unable to perform the analyses investigating severe cytopenias at D90 and best response because everyone with severe cytopenias had an event. -->
+<!-- ```{r glm} -->
+<!-- mva_dat <- surv_dat %>%  -->
+<!--   # filter(os_from_infusion_months > 3) %>%  -->
+<!--   mutate(ORR_as_best_response = case_when( -->
+<!--     ORR_as_best_response == "ORR"         ~ 1, -->
+<!--     ORR_as_best_response == "never ORR"   ~ 0 -->
+<!--   ))  -->
+
+<!-- # glm(ORR_as_best_response ~ gr3_cytopenia_90d, -->
+<!-- #     data = mva_dat, -->
+<!-- #     family = "binomial") %>% -->
+<!-- #   tbl_regression(exponentiate = TRUE,  -->
+<!-- #                  intercept = TRUE) %>% -->
+<!-- #   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
+<!-- #   modify_spanning_header(everything() ~ "**ORR_as_best_response**") %>% -->
+<!-- #   bold_p(t = .05)  -->
+<!-- ``` -->

### 2024-04-03 cilta_cel/Manuscript analyses.Rmd
Update data for analysis

@@
 output:
+  word_document:
+    toc: true
   html_document:
@@
 Characteristics <-
-  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
+  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                     sheet = "CHARACTERISTICS AND OUTCOMES ", skip = 1)
 Counts <-
-  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
+  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                     sheet = "COUNTS")
 Infections <-
-  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
+  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                     sheet = "INFECTIONS")
 Support <-
-  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
+  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                     sheet = "SUPPORT")
 Pneumo_titers <-
-  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
+  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                     sheet = "BACTERIAL AND VIRAL TITERS")
 Apheresis <- 
-  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
+  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                     sheet = "APHERESIS")

### 2024-04-20 cilta_cel/Manuscript analyses.Rmd
Add variable and update figures

@@
     TRUE                                    ~ .
-  )))
+  ))) %>% 
+  mutate(circulating_plasma_cell = case_when(
+    plasmacytes_day_5_percent == 0          ~ "0",
+    plasmacytes_day_5_percent > 0           ~ "> 0",
+  ), circulating_plasma_cell = factor(circulating_plasma_cell, 
+                                      levels = c("0", "> 0")))
 
@@
                          extramedullary_disease_yes_no = "Extramedullary disease",
-                         bm_plasma_cell_percent_at_pre_ld = "Circulating Plasma Cells?",
+                         circulating_plasma_cell = "UPDATED Circulating Plasma Cells",
                          high_marrow_burden_50_percent = "High marrow burden (≥50%)",
@@
 
-tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() #%>%
+tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) #%>% as_gt() #%>%
   # gt::tab_source_note(gt::md("**At 30days: <br>
@@
                           "Day 7", "Day 14", "Day 21",
-                          "Day 30", "Day 90", "Day 180")) %>% as_gt() #%>%
+                          "Day 30", "Day 90", "Day 180")) # %>% as_gt() #%>%
 # gt::tab_source_note(gt::md("**Not evaluable patients are removed from the denominator <br>
@@
 ```
+<br>
 
@@
   # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(bm_plasma_cell_percent_at_pre_ld,
+  select(circulating_plasma_cell,
          number_of_prior_lines_of_therapy,
@@
                 c(extramedullary_disease_yes_no,
-                  bm_plasma_cell_percent_at_pre_ld,
+                  circulating_plasma_cell,
                   cytopenia_apheresis,`cytopenia_-5d`,
@@
                 ~"categorical",
-                c(bm_plasma_cell_percent_at_pre_ld,
-                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
+                c(number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
                 ~ "continuous"),
@@
                 c(extramedullary_disease_yes_no,
-                  bm_plasma_cell_percent_at_pre_ld,
                   cytopenia_apheresis,`cytopenia_-5d`,
@@
   # filter(is.na(Not_evaluable_at_90days)) %>%  ######################### Fix evaluable----------
-  select(bm_plasma_cell_percent_at_pre_ld,
+  select(circulating_plasma_cell,
          number_of_prior_lines_of_therapy,
@@
                 ~ "categorical",
-                c(bm_plasma_cell_percent_at_pre_ld,
-                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day90`)
+                c(number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day90`)
                 ~ "continuous"),
@@
 
-## Figure S1. Inflammatory markers after ide-cel
+## Figure S1. Inflammatory markers after cilta-cel
 
@@
   scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 5 
+  stat_compare_means(label.x = 1.2 
                      # aes(label = paste0("p = ", ..p.format..))
@@
 Ferritin <- fig_dat %>% 
-  select(pt_identifier, starts_with("ferritin_")) %>% 
+  select(pt_identifier, starts_with("ferritin_"), -ferritin_score) %>% 
   pivot_longer(cols = -c(pt_identifier)) %>% 
@@
 CRP <- fig_dat %>% 
-  select(pt_identifier, starts_with("crp_")) %>% 
+  select(pt_identifier, starts_with("crp_"), -crp_score) %>% 
   pivot_longer(cols = -c(pt_identifier)) %>% 
@@
   scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 5 
+  stat_compare_means(label.x = 1.2
                      # aes(label = paste0("p = ", ..p.format..))
@@
 plot_annotation(tag_levels = "A")
+
+# ggsave("Figure S1 Inflammatory markers after cilta-cel.pdf",
+#        width = 6,
+#        height = 10)
 ```
@@
     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  ) #+ ylim(0, 6)
+    labels = c("Apheresis","-5 ", "0", "7", "14", "21", "30", "90", "180")
+  ) +
+  theme(text = element_text(size = 8))
 
@@
     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  ) # +ylim(7.5, 12)
+    labels = c("Apheresis","-5 ", "0", "7", "14", "21", "30", "90", "180")
+  ) +
+  theme(text = element_text(size = 8))
 
@@
     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  ) # + ylim(0, 1.1)
+    labels = c("Apheresis","-5 ", "0", "7", "14", "21", "30", "90", "180")
+  ) +
+  theme(text = element_text(size = 8))
 
@@
     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  ) # + ylim(20, 170)
+    labels = c("Apheresis","-5 ", "0", "7", "14", "21", "30", "90", "180")
+  ) +
+  theme(text = element_text(size = 8))
 
@@
     breaks = c(-28, -5, 30, 90, 180),
-    labels = c("Apheresis", "-5", "30", "90", "180"))# + 
-  # ylim(0, 2000)
+    labels = c("Apheresis", "-5 ", "30", "90", "180")) +
+  theme(text = element_text(size = 8))
 
@@
     labels = c("Apheresis", "30", "90", "180")
-  )
+  ) +
+  theme(text = element_text(size = 8))
 
@@
   plot_annotation(tag_levels = "A")
+
+# ggsave("Figure 2 Cellular and humoral immune reconstitution after cilta-cel.pdf",
+#        width = 15, 
+#        height = 8)
 ```
@@
   # add_row("name"="Leukopenia",  "day"="apheresis", "value"= "Yes", "grade"="Any grade", "count"=0, "perc"=0) %>% 
-  mutate(day = factor(day, levels = c("apheresis", "-5d", "30d", "60d", "90d", "180d"))) %>% 
+  mutate(day = case_when(
+    day == "apheresis"    ~ "Apheresis",
+    day == "-5d"    ~ "Day -5",
+    day == "30d"    ~ "Day 30",
+    day == "60d"    ~ "Day 60",
+    day == "90d"    ~ "Day 90",
+    day == "180d"    ~ "Day 180"
+  )) %>% 
+  mutate(day = factor(day, levels = c("Apheresis", "Day -5", "Day 30", "Day 60", "Day 90", "Day 180"))) %>% 
   mutate(name = str_replace(name, "^cytopenia", "Any Cytopenia")) %>% 
@@
            position=position_dodge(width=0.9))+
-  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 5,
+  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 3,
             position = position_dodge(width=0.9), vjust=-1.5
@@
   ylim(0, 60)+
-  labs(fill = NULL, x= NULL, y = "%")+
-  theme_classic(base_size = 14)+
+  labs(fill = NULL, x= NULL, y = "Percent")+
+  theme_classic(base_size = 9)+
   theme(legend.position="bottom")
+
+# ggsave("Figure 3 Cytopenias over time.pdf",
+#        width = 7,
+#        height = 4)
+
 ```
@@
 #            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
+#            font.x = c(12, "bold", "black"),
+#            font.y = c(12, "bold", "black"),
+#            font.legend = c(12, "black"),
+#            font.tickslab = c(10, "bold", "black"),
 #            size = 1.5,
@@
 #            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
+# ) + guides(colour = guide_legend(nrow = 1))
 # 
@@
 #                    ) + 
-#   guides(colour = guide_legend(ncol = 1))
+#   guides(colour = guide_legend(nrow = 1))
 # 
@@
 ```{r violin plot}
-cilta %>%
+a <- cilta %>%
   mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
@@
   scale_color_manual(values = c("black", "red"))+
-  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))
-
-cilta %>%
+  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
+  theme(axis.text.x = element_text(angle = 45, 
+                                   hjust = 1#,
+                                   # vjust = 0.5
+                                   ))
+
+b <- cilta %>%
   mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
@@
   scale_color_manual(values = c("black", "red"))+
-  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))#+
+  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
   # coord_flip()
-
-cilta %>%
+  theme(axis.text.x = element_text(angle = 45, 
+                                   hjust = 1#,
+                                   # vjust = 0.5
+                                   ))
+
+c <- cilta %>%
   mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>%
@@
                                    ))
-```
-
-## Figure S3. Viral titers after ide-cel
+
+a /
+  b /
+  c +
+  plot_annotation(tag_levels = "A")
+
+# ggsave("Figure 4 Infection density.pdf",
+#        width = 7,
+#        height = 10)
+
+```
+
+## Figure S3. Viral titers after cilta-cel
 Focus on MCC patients / I didn't use day 180 as they are less values but I can add it if you want.
@@
   geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  theme_classic()+
+  scale_fill_discrete(name = "HSV 1/2 IgG")+
   ggtitle("Evolution of virus titers")
@@
   summarise(count=n()) %>% 
+  mutate(vzv_ig_g_apheresis = factor(vzv_ig_g_apheresis, levels = c("Positive", "Negative"))) %>%
 
@@
   geom_alluvium(aes(fill = vzv_ig_g_apheresis), 
-                color = c("transparent", "transparent", "white", "transparent", "transparent", "transparent")
+                color = c("transparent", "white", "transparent", "transparent", "transparent", "transparent")
   )+
@@
   geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+  scale_fill_discrete(name = "VZV IgG")+
   # geom_hline(yintercept = 5, color = "blue")+
-  theme_classic()+
   ggtitle("Evolution of virus titers")
@@
   geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  theme_classic()+
+  scale_fill_discrete(name = "CMV IgG")+
   ggtitle("Evolution of virus titers")
@@
   plot_annotation(tag_levels = "A")
+
+# ggsave("Figure S3. Viral titers after cilta-cel.pdf",
+#        width = 7,
+#        height = 10)
 ```
@@
   theme_classic()+
+  scale_fill_discrete(name = "HSV 1/2 IgG")+
   ggtitle("Evolution of virus titers")
@@
   theme_classic()+
+  scale_fill_discrete(name = "VZV IgG")+
   ggtitle("Evolution of virus titers")
@@
   plot_annotation(tag_levels = "A")
-```
-
-## Figure S4. Pneumococcal titers after ide-cel
+
+# ggsave("Figure S3+day180 Viral titers after cilta-cel.pdf",
+#        width = 7,
+#        height = 10)
+```
+
+## Figure S4. Pneumococcal titers after cilta-cel
 
@@
          intersect(starts_with("pneumo"), ends_with("change"))) %>% 
+  rename(PolyAb3 = pneumo_poly_ab3_change, PolyAb6 = pneumo_poly_ab6_change, 
+         PolyAb14 = pneumo_poly_ab14_change, PolyAb19 = pneumo_poly_ab19_change,
+         PolyAb23 = pneumo_poly_ab23_change, Serotype1 = pneumo_serotype1_ig_g_change,
+         Serotype4 = pneumo_serotype_4_ig_g_change, Serotype5 = pneumo_serotype5_ig_g_change,
+         Serotype7F = pneumo_serotype7f_ig_g_change, Serotype8 = pneumo_serotype8_ig_g_change,
+         Serotype9N = pneumo_serotype9n_ig_g_change, Serotype9V = pneumo_serotype9v_ig_g_change,
+         Serotype12F = pneumo_serotype12f_ig_g_change, Serotype18C = pneumo_serotype18c_ig_g_change
+         ) %>% 
   drop_na() %>% 
@@
 
-ht_list <- Heatmap(df, name = "change", 
-        rect_gp = gpar(col = "white", lwd = 0.1),
-        column_title = "Change in titers",
-        # show_column_names =FALSE,
+ht_list <- Heatmap(df, name = " ", 
+        rect_gp = gpar(col = "grey", lwd = 0.001), 
+        column_title_side = "bottom",
+        column_title = "Patients",
+        show_column_names =FALSE,
         row_names_side = "left",
@@
         col = colors)
-draw(ht_list, heatmap_legend_side = "bottom")
+pdf("Figure S4 Pneumococcal titers after cilta-cel.pdf", 
+    width = 8,
+    height = 6)
+draw(ht_list, heatmap_legend_side = "right")
+dev.off()
+
 ```
@@
   labs(y="")
+
+# ggsave("Figure S2 Forest plot 5 variables.pdf", 
+#        device = cairo_pdf,
+#        width = 7,
+#        height = 6)
+
 ```
@@
   labs(y="")
+
+# ggsave("Figure S2 Forest plot 3 variables.pdf", 
+#        device = cairo_pdf,
+#        width = 7,
+#        height = 5)
 ```
@@
 ## Survival analysis - KM by gr3_cytopenia_90d
+```{r}
+ggsave_workaround <- function(g){
+  survminer:::.build_ggsurvplot(x = g,
+                                surv.plot.height = NULL,
+                                risk.table.height = NULL,
+                                ncensor.plot.height = NULL)}
+```
+
 ```{r Survival analysis - KM by gr3_cytopenia_90d}
-surv_dat <- fig_dat %>% 
-  mutate(ORR_as_best_response = case_when(
-    ORR_as_best_response == "ORR"         ~ "ORR",
-    ORR_as_best_response == "SD/PD"       ~ "never ORR",
-    # TRUE                                  ~ "never ORR"
-  ))
+surv_dat <- fig_dat #%>% 
+  # mutate(ORR_as_best_response = case_when(
+  #   ORR_as_best_response == "ORR"         ~ "ORR",
+  #   ORR_as_best_response == "SD/PD"       ~ "never ORR",
+  #   # TRUE                                  ~ "never ORR"
+  # ))
 
 library(survival)
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ gr3_cytopenia_90d, 
+myplot <- ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ gr3_cytopenia_90d, 
                    data=surv_dat),
-           title = "PFS Analysis",
+           # title = "PFS Analysis",
            font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
+           font.x = c(12, "bold", "black"),
+           font.y = c(12, "bold", "black"),
+           font.legend = c(12, "black"),
+           font.tickslab = c(12, "bold", "black"),
            size = 1.5,
 
-           xlab = "Time in months",
+           xlab = "Time (months)",
+           ylab = "PFS (probability)",
            legend = "top",
-           legend.title = "",
+           legend.title = "≥ Grade 3 cytopenia at D90",
+           legend.labs = c("No", "Yes"),
            pval = TRUE,
@@
            # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
+           censor = TRUE,
+           risk.table = TRUE, risk.table.y.text = FALSE,
+           tables.theme = theme_survminer(#base_size = 5,
+                                          font.main = c(12, "bold", "black"),
+                                          # font.x = c(10, "bold", "black"),
+                                          # font.y = c(16, "bold", "transparent"),
+                                          # font.tickslab = c(19, "bold", "black")
+                                          )
+) + guides(colour = guide_legend(nrow = 1))
+risk.table.ylab <- "≥ Grade 3 \ncytopenia at D90"
+myplot$table <- myplot$table + labs(y = risk.table.ylab)
+myplot
+
+# ggsave("Survival plot by gr3 cytopenia day 90.pdf", 
+#        width = 7,
+#        height = 5)
+
+# fig_surv_cytday90 <- ggsave_workaround(myplot)
+# 
+# ggsave("Survival plot by gr3 cytopenia day 90 - risk table.pdf",
+#        plot = fig_surv_cytday90,
+#        path= paste0(here::here(), "/cilta_cel"),
+#        width = 6, height = 6,
+#        units = c("in"),
+#        dpi = 600)
 
@@
 #            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
+#            font.x = c(12, "bold", "black"),
+#            font.y = c(12, "bold", "black"),
+#            font.legend = c(12, "black"),
+#            font.tickslab = c(10, "bold", "black"),
 #            size = 1.5,
 # 
-#            xlab = "Time in months",
+#            xlab = "Time (months)",
 #            legend = "top",
@@
 ```{r Survival analysis - KM by ORR_as_best_response}
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ ORR_as_best_response, 
+myplot <- ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ ORR_as_best_response, 
                    data=surv_dat),
-           title = "PFS Analysis",
+           # title = "PFS Analysis",
            font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
+           font.x = c(12, "bold", "black"),
+           font.y = c(12, "bold", "black"),
+           font.legend = c(12, "black"),
+           font.tickslab = c(10, "bold", "black"),
            size = 1.5,
 
-           xlab = "Time in months",
+           xlab = "Time (months)",
+           ylab = "PFS (probability)",
            legend = "top",
            legend.title = "",
+           legend.labs = c("ORR", "SD/PD"),
            pval = TRUE,
@@
            # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
+           censor = TRUE,
+           risk.table = TRUE,
+           tables.theme = theme_survminer(
+             font.main = c(10, "bold", "black")
+           )
+) + guides(colour = guide_legend(nrow = 1))
+myplot
+# ggsave("Survival plot by ORR as best response.pdf", 
+#        width = 7,
+#        height = 5)
+
+# fig_surv_ORR <- ggsave_workaround(myplot)
+# 
+# ggsave("Survival plot by ORR as best response - risk table.pdf",
+#        plot = fig_surv_ORR,
+#        path= paste0(here::here(), "/cilta_cel"),
+#        width = 6, height = 6,
+#        units = c("in"),
+#        dpi = 600)
 
@@
 ```{r Survival analysis - KM by gr3_cytopenia_30d}
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ gr3_cytopenia_30d, 
+myplot <- ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ gr3_cytopenia_30d, 
                    data=surv_dat),
-           title = "PFS Analysis",
+           # title = "PFS Analysis",
            font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
+           font.x = c(12, "bold", "black"),
+           font.y = c(12, "bold", "black"),
+           font.legend = c(12, "black"),
+           font.tickslab = c(10, "bold", "black"),
            size = 1.5,
 
-           xlab = "Time in months",
+           xlab = "Time (months)",
+           ylab = "PFS (probability)",
            legend = "top",
-           legend.title = "",
+           legend.title = "≥ Grade 3 cytopenia at D30",
+           legend.labs = c("No", "Yes"),
            pval = TRUE,
@@
            # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
+           censor = TRUE,
+           risk.table = TRUE,
+           tables.theme = theme_survminer(
+             font.main = c(12, "bold", "black")
+           )
+) + guides(colour = guide_legend(nrow = 1))
+risk.table.ylab <- "≥ Grade 3 \ncytopenia at D30"
+myplot$table <- myplot$table + labs(y = risk.table.ylab)
+myplot
+# ggsave("Survival plot by gr3 cytopenia day 30.pdf", 
+#        width = 7,
+#        height = 5)
+
+# fig_surv_cytday30 <- ggsave_workaround(myplot)
+# 
+# ggsave("Survival plot by gr3 cytopenia day 30 - risk table.pdf",
+#        plot = fig_surv_cytday30,
+#        path= paste0(here::here(), "/cilta_cel"),
+#        width = 6, height = 6,
+#        units = c("in"),
+#        dpi = 600)
 
@@
 ```{r Survival analysis - KM by ht_score}
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ ht_score, 
+myplot <- ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ ht_score, 
                    data=surv_dat),
-           title = "PFS Analysis",
+           # title = "PFS Analysis",
            font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
+           font.x = c(12, "bold", "black"),
+           font.y = c(12, "bold", "black"),
+           font.legend = c(12, "black"),
+           font.tickslab = c(10, "bold", "black"),
            size = 1.5,
 
-           xlab = "Time in months",
+           xlab = "Time (months)",
+           ylab = "PFS (probability)",
            legend = "top",
-           legend.title = "",
+           legend.title = "HT score",
+           legend.labs = c("Low", "High"),
            pval = TRUE,
@@
            # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
+           censor = TRUE,
+           risk.table = TRUE,
+           tables.theme = theme_survminer(
+             font.main = c(12, "bold", "black")
+           )
+) + guides(colour = guide_legend(nrow = 1))
+myplot
+# ggsave("Survival plot by HTscore.pdf", 
+#        width = 7,
+#        height = 5)
+
+# fig_surv_HTscore <- ggsave_workaround(myplot)
+# 
+# ggsave("Survival plot by HTscore - risk table.pdf",
+#        plot = fig_surv_HTscore,
+#        path= paste0(here::here(), "/cilta_cel"),
+#        width = 6, height = 6,
+#        units = c("in"),
+#        dpi = 600)
 
@@
 ```{r Survival analysis - KM by gr3_early_icaht}
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ any_early_icaht,
+myplot <- ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ any_early_icaht,
                    data=surv_dat),
-           title = "PFS Analysis",
+           # title = "PFS Analysis",
            font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
+           font.x = c(12, "bold", "black"),
+           font.y = c(12, "bold", "black"),
+           font.legend = c(12, "black"),
+           font.tickslab = c(10, "bold", "black"),
            size = 1.5,
 
-           xlab = "Time in months",
+           xlab = "Time (months)",
+           ylab = "PFS (probability)",
            legend = "top",
-           legend.title = "",
+           legend.title = "Early ICAHT",
+           legend.labs = c("No", "Yes"),
            pval = TRUE,
@@
            # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
+           censor = TRUE,
+           risk.table = TRUE,
+           tables.theme = theme_survminer(
+             font.main = c(12, "bold", "black")
+           )
+) + guides(colour = guide_legend(nrow = 1))
+myplot
+# ggsave("Survival plot by any early ICAHT.pdf", 
+#        width = 7,
+#        height = 5)
+
+# fig_surv_earlyicaht <- ggsave_workaround(myplot)
+# 
+# ggsave("Survival plot by any early ICAHT - risk table.pdf",
+#        plot = fig_surv_earlyicaht,
+#        path= paste0(here::here(), "/cilta_cel"),
+#        width = 6, height = 6,
+#        units = c("in"),
+#        dpi = 600)
 
@@
 #            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
+#            font.x = c(12, "bold", "black"),
+#            font.y = c(12, "bold", "black"),
+#            font.legend = c(12, "black"),
+#            font.tickslab = c(10, "bold", "black"),
 #            size = 1.5,
 #
-#            xlab = "Time in months",
+#            xlab = "Time (months)",
 #            legend = "top",
@@
 #            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
+# ) + guides(colour = guide_legend(nrow = 1))
 #
@@
 ```{r Survival analysis - KM by gr3_late_icaht}
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ any_late_icaht,
+myplot <- ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ any_late_icaht,
                    data=surv_dat),
-           title = "PFS Analysis",
+           # title = "PFS Analysis",
            font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
+           font.x = c(12, "bold", "black"),
+           font.y = c(12, "bold", "black"),
+           font.legend = c(12, "black"),
+           font.tickslab = c(10, "bold", "black"),
            size = 1.5,
 
-           xlab = "Time in months",
+           xlab = "Time (months)",
+           ylab = "PFS (probability)",
            legend = "top",
-           legend.title = "",
+           legend.title = "Late ICAHT",
+           legend.labs = c("No", "Yes"),
            pval = TRUE,
@@
            # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
+           censor = TRUE,
+           risk.table = TRUE,
+           tables.theme = theme_survminer(
+             font.main = c(12, "bold", "black")
+           )
+) + guides(colour = guide_legend(nrow = 1))
+myplot
+# ggsave("Survival plot by any late ICAHT.pdf", 
+#        width = 7,
+#        height = 5)
+
+# fig_surv_lateicaht <- ggsave_workaround(myplot)
+# 
+# ggsave("Survival plot by any late ICAHT - risk table.pdf",
+#        plot = fig_surv_lateicaht,
+#        path= paste0(here::here(), "/cilta_cel"),
+#        width = 6, height = 6,
+#        units = c("in"),
+#        dpi = 600)
 
@@
 #   add_nevent(location = "level") %>% add_n(location = "level")
+```
+
+```{r}
+# ggarrange(fig_surv_HTscore, fig_surv_cytday30, 
+#           fig_surv_earlyicaht, fig_surv_cytday90, 
+#           fig_surv_lateicaht, 
+#           ncol = 3, nrow = 2, 
+#           labels="AUTO")
+
+# ggsave("Survival panel.pdf", device = cairo_pdf,
+#        path = paste0(here::here(), "/cilta_cel"), 
+#        width = 14, height = 11, 
+#        units = c("in"), 
+#        dpi=600, 
+#        bg="white")
 ```

### 2025-02-12 cilta_cel/Manuscript analyses.Rmd
Add additional analyses

@@
 
+```{r death}
+cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  mutate(os_event = case_when(
+    os_event == 1          ~ "Died",
+    os_event == 0          ~ "Alive"
+  )) %>% 
+  select(os_event) %>% 
+  tbl_summary() %>% 
+  bold_labels() %>% add_stat_label()
+
+cilta %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>% 
+  filter(os_event == 1) %>% 
+  select(`cause of death` = cause_of_death_myeloma_toxicitiy_unrelated) %>% 
+  tbl_summary() %>% 
+  bold_labels() %>% add_stat_label()
+```
+
 ## Table 1. Patient baseline characteristics
@@
 
-## Table 3 A-B. Cytopenias following ide-cel
+## Table 3 A-B. Cytopenias following cilta-cel
 Evaluable patients (who survived and did not progressed) are included for each time points.
@@
 
-## Table S8. Details of infections after ide-cel
+## Table S2. severe infection
+```{r}
+cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  select(any_sevinfection) %>% 
+  tbl_summary() %>% 
+  bold_labels() %>% add_stat_label() %>%
+  modify_spanning_header(all_stat_cols() ~ "**Severe infections in the first 30 days**")
+
+cilta %>% 
+  filter(time_from_infusion_to_infection_days > 30 &
+           time_from_infusion_to_infection_days <= 100) %>% 
+  select(any_sevinfection) %>% 
+  tbl_summary() %>% 
+  bold_labels() %>% add_stat_label() %>%
+  modify_spanning_header(all_stat_cols() ~ "**Severe infections day 31 – 100**")
+
+cilta %>% 
+  filter(time_from_infusion_to_infection_days > 100) %>% 
+  select(any_sevinfection) %>% 
+  tbl_summary() %>% 
+  bold_labels() %>% add_stat_label() %>%
+  modify_spanning_header(all_stat_cols() ~ "**Severe infections after day 100**")
+
+```
+
+## Table S8. Details of infections after cilta-cel
 Patients can be counted multiple times if multiple infections.
@@
 
-```{r Figure 2. Inflammatory markers after ide-cel, fig.height=12}
+```{r Figure 2. Inflammatory markers after cilta-cel, fig.height=12}
 LDH <- fig_dat %>% 
@@
 Focus on MCC patients / I didn't use day 180 as they are less values but I can add it if you want.
-```{r Figure S1. Viral titers after ide-cel}
+```{r Figure S1. Viral titers after cilta-cel}
 fig_dat <- cilta %>% 
@@
 
-```{r Figure S2. Pneumococcal titers after ide-cel, fig.width=15, fig.height=12}
+```{r Figure S2. Pneumococcal titers after cilta-cel, fig.width=15, fig.height=12}
 library(ComplexHeatmap)

### 2025-02-12 cilta_cel/Severe infection table.Rmd
Add additional analyses

--- 2024-04-03 cilta_cel/Manuscript analyses.Rmd
@@
   janitor::clean_names()
-```
-
-```{r exploratory function}
-# check_data <- function(data){
-#   
-#   for(i in 1:length(colnames(data))) {
-#     
-#     if(class(data[[i]]) == "factor" | class(data[[i]]) == "character") {
-#       
-#       # print(data[i])
-#       print(colnames(data[i]))
-#       print(table(data[[i]]))
-#     }
-#     
-#   }
-# }
-# 
-# check_data(cart[2:50])
-# check_data(cart[51:100])
-# check_data(cart[101:150])
-# check_data(cart[151:200]) # has < : "CRP Pre-Leukapheresis", 
-# check_data(cart[201:250]) # has < :"CRP day +21",  "CRP day +30", 
-# # has > :  "CRP day +90"
-# check_data(cart[251:300]) # has < : "CRP day +180"
-# check_data(cart[1:44, 301:353]) # need to see patient in Moffitt
 ```
@@
 
-### Tables
-Patients evaluable at each time point
-```{r evaluable}
-day7 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (7 / 30.417)) %>% 
-  select(pt_identifier) %>% 
-  tbl_summary(missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-day14 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (14 / 30.417)) %>% 
-  select(pt_identifier) %>% 
-  tbl_summary(missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-day21 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (21 / 30.417)) %>% 
-  select(pt_identifier) %>% 
-  tbl_summary(missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-day30 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (30 / 30.417)) %>% 
-  select(pt_identifier) %>% 
-  tbl_summary(missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-day90 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > 3) %>% 
-  select(pt_identifier) %>% 
-  tbl_summary(missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-day180 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > 6) %>% 
-  select(pt_identifier) %>% 
-  tbl_summary(missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-mon12 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > 12) %>% 
-  select(pt_identifier) %>% 
-  tbl_summary(missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-tbl_merge(list(day7, day14, day21, day30, day90, day180, mon12), 
-          tab_spanner = c("day7", "day14", "day21", "day30", "day90", "day180", "month12"))
+```{r}
+cilta <- cilta %>% 
+  mutate(infection_type_bacterial_viral_fungal_parasitic = 
+           factor(infection_type_bacterial_viral_fungal_parasitic, 
+                  levels = c("Bacterial", "Fungal", "Viral")))
 ```
 
-```{r infused}
+# Any infection
+85 infection that you separated into 88 in 51 patients
+```{r}
 cilta %>% 
   distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(`infused?` = notinfused) %>% 
-  tbl_summary(missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
+  select("Patient with infection" = any_infection) %>% 
+  tbl_summary() %>% 
+  bold_levels() %>% 
+  modify_header(update = all_stat_cols() ~ "Overall number of patient = {n}")
+
+cilta %>% 
+  select("Overall number of infection"= any_infection) %>% 
+  tbl_summary() %>% 
+  bold_levels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
 ```
 
-## Table 1. Patient baseline characteristics
-```{r Table 1}
+6 patients experienced infection in the first 30 days then had another infection between days 31 and 100
+```{r}
+infection_30days <- cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  filter(any_infection == "Yes")
+
+cilta %>% 
+  filter(time_from_infusion_to_infection_days > 30 &
+           time_from_infusion_to_infection_days <= 100) %>% 
+  filter(any_infection == "Yes") %>% 
+  filter(pt_identifier %in% c(infection_30days$pt_identifier)) %>% 
+  select(pt_identifier) %>% 
+  distinct() %>% 
+  tbl_summary()
+
+```
+
+# In the first 30 days after cilta-cel, 30 infections occurred in 23 patients; 15 severe infections occurred in 9 patients
+```{r}
+cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(any_infection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_infection = "Patient with infection"),
+              type = list(any_infection ~ "dichotomous"),
+              value = list(any_infection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+
+cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  select(any_infection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_infection = "Overall infection"),
+              type = list(any_infection ~ "dichotomous"),
+              value = list(any_infection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+
+cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(any_sevinfection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_sevinfection = "Patient with severe infection"),
+              type = list(any_sevinfection ~ "dichotomous"),
+              value = list(any_sevinfection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+
+cilta %>% 
+  filter(time_from_infusion_to_infection_days <= 30) %>% 
+  select(any_sevinfection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_sevinfection = "Overall severe infection"),
+              type = list(any_sevinfection ~ "dichotomous"),
+              value = list(any_sevinfection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+```
+
+Between days 31 and 100, 32 infections occurred in 24 patients, with __ severe infections all in different patients
+```{r}
+infection_patient_31_100 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days > 30 &
+           time_from_infusion_to_infection_days <= 100) %>% 
+  distinct(pt_identifier, .keep_all = TRUE)
+infection_patient_31_100 %>%
+  select(any_infection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_infection = "Patient with infection"),
+              type = list(any_infection ~ "dichotomous"),
+              value = list(any_infection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+
+cilta %>% 
+  filter(time_from_infusion_to_infection_days > 30 &
+           time_from_infusion_to_infection_days <= 100) %>% 
+  select(any_infection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_infection = "Overall infection"),
+              type = list(any_infection ~ "dichotomous"),
+              value = list(any_infection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+
+cilta %>% 
+filter(time_from_infusion_to_infection_days > 30 &
+           time_from_infusion_to_infection_days <= 100) %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(any_sevinfection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_sevinfection = "Patient with severe infection"),
+              type = list(any_sevinfection ~ "dichotomous"),
+              value = list(any_sevinfection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+
+cilta %>% 
+filter(time_from_infusion_to_infection_days > 30 &
+           time_from_infusion_to_infection_days <= 100) %>% 
+  select(any_sevinfection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_sevinfection = "Overall severe infection"),
+              type = list(any_sevinfection ~ "dichotomous"),
+              value = list(any_sevinfection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+```
+
+After day 100, 23 infections occurred in 17 patients, with __ severe infections all in different patients
+```{r}
+infection_patient_31_100 <- cilta %>% 
+  filter(time_from_infusion_to_infection_days > 100) %>% 
+  distinct(pt_identifier, .keep_all = TRUE)
+infection_patient_31_100 %>%
+  select(any_infection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_infection = "Patient with infection"),
+              type = list(any_infection ~ "dichotomous"),
+              value = list(any_infection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+
+cilta %>% 
+  filter(time_from_infusion_to_infection_days > 100) %>% 
+  select(any_infection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_infection = "Overall infection"),
+              type = list(any_infection ~ "dichotomous"),
+              value = list(any_infection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+
+cilta %>% 
+  filter(time_from_infusion_to_infection_days > 100) %>% 
+  distinct(pt_identifier, .keep_all = TRUE) %>%
+  select(any_sevinfection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_sevinfection = "Patient with severe infection"),
+              type = list(any_sevinfection ~ "dichotomous"),
+              value = list(any_sevinfection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+
+cilta %>% 
+  filter(time_from_infusion_to_infection_days > 100) %>% 
+  select(any_sevinfection) %>% 
+  tbl_summary(statistic = everything() ~ "{n}",
+              label = list(any_sevinfection = "Overall severe infection"),
+              type = list(any_sevinfection ~ "dichotomous"),
+              value = list(any_sevinfection ~ "Yes")) %>% 
+  bold_labels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
+```
+
+Any severe infection
+28 infection that you will probably separate into more type. The next table should help you with that.
+```{r}
 cilta %>% 
   distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(os_from_infusion_months, age, agecat, male_sex, sex,
-         extramedullary_disease_yes_no, 
-         high_marrow_burden_50_percent, ecog_at_ld, 
-         r_iss_at_car_t_infusion, 
-         cytogenetics, cytogenetics_incl_1q,
-         deletion_17p_prior_to_car_t_infusion_yes_no,
-         t_4_14_prior_to_car_t_infusion_yes_no,
-         t_14_16_prior_to_car_t_infusion_yes_no, gain_amp1q21,
-         bridging_therapy_yes_no,
-         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
-         Prior_bcma_therapy,
-         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
-         ht_score, early_icaht_cat, any_early_icaht,
-         gr3_early_icaht, 
-         late_icaht_cat, any_late_icaht,
-         gr3_late_icaht) %>% 
-  tbl_summary(
-    type = list(
-      c(agecat, sex, 
-        extramedullary_disease_yes_no, high_marrow_burden_50_percent,
-        cytogenetics, cytogenetics_incl_1q,
-        deletion_17p_prior_to_car_t_infusion_yes_no,
-        t_4_14_prior_to_car_t_infusion_yes_no,
-        t_14_16_prior_to_car_t_infusion_yes_no, gain_amp1q21,
-        bridging_therapy_yes_no, prior_auto_sct_yes_no,
-        Prior_bcma_therapy,
-        # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-        immuno, proteasome, dara, doubleref, tripleref, pentaref,
-        did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
-        ht_score, early_icaht_cat, any_early_icaht,
-         gr3_early_icaht, 
-         late_icaht_cat, any_late_icaht,
-         gr3_late_icaht)
-      ~"categorical"),
-
-    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
-    digits = all_continuous() ~ 1
-  ) %>% 
-  bold_labels() %>% add_stat_label() %>% 
-  modify_footnote(update = everything() ~ NA)
+  select("Patient with severe infection" = any_sevinfection) %>% 
+  tbl_summary() %>% 
+  bold_levels() %>% 
+  modify_header(update = all_stat_cols() ~ "Overall number of patient = {n}")
+
+cilta %>% 
+  select("Overall number of severe infection"= any_sevinfection) %>% 
+  tbl_summary() %>% 
+  bold_levels() %>% 
+  modify_header(update = all_stat_cols() ~ "**{level}**")
 ```
 
-## Table 2. Clinical outcomes
-```{r}
-tbl1 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(max_crs_grade_0_5, CRS_gradecat,
-         day_of_onset_crs_relative_to_infusion,
-         day_of_max_crs_relative_to_infusion,
-         duration_of_crs_days, 
-         max_icans, ICANS_gradecat,
-         day_of_onset_icans_relative_to_infusion,
-         day_of_max_icans_relative_to_infusion,
-         duration_of_icans_days,
-         delayed_neuro,
-         parkinsonian_neurotoxicity_yes_no,
-         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
-         delayed_neuro_type,
-         hlh, hlh_hlh_like_toxicities,
-         overall_hlh) %>% 
-  tbl_summary(type = list(
-    c(day_of_onset_crs_relative_to_infusion,
-      day_of_max_crs_relative_to_infusion,
-      duration_of_crs_days,
-      day_of_onset_icans_relative_to_infusion,
-      day_of_max_icans_relative_to_infusion,
-      duration_of_icans_days) ~ "continuous",
-    c(delayed_neuro,
-      parkinsonian_neurotoxicity_yes_no,
-      other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
-      hlh, hlh_hlh_like_toxicities,
-      overall_hlh) 
-    ~ "categorical"),
-    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
-    digits = all_continuous() ~ 1,
-    missing = "no"
-    ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl2 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(steroid_use_yes_no, tocilizumab_yes_no, 
-         anakinra_yes_no) %>% 
-  tbl_summary(type = list(
-    c(steroid_use_yes_no, tocilizumab_yes_no, 
-      anakinra_yes_no) ~ "categorical"),
-    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-    digits = all_continuous() ~ 1
-    ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl3 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(MRD_day30,
-         ORR_30days,
-         day30_response,
-         day30_response_v2) %>% 
-  tbl_summary(type = list(
-    c(MRD_day30) ~ "categorical"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl4 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(day30_response_v2 == "sCR or CR") %>% 
-  select(MRD_day30) %>% 
-  tbl_summary(type = list(
-    c(MRD_day30) ~ "categorical"),
-    label = list(MRD_day30 ~ 
-                   "MRD_day30 within CR/sCR"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl5 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(MRD_mon3,
-         ORR_mon3,
-         mon3_response,
-         mon3_response_v2) %>% 
-  tbl_summary(type = list(
-    c(MRD_mon3) ~ "categorical"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl6 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(mon3_response_v2 == "sCR or CR") %>% 
-  select(MRD_mon3) %>% 
-  tbl_summary(type = list(c(MRD_mon3) ~ "categorical"),
-              label = list(MRD_mon3 ~ "MRD_mon3 within CR/sCR"),
-              digits = all_continuous() ~ 1,
-              missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl7 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(ORR_as_best_response, best_ORRcollapsed,
-         best_response, best_response_MRD) %>% 
-  tbl_summary(#type = list(c(MRD_mon3) ~ "categorical"),
-              # label = list(best_response ~ "best response in the first 90 days"),
-              digits = all_continuous() ~ 1,
-              missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl8 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(best_response == "sCR or CR") %>% 
-  select(best_response_MRD) %>% 
-  tbl_summary(type = list(c(best_response_MRD) ~ "categorical"),
-              label = list(best_response_MRD ~ "best_response_MRD within CR/sCR"),
-              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1,
-              missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() #%>%
-  # gt::tab_source_note(gt::md("**At 30days: <br>
-  #                            1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
-  #                            1 patients was not evaluated. <br>
-  #                            At 90days: <br>
-  #                            1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
-  #                            1 patient is not Heme not evaluable; <br>
-  #                            2 patients were not evaluated; <br>
-  #                            1 patients is not evaluable by death**"))
-
-```
-
-<!-- For responses make denominator evaluable patients -->
-<!-- Patient who died or was lost to follow-up or had non-secretory disease would not be evaluable -->
-
-## Table S3. Apheresis and product characteristics
-```{r Apheresis and product characteristics}
-cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(tbv, whole_blood_processed_m_l,
-         final_collection_volume_m_l, 
-         tbv_processed, 
-         access_type,
-         run_time_min,
-         time_from_apheresis_to_car_t_infusion_days, total_bags,
-         total_dose_volume_m_l, cell_dose_million_cells
-  ) %>% 
-  tbl_summary(type = list(
-    c(tbv, total_bags) ~ "continuous"),
-    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-    digits = all_continuous() ~ 1,
-  missing = "no") %>% 
-  bold_labels() %>% add_stat_label()
-```
-
-## Table 3 A-B. Cytopenias following ide-cel
-Evaluable patients (who survived and did not progressed) are included for each time points.
-```{r Table 3}
-tbl1 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select("Leukopenia" = Leukopenia_apheresis, 
-         "Grade3+ Leukopenia" = gr3_Leukopenia_apheresis, 
-         "Neutropenia" = Neutropenia_apheresis, 
-         "Grade3+ Neutropenia" = gr3_Neutropenia_apheresis, 
-         "Anemia" = Anemia_apheresis, 
-         "Grade3+ Anemia" = gr3_Anemia_apheresis, 
-         "Thrombocytopenia" = Thrombocytopenia_apheresis, 
-         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_apheresis,
-         "Any Cytopenia" = cytopenia_apheresis,
-         "Grade3+ Cytopenia" = gr3_cytopenia_apheresis
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl2 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select("Leukopenia" = `Leukopenia_-5d`, 
-         "Grade3+ Leukopenia" = `gr3_Leukopenia_-5d`, 
-         "Neutropenia" = `Neutropenia_-5d`, 
-         "Grade3+ Neutropenia" = `gr3_Neutropenia_-5d`,
-         "Anemia" = `Anemia_-5d`, 
-         "Grade3+ Anemia" = `gr3_Anemia_-5d`, 
-         "Thrombocytopenia" = `Thrombocytopenia_-5d`, 
-         "Grade3+ Thrombocytopenia" = `gr3_Thrombocytopenia_-5d`,
-         "Any Cytopenia" = `cytopenia_-5d`,
-         "Grade3+ Cytopenia" = `gr3_cytopenia_-5d`
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl3 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select("Leukopenia" = Leukopenia_0d, 
-         "Grade3+ Leukopenia" = gr3_Leukopenia_0d, 
-         "Neutropenia" = Neutropenia_0d, 
-         "Grade3+ Neutropenia" = gr3_Neutropenia_0d, 
-         "Anemia" = Anemia_0d, 
-         "Grade3+ Anemia" = gr3_Anemia_0d,
-         "Thrombocytopenia" = Thrombocytopenia_0d, 
-         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_0d,
-         "Any Cytopenia" = cytopenia_0d,
-         "Grade3+ Cytopenia" = gr3_cytopenia_0d
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl4 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (7 / 30.417)) %>% 
-  select("Leukopenia" = Leukopenia_7d, 
-         "Grade3+ Leukopenia" = gr3_Leukopenia_7d, 
-         "Neutropenia" = Neutropenia_7d, 
-         "Grade3+ Neutropenia" = gr3_Neutropenia_7d, 
-         "Anemia" = Anemia_7d, 
-         "Grade3+ Anemia" = gr3_Anemia_7d, 
-         "Thrombocytopenia" = Thrombocytopenia_7d, 
-         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_7d,
-         "Any Cytopenia" = cytopenia_7d,
-         "Grade3+ Cytopenia" = gr3_cytopenia_7d
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl5 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (14 / 30.417)) %>% 
-select("Leukopenia" = Leukopenia_14d, 
-       "Grade3+ Leukopenia" = gr3_Leukopenia_14d, 
-       "Neutropenia" = Neutropenia_14d, 
-       "Grade3+ Neutropenia" = gr3_Neutropenia_14d,
-       "Anemia" = Anemia_14d, 
-       "Grade3+ Anemia" = gr3_Anemia_14d,
-       "Thrombocytopenia" = Thrombocytopenia_14d, 
-       "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_14d,
-       "Any Cytopenia" = cytopenia_14d,
-       "Grade3+ Cytopenia" = gr3_cytopenia_14d
-) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl6 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (21 / 30.417)) %>% 
-  select("Leukopenia" = Leukopenia_21d,
-         "Grade3+ Leukopenia" = gr3_Leukopenia_21d, 
-         "Neutropenia" = Neutropenia_21d, 
-         "Grade3+ Neutropenia" = gr3_Neutropenia_21d, 
-         "Anemia" = Anemia_21d, 
-         "Grade3+ Anemia" = gr3_Anemia_21d,
-         "Thrombocytopenia" = Thrombocytopenia_21d, 
-         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_21d,
-         "Any Cytopenia" = cytopenia_21d,
-         "Grade3+ Cytopenia" = gr3_cytopenia_21d
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl7 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (30 / 30.417)) %>% 
-  select("Leukopenia" = Leukopenia_30d, 
-         "Grade3+ Leukopenia" = gr3_Leukopenia_30d,
-         "Neutropenia" = Neutropenia_30d, 
-         "Grade3+ Neutropenia" = gr3_Neutropenia_30d,
-         "Anemia" = Anemia_30d, 
-         "Grade3+ Anemia" = gr3_Anemia_30d, 
-         "Thrombocytopenia" = Thrombocytopenia_30d,
-         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_30d,
-         "Any Cytopenia" = cytopenia_30d,
-         "Grade3+ Cytopenia" = gr3_cytopenia_30d
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl8 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > 3) %>% 
-  select("Leukopenia" = Leukopenia_90d, 
-         "Grade3+ Leukopenia" = gr3_Leukopenia_90d,
-         "Neutropenia" = Neutropenia_90d, 
-         "Grade3+ Neutropenia" = gr3_Neutropenia_90d,
-         "Anemia" = Anemia_90d,
-         "Grade3+ Anemia" = gr3_Anemia_90d,
-         "Thrombocytopenia" = Thrombocytopenia_90d, 
-         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_90d,
-         "Any Cytopenia" = cytopenia_90d,
-         "Grade3+ Cytopenia" = gr3_cytopenia_90d
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl9 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > 6) %>% 
-  select("Leukopenia" = Leukopenia_180d, 
-         "Grade3+ Leukopenia" = gr3_Leukopenia_180d,
-         "Neutropenia" = Neutropenia_180d, 
-         "Grade3+ Neutropenia" = gr3_Neutropenia_180d,
-         "Anemia" = Anemia_180d,
-         "Grade3+ Anemia" = gr3_Anemia_180d,
-         "Thrombocytopenia" = Thrombocytopenia_180d, 
-         "Grade3+ Thrombocytopenia" = gr3_Thrombocytopenia_180d,
-         "Any Cytopenia" = cytopenia_180d,
-         "Grade3+ Cytopenia" = gr3_cytopenia_180d
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8, tbl9), 
-          tab_spanner = c("Apheresis", "Day -5", "Day 0", 
-                          "Day 7", "Day 14", "Day 21",
-                          "Day 30", "Day 90", "Day 180")) %>% as_gt() #%>%
-# gt::tab_source_note(gt::md("**Not evaluable patients are removed from the denominator <br>
-#                            1 patient has missing 90 days values**"))
-```
-
-```{r}
-tbl1 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(any_early_icaht, 
-         gr3_early_icaht, 
-         any_late_icaht, 
-         gr3_late_icaht
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl2 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(any_early_icaht, 
-         gr3_early_icaht, 
-         any_late_icaht, 
-         gr3_late_icaht
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl3 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(any_early_icaht, 
-         gr3_early_icaht, 
-         any_late_icaht, 
-         gr3_late_icaht
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl4 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (7 / 30.417)) %>% 
-  select(any_early_icaht, 
-         gr3_early_icaht, 
-         any_late_icaht, 
-         gr3_late_icaht
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl5 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (14 / 30.417)) %>% 
-select(any_early_icaht, 
-         gr3_early_icaht, 
-         any_late_icaht, 
-         gr3_late_icaht
-) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl6 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (21 / 30.417)) %>% 
-  select(any_early_icaht, 
-         gr3_early_icaht, 
-         any_late_icaht, 
-         gr3_late_icaht
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl7 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (30 / 30.417)) %>% 
-  select(any_early_icaht, 
-         gr3_early_icaht, 
-         any_late_icaht, 
-         gr3_late_icaht
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl8 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > 3) %>% 
-  select(any_early_icaht, 
-         gr3_early_icaht, 
-         any_late_icaht, 
-         gr3_late_icaht
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl9 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > 6) %>% 
-  select(any_early_icaht, 
-         gr3_early_icaht, 
-         any_late_icaht, 
-         gr3_late_icaht
-  ) %>% 
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-              digits = all_continuous() ~ 1,
-              missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8, tbl9), 
-          tab_spanner = c("Apheresis", "Day -5", "Day 0", 
-                          "Day 7", "Day 14", "Day 21",
-                          "Day 30", "Day 90", "Day 180"))
-```
-
-## Table 4. Bone marrow biopsy findings
-```{r Table 4}
-tbl1 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select("marrow cellularity" = marrow_cellularity_baseline_normo_hypo_hyper, 
-         "marrow cellularity (%)" = marrow_cellularity_baseline_percent,
-         "% CD138 positive by IHC" = marrow_cd138_baseline_percent,
-         # "is cellularity variable?"= contains("marrow_cellularity_baseline") & contains("is_variable_"),
-         "Fibrosis grade" = marrow_fibrosis_baseline_0_1_2_3, 
-         "Dysplasia present" = marrow_dysplasia_baseline_yes_no
-  ) %>% 
-  tbl_summary(type = list(
-    c("marrow cellularity (%)", "% CD138 positive by IHC",
-      "Fibrosis grade") ~ "continuous",
-    c("Dysplasia present") ~ "categorical"
-  ),
-  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-  digits = all_continuous() ~ 1#,
-  # missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl2 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > (30 / 30.417)) %>% 
-  select("marrow cellularity" = marrow_cellularity_day_30_normo_hypo_hyper, 
-         "marrow cellularity (%)" = marrow_percent_cellularity_day_30,
-         "% CD138 positive by IHC" = marrow_percent_cd138_day_30, 
-         # "is cellularity variable?"= contains("marrow_cellularity_day_30") & contains("is_variable_"),
-         "Fibrosis grade" = marrow_fibrosis_day_30_0_1_2_3, 
-         "Dysplasia present" = marrow_dysplasia_day_30_yes_no
-  ) %>% 
-  tbl_summary(type = list(
-    c("marrow cellularity (%)", "% CD138 positive by IHC",
-      "Fibrosis grade") ~ "continuous",
-    c("Dysplasia present") ~ "categorical"
-  ),
-  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-  digits = all_continuous() ~ 1#,
-  # missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl3 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > 3) %>% 
-  select("marrow cellularity" = marrow_cellularity_day_90_normo_hypo_hyper, 
-         "marrow cellularity (%)" = marrow_percent_cellularity_day_90,
-         "% CD138 positive by IHC" = marrow_percent_cd138_day_90, 
-         # "is cellularity variable?"= contains("marrow_cellularity_day_90") & contains("is_variable_"),
-         "Fibrosis grade" = marrow_fibrosis_day_90_0_1_2_3, 
-         "Dysplasia present" = marrow_dysplasia_day_90_yes_no
-  ) %>% 
-  tbl_summary(type = list(
-    c("marrow cellularity (%)", "% CD138 positive by IHC",
-      "Fibrosis grade") ~ "continuous",
-    c("Dysplasia present") ~ "categorical"
-  ),
-  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-  digits = all_continuous() ~ 1#,
-  # missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl4 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  filter(pfs_event == 0 | pfs_from_infusion_months > 6) %>% 
-  select("marrow cellularity" = marrow_cellularity_day_180_normo_hypo_hyper, 
-         "marrow cellularity (%)" = marrow_percent_cellularity_day_180,
-         "% CD138 positive by IHC" = marrow_percent_cd138_day_180, 
-         # "is cellularity variable?"= contains("marrow_cellularity_day_180") & contains("is_variable_"),
-         "Fibrosis grade" = marrow_fibrosis_day_180_0_1_2_3, 
-         "Dysplasia present" = marrow_dysplasia_day_180_yes_no
-  ) %>% 
-  tbl_summary(type = list(
-    c("marrow cellularity (%)", "% CD138 positive by IHC",
-      "Fibrosis grade") ~ "continuous",
-    c("Dysplasia present") ~ "categorical"
-  ),
-  statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-  digits = all_continuous() ~ 1#,
-  # missing = "no"
-  ) %>% 
-  bold_labels() %>% add_stat_label()
-
-tbl_merge(list(tbl1, tbl2, tbl3, tbl4), 
-          tab_spanner = c("Baseline", "Day 30", "Day 90", "Day 180"))
-```
-
-## Table 5. Supportive therapies and engraftment
-
-```{r Table 5. Supportive therapies and engraftment}
-tbl1 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(need_for_g_csf_post_infus_yes_1_no_0) %>%
-  tbl_summary() %>%
-  bold_labels() %>% add_stat_label()
-
-tbl1_1 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(first_day_of_gcsf, last_day_of_gcsf,
-         gcsf_duration) %>%
-  tbl_summary(type = list(
-    everything() ~ "continuous"),
-    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>%
-  add_stat_label()
-
-tbl2 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(cd34_stem_cell_boost_yes_1_no_0) %>%
-  tbl_summary() %>%
-  bold_labels() %>% add_stat_label()
-
-tbl2_1 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(day_of_stem_cell_boost, boost_cell_dose_million_cells) %>%
-  tbl_summary(type = list(
-    everything() ~ "continuous"),
-    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>%
-  add_stat_label()
-
-tbl3 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(day_of_neutrophil_recovery) %>%
-  tbl_summary(statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>%
-  bold_labels() %>% add_stat_label()
-
-tbl3_1 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(neutrophil_recovery_ANC_never_below_500, neutrophil_recovery_did_not_recover) %>%
-  tbl_summary(type = list(
-    everything() ~ "dichotomous"),
-    missing = "no") %>%
-  add_stat_label()
-
-tbl4 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(transfusion_postCART) %>%
-  tbl_summary(type = list(everything() ~ "dichotomous"),
-    missing = "no") %>%
-  bold_labels() %>% add_stat_label()
-
-tbl4_1 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(rbc_transfusion_within_30d_post_cart_yes_1_no_0, plt_transfusion_within_30d_post_cart_yes_1_no_0,
-         rbc_transfusion_30d_post_cart_yes_1_no_0, plt_transfusion_30d_post_cart_yes_1_no_0) %>%
-  tbl_summary(
-    missing = "no") %>%
-  add_stat_label()
-
-tbl5 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(tpo_agonist_post_cart_yes_1_no_0) %>%
-  tbl_summary(
-    missing = "no") %>%
-  bold_labels() %>% add_stat_label()
-
-tbl5_1 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(first_day_of_tpo_agonist, last_day_of_tpo_agonist,
-         tpo_duration) %>%
-  tbl_summary(type = list(
-    everything() ~ "continuous"),
-    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>%
-  add_stat_label()
-
-tbl6 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(need_for_ivig_yes_1_no_0) %>%
-  tbl_summary() %>%
-  bold_labels() %>% add_stat_label()
-
-tbl6_1 <- cilta %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>%
-  select(first_day_of_ivig, last_day_of_ivig,
-         ivig_duration) %>%
-  tbl_summary(type = list(
-    everything() ~ "continuous"),
-    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>%
-  add_stat_label()
-
-tbl_stack(list(tbl1, tbl1_1, tbl2, tbl2_1, tbl3, tbl3_1,
-               tbl4, tbl4_1, tbl5, tbl5_1, tbl6, tbl6_1))
-```
-
-## Table S4a. Patient characteristics by grade 3+ cytopenia at Day 30
-```{r Patient characteristics by grade 3+ cytopenia at Day 30}
-cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(bm_plasma_cell_percent_at_pre_ld,
-         number_of_prior_lines_of_therapy,
-         number_prior_lines_therapy,
-         # `Days from last bridging to CAR-T infusion`,         ################# Not in data?
-         lenalidomide_exposed_vs_refractory_vs_not_exposed,
-         bortezomib_exposed_vs_refractory_vs_not_exposed,
-         carfilzomib_exposed_vs_refractory_vs_not_exposed,
-         pomalidomide_exposed_vs_refractory_vs_not_exposed,
-         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
-         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-         "Marrow Cellularity (%) at Day30" = marrow_percent_cellularity_day_30,
-         os_from_infusion_months, age, agecat, male_sex, sex,
-         extramedullary_disease_yes_no, 
-         high_marrow_burden_50_percent, ecog_at_ld, 
-         r_iss_at_car_t_infusion, 
-         cytogenetics, cytogenetics_incl_1q,
-         bridging_therapy_yes_no,
-         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
-         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
-         Prior_bcma_therapy,
-         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
-         cytopenia_apheresis, Neutropenia_apheresis,
-         Anemia_apheresis,Thrombocytopenia_apheresis,
-         `cytopenia_-5d`, `Neutropenia_-5d`,
-         `Anemia_-5d`, `Thrombocytopenia_-5d`,
-         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
-         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
-         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
-         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
-         ht_score,
-         gr3_cytopenia_30d) %>% 
-  tbl_summary(by = gr3_cytopenia_30d,
-              type = list(
-                c(extramedullary_disease_yes_no,
-                  bm_plasma_cell_percent_at_pre_ld,
-                  cytopenia_apheresis,`cytopenia_-5d`,
-                  cytogenetics, cytogenetics_incl_1q,
-                  bridging_therapy_yes_no,
-                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-                  prior_auto_sct_yes_no,
-                  Prior_bcma_therapy,
-                  immuno, proteasome, dara,
-                  doubleref, tripleref, pentaref,
-                  cytopenia_apheresis, Neutropenia_apheresis,
-                  Anemia_apheresis,Thrombocytopenia_apheresis,
-                  `cytopenia_-5d`, `Neutropenia_-5d`,
-                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
-                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
-                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
-                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
-                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
-                  ht_score,
-                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
-                ~"categorical",
-                c(bm_plasma_cell_percent_at_pre_ld,
-                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
-                ~ "continuous"),
-              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1
-  ) %>% 
-  bold_labels() %>% add_stat_label() %>% add_p() %>% 
-  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
-```
-
-## Table S4b. Patient characteristics by ANY early ICAHT
-```{r Patient characteristics by grade 3+ early ICAHT}
-cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(bm_plasma_cell_percent_at_pre_ld,
-         number_of_prior_lines_of_therapy,
-         number_prior_lines_therapy,
-         # `Days from last bridging to CAR-T infusion`,         ################# Not in data?
-         lenalidomide_exposed_vs_refractory_vs_not_exposed,
-         bortezomib_exposed_vs_refractory_vs_not_exposed,
-         carfilzomib_exposed_vs_refractory_vs_not_exposed,
-         pomalidomide_exposed_vs_refractory_vs_not_exposed,
-         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
-         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-         "Marrow Cellularity (%) at Day30" = marrow_percent_cellularity_day_30,
-         os_from_infusion_months, age, agecat, male_sex, sex,
-         extramedullary_disease_yes_no, 
-         high_marrow_burden_50_percent, ecog_at_ld, 
-         r_iss_at_car_t_infusion, 
-         cytogenetics, cytogenetics_incl_1q,
-         bridging_therapy_yes_no,
-         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
-         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
-         Prior_bcma_therapy,
-         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
-         cytopenia_apheresis, Neutropenia_apheresis,
-         Anemia_apheresis,Thrombocytopenia_apheresis,
-         `cytopenia_-5d`, `Neutropenia_-5d`,
-         `Anemia_-5d`, `Thrombocytopenia_-5d`,
-         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
-         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
-         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
-         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
-         ht_score,
-         any_early_icaht) %>% 
-  tbl_summary(by = any_early_icaht,
-              type = list(
-                c(extramedullary_disease_yes_no,
-                  bm_plasma_cell_percent_at_pre_ld,
-                  cytopenia_apheresis,`cytopenia_-5d`,
-                  cytogenetics, cytogenetics_incl_1q,
-                  bridging_therapy_yes_no,
-                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-                  prior_auto_sct_yes_no,
-                  Prior_bcma_therapy,
-                  immuno, proteasome, dara,
-                  doubleref, tripleref, pentaref,
-                  cytopenia_apheresis, Neutropenia_apheresis,
-                  Anemia_apheresis,Thrombocytopenia_apheresis,
-                  `cytopenia_-5d`, `Neutropenia_-5d`,
-                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
-                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
-                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
-                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
-                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
-                  ht_score,
-                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
-                ~"categorical",
-                c(bm_plasma_cell_percent_at_pre_ld,
-                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
-                ~ "continuous"),
-              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1
-  ) %>% 
-  bold_labels() %>% add_stat_label() %>% add_p() %>% 
-  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Early ICAHT**")
-```
-
-## Table S5a. Patient characteristics by grade 3+ cytopenia at Day 90
-```{r Patient characteristics by grade 3+ cytopenia at Day 90}
-cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_90days)) %>%  ######################### Fix evaluable----------
-  select(bm_plasma_cell_percent_at_pre_ld,
-         number_of_prior_lines_of_therapy,
-         number_prior_lines_therapy,
-         # `Days from last bridging to CAR-T infusion`,
-         lenalidomide_exposed_vs_refractory_vs_not_exposed,
-         bortezomib_exposed_vs_refractory_vs_not_exposed,
-         carfilzomib_exposed_vs_refractory_vs_not_exposed,
-         pomalidomide_exposed_vs_refractory_vs_not_exposed,
-         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
-         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-         "Marrow Cellularity (%) at Day90" = marrow_percent_cellularity_day_90,
-         os_from_infusion_months,
-         age, agecat, male_sex, sex,
-         extramedullary_disease_yes_no, 
-         high_marrow_burden_50_percent, ecog_at_ld, r_iss_at_car_t_infusion, 
-         cytogenetics, cytogenetics_incl_1q,
-         bridging_therapy_yes_no,
-         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
-         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
-         Prior_bcma_therapy,
-         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
-         cytopenia_apheresis, Neutropenia_apheresis,
-         Anemia_apheresis,Thrombocytopenia_apheresis,
-         `cytopenia_-5d`, `Neutropenia_-5d`,
-         `Anemia_-5d`, `Thrombocytopenia_-5d`,
-         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
-         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
-         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
-         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
-         ht_score,
-         gr3_cytopenia_90d) %>% 
-  tbl_summary(by = gr3_cytopenia_90d,
-              type = list(
-                c(extramedullary_disease_yes_no,
-                  bm_plasma_cell_percent_at_pre_ld,
-                  cytopenia_apheresis,`cytopenia_-5d`,
-                  cytogenetics, cytogenetics_incl_1q,
-                  bridging_therapy_yes_no,
-                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-                  prior_auto_sct_yes_no,
-                  immuno, proteasome, dara,
-                  doubleref, tripleref, pentaref,
-                  cytopenia_apheresis, Neutropenia_apheresis,
-                  Anemia_apheresis,Thrombocytopenia_apheresis,
-                  `cytopenia_-5d`, `Neutropenia_-5d`,
-                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
-                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
-                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
-                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
-                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
-                  ht_score,
-                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
-                ~ "categorical",
-                c(bm_plasma_cell_percent_at_pre_ld,
-                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day90`)
-                ~ "continuous"),
-              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1
-  ) %>% 
-  bold_labels() %>% add_stat_label() %>%  add_p() %>% 
-  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 90?**")
-```
-
-## Table S5b. Patient characteristics by ANY late ICAHT
-```{r Patient characteristics by grade 3+ late ICAHT}
-cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_90days)) %>%  ######################### Fix evaluable----------
-  select(bm_plasma_cell_percent_at_pre_ld,
-         number_of_prior_lines_of_therapy,
-         number_prior_lines_therapy,
-         # `Days from last bridging to CAR-T infusion`,
-         lenalidomide_exposed_vs_refractory_vs_not_exposed,
-         bortezomib_exposed_vs_refractory_vs_not_exposed,
-         carfilzomib_exposed_vs_refractory_vs_not_exposed,
-         pomalidomide_exposed_vs_refractory_vs_not_exposed,
-         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
-         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
-         "Marrow Cellularity (%) at Day90" = marrow_percent_cellularity_day_90,
-         os_from_infusion_months,
-         age, agecat, male_sex, sex,
-         extramedullary_disease_yes_no, 
-         high_marrow_burden_50_percent, ecog_at_ld, r_iss_at_car_t_infusion, 
-         cytogenetics, cytogenetics_incl_1q,
-         bridging_therapy_yes_no,
-         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
-         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
-         Prior_bcma_therapy,
-         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
-         cytopenia_apheresis, Neutropenia_apheresis,
-         Anemia_apheresis,Thrombocytopenia_apheresis,
-         `cytopenia_-5d`, `Neutropenia_-5d`,
-         `Anemia_-5d`, `Thrombocytopenia_-5d`,
-         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
-         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
-         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
-         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
-         ht_score,
-         any_late_icaht) %>% 
-  tbl_summary(by = any_late_icaht,
-              type = list(
-                c(extramedullary_disease_yes_no,
-                  bm_plasma_cell_percent_at_pre_ld,
-                  cytopenia_apheresis,`cytopenia_-5d`,
-                  cytogenetics, cytogenetics_incl_1q,
-                  bridging_therapy_yes_no,
-                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-                  prior_auto_sct_yes_no,
-                  immuno, proteasome, dara,
-                  doubleref, tripleref, pentaref,
-                  cytopenia_apheresis, Neutropenia_apheresis,
-                  Anemia_apheresis,Thrombocytopenia_apheresis,
-                  `cytopenia_-5d`, `Neutropenia_-5d`,
-                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
-                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
-                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
-                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
-                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
-                  ht_score,
-                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
-                ~ "categorical",
-                c(bm_plasma_cell_percent_at_pre_ld,
-                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day90`)
-                ~ "continuous"),
-              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1
-  ) %>% 
-  bold_labels() %>% add_stat_label() %>%  add_p() %>% 
-  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Late ICAHT**")
-```
-
-## Table S6a. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30
-```{r CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ cytopenia at Day 30}
-tbl1 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(cell_dose_million_cells,
-         CRS_gradecat,
-         day_of_onset_crs_relative_to_infusion,
-         day_of_max_crs_relative_to_infusion,
-         duration_of_crs_days, 
-         ICANS_gradecat,
-         day_of_onset_icans_relative_to_infusion,
-         day_of_max_icans_relative_to_infusion,
-         duration_of_icans_days, 
-         delayed_neuro,
-         parkinsonian_neurotoxicity_yes_no,
-         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
-         delayed_neuro_type,
-         hlh, hlh_hlh_like_toxicities,
-         overall_hlh,
-         gr3_cytopenia_30d) %>% 
-  tbl_summary(by = gr3_cytopenia_30d,
-              type = list(
-                c(day_of_onset_crs_relative_to_infusion,
-                  day_of_max_crs_relative_to_infusion,
-                  duration_of_crs_days,
-                  day_of_onset_icans_relative_to_infusion,
-                  day_of_max_icans_relative_to_infusion,
-                  duration_of_icans_days) ~ "continuous",
-                c(delayed_neuro,
-                  other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
-                  parkinsonian_neurotoxicity_yes_no,
-                  hlh, hlh_hlh_like_toxicities,
-                  overall_hlh) ~ "categorical"),
-              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-    digits = all_continuous() ~ 1,
-    missing = "no") %>% 
-  bold_labels() %>% add_stat_label() %>% add_p() %>% 
-  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
-
-tbl2 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(steroid_use_yes_no, tocilizumab_yes_no, 
-         anakinra_yes_no, gr3_cytopenia_30d) %>% 
-  tbl_summary(by = gr3_cytopenia_30d,
-              type = list(
-    c(steroid_use_yes_no, tocilizumab_yes_no, 
-      anakinra_yes_no) ~ "categorical"),
-    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-    digits = all_continuous() ~ 1) %>% 
-  bold_labels() %>% add_stat_label() %>% add_p()
-
-tbl3 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(#day_30_mrd_by_clono_seq_positive_vs_negative,
-         ORR_30days, CRorbetter_30days,
-         # day30_response_v2, 
-         gr3_cytopenia_30d) %>% 
-  tbl_summary(by = gr3_cytopenia_30d,
-    #           type = list(
-    # c(day_30_mrd_by_clono_seq_positive_vs_negative) ~ "categorical"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>% 
-  bold_labels() %>% add_stat_label() %>% add_p()
-
-# tbl4 <- cart1 %>% 
-#   distinct(pt_identifier, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_30days)) %>% 
-#   filter(day30_response_v2 == "sCR or CR") %>% 
-#   select(day_30_mrd_by_clono_seq_positive_vs_negative, gr3_cytopenia_30d) %>% 
-#   tbl_summary(by =gr3_cytopenia_30d,
-#               type = list(c(day_30_mrd_by_clono_seq_positive_vs_negative) ~ "categorical"),
-#               label = list(day_30_mrd_by_clono_seq_positive_vs_negative ~ "day_30_mrd_by_clono_seq_positive_vs_negative within CR/sCR"),
-#               digits = all_continuous() ~ 1,
-#               missing = "no") %>% 
-#   bold_labels() %>% add_stat_label() %>% add_p()
-
-tbl5 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(#MRD_mon3,
-         ORR_mon3, CRorbetter_mon3,
-         # mon3_response_v2, 
-         gr3_cytopenia_30d) %>% 
-  tbl_summary(by = gr3_cytopenia_30d,
-    #           type = list(
-    # c(MRD_mon3) ~ "categorical"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>% 
-  bold_labels() %>% add_stat_label() %>% add_p()
-
-# tbl6 <- cart1 %>% 
-#   distinct(pt_identifier, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_30days)) %>% 
-#   filter(mon3_response_v2 == "sCR or CR") %>% 
-#   select(MRD_mon3, gr3_cytopenia_30d) %>% 
-#   tbl_summary(by =gr3_cytopenia_30d,
-#               type = list(c(MRD_mon3) ~ "categorical"),
-#               label = list(MRD_mon3 ~ "MRD_mon3 within CR/sCR"),
-#               digits = all_continuous() ~ 1,
-#               missing = "no") %>% 
-#   bold_labels() %>% add_stat_label() %>% add_p()
-
-tbl7 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(best_response, best_ORRcollapsed,
-         gr3_cytopenia_30d) %>% 
-  tbl_summary(by = gr3_cytopenia_30d,
-              #type = list(c(MRD_mon3) ~ "categorical"),
-              label = list(best_response ~ "best response in the first 90 days"),
-              digits = all_continuous() ~ 1,
-              missing = "no") %>% 
-  bold_labels() %>% add_stat_label() %>% add_p()
-
-# tbl8 <- cart1 %>% 
-#   distinct(pt_identifier, .keep_all = TRUE) %>% 
-#   filter(is.na(Not_evaluable_at_30days)) %>% 
-#   filter(best_response == "sCR or CR") %>% 
-#   select(MRDneg_in_best_response, gr3_cytopenia_30d) %>% 
-#   tbl_summary(by =gr3_cytopenia_30d,
-#               type = list(c(MRDneg_in_best_response) ~ "categorical"),
-#               label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
-#               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-#               digits = all_continuous() ~ 1,
-#               missing = "no") %>% 
-#   bold_labels() %>% add_stat_label() %>% add_p()
-
-tbl_stack(list(tbl1, tbl2, tbl3, tbl5, tbl7))
-```
-
-## Table S6b. CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by ANY early ICAHT
-```{r CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy by grade 3+ early ICAHT}
-tbl1 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(cell_dose_million_cells,
-         CRS_gradecat,
-         day_of_onset_crs_relative_to_infusion,
-         day_of_max_crs_relative_to_infusion,
-         duration_of_crs_days, 
-         ICANS_gradecat,
-         day_of_onset_icans_relative_to_infusion,
-         day_of_max_icans_relative_to_infusion,
-         duration_of_icans_days, 
-         delayed_neuro,
-         parkinsonian_neurotoxicity_yes_no,
-         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
-         delayed_neuro_type,
-         hlh, hlh_hlh_like_toxicities,
-         overall_hlh,
-         any_early_icaht) %>% 
-  tbl_summary(by = any_early_icaht,
-              type = list(
-                c(day_of_onset_crs_relative_to_infusion,
-                  day_of_max_crs_relative_to_infusion,
-                  duration_of_crs_days,
-                  day_of_onset_icans_relative_to_infusion,
-                  day_of_max_icans_relative_to_infusion,
-                  duration_of_icans_days) ~ "continuous",
-                c(delayed_neuro,
-                  other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
-                  parkinsonian_neurotoxicity_yes_no,
-                  hlh, hlh_hlh_like_toxicities,
-                  overall_hlh) ~ "categorical"),
-              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-    digits = all_continuous() ~ 1,
-    missing = "no") %>% 
-  bold_labels() %>% add_stat_label() %>% add_p() %>% 
-  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Early ICAHT**")
-
-tbl2 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(steroid_use_yes_no, tocilizumab_yes_no, 
-         anakinra_yes_no, any_early_icaht) %>% 
-  tbl_summary(by = any_early_icaht,
-              type = list(
-    c(steroid_use_yes_no, tocilizumab_yes_no, 
-      anakinra_yes_no) ~ "categorical"),
-    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-    digits = all_continuous() ~ 1) %>% 
-  bold_labels() %>% add_stat_label() %>% add_p()
-
-tbl3 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(#day_30_mrd_by_clono_seq_positive_vs_negative,
-         ORR_30days, CRorbetter_30days,
-         # day30_response_v2, 
-         any_early_icaht) %>% 
-  tbl_summary(by = any_early_icaht,
-    #           type = list(
-    # c(day_30_mrd_by_clono_seq_positive_vs_negative) ~ "categorical"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>% 
-  bold_labels() %>% add_stat_label() %>% add_p()
-
-tbl5 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(#MRD_mon3,
-         ORR_mon3, CRorbetter_mon3,
-         # mon3_response_v2, 
-         any_early_icaht) %>% 
-  tbl_summary(by = any_early_icaht,
-    #           type = list(
-    # c(MRD_mon3) ~ "categorical"),
-    digits = all_continuous() ~ 1,
-    missing = "no") %>% 
-  bold_labels() %>% add_stat_label() %>% add_p()
-
-tbl7 <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
-  select(best_response, best_ORRcollapsed,
-         any_early_icaht) %>% 
-  tbl_summary(by = any_early_icaht,
-              #type = list(c(MRD_mon3) ~ "categorical"),
-              label = list(best_response ~ "best response in the first 90 days"),
-              digits = all_continuous() ~ 1,
-              missing = "no") %>% 
-  bold_labels() %>% add_stat_label() %>% add_p()
-
-tbl_stack(list(tbl1, tbl2, tbl3, tbl5, tbl7))
-```
-
-## Table S8. Details of infections after ide-cel
-Patients can be counted multiple times if multiple infections.
-```{r infection details 30 first days}
+## Details of severe infections after cilta-cel
+```{r severe infection details 30 first days}
 tbl1 <- cilta %>% 
   filter(time_from_infusion_to_infection_days <= 30) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   select(infection_type_bacterial_viral_fungal_parasitic) %>% 
@@
                   type= "level",
-                  level_value = c("Fungal", "Viral")) %>%
+                  level_value = "Fungal") %>%
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = "Viral") %>%
   remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>%
@@
   modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  modify_footnote(update = everything() ~ NA) %>%
   modify_spanning_header(all_stat_cols() ~ "**Infections in the first 30 days**")
@@
   filter(time_from_infusion_to_infection_days <= 30) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   filter(infection_type_bacterial_viral_fungal_parasitic == "Bacterial") %>%
@@
   filter(time_from_infusion_to_infection_days <= 30) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   select(infection_type_bacterial_viral_fungal_parasitic) %>% 
@@
                   type= "level",
-                  level_value = c("Bacterial", "Viral")) %>% 
+                  level_value = "Bacterial") %>% 
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = "Viral") %>% 
   remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
@@
   filter(time_from_infusion_to_infection_days <= 30) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   filter(infection_type_bacterial_viral_fungal_parasitic == "Fungal") %>%
@@
                   type= "level",
-                  level_value = c("Bacterial", "Fungal")) %>% 
+                  level_value = "Bacterial") %>% 
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = "Fungal") %>% 
   remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
@@
   filter(time_from_infusion_to_infection_days <= 30) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   filter(infection_type_bacterial_viral_fungal_parasitic == "Viral") %>%
@@
 
-```{r infection details between 31 - 100 days}
+```{r severe infection details between 31 - 100 days}
 tbl1 <- cilta %>% 
@@
            time_from_infusion_to_infection_days <= 100) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   select(infection_type_bacterial_viral_fungal_parasitic) %>% 
@@
            time_from_infusion_to_infection_days <= 100) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   filter(infection_type_bacterial_viral_fungal_parasitic == "Bacterial") %>%
@@
                   type= "level",
-                  level_value = c("Bacterial", "Viral")) %>% 
+                  level_value = "Bacterial") %>% 
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = "Viral") %>%
   remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
@@
                   type= "level",
-                  level_value = c("Bacterial", "Fungal")) %>% 
+                  level_value = "Bacterial") %>% 
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = "Fungal") %>%
   remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
@@
            time_from_infusion_to_infection_days <= 100) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   filter(infection_type_bacterial_viral_fungal_parasitic == "Viral") %>%
@@
 
-tbl_stack(list(tbl1, tbl1_1, #tbl2,# tbl2_1, 
+tbl_stack(list(tbl1, tbl1_1, tbl2,# tbl2_1, 
                tbl3, tbl3_1))
@@
 
-```{r infection details after 100 days}
+```{r severe infection details after 100 days}
 tbl1 <- cilta %>% 
   filter(time_from_infusion_to_infection_days > 100) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   select(infection_type_bacterial_viral_fungal_parasitic) %>% 
@@
   filter(time_from_infusion_to_infection_days > 100) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   filter(infection_type_bacterial_viral_fungal_parasitic == "Bacterial") %>%
@@
 
-# tbl2 <- cilta %>% 
-#   filter(time_from_infusion_to_infection_days > 100) %>% 
-#   select(infection_type_bacterial_viral_fungal_parasitic) %>% 
-#   tbl_summary() %>%
-#   remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
-#                   type= "level",
-#                   level_value = c("Bacterial", "Viral")) %>% 
-#   remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>% 
-#   add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
-#   bold_levels() %>%
-#   modify_column_indent(columns = label, undo = TRUE)
-# 
+tbl2 <- cilta %>%
+  filter(time_from_infusion_to_infection_days > 100) %>%
+  select(infection_type_bacterial_viral_fungal_parasitic) %>%
+  tbl_summary() %>%
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = "Bacterial") %>% 
+  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
+                  type= "level",
+                  level_value = "Viral") %>%
+  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>%
+  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
+  bold_levels() %>%
+  modify_column_indent(columns = label, undo = TRUE)
+
 # tbl2_1 <- cilta %>% 
@@
   filter(time_from_infusion_to_infection_days > 100) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   select(infection_type_bacterial_viral_fungal_parasitic) %>% 
@@
   filter(time_from_infusion_to_infection_days > 100) %>% 
+  filter(any_sevinfection == "Yes") %>% 
   filter(infection_type_bacterial_viral_fungal_parasitic == "Viral") %>%
@@
 ```
-
-## Table S9. Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
-```{r Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy}
-cilta %>% 
-  arrange(pt_identifier, desc(any_infection)) %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(os_from_infusion_months, age, agecat, male_sex, sex,
-         extramedullary_disease_yes_no, 
-         high_marrow_burden_50_percent, ecog_at_ld, 
-         r_iss_at_car_t_infusion, 
-         cytogenetics, cytogenetics_incl_1q,
-         deletion_17p_prior_to_car_t_infusion_yes_no,
-         t_4_14_prior_to_car_t_infusion_yes_no,
-         t_14_16_prior_to_car_t_infusion_yes_no, gain_amp1q21,
-         bridging_therapy_yes_no,
-         number_prior_lines_therapy,
-         number_of_prior_lines_of_therapy,
-         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
-         Prior_bcma_therapy,
-         immuno, proteasome, dara, doubleref, tripleref, pentaref,
-         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
-         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-         # `Days from last bridging to CAR-T infusion`,
-         cell_dose_million_cells,
-         need_for_g_csf_post_infus_yes_1_no_0,
-         cd34_stem_cell_boost_yes_1_no_0,
-         need_for_ivig_yes_1_no_0,
-
-         CRS_gradecat, ICANS_gradecat,
-         delayed_neuro,
-         parkinsonian_neurotoxicity_yes_no,
-         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
-         delayed_neuro_type,
-         hlh, hlh_hlh_like_toxicities,
-         overall_hlh,
-         steroid_use_yes_no, 
-         tocilizumab_yes_no, anakinra_yes_no,
-         bridging_therapy_yes_no, any_infection) %>% 
-  tbl_summary(by= any_infection, 
-              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-              type = list(all_dichotomous() ~ "categorical", 
-                          number_of_prior_lines_of_therapy ~ "continuous")) %>%
-  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
-  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Any infection**")
-
-cilta %>% 
-  arrange(pt_identifier, desc(any_infection), desc(any_sevinfection)) %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(os_from_infusion_months, age, agecat, male_sex, sex,
-         extramedullary_disease_yes_no, 
-         high_marrow_burden_50_percent, ecog_at_ld, 
-         r_iss_at_car_t_infusion, 
-         cytogenetics, cytogenetics_incl_1q,
-         deletion_17p_prior_to_car_t_infusion_yes_no,
-         t_4_14_prior_to_car_t_infusion_yes_no,
-         t_14_16_prior_to_car_t_infusion_yes_no, gain_amp1q21,
-         bridging_therapy_yes_no,
-         number_prior_lines_therapy,
-         number_of_prior_lines_of_therapy,
-         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
-         Prior_bcma_therapy,
-         immuno, proteasome, dara, doubleref, tripleref, pentaref,
-         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
-         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
-         # `Days from last bridging to CAR-T infusion`,
-         cell_dose_million_cells,
-         need_for_g_csf_post_infus_yes_1_no_0,
-         cd34_stem_cell_boost_yes_1_no_0,
-         need_for_ivig_yes_1_no_0,
-
-         CRS_gradecat, ICANS_gradecat,
-         delayed_neuro,
-         parkinsonian_neurotoxicity_yes_no,
-         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
-         delayed_neuro_type,
-         hlh, hlh_hlh_like_toxicities,
-         overall_hlh,
-         steroid_use_yes_no, 
-         tocilizumab_yes_no, anakinra_yes_no,
-         bridging_therapy_yes_no, any_sevinfection) %>% 
-  tbl_summary(by=any_sevinfection, 
-              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-              type = list(all_dichotomous() ~ "categorical", 
-                          number_of_prior_lines_of_therapy ~ "continuous")) %>%
-  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
-  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
-```
-
-## Table S10 A-B. Patients with infections by cell counts and immunoglobulin levels
-```{r Patients with infections by cell counts and immunoglobulin levels}
-cilta %>%
-  arrange(pt_identifier, desc(any_infection)) %>% 
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(ig_g_day_5, ig_a_day_5, ig_m_day_5,
-         wbc_day_5, anc_day_5_k_ul,
-         # `Eos day -5 (k/ul)`, `Monos day -5 (k/ul)`, 
-         # `CD3 apheresis`, `CD56 apheresis`, 
-         cd4_apheresis, cd8_apheresis,
-         cd19_apheresis, 
-         ig_g_day_90, ig_a_day_90, ig_m_day_90,
-         wbc_day_90, anc_day_90,
-         # `Eos day +90`, `Monos day +90`,
-         # `CD3 day +90`, `CD56 day +90`, 
-         cd4_day_90, cd8_day_90,
-         cd19_day_90, ht_score,
-         any_infection) %>% 
-  tbl_summary(by = any_infection,
-              type = list(-ht_score ~ "continuous"),
-              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1) %>% 
-  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
-  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Any infection**")
-
-cilta %>% 
-  arrange(pt_identifier, desc(any_infection), desc(any_sevinfection)) %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(ig_g_day_5, ig_a_day_5, ig_m_day_5,
-         wbc_day_5, anc_day_5_k_ul,
-         # `Eos day -5 (k/ul)`, `Monos day -5 (k/ul)`, 
-         # `CD3 apheresis`, `CD56 apheresis`, 
-         cd4_apheresis, cd8_apheresis,
-         cd19_apheresis, 
-         ig_g_day_90, ig_a_day_90, ig_m_day_90,
-         wbc_day_90, anc_day_90,
-         # `Eos day +90`, `Monos day +90`,
-         # `CD3 day +90`, `CD56 day +90`, 
-         cd4_day_90, cd8_day_90,
-         cd19_day_90, ht_score,
-         any_sevinfection) %>% 
-  tbl_summary(by = any_sevinfection,
-              type = list(-ht_score ~ "continuous"),
-              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1) %>% 
-  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
-  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
-  modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
-```
-
-## Table S10 C-D. Immunoglobulin levels excluding patients with that type of myeloma 
-(myeloma_involved_heavy_chain != "Igg")
-```{r Immunoglobulin levels excluding patients with that type of myeloma}
-cilta %>% 
-  filter(myeloma_involved_heavy_chain != "Igg" | is.na(myeloma_involved_heavy_chain)) %>% 
-  arrange(pt_identifier, desc(any_infection)) %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(ig_g_day_5, ig_g_day_30,
-         ig_g_day_90, any_infection) %>% 
-  tbl_summary(by = any_infection,
-              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1
-  ) %>% 
-  add_p() %>% bold_labels() %>% add_stat_label() %>% 
-  add_overall() %>% 
-  modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Any infection**")
-
-cilta %>% 
-  filter(myeloma_involved_heavy_chain != "Igg" | is.na(myeloma_involved_heavy_chain)) %>% 
-  arrange(pt_identifier, desc(any_infection), desc(any_sevinfection)) %>%
-  distinct(pt_identifier, .keep_all = TRUE) %>% 
-  select(ig_g_day_5, ig_g_day_30,
-         ig_g_day_90, any_sevinfection) %>% 
-  tbl_summary(by = any_sevinfection,
-              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
-              digits = all_continuous() ~ 1
-  ) %>% 
-  add_p() %>% bold_labels() %>% add_stat_label() %>% 
-  add_overall() %>% 
-  modify_footnote(update = everything() ~ NA) %>%
-  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
-```
-
-### Figures
-```{r fig_dat}
-fig_dat <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE)
-```
-
-## Figure 1. Consort diagram
-This will help for creating the figure. It shows the patients who had PD or died with info of the event.
-```{r}
-fig_dat %>% 
-  mutate(pfs_from_infusion_days = 
-           interval(
-             start = date_of_car_t_infusion, 
-             end = pfs_date)/
-           duration(n=1, units = "days")) %>% 
-  filter(os_event == 1 | pfs_event == 1) %>% 
-  mutate(event_at = case_when(
-    !is.na(date_of_pd) & pfs_from_infusion_months < 1        ~ "had pd",
-    !is.na(date_of_pd) & pfs_from_infusion_months < 3        ~ "had pd",
-    !is.na(date_of_pd) & pfs_from_infusion_months < 6        ~ "had pd",
-    !is.na(date_of_pd) & pfs_from_infusion_months < 12       ~ "had pd",
-    os_event == 1 & pfs_from_infusion_months < 1        ~ "died",
-    os_event == 1 & pfs_from_infusion_months < 3        ~ "died",
-    os_event == 1 & pfs_from_infusion_months < 6        ~ "died",
-    os_event == 1 & pfs_from_infusion_months < 12       ~ "died",
-  )) %>% 
-  mutate(phrase = paste("Patient", pt_identifier, event_at, "at day", pfs_from_infusion_days)
-  ) %>% 
-  arrange(pfs_from_infusion_days) %>% 
-  select(phrase, `cause of death` = cause_of_death_myeloma_toxicitiy_unrelated,
-         `CRS grade` = max_crs_grade_0_5, max_icans, delayed_neuro, `delayed neurotoxicity` = delayed_neuro_type, parkinsonian_neurotoxicity_yes_no, what_non_parkinsonian_neurotoxicity, infection_type_bacterial_viral_fungal_parasitic,  `infection details` = infection_type_details)
-
-a <- fig_dat %>% 
-  mutate(pfs_from_infusion_days = 
-           interval(
-             start = date_of_car_t_infusion, 
-             end = pfs_date)/
-           duration(n=1, units = "days")) %>% 
-  filter(os_event == 1 | pfs_event == 1) %>% 
-  mutate(event_at = case_when(
-    !is.na(date_of_pd) & pfs_from_infusion_months < 1        ~ "had pd",
-    !is.na(date_of_pd) & pfs_from_infusion_months < 3        ~ "had pd",
-    !is.na(date_of_pd) & pfs_from_infusion_months < 6        ~ "had pd",
-    !is.na(date_of_pd) & pfs_from_infusion_months < 12       ~ "had pd",
-    os_event == 1 & pfs_from_infusion_months < 1        ~ "died",
-    os_event == 1 & pfs_from_infusion_months < 3        ~ "died",
-    os_event == 1 & pfs_from_infusion_months < 6        ~ "died",
-    os_event == 1 & pfs_from_infusion_months < 12       ~ "died",
-  )) %>% 
-  filter(event_at == "died") %>% 
-  arrange(pfs_from_infusion_days) %>% 
-  select(pt_identifier, event_at, pfs_from_infusion_days, `cause of death` = cause_of_death_myeloma_toxicitiy_unrelated,
-         `CRS grade` = max_crs_grade_0_5, max_icans, delayed_neuro, `delayed neurotoxicity` = delayed_neuro_type, parkinsonian_neurotoxicity_yes_no, what_non_parkinsonian_neurotoxicity, infection_type_bacterial_viral_fungal_parasitic,  `infection details` = infection_type_details)
-write_csv(a, paste0(here::here(), "/cilta_cel/cause of death cilta-cel data.csv"))
-```
-
-## Figure S1. Inflammatory markers after ide-cel
-
-```{r Figure 2. Inflammatory markers after ide-cel, fig.height=12}
-LDH <- fig_dat %>% 
-  select(pt_identifier, starts_with("ldh_")) %>% 
-  pivot_longer(cols = -c(pt_identifier)) %>% 
-  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
-         day = case_when(
-           str_detect(name, "apheresis")            ~ "-28",
-           str_detect(name, "pretreatment")         ~ "-28",
-           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
-         ), 
-         day = case_when(
-           day == 5                                 ~ "-5",
-           TRUE                                     ~ day
-         ),
-         day = factor(day, levels = c("-28", "-5", "0", 
-                                      "7", "14", "21", "30", "90", "180"))) %>% 
-  ggplot(aes(x=day, y=value)) + 
-  geom_boxplot() + 
-  xlab("Days") + ylab("LDH represented with a log2 scale") + 
-  theme_classic() + ggtitle("LDH") + 
-  scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 5 
-                     # aes(label = paste0("p = ", ..p.format..))
-  #                  aes(
-  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
-  )
-
-# cart1$`Ferritin day +7`[cart1$`Ferritin day +7`==">33511"] <- 33511
-# cart1$`Ferritin day +7` <- as.numeric(cart1$`Ferritin day +7`)
-Ferritin <- fig_dat %>% 
-  select(pt_identifier, starts_with("ferritin_")) %>% 
-  pivot_longer(cols = -c(pt_identifier)) %>% 
-  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
-         day = case_when(
-           str_detect(name, "apheresis")            ~ "-28",
-           str_detect(name, "pretreatment")         ~ "-28",
-           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
-         ), 
-         day = case_when(
-           day == 5                                 ~ "-5",
-           TRUE                                     ~ day
-         ),
-         day = factor(day, levels = c("-28", "-5", "0", 
-                                      "7", "14", "21", "30", "90", "180"))) %>% 
-  ggplot(aes(x=day, y=value)) + 
-  geom_boxplot() + 
-  xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
-  theme_classic() + ggtitle("Ferritin") + 
-  scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 5 
-                     # aes(label = paste0("p = ", ..p.format..))
-  #                  aes(
-  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
-  )
-
-# cart1$`CRP Pre-Leukapheresis`[cart1$`CRP Pre-Leukapheresis`=="<0.03"] <- 0.07
-# cart1$`CRP Pre-Leukapheresis` <- as.numeric(cart1$`CRP Pre-Leukapheresis`)
-# cart1$`CRP day +14`[cart1$`CRP day +14`=="<0.03"] <- 0.07
-# cart1$`CRP day +14` <- as.numeric(cart1$`CRP day +14`)
-# cart1$`CRP day +21`[cart1$`CRP day +21`=="<0.03"] <- 0.07
-# cart1$`CRP day +21` <- as.numeric(cart1$`CRP day +21`)
-# cart1$`CRP day +30`[cart1$`CRP day +30`=="<0.03"] <- 0.07
-# cart1$`CRP day +30` <- as.numeric(cart1$`CRP day +30`)
-CRP <- fig_dat %>% 
-  select(pt_identifier, starts_with("crp_")) %>% 
-  pivot_longer(cols = -c(pt_identifier)) %>% 
-  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
-         day = case_when(
-           str_detect(name, "apheresis")            ~ "-28",
-           str_detect(name, "pretreatment")         ~ "-28",
-           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
-         ), 
-         day = case_when(
-           day == 5                                 ~ "-5",
-           TRUE                                     ~ day
-         ),
-         day = factor(day, levels = c("-28", "-5", "0", 
-                                      "7", "14", "21", "30", "90", "180"))) %>% 
-  ggplot(aes(x=day, y=value)) + 
-  geom_boxplot() + 
-  xlab("Days") + ylab("CRP represented with a log2 scale") + 
-  theme_classic() + ggtitle("CRP") + 
-  scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 5 
-                     # aes(label = paste0("p = ", ..p.format..))
-  #                  aes(
-  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
-  )
-
-(LDH) /
-(Ferritin) /
-(CRP)+
-plot_annotation(tag_levels = "A")
-```
-
-## Figure 2. Cellular and humoral immune reconstitution after cilta-cel
-```{r timeserie, fig.width=12, fig.height=12}
-# WBC
-val <- fig_dat %>% reframe(wbc_apheresis = MedianCI(wbc_apheresis, conf.level = 0.95, na.rm = TRUE),
-                  wbc_day_5 = MedianCI(wbc_day_5, conf.level = 0.95, na.rm = TRUE),
-                  wbc_day_0_k_u_l = MedianCI(wbc_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE),
-                  wbc_day_7 = MedianCI(wbc_day_7, conf.level = 0.95, na.rm = TRUE),
-                  wbc_day_14 = MedianCI(wbc_day_14, conf.level = 0.95, na.rm = TRUE),
-                  wbc_day_21 = MedianCI(wbc_day_21, conf.level = 0.95, na.rm = TRUE),
-                  wbc_day_30 = MedianCI(wbc_day_30, conf.level = 0.95, na.rm = TRUE),
-                  wbc_day_90 = MedianCI(wbc_day_90, conf.level = 0.95, na.rm = TRUE),
-                  wbc_day_180 = MedianCI(wbc_day_180, conf.level = 0.95, na.rm = TRUE))
-timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
-WBC_fig <-
-  data.frame(timepoints,
-             t(val))
-
-WBC_fig <-
-  WBC_fig %>%
-  ggplot(aes(x = timepoints, y = X1, group = 1)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median WBC") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  ) #+ ylim(0, 6)
-
-# ANC
-val <- fig_dat %>% reframe(anc_apheresis = MedianCI(anc_apheresis, conf.level = 0.95, na.rm = TRUE),
-                  anc_day_5_k_ul = MedianCI(anc_day_5_k_ul, conf.level = 0.95, na.rm = TRUE),
-                  anc_day_0_k_u_l = MedianCI(anc_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE),
-                  anc_day_7 = MedianCI(anc_day_7, conf.level = 0.95, na.rm = TRUE),
-                  anc_day_14 = MedianCI(anc_day_14, conf.level = 0.95, na.rm = TRUE),
-                  anc_day_21 = MedianCI(anc_day_21, conf.level = 0.95, na.rm = TRUE),
-                  anc_day_30 = MedianCI(anc_day_30, conf.level = 0.95, na.rm = TRUE),
-                  anc_day_90 = MedianCI(anc_day_90, conf.level = 0.95, na.rm = TRUE),
-                  anc_day_180 = MedianCI(anc_day_180, conf.level = 0.95, na.rm = TRUE))
-timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
-ANC_fig <-
-  data.frame(timepoints,
-             t(val))
-
-ANC_fig <- ANC_fig %>% 
-  ggplot(aes(x = timepoints, y = X1, group = 1)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median ANC") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  ) #+ ylim(0, 6)
-
-# HB
-val <- fig_dat %>% reframe(hb_apheresis = MedianCI(hb_apheresis, conf.level = 0.95, na.rm = TRUE),
-                  hb_day_5 = MedianCI(hb_day_5, conf.level = 0.95, na.rm = TRUE),
-                  hb_day_0_k_u_l = MedianCI(hb_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE),
-                  hb_day_7 = MedianCI(hb_day_7, conf.level = 0.95, na.rm = TRUE),
-                  hb_day_14 = MedianCI(hb_day_14, conf.level = 0.95, na.rm = TRUE),
-                  hb_day_21 = MedianCI(hb_day_21, conf.level = 0.95, na.rm = TRUE),
-                  hb_day_30 = MedianCI(hb_day_30, conf.level = 0.95, na.rm = TRUE),
-                  hb_day_90 = MedianCI(hb_day_90, conf.level = 0.95, na.rm = TRUE),
-                  hb_day_180 = MedianCI(hb_day_180, conf.level = 0.95, na.rm = TRUE))
-timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
-Hb_fig <-
-  data.frame(timepoints,
-             t(val))
-
-Hb_fig <- Hb_fig %>% 
-  ggplot(aes(x = timepoints, y = X1, group = 1)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median Hb") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  ) # +ylim(7.5, 12)
-
-# ALC
-val <- fig_dat %>% reframe(alc_apheresis = MedianCI(alc_apheresis, conf.level = 0.95, na.rm = TRUE),
-                  alc_day_5_k_ul = MedianCI(alc_day_5_k_ul, conf.level = 0.95, na.rm = TRUE),
-                  alc_day_0_k_u_l = MedianCI(alc_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE),
-                  alc_day_7 = MedianCI(alc_day_7, conf.level = 0.95, na.rm = TRUE),
-                  alc_day_14 = MedianCI(alc_day_14, conf.level = 0.95, na.rm = TRUE),
-                  alc_day_21 = MedianCI(alc_day_21, conf.level = 0.95, na.rm = TRUE),
-                  alc_day_30 = MedianCI(alc_day_30, conf.level = 0.95, na.rm = TRUE),
-                  alc_day_90 = MedianCI(alc_day_90, conf.level = 0.95, na.rm = TRUE),
-                  alc_day_180 = MedianCI(alc_day_180, conf.level = 0.95, na.rm = TRUE))
-timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
-ALC_fig <-
-  data.frame(timepoints,
-             t(val))
-
-ALC_fig <- ALC_fig %>% 
-  ggplot(aes(x = timepoints, y = X1, group = 1)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median ALC") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  ) # + ylim(0, 1.1)
-
-# Plt
-val <- fig_dat %>% reframe(plt_apheresis = MedianCI(plt_apheresis, conf.level = 0.95, na.rm = TRUE),
-                  plt_day_5_k_ul = MedianCI(plt_day_5_k_ul, conf.level = 0.95, na.rm = TRUE),
-                  plt_day_0_k_u_l = MedianCI(plt_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE),
-                  plt_day_7 = MedianCI(plt_day_7, conf.level = 0.95, na.rm = TRUE),
-                  plt_day_14 = MedianCI(plt_day_14, conf.level = 0.95, na.rm = TRUE),
-                  plt_day_21 = MedianCI(plt_day_21, conf.level = 0.95, na.rm = TRUE),
-                  plt_day_30 = MedianCI(plt_day_30, conf.level = 0.95, na.rm = TRUE),
-                  plt_day_90 = MedianCI(plt_day_90, conf.level = 0.95, na.rm = TRUE),
-                  plt_day_180 = MedianCI(plt_day_180, conf.level = 0.95, na.rm = TRUE))
-timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180)
-Plt_fig <-
-  data.frame(timepoints,
-             t(val))
-
-Plt_fig <- Plt_fig %>% 
-  ggplot(aes(x = timepoints, y = X1, group = 1)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median Plt") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180),
-    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180")
-  ) # + ylim(20, 170)
-
-# IgG
-timepoints2 <- c(-28, -5, 30, 90, 180)
-val <- fig_dat %>% reframe(ig_g_apheresis = MedianCI(ig_g_apheresis, conf.level = 0.95, na.rm = TRUE),
-                  ig_g_day_5 = MedianCI(ig_g_day_5, conf.level = 0.95, na.rm = TRUE),
-                  ig_g_day_30 = MedianCI(ig_g_day_30, conf.level = 0.95, na.rm = TRUE),
-                  ig_g_day_90 = MedianCI(ig_g_day_90, conf.level = 0.95, na.rm = TRUE),
-                  ig_g_day_180 = MedianCI(ig_g_day_180, conf.level = 0.95, na.rm = TRUE))
-IgG_fig <-
-  data.frame(timepoints2,
-             t(val))
-
-IgG_fig <- IgG_fig %>% 
-  ggplot(aes(x = timepoints2, y = X1, group = 1)) + 
-  geom_line(col = "blue") +
-  xlab("Days relative to infusion") + 
-  ylab("Median IgG") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, -5, 30, 90, 180),
-    labels = c("Apheresis", "-5", "30", "90", "180"))# + 
-  # ylim(0, 2000)
-
-# CD4
-timepoints3 <- c(-28, 30, 90, 180)
-val <- fig_dat %>% reframe(cd4_apheresis = MedianCI(cd4_apheresis, conf.level = 0.95, na.rm = TRUE),
-                  cd4_day_30 = MedianCI(cd4_day_30, conf.level = 0.95, na.rm = TRUE),
-                  cd4_day_90 = MedianCI(cd4_day_90, conf.level = 0.95, na.rm = TRUE),
-                  cd4_day_180 = MedianCI(cd4_day_180, conf.level = 0.95, na.rm = TRUE))
-CD4_fig <-
-  data.frame(timepoints3,
-             t(val))
-
-CD4_fig <- CD4_fig %>% 
-  ggplot(aes(x = timepoints3, y = X1, group = 1)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median CD4") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, 30, 90, 180),
-    labels = c("Apheresis", "30", "90", "180")
-  )
-
-#CD8
-timepoints3 <- c(-28, 30, 90, 180)
-val <- fig_dat %>% reframe(cd8_apheresis = MedianCI(cd8_apheresis, conf.level = 0.95, na.rm = TRUE),
-                  cd8_day_30 = MedianCI(cd8_day_30, conf.level = 0.95, na.rm = TRUE),
-                  cd8_day_90 = MedianCI(cd8_day_90, conf.level = 0.95, na.rm = TRUE),
-                  cd8_day_180 = MedianCI(cd8_day_180, conf.level = 0.95, na.rm = TRUE))
-CD8_fig <-
-  data.frame(timepoints3,
-             t(val))
-
-CD8_fig <- CD8_fig %>% 
-  ggplot(aes(x = timepoints3, y = X1, group = 1)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median CD8") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, 30, 90, 180),
-    labels = c("Apheresis", "30", "90", "180")
-  )
-
-#CD19
-timepoints3 <- c(-28, 30, 90, 180)
-val <- fig_dat %>% reframe(cd19_apheresis = MedianCI(cd19_apheresis, conf.level = 0.95, na.rm = TRUE),
-                  cd19_day_30 = MedianCI(cd19_day_30, conf.level = 0.95, na.rm = TRUE),
-                  cd19_day_90 = MedianCI(cd19_day_90, conf.level = 0.95, na.rm = TRUE),
-                  cd19_day_180 = MedianCI(cd19_day_180, conf.level = 0.95, na.rm = TRUE))
-CD19_fig <-
-  data.frame(timepoints3,
-             t(val))
-
-CD19_fig <- CD19_fig %>% 
-  ggplot(aes(x = timepoints3, y = X1, group = 1)) + 
-  geom_line(col = "blue") + 
-  xlab("Days relative to infusion") + 
-  ylab("Median CD19") + 
-  theme_classic() + 
-  geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) + 
-  scale_x_continuous(
-    breaks = c(-28, 30, 90, 180),
-    labels = c("Apheresis", "30", "90", "180")
-  )
-
-(WBC_fig | ANC_fig | CD4_fig) /
-  (Hb_fig | ALC_fig | CD8_fig) /
-  (Plt_fig | IgG_fig | CD19_fig) +
-  plot_annotation(tag_levels = "A")
-```
-<br>
-
-<!-- Aggregated median -->
-<!-- ```{r timeserie aggreagate med, fig.width=12, fig.height=12} -->
-<!-- fig_dat <- cilta %>%  -->
-<!--   distinct(pt_identifier, .keep_all = TRUE) -->
-
-<!-- timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180) -->
-<!-- WBC_agg <- fig_dat %>%  -->
-<!--   select(site, starts_with("wbc_")) %>%  -->
-<!--   group_by(site) %>%  -->
-<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
-<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
-<!--   ungroup() %>% select(-site) %>%  -->
-<!--   group_by(type) %>%  -->
-<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
-<!--   ungroup() %>%  -->
-<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
-<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
-<!--   mutate(timepoints = timepoints) %>%  -->
-<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
-<!--   geom_line(col = "blue") +  -->
-<!--   xlab("Days relative to infusion") +  -->
-<!--   ylab("Median WBC") +  -->
-<!--   theme_classic() +  -->
-<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
-<!--   scale_x_continuous( -->
-<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
-<!--     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180") -->
-<!--   ) -->
-
-<!-- ANC_agg <- fig_dat %>%  -->
-<!--   select(site, starts_with("anc_"), -anc_0_75_x_10_9_l_0_75_k_u_l) %>%  -->
-<!--   group_by(site) %>%  -->
-<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
-<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
-<!--   ungroup() %>% select(-site) %>%  -->
-<!--   group_by(type) %>%  -->
-<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
-<!--   ungroup() %>%  -->
-<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
-<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
-<!--   mutate(timepoints = timepoints) %>%  -->
-<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
-<!--   geom_line(col = "blue") +  -->
-<!--   xlab("Days relative to infusion") +  -->
-<!--   ylab("Median ANC") +  -->
-<!--   theme_classic() +  -->
-<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
-<!--   scale_x_continuous( -->
-<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
-<!--     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180") -->
-<!--   )  -->
-
-<!-- Hb_agg <- fig_dat %>%  -->
-<!--   select(site, starts_with("hb_")) %>%  -->
-<!--   group_by(site) %>%  -->
-<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
-<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
-<!--   ungroup() %>% select(-site) %>%  -->
-<!--   group_by(type) %>%  -->
-<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
-<!--   ungroup() %>%  -->
-<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
-<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
-<!--   mutate(timepoints = timepoints) %>%  -->
-<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
-<!--   geom_line(col = "blue") +  -->
-<!--   xlab("Days relative to infusion") +  -->
-<!--   ylab("Median Hb") +  -->
-<!--   theme_classic() +  -->
-<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
-<!--   scale_x_continuous( -->
-<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
-<!--     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180") -->
-<!--   )  -->
-
-<!-- ALC_agg <- fig_dat %>%  -->
-<!--   select(site, starts_with("alc_"), -alc_0_3_x_10_9_l_0_3k_u_l) %>%  -->
-<!--   group_by(site) %>%  -->
-<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
-<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
-<!--   ungroup() %>% select(-site) %>%  -->
-<!--   group_by(type) %>%  -->
-<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
-<!--   ungroup() %>%  -->
-<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
-<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
-<!--   mutate(timepoints = timepoints) %>%  -->
-<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
-<!--   geom_line(col = "blue") +  -->
-<!--   xlab("Days relative to infusion") +  -->
-<!--   ylab("Median ALC") +  -->
-<!--   theme_classic() +  -->
-<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
-<!--   scale_x_continuous( -->
-<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
-<!--     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180") -->
-<!--   )  -->
-
-<!-- Plt_agg <- fig_dat %>%  -->
-<!--   select(site, starts_with("plt_"), -c(starts_with("plt_transfusion"))) %>%  -->
-<!--   group_by(site) %>%  -->
-<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
-<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
-<!--   ungroup() %>% select(-site) %>%  -->
-<!--   group_by(type) %>%  -->
-<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
-<!--   ungroup() %>%  -->
-<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
-<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
-<!--   mutate(timepoints = timepoints) %>%  -->
-<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
-<!--   geom_line(col = "blue") +  -->
-<!--   xlab("Days relative to infusion") +  -->
-<!--   ylab("Median Plt") +  -->
-<!--   theme_classic() +  -->
-<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
-<!--   scale_x_continuous( -->
-<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
-<!--     labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "90", "180") -->
-<!--   ) -->
-
-<!-- timepoints2 <- c(-28, -5, 30, 90, 180) -->
-<!-- IgG_agg <- fig_dat %>%  -->
-<!--   select(site, ig_g_apheresis, starts_with("ig_g_day")) %>%  -->
-<!--   group_by(site) %>%  -->
-<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
-<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
-<!--   ungroup() %>% select(-site) %>%  -->
-<!--   group_by(type) %>%  -->
-<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
-<!--   ungroup() %>%  -->
-<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
-<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
-<!--   mutate(timepoints = timepoints2) %>%  -->
-<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
-<!--   geom_line(col = "blue") +  -->
-<!--   xlab("Days relative to infusion") +  -->
-<!--   ylab("Median Plt") +  -->
-<!--   theme_classic() +  -->
-<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
-<!--   scale_x_continuous( -->
-<!--     breaks = c(-28, -5, 0, 30, 90, 180), -->
-<!--     labels = c("Apheresis", "-5", "0", "30", "90", "180") -->
-<!--   ) -->
-
-<!-- timepoints3 <- c(-28, 30, 90, 180) -->
-<!-- CD4_fig <- fig_dat %>%  -->
-<!--   select(site, starts_with("cd4_")) %>%  -->
-<!--   group_by(site) %>%  -->
-<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
-<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
-<!--   ungroup() %>% select(-site) %>%  -->
-<!--   group_by(type) %>%  -->
-<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
-<!--   ungroup() %>%  -->
-<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
-<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
-<!--   mutate(timepoints = timepoints3) %>%  -->
-<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
-<!--   geom_line(col = "blue") +  -->
-<!--   xlab("Days relative to infusion") +  -->
-<!--   ylab("Median CD4") +  -->
-<!--   theme_classic() +  -->
-<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
-<!--   scale_x_continuous( -->
-<!--     breaks = c(-28, 30, 90, 180), -->
-<!--     labels = c("Apheresis", "30", "90", "180") -->
-<!--   ) -->
-<!-- CD8_fig <- fig_dat %>%  -->
-<!--   select(site, starts_with("cd8_")) %>%  -->
-<!--   group_by(site) %>%  -->
-<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
-<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
-<!--   ungroup() %>% select(-site) %>%  -->
-<!--   group_by(type) %>%  -->
-<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
-<!--   ungroup() %>%  -->
-<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
-<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
-<!--   mutate(timepoints = timepoints3) %>%  -->
-<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
-<!--   geom_line(col = "blue") +  -->
-<!--   xlab("Days relative to infusion") +  -->
-<!--   ylab("Median CD8") +  -->
-<!--   theme_classic() +  -->
-<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
-<!--   scale_x_continuous( -->
-<!--     breaks = c(-28, 30, 90, 180), -->
-<!--     labels = c("Apheresis", "30", "90", "180") -->
-<!--   ) -->
-<!-- CD19_fig <- fig_dat %>%  -->
-<!--   select(site, starts_with("cd19_")) %>%  -->
-<!--   group_by(site) %>%  -->
-<!--   reframe(across(.cols = everything(), \(x) MedianCI(x, na.rm = TRUE))) %>%  -->
-<!--   mutate(type = rep(c("Median", "lwr.ci", "upr.ci"), 5), .before = 1) %>%  -->
-<!--   ungroup() %>% select(-site) %>%  -->
-<!--   group_by(type) %>%  -->
-<!--   summarise(across(.cols = everything(), list(median = median) , na.rm = TRUE)) %>%  -->
-<!--   ungroup() %>%  -->
-<!--   pivot_longer(cols = -type, names_to = 'Type') %>%  -->
-<!--   pivot_wider(names_from = type, values_from = value) %>%  -->
-<!--   mutate(timepoints = timepoints3) %>%  -->
-<!--   ggplot(aes(x = timepoints, y = Median)) +  -->
-<!--   geom_line(col = "blue") +  -->
-<!--   xlab("Days relative to infusion") +  -->
-<!--   ylab("Median CD19") +  -->
-<!--   theme_classic() +  -->
-<!--   geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) +  -->
-<!--   scale_x_continuous( -->
-<!--     breaks = c(-28, 30, 90, 180), -->
-<!--     labels = c("Apheresis", "30", "90", "180") -->
-<!--   ) -->
-
-<!-- (WBC_agg | ANC_agg | CD4_fig) / -->
-<!--   (Hb_agg | ALC_agg | CD8_fig) / -->
-<!--   (Plt_agg | IgG_agg | CD19_fig) + -->
-<!--   plot_annotation(tag_levels = "A") -->
-<!-- ``` -->
-
-<!-- <span style="color:blue">**IgG I need to fix the other 109**</span>  -->
-
-<!-- Values less than the limit of detection (<109) were considered to be 77 which is the lower limit of detection divided by the square root of 2.
-One patient had an IgG day 0 value of <320.
-As this is above the limit of detection, I used the midway point between 320 and the lower limit of detection -- 214 -- as the value instead of <320.
--->
-
-<br>
-
-## Figure 3. Cytopenias over time
-
-```{r Figure 4. Cytopenias over time, fig.width=12, fig.height=7}
-# fig_dat %>% 
-#   select(PT,
-#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
-#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
-#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
-#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
-#   ) %>% 
-#   pivot_longer(cols = `gr3_Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
-#   group_by(name, value) %>% 
-#   filter(!is.na(value)) %>% 
-#   summarise(count=n()) %>% 
-#   mutate(perc=(count/sum(count)*100)
-#   ) %>% 
-#   separate("name", into = c("gr3", "name", "day"), sep = "_") %>% 
-#   filter(value == "Yes") %>% 
-#   # unite(time, c("day":"me"), sep = " ") %>% 
-#   ggplot(aes(x= day, y= perc, fill= name))+
-#   geom_bar(stat = "identity",
-#            position=position_dodge(width=0.9))+
-#   scale_fill_viridis_d() +
-#   labs(fill = NULL, y = "%", title = "Grade 3+")+
-#   theme_classic()
-# 
-# fig_dat %>% 
-#   select(PT,
-#          `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
-#          `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
-#          `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
-#          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
-#          
-#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
-#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
-#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
-#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
-#   ) %>% 
-#   pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
-#   mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
-#          grade = case_when(
-#            grade == "gr3_"       ~ "Grade 3+",
-#            TRUE                  ~ "Any grade"
-#          )) %>% 
-#   mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
-#          name2 = coalesce(name1, name)) %>% 
-#   group_by(name2, value, grade) %>% 
-#   filter(!is.na(value)) %>% 
-#   summarise(count=n()) %>%
-#   group_by(name2, grade) %>% 
-#   mutate(perc=(count/sum(count)*100)
-#   ) %>%
-#   separate("name2", into = c("name", "day"), sep = "_") %>% 
-#   filter(value == "Yes") %>% 
-#   # unite(time, c("day":"me"), sep = " ") %>% 
-#   ggplot(aes(x= day, y= perc, fill= name, alpha= grade))+
-#   geom_bar(stat = "identity",
-#            position=position_dodge(width=0.9))+
-#   scale_fill_viridis_d() + 
-#   scale_alpha_ordinal(range = c(0.5, 1))+
-#   labs(fill = NULL, y = "%")+
-#   theme_classic()
-
-a <- fig_dat %>% 
-  select(pt_identifier,
-         Leukopenia_apheresis,
-         `Leukopenia_-5d`, Leukopenia_30d, #Leukopenia_60d,
-         Leukopenia_90d, Leukopenia_180d,
-         Neutropenia_apheresis,
-         `Neutropenia_-5d`, Neutropenia_30d, #Neutropenia_60d,
-         Neutropenia_90d, Neutropenia_180d,
-         Anemia_apheresis,
-         `Anemia_-5d`, Anemia_30d, #Anemia_60d, 
-         Anemia_90d, Anemia_180d,
-         Thrombocytopenia_apheresis,
-         `Thrombocytopenia_-5d`, Thrombocytopenia_30d, #Thrombocytopenia_60d, 
-         Thrombocytopenia_90d, Thrombocytopenia_180d,
-         cytopenia_apheresis, `cytopenia_-5d`, cytopenia_30d,# cytopenia_60d, 
-         cytopenia_90d, cytopenia_180d,
-
-         gr3_Leukopenia_apheresis,
-         `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, #gr3_Leukopenia_60d, 
-         gr3_Leukopenia_90d, gr3_Leukopenia_180d,
-         gr3_Neutropenia_apheresis,
-         `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, #gr3_Neutropenia_60d, 
-         gr3_Neutropenia_90d, gr3_Neutropenia_180d,
-         gr3_Anemia_apheresis,
-         `gr3_Anemia_-5d`, gr3_Anemia_30d, #gr3_Anemia_60d, 
-         gr3_Anemia_90d, gr3_Anemia_180d,
-         gr3_Thrombocytopenia_apheresis,
-         `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, #gr3_Thrombocytopenia_60d, 
-         gr3_Thrombocytopenia_90d, gr3_Thrombocytopenia_180d,
-         gr3_cytopenia_apheresis, `gr3_cytopenia_-5d`, gr3_cytopenia_30d, #gr3_cytopenia_60d, 
-         gr3_cytopenia_90d, gr3_cytopenia_180d
-  ) %>% 
-  pivot_longer(cols = Neutropenia_apheresis: gr3_cytopenia_180d) %>% 
-  mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
-         grade = case_when(
-           grade == "gr3_"       ~ "Grade 3+",
-           TRUE                  ~ "Any grade"
-         )) %>% 
-  mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
-         name2 = coalesce(name1, name)) %>% 
-  group_by(name2, value, grade) %>% 
-  filter(!is.na(value)) %>%
-  summarise(count=n()) %>%
-  group_by(name2, grade) %>% 
-  mutate(perc=(count/sum(count)*100)
-  ) %>%
-  separate("name2", into = c("name", "day"), sep = "_") %>% 
-  ungroup()
-
-# We want to plot the Yes patients 
-# but filtering filter(value == "Yes") leave blanks if all patients are NO
-# Code to fix it is :
-c <- a %>% 
-  arrange(name, day, grade, desc(value)) %>%  # desc to have yes first
-  distinct(name, day, grade, .keep_all = TRUE) %>% 
-  mutate(count = case_when(
-    value == "No"           ~ 0,
-    TRUE                    ~ count
-  ), perc = case_when(
-    value == "No"           ~ 0,
-    TRUE                    ~ perc
-  )) %>%
-
-  # filter(value == "Yes") %>% 
-  # add_row("name"="Leukopenia",  "day"="apheresis", "value"= "Yes", "grade"="Any grade", "count"=0, "perc"=0) %>% 
-  mutate(day = factor(day, levels = c("apheresis", "-5d", "30d", "60d", "90d", "180d"))) %>% 
-  mutate(name = str_replace(name, "^cytopenia", "Any Cytopenia")) %>% 
-  mutate(name = factor(name, levels = c("Anemia", "Neutropenia", "Thrombocytopenia", "Any Cytopenia"))) %>% 
-  filter(!is.na(name))
-
-b <- c %>% filter(grade == "Any grade")
-c %>% filter(grade == "Grade 3+") %>% 
-  ggplot(aes(x= day, 
-             y= perc, 
-             fill= name, alpha= 1
-             ))+
-  geom_bar(stat = "identity",
-           position=position_dodge(width=0.9))+
-  geom_bar(stat = "identity",
-           position=position_dodge(width=0.9), data= b,
-           aes(x= day, y= perc, fill= name), alpha= 0.4)+
-  scale_fill_brewer(palette = "Spectral")+
-  labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
-  theme_classic()+
-  scale_alpha_continuous(limits = c(0.4,1), breaks = c(0.4,1),
-                         labels= c("Any Grade", "Grade 3+"))
-
-c %>% filter(grade == "Grade 3+") %>% 
-  ggplot(aes(x= day, 
-             y= perc, 
-             fill= name, 
-             ))+
-  geom_bar(stat = "identity",
-           position=position_dodge(width=0.9))+
-  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 5,
-            position = position_dodge(width=0.9), vjust=-1.5
-            )+
-
-  scale_fill_brewer(palette = "Spectral")+
-  ylim(0, 60)+
-  labs(fill = NULL, x= NULL, y = "%")+
-  theme_classic(base_size = 14)+
-  theme(legend.position="bottom")
-```
-
-## Figure 4. Cumulative incidence of infection and infection density
-```{r Figure 5}
-library(tidycmprsk)
-library(ggsurvfit)
-
-risk_comp <- cilta %>%
-  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
-  mutate(event_type = case_when(
-    infection_type_bacterial_viral_fungal_parasitic == "Bacterial"      ~ "Bacterial",
-    infection_type_bacterial_viral_fungal_parasitic == "Fungal"         ~ "Fungal",
-    infection_type_bacterial_viral_fungal_parasitic == "Viral"          ~ "Viral",
-    is.na(infection_type_bacterial_viral_fungal_parasitic)              ~ NA_character_
-  )) %>%
-  mutate(event_type =
-           factor(event_type, levels= c("Bacterial","Fungal", "Viral"))) %>%
-  mutate(infection_event = case_when(
-    is.na(event_type)                        ~ 0,
-    !is.na(event_type)                       ~ 1
-  )) %>% 
-  # mutate(event_type = case_when(
-  #   is.na(event_type)                        ~ "N",
-  #   TRUE ~ event_type
-  # )) %>% 
-  mutate(date_of_event = interval(start = date_of_car_t_infusion,
-                                  end = date_of_infection) /
-           duration(n = 1, units = "days"),
-         date_of_event = case_when(
-      is.na(date_of_event)             ~ os_from_infusion_days,
-      TRUE                             ~ date_of_event)) %>% 
-  select(pt_identifier, date_of_event, infection_event, event_type, os_from_infusion_days, os_event, race) 
-# 
-# cum_inc <- cuminc(risk_comp$date_of_event, risk_comp$event_type)
-# timepoints(cum_inc, times = c(0, 100, 200, 300, 400))$est
-# 
-# ggcompetingrisks(fit = cum_inc, multiple_panels = F, xlab = "Days", ylab = "Cumulative incidence of event",title = "Competing Risks Analysis"
-#                  )
-
-# cum_inc <- cuminc(Surv(date_of_event, infection_event) ~ 1, data = b) %>%
-#   ggcuminc(outcome = c("Bacterial", "Fungal", "Viral"),
-#            geom_step(linewidth=10)) +
-#   ylim(c(0, 1)) +
-#   labs(
-#     x = "Days"
-#   )+
-#   add_risktable()
-# cum_inc
-# 
-# survfit2(Surv(date_of_event, event_type) ~ 1, data = a) %>%
-#   ggcuminc(outcome = c("Viral", "Fungal")#,
-#            # geom_step(linewidth=10)
-#            ) +
-#   # ylim(c(0, 0.25)) +
-#   labs(
-#     x = "Days"
-#   )+
-#   add_risktable()
-```
-
-```{r ggsurvplot combine}
-# risk_comp <- risk_comp %>% 
-#   filter(date_of_event > 0) 
-# a <- risk_comp %>% 
-#   arrange(pt_identifier, desc(infection_event)) %>% 
-#   distinct(pt_identifier, .keep_all = TRUE)
-# 
-# # OS
-# os <- survfit(Surv(os_from_infusion_days, os_event) ~ 1, data=a)
-# ggsurvplot(survfit(Surv(os_from_infusion_days, os_event) ~ 1, 
-#                    data=a),
-#            title = "OS Analysis",
-#            fun = "event",
-#            
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-# 
-#            xlab = "Time in days", 
-#            palette = "orange",
-#            legend = "top",
-#            legend.title = "",
-#            # pval = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# )
-# 
-# # Overall infections
-# ov_inf <- survfit(Surv(date_of_event, infection_event) ~ 1, data=a)
-# ggsurvplot(survfit(Surv(date_of_event, infection_event) ~ 1, 
-#                    data=a),
-#            title = "Cumulative Incidence Analysis",
-#            fun = "event",
-#            
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-# 
-#            xlab = "Time in days",
-#            legend = "top",
-#            legend.title = "",
-#            legend.labs = c("Overall infections"),
-#            # pval = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# )
-# 
-# # By infection types
-# ggsurvplot(survfit(Surv(date_of_event, infection_event) ~ event_type, 
-#                    data=a),
-#            title = "Cumulative Incidence Analysis",
-#            fun = "event",
-#            
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-# 
-#            xlab = "Time in days",
-#            legend = "top",
-#            legend.title = "",
-#            # legend.labs = c("Bact", "Fungal"),
-#            # palette = c("blue", "green", "purple", "red"),
-#            pval = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# 
-# 
-# 
-# 
-# b <- risk_comp %>% 
-#   mutate(event_type =
-#            factor(event_type, levels= c("Bacterial"))) %>%
-#   mutate(infection_event = case_when(
-#     event_type == "Bacterial"     ~ 1,
-#     TRUE                          ~ 0
-#   )) %>% 
-#   arrange(pt_identifier, desc(event_type)) %>% 
-#   distinct(pt_identifier, .keep_all = TRUE)
-# 
-# bact_inf <- survfit(Surv(date_of_event, infection_event) ~ 1, data=b)
-# ggsurvplot(survfit(Surv(date_of_event, infection_event) ~ 1, 
-#                    data=b),
-#            title = "Cumulative Incidence Analysis",
-#            fun = "event",
-#            
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-# 
-#            xlab = "Time in days",
-#            legend = "top",
-#            legend.title = "",
-#            legend.labs = c("Bacterial"),
-#            # palette = c("blue", "green", "purple", "red"),
-#            # pval = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# b <- risk_comp %>% 
-#   mutate(event_type =
-#            factor(event_type, levels= c("Viral"))) %>%
-#   # mutate(date_of_event = case_when(
-#     # pt_identifier == ""   ~ 385,
-#     # TRUE                          ~ date_of_event
-#     # )) %>%
-#   mutate(infection_event = case_when(
-#     # pt_identifier == "" ~ 0,
-#     event_type == "Viral"     ~ 1,
-#     TRUE                          ~ 0
-#   )) %>% 
-#   arrange(pt_identifier, desc(event_type)) %>% 
-#   distinct(pt_identifier, .keep_all = TRUE)
-# 
-# viral_inf <- survfit(Surv(date_of_event, infection_event) ~ 1, data=b)
-# ggsurvplot(survfit(Surv(date_of_event, infection_event) ~ 1, 
-#                    data=b),
-#            title = "Cumulative Incidence Analysis",
-#            fun = "event",
-#            
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-# 
-#            xlab = "Time in days",
-#            legend = "top",
-#            legend.title = "",
-#            legend.labs = c("Viral"),
-#            # palette = c("blue", "green", "purple", "red"),
-#            # pval = TRUE,
-#            cumevents = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# ggsurvfit(viral_inf, type = "risk") +
-#   labs(
-#     x = "Days",
-#     y = "Event-free proportion"
-#   ) +
-#   add_censor_mark()
-# 
-# survfit2(Surv(date_of_event, infection_event) ~ 1, b) %>%
-#   ggcuminc(outcome = "Viral") +
-#   add_confidence_interval() +
-#   add_risktable() +
-#   scale_ggsurvfit()
-# 
-# 
-# risk_comp %>% 
-#   filter(event_type == "Viral") %>%
-#   arrange(date_of_event) %>% 
-#   distinct(pt_identifier, .keep_all = TRUE) %>% 
-#   mutate(n = cumsum(infection_event)) %>% 
-#   mutate(n2 = n / 105) %>%
-#   ggplot(aes(x = date_of_event, y = n2))+
-#   geom_step()+
-#   ylim(0,1)
-# 
-# 
-# 
-# 
-# 
-# 
-# 
-# 
-# 
-# 
-# 
-# # Fungal
-# b <- risk_comp %>% 
-#   mutate(event_type =
-#            factor(event_type, levels= c("Fungal"))) %>%
-#   mutate(infection_event = case_when(
-#     event_type == "Fungal"     ~ 1,
-#     TRUE                          ~ 0
-#   )) %>% 
-#   arrange(pt_identifier, desc(event_type)) %>% 
-#   distinct(pt_identifier, .keep_all = TRUE)
-# 
-# fungal_inf <- survfit(Surv(date_of_event, infection_event) ~ 1, data=b)
-# ggsurvplot(survfit(Surv(date_of_event, infection_event) ~ 1, 
-#                    data=b),
-#            title = "Cumulative Incidence Analysis",
-#            fun = "event",
-#            
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-# 
-#            xlab = "Time in days",
-#            legend = "top",
-#            legend.title = "",
-#            legend.labs = c("Fungal"),
-#            # palette = c("blue", "green", "purple", "red"),
-#            # pval = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# # inf_by_type <- survfit(Surv(date_of_event, infection_event) ~ 1, data=risk_comp)
-# 
-# fit <- list(Overall_infections = ov_inf, OS = os, 
-#             Bacterial = bact_inf,
-#             Viral = viral_inf,
-#             Fungal = fungal_inf
-#             )
-# ggsurvplot_combine(fit, risk_comp, combine = TRUE,
-#                    fun = "event",
-#                    legend.title = "",
-#                    ylim = c(0,1)
-#                    ) + 
-#   guides(colour = guide_legend(ncol = 1))
-# 
-# 
-# fit <- list(By_type = inf_by_type, OS = os)
-# ggsurvplot_combine(fit, risk_comp, combine = TRUE,
-#                    fun = "cumhaz") + 
-#   guides(colour = guide_legend(ncol = 1))
-# 
-# 
-# fit <- list(Overall_infections = ov_inf, By_type = inf_by_type, OS = os)
-# ggsurvplot_combine(fit, risk_comp, combine = TRUE,
-#                    fun = "cumhaz") + 
-#   guides(colour = guide_legend(ncol = 1))
-```
-
-```{r violin plot}
-cilta %>%
-  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
-  select(pt_identifier, any_infection, any_sevinfection, date_of_infection, 
-         time_from_infusion_to_infection_days, infection_type_bacterial_viral_fungal_parasitic,
-         infection_type_cat) %>% 
-  mutate(any_sevinfection = case_when(
-    any_sevinfection == "Yes"           ~ "Severe"
-  )) %>% 
-  mutate(any_infection = case_when(
-    any_sevinfection == "Severe"        ~ NA_character_,
-    any_infection == "Yes"              ~ "Not severe"
-  )) %>% 
-  pivot_longer(cols = c(any_infection, any_sevinfection), 
-               names_to = "Infection", 
-               values_to = "Infection severity") %>% 
-  drop_na(`Infection severity`) %>% 
-  mutate(infection_type_cat = str_replace(infection_type_cat, " \\+ ", " and ")) %>% 
-  separate_wider_delim(cols = infection_type_cat, delim = " and ",
-                       names = c("infection_type_cat1", "infection_type_cat2"), 
-                       too_few = "align_start", too_many = "merge", 
-                       cols_remove = TRUE) %>% 
-  pivot_longer(cols = c(infection_type_cat1, infection_type_cat2), 
-               names_to = NULL, 
-               values_to = "Infection categories") %>% 
-  drop_na(`Infection categories`) %>% 
-  ggplot(aes(x = infection_type_bacterial_viral_fungal_parasitic, 
-             y = time_from_infusion_to_infection_days))+
-  geom_violin()+
-  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
-  # geom_point(aes(color = `Infection severity`), position = "jitter")
-  labs(x = NULL, y = "Infection onset time (days)")+
-  scale_color_manual(values = c("black", "red"))+
-  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))
-
-cilta %>%
-  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
-  select(pt_identifier, any_infection, any_sevinfection, date_of_infection, 
-         time_from_infusion_to_infection_days,
-         infection_type_cat) %>% 
-  mutate(any_sevinfection = case_when(
-    any_sevinfection == "Yes"           ~ "Severe"
-  )) %>% 
-  mutate(any_infection = case_when(
-    any_sevinfection == "Severe"        ~ NA_character_,
-    any_infection == "Yes"              ~ "Not severe"
-  )) %>% 
-  pivot_longer(cols = c(any_infection, any_sevinfection), 
-               names_to = "Infection", 
-               values_to = "Infection severity") %>% 
-  drop_na(`Infection severity`) %>% 
-  mutate(infection_type_cat = str_replace(infection_type_cat, "and Respiratory infection", "and Respiratory infections")) %>% 
-  mutate(infection_type_cat = str_replace(infection_type_cat, " \\+ ", " and ")) %>% 
-  separate_wider_delim(cols = infection_type_cat, delim = " and ",
-                       names = c("infection_type_cat1", "infection_type_cat2"), 
-                       too_few = "align_start", too_many = "merge", 
-                       cols_remove = TRUE) %>% 
-  pivot_longer(cols = c(infection_type_cat1, infection_type_cat2), 
-               names_to = NULL, 
-               values_to = "Infection categories") %>% 
-  drop_na(`Infection categories`) %>% 
-  ggplot(aes(x = `Infection categories`, 
-             y = time_from_infusion_to_infection_days))+
-  geom_violin()+
-  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
-  # geom_point(aes(color = `Infection severity`), position = "jitter")
-  labs(x = NULL, y = "Infection onset time (days)")+
-  scale_color_manual(values = c("black", "red"))+
-  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))#+
-  # coord_flip()
-
-cilta %>%
-  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>%
-  filter(infection_type_bacterial_viral_fungal_parasitic == "Viral") %>%
-  select(pt_identifier, any_infection, any_sevinfection, date_of_infection,
-         time_from_infusion_to_infection_days,
-         viral_category) %>%
-  mutate(any_sevinfection = case_when(
-    any_sevinfection == "Yes"           ~ "Severe"
-  )) %>%
-  mutate(any_infection = case_when(
-    any_sevinfection == "Severe"        ~ NA_character_,
-    any_infection == "Yes"              ~ "Not severe"
-  )) %>%
-  pivot_longer(cols = c(any_infection, any_sevinfection),
-               names_to = "Infection",
-               values_to = "Infection severity") %>%
-  drop_na(`Infection severity`) %>%
-  mutate(viral_category = str_replace(viral_category, ", ", " And ")) %>% 
-  mutate(viral_category = str_replace(viral_category, "Rhinovius", "Rhinovirus")) %>% 
-  mutate(viral_category = str_replace(viral_category, "parainfluenza", "Parainfluenza")) %>% 
-  mutate(viral_category = str_replace(viral_category, "Metapneurmovirus", "Metapneumovirus")) %>% 
-  mutate(viral_category = str_remove(viral_category, "\\? ")) %>% 
-  separate_wider_delim(cols = viral_category, delim = " And ",
-                       names = c("viral_category1", "viral_category2"), 
-                       too_few = "align_start", too_many = "merge", 
-                       cols_remove = FALSE) %>% 
-  pivot_longer(cols = c(viral_category1, viral_category2), 
-               names_to = NULL, 
-               values_to = "Viral categories") %>% 
-  drop_na(`Viral categories`) %>% 
-  ggplot(aes(x = `Viral categories`,
-             y = time_from_infusion_to_infection_days))+
-  geom_violin()+
-  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
-  labs(x = NULL, y = "Infection onset time (days)")+
-  scale_color_manual(values = c("black", "red"))+
-  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
-  # coord_flip()
-  theme(axis.text.x = element_text(angle = 45, 
-                                   hjust = 1#,
-                                   # vjust = 0.5
-                                   ))
-```
-
-## Figure S3. Viral titers after ide-cel
-Focus on MCC patients / I didn't use day 180 as they are less values but I can add it if you want.
-```{r Figure S1. Viral titers after ide-cel}
-fig_dat <- cilta %>% 
-  distinct(pt_identifier, .keep_all = TRUE)
-moffitt_subset <- fig_dat %>% filter(site == "Moffitt")
-```
-
-### A)	HSV 1/2 IgG
-See below
-```{r HSV 1/2 IgG}
-# Alluvial
-library(ggalluvial)
-
-alluvial_A <- moffitt_subset %>% 
-  select(pt_identifier, igg_hsv_change,
-         ig_g_hsv1_2_apheresis, ig_g_hsv1_2_d90) %>%
-  drop_na() %>%
-  group_by(ig_g_hsv1_2_apheresis, ig_g_hsv1_2_d90) %>% 
-  summarise(count=n()) %>%
-
-  ggplot(aes(axis1 = ig_g_hsv1_2_apheresis, axis2 = ig_g_hsv1_2_d90,
-             y = count)) +
-  geom_alluvium(aes(fill = ig_g_hsv1_2_apheresis)
-  )+
-  geom_stratum()+
-  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  theme_classic()+
-  ggtitle("Evolution of virus titers")
-```
-
-### B)	VZV IgG (positive=immune vs negative or equivocal=not immune)
-See below
-```{r VZV IgG}
-# Alluvial
-alluvial_B <- moffitt_subset %>% 
-  select(pt_identifier, igg_vzv_change,
-         vzv_ig_g_apheresis, vzv_ig_g_d90
-  ) %>% 
-  drop_na() %>% 
-  group_by(vzv_ig_g_apheresis, vzv_ig_g_d90) %>% 
-  summarise(count=n()) %>%
-
-  ggplot(aes(axis1 = vzv_ig_g_apheresis, axis2= vzv_ig_g_d90,
-             y = count)) +
-  geom_alluvium(aes(fill = vzv_ig_g_apheresis), 
-                color = c("transparent", "transparent", "white", "transparent", "transparent", "transparent")
-  )+
-  geom_stratum()+
-  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  # geom_hline(yintercept = 5, color = "blue")+
-  theme_classic()+
-  ggtitle("Evolution of virus titers")
-```
-
-### C)	CMV IgG (positive=immune vs negative=not immune)
-```{r CMV IgG}
-alluvial_C <- moffitt_subset %>% 
-  select(pt_identifier, igg_cmv_change,
-         cmv_ig_g_apheresis, cmv_ig_g_d90
-  ) %>% 
-  drop_na() %>% 
-  group_by(cmv_ig_g_apheresis, cmv_ig_g_d90) %>% 
-  summarise(count=n()) %>%
-
-  ggplot(aes(axis1 = cmv_ig_g_apheresis, axis2= cmv_ig_g_d90,
-             y = count)) +
-  geom_alluvium(aes(fill = cmv_ig_g_apheresis)
-  )+
-  geom_stratum()+
-  # geom_segment(aes(x=1.17, y=12, xend=1.83, yend=12), 
-  #              color= "white", size=0.3)+
-  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  theme_classic()+
-  ggtitle("Evolution of virus titers")
-```
-
-```{r alluvial combine, fig.height=12}
-(alluvial_A) /
-  (alluvial_B) + #/
-  # (alluvial_C) +
-  plot_annotation(tag_levels = "A")
-```
-
-### A)	HSV 1/2 IgG with day 180
-See below
-```{r HSV 1/2 IgG with day 180}
-# Alluvial
-library(ggalluvial)
-
-alluvial_A <- moffitt_subset %>% 
-  select(pt_identifier, igg_hsv_change,
-         ig_g_hsv1_2_apheresis, ig_g_hsv1_2_d90, ig_g_hsv1_2_d180) %>%
-  drop_na() %>%
-  group_by(ig_g_hsv1_2_apheresis, ig_g_hsv1_2_d90, ig_g_hsv1_2_d180) %>% 
-  summarise(count=n()) %>%
-
-  ggplot(aes(axis1 = ig_g_hsv1_2_apheresis, axis2 = ig_g_hsv1_2_d90, axis3 = ig_g_hsv1_2_d180,
-             y = count)) +
-  geom_alluvium(aes(fill = ig_g_hsv1_2_apheresis)
-  )+
-  geom_stratum()+
-  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  theme_classic()+
-  ggtitle("Evolution of virus titers")
-```
-12 patients don't have data at day 180.
-
-### B)	VZV IgG (positive=immune vs negative or equivocal=not immune) with day 180
-See below
-```{r VZV IgG with day 180}
-# Alluvial
-alluvial_B <- moffitt_subset %>% 
-  select(pt_identifier, igg_vzv_change,
-         vzv_ig_g_apheresis, vzv_ig_g_d90, vzv_ig_g_d180
-  ) %>% 
-  drop_na() %>% 
-  group_by(vzv_ig_g_apheresis, vzv_ig_g_d90, vzv_ig_g_d180) %>% 
-  summarise(count=n()) %>%
-
-  ggplot(aes(axis1 = vzv_ig_g_apheresis, axis2= vzv_ig_g_d90, axis3 = vzv_ig_g_d180,
-             y = count)) +
-  geom_alluvium(aes(fill = vzv_ig_g_apheresis)
-  )+
-  geom_stratum()+
-  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  # geom_hline(yintercept = 5, color = "blue")+
-  theme_classic()+
-  ggtitle("Evolution of virus titers")
-```
-11 patients don't have data at day 180.
-
-```{r alluvial day 180 combine, fig.height=12}
-(alluvial_A) /
-  (alluvial_B) + #/
-  # (alluvial_C) 
-  plot_annotation(tag_levels = "A")
-```
-
-## Figure S4. Pneumococcal titers after ide-cel
-
-Antibody concentration >1.0 is considered long-term protection (immune)
-If antibody concentration ≤1.0 consider negative (not immune)
-```{r, fig.width=12, fig.height=12}
-# Histogram
-# fig_dat %>% 
-#   select(PT, 
-#          starts_with("Pneumo"), -ends_with("change")) %>% 
-#   pivot_longer(cols = -PT) %>% 
-#   filter(!is.na(value)) %>% 
-#   mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
-#   mutate(name = str_remove(name, " apheresis| D90")) %>% 
-#   
-#   group_by(name, day, value) %>% 
-#   summarise(count=n()) %>% 
-#   mutate(perc=(count/sum(count)*100)
-#   ) %>% 
-# 
-#   ggplot(aes(x= day, y= perc, fill= value))+
-#   # geom_bar(stat = "identity",
-#   #          position=position_dodge2(width=0.9, preserve = "single"))+
-#   geom_bar(stat = "identity")+
-#   labs(x= "Days relative to infusion", y= "Proportion immunity (%)",
-#        fill= "Immunity")+
-#   scale_y_continuous(expand = c(0, 0))+
-#   theme_classic()+
-#   facet_wrap(.~ name)
-```
-
-```{r, fig.width=12, fig.height=14}
-# Tile
-# fig_dat %>% 
-#   select(PT, 
-#          starts_with("Pneumo"), -ends_with("change")) %>% 
-#   pivot_longer(cols = -PT) %>% 
-#   mutate(day = str_match(name, ".*(apheresis|D90)")[,2]) %>% 
-#   mutate(name = str_remove(name, " apheresis| D90")) %>% 
-#   
-#   
-#   filter(!is.na(value)) %>% 
-#   arrange(value) %>% 
-#   ggplot(aes(x= day, y= fct_reorder2(PT, value, day), fill= value))+
-#   geom_tile(color = "white")+
-#   labs(fill = NULL, x = NULL, y= NULL)+
-#   theme_classic()+
-#   facet_wrap(.~ name)
-```
-
-```{r Figure S2. Pneumococcal titers after ide-cel, fig.width=15, fig.height=12}
-library(ComplexHeatmap)
-mat <- moffitt_subset %>% 
-  select(pt_identifier, 
-         intersect(starts_with("pneumo"), ends_with("change"))) %>% 
-  drop_na() %>% 
-  mutate(new_sort =
-           c(4,3,12,31,13,14,9,15,5,6,8,10,32,16,18,17,19,30,2,1,20,21,40,22),
-         .before = 2) %>%
-
-  arrange(new_sort) %>%
-    select(-new_sort)
-
-df5 <- t((as.matrix(mat)))
-
-df <- df5 %>% `colnames<-`(c(.[1,])) %>% 
-  .[-1,]
-
-df <- df %>% 
-sub(pattern = " 1.00", replacement = "Acquired immunity") %>% 
-sub(pattern = " 0.25", replacement = "Positive overtime") %>% 
-sub(pattern = "-0.25", replacement = "Negative overtime") %>% 
-sub(pattern = "-1.00", replacement = "Lost immunity")
-
-colors = structure(c("blue", "darkgrey", "lightgrey", "red"), 
-                   names = c("Lost immunity", "Negative overtime", "Positive overtime", "Acquired immunity"))
-
-ht_list <- Heatmap(df, name = "change", 
-        rect_gp = gpar(col = "white", lwd = 0.1),
-        column_title = "Change in titers",
-        # show_column_names =FALSE,
-        row_names_side = "left",
-        row_names_gp = gpar(fontsize = 11),
-        col = colors)
-draw(ht_list, heatmap_legend_side = "bottom")
-```
-
-## Table S7 and Figure S2. MVA and forest plot
-Limit to evaluable patients at day 90 (For Grade 3+ Cytopenia at days 90 MVA)
-```{r MVA and forest plot}
-mva_dat <- fig_dat %>% 
-  filter(os_from_infusion_months > 3) %>% 
-  mutate(gr3_cytopenia_30d = case_when(
-    gr3_cytopenia_30d == "No"    ~ 0,
-    gr3_cytopenia_30d == "Yes"   ~ 1
-  )) %>% 
-  mutate(gr3_cytopenia_90d = case_when(
-    gr3_cytopenia_90d == "No"    ~ 0,
-    gr3_cytopenia_90d == "Yes"   ~ 1
-  )) %>% 
-  mutate(any_late_icaht = case_when(
-    any_late_icaht == "No"    ~ 0,
-    any_late_icaht == "Yes"   ~ 1
-  )) %>% 
-  mutate(CRS_grade2 = case_when(
-    max_crs_grade_0_5 < 2                              ~ "No CRS or Grade < 2",
-    max_crs_grade_0_5 >= 2                             ~ "Grade ≥2"),
-    CRS_grade2 = factor(CRS_grade2, levels = c("No CRS or Grade < 2", "Grade ≥2"))
-  )
-
-glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + ht_score + 
-      number_of_prior_lines_of_therapy,
-    data = mva_dat,
-    family = "binomial") %>%
-  tbl_regression(exponentiate = TRUE, 
-                 intercept = TRUE) %>%
-  add_nevent(location = "level") %>% add_n(location = "level") %>%
-  modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
-  bold_p(t = .05)
-glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + ht_score,
-    data = mva_dat,
-    family = "binomial") %>%
-  tbl_regression(exponentiate = TRUE, 
-                 intercept = TRUE) %>%
-  add_nevent(location = "level") %>% add_n(location = "level") %>%
-  modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
-  bold_p(t = .05)
-
-```
-
-```{r}
-mva_dat_icaht <- fig_dat %>% 
-  mutate(any_late_icaht = case_when(
-    any_late_icaht == "No"    ~ 0,
-    any_late_icaht == "Yes"   ~ 1
-  ))
-
-glm(any_late_icaht ~ high_marrow_burden_50_percent + ht_score + 
-      number_of_prior_lines_of_therapy,
-    data = mva_dat_icaht,
-    family = "binomial") %>%
-  tbl_regression(exponentiate = TRUE, 
-                 intercept = TRUE) %>%
-  add_nevent(location = "level") %>% add_n(location = "level") %>%
-  modify_spanning_header(everything() ~ "**Any late ICAHT**") %>%
-  bold_p(t = .05)
-glm(any_late_icaht ~ high_marrow_burden_50_percent + ht_score,
-    data = mva_dat_icaht,
-    family = "binomial") %>%
-  tbl_regression(exponentiate = TRUE, 
-                 intercept = TRUE) %>%
-  add_nevent(location = "level") %>% add_n(location = "level") %>%
-  modify_spanning_header(everything() ~ "**Any late ICAHT**") %>%
-  bold_p(t = .05)
-
-```
-
-older MVA
-```{r}
-# glm(gr3_cytopenia_30d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + CRS_grade2 + steroid_use_yes_no + number_of_prior_lines_of_therapy,
-#     data = mva_dat,
-#     family = "binomial") %>%
-#   tbl_regression(exponentiate = TRUE, 
-#                  intercept = TRUE) %>%
-#   add_nevent(location = "level") %>% add_n(location = "level") %>%
-#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 30**") %>%
-#   bold_p(t = .05) 
-# 
-# glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + CRS_grade2 + steroid_use_yes_no + number_of_prior_lines_of_therapy,
-#     data = mva_dat,
-#     family = "binomial") %>%
-#   tbl_regression(exponentiate = TRUE, 
-#                  intercept = TRUE) %>%
-#   add_nevent(location = "level") %>% add_n(location = "level") %>%
-#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
-#   bold_p(t = .05) 
-# 
-# glm(gr3_cytopenia_30d ~ high_marrow_burden_50_percent + CRS_grade2 + steroid_use_yes_no + number_of_prior_lines_of_therapy,
-#     data = mva_dat,
-#     family = "binomial") %>%
-#   tbl_regression(exponentiate = TRUE, 
-#                  intercept = TRUE) %>%
-#   add_nevent(location = "level") %>% add_n(location = "level") %>%
-#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 30**") %>%
-#   bold_p(t = .05)
-
-glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + 
-      steroid_use_yes_no + number_of_prior_lines_of_therapy + baseline_ferritin_cat,
-    data = mva_dat,
-    family = "binomial") %>%
-  tbl_regression(exponentiate = TRUE, 
-                 intercept = TRUE) %>%
-  add_nevent(location = "level") %>% add_n(location = "level") %>%
-  modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
-  bold_p(t = .05)
-```
-
-```{r forest plot 5}
-forest_p <- 
-  glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` +
-        steroid_use_yes_no + number_of_prior_lines_of_therapy + baseline_ferritin_cat,
-    data = mva_dat,
-    family = "binomial") %>%
-  tbl_regression(exponentiate = TRUE) %>%
-  as_tibble() %>% 
-  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
-  fill(OR, `95% CI`, .direction = "up") %>% 
-  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
-  filter(Characteristic %in% c("High marrow burden (≥50%)",
-                 "gr3_cytopenia_-5d",
-                 "baseline_ferritin_cat",
-                 "Steroid Use",
-                 "Number of prior lines of therapy") ) %>% 
-  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
-  mutate(name= case_when(
-    Characteristic == "High marrow burden (≥50%)"      ~ "High marrow burden (≥50%)",
-    Characteristic == "gr3_cytopenia_-5d"      ~ "Grade ≥ 3 Cytopenia at Day -5",
-    Characteristic == "Steroid Use"      ~ "Steroid use",
-    Characteristic == "Number of prior lines of therapy"      ~ "Number of prior lines of therapy",
-    Characteristic == "baseline_ferritin_cat"      ~ "Baseline ferritin"
-  ))
-
-ggplot(data=forest_p, aes(y=name, x=OR, xmin=lower, xmax=upper)) +
-  geom_point() + 
-  geom_errorbarh(height=.1) +
-  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
-  theme_classic()+
-  scale_x_log10(breaks = c(0, 0.25, 0.5, 1, 2.5, 5, 10, 40))+
-  labs(y="")
-```
-
-```{r MVA 3}
-glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` + 
-      number_of_prior_lines_of_therapy,
-    data = mva_dat,
-    family = "binomial") %>%
-  tbl_regression(exponentiate = TRUE, 
-                 intercept = TRUE) %>%
-  add_nevent(location = "level") %>% add_n(location = "level") %>%
-  modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
-  bold_p(t = .05) 
-```
-
-```{r forest plot 3}
-forest_p <- 
-  glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` +
-        number_of_prior_lines_of_therapy,
-    data = mva_dat,
-    family = "binomial") %>%
-  tbl_regression(exponentiate = TRUE) %>%
-  as_tibble() %>% 
-  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
-  fill(OR, `95% CI`, .direction = "up") %>% 
-  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
-  filter(Characteristic %in% c("High marrow burden (≥50%)",
-                 "gr3_cytopenia_-5d",
-                 "Number of prior lines of therapy") ) %>% 
-  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
-  mutate(name= case_when(
-    Characteristic == "High marrow burden (≥50%)"      ~ "High marrow burden (≥50%)",
-    Characteristic == "gr3_cytopenia_-5d"      ~ "Grade ≥ 3 Cytopenia at Day -5",
-    # Characteristic == "Steroid Use"      ~ "Steroid use",
-    Characteristic == "Number of prior lines of therapy"      ~ "Number of prior lines of therapy"
-    # Characteristic == "baseline_ferritin_cat"      ~ "Baseline ferritin"
-  ))
-
-ggplot(data=forest_p, aes(y=name, x=OR, xmin=lower, xmax=upper)) +
-  geom_point() + 
-  geom_errorbarh(height=.1) +
-  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
-  theme_classic()+
-  scale_x_log10(breaks = c(0, 0.25, 0.5, 1, 2.5, 5, 10, 40))+
-  labs(y="")
-```
-
-## Survival analysis - KM by gr3_cytopenia_90d
-```{r Survival analysis - KM by gr3_cytopenia_90d}
-surv_dat <- fig_dat %>% 
-  mutate(ORR_as_best_response = case_when(
-    ORR_as_best_response == "ORR"         ~ "ORR",
-    ORR_as_best_response == "SD/PD"       ~ "never ORR",
-    # TRUE                                  ~ "never ORR"
-  ))
-
-library(survival)
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ gr3_cytopenia_90d, 
-                   data=surv_dat),
-           title = "PFS Analysis",
-           font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
-           size = 1.5,
-
-           xlab = "Time in months",
-           legend = "top",
-           legend.title = "",
-           pval = TRUE,
-           conf.int = FALSE,
-           # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
-
-coxph(Surv(time = surv_dat$pfs_from_infusion_months, 
-                   event = surv_dat$pfs_event) ~ gr3_cytopenia_90d, 
-              data = surv_dat)  %>% 
-  tbl_regression(exponentiate = TRUE) %>% 
-  bold_p(t = .05) %>% 
-  add_nevent(location = "level") %>% add_n(location = "level")
-
-# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ gr3_cytopenia_90d, 
-#                    data=surv_dat),
-#            title = "OS Analysis",
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-# 
-#            xlab = "Time in months",
-#            legend = "top",
-#            legend.title = "",
-#            pval = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# coxph(Surv(time = surv_dat$os_from_infusion_months, 
-#                    event = surv_dat$os_event) ~ gr3_cytopenia_90d, 
-#               data = surv_dat)  %>% 
-#   tbl_regression(exponentiate = TRUE) %>% 
-#   bold_p(t = .05) %>% 
-#   add_nevent(location = "level") %>% add_n(location = "level")
-```
-
-## Survival analysis - KM by ORR_as_best_response
-```{r Survival analysis - KM by ORR_as_best_response}
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ ORR_as_best_response, 
-                   data=surv_dat),
-           title = "PFS Analysis",
-           font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
-           size = 1.5,
-
-           xlab = "Time in months",
-           legend = "top",
-           legend.title = "",
-           pval = TRUE,
-           conf.int = FALSE,
-           # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
-
-coxph(Surv(time = surv_dat$pfs_from_infusion_months, 
-                   event = surv_dat$pfs_event) ~ ORR_as_best_response, 
-              data = surv_dat)  %>% 
-  tbl_regression(exponentiate = TRUE) %>% 
-  bold_p(t = .05) %>% 
-  add_nevent(location = "level") %>% add_n(location = "level")
-
-# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ ORR_as_best_response, 
-#                    data=surv_dat),
-#            title = "OS Analysis",
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-# 
-#            xlab = "Time in months",
-#            legend = "top",
-#            legend.title = "",
-#            pval = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# coxph(Surv(time = surv_dat$os_from_infusion_months, 
-#                    event = surv_dat$os_event) ~ ORR_as_best_response, 
-#               data = surv_dat)  %>% 
-#   tbl_regression(exponentiate = TRUE) %>% 
-#   bold_p(t = .05) %>% 
-#   add_nevent(location = "level") %>% add_n(location = "level")
-```
-
-## Survival analysis - KM by gr3 cytopenia at day 30
-```{r Survival analysis - KM by gr3_cytopenia_30d}
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ gr3_cytopenia_30d, 
-                   data=surv_dat),
-           title = "PFS Analysis",
-           font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
-           size = 1.5,
-
-           xlab = "Time in months",
-           legend = "top",
-           legend.title = "",
-           pval = TRUE,
-           conf.int = FALSE,
-           # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
-
-coxph(Surv(time = surv_dat$pfs_from_infusion_months, 
-                   event = surv_dat$pfs_event) ~ gr3_cytopenia_30d, 
-              data = surv_dat)  %>% 
-  tbl_regression(exponentiate = TRUE) %>% 
-  bold_p(t = .05) %>% 
-  add_nevent(location = "level") %>% add_n(location = "level")
-
-# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ gr3_cytopenia_30d, 
-#                    data=surv_dat),
-#            title = "OS Analysis",
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-# 
-#            xlab = "Time in months",
-#            legend = "top",
-#            legend.title = "",
-#            pval = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# coxph(Surv(time = surv_dat$os_from_infusion_months, 
-#                    event = surv_dat$os_event) ~ gr3_cytopenia_30d, 
-#               data = surv_dat)  %>% 
-#   tbl_regression(exponentiate = TRUE) %>% 
-#   bold_p(t = .05) %>% 
-#   add_nevent(location = "level") %>% add_n(location = "level")
-```
-
-## Survival analysis - KM by CAR-HEMATOTOX score
-```{r Survival analysis - KM by ht_score}
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ ht_score, 
-                   data=surv_dat),
-           title = "PFS Analysis",
-           font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
-           size = 1.5,
-
-           xlab = "Time in months",
-           legend = "top",
-           legend.title = "",
-           pval = TRUE,
-           conf.int = FALSE,
-           # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
-
-coxph(Surv(time = surv_dat$pfs_from_infusion_months, 
-                   event = surv_dat$pfs_event) ~ ht_score, 
-              data = surv_dat)  %>% 
-  tbl_regression(exponentiate = TRUE) %>% 
-  bold_p(t = .05) %>% 
-  add_nevent(location = "level") %>% add_n(location = "level")
-
-# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ ht_score, 
-#                    data=surv_dat),
-#            title = "OS Analysis",
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-# 
-#            xlab = "Time in months",
-#            legend = "top",
-#            legend.title = "",
-#            pval = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# coxph(Surv(time = surv_dat$os_from_infusion_months, 
-#                    event = surv_dat$os_event) ~ ht_score, 
-#               data = surv_dat)  %>% 
-#   tbl_regression(exponentiate = TRUE) %>% 
-#   bold_p(t = .05) %>% 
-#   add_nevent(location = "level") %>% add_n(location = "level")
-```
-
-## Survival analysis - KM by ANY early ICAHT
-```{r Survival analysis - KM by gr3_early_icaht}
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ any_early_icaht,
-                   data=surv_dat),
-           title = "PFS Analysis",
-           font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
-           size = 1.5,
-
-           xlab = "Time in months",
-           legend = "top",
-           legend.title = "",
-           pval = TRUE,
-           conf.int = FALSE,
-           # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
-
-coxph(Surv(time = surv_dat$pfs_from_infusion_months,
-                   event = surv_dat$pfs_event) ~ any_early_icaht,
-              data = surv_dat)  %>%
-  tbl_regression(exponentiate = TRUE) %>%
-  bold_p(t = .05) %>%
-  add_nevent(location = "level") %>% add_n(location = "level")
-
-# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ gr3_early_icaht,
-#                    data=surv_dat),
-#            title = "OS Analysis",
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-#
-#            xlab = "Time in months",
-#            legend = "top",
-#            legend.title = "",
-#            pval = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
-#
-# coxph(Surv(time = surv_dat$os_from_infusion_months,
-#                    event = surv_dat$os_event) ~ gr3_early_icaht,
-#               data = surv_dat)  %>%
-#   tbl_regression(exponentiate = TRUE) %>%
-#   bold_p(t = .05) %>%
-#   add_nevent(location = "level") %>% add_n(location = "level")
-```
-
-## Survival analysis - KM by ANY late ICAHT
-```{r Survival analysis - KM by gr3_late_icaht}
-ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ any_late_icaht,
-                   data=surv_dat),
-           title = "PFS Analysis",
-           font.main = c(20, "bold", "black"),
-           font.x = c(18, "bold", "black"),
-           font.y = c(18, "bold", "black"),
-           font.legend = c(16, "black"),
-           font.tickslab = c(16, "bold", "black"),
-           size = 1.5,
-
-           xlab = "Time in months",
-           legend = "top",
-           legend.title = "",
-           pval = TRUE,
-           conf.int = FALSE,
-           # Censor
-           censor = TRUE
-) + guides(colour = guide_legend(ncol = 1))
-
-coxph(Surv(time = surv_dat$pfs_from_infusion_months,
-                   event = surv_dat$pfs_event) ~ any_late_icaht,
-              data = surv_dat)  %>%
-  tbl_regression(exponentiate = TRUE) %>%
-  bold_p(t = .05) %>%
-  add_nevent(location = "level") %>% add_n(location = "level")
-
-# ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ gr3_late_icaht,
-#                    data=surv_dat),
-#            title = "OS Analysis",
-#            font.main = c(20, "bold", "black"),
-#            font.x = c(18, "bold", "black"),
-#            font.y = c(18, "bold", "black"),
-#            font.legend = c(16, "black"),
-#            font.tickslab = c(16, "bold", "black"),
-#            size = 1.5,
-#
-#            xlab = "Time in months",
-#            legend = "top",
-#            legend.title = "",
-#            pval = TRUE,
-#            conf.int = FALSE,
-#            # Censor
-#            censor = TRUE
-# ) + guides(colour = guide_legend(ncol = 1))
-#
-# coxph(Surv(time = surv_dat$os_from_infusion_months,
-#                    event = surv_dat$os_event) ~ gr3_late_icaht,
-#               data = surv_dat)  %>%
-#   tbl_regression(exponentiate = TRUE) %>%
-#   bold_p(t = .05) %>%
-#   add_nevent(location = "level") %>% add_n(location = "level")
-```
-
-<!-- ## UVA best ORR by gr3 cytopenia at day 90 -->
-<!-- I was unable to perform the analyses investigating severe cytopenias at D90 and best response because everyone with severe cytopenias had an event. -->
-<!-- ```{r glm} -->
-<!-- mva_dat <- surv_dat %>%  -->
-<!--   # filter(os_from_infusion_months > 3) %>%  -->
-<!--   mutate(ORR_as_best_response = case_when( -->
-<!--     ORR_as_best_response == "ORR"         ~ 1, -->
-<!--     ORR_as_best_response == "never ORR"   ~ 0 -->
-<!--   ))  -->
-
-<!-- # glm(ORR_as_best_response ~ gr3_cytopenia_90d, -->
-<!-- #     data = mva_dat, -->
-<!-- #     family = "binomial") %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE,  -->
-<!-- #                  intercept = TRUE) %>% -->
-<!-- #   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
-<!-- #   modify_spanning_header(everything() ~ "**ORR_as_best_response**") %>% -->
-<!-- #   bold_p(t = .05)  -->
-<!-- ``` -->

### 2025-06-12 MM_teclistamab/Rmd/teclistamab_analyses.Rmd
First analysis

---
title: "Teclistamab analyses"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options:
  chunk_output_type: console
---

<style type= "text/css">

. figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(here)
library(tidyverse)
library(ggplot2)
library(gtsummary)
library(labelled)
library(DescTools)
library(patchwork)
library(ggbreak)
library(survival)
library(survminer)
theme_set(theme_classic())
theme_gtsummary_compact()
```

```{r load}
# path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Analyses", "Janssen Teclistamab")

data <- 
  read_csv(locale = locale(encoding="latin1"),
    paste0(#path, 
           here(), 
           "/Tec_05222025.csv")#,
    # na = "N/A"
    ) %>% 
  janitor::clean_names()
```

```{r column name}
data <- data %>% 
  `colnames<-`(paste0(colnames(.), "~", .[1,])) %>% 
  `colnames<-`(str_remove(colnames(.), "~NA")) %>% 
  janitor::clean_names() %>% 
  rename(pt_identifier = patient_identifier_use_same_id_for_cns_amyloid_sheets_if_appropriate,
         if_ineligible_for_bs_ab_trial_why_not_be_specific_and_can_separate_reasons_with_commas = 
           if_ineligible_for_bs_ab_trial_why_not_be_specific_and_can_separate_reasons_with_commas_no_0_y_1, 
         date_of_infection_1st = date_of_infection_74,
         infection_severity_1st_severe_hospitalization_or_requiring_iv_antibiotics = infection_severity_73_severe_hospitalization_or_requiring_iv_antibiotics,
         date_of_infection_2nd = date_of_infection_77,
         infection_severity_2nd_severe_hospitalization_or_requiring_iv_antibiotics = infection_severity_76_severe_hospitalization_or_requiring_iv_antibiotics,
         date_of_infection_3rd = date_of_infection_80,
         infection_severity_3rd_severe_hospitalization_or_requiring_iv_antibiotics = infection_severity_79_severe_hospitalization_or_requiring_iv_antibiotics,
         date_of_infection_4th = date_of_infection_83,
         infection_severity_4th_severe_hospitalization_or_requiring_iv_antibiotics = infection_severity_82_severe_hospitalization_or_requiring_iv_antibiotics
         ) %>% 
  slice(-1)

data1 <- type.convert(data, as.is = TRUE)
```

# Data

What we did:

- The start date to calculate survival and days of onset is date_of_bs_ab_step_up_d1.   
- There was text into the variable date_of_first_bs_ab_full_dose. The text was transferred into reason_no_date_of_first_bs_ab_full_dose.  
  Patient with text have progressed.   
- max_crp has a date, now it is NA.   
- date_of_max_crs has 0/1.   
- Difference between prior_cart_0_no_1_yes and Prior CART (yes/no)? The later has 0/1 values so I am using prior_cart_0_no_1_yes.   
- baseline_crp_prior_to_bs_ab_initiation_mg_l has a "4.4." value. It was replaced by "4.4".   
- ALC Day 15 has a value of “-85“ and was replaced by 85.   
- in_out_patient was coded "In" for patient with hospital length stay values and "Out" when no values.

Issues in data with no impact for now:

- Wrong date of Discontinuation "1/0/1900" or should be NA as the value in Discontinuation (yes/no) is "No". If the date is wrong, then Discontinuation (yes/no) should be "Yes".    
- Wrong date of MM diagnosis "10/1/20218".   
- For treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays,
should I combine "CRS and Infection" and "Infection and CRS"? others? or is there an time order to consider?   
- date_of_max_ferritin has a date "20-Sep".   
- date of max crp.   
- Prior BsAb  (yes/no) has a “0” value.   
- difference between prior_bcma_directed_therapy_no_0_y_1 and prior_bcma_directed_therapy_yes_no. Looks none others that the yes/no is not recoded well so I am using 0/1 that I recoded myself.   
- #Infection_1 (Bacterial, Viral fungal) has numbers instead of “Bacterial”, “Viral” etc .

```{r temp_fix}
temp_fix <- data1 %>% 
  mutate(baseline_crp_prior_to_bs_ab_initiation_mg_l = case_when(
    baseline_crp_prior_to_bs_ab_initiation_mg_l == "4.4."        ~ 4.4,
    TRUE                  ~ as.numeric(baseline_crp_prior_to_bs_ab_initiation_mg_l)
  )) %>% 
  mutate(alc_day_15 = case_when(
    alc_day_15 == "85-"   ~ 85,
    TRUE                  ~ as.numeric(alc_day_15)
  )) %>% 
  mutate_at(c(   ############################### Remove when fix temp un necessary
              "max_crp"
  ), ~ as.numeric(.)
  )
```

```{r data cleaning}
data1 <- temp_fix %>% 
  # General----
  # Fix letter case and missing
  # mutate(across(where(is.character), ~ str_replace(., "NE|ND|N/A|Not done", NA_character_))) %>%
  mutate(across(c(where(is.character),
                  -c("pt_identifier",
                     "myeloma_involved_heavy_chain_ig_g_ig_a_ig_m_ig_d_ig_e_or_blank",
                     "best_documented_emd_response"
                     )),
                ~ str_to_sentence(.) )) %>%
  mutate(across(c(contains("vgpr"), #"response_to_bridging_chemotherapy"
                  ),
                ~ str_to_upper(.) )) %>%
  # Recode 0/1
  mutate_at(c("bs_ab_served_only_as_pre_car_t_bridging_0_no_1_yes",
              "pfs_with_1st_line_mm_diagnosis_18_months_0_no_1_yes",
              "oligo_or_non_secretory_at_bs_ab_initiation_0_no_1_yes", 
              "deletion_17p_prior_to_bs_ab_0_no_1_yes",
              "t_4_14_prior_to_bs_ab_0_no_1_yes",
              "t_14_16_prior_to_bs_ab_0_no_1_yes",
              "gain_amp1q21_prior_to_bs_ab_0_no_1_yes",
              "amp_1_q_only_0_no_1_yes",
              "deletion_1p_0_no_1_yes",
              "prior_auto_sct_no_0_yes_1",
              "prior_cart_0_no_1_yes",
              "amyloidosis_if_yes_fill_out_amyloid_sheet_as_well_please_once_youre_done_with_this_one_0_no_1_yes",
              "active_cns_mm_if_yes_fill_out_cns_sheet_as_well_once_done_with_this_one_0_no_1_yes",
              "active_pcl_5_percent_cp_cs_within_30_days_prior_or_after_bs_ab_initiation_0_no_1_yes",
              "prior_bcma_directed_therapy_no_0_y_1",
              "triple_class_refractory_i_mi_d_pi_anti_cd38_no_0_y_1",
              "penta_refractory_2_p_is_2_i_mi_ds_anti_cd38_no_0_y_1",
              "eligible_for_corresponding_bs_ab_trial_on_first_dose_use_trial_elig_sheet_to_help_you_no_0_y_1",
              "high_marrow_burden_50_percent_p_cs_if_checked_within_30_days_before_bs_ab_initiation_n_0_y_1",
              "prophylactic_tocilizumab_n_0_y_1",
              "recurrent_crs_n_0_y_1",
              "tocilizumab_as_tx_n_0_y_1",
              "steroid_use_as_tx_n_0_y_1",
              "anakinra_n_0_y_1",
              "infection_n_0_y_1",
              "icu_admission_during_first_cycle_n_0_y_1",
              "need_for_gcsf", "need_for_tpo_agonist",
              "ivig_use_yes_1_no_0", 
              "hemodialysis_pre_bs_ab_y_1_n_0",
              "hemodialysis_post_bs_ab_y_1_n_0",
              "modification_in_schedule_to_monthly_0_no_1_yes"
  ), 
  ~ case_when(
    . == 1                                              ~ "Yes",
    . == 0                                              ~ "No",
    TRUE                                                ~ as.character(.)
  )) %>% 
  # Recode 1/2
  mutate_at(c("any_invasive_second_primary_malignancy_exclude_non_melanoma_skin_cancer_dcis_etc_1_yes_2_no"
  ), 
  ~ case_when(
    . == 1                                              ~ "Yes",
    . == 2                                              ~ "No",
    TRUE                                                ~ NA_character_
  )) %>% 
  # Exposed, refractory
  mutate_at(c("bortezomib_status_exposed_0_vs_refractory_1_vs_naive_2",
              "carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2",
              "lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2",
              "pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2",
              "daratumumab_or_isatuximab_status_exposed_0_vs_refractory_1_vs_naive_2"
  ), 
  ~ case_when(
    . == 0                                              ~ "Exposed",
    . == 1                                              ~ "Refractory",
    . == 2                                              ~ "Naive",
    TRUE                                                ~ NA_character_
  )) %>% 
  # mutate_at(c("baseline_crp_prior_to_bs_ab_initiation_mg_l"#,   ############################### Remove when fix temp un necessary
  #             # "max_crp"
  # ), ~ as.numeric(.)
  # ) %>%
  mutate_at(c("ecog_ps_at_bs_ab_initiation_0_5"#,
              # "max_crs_grade_0_5",
              # "max_icans_grade_grade"
  ), ~ factor(.)
  ) %>%
  mutate(reason_no_date_of_first_bs_ab_full_dose = case_when(
    date_of_first_bs_ab_full_dose %in% 
      c("Cmo before receiving full dose",
        "Withdrew care after d5")              ~ date_of_first_bs_ab_full_dose
  ), .after = date_of_first_bs_ab_full_dose) %>% 
  # mutate(was_discontinued = case_when(
  #   date_of_disocntinuation_if_cotinues_enter_0 == 0     ~ "Continued",
  #   !is.na(date_of_disocntinuation_if_cotinues_enter_0)  ~ "Discontinued"
  # ), .after = ) %>%
  mutate(across(c("date_of_mm_diagnosis",
                  "date_of_bs_ab_step_up_d1",
                  "date_of_first_bs_ab_full_dose",
                  "date_of_max_ferritin",
                  "date_of_max_crp",
                  "date_of_onset_of_crs",
                  "date_of_max_crs",
                  "date_of_onset_of_icans",
                  "date_of_max_ican",
                  "date_of_infection_1st",
                  "date_of_infection_2nd",
                  "date_of_infection_3rd",
                  "date_of_infection_4th",
                  "anc_nadir_date", "hgb_nadir_date",
                  "plt_nadir_date", "date_of_ig_g_nadir",
                  "date_of_first_ivig_dose_following_bs_ab_administration",
                  "date_of_best_mrd_response_relative_to_bs_ab_start",
                  "date_of_pd",
                  "date_of_disocntinuation_if_cotinues_enter_0",
                  "date_of_death", "date_of_last_contact",
                  "date_of_first_exposure_to_prior_bcma_agent",
                  "date_of_last_exposure_to_prior_bcma_agent",
                  "date_last_exposure",
                  "while_on_bs_ab_date_of_first_documented_emd_response",
                  "date_of_best_documented_emd_response",
                  "date_of_last_imaging_before_data_cutoff_only_in_pts_who_are_still_responding"),
                ~ as.Date(., 
                          tryFormats = c("%m/%d/%y", "%m/%d/%Y"), 
                          origin = "1899-12-30"))) %>% 
  # Treatment
  mutate(bs_ab_name_tec_1_tal_2_elra_3 = case_when(
    bs_ab_name_tec_1_tal_2_elra_3 == 1        ~ "Teclistamab",
    bs_ab_name_tec_1_tal_2_elra_3 == 2        ~ "tal",
    bs_ab_name_tec_1_tal_2_elra_3 == 3        ~ "elra",
    TRUE                                      ~ as.character(bs_ab_name_tec_1_tal_2_elra_3)
  )) %>% 
  mutate(sex_0_male_1_female = case_when(
    sex_0_male_1_female == 0                  ~ "Male",
    sex_0_male_1_female == 1                  ~ "Female",
    TRUE                                      ~ as.character(sex_0_male_1_female)
  )) %>% 
  mutate(race_white_0_black_1_aapi_2_american_indian_3_other_4_unk_5 = case_when(
    race_white_0_black_1_aapi_2_american_indian_3_other_4_unk_5 == 0        ~ "White",
    race_white_0_black_1_aapi_2_american_indian_3_other_4_unk_5 == 1        ~ "Black",
    race_white_0_black_1_aapi_2_american_indian_3_other_4_unk_5 == 2        ~ "Asian American and Pacific Islander",
    race_white_0_black_1_aapi_2_american_indian_3_other_4_unk_5 == 3        ~ "American_indian",
    race_white_0_black_1_aapi_2_american_indian_3_other_4_unk_5 == 4        ~ "Other",
    race_white_0_black_1_aapi_2_american_indian_3_other_4_unk_5 == 5        ~ "Unknown",
    TRUE                                      ~ as.character(race_white_0_black_1_aapi_2_american_indian_3_other_4_unk_5)
  )) %>% 
  mutate(hispanic_1_if_hispanic_latin_x_or_spanish_origin_0_if_no_unknown = case_when(
    hispanic_1_if_hispanic_latin_x_or_spanish_origin_0_if_no_unknown == 0        ~ "No/Unknown",
    hispanic_1_if_hispanic_latin_x_or_spanish_origin_0_if_no_unknown == 1        ~ "Hispanic, latinX, spanish origin",
    TRUE                                      ~ as.character(hispanic_1_if_hispanic_latin_x_or_spanish_origin_0_if_no_unknown)
  )) %>%

  mutate(myeloma_involved_light_chain_kappa_lambda_biclonal_blank = case_when(
    myeloma_involved_light_chain_kappa_lambda_biclonal_blank == "K"        ~ "Kappa",
    TRUE                                      ~ as.character(myeloma_involved_light_chain_kappa_lambda_biclonal_blank)
  )) %>%

  mutate(pcl_5_percent_cp_cs_at_any_point_from_dx_through_last_pre_bs_ab_lo_t_0_no_1_secondary_pcl_not_at_dx_2_primary_pcl_at_dx = case_when(
    pcl_5_percent_cp_cs_at_any_point_from_dx_through_last_pre_bs_ab_lo_t_0_no_1_secondary_pcl_not_at_dx_2_primary_pcl_at_dx == 0        ~ "No",
    pcl_5_percent_cp_cs_at_any_point_from_dx_through_last_pre_bs_ab_lo_t_0_no_1_secondary_pcl_not_at_dx_2_primary_pcl_at_dx == 1        ~ "Secondary PCL (not at Dx)",
    pcl_5_percent_cp_cs_at_any_point_from_dx_through_last_pre_bs_ab_lo_t_0_no_1_secondary_pcl_not_at_dx_2_primary_pcl_at_dx == 2        ~ "Primary PCL (at Dx)",
    TRUE                                      ~ as.character(pcl_5_percent_cp_cs_at_any_point_from_dx_through_last_pre_bs_ab_lo_t_0_no_1_secondary_pcl_not_at_dx_2_primary_pcl_at_dx)
  )) %>%

  mutate(number_infection_1_bacterial_viral_fungal) %>%

  mutate(infection_severity_1st_severe_hospitalization_or_requiring_iv_antibiotics = case_when(
    infection_severity_1st_severe_hospitalization_or_requiring_iv_antibiotics == "N/a"        ~ NA_character_,
    TRUE       ~ infection_severity_1st_severe_hospitalization_or_requiring_iv_antibiotics
  )) %>%
  mutate(in_out_patient = case_when(
    is.na(if_inpatient_length_of_hospital_stay_total_days_including_all_admissions_0_if_done_outpt_with_no_admissions)
    ~ "Out",
    !is.na(if_inpatient_length_of_hospital_stay_total_days_including_all_admissions_0_if_done_outpt_with_no_admissions)
    ~ "In"
  ), .after = if_inpatient_length_of_hospital_stay_total_days_including_all_admissions_0_if_done_outpt_with_no_admissions) %>% 
  mutate(days_of_icu_admission = case_when(
    days_of_icu_admission == 0             ~ NA_real_,
    TRUE                                   ~ days_of_icu_admission
  )) %>%

  mutate(treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays = str_replace(
    treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays, 
    "1", "Infection")) %>% 
  mutate(treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays = str_replace(
    treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays, 
    "2", "Cytopenias")) %>% 
  mutate(treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays = str_replace(
    treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays, 
    "3", "CRS")) %>% 
  mutate(treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays = str_replace(
    treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays, 
    "4", "ICANS")) %>% 
  mutate(treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays = str_replace(
    treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays, 
    "5", "Other")) %>% 
  # mutate(treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays = case_when(
    # treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays == 1        ~ "Infection",
    # treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays == 2        ~ "Cytopenias",
    # treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays == 3        ~ "CRS",
    # treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays == 4        ~ "ICANS",
    # treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays == 5        ~ "Other",
  #   TRUE                                      ~ treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays
  # )) %>%

  mutate(reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain = case_when(
    reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain == 1        ~ "PD",
    reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain == 2        ~ "Toxicity",
    reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain == 3        ~ "Ongoing response",
    reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain == 4        ~ "Death",
    reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain == 5        ~ "Other",
    TRUE                                      ~ reason_for_discontinuation_pd_1_toxicity_2_ongoing_response_3_death_4_other_5_explain
  )) %>%

  mutate(cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain = case_when(
    cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain == 1        ~ "PD",
    cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain == 2        ~ "infection_while_of_bs_ab",
    cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain == 3        ~ "CRS",
    cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain == 4        ~ "ICANS",
    cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain == 5        ~ "Others",
    TRUE                                      ~ as.character(cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain)
  )) %>%

  mutate(type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3 = case_when(
    type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3 == 1        ~ "ADC",
    type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3 == 2        ~ "CART",
    type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3 == 3        ~ "BsAb",
    TRUE                                      ~ as.character(type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3)
  )) %>%

  mutate(response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 = case_when(
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == 1        ~ "CR",
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == 2        ~ "VGPR",
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == 3        ~ "PR",
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == 4        ~ "SD",
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == 5        ~ "PD",
    response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6 == 6        ~ "NE",
    TRUE                                      ~ as.character(response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6)
  )) %>%

  mutate(just_prior_to_bs_ab_initiation_is_there_true_emd_if_none_move_to_column_gk_0_none_1_paraskeletal_only_2_true_emd_paraskeletal = case_when(
    just_prior_to_bs_ab_initiation_is_there_true_emd_if_none_move_to_column_gk_0_none_1_paraskeletal_only_2_true_emd_paraskeletal == 0        ~ "None",
    just_prior_to_bs_ab_initiation_is_there_true_emd_if_none_move_to_column_gk_0_none_1_paraskeletal_only_2_true_emd_paraskeletal == 1        ~ "Paraskeletal only",
    just_prior_to_bs_ab_initiation_is_there_true_emd_if_none_move_to_column_gk_0_none_1_paraskeletal_only_2_true_emd_paraskeletal == 2        ~ "True EMD (+/-paraskeletal)",
    TRUE                                      ~ as.character(just_prior_to_bs_ab_initiation_is_there_true_emd_if_none_move_to_column_gk_0_none_1_paraskeletal_only_2_true_emd_paraskeletal)
  )) %>%

  mutate(total_number_true_emd_plasmacytomas_if_1_2_sites_write_1_or_2_if_2_plasmacytomas_just_write_3 = case_when(
    total_number_true_emd_plasmacytomas_if_1_2_sites_write_1_or_2_if_2_plasmacytomas_just_write_3 == 1        ~ "1 site",
    total_number_true_emd_plasmacytomas_if_1_2_sites_write_1_or_2_if_2_plasmacytomas_just_write_3 == 2        ~ "2 sites",
    total_number_true_emd_plasmacytomas_if_1_2_sites_write_1_or_2_if_2_plasmacytomas_just_write_3 == 3        ~ ">2 sites",
    TRUE                                      ~ as.character(total_number_true_emd_plasmacytomas_if_1_2_sites_write_1_or_2_if_2_plasmacytomas_just_write_3)
  )) %>%

  mutate(xrt_2_weeks_before_and_after_3_months_of_bs_ab_starting_yes_no_response = case_when(
    xrt_2_weeks_before_and_after_3_months_of_bs_ab_starting_yes_no_response == "N"         ~ "No",
    TRUE                                      ~ xrt_2_weeks_before_and_after_3_months_of_bs_ab_starting_yes_no_response
  )) %>%
  mutate(true_emd_relapse_yes_no = case_when(
    true_emd_relapse_yes_no == "Y"         ~ "Yes",
    is.na(true_emd_relapse_yes_no)         ~ NA_character_,
    TRUE                                   ~ as.character(true_emd_relapse_yes_no)
  )) %>%

  mutate(if_yes_what_location_0_same_site_1_new_site_2_both = case_when(
    if_yes_what_location_0_same_site_1_new_site_2_both == 0        ~ "Same site",
    if_yes_what_location_0_same_site_1_new_site_2_both == 1        ~ "New site",
    if_yes_what_location_0_same_site_1_new_site_2_both == 2        ~ "Both",
    TRUE                                      ~ as.character(if_yes_what_location_0_same_site_1_new_site_2_both)
  ))

# Fix the "<" and ">" to take the min or max or each column including numbers next to the signs----
# Also replace "Suboptimal" by NA
vec_col <- c("ig_g_nadir_during_first_6_cycles_mg_d_l",
             "baseline_ig_g_prior_to_bs_ab_initiation_mg_d_l"
             )
class(data1) <- "data.frame"

for (i in vec_col) {

  if (class(data1[, i]) == "character") {

    data1 <- data1 %>% 
      mutate(wo_sign = as.numeric(str_remove(data1[, i], ">|<"))) %>% 
      mutate(!!i := case_when(
        str_detect(data1[, i], ">")                 ~ max(wo_sign, na.rm = TRUE),
        str_detect(data1[, i], "<")                 ~ min(wo_sign, na.rm = TRUE),
        TRUE                                         ~ as.numeric(wo_sign)
      )) %>% 
      select(-c(wo_sign))
  }
}

```

```{r}
data2 <- data1 %>% 
  # Age categories----
  mutate(agecat = case_when(
    age_at_bs_ab_initiation < 70                                         ~ "< 70 years",
    age_at_bs_ab_initiation >= 70                                        ~ "≥ 70 years"
  ),
  agecat = factor(agecat, levels = c("< 70 years", "≥ 70 years")),
  .after = age_at_bs_ab_initiation
  ) %>% 
  # Sex categories----
  mutate(male_sex = case_when(
    sex_0_male_1_female == "Male"                                    ~ 1,
    sex_0_male_1_female == "Female"                                  ~ 0
  ), .after = sex_0_male_1_female) %>%

  # ECOG
  mutate(ecog_ps_at_bs_ab_initiation_0_5 = case_when(
    ecog_ps_at_bs_ab_initiation_0_5 == 0 |
      ecog_ps_at_bs_ab_initiation_0_5 == 1                                ~ "0-1",
    ecog_ps_at_bs_ab_initiation_0_5 %in% c(2:5)                           ~ "2-5"
  )) %>%
  # Cytogenetics ----
  mutate(cytogenetics = case_when(
    deletion_17p_prior_to_bs_ab_0_no_1_yes == "Yes" | 
      t_4_14_prior_to_bs_ab_0_no_1_yes == "Yes" | 
      t_14_16_prior_to_bs_ab_0_no_1_yes == "Yes"             ~ "Yes",
    deletion_17p_prior_to_bs_ab_0_no_1_yes == "No" &
      t_4_14_prior_to_bs_ab_0_no_1_yes == "No" &
      t_14_16_prior_to_bs_ab_0_no_1_yes == "No"               ~ "No",
    TRUE                                                           ~ NA_character_
  ), .before = deletion_17p_prior_to_bs_ab_0_no_1_yes) %>% 
  # Refractory status ----
  mutate(lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 = case_when(
    str_detect(
      lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2, "Ref")     ~ "Refractory",
    TRUE           ~ lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2
  )) %>% 
  mutate(immuno = case_when(
    lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" |
      pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory"           ~ "Yes",
    TRUE                                                           ~ "No"
  ), .after = pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2) %>% 
  mutate(proteasome = case_when(
    bortezomib_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" |
      carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory"            ~ "Yes",
    TRUE                                                           ~ "No"
  ), .after = carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2) %>% 
  mutate(dara = case_when(
    daratumumab_or_isatuximab_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory"            ~ "Yes",
    TRUE                                                           ~ "No"
  ), .after = daratumumab_or_isatuximab_status_exposed_0_vs_refractory_1_vs_naive_2) %>% 
  mutate(doubleref = case_when(
    proteasome == "Yes" &
      immuno == "Yes"                                              ~ "Yes",
    TRUE                                                           ~ "No"
  ), .after = proteasome) %>% 
  # mutate(triple_class_refractory_i_mi_d_pi_anti_cd38_no_0_y_1 = case_when(
  #   proteasome == "Yes" &
  #     immuno == "Yes" &
  #     daratumumab_or_isatuximab_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory"          ~ "Yes",
  #   TRUE                                                           ~ "No"
  # )) %>% 
  # mutate(penta_refractory_2_p_is_2_i_mi_ds_anti_cd38_no_0_y_1 = case_when(
  #   bortezomib_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" & 
  #     carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" &
  #     lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" & 
  #     pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory" & 
  #     daratumumab_or_isatuximab_status_exposed_0_vs_refractory_1_vs_naive_2 == "Refractory"          ~ "Yes",
  #   TRUE                                                           ~ "No"
  # )) %>% 
  mutate(number_of_prior_lines_of_therapy_before_bs_ab_cat = case_when(
    number_of_prior_lines_of_therapy_before_bs_ab <= 4                        ~ "≤ 4",
    number_of_prior_lines_of_therapy_before_bs_ab > 4                         ~ "> 4"
  ))
```

```{r toxicities}
cart2 <- data2 %>% 
# CRS ----
  mutate(CRS_any = ifelse(max_crs_grade_0_5 == 0, "No", "Yes"),
       crs_any_coded_0_1 = ifelse(CRS_any == "No", 0, 1),
       CRS_gradecat = case_when(
         max_crs_grade_0_5 == 0                             ~ "No CRS",
         max_crs_grade_0_5 == 1                             ~ "Grade 1 or 2",
         max_crs_grade_0_5 == 2                             ~ "Grade 1 or 2",
         max_crs_grade_0_5 >= 3                             ~ "Grade ≥3"),
       CRS_gradecat = factor(CRS_gradecat, levels = c("No CRS", "Grade 1 or 2", "Grade ≥3")),
       gr3_CRS = case_when(
         max_crs_grade_0_5 %in% c(0:2)                      ~ "Grade <3",
         max_crs_grade_0_5 %in% c(3:5)                      ~ "Grade ≥3",
         TRUE                                                   ~ NA_character_
       ), .after = max_crs_grade_0_5) %>% 
  mutate(gr2_CRS = case_when(
    max_crs_grade_0_5 %in% c(0:1)                      ~ "Grade <2",
    max_crs_grade_0_5 %in% c(2:5)                      ~ "Grade ≥2",
    TRUE                                               ~ NA_character_
  ), .after = CRS_any) %>%
  mutate(day_of_onset_crs_relative_to_initiation =
           interval(start = date_of_bs_ab_step_up_d1, end = date_of_onset_of_crs) /
           duration(n =1, unit = "days")
  ) %>%
  mutate(day_of_max_crs_relative_to_initiation =
           interval(start = date_of_bs_ab_step_up_d1, end = date_of_max_crs) /
           duration(n =1, unit = "days")
  ) %>%
  mutate(day_of_onset_icans_relative_to_initiation =
           interval(start = date_of_bs_ab_step_up_d1, end = date_of_onset_of_icans) /
           duration(n =1, unit = "days")
  ) %>%
  mutate(day_of_max_icans_grade_relative_to_initiation =
           interval(start = date_of_bs_ab_step_up_d1, end = date_of_max_ican) /
           duration(n =1, unit = "days")
  ) %>%
  # censored days > 100 to 100
  # mutate(across(c(day_of_onset_crs_relative_to_initiation,
  #                 day_of_max_crs_relative_to_initiation,
  #                 day_of_onset_icans_relative_to_initiation,
  #                 day_of_max_icans_grade_relative_to_initiation), ~ case_when(
  #   . > 100                                                       ~ 100,
  #   TRUE                                                          ~ as.numeric(.)
  # ))) %>%

  # ICANS ----
  mutate(ICANS_any = ifelse(max_icans_grade == 0, "No", "Yes"),
       ICANS_any2 = ifelse(ICANS_any == "No", 0, 1),
       ICANS_gradecat = case_when(
         max_icans_grade == 0                                ~ "No ICANS",
         max_icans_grade == 1                                ~ "Grade 1 or 2",
         max_icans_grade == 2                                ~ "Grade 1 or 2",
         max_icans_grade >= 3                                ~ "Grade ≥3"),
       ICANS_gradecat = factor(ICANS_gradecat, levels = c("No ICANS", "Grade 1 or 2", "Grade ≥3")),
       gr3_ICANS = case_when(
         max_icans_grade %in% c(0:2)                         ~ "Grade <3",
         max_icans_grade %in% c(3:5)                         ~ "Grade ≥3",
         TRUE                                          ~ NA_character_
       ), .after = max_icans_grade) %>% 
  mutate(gr2_ICANS = case_when(
    max_icans_grade %in% c(0:1)                              ~ "Grade <2",
    max_icans_grade %in% c(2:5)                              ~ "Grade ≥2",
    TRUE                                               ~ NA_character_
  ), .after = ICANS_any2)
  # BCMA ----

```

```{r survival}
cart3 <- cart2 %>% 
  # pfs
  mutate(pfs_event = case_when(
    !is.na(date_of_pd) | !is.na(date_of_death)         ~ 1,
    TRUE                                               ~ 0
  ), .after = death_yes_no) %>% 
  mutate(pfs_date = coalesce(date_of_pd, date_of_death, date_of_last_contact), 
         .after = death_yes_no) %>% 
  mutate(pfs_from_initiation_months = 
           interval(
             start = date_of_bs_ab_step_up_d1, 
             end = pfs_date)/
           duration(n=1, units = "months"), 
         .after = death_yes_no) %>% 
  # os 
  mutate(os_event = case_when(
    !is.na(date_of_death)                              ~ 1,
    TRUE                                               ~ 0
  ), 
  .after = death_yes_no) %>% 
  mutate(os_date = coalesce(date_of_death, date_of_last_contact), 
         .after = death_yes_no) %>% 
  mutate(os_from_initiation_months = 
           interval(
             start = date_of_bs_ab_step_up_d1, 
             end = os_date)/
           duration(n=1, units = "months"), 
         .after = death_yes_no)
```

```{r response}
cart4 <- cart3 %>%   
  # mutate(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd = case_when(
  #   str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "evaluable")   ~ NA_character_,
  #   TRUE           ~ day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd
  # )) %>% 
  mutate(day30_response = case_when(
    (os_event == 1 | pfs_event == 1) & 
      pfs_from_initiation_months < 1                                   ~ "Died or progressed before day 30",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "EVAL")        ~ NA_character_,
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "VGPR")        ~ "VGPR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "PR")          ~ "PR",
    # str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "UCR")	       ~ "UCR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "CR")          ~ "sCR or CR",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "MR") |
      str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "SD")        ~ "SD",
    str_detect(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, "PD")          ~ "PD",
    is.na(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd)                     ~ NA_character_,
    TRUE           ~ day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd
  ), .after = day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd) %>% 
  mutate(day30_response_v2 = case_when(
    str_detect(day30_response, "Died")                               ~ "PD",
    is.na(day30_response)                                            ~ NA_character_,
    TRUE           ~ day30_response
  ), .after = day30_response) %>% 
  mutate(ORR_30days = case_when(
    str_detect(day30_response_v2, "CR|PR")                           ~ "ORR",
    is.na(day30_response_v2)                                         ~ NA_character_,
    TRUE                                                             ~ "PD/SD/MR"
  ), .after = day30_response_v2) %>% 
  mutate(CRorbetter_30days = case_when(
    str_detect(day30_response_v2, "CR")	                             ~ "sCR or CR",
    is.na(day30_response_v2)                                         ~ NA_character_,
    TRUE                                                             ~ "Others"
  ), .after = ORR_30days) %>% 
  # Day 90 response ----
  mutate(mon3_response = case_when(
    day30_response_v2 == "PD"                                        ~ "PD",
    (os_event == 1 | pfs_event == 1) & 
      pfs_from_initiation_months < 3                                   ~ "Died or progressed before 3 months",
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "EVAL")      ~ NA_character_,
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "VGPR")      ~ "VGPR",
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "PR")        ~ "PR",
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "CR")	       ~ "sCR or CR",
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "MR") |
      str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "SD")      ~ "SD",
    str_detect(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, "PD")       ~ "PD",
    is.na(day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd)                     ~ NA_character_,
    TRUE           ~ day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd
  ), .after = day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd) %>% 
  mutate(mon3_response_v2 = case_when(
    str_detect(mon3_response, "Died")                              ~ "PD",
    is.na(mon3_response)                                           ~ NA_character_,
    TRUE           ~ mon3_response
  ), .after = mon3_response) %>% 
  mutate(ORR_mon3 = case_when(
    str_detect(mon3_response_v2, "CR|PR")                          ~ "ORR",
    is.na(mon3_response_v2)                                        ~ NA_character_,
    TRUE                                                            ~ "PD/SD/MR"
  ), .after = mon3_response_v2) %>% 
  mutate(CRorbetter_mon3 = case_when(
    mon3_response_v2 == "sCR or CR"                        	      ~ "sCR or CR",
    is.na(mon3_response_v2)                                        ~ NA_character_,
    TRUE                                                            ~ "Others"
  ), .after = ORR_mon3) %>%

    # Best response
  mutate(ORR_as_best_response = case_when(
    ORR_30days == "ORR" |
    ORR_mon3 == "ORR" #|
    # ORR_mon6 == "ORR" |
    # ORR_mon9 == "ORR" |
    # ORR_mon12 == "ORR"                                            
                                                                  ~ "ORR",
    is.na(ORR_30days) & 
      is.na(ORR_mon3) #& 
      # is.na(ORR_mon6) & 
      # is.na(ORR_mon9) &
      # is.na(ORR_mon12)                                            
                                                                  ~ NA_character_, 
     TRUE                                                         ~ "SD/PD"
  ), .after = CRorbetter_mon3) %>% 
  mutate(best_CRorbetter = case_when(
     CRorbetter_30days == "sCR or CR" | 
       CRorbetter_mon3 == "sCR or CR" #| 
       # CRorbetter_mon6 == "sCR or CR" | 
       # CRorbetter_mon9 == "sCR or CR" | 
       # CRorbetter_mon12 == "sCR or CR"                            
                                                                   ~ "sCR or CR",
     is.na(CRorbetter_30days) & 
       is.na(CRorbetter_mon3) #& 
       # is.na(CRorbetter_mon6) & 
       # is.na(CRorbetter_mon9) & 
       # is.na(CRorbetter_mon12) 
                                                                   ~ NA_character_, 
     TRUE                                                         ~ "< CR"
   ), .after = CRorbetter_mon3) %>%
  mutate(best_response = case_when(
    day30_response_v2 == "sCR or CR" |
      mon3_response_v2 == "sCR or CR" #|
      # mon6_response_v2 == "sCR or CR" |
      # mon9_response_v2 == "sCR or CR" |
      # mon12_response_v2 == "sCR or CR"                            
                                                                  ~ "sCR or CR",
    day30_response_v2 == "VGPR" |
      mon3_response_v2 == "VGPR" #|
      # mon6_response_v2 == "VGPR" |
      # mon9_response_v2 == "VGPR" |
      # mon12_response_v2 == "VGPR"                                 
                                                                  ~ "VGPR",
    day30_response_v2 == "PR" |
      mon3_response_v2 == "PR" #|
      # mon6_response_v2 == "PR" |
      # mon9_response_v2 == "PR" |
      # mon12_response_v2 == "PR"                                   
                                                                  ~ "PR",
    day30_response_v2 == "SD" |
      mon3_response_v2 == "SD" #|
      # mon6_response_v2 == "SD" |
      # mon9_response_v2 == "SD" |
      # mon12_response_v2 == "SD"                                   
                                                                  ~ "SD",
    day30_response_v2 == "PD" |
      mon3_response_v2 == "PD" #|
      # mon6_response_v2 == "PD" |
      # mon9_response_v2 == "PD" |
      # mon12_response_v2 == "PD"                                   
                                                                  ~ "PD",
    TRUE                                                          ~ NA_character_
  ), .after = best_CRorbetter) %>% 
  mutate(best_ORRcollapsed = case_when(
    str_detect(best_response, "CR|PR")                            ~ "PR or better", 
    str_detect(best_response, "SD|PD")                            ~ "< PR",
    TRUE                                                          ~ NA_character_
  ), .after = best_response) #%>% 
  # MRD----
  # mutate(across(c(contains("mrd_by_")),
  #           ~ case_when(
  #             . == "Positive"                                     ~ "Positive",
  #             . == "Negative"                                     ~ "Negative",
  #             TRUE                                                ~ NA_character_
  #           ))) %>%
  # mutate(MRD_day30 = coalesce(day_30_mrd_by_clono_seq_positive_vs_negative, 
  #                              day_30_mrd_by_flow_positive_vs_negative
  # )) %>%
  # mutate(MRD_mon3 = coalesce(x3_month_mrd_by_clono_seq_positive_vs_negative,
  #                              x3_month_mrd_by_flow_positive_vs_negative
  # )) %>% 
  # mutate(MRD_mon6 = coalesce(x6_month_mrd_by_clono_seq_positive_vs_negative,
  #                              x6_month_mrd_by_flow_positive_vs_negative
  # )) %>%
  # mutate(MRD_mon9 = coalesce(x9_month_mrd_by_clono_seq_positive_vs_negative,
  #                              x9_month_mrd_by_flow_positive_vs_negative
  # )) %>% 
  # mutate(MRD_mon12 = coalesce(x12_month_mrd_by_clono_seq_positive_vs_negative,
  #                              x12_month_mrd_by_flow_positive_vs_negative
  # )) %>% 
  # mutate(response_MRD_day30 = case_when(
  #   day30_response_v2 == "sCR or CR" & 
  #     MRD_day30 == "Negative"                                     ~ "sCR or CR, MRD-",
  #   day30_response_v2 == "sCR or CR" & 
  #     MRD_day30 == "Positive"                                     ~ "sCR or CR, MRD+",
  #   day30_response_v2 == "sCR or CR" & 
  #     is.na(MRD_day30)                                            ~ "sCR or CR, MRD unknown",
  #   TRUE ~ day30_response_v2
  # )) %>%
  # mutate(response_MRD_mon3 = case_when(
  #   mon3_response_v2 == "sCR or CR" & 
  #     MRD_mon3 == "Negative"                                      ~ "sCR or CR, MRD-",
  #   mon3_response_v2 == "sCR or CR" & 
  #     MRD_mon3 == "Positive"                                      ~ "sCR or CR, MRD+",
  #   mon3_response_v2 == "sCR or CR" & 
  #     is.na(MRD_mon3)                                             ~ "sCR or CR, MRD unknown",
  #   TRUE ~ mon3_response_v2
  # )) %>%
  # mutate(response_MRD_mon6 = case_when(
  #   mon6_response_v2 == "sCR or CR" & 
  #     MRD_mon6 == "Negative"                                      ~ "sCR or CR, MRD-",
  #   mon6_response_v2 == "sCR or CR" & 
  #     MRD_mon6 == "Positive"                                      ~ "sCR or CR, MRD+",
  #   mon6_response_v2 == "sCR or CR" & 
  #     is.na(MRD_mon6)                                             ~ "sCR or CR, MRD unknown",
  #   TRUE ~ mon6_response_v2
  # )) %>%
  # mutate(response_MRD_mon9 = case_when(
  #   mon9_response_v2 == "sCR or CR" & 
  #     MRD_mon9 == "Negative"                                      ~ "sCR or CR, MRD-",
  #   mon9_response_v2 == "sCR or CR" & 
  #     MRD_mon9 == "Positive"                                      ~ "sCR or CR, MRD+",
  #   mon9_response_v2 == "sCR or CR" & 
  #     is.na(MRD_mon9)                                             ~ "sCR or CR, MRD unknown",
  #   TRUE ~ mon9_response_v2
  # )) %>%
  # mutate(response_MRD_mon12 = case_when(
  #   mon12_response_v2 == "sCR or CR" & 
  #     MRD_mon12 == "Negative"                                      ~ "sCR or CR, MRD-",
  #   mon12_response_v2 == "sCR or CR" & 
  #     MRD_mon12 == "Positive"                                      ~ "sCR or CR, MRD+",
  #   mon12_response_v2 == "sCR or CR" & 
  #     is.na(MRD_mon12)                                             ~ "sCR or CR, MRD unknown",
  #   TRUE ~ mon12_response_v2
  # )) %>% 
  # mutate(best_response_MRD = case_when (
  #   response_MRD_day30 == "sCR or CR, MRD-" | 
  #     response_MRD_mon3 == "sCR or CR, MRD-" | 
  #     response_MRD_mon6 == "sCR or CR, MRD-" | 
  #     response_MRD_mon9 == "sCR or CR, MRD-" | 
  #     response_MRD_mon12 == "sCR or CR, MRD-"                      ~ "sCR or CR, MRD-",
  #    response_MRD_day30 == "sCR or CR, MRD+" | 
  #     response_MRD_mon3 == "sCR or CR, MRD+" | 
  #     response_MRD_mon6 == "sCR or CR, MRD+" | 
  #     response_MRD_mon9 == "sCR or CR, MRD+" | 
  #     response_MRD_mon12 == "sCR or CR, MRD+"                      ~ "sCR or CR, MRD+",
  #    response_MRD_day30 == "sCR or CR, MRD unknown" | 
  #     response_MRD_mon3 == "sCR or CR, MRD unknown" | 
  #     response_MRD_mon6 == "sCR or CR, MRD unknown" | 
  #     response_MRD_mon9 == "sCR or CR, MRD unknown" | 
  #     response_MRD_mon12 == "sCR or CR, MRD unknown"               ~ "sCR or CR, MRD unknown",
  #   TRUE ~ best_response
  # )) %>%
  # mutate(MRDneg_in_best_response = case_when(
  #   MRD_day30 ==  "Negative" |
  #     MRD_mon3 ==  "Negative" |
  #     MRD_mon6 ==  "Negative" |
  #     MRD_mon9 ==  "Negative" |
  #     MRD_mon12 ==  "Negative"                                    ~ "Negative",
  #   MRD_day30 ==  "Positive" |
  #   MRD_mon3 ==  "Positive" |
  #   MRD_mon6 ==  "Positive" |
  #   MRD_mon9 ==  "Positive" |
  #     MRD_mon12 ==  "Positive"                                    ~ "Positive",
#   TRUE                                                          ~ NA_character_
# )) %>% 
  # mutate(bridging_response = case_when(
  #   response_to_bridging_chemotherapy == "MR" |
  #     response_to_bridging_chemotherapy == "SD/MR" |
  #     response_to_bridging_chemotherapy == "SD" |
  #     response_to_bridging_chemotherapy == "PD" |
  #     response_to_bridging_chemotherapy == "No"               ~ "SD/PD",
  #   response_to_bridging_chemotherapy == "CR" |
  #     response_to_bridging_chemotherapy == "PR" |
  #     response_to_bridging_chemotherapy == "VGPR"             ~ "PR or better",
  #   response_to_bridging_chemotherapy == "Not Evaluable" |
  #     response_to_bridging_chemotherapy == "ND" |
  #     response_to_bridging_chemotherapy == "Unknown"          ~ NA_character_,
  #   TRUE                                                      ~ NA_character_ 
  # ))
```

```{r infection}
bsab_data <- cart4 %>%
  # Infection ----
  mutate(time_from_bsab_therapy_to_infection_days = 
           interval(
             start = date_of_bs_ab_step_up_d1, 
             end = date_of_infection_1st)/
           duration(n=1, units = "days"), 
         # no need of the following for this data but keep in case
         time_from_bsab_therapy_to_infection_days = case_when(
    time_from_bsab_therapy_to_infection_days >= 0     ~ time_from_bsab_therapy_to_infection_days,
    TRUE                                          ~ NA_real_
    ), .after = date_of_infection_1st) #%>% 
  # mutate(any_infection = case_when(
  #   time_from_bsab_therapy_to_infection_days >= 0     ~ infection_yes_1_no_0,
  #   TRUE                                          ~ "No"
  # )) %>%
  # mutate(any_sevinfection = case_when(
  #   time_from_bsab_therapy_to_infection_days >= 0     ~ severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0,
  #   TRUE                                          ~ "No"
  # )) %>% 
  # mutate(across(c("infection_type_details", "infection_type_bacterial_viral_fungal_parasitic",
  #                 "infection_type_cat"), ~ case_when(
  #   time_from_bsab_therapy_to_infection_days >= 0     ~ .,
  #   TRUE                                          ~ NA_character_
  # ))) %>% 
  # mutate(overall_hlh = case_when(
  #   hlh == "Yes" |
  #   hlh_hlh_like_toxicities == "Yes"              ~ "Yes",
  #   hlh == "No" &
  #   hlh_hlh_like_toxicities == "No"               ~ "No"
  # ))

# cart7 <- cart6 %>% 
#   mutate(infection = case_when(
#     notinfused=="YES" ~ NA_character_,
#     notinfused=="NO" & is.na(`Infection Type`) & is.na(`Infection (Yes, No)`) ~ NA_character_,
#     notinfused=="NO" & `Infection Type` == "No" ~ "No", 
#     notinfused=="NO" & `Infection Type` != "No" ~ "Yes",
#     notinfused=="NO" & is.na(`Infection Type`) ~ "No",
#     TRUE ~ NA_character_
#   )) %>%
#   mutate(infection_type = case_when(
#     infection=="No" | is.na(infection) ~ NA_character_,
#     infection=="Yes" & `Infection Details (specific infection, ie. E.coli bacteremia, etc.)` == "fungus was unidentified" ~ "Fungal",
#     infection== "Yes" & `Infection Details (specific infection, ie. E.coli bacteremia, etc.)` == "E. coli bacteremia and Salmonella GI infection treated with ceftriaxone x 7 days" ~ "Bacterial",
#     infection=="Yes" & `Infection Type`=="bacterial + viral" ~ "Bacterial + Viral",
#     infection=="Yes" & `Infection Type`=="viral" ~ "Viral",
#     infection=="Yes" & `Infection Type`=="All of the above" ~ "Bacterial, Viral, and Fungal",
#     infection=="Yes" & `Infection Type`=="Bacterial; Viral; Bacterial" ~ "Bacterial + Viral",
#     infection=="Yes" & `Infection Type`=="Viral; Bacterial; Bacterial" ~ "Bacterial + Viral",
#     TRUE ~ `Infection Type`
#   )) %>% 
#   mutate(infection_severity = case_when(
#      infection=="No" | is.na(infection) ~ NA_character_,
#      infection=="Yes" & is.na(`Infection Severity (Severe = hospitalization or requiring IV antibiotics)`) ~ NA_character_,
#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="severe" ~ "Severe",
#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="Yes" ~ "Severe",
#      infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="non-severe" ~ "Not severe",
#     infection=="Yes" & `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`=="Non-Severe" ~ "Not severe",
#     TRUE ~ `Infection Severity (Severe = hospitalization or requiring IV antibiotics)`
#   )) %>%
#   mutate(infection_type = factor(infection_type, levels = c("Bacterial", "Fungal", "Viral", "Bacterial + Fungal", "Bacterial + Viral", "Bacterial, Viral, and Fungal")))
```

```{r Labeling}
## Labeling ----
var_label(bsab_data) <- list(age_at_bs_ab_initiation = "Patient age", agecat = "Patient age - Categories",

                             bs_ab_name_tec_1_tal_2_elra_3 = "Therapy name",
                             bs_ab_served_only_as_pre_car_t_bridging_0_no_1_yes = "Served as pre-CART bridging",
                             pfs_with_1st_line_mm_diagnosis_18_months_0_no_1_yes = "PFS 1st line",

                         male_sex = "Male Sex", sex_0_male_1_female = "Sex",
                         race_white_0_black_1_aapi_2_american_indian_3_other_4_unk_5 = "Race",
                         hispanic_1_if_hispanic_latin_x_or_spanish_origin_0_if_no_unknown = "Ethnicity",
                         # race_eth = "Race and ethnicity",
                         # extramedullary_disease_yes_no = "Extramedullary disease",
                         # circulating_plasma_cell = "UPDATED Circulating Plasma Cells",
                         high_marrow_burden_50_percent_p_cs_if_checked_within_30_days_before_bs_ab_initiation_n_0_y_1 = 
                           "High marrow burden (≥50%)",
                         ecog_ps_at_bs_ab_initiation_0_5 = "ECOG PS at therapy initiation",
                         # `ECOG > or = 2? (Yes, No)` ,
                         # r_iss_at_car_t_initiation = "R-ISS at cart initiation",
                         oligo_or_non_secretory_at_bs_ab_initiation_0_no_1_yes = "Oligo or non secretory at initiation",
                         myeloma_involved_heavy_chain_ig_g_ig_a_ig_m_ig_d_ig_e_or_blank = "Myeloma involved heavy chain",
                         myeloma_involved_light_chain_kappa_lambda_biclonal_blank = "Myeloma involved light chain",
                         prior_cart_0_no_1_yes = "Received prior CART",
                         amyloidosis_if_yes_fill_out_amyloid_sheet_as_well_please_once_youre_done_with_this_one_0_no_1_yes =
                           "Amyloidosis",
                         active_cns_mm_if_yes_fill_out_cns_sheet_as_well_once_done_with_this_one_0_no_1_yes = 
                           "Active CNS",
                         pcl_5_percent_cp_cs_at_any_point_from_dx_through_last_pre_bs_ab_lo_t_0_no_1_secondary_pcl_not_at_dx_2_primary_pcl_at_dx = 
                           "PCL (?5% CPCs) at any point from Dx through last pre-BsAb LoT?",
                         active_pcl_5_percent_cp_cs_within_30_days_prior_or_after_bs_ab_initiation_0_no_1_yes = 
                           "Active PCL (?5% CPCs) within 30 days prior or after BsAb initiation?",
                         percent_cp_cs_if_pb_checked_within_30_days_before_bs_ab_initiation = 
                           "% CPCs if PB checked within 30 days before BsAb initiation",
                         prophylactic_tocilizumab_n_0_y_1 = "Prophylactic Tocilizumab",

                         cytogenetics = "High risk cytogenetics (not include gain 1q)", 
                         deletion_17p_prior_to_bs_ab_0_no_1_yes = "Deletion 17p at initiation", 
                         t_4_14_prior_to_bs_ab_0_no_1_yes = "t(4:14) at initiation", 
                         t_14_16_prior_to_bs_ab_0_no_1_yes = "t(4:16) at initiation", 
                         gain_amp1q21_prior_to_bs_ab_0_no_1_yes = "Gain/amp 1q21",
                         amp_1_q_only_0_no_1_yes = "Amp 1q only",
                         deletion_1p_0_no_1_yes = "Deletion 1p",
                         number_of_prior_lines_of_therapy_before_bs_ab = "Number of prior lines of therapy",
                         number_of_prior_lines_of_therapy_before_bs_ab_cat = "Number of prior lines of therapy (cat)",
                         # bridging_therapy_yes_no = "Bridging Therapy",
                         prior_auto_sct_no_0_yes_1 = "Prior autoSCT",
                         # prior_allo_sct_within_6_months_before_apheresis = "Prior alloSCT",
                         prior_bcma_directed_therapy_no_0_y_1 = "Prior BCMA-directed therapy",
                         need_for_gcsf = "Granulocyte colony stimulating factor (G-CSF)",
                         ivig_use_yes_1_no_0 = "Intravenous immunoglobulin (IVIG)",
                         # cd34_stem_cell_boost_yes_1_no_0 = "CD34 stem cell boost",
                         # day_of_neutrophil_recovery = "Day of neutrophil recovery",
                         # transfusion_postCART = "Transfusion post-CAR T",
                         need_for_tpo_agonist = "Thrombopoietin (TPO) agonist",
                         # bmicat = "BMI at apheresis - Normal, Overweight, Obese", 
                         steroid_use_as_tx_n_0_y_1 = "Steroid Use", tocilizumab_as_tx_n_0_y_1 = "Tocilizumab Use", 
                         anakinra_n_0_y_1 = "Anakinra Use",
                         proteasome = "Refractory to Proteasome Inhibitors", 
                         lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 = "Refractory to Lenalidomide",
                         bortezomib_status_exposed_0_vs_refractory_1_vs_naive_2 = "Refractory to Bortezomib", 
                         carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2 = "Refractory to Carfilzomib", 
                         pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2 = "Refractory to Pomalidomide",
                         dara = "Refractory to Daratumumab or Isatuximab",
                         immuno = "Refractory to Immunomodulators", doubleref = "Double refractory", 
                         triple_class_refractory_i_mi_d_pi_anti_cd38_no_0_y_1= "Triple refractory", 
                         penta_refractory_2_p_is_2_i_mi_ds_anti_cd38_no_0_y_1= "Penta refractory",

                         baseline_b2m_prior_to_bs_ab_initiation = "Baseline B2M prior to therapy",
                         baseline_ldh_prior_to_bs_ab_initiation_u_l = "Baseline LDH prior to therapy (u/l)",
                         baseline_albumin_prior_to_bs_ab_initiation_g_d_l = "Baseline albumin prior to therapy (g/dl)",
                         baseline_ferritin_prior_to_bs_ab_initiation_ng_m_l = "Baseline ferritin prior to therapy (ng/ml)",
                         max_ferritin = "Max ferritin",
                         baseline_crp_prior_to_bs_ab_initiation_mg_l = "Baseline CRP prior to therapy (mg/l)",
                         max_crp = "Max CRP",
                         baseline_ig_g_prior_to_bs_ab_initiation_mg_d_l = "Baseline Igg prior to therapy (mg/dl)",
                         baseline_anc_k_u_l_ie_100_200_etc = "Baseline ANC (k/ul) ie_100_200",
                         baseline_hgb = "Baseline HGB",
                         baseline_pl_ts = "baseline PLTs",
                         baseline_alc_k_u_l_ie_100_200_etc = "Baseline ALC (k/ul) ie_100_200",
                         alc_day_8 = "ALC day8",
                         alc_day_15 = "ALC day15",
                         alc_day_22 = "ALC day22",
                         alc_c2d1 = "ALC C2D1",
                         c2d1_ig_g_level_if_checked_mg_d_l = "C2D1 Igg (mg/dl)",
                         anc_nadir_value_during_first_6_cycles_k_u_l_ie_100_200_etc = "ANC during first 6 cycles (nadir)",
                         hgb_nadir_value_during_first_6_cycles = "HGB during first 6 cycles (nadir)",
                         plt_nadir_value_during_first_6_cycles = "PLT during first 6 cycles (nadir)",
                         ig_g_nadir_during_first_6_cycles_mg_d_l = "Igg during first 6 cycles (nadir)",
                         cr_cl_prior_to_step_up_dose_number_1_m_l_min = "CrCl prior to step up dose 1 (ml/min)",
                         cr_cl_at_d30 = "CrCl day 30",
                         cr_cl_at_d90 = "CrCl day 90",
                         hemodialysis_pre_bs_ab_y_1_n_0 = "Hemodialysis pre-BsAb",
                         hemodialysis_post_bs_ab_y_1_n_0 = "Hemodialysis post-BsAb",
                         number_of_prior_bcma_directed_agents = "Number of prior BCMA",
                         prior_adc_yes_no = "Prior ADC",
                         prior_adc_name = "Prior ADC name",
                         # prior_cart_yes_no = "Prior CART",
                         prior_cart_name = "Prior CART name",
                         prior_bs_ab_yes_no = "Prior BsAb",
                         prior_bs_ab_name = "Prior BsAb name",
                         prior_gprc5d_yes_no = "Prior gprc5d",
                         talquetamab_toxicities_oral_toxicities_e_g_dysgeusia_if_so_describe =
                           "Talquetamab toxicities",
                         just_prior_to_bs_ab_initiation_is_there_true_emd_if_none_move_to_column_gk_0_none_1_paraskeletal_only_2_true_emd_paraskeletal = 
                           "EMD prior to BsAb initiation",
                         total_number_true_emd_plasmacytomas_if_1_2_sites_write_1_or_2_if_2_plasmacytomas_just_write_3 =
                           "Total number true EMD",
                         total_number_paraskelatal_plasmacytomas = "Total number paraskelatal plasmacytomas",
                         true_emd_relapse_yes_no = "True EMD relapse",
                         best_documented_emd_response = "Best documented EMD response",
                         xrt_2_weeks_before_and_after_3_months_of_bs_ab_starting_yes_no_response =
                           "XRT 2 weeks before and after  3 months of BsAb",
                         # bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese", 
                         max_crs_grade_0_5 = "CRS Grade (0-5)",
                         CRS_any = "Any CRS", CRS_gradecat = "CRS Grade", 
                         gr2_CRS = "Grade2 CRS",
                         gr3_CRS = "Grade3 CRS",
                         recurrent_crs_n_0_y_1 = "Recurrent CRS",
                         max_icans_grade = "ICANS Grade (0-5)",
                         ICANS_any = "Any ICANS", ICANS_gradecat = "ICANS Grade", 
                         gr2_ICANS = "Grade 2 ICANS",
                         day_of_onset_crs_relative_to_initiation = "Day of onset of CRS relative to initiation",
                         day_of_max_crs_relative_to_initiation = "Day of Max CRS (relative to initiation)",
                         duration_of_crs_days = "Duration of CRS (days)", 
                         day_of_onset_icans_relative_to_initiation = "Day of onset of ICANS relative to initiation",
                         day_of_max_icans_grade_relative_to_initiation = "Day of Max ICANS (relative to initiation)",
                         duration_of_icans_days = "Duration of ICANS (days)", 
                         # delayed_neuro = "Delayed Neurotoxicity",
                         # parkinsonian_neurotoxicity_yes_no = "Parkinsonian Neurotoxicity",
                         # other_delayed_non_parkinsonian_neurologic_toxicity_yes_no = 
                         #   "Other/Delayed Non-Parkinsonian Neurologic Toxicity",
                         # delayed_neuro_type = "Delayed Neurotoxicity Type",
                         # hlh = "HLH", hlh_hlh_like_toxicities = "HLH/HLH-Like Toxicities?",
                         # overall_hlh = "Combined HLHs",
                         infection_n_0_y_1 = "Infection",
                         time_from_bsab_therapy_to_infection_days = "Time from BsAb to infection (days)",
                         number_of_infections = "Total number of infections",
                         number_infection_1_bacterial_viral_fungal = "Infection type (1st)",
                         infection_severity_1st_severe_hospitalization_or_requiring_iv_antibiotics = "Infection severity (1st)",
                         number_infection_2_bacterial_viral_fungal = "Infection type (2nd)",
                         infection_severity_2nd_severe_hospitalization_or_requiring_iv_antibiotics = "Infection severity (2nd)",
                         number_infection_3_bacterial_viral_fungal = "Infection type (3rd)",
                         infection_severity_3rd_severe_hospitalization_or_requiring_iv_antibiotics = "Infection severity (3rd)",
                         number_infection_4_bacterial_viral_fungal = "Infection type (4th)",
                         infection_severity_4th_severe_hospitalization_or_requiring_iv_antibiotics = "Infection severity (4th)",

                         treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays =
                           "Cause for treatment delays during first cycle",
                         icu_admission_during_first_cycle_n_0_y_1 = "ICU admission during first cycle",
                         days_of_icu_admission = "Days of ICU admission",
                         in_out_patient = "In/Out patient",
                         if_inpatient_length_of_hospital_stay_total_days_including_all_admissions_0_if_done_outpt_with_no_admissions = 
                           "Length of hospital stay total (days)",
                         # tbv = "TBV", whole_blood_processed_m_l = "Whole blood processed (mL)",
                         # final_collection_volume_m_l = "Final collection volume (mL)", 
                         # tbv_processed = "TBV processed", 
                         # access_type = "Access type", total_bags = "Total bags",
                         # run_time_min = "Run time (min)",
                         # total_dose_volume_m_l = "Total dose volume (mL)", 
                         # cell_dose_million_cells = "Total cell dose (million cells)",
                         day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd = "Raw day 30 Response",
                         day30_response = "Day 30 Response - Evaluable patients",
                         day30_response_v2 = "Day 30 Response - All patients",
                         ORR_30days = "Day 30 ORR",
                         CRorbetter_30days = "Day 30 CR or better - Evaluable patients",

                         day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd = "Raw day 90 Response",
                         mon3_response = "Day 90 Response - Evaluable patients",
                         mon3_response_v2 = "Day 90 Response - All patients",
                         ORR_mon3 = "Day 90 ORR",
                         CRorbetter_mon3 = "Day 90 CR or better - Evaluable patients",

                         best_CRorbetter = "Best CR or better - Evaluable patients",
                         best_response = "Best Response - Evaluable patients",
                         best_ORRcollapsed = "Best ORR at ≤ 3 months",
                         ORR_as_best_response = "ORR as best response",
                         best_response_s_cr_cr_vgpr_pr_mr_sd_pd = "Raw best response",
                         best_response_mrd_flow_positive_vs_negative = "Raw best MRD response (flow)",
                         best_response_mrd_clonoseq_positive_vs_negative = "Raw best MRD response (clonoseq)",
                         progression_yes_no = "Progression",
                         pfs_event = "PFS events",
                         pfs_from_initiation_months = "PFS time (months)",
                         death_yes_no = "Death",
                         os_event = "OS events",
                         os_from_initiation_months = "Follow-up time from initiation (months)",
                         cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain =
                           "Cause of death",

                         discontinuation_yes_no = "Discontinuation",

                         eligible_for_corresponding_bs_ab_trial_on_first_dose_use_trial_elig_sheet_to_help_you_no_0_y_1 =
                           "Eligible for corresponding BsAb trial on first dose"#,
                         # best_response = "Best response in first 90 days"
)

```
<br>

# Tables
## Table 1. Patient characteristics
```{r Table 1}
bsab_data %>% 
  select(age_at_bs_ab_initiation, agecat, 
         sex_0_male_1_female, #male_sex, 
         race_white_0_black_1_aapi_2_american_indian_3_other_4_unk_5, 
         hispanic_1_if_hispanic_latin_x_or_spanish_origin_0_if_no_unknown, 
         ecog_ps_at_bs_ab_initiation_0_5,
         in_out_patient) %>%
  tbl_summary(by = in_out_patient,
    # type = list(
    #   c(agecat, sex, 
    #     extramedullary_disease_yes_no, high_marrow_burden_50_percent,
    #     cytogenetics, cytogenetics_incl_1q,
    #     deletion_17p_prior_to_bs_ab_0_no_1_yes,
    #     t_4_14_prior_to_bs_ab_0_no_1_yes,
    #     t_14_16_prior_to_bs_ab_0_no_1_yes, gain_amp1q21,
    #     bridging_therapy_yes_no, prior_auto_sct_no_0_yes_1,
    #     prior_bcma_directed_therapy_no_0_y_1,
    #     # `Received alkylating therapy with bridging (Yes=1, No=0)`,
    #     immuno, proteasome, dara, doubleref, triple_class_refractory_i_mi_d_pi_anti_cd38_no_0_y_1, penta_refractory_2_p_is_2_i_mi_ds_anti_cd38_no_0_y_1,
    #     did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
    #     ht_score, early_icaht_cat, any_early_icaht,
    #      gr3_early_icaht, 
    #      late_icaht_cat, any_late_icaht,
    #      gr3_late_icaht)
    #   ~"categorical"),

    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_footnote(list(update = everything() ~ NA))
```

## Table 2. Disease characteristics
```{r Table 2}
bsab_data %>% 
  select(oligo_or_non_secretory_at_bs_ab_initiation_0_no_1_yes, myeloma_involved_heavy_chain_ig_g_ig_a_ig_m_ig_d_ig_e_or_blank, 
         myeloma_involved_light_chain_kappa_lambda_biclonal_blank, 
         high_marrow_burden_50_percent_p_cs_if_checked_within_30_days_before_bs_ab_initiation_n_0_y_1,
         cytogenetics, deletion_17p_prior_to_bs_ab_0_no_1_yes, 
         t_4_14_prior_to_bs_ab_0_no_1_yes, t_14_16_prior_to_bs_ab_0_no_1_yes, gain_amp1q21_prior_to_bs_ab_0_no_1_yes, 
         amp_1_q_only_0_no_1_yes, deletion_1p_0_no_1_yes,
         amyloidosis_if_yes_fill_out_amyloid_sheet_as_well_please_once_youre_done_with_this_one_0_no_1_yes, 
         active_cns_mm_if_yes_fill_out_cns_sheet_as_well_once_done_with_this_one_0_no_1_yes, 
         pcl_5_percent_cp_cs_at_any_point_from_dx_through_last_pre_bs_ab_lo_t_0_no_1_secondary_pcl_not_at_dx_2_primary_pcl_at_dx, 
         active_pcl_5_percent_cp_cs_within_30_days_prior_or_after_bs_ab_initiation_0_no_1_yes, 
         eligible_for_corresponding_bs_ab_trial_on_first_dose_use_trial_elig_sheet_to_help_you_no_0_y_1,
         in_out_patient) %>%
  tbl_summary(by = in_out_patient,
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_footnote(list(update = everything() ~ NA))
```

## Table 3. Hospital
```{r table 3}
bsab_data %>% 
  select(in_out_patient,
         if_inpatient_length_of_hospital_stay_total_days_including_all_admissions_0_if_done_outpt_with_no_admissions, 
         icu_admission_during_first_cycle_n_0_y_1, days_of_icu_admission
         ) %>%
  tbl_summary(type = list(days_of_icu_admission ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>%# add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_footnote(list(update = everything() ~ NA))
```

## Table 4. Baseline
```{r table 4}
bsab_data %>% 
  select(percent_cp_cs_if_pb_checked_within_30_days_before_bs_ab_initiation,
         baseline_b2m_prior_to_bs_ab_initiation, 
         baseline_ldh_prior_to_bs_ab_initiation_u_l, baseline_albumin_prior_to_bs_ab_initiation_g_d_l, 
         baseline_ferritin_prior_to_bs_ab_initiation_ng_m_l, max_ferritin, 
         baseline_crp_prior_to_bs_ab_initiation_mg_l, max_crp, 
         baseline_ig_g_prior_to_bs_ab_initiation_mg_d_l,
         ig_g_nadir_during_first_6_cycles_mg_d_l,
         c2d1_ig_g_level_if_checked_mg_d_l, 
         baseline_anc_k_u_l_ie_100_200_etc, anc_nadir_value_during_first_6_cycles_k_u_l_ie_100_200_etc, 
         baseline_hgb, hgb_nadir_value_during_first_6_cycles, 
         baseline_pl_ts, plt_nadir_value_during_first_6_cycles, 
         baseline_alc_k_u_l_ie_100_200_etc, alc_day_8, alc_day_15, alc_day_22, alc_c2d1, 
         in_out_patient) %>%
  tbl_summary(by = in_out_patient,
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_footnote(list(update = everything() ~ NA))
```

## Table 5. Therapies
```{r table 5}
bsab_data %>% 
  select(bs_ab_name_tec_1_tal_2_elra_3, bs_ab_served_only_as_pre_car_t_bridging_0_no_1_yes,
         prior_cart_0_no_1_yes, #prior_cart_yes_no, 
         prior_cart_name, prior_bs_ab_yes_no, prior_bs_ab_name, 
         prior_adc_yes_no, prior_adc_name, 
         prior_bcma_directed_therapy_yes_no, prior_bcma_directed_therapy_no_0_y_1, 
         number_of_prior_bcma_directed_agents, 
         type_of_most_recent_bcma_agent_adc_1_cart_2_bs_ab_3, most_recent_bcma_agent_name, 
         response_to_most_recent_bmca_agent_cr_1_vgpr_2_pr_3_sd_4_pd_5_ne_6, prior_gprc5d_yes_no,
         prophylactic_tocilizumab_n_0_y_1,
         tocilizumab_as_tx_n_0_y_1, steroid_use_as_tx_n_0_y_1, anakinra_n_0_y_1,
         ivig_use_yes_1_no_0,

         need_for_gcsf, need_for_tpo_agonist,

         treatment_delays_during_first_cycle_infection_1_cytoepnias_2_crs_3_icans_4_other_5_explain_leave_blank_if_no_delays,
         number_of_prior_lines_of_therapy_before_bs_ab_cat,
         number_of_prior_lines_of_therapy_before_bs_ab, prior_auto_sct_no_0_yes_1,

         bortezomib_status_exposed_0_vs_refractory_1_vs_naive_2, carfilzomib_status_exposed_0_vs_refractory_1_vs_naive_2, 
         proteasome, 
         lenalidomide_status_exposed_0_vs_refractory_1_vs_naive_2, pomalidomide_status_exposed_0_vs_refractory_1_vs_naive_2, 
         immuno, daratumumab_or_isatuximab_status_exposed_0_vs_refractory_1_vs_naive_2, dara, 
         doubleref, 
         triple_class_refractory_i_mi_d_pi_anti_cd38_no_0_y_1, 
         penta_refractory_2_p_is_2_i_mi_ds_anti_cd38_no_0_y_1,

         talquetamab_toxicities_oral_toxicities_e_g_dysgeusia_if_so_describe, 
         talquetamab_only_target_dose_for_c2d1_0_4_q1w_0_8_q2w_or_other,
         x147_reason_for_stopping_talquetamab_if_not_for_pd_be_specific, 
         x148_tal_specifically_designed_as_pre_car_t_holding_or_bridging_y_n,
         in_out_patient) %>%
  tbl_summary(by = in_out_patient,
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_footnote(list(update = everything() ~ NA))
```

## Table 6. Toxicities
```{r Table 6}
bsab_data %>% 
  select(max_crs_grade_0_5, CRS_any, #crs_any_coded_0_1, 
         CRS_gradecat, 
         gr2_CRS, gr3_CRS, duration_of_crs_days, 
         recurrent_crs_n_0_y_1, 
         day_of_onset_crs_relative_to_initiation, 
         day_of_max_crs_relative_to_initiation, 
         max_icans_grade, ICANS_any, ICANS_any2, gr2_ICANS, ICANS_gradecat, 
         gr3_ICANS, duration_of_icans_days,
         day_of_onset_icans_relative_to_initiation, day_of_max_icans_grade_relative_to_initiation,
         cr_cl_prior_to_step_up_dose_number_1_m_l_min, cr_cl_at_d30, cr_cl_at_d90, 
         hemodialysis_pre_bs_ab_y_1_n_0, 
         hemodialysis_post_bs_ab_y_1_n_0,
         in_out_patient) %>%
  tbl_summary(by = in_out_patient,
              type = list(
                c(duration_of_crs_days, duration_of_icans_days,
                  day_of_onset_icans_relative_to_initiation, day_of_max_icans_grade_relative_to_initiation) ~ "continuous"),
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_footnote(list(update = everything() ~ NA))
```

## Table 7. Responses
```{r Table 7}
bsab_data %>% 
  select(day_30_response_s_cr_cr_vgpr_pr_mr_sd_pd, 
         day30_response, day30_response_v2, ORR_30days, CRorbetter_30days, day_90_response_s_cr_cr_vgpr_pr_mr_sd_pd, 
         mon3_response, mon3_response_v2, ORR_mon3, CRorbetter_mon3, best_CRorbetter, best_response, best_ORRcollapsed, 
         ORR_as_best_response, best_response_s_cr_cr_vgpr_pr_mr_sd_pd, best_response_mrd_flow_positive_vs_negative, 
         best_response_mrd_clonoseq_positive_vs_negative,
         just_prior_to_bs_ab_initiation_is_there_true_emd_if_none_move_to_column_gk_0_none_1_paraskeletal_only_2_true_emd_paraskeletal,
         total_number_true_emd_plasmacytomas_if_1_2_sites_write_1_or_2_if_2_plasmacytomas_just_write_3, 
         locations_of_true_emd_be_specific, total_number_paraskelatal_plasmacytomas, 
         xrt_2_weeks_before_and_after_3_months_of_bs_ab_starting_yes_no_response, best_documented_emd_response, 
         true_emd_relapse_yes_no, if_yes_what_location_0_same_site_1_new_site_2_both, concurrent_biochemical_relpase_yes_no, 
         concurrent_pmd_relapse_yes_no,
         in_out_patient) %>%
  tbl_summary(by = in_out_patient,
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_footnote(list(update = everything() ~ NA))
```

## Table 8. Clinical outcomes
```{r Table 8}
bsab_data %>% 
  select(progression_yes_no, pfs_from_initiation_months, #pfs_event, 
         death_yes_no, #os_event, 
         os_from_initiation_months, 
         cause_of_death_pd_1_infection_while_of_bs_ab_2_crs_3_icans_4_other_5_explain,
         in_out_patient) %>%
  tbl_summary(by = in_out_patient,
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_footnote(list(update = everything() ~ NA))
```

## Table 9. Infections
```{r table 9}
bsab_data %>% 
  select(infection_n_0_y_1, number_of_infections, number_infection_1_bacterial_viral_fungal, 
         infection_severity_1st_severe_hospitalization_or_requiring_iv_antibiotics, time_from_bsab_therapy_to_infection_days, 
         number_infection_2_bacterial_viral_fungal, infection_severity_2nd_severe_hospitalization_or_requiring_iv_antibiotics, 
         number_infection_3_bacterial_viral_fungal, infection_severity_3rd_severe_hospitalization_or_requiring_iv_antibiotics, 
         number_infection_4_bacterial_viral_fungal, infection_severity_4th_severe_hospitalization_or_requiring_iv_antibiotics,
         in_out_patient) %>%
  tbl_summary(by = in_out_patient,
              type = list(
                c(number_of_infections) ~ "continuous"),
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_footnote(list(update = everything() ~ NA))
```

# Survival
## OS
```{r Survival analysis - KM by in_out_patient}
ggsurvplot(survfit(Surv(os_from_initiation_months, os_event) ~ in_out_patient, 
                   data = bsab_data),
           # title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(15, "bold", "black"),
           font.y = c(15, "bold", "black"),
           font.legend = c(14, "black"),
           font.tickslab = c(12, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           ylab = "OS (probability)",
           legend = "top",
           legend.title = "",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           risk.table = TRUE, risk.table.y.text = TRUE,
           tables.theme = theme_survminer(#base_size = 5,
                                          font.main = c(14, "bold", "black"),
                                          # font.x = c(10, "bold", "black"),
                                          # font.y = c(16, "bold", "transparent"),
                                          # font.tickslab = c(19, "bold", "black")
                                          )
) %++% guides(colour = guide_legend(nrow = 1))

coxph(Surv(time = bsab_data$os_from_initiation_months, 
                   event = bsab_data$os_event) ~ in_out_patient, 
              data = bsab_data)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```

## PFS
```{r PFS analysis - KM by in_out_patient}
ggsurvplot(survfit(Surv(pfs_from_initiation_months, pfs_event) ~ in_out_patient, 
                   data = bsab_data),
           # title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(15, "bold", "black"),
           font.y = c(15, "bold", "black"),
           font.legend = c(14, "black"),
           font.tickslab = c(12, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           ylab = "PSS (probability)",
           legend = "top",
           legend.title = "",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           risk.table = TRUE, risk.table.y.text = TRUE,
           tables.theme = theme_survminer(#base_size = 5,
                                          font.main = c(14, "bold", "black"),
                                          # font.x = c(10, "bold", "black"),
                                          # font.y = c(16, "bold", "transparent"),
                                          # font.tickslab = c(19, "bold", "black")
                                          )
) %++% guides(colour = guide_legend(nrow = 1))

coxph(Surv(time = bsab_data$pfs_from_initiation_months, 
                   event = bsab_data$pfs_event) ~ in_out_patient, 
              data = bsab_data)  %>% 
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```

### 2025-06-13 cilta_cel/Manuscript analyses.Rmd
Update figure code for publication requirements

@@
   geom_boxplot() + 
-  xlab("Days") + ylab("LDH represented with a log2 scale") + 
+  xlab("Days") + ylab("LDH (log2 scale)") + 
   theme_classic() + ggtitle("LDH") + 
   scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 1.2 
+  stat_compare_means(label.x = 1.2 , label.y.npc = 0.95,
+                     size = 5
                      # aes(label = paste0("p = ", ..p.format..))
@@
 
-# cart1$`Ferritin day +7`[cart1$`Ferritin day +7`==">33511"] <- 33511
+# cart1$`Ferritin day +7`[cart1$`Ferritin day +7`==">33511"] <- /33511
 # cart1$`Ferritin day +7` <- as.numeric(cart1$`Ferritin day +7`)
@@
   geom_boxplot() + 
-  xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
+  xlab("Days") + ylab("Ferritin (log2 scale)") + 
   theme_classic() + ggtitle("Ferritin") + 
   scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 1.2 
+  stat_compare_means(label.x = 1.2 , label.y.npc = 0.95,
+                     size = 5
                      # aes(label = paste0("p = ", ..p.format..))
@@
   geom_boxplot() + 
-  xlab("Days") + ylab("CRP represented with a log2 scale") + 
+  xlab("Days") + ylab("CRP (log2 scale)") + 
   theme_classic() + ggtitle("CRP") + 
   scale_y_continuous(trans = "log2") +
-  stat_compare_means(label.x = 1.2
+  stat_compare_means(label.x = 1.2, label.y.npc = 0.95,
+                     size = 5
                      # aes(label = paste0("p = ", ..p.format..))
@@
 (CRP)+
-plot_annotation(tag_levels = "A")
-
-# ggsave("Figure S1 Inflammatory markers after cilta-cel.pdf",
+plot_annotation(tag_levels = "A") &
+  theme(plot.tag = element_text(size = 17),
+        text = element_text(size = 16))
+
+# ggsave("Figure S1 Inflammatory markers after cilta-cel_03-12-25_300dpi.pdf",
 #        width = 6,
 #        height = 10)
+
+ggsave("Figure S1 Inflammatory markers after cilta-cel_600dpi_1column_compress.tiff",
+       dpi = 600, units = "in",
+       width = 8,
+       height = 11, compression = "lzw")
+
 ```
@@
   (Plt_fig | IgG_fig | CD19_fig) +
-  plot_annotation(tag_levels = "A")
-
-# ggsave("Figure 2 Cellular and humoral immune reconstitution after cilta-cel.pdf",
-#        width = 15, 
-#        height = 8)
+  plot_annotation(tag_levels = "A") &
+  theme(plot.tag = element_text(size = 15),
+        axis.title = element_text(size = 13),
+        axis.text.y = element_text(size = 11),
+        axis.text.x = element_text(size = 8),
+        legend.title = element_text(size = 13),
+        legend.text = element_text(size = 11))
+
+ggsave("Figure 2 Cellular and humoral immune reconstitution after cilta-cel_600dpi_2column.tiff",
+       dpi = 600, units = "in",
+       width = 16,
+       height = 8)
+
+# (WBC_fig | ANC_fig) /
+#   (CD4_fig | Hb_fig) / 
+#   (ALC_fig | CD8_fig) /
+#   (Plt_fig | IgG_fig) / 
+#   (CD19_fig | plot_spacer()) +
+#   plot_annotation(tag_levels = "A") &
+#   theme(plot.tag = element_text(size = 16),
+#         axis.title = element_text(size = 16),
+#         axis.text.y = element_text(size = 14),
+#         axis.text.x = element_text(size = 13),
+#         legend.title = element_text(size = 16),
+#         legend.text = element_text(size = 14))
+# 
+# ggsave("Figure 2 Cellular and humoral immune reconstitution after cilta-cel_600dpi_2column_.jpeg",
+#        dpi = 600, units = "in",
+#        width = 16,
+#        height = 13)
+
 ```
@@
            position=position_dodge(width=0.9))+
-  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 3,
+  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 4,
             position = position_dodge(width=0.9), vjust=-1.5
@@
   theme_classic(base_size = 9)+
-  theme(legend.position="bottom")
-
-# ggsave("Figure 3 Cytopenias over time.pdf",
-#        width = 7,
-#        height = 4)
+  theme(legend.position="bottom", text = element_text(size = 16))
+
+ggsave("Figure 3 Cytopenias over time_600dpi_1column_compress.tiff",
+       dpi = 600, units = "in",
+       width = 8,
+       height = 4, compression = "lzw")
+
+c %>% filter(grade == "Grade 3+") %>% 
+  ggplot(aes(x= day, 
+             y= perc, 
+             fill= name, 
+             ))+
+  geom_bar(stat = "identity",
+           position=position_dodge(width=0.9))+
+  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 7,
+            position = position_dodge(width=0.9), vjust=-1.5
+            )+
+
+  scale_fill_brewer(palette = "Spectral")+
+  ylim(0, 60)+
+  labs(fill = NULL, x= NULL, y = "Percent")+
+  theme_classic(base_size = 9)+
+  theme(legend.position="bottom", text = element_text(size = 20))
+ggsave("Figure 3 Cytopenias over time_600dpi_2column_compress.tiff",
+       dpi = 600, units = "in",
+       width = 16,
+       height = 8, compression = "lzw")
 
@@
 #            font.main = c(20, "bold", "black"),
-#            font.x = c(12, "bold", "black"),
-#            font.y = c(12, "bold", "black"),
-#            font.legend = c(12, "black"),
-#            font.tickslab = c(10, "bold", "black"),
+#            font.x = c(15, "bold", "black"),
+#            font.y = c(15, "bold", "black"),
+#            font.legend = c(14, "black"),
+#            font.tickslab = c(12, "bold", "black"),
 #            size = 1.5,
@@
   # geom_point(aes(color = `Infection severity`), position = "jitter")
-  labs(x = NULL, y = "Infection onset time (days)")+
+  labs(x = NULL, y = "Infection onset (days)")+
   scale_color_manual(values = c("black", "red"))+
@@
                                    # vjust = 0.5
-                                   ))
+                                   ), 
+        text = element_text(size = 15))
 
@@
   geom_jitter(aes(color = `Infection severity`), width = 0.2)+
-  labs(x = NULL, y = "Infection onset time (days)")+
+  labs(x = NULL, y = "Infection onset (days)")+
   scale_color_manual(values = c("black", "red"))+
@@
   c +
-  plot_annotation(tag_levels = "A")
-
-# ggsave("Figure 4 Infection density.pdf",
-#        width = 7,
-#        height = 10)
+  plot_annotation(tag_levels = "A")&
+  theme(plot.tag = element_text(size = 15),
+        axis.title = element_text(size = 15),
+        axis.text = element_text(size = 13),
+        legend.text = element_text(size = 15), 
+        legend.title = element_text(size = 15))
+
+ggsave("Figure 4 Infection density_600dpi_1column_compress.tiff",
+       dpi = 600, units = "in",
+       width = 8,
+       height = 11, compression = "lzw")
 
@@
   # (alluvial_C) +
-  plot_annotation(tag_levels = "A")
-
-# ggsave("Figure S3. Viral titers after cilta-cel.pdf",
-#        width = 7,
-#        height = 10)
+  plot_annotation(tag_levels = "A")&
+  theme(text = element_text(size = 15)#,
+        # plot.tag = element_text(size = 15)
+        )
+
+ggsave("Figure S3. Viral titers after cilta-cel_600dpi_1column.tiff",
+       dpi = 600, units = "in",
+       width = 8,
+       height = 10, compression = "lzw")
 ```
@@
   # (alluvial_C) 
-  plot_annotation(tag_levels = "A")
-
-# ggsave("Figure S3+day180 Viral titers after cilta-cel.pdf",
-#        width = 7,
-#        height = 10)
+  plot_annotation(tag_levels = "A")&
+  theme(text = element_text(size = 15))
+
+ggsave("Figure S3+day180 Viral titers after cilta-cel_600dpi_1column_compress.tiff",
+       dpi = 600, units = "in",
+       width = 8,
+       height = 10, compression = "lzw")
 ```
@@
         row_names_side = "left",
-        row_names_gp = gpar(fontsize = 11),
+        row_names_gp = gpar(fontsize = 14),
+        heatmap_legend_param = list(labels_gp = gpar(fontsize = 14)),
         col = colors)
-pdf("Figure S4 Pneumococcal titers after cilta-cel.pdf", 
+ht_list
+# pdf("Figure S4 Pneumococcal titers after cilta-cel.pdf", 
+#     width = 8,
+#     height = 6)
+# draw(ht_list, heatmap_legend_side = "right")
+# dev.off()
+
+tiff("Figure S4 Pneumococcal titers after cilta-cel_600dpi_1column.tiff", 
+     res = 600, units = "in",
     width = 8,
-    height = 6)
-draw(ht_list, heatmap_legend_side = "right")
+    height = 5)
+ht_list
+# draw(ht_list, heatmap_legend_side = "right")
+dev.off()
+
+ragg::agg_tiff("ht_list.tiff", width = 8,
+    height = 5, units = "in", res = 600, compression = "lzw")
+ht_list
 dev.off()
@@
   mutate(name= case_when(
-    Characteristic == "High marrow burden (≥50%)"      ~ "High marrow burden (≥50%)",
-    Characteristic == "gr3_cytopenia_-5d"      ~ "Grade ≥ 3 Cytopenia at Day -5",
+    Characteristic == "High marrow burden (≥50%)"      ~ "High marrow \nburden (≥50%)",
+    Characteristic == "gr3_cytopenia_-5d"      ~ "Grade ≥ 3 Cytopenia \nat Day -5",
     Characteristic == "Steroid Use"      ~ "Steroid use",
-    Characteristic == "Number of prior lines of therapy"      ~ "Number of prior lines of therapy",
+    Characteristic == "Number of prior lines of therapy"      ~ "Number of prior \nlines of therapy",
     Characteristic == "baseline_ferritin_cat"      ~ "Baseline ferritin"
@@
   scale_x_log10(breaks = c(0, 0.25, 0.5, 1, 2.5, 5, 10, 40))+
-  labs(y="")
-
-# ggsave("Figure S2 Forest plot 5 variables.pdf", 
-#        device = cairo_pdf,
-#        width = 7,
-#        height = 6)
+  labs(y="") %>% 
+  theme(text = element_text(size = 15),
+        axis.title.y = element_blank())
+
+ggsave("Figure S2 Forest plot 5 variables_600dpi_1column_wraplabel_compress.tiff",
+       dpi = 600, units = "in",
+       width = 8,
+       height = 4, compression = "lzw"#6
+       )
 
@@
            font.main = c(20, "bold", "black"),
-           font.x = c(12, "bold", "black"),
-           font.y = c(12, "bold", "black"),
-           font.legend = c(12, "black"),
+           font.x = c(15, "bold", "black"),
+           font.y = c(15, "bold", "black"),
+           font.legend = c(14, "black"),
            font.tickslab = c(12, "bold", "black"),
@@
            censor = TRUE,
-           risk.table = TRUE, risk.table.y.text = FALSE,
+           risk.table = TRUE, risk.table.y.text = TRUE,
            tables.theme = theme_survminer(#base_size = 5,
-                                          font.main = c(12, "bold", "black"),
+                                          font.main = c(14, "bold", "black"),
                                           # font.x = c(10, "bold", "black"),
@@
                                           )
-) + guides(colour = guide_legend(nrow = 1))
+) %++% guides(colour = guide_legend(nrow = 1))
 risk.table.ylab <- "≥ Grade 3 \ncytopenia at D90"
@@
 
-# fig_surv_cytday90 <- ggsave_workaround(myplot)
+fig_surv_cytday90 <- ggsave_workaround(myplot)
 # 
@@
            font.main = c(20, "bold", "black"),
-           font.x = c(12, "bold", "black"),
-           font.y = c(12, "bold", "black"),
-           font.legend = c(12, "black"),
-           font.tickslab = c(10, "bold", "black"),
+           font.x = c(15, "bold", "black"),
+           font.y = c(15, "bold", "black"),
+           font.legend = c(14, "black"),
+           font.tickslab = c(12, "bold", "black"),
            size = 1.5,
@@
            tables.theme = theme_survminer(
-             font.main = c(10, "bold", "black")
+             font.main = c(14, "bold", "black")
            )
-) + guides(colour = guide_legend(nrow = 1))
+) %++% guides(colour = guide_legend(nrow = 1))
 myplot
@@
 
-# fig_surv_ORR <- ggsave_workaround(myplot)
+fig_surv_ORR <- ggsave_workaround(myplot)
 # 
@@
            tables.theme = theme_survminer(
-             font.main = c(12, "bold", "black")
+             font.main = c(14, "bold", "black")
            )
-) + guides(colour = guide_legend(nrow = 1))
+) %++% guides(colour = guide_legend(nrow = 1))
 risk.table.ylab <- "≥ Grade 3 \ncytopenia at D30"
@@
 
-# fig_surv_cytday30 <- ggsave_workaround(myplot)
+fig_surv_cytday30 <- ggsave_workaround(myplot)
 # 
@@
            tables.theme = theme_survminer(
-             font.main = c(12, "bold", "black")
+             font.main = c(14, "bold", "black")
            )
-) + guides(colour = guide_legend(nrow = 1))
+) %++% guides(colour = guide_legend(nrow = 1))
 myplot
@@
 
-# fig_surv_HTscore <- ggsave_workaround(myplot)
+fig_surv_HTscore <- ggsave_workaround(myplot)
 # 
@@
 
-# fig_surv_earlyicaht <- ggsave_workaround(myplot)
+fig_surv_earlyicaht <- ggsave_workaround(myplot)
 # 
@@
 
-# fig_surv_lateicaht <- ggsave_workaround(myplot)
+fig_surv_lateicaht <- ggsave_workaround(myplot)
 # 
@@
 ```{r}
-# ggarrange(fig_surv_HTscore, fig_surv_cytday30, 
-#           fig_surv_earlyicaht, fig_surv_cytday90, 
-#           fig_surv_lateicaht, 
-#           ncol = 3, nrow = 2, 
-#           labels="AUTO")
-
-# ggsave("Survival panel.pdf", device = cairo_pdf,
+ggarrange(fig_surv_HTscore, fig_surv_cytday30,
+          fig_surv_earlyicaht, fig_surv_cytday90,
+          fig_surv_lateicaht,
+          ncol = 3, nrow = 2,
+          labels="AUTO")
+
+ggsave("Survival panel_600dpi_2column_compress.tiff", #device = cairo_pdf,
        # path = paste0(here::here(), "/cilta_cel"),
-#        width = 14, height = 11, 
+       width = 16, height = 11,
        # units = c("in"),
-#        dpi=600, 
-#        bg="white")
+       dpi=600, compression = "lzw",
+       bg="white")
+
+ggarrange(fig_surv_HTscore, fig_surv_cytday30,
+          fig_surv_cytday90, fig_surv_earlyicaht, 
+          fig_surv_lateicaht,
+          ncol = 3, nrow = 2,
+          labels="AUTO")
+
+ggsave("Survival panel_600dpi_2column_reordered_compress.tiff", #device = cairo_pdf,
+       # path = paste0(here::here(), "/cilta_cel"),
+       width = 16, height = 11,
+       # units = c("in"),
+       dpi=600, compression = "lzw",
+       bg="white")
 ```
